    
\DeclareSpell{Bloodstone Mirror}{abjuration|V,  S,  M (a red bloodstone worth 500 gp)|1 standard action|personal|Targets: you|1 hour/level||}[]
    \DeclareSpellDescription{Bloodstone Mirror}{Developed due to Arazni's fear that her stolen organs might be used to control her, this spell reflects any attempts to steal your free will. Whenever you are exposed to a mind-affecting effect or a spell that would otherwise give another creature control of your actions (such as control undead), you can dispel this effect as an immediate action to redirect the spell to a creature within 30 feet. The affected creature must attempt a save against the original DC of the triggering effect. On a failure, it is subject to the effects of the triggering spell, with the exception that you are treated as the original caster (statistics determined by caster level are still calculated according to its original caster). The target creature applies any spell resistance or immunities it has normally. You can have only one instance of this spell active at a time.}
        
\DeclareSpell{Litany Of The Red Crusader}{necromancy|V,  S,  DF|1 swift action|close (25 ft. + 5 ft./2 levels)|Targets: one creature|1 round|Fortitude negates|yes}[]
    \DeclareSpellDescription{Litany Of The Red Crusader}{Followers of Arazni have made use of this litany since her days as a crusader and herald. Each time the target creature takes piercing or slashing damage, it takes 1 point of bleed damage; this bleed damage stacks with itself. While subject to this spell, the target cannot be the target of another spell that has the word "litany" in the title.}
        
\DeclareSpell{Unspoken Name}{divination|V,  S|1 minute|personal|Targets: you|24 hours or until discharged||}[]
    \DeclareSpellDescription{Unspoken Name}{Prized among those who seek to monitor the attention paid to them, this spell is said to be used by Arazni to identify those followers who dare refer to her as "the Harlot Queen" so she might summarily dismiss them. When you cast this spell, designate a word, phrase, or name. If a creature within 1 mile of you uses that word, phrase, or name to refer to you, you immediately learn that creature's name, appearance, and location. This discharges the spell.}
    