    
\DeclareSpell{Air Of Authority}{illusion (glamer) []|V,  S|1 standard action|personal|Targetsyou|1 minute/level (D)||}[]
    \DeclareSpellDescription{Air Of Authority}{You gain an unmistakable air of authority, which clouds creatures' minds and causes them to believe that you are their direct superior. Each creature with whom you attempt to leverage your newfound authority receives a Will save to disbelieve the illusion. Otherwise, it treats you as it would its direct superior. Creatures with different direct superiors see you in different ways, which can potentially lead to conflicts that allow additional saving throws (for instance, if a cook sees you as the head chef, he might be quite perplexed to see the vizier treating you as if you were the king).}
        
\DeclareSpell{Bleaching Resistance}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|personal|Targetsyou|24 hours||}[]
    \DeclareSpellDescription{Bleaching Resistance}{Ability score drain from the Bleaching doesn't affect your ability score modifiers while you're affected by this spell. This spell does not remove the Bleaching's effect on your appearance, nor does it prevent you from suffering further ability penalties, dying, or becoming a bleachling as a result of the Bleaching.}
        
\DeclareSpell{Burn Corruption}{evocation () [fire,  good]|V,  S|1 standard action|long (400 ft. + 40 ft./level)|Area10-ft. cube/level (S)|instantaneous|Reflex half|yes}[]
    \DeclareSpellDescription{Burn Corruption}{This spell fills the area with violet flames that scour an area clean of life-especially of the corrupted life of the Abyss.  Creatures (and foliage) in the area take 1d8 points of fire damage per 2 caster levels you possess (maximum 7d8) unless they are outsiders with the chaotic and evil subtypes or are otherwise tainted by demons, in which case they instead take 1d6 points of fire damage per caster level (maximum 15d6). This fire damage ignores the fire resistance granted by the demon subtype, but it does not penetrate any other form of fire resistance or immunity.}
        
\DeclareSpell{Champion's Bout}{enchantment (compulsion) [mind-affecting]|V,  S|1 round|medium (100 ft. + 10 ft./level)|Targetstwo creatures|1 round/level|Will negates (see text)|yes (see text)}[]
    \DeclareSpellDescription{Champion's Bout}{You allow two chosen champions to fight without interference. The two creatures must be willing in order for the spell to work. After you cast this spell, any creature attempting to aid or hinder either of the two targets in any way must succeed at a Will save or lose its action instead (spell resistance applies). A creature that fails its Will save against champion's bout cannot attempt to interfere again. If a creature successfully interferes with the bout, the spell ends immediately.}
        
\DeclareSpell{Damnation Of Memory}{enchantment (compulsion) [mind-affecting]|V,  S,  F (a massive,  flawless gemstone worth 5, 000 gp)|1 hour|long (400 ft. + 40 ft./level)|Targetsall living creatures within range|permanent|Will negates|yes}[]
    \DeclareSpellDescription{Damnation Of Memory}{You name one creature and excise all memory of that creature's involvement in events the targets remember. The targets either forget who exactly performed the named creature's deeds or assume some other individual performed them. Alternatively, you can name either one event lasting no more than 10 minutes per caster level or a single topic (defined at the GM's discretion) such as a shameful secret of the king that was recently revealed or a small revolt that was quelled messily, and erase all recollection of that subject from the minds of all creatures within the area. Memory of facts and topics that are common knowledge (information with a Knowledge check DC of 10 or less) cannot be stolen via this spell.  The lost memories are stored in the focus gem (which grows dull inside and cannot be used as a focus or material component for any other spell, including another casting of this spell). The targets emanate no magic and the spell cannot be dispelled from them; only the focus retains a magic aura, and only by targeting the gem can the spell be dispelled, disjoined, or suppressed with antimagic. If the gem is destroyed or the spell is dispelled (which destroys the gem), all stolen memories return to the affected creatures.}
        
\DeclareSpell{Elemental Mastery}{transmutation () [see text]|V,  S|1 standard action|personal|Targetsyou|1 minute/level||}[]
    \DeclareSpellDescription{Elemental Mastery}{You gain mastery over the element matching the elemental essence in your blood (fire for ifrits, earth for oreads, air for sylphs, and water for undines). If you are a suli, you can choose any one of the four options as you cast this spell, but the duration is reduced to 1 round per level. Your mastery gives you an insight bonus to your speed or a new movement mode, depending on the element you master, and grants one additional benefit. This spell's descriptor matches the chosen element.     Element (Race)MovementBenefitAir Fly (suli, sylph)30 ft.+1 circumstance bonus (average) on attack rolls when both you and your foe are airborne.Earth Burrow (oread, suli)15 ft.+1 circumstance bonus on attack rolls when both you and your foe are touching the ground.Fire (ifrit, suli)+20 ft.+1 circumstance bonus all speeds on attack rolls when your foe is on fire.Water (suli, undine)+30 ft.+1 circumstance bonus swim on attack rolls when both you and your foe are touching water. }
        
\DeclareSpell{Fable Tapestry}{illusion (shadow) [shadow]|V,  S,  F (your kapenia)|1 round|close (25 ft. + 5 ft./2 levels)|Effect1 legendary character/4 caster levels|1 round/level|Will disbelief|yes}[]
    \DeclareSpellDescription{Fable Tapestry}{The spell weaves shadows and colors from your kapenia into the shape of legendary characters from Varisian folktales.  This spell functions as shadow conjuration emulating summon monster I, except as noted here. You can summon only one copy of the same character at the same time, even with multiple castings of this spell. The shadow creatures are 40\% real and are drawn from the list below.    CharacterSourceAnelda the beautiful (freelance thief)NPC Codex 147Old Mother Toad (fey giant toad)Bestiary 3 116Sonnorae the storyteller (con artist)NPC Codex 29Vyushbaro the savior (carousing champion)NPC Codex 47Winter's Son (evasive slip)NPC Codex 65Zykomso the slaver (bearded devil)Bestiary 73 }
        
\DeclareSpell{Fire's Friend}{evocation () [fire]|V,  S,  M (a flame of any size)|1 standard action|personal|Targetsyou|1 round/level||}[]
    \DeclareSpellDescription{Fire's Friend}{You cloak yourself in flames that do not harm you or your carried equipment but damage other creatures and objects. The flames cast light as a torch. Any creature that attacks you with a non-reach melee weapon or that begins its turn engaged in a grapple with you takes 1d6 points of fire damage and must succeed at a Reflex save or catch fire. The creature can negate the damage (and avoid catching fire) with spell resistance. Any time you end your movement in the same square as a flammable object or creature, that creature or object must succeed at a Reflex save or catch fire.}
        
\DeclareSpell{Fleshwarping Swarm}{conjuration (summoning) []|V,  S,  M/DF (a square of red cloth)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone swarm of bats, rats, or spiders|concentration + 2 rounds and 1 hour/level (see text)|none|no}[]
    \DeclareSpellDescription{Fleshwarping Swarm}{This spell functions as summon swarm, except that living and undead creatures that fail their saving throw against the swarm's distraction find that their limbs twist and spasm, as their bodies become susceptible to transmutations. Such creatures take a -4 penalty to Dexterity and on saving throws against transmutation effects for 1 hour per caster level.}
        
\DeclareSpell{Lament Of Summer's Last Breath}{abjuration () [fire,  good]|V|1 standard action|close (25 ft. + 5 ft./2 levels)|Area30-ft. radius spread centered on a creature, object, or point in space|1 round/level|Will negates (see text)|yes}[]
    \DeclareSpellDescription{Lament Of Summer's Last Breath}{You wrap the target in a mantle of summery air, within which the ambient temperature never falls below 70 degrees Fahrenheit. Creatures with the cold subtype that start their turns in the area take an amount of fire damage equal to 1d4 points + 1 point per 2 caster levels (maximum 1d4+5) with no saving throw. Each time an evil dragon, fey, or giant takes damage from the spell, it must succeed at a Will saving throw or become shaken for 1 round. Creatures attempting to cast a cold spell in the area must succeed at a Will save or the spell fails. Succeeding at one such save to cast a spell allows a creature to continue casting cold spells in the area for the spell's remainder.}
        
\DeclareSpell{Lost Passage}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|long (400 ft. + 40 ft./level)|Areaone 30-ft. cube/level (S)|2 hours/level (D)|Will partial|yes}[]
    \DeclareSpellDescription{Lost Passage}{Creatures in the area of this spell are subject to a subtle enchantment that confounds their senses of direction, interferes with recognizing landmarks, and causes them to misjudge distances and angles. Creatures that enter the area must succeed at a new Survival check to avoid becoming lost immediately, whether or not they succeed at their saving throws. Those that fail the save take a penalty on such Survival checks equal to double your caster level, treat all squares they enter as difficult terrain for as long as they are in the area and for 1 hour per caster level thereafter, lose the benefit of all effects that allow them to ignore difficult terrain, and take a -4 penalty to Dexterity.  Lost passage can be made permanent with permanency at a cost of 10,000 gp.}
        
\DeclareSpell{Lost Locale}{enchantment (compulsion) [mind-affecting]|V,  S|24 hours|1 mile/level|Areaone 1-mile cube/level|2 hours/level (D)|Will partial|yes}[]
    \DeclareSpellDescription{Lost Locale}{This spell functions as lost passage (see below), except that it affects a larger area. Lost locale can be made permanent with permanency at a cost of 90,000 gp.}
        
\DeclareSpell{Mantle Of The Magic Warriors}{transmutation () [good]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone good-aligned creature/3 levels|1 minute/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Mantle Of The Magic Warriors}{You weave golden masks shaped like animals around the targets' faces, imbuing each target with an animal spirit that matches her strength of character. Each target gains one animal special ability of your choice granted by beast shape I. You can choose a different special ability for each target.}
        
\DeclareSpell{Martial Telekinesis}{evocation () []|V,  S|1 standard action|long (400 ft. + 40 ft./level)|Targetssee text|instantaneous|Will none; see text|yes; see text}[]
    \DeclareSpellDescription{Martial Telekinesis}{You mingle the power of your mind and body to exert force beyond your reach. This spell functions as the combat maneuver version of telekinesis, except as noted above. Alternatively, you can inflict a telekinetic unarmed strike with this spell, using your own unarmed strike damage and applying your primary spellcasting ability score modifier to the damage in place of your Strength modifier.}
        
\DeclareSpell{Miasmal Dread}{enchantment (compulsion) [fear,  mind-affecting]|V,  S|1 standard action|30 feet|Areacone-shaped burst|instantaneous|none|no}[]
    \DeclareSpellDescription{Miasmal Dread}{A cloud of sickly green mist pours from your mouth and coalesces around creatures in the cone. Attempt a single Intimidate check to demoralize as part of casting the spell, comparing the result against the DC to Intimidate each foe within the area. You demoralize all foes whose DC you meet or exceed.}
        
\DeclareSpell{Murderous Crow}{conjuration (summoning) [see text]|V,  S,  F (a crow's feather)|1 round|medium (100 ft. + 10 ft./level)|Effectone crow|1 round/level|none|no}[]
    \DeclareSpellDescription{Murderous Crow}{You conjure a supernaturally vicious and clever crow to watch over you on the battlefield. Choose one of the following templates; the crow has that template and this spell gains the descriptor listed in parentheses: celestial (good), entropicB2 (chaotic), fiendish (evil), or resoluteB2 (lawful). In addition to its normal abilities, the crow gains the Improved StealAPG feat  as a bonus feat and gains an eye rake attack. If both of its claw attacks hit the same living foe in a single round, that foe must succeed at a DC 13 Reflex save or be blinded as the bird scratches and tears at the foe's eyes. The blindness lasts for 1d4 days or until healed with remove blindness.  If the focus leaves your possession, the crow vanishes and the spell ends.}
        
\DeclareSpell{Overlook}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|personal|Targetsyou|1 minute/level||}[]
    \DeclareSpellDescription{Overlook}{You enhance your natural ability to seem small and unimportant, causing those around you to overlook you. You gain a +20 bonus on Stealth checks, which doesn't stack with  bonuses from effects that actually make you sneakier, such as invisibility or respectful quiet (see below); you do not need cover or concealment to hide; and you can hide while you are being observed. If a creature fails to notice you because of this spell, that creature can still remember seeing a halfling pass by, but attach no importance to the memory. You do not gain these benefits against creatures that are immune to compulsions or mind-affecting effects, and spell resistance applies. If you take an actively aggressive or extremely conspicuous action, creatures automatically notice you, and you gain no further benefits against those creatures for the remainder of the spell's duration.}
        
\DeclareSpell{Probe History}{divination () []|V,  S,  DF|1 round|close (25 ft. + 5 ft./2 levels)|Targetsone creature|instantaneous|Will negates|yes}[]
    \DeclareSpellDescription{Probe History}{You gain a glimpse of a potential reality similar to this one but that never was. If the target fails her Will save, you can ask about one topic and attempt the appropriate Knowledge check with a +5 competence bonus; track Knowledge checks attempted with this spell separately for the purpose of disallowing retries on Knowledge checks. You learn information on that topic from a reality in which you were an acquaintance of the target, although the differences in that reality might cause the answer to be subtly different than in your own. Once you have probed a target's history, successfully or not, you cannot target the same creature's history or search for the same information in another creature's history.}
        
\DeclareSpell{Respectful Quiet}{illusion (glamer) []|V,  S,  DF|1 standard action|medium (100 ft. + 10 ft./level)|Targetsany number of creatures in a 30-ft.-radius burst|1 minute/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Respectful Quiet}{All targets are rendered silent, as per silence. The silence affects the entirety of each creature but does not extend beyond. However, the silence is one-way-sounds from outside the creatures' spaces can still enter. Quieted creatures gain a +10 circumstance bonus on Stealth checks.}
        
\DeclareSpell{Shadow Of Doubt}{enchantment (compulsion) [darkness,  emotion,  evil,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature/3 levels|1 round/level|Will partial (see text)|yes}[]
    \DeclareSpellDescription{Shadow Of Doubt}{You create a shadowy aura of doubt fueled by a foe's own inner flaws. Targets perceive all illumination as if it were one light level darker, to a minimum light level of darkness (not supernatural darkness), even on a successful saving throw.  Fleeting mental shadows of regrets and anxieties distract the spell's targets; at the start of each of their turns, they must each succeed at a Will save or be staggered for 1 round. A good-aligned target takes a -4 penalty on saving throws against this effect; an evil-aligned target gains a +4 bonus instead.}
        
\DeclareSpell{Siege Scatter}{evocation () [earth]|V,  S|1 round|long (400 ft. + 40 ft./level)|Area50-ft.-radius spread|instantaneous|Reflex partial (see text)|yes (harmless)}[]
    \DeclareSpellDescription{Siege Scatter}{A roiling blast of rough rock and dirt scatters along the ground in the area, dealing 1d6 points of slashing damage per 2 caster levels (maximum 5d6) to all creatures on the ground in the area, even on a successful saving throw. Creatures in the area that fail the Reflex save fall prone and are knocked to the nearest edge of the area, taking 1d6 points of bludgeoning damage for every 10 feet they travel this way. Creatures that did not move during the past round and those with the stability racial trait gain a +4 bonus on the saving throw.}
        
\DeclareSpell{Summon Giant Ally I}{conjuration (summoning) [see text]|V,  S,  F/DF (bit of cloth from a giant's bag)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectone or more giants|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Giant Ally I}{This spell functions as summon nature's ally VI, except its casting time is shorter and you can summon one cave, hill, marsh, river, slag, stone, or wood giant.}
        
\DeclareSpell{Summon Giant Ally II}{conjuration (summoning) [see text]|V,  S,  F/DF (bit of cloth from a giant's bag)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectone or more giants|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Giant Ally II}{This spell functions as summon giant ally I, except you can summon one desert, fire, frost, or jungle giant or 1d3 cave, hill, marsh, river, slag, stone, or wood giants.}
        
\DeclareSpell{Summon Giant Ally III}{conjuration (summoning) [see text]|V,  S,  F/DF (bit of cloth from a giant's bag)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectone or more giants|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Giant Ally III}{This spell functions as summon giant ally I, except you can summon one ash or cloud giant; 1d3 desert, fire, frost, or jungle giants; or 1d4+1 cave, hill, marsh, river, slag, stone, or wood giants.}
        
\DeclareSpell{Summon Kami}{conjuration () []|V,  S,  DF|1 round|close (25 ft. + 5 ft./2 levels)|Effectone or more kami|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Kami}{This spell functions as summon nature's ally V, except you can summon one kodama, 1d3 fukujin, or 1d4+1 shikigami.}
        
\DeclareSpell{Suppressing Stone}{evocation () []|V,  S,  F (one ioun stone worth at least 1, 000 gp)|1 standard action|personal|Targetsyou|10 minutes/level or until discharged (D)||}[]
    \DeclareSpellDescription{Suppressing Stone}{You infuse arcane power into the focus ioun stone, which must be currently floating around your head. If the ioun stone ever ceases floating around you, the spell ends immediately, and the spell fails if the ioun stone in question is cracked, burned, flawed, or otherwise of lesser value (such as a dull gray ioun stone). While the spell is active, you gain a +1 resistance bonus on saving throws against mind-affecting effects for every 4 caster levels (maximum +5 at caster level 20). Whenever you fail a saving throw against a mind-affecting spell or effect, you can burn out the focus, transforming it irrevocably into a dull gray ioun stone and ending this spell, but suppressing the mind-affecting effect for 1 round per 2,500 gp of value of the focus (minimum 1 round). Rounds during which the effect is suppressed still count against its duration, and the effect can still be dispelled or disrupted during this time.}
        
\DeclareSpell{Wall Of Brine}{conjuration (creation) [water]|V,  S,  M/DF (a bit of coral)|1 standard action|medium (100 ft. + 10 ft./level)|Effectwall up to 10 ft./level long and 5 ft./level high (S)|concentration + 1 round/level|none; see text|yes}[]
    \DeclareSpellDescription{Wall Of Brine}{You conjure a 5-foot-thick wall of seawater with a powerful current flowing toward one side of the wall, selected by you; a creature attempting to swim against this current must spend 4 squares of movement to enter a square of the wall. A creature that begins its turn in the wall is ejected in the direction of the current just before it acts. The wall provides cover against attacks from out of the water, as usual for a body of water. The water and the currents deflect physical ranged attacks into or through the wall, unless a weapon used is exceptionally massive (such as a siege engine). A creature submerged in the wall takes the usual penalties for underwater combat. The wall blocks gases and liquids and prevents water from mixing at its edges.}
        
\DeclareSpell{Zephyr's Fleetness}{transmutation () [air]|V,  S|1 round|long (400 ft. + 40 ft./level)|Targetsone creature/2 levels|1 minute/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Zephyr's Fleetness}{You can call upon the spirits of the air to grant agility to your allies. Each target gains a +30 foot enhancement bonus to its land speed and fly speed (if any). Each target can also move (and charge) through difficult terrain without penalty.}
    