    
\DeclareSpell{Besmara's Grasping Depths}{necromancy (haunted) [emotionUM,  fear,  mind-affecting]|V,  S,  M/DF (a vial of sea water)|1 standard action|close (25 ft. + 5 ft./2 levels)|Area: one 5-ft. cube/level (S)|see text|Will partial; see text|yes}[]
    \DeclareSpellDescription{Besmara's Grasping Depths}{You call upon the restless souls of those who died at sea. This spell can be cast only on an area of deep water. When a creature enters the area, the haunt manifests, automatically grabbing the creature and dragging it under the water on initiative count 10. Each round, the haunt deals 1d6 points of nonlethal damage as it drags its victim down 10 feet; a successful DC 15 Swim check reduces the descent to 5 feet and negates the nonlethal damage. Each round in the haunt's clutches reduces the duration the victim can hold her breath by 2 rounds (Pathfinder RPG Core Rulebook 445). A victim can make a single move or standard action each round while in the haunt's grasp if she succeeds at a Will save; on a failed save, she can only struggle helplessly against the haunt. A victim cannot use her actions to swim toward the surface while the haunt is active. If the haunt reaches the bottom of its body of water, it pounds its victim against the bottom, dealing 2d6 points of nonlethal damage per round to the victim and reducing the  duration the victim can hold her breath by an additional round. This continues until either the haunt is neutralized (in which case the victim must still swim to the surface) or the victim drowns.  The haunt can grab and attempt to drown multiple creatures in its area on its initiative count. The magic holding the haunt together is unstable and deteriorates while the haunt is active. Each round at the end of its turn, the haunt automatically loses 1d6 hit points per creature it is currently affecting. Furthermore, the spell's haunt-like manifestation is active throughout the spell's duration, rendering it vulnerable to effects that damage haunts. When the haunt reaches 0 hit points, the spell ends.}
        
\DeclareSpell{Crafter's Nightmare}{necromancy (haunted) [emotionUM,  fear,  mind-affecting]|V,  S,  M (a broken tool)|1 standard action|close (25 ft. + 5 ft./2 levels)|Area: one 5-ft. cube/level (S)|1 day/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Crafter's Nightmare}{You concentrate feelings of competitiveness, envy, and ill will into a poltergeist-like haunt that wreaks havoc on its victim's long-term endeavors. Every time a creature in the affected area attempts a Craft or Profession check to generate income, create an item, or earn capital (Pathfinder RPG Ultimate Campaign 85), any skill check required for crafting or repairing a magic item, or any skill check required for an occult ritual (Pathfinder RPG Occult Adventures 208), the haunt imposes a -5 penalty on the check. If the creature fails its check by 5 or more, the haunt's mischief deals 1d6 points of damage to the creature in addition to any other negative effects from such a failure. If the creature attempts to cast a spell with a casting time of 1 minute or longer, the haunt becomes similarly disruptive, requiring the caster to succeed at a concentration check (DC = 15 + spell level) or lose the spell and take 1d6 points of damage from the mischief. Each time the haunt is disruptive, the spell's haunt-like manifestation occurs during that round.}
        
\DeclareSpell{Frigid Souls}{necromancy (haunted) [cold,  emotionUM,  fear,  mind-affecting]|V,  S,  DF/M (a bloody icicle)|1 standard action|close (25 ft. + 5 ft./2 levels)|Area: one 5-ft. cube/level (S)|1 hour/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Frigid Souls}{You harness the Irriseni people's palpable fear of their frozen environment and cruel Jadwiga overlords into a haunt that withers defenses against the cold. Any creature that enters the affected area must succeed at a Will save or gain spell resistance equal to 11 + your caster level against any abjuration effect that provides resistance to or protection against cold damage or cold climates. This spell resistance cannot be voluntarily lowered. Once every 30 minutes as an immediate action, the haunt attempts a dispel check (1d20 + your caster level) against an active abjuration effect currently protecting a creature in the affected area against cold, even if it was active before the creature was haunted or it successfully bypassed the spell resistance imposed by the haunt. Against creatures with multiple layers of protection, these dispel checks start with the highest-level abjuration effects and work their way down the list. Each time the haunt attempts a dispel check, the spell's haunt-like manifestation occurs during that round.}
        
\DeclareSpell{Grim Stalker}{necromancy (haunted) [death,  emotionUM,  fear,  mind-affecting]|V,  S,  DF/M (a hound's fang)|1 minute|touch|Targets: one object touched|1 day/level (D)|Will negates (object); see text|yes (object)}[]
    \DeclareSpellDescription{Grim Stalker}{You bind spirits of ill fate to an object, focusing their wrath onto the next creature that touches the object. When a creature touches the target object, it can attempt a Will save to negate the spell's effect. Although a successful save prevents the creature from becoming haunted, the haunt still resides within the object, and targets either the next creature to touch the object or the same creature again if it still holds the object after 24 hours. The haunt remains within the object until a creature fails its save or the spell's duration ends.  Once a creature is affected by the haunt, it begins noticing a large, black mastiff with ominous green eyes watching and following it from a distance, always just beyond the range of focus or interaction. The grim stalker terrorizes the creature's sleep, affecting it as per nightmare every night during the spell's duration (Will negates for one night). Each time the creature takes hit point damage, the grim stalker lunges closer, causing the creature to become shaken for 1 round (Will negates). Each time the creature is reduced to less than one-tenth of its maximum hit points, the grim stalker lunges at the creature as an immediate action, affecting it as per phantasmal killer.  Each time the grim stalker lunges at the affected creature, the spell's haunt-like manifestation occurs during that round. Alternatively, a haunted creature can attempt to force the grim  stalker to manifest using a simple ritual that requires a successful Knowledge (arcana), Knowledge (religion), or Spellcraft check; occult reagents costing 450 gp (which are consumed as part of the ritual); and a full-round action. The DC for this check equals the spell's save DC. Successfully performing the ritual causes the grim stalker to manifest as a Nessian warhound (Pathfinder RPG Bestiary 173) in an available square 20 feet away from the victim, save that its only subtype is extraplanar, its alignment is neutral, its bite and breath weapon deal negative energy damage instead of fire damage, and it has negative energy affinity instead of fire immunity and vulnerability to cold. The grim stalker immediately attacks the affected creature, persisting until either it or the creature is slain, at which point the spell effect (and the warhound) disappears.}
        
\DeclareSpell{Horrifying Visage}{necromancy (haunted) [emotionUM,  fear,  mind-affecting]|V,  S,  M (a live spider)|1 standard action|close (25 ft. + 5 ft./2 levels)|Area: one 5-ft. cube/level (S)|1 day/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Horrifying Visage}{You channel residual feelings of terror into the minds of creatures within the area, causing those fears to manifest when confronted with a specific object. All creatures in the area must succeed at a Will save or acquire a phobia (Pathfinder RPG GameMastery Guide 250) for the spell's duration. You choose one kind of creature, object, or image within the area of the spell when it is cast that triggers the phobia. The kind of creature, object, or image that triggers the phobia must be named specifically. A creature type or subtype is not specific enough. The phobia can be cured using traditional methods of treating insanity, and spells or effects that prevent possession or mind control suppress the phobia for their duration. Each time the phobia is triggered in an affected creature, the spell's haunt-like manifestation occurs during that round.}
        
\DeclareSpell{Mischievous Shadow}{necromancy (haunted) [emotionUM,  fear,  mind-affecting]|V,  S,  M (a black candle)|1 standard action|close (25 ft. + 5 ft./2 levels)|Area: one 5-ft. cube/level (S)|1 day/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Mischievous Shadow}{You direct spirits into the shadows of creatures. The shadows of creatures that fail their Will saving throws appear slightly different for the duration of the spell, bearing small horns, unusually long and slender arms, or other small discrepancies. This spell does not work on creatures that do not cast shadows or reflections. At will as an immediate action (but no more often than once every 10 minutes), a mischievous shadow can interfere with its host's actions or the actions of adjacent creatures by interacting with their shadows in ways that affect their physical counterparts, such as grabbing the shadow of a crossbow to redirect the physical weapon's aim. Each disruption either imposes a -8 penalty on a single attack roll, combat maneuver check, or Strength- or Dexterity-based skill check, or requires a spellcaster to succeed at a concentration check (DC = 15 + spell level) or lose a spell being cast. If you are within range of the spell effect, you can decide how these shadows interfere; otherwise, their actions are timed and decided by the GM as needed, typically manifesting during important or crucial roles. Each time a mischievous shadow makes such a disruption, the spell's haunt-like manifestation occurs during that round.}
        
\DeclareSpell{Skin Tag}{necromancy (haunted) [emotionUM,  fear,  mind-affecting]|V,  S,  M (beverage or food item,  plus special reagents worth 25 gp)|1 minute|touch (object); 1 mile (remote effects)|Targets: 1 beverage or piece of food touched|1 day plus 1 day/level (D)|none (object), Fortitude negates; see text|no (object), yes (creature)}[]
    \DeclareSpellDescription{Skin Tag}{You mix a malign spirit into a piece of food, a drink, or some other item to be consumed (including alchemical items, potions, elixirs, or similar items). The skin tag spell discharges when the item is consumed, affecting the creature that used the item unless it succeeds at a Fortitude save. The spirit embeds itself somewhere in the affected creature's skin, forming a painless set of wrinkles and tags of skin that looks vaguely like a face when the haunt activates. You are considered to have a body part from the affected creature for the purpose of scrying and similar divination spells. Once per day as a standard action, you can remotely cause the spirit to make the affected creature's skin crawl, causing the creature to become sickened for 1d4 rounds + 1 round per 2 caster levels you have (to a maximum of 5 extra rounds at 10th level) unless it succeeds at a Fortitude save. Alternatively, once per day you can remotely use a hex, a mind-affecting spell, or a necromancy spell that causes disease or possession on the affected creature. Each time you use the  remote sickening or spell or hex effect, the spell's haunt-like manifestation occurs during that round.}
        
\DeclareSpell{Unsettling Presence}{necromancy (haunted) [emotionUM,  fear,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Area: one 5-ft. cube/level (S)|1 hour/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Unsettling Presence}{Those in this spell's area who fail their Will saving throws harbor a faint sense of paranoia and evoke the same feeling in others for the duration of the spell. Domesticated animals (not including familiars and animal companions) don't willingly approach affected creatures unless the animal's master succeeds at a DC 25 Handle Animal, Ride, or wild empathy check. Affected creatures take a -4 penalty on Handle Animal, Ride, and wild empathy checks against familiars, animal companions, animal cohorts, and other permanent companions provided by class abilities for the spell's duration. Anyone an affected creature interacts with must succeed at a Will save or have its initial attitude automatically worsened by one step for the spell's duration. Every time an affected creature attempts a Sense Motive check to get a hunch or detect a Bluff from another creature (or vice versa), it must succeed at a Will save or automatically assume the other party is lying or otherwise harbors ill will against it. Each time this spell causes an affected creature (or someone interacting with the affected creature) to attempt a Will saving throw, the spell's hauntlike manifestation occurs.}
        
\DeclareSpell{Urgathoa's Beacon}{necromancy (haunted) [emotionUM,  evil,  fear,  mind-affecting]|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Area: one 5-ft. cube/level (S)|1 hour/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Urgathoa's Beacon}{You shroud an area in Urgathoa's unclean influence, rendering those who pass through it and fail their Will saving throws more enticing to ravenous undead. When an affected creature comes within 60 feet of an undead creature, the spell immediately draws the undead creature's attention, granting it a +4 bonus  on Perception checks to notice the affected creature and on saving throws to resist spells that hide or disguise the affected creature (such as hide from undead). Once the undead creature notices the affected creature, it feels compelled to kill and devour the affected creature, and gains a +1 profane bonus on attack rolls made against the affected creature and a +1 profane bonus on saving throws against the affected creature's spells and special abilities. The undead also ignores any concealment less than total concealment that an affected creature has. Each time the spell draws an undead creature's attention to an affected creature, the spell's haunt-like manifestation occurs during that round.}
    