    
\DeclareSpell{Beloved Of The Forge}{divination () []|V,  S|1 standard action|personal|Targetsyou|1 hour/level||}[]
    \DeclareSpellDescription{Beloved Of The Forge}{You gain an innate sense of the direction to your home or to the place where you last attempted a Craft check, whichever you choose when you cast the spell. You gain a +10 insight bonus on Survival checks made to find your way back to the chosen place. While under the effects of this spell, items in your possession gain a +2 luck bonus on saving throws against spells and effects, and you gain a +5 luck bonus on Craft checks to create or repair objects with Craft skills in which you are trained.}
        
\DeclareSpell{Blessing Of Liberty}{abjuration () []|V,  S,  M (a feather or small object that symbolizes good fortune)|1 standard action|personal|Targetsyou|1 minute/level||}[]
    \DeclareSpellDescription{Blessing Of Liberty}{You imbue yourself with the blessings of liberty. You gain a +1 luck bonus per 6 caster levels (minimum +1, maximum +3) to  your CMD and on saving throws against spells and traps that would move you or impede your movement. You can end the spell's effects as a swift action to gain a +20 foot enhancement bonus to your base speed for 1 round per whole minute of duration remaining.}
        
\DeclareSpell{Harmless Form}{transmutation (polymorph) []|V,  S|1 standard action|touch|Targetsone willing animal companion, familiar, or spirit animal|8 hours (D)|Fort negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Harmless Form}{You transform the target into a harmless animal of the same approximate body type. The form assumed must be one considered unobtrusive by local communities, such as a cat, a dog, a hunting hawk, a horse, or a rat. This transformation can reduce the target by up to two size categories, but cannot make an animal smaller than Tiny. It cannot increase the size of the target or give it new natural attacks or new forms of movement. The spell otherwise functions as beast shape II.}
        
\DeclareSpell{Harvest Season}{abjuration () []|V,  S,  M|1 minute|close (25 ft. + 5 ft./2 levels)|Targetsone plant|instantaneous; see text|none|no}[]
    \DeclareSpellDescription{Harvest Season}{You cause an explosive burst of growth in a single plant, causing it to grow through a cycle of flower, fruit, or grain production as appropriate. If the plant is not one that normally produces food fit for humanoid consumption, it produces edible flowers under the effect of this spell. The plant produces enough food to nourish one Medium creature per caster level. Food harvested through this spell rots if not eaten within 24 hours. This spell nourishes, fertilizes, and pollinates the plant, and doesn't harm the plant in any way. This spell has no effect on plant creatures.}
        
\DeclareSpell{Wall Of Clockwork}{conjuration (creation) []|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Effectwall of bronze clockworks whose area is up to one 5-ft.-square/level (S)|1 minute/level|Reflex half or Reflex negates; see text|yes}[]
    \DeclareSpellDescription{Wall Of Clockwork}{An immobile, vertical wall of spinning cogs and gears springs into existence. Any creature passing through the wall takes 1d6 points of piercing  and slashing damage per 2 caster levels (maximum 10d6); a successful Reflex save halves the damage.  The wall cannot be conjured so that it occupies the same space as a creature or another object. It must always be a flat plane, though you can shape its edges to fit the available space.  A wall of clockwork provides cover (+4 bonus to AC, +2 bonus on Reflex saves) against attacks made through it.  A wall of clockwork is 1 inch thick per 4 caster levels. You can double the wall's area by halving its thickness. Each 5-foot square of the wall has 30 hit points per inch of thickness and hardness 9. A section of wall whose hit points drop to 0 is breached. If a creature tries to break through the wall with a single attack, the DC for the Strength check is 25 + 2 per inch of thickness. If an attacker an attack roll of a natural 20 (and only a natural 20, regardless of the weapon's threat range) and confirms the critical hit (even though the wall is otherwise immune to critical hits), that section of wall gains the broken condition. If already broken, that section of wall is destroyed instead.  Bronze created by this spell is not suitable for use in the creation of other objects (even for the limited duration of the spell) and cannot be sold.}
        
\DeclareSpell{Cloak Of Secrets}{illusion (glamer) []|V,  S|1 minute|close (25 ft. + 5 ft./2 levels)|Area5-ft.-radius emanation centered on a point in space|10 minutes/level (D)|none|no}[]
    \DeclareSpellDescription{Cloak Of Secrets}{This spell forms an invisible bubble that filters all speech coming from inside the affected area so that creatures outside hear a completely different version of the conversation. The bubble also disguises lip movements to match the false conversation. Any creature listening to the conversation for at least 1 round can attempt a DC 15 Sense Motive check to realize that the apparent conversation doesn't actually make any sense. The bubble also obscures the verbal components of spells cast within the area so it's impossible to identify spells by their verbal components alone, and anyone outside the bubble attempting a Spellcraft check to identify a spell cast within the bubble takes a -5 penalty on the check. Furthermore, the bubble renders any language-dependent spells and effects used within the bubble ineffective against creatures outside the area.}
        
\DeclareSpell{Coin Shot}{transmutation () []|S|1 standard action|touch|Targetsup to three coins touched|10 minutes or until discharged|none|yes (harmless, object)}[]
    \DeclareSpellDescription{Coin Shot}{You turn up to three coins into deadly projectiles that gain the velocity of a bullet when thrown. The coins retain their normal appearance but can be used as simple thrown weapons with a range increment of 20 feet and a critical multiplier of x2. The transmuted coins are treated as ammunition for the purposes of drawing them. Like firearm bullets, the coins deal bludgeoning and piercing damage, and attacks with them are resolved as touch attacks within the first range increment. Regardless of whether a transmuted coin hits or misses the target, it is  destroyed after the attack. Only you can make attacks with the coins, though other creatures can safely handle them without discharging the spell.  You can make a single ranged attack with a coin as part of casting this spell. Different types of coins create different bullet effects. Copper coins deal 1d4 points of damage. Silver coins deal 1d6 points of damage and count as silver for the purpose of overcoming damage reduction. Gold coins deal 1d8 points of damage and count as masterwork weapons. Platinum coins deal 1d10 points of damage, count as masterwork weapons, and are treated as adamantine weapons for the purposes of overcoming damage reduction and bypassing hardness. All coin bullets deal an additional 1 point of damage per 2 caster levels (to a maximum of an extra 10 points of damage at 20th level).}
        
\DeclareSpell{Ears Of The City}{divination () []|V,  S,  M/DF (a small piece of a brick)|1 standard action|touch|Targetsone creature|1 round/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Ears Of The City}{The target of this spell sees and hears a stream of past scenes and pieces of conversations related to local people and events. The flashes are so brief that it is impossible to identify individual people or places, but when the target concentrates on a particular topic or individual, she can piece together a coherent narrative told in a multitude of changing voices in her mind.  Each round for the duration of the spell, the target can attempt a Diplomacy check to gather information as though she had spent 1d4 hours talking to local people. Since the information gathering doesn't involve actual interaction with people, only observation, the target can use her Perception skill instead of her Diplomacy skill. While thus concentrating, the target is effectively blind and deaf.}
        
\DeclareSpell{Illusory Crowd}{illusion (figment) []|V,  S,  M (a shirt button)|1 standard action|medium (100 ft. + 10 ft./level)|Effectone 10-ft. cube of illusory people|1 minute/level (D)|Will disbelief (if interacted with)|no}[]
    \DeclareSpellDescription{Illusory Crowd}{This spell creates an illusion of a stationary group of people milling about. They can be of any humanoid race or ethnicity you are familiar with, and they speak a language of your choice that you know. To anyone not paying close attention, their  conversations sound perfectly normal but are in fact repetitive and essentially meaningless. The crowd appears to be a group of typical citizens, and cannot duplicate any specific group, guild, or military squad.  The crowd affects movement and provides cover like a real crowd (Pathfinder RPG Core Rulebook 436), b ut a nyone who disbelieves the illusion can move and attack through the crowd without impediment. Each round a creature enters or makes an attack through a crowd-filled square, it can attempt a save to disbelieve the illusion. Similarly, any creature that spends a round listening to or talking to the crowd can attempt a save to disbelieve the illusion. If the group is placed in any terrain other than urban, each creature attempting a save to disbelieve the spell gains a +5 bonus on the save.}
        
\DeclareSpell{Locksight}{divination () []|V,  S,  M/DF (a small key)|1 standard action|touch|Targetsone creature|1 hour/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Locksight}{The target can observe for 1 full round a lock that he is aware of (or object that includes a lock, such as a chest or door) that is within 60 feet to automatically determine whether it is open, closed, or jammed. If the target creature is trained in Disable Device, by concentrating on a lock for 3 rounds, he can also determine the quality of the lock (simple, average, good, or superior). This spell does not enable the target to see hidden locks, such as those on secret doors.}
        
\DeclareSpell{Peace Bond}{abjuration () []|V,  S,  M/DF (a glass cube)|1 standard action|close (25 ft. + 5 ft./2 levels)|Areaone or more 5-ft. cubes, no two of which can be more than 30 ft. apart|1 minute/level|none|no}[]
    \DeclareSpellDescription{Peace Bond}{This spell creates one glowing rune of peace, plus one per 2 caster levels above 1st (to a maximum of five runes at 9th level). An identical symbol appears on your forehead  for the duration of the spell and cannot be disguised (though it is visible only if you are visible). Each rune illuminates a 5-foot cube, preventing any spell you cast of up to 3rd level and that has a defined area (as opposed to targets or an effect) from entering or affecting the 5-foot cube. For example, creatures and items within any square affected by peace bond take no damage from a fireball you cast. However, if you cast stinking cloud, the noxious vapors are an effect and enter such cubes normally. This spell does not break line of effect within any other spells you cast; it simply negates all effects of your 1st-, 2nd- and 3rd-level area spells within the peace bond's area. Peace bond offers no protection against your spell-like abilities or supernatural area effects.}
        
\DeclareSpell{Speak Local Language}{divination () []|V,  M/DF (a worn-out coin)|1 standard action|touch|Targetscreature touched|10 min./level|Will negates (harmless)|no}[]
    \DeclareSpellDescription{Speak Local Language}{This spell functions as tongues, except the creature touched gains only the ability to speak and understand a regional human language, such as Varisian or Common (Taldane in the Inner Sea region or Tien in Tian Xia), and the language granted must be one you know. You must select the language at the time of casting. The language can't be a dead language, such as Ancient Osiriani or Jistka. The target speaks the language with a native accent, but the spell doesn't impart knowledge about any culture associated with the language, nor does it change the target's appearance.}
    