    
\DeclareSpell{Accursed Glare}{necromancy [curse]|V,  S|1 round|close (25 ft. + 5 ft./2 levels)|Targets: one creature|1 day/level|Will negates|yes}[]
    \DeclareSpellDescription{Accursed Glare}{You channel a fell curse through your glare. If the target fails its saving throw, it begins to obsessively second-guess its actions and attract bad luck. Whenever the target attempts an attack roll or saving throw while the curse lasts, it must roll twice and take the lower result. While you cast this spell, an ally within range of the subject can attempt an Intimidate check as a move action (DC = save DC of this spell); on a success, the ally adds its own glare to yours, granting you a +2 bonus on your caster level check to overcome spell resistance (if any). Multiple allies can attempt Intimidate checks; this bonus stacks.}
        
\DeclareSpell{Share Skin}{necromancy|V,  S|1 standard action|touch|Targets: one animal touched|1 hour/level or until you return to your body|Will negates; see text|yes}[]
    \DeclareSpellDescription{Share Skin}{Duration 1 minute/level or until you return to your body You can possess an animal's body in a manner that functions like magic jar, except as noted here. Your body vanishes while the effect lasts and you don't require a receptacle.}
        
\DeclareSpell{Greater Share Skin}{necromancy|V,  S|1 standard action|touch|Targets: one creature touched|1 hour/level or until you return to your body|Will negates; see text|yes}[]
    \DeclareSpellDescription{Greater Share Skin}{This spell functions like share skin, except as noted here.\\\\

{\centering\bf Share Skin\hrule}

Duration 1 minute/level or until you return to your body You can possess an animal's body in a manner that functions like magic jar, except as noted here. Your body vanishes while the effect lasts and you don't require a receptacle.}
    