    
\DeclareSpell{Enchantment Sight}{divination () []|V,  S|1 standard action|personal|Targetsyou|10 minutes/level (D)||}[]
    \DeclareSpellDescription{Enchantment Sight}{Your irises take on a purplish tinge and you can see whether creatures within 60 feet of you are affected by an enchantment effect. To your eyes only, a creature under the effects of an enchantment spell glows with a simple white light around its head. You can immediately discern whether the brightness of the light is faint, moderate, strong, or overwhelming depending on the highest spell level of enchantment currently in effect (as per detect magic). Enchantments of the charm or compulsion subschool glow with a scarlet or emerald hue, respectively.  If a creature under an enchantment effect is in your line of sight, you can attempt a Spellcraft check as a move action to determine the highest-level spell or spell effect (DC = 15 + the spell level, or 15 + 1/2 the caster level for a non-spell effect). Effects that block divination magic also block this spell.  Enchantment sight can be made permanent with a permanency spell cast by a caster of 9th level or higher, at a cost of 2,500 gp.}
        
\DeclareSpell{Reveal Emotions}{divination () []|V,  S|1 minute|close (25 ft. + 5 ft./2 levels)|Area40-ft.-radius spread|1 hour/level (D)|none|yes}[]
    \DeclareSpellDescription{Reveal Emotions}{You create an area that draws out a creature's emotion aura (Pathfinder RPG Occult Adventures 198). Creatures within this area constantly glow with colors that represent their current overall  emotional state and continue to do so for 1d4 rounds after leaving the area. This glow is clearly visible to any creature that can see the creature. Emotionless creatures or creatures unaffected by this spell glow with a dull purple hue while within the area.}
        
\DeclareSpell{Shroud Of Innocuity}{illusion (glamer) []|V,  S|1 minute|close (25 ft. + 5 ft./2 levels)|Targetsone willing creature plus one/2 caster levels, no two of which can be more than 30 ft. apart|1 hour/level (D)|none (harmless); see text|no}[]
    \DeclareSpellDescription{Shroud Of Innocuity}{All affected creatures are veiled with a commonplace appearance. This appearance varies based on the viewer, but is always an ordinary member of that viewer's race, ethnicity, or nationality. This familiarity grants a +2 bonus on Diplomacy checks attempted by affected targets against those not affected by the spell.  Creatures with an attitude of unfriendly or hostile toward an affected target can attempt a Will save to disbelieve the effect the first time they encounter that target.}
        
\DeclareSpell{Speechreader's Sight}{divination () []|V,  S|1 standard action|personal|Targetsyou|1 hour/level (D)||}[]
    \DeclareSpellDescription{Speechreader's Sight}{If a creature within 100 feet that you can see is speaking a language you understand, you can read its lips with perfect accuracy. Reading lips in this manner gives the exact wording of conversation and does not assist in deciphering any obfuscated ideas such as secret messages or slang. Reading lips requires moderate concentration, and you take a -4 penalty on other Perception checks while doing so.  Speechreader's sight can be made permanent with a permanency spell cast by a caster of 9th level or higher, at a cost of 2,500 gp.}
        
\DeclareSpell{False Face}{transmutation (polymorph) []|V,  S,  M (a folded-paper mask)|1 standard action|personal|Targetsyou|1 hour/level||}[]
    \DeclareSpellDescription{False Face}{This spell alters details of your appearance so that you are no longer recognizable as yourself. Your new appearance is within the norms for your race, ethnicity, and gender. You lack control over the details of your appearance; however, when casting false face, you can choose an appearance you previously used, allowing you to maintain specific identities.}
        
\DeclareSpell{Perceive Betrayal}{divination () []|V,  S,  M (12 drops of blood),  F (a silver circlet worth 500 gp)|1 minute|personal|Targetsyou|1 hour/level||}[]
    \DeclareSpellDescription{Perceive Betrayal}{By donning a silver circlet anointed with blood, you gain the ability to sense traitorous intent toward a single person to whom you defer, designated when you cast the spell. The spell alerts you when a creature with traitorous intent is within 200 feet, although it doesn't identify the source. By concentrating, you can learn the strength of the greatest threat, based on the following categories.  Ill Will: Someone dislikes your liege, but isn't planning to act against her.  Plotting: Someone is actively conspiring against your liege.  Imminent: Someone is in the process of carrying out a plot against your liege.  Creatures that are immune to mind-affecting or thought-detecting effects cannot have their intent detected by perceive betrayal.}
        
\DeclareSpell{Pierce Facade}{divination () []|V,  S,  M/DF (an eagle's eye)|1 standard action|touch|Targetscreature touched|10 minutes/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Pierce Facade}{The target gains a +5 insight bonus on Perception checks to see through disguises. This bonus increases to +10 at caster level 7th.}
    