    
\DeclareSpell{Medusa's Bane}{abjuration () []|V,  S,  M (tiny fragment of a mirror)|1 standard action|personal|Targetsyou|1 round/level||}[]
    \DeclareSpellDescription{Medusa's Bane}{This spell causes your eyes to take on a silvery mirror-like quality, transforming your eyes into metallic-looking orbs that reflect the world you see. Your vision is in no way impaired while this spell is in effect, but you are granted immunity to gaze attacks for the spell's duration. As an immediate action, you can reflect a creature's gaze back on itself, forcing the target of the gaze attack to save against its own gaze weapon or be affected by it. This reflection bypasses the typical immunity creatures with gaze attacks have to their own race's gaze attack, but does not bypass any other resistances or immunities the creature might have. Once you choose to reflect a gaze attack in this manner, the effect of medusa's bane immediately ends.}
        
\DeclareSpell{Enlightened Step}{transmutation () [air,  meditative]|V,  M (soothing incense worth 600 gp)|1 hour|personal|Targetsyou|24 hours or until discharged||}[]
    \DeclareSpellDescription{Enlightened Step}{Through careful regulation of your body's mystical energies, thoughtful control of your poise and balance, and the focus in your mind on the surety of each and every step you take, you are able to make your steps lighter than air. This grants you the benefits of air walk, except as noted above. Additionally, at any time during the spell's duration, you can expend the spell's remaining duration as a swift action in order to gain a fly speed of 120 feet with perfect maneuverability for 1 minute. After this time, the spell ends.}
        
\DeclareSpell{Firewalker's Meditation}{abjuration () [meditative]|V,  M (soothing incense worth 400 gp)|1 hour|personal|Targetsyou|24 hours or until discharged||}[]
    \DeclareSpellDescription{Firewalker's Meditation}{You focus your mind on blocking out pain, allowing your body to endure punishments that would be otherwise unbearable. While under the effects of this spell, you continue to register pain-you simply don't suffer the deleterious effects such sensations bring. For example, if you were lit on fire as you slept, you would still wake from the pain of burning even though some of the fire damage you endured (perhaps all of it) would be negated by this spell.  You gain DR 5/magic, resist fire 10, and a +4 bonus on saving throws to resist pain effects. Once the spell has prevented a total of 10 points of damage per caster level (maximum 100 points), it is discharged. At any time during the spell's duration when you take damage that would be subject to the damage  reduction or energy resistance granted by this spell, you can expend the spell's remaining duration as an immediate action in order to increase the effects to DR 10/magic, resist fire 30, and immunity to pain effects. If you do so, these enhanced effects persist for 3 rounds. After this time, the spell ends.}
        
\DeclareSpell{Rite Of Bodily Purity}{abjuration () [meditative]|V,  M (soothing incense worth 100 gp)|1 hour|personal|Targetsyou|24 hours or until discharged||}[]
    \DeclareSpellDescription{Rite Of Bodily Purity}{You energize your body's immune system, improving your ability to resist toxins and ailments. You gain a +2 resistance bonus on saving throws to resist diseases, drugs, and poisons. Additionally, at any time during the spell's duration, whenever you fail a saving throw to resist a disease, drug, or poison, you can expend the spell's remaining duration as an immediate action in order to reroll that saving throw. You must take the second result, even if it's worse. The +2 resistance bonus granted by the spell applies to the reroll, but after you make this reroll, the spell ends.}
        
\DeclareSpell{Rite Of Centered Mind}{abjuration () [meditative]|V,  M (soothing incense worth 100 gp)|1 hour|personal|Targetsyou|24 hours or until discharged||}[]
    \DeclareSpellDescription{Rite Of Centered Mind}{You heighten your awareness of your own thoughts, allowing you to more easily resist outside influences. You gain a +1 resistance bonus on saving throws to resist mind-affecting effects. This resistance bonus is increased to +2 if the effect is an emotion or fear effect. Additionally, at any time during the spell's duration, whenever you fail a saving throw to resist a mind-affecting effect, you can expend the spell's remaining duration as an immediate action in order to reroll that saving throw. You must take the second result, even if it's worse. The +2 resistance bonus granted by the spell applies to the reroll, but after you make this reroll, the spell ends.}
        
\DeclareSpell{See Beyond}{divination () [meditative]|V,  M (soothing incense worth 300 gp)|1 hour|personal|Targetsyou|24 hours or until discharged||}[]
    \DeclareSpellDescription{See Beyond}{You attune your mind and your sight to the hidden world of spirits. You gain a +5 circumstance bonus on Perception checks; this circumstance bonus increases to a +10 circumstance bonus  on Perception checks to find invisible creatures or objects, incorporeal creatures or objects, or things that exist only on the Ethereal Plane. Additionally, at any time during the spell's duration, you can push your ethereal vision even further as a swift action. When you do, you can see through solid objects (as if using a ring of x-ray vision) for 5 rounds. After this time, the spell ends.}
        
\DeclareSpell{Spirit Bonds}{divination () [meditative]|V,  M (soothing incense worth 300 gp)|1 hour|personal|Targetsyou; see text|24 hours or until discharged||}[]
    \DeclareSpellDescription{Spirit Bonds}{You heighten your awareness of up to one willing creature or object per 3 caster levels, each of which must be within 30 feet of you during the entire hour you spend preparing spells and casting spirit bonds. By concentrating on one of these creatures or objects as a full-round action, you can learn its direction and relative distance from your location, provided that it is on the same plane. In the case of a creature, you can also learn the state of its emotion or health aura as a full-round action (see page 198 of Pathfinder RPG Occult Adventures for more information about auras). In the case of an object, you can also get a sense of how damaged it is, similar to reading the health aura of a creature, or, in the case of a magic item that must be activated, you can learn when it was last activated (a full-round action in either case).  Additionally, at any time during the spell's duration, you can deliver a single message to any of the creatures that participated in the spell. This message is delivered telepathically regardless of range and can be up to 25 words in length. Delivering a message in this way severs your connection with that character, and you can no longer learn information about that creature through this spell, but doing so does not impact the remaining duration you have linked to other creatures or objects.}
        
\DeclareSpell{Visualization Of The Body}{transmutation () [meditative]|V,  M (soothing incense worth 200 gp)|1 hour|personal|Targetsyou|24 hours or until discharged||}[]
    \DeclareSpellDescription{Visualization Of The Body}{You focus your mind on one aspect of your body, aligning the energies within your body to enhance that element. Choose a single physical ability score (Constitution, Dexterity, or Strength). If you choose Strength or Dexterity, you gain a +5 bonus on skill checks associated with that ability score. If you choose Constitution, your maximum and current hit points increase by an amount equal to your Hit Dice.  At any time during the spell's duration, you can expend the spell's remaining duration as an immediate action in order to gain a one-time physical enhancement associated with the  ability score you chose to visualize, as detailed below. After you do so, the spell ends.  Constitution: You immediately regain a number of hit points equal to 1d8 + your total character level.  Dexterity: You gain a +4 dodge bonus to your Armor Class for 3 rounds.  Strength: You gain a +6 bonus on all Strength checks to break objects and on checks to escape or establish grapples for 1 minute.}
        
\DeclareSpell{Visualization Of The Mind}{transmutation () [meditative]|V,  M (soothing incense worth 200 gp)|1 hour|personal|Targetsyou|24 hours or until discharged||}[]
    \DeclareSpellDescription{Visualization Of The Mind}{You enhance a single aspect of your mind, nurturing and empowering it. Choose a single mental ability score (Charisma, Intelligence, or Wisdom). You gain a +5 bonus on ability checks and skill checks associated with that ability score.  At any time during the spell's duration, you can expend the spell's remaining duration as an immediate action in order to gain a one-time mental enhancement associated with the ability score you chose to visualize, as detailed below. After you do so, the spell ends.  Charisma: You are immediately infused with a wave of supernatural luck, and gain a +2 luck bonus on all d20 rolls for 1 minute.  Intelligence: You immediately gain a flash of insight, and gain a number of ranks equal to your Hit Dice in any skill in which you have no ranks. These ranks last for 1 minute, during which time you can also treat that skill as a class skill.  Wisdom: When you fail a Will save, you can immediately attempt that saving throw again, gaining a +4 bonus on the new saving throw to resist the effect.}
    