    
\DeclareSpell{Possession Trap}{necromancy () []|V,  S,  F (a gem or crystal worth at least 500 gp)|1 standard action|personal|Targetsyou|24 hours or until activated (see text); 1 round/level||}[]
    \DeclareSpellDescription{Possession Trap}{You place a protective ward over your spirit that ensnares creatures attempting to possess you. Should a creature attempt to possess you (such as via magic jar or a similar effect) while you are under the effects of possession trap, that creature must first succeed at a Will save or its possession attempt is ruined and its spirit is shunted into this spell's focus gem. The trapped creature is contained within the focus gem for 1 round per caster level, acting as though it were trapped in a magic jar for the duration of this effect. This effect fails if you are not carrying the focus gem during the time of the possession attempt.
If the possessor's Will save is successful, you are affected by its possession attempt as normal, and may attempt a saving throw against this possession attempt if one is normally allowed. Regardless of whether the possessor fails or succeeds at its save against possession trap, you immediately become aware of the possession attempt and whether or not a creature is trapped in the focus gem. If the focus gem is destroyed while it contains a creature, the creature is immediately released.
Once this spell is triggered, it offers no further protection, and a trapped creature can attempt to possess you again once it's free of the focus gem.}
        
\DeclareSpell{Sphere Of Warding}{abjuration () []|V,  S,  DF|1 standard action|touch|Effect10-ft.-radius sphere emanating from point touched|1 hour/level|Will negates (see text)|yes}[]
    \DeclareSpellDescription{Sphere Of Warding}{You create a luminescent sphere of orbiting energy that harms incorporeal creatures and dispossesses them of any stolen bodies. An incorporeal creature must succeed at a Will save to enter a space overlapping with the sphere; failure means the creature cannot pass through the sphere, as though it were a wall of force. If the incorporeal creature succeeds, it may pass through the sphere at will, though if it ends its turn within the sphere, it takes a number of points of force damage equal to 1d6 + 1 per caster level (maximum +10).
If a creature possessing another creature's body (via either magic jar or a similar effect) enters a sphere of warding, that creature is immediately ejected from its host body, the host's spirit returns to its body if it's able, and the possession immediately ends. When ejected, the body enters the sphere, while the possessing creature takes the appropriate amount of force damage (no save) and is shunted to the exterior of the sphere.}
        
\DeclareSpell{Carrion Compass}{divination () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone undead creature|10 minutes/level|Will negates|no}[]
    \DeclareSpellDescription{Carrion Compass}{You animate one of the target's fetid organs so that it leads you to the undead creature's most recent controller or the cause of the creature's undeath.
The organ (typically the heart, the brain, or an eyeball) floats in front of you at chest level and slowly leads you to the undead creature's most recent controller at a rate of 30 feet per round, always staying within your range of vision. If the creature from which the organ originated had no controller, but rather was created deliberately by another creature, the organ instead leads you to that creator.
If the undead was animated by an effect or event at a particular location, the organ leads you to that location.
If the creature was animated by none of the methods above, if it was self-created, or if the creature's most recent controller no longer exists, the spell fails. Once the organ is within 10 feet of its intended destination, the spell ends, and the organ falls to the ground.
The organ cannot engage in combat or execute any other task aside from leading you to its intended target. It may pass through small slits and crevices, though it will not leave your range of vision. The organ cannot travel more than 5 miles from the spot where you cast the spell. If the undead creature to which the organ belonged is destroyed, the spell ends and the organ falls to the ground.}
        
\DeclareSpell{Empower Holy Water}{transmutation () [good]|V,  S|1 standard action|touch|Targetsone or more vials of holy water|1 minute/level|none (object)|no}[]
    \DeclareSpellDescription{Empower Holy Water}{You empower a vial of holy water to deal additional damage to undead creatures. You can empower one vial of holy water at 4th level, two at 8th level, and three at 12th level.
When thrown at an undead creature, the affected vial of holy water deals an amount of bonus damage equal to your caster level (maximum +10) on a direct hit, and half that amount of bonus damage (maximum +5) to creatures caught in the splash area. This additional damage is positive energy damage, and has no effect on living creatures.}
        
\DeclareSpell{Force Anchor}{conjuration (creation) [force]|V,  S,  M (a twisted nail)|1 standard action|medium (100 ft. + 10 ft./level)|Effectone anchor of force|1 round/level|none|yes}[]
    \DeclareSpellDescription{Force Anchor}{You conjure an anchor of pure force that immediately skewers your target on a successful ranged touch attack. If it hits, the attack deals the target 1d4 points of force damage per 2 caster levels (max 5d4) and the anchor becomes firmly lodged in the target's torso.
The anchor has no weight, but its wide flukes prevent the target from moving through any space smaller than the creature's size. The anchor also prevents incorporeal targets from moving through solid objects. Whenever the target moves through a square occupied by another creature, the square counts as 2 squares for the purpose of calculating movement, even if the square's occupant is the target's ally.}
        
\DeclareSpell{Life Shield}{conjuration (healing) []|S,  DF|1 standard action|personal|Targetsyou|1 minute/level or until discharged||}[]
    \DeclareSpellDescription{Life Shield}{You surround yourself with a positive energy field that damages undead opponents. Each time an undead creature damages you with a melee attack, that creature takes an amount of positive energy damage equal to half the damage it dealt to you. This damage is calculated after applying your damage reduction, resistances, and other defenses. Once this spell has dealt 5 points of damage per caster level (maximum 50), it is discharged.}
        
\DeclareSpell{Necromantic Burden}{necromancy () []|V,  S,  M/DF (a handful of knucklebones)|1 round|close (25 ft. + 5 ft./2 levels)|Targetsone undead creature|1 hour/level|Will negates|yes}[]
    \DeclareSpellDescription{Necromantic Burden}{You make an undead creature more difficult for necromancers and clerics to control via effects such as Command Undead or control undead. If the target fails its Will save, the target's effective number of Hit Dice is doubled for the purposes of determining whether it remains under the control of another creature.
Regardless of the target's actual Hit Dice, its effective HD cannot exceed twice your caster level. (For example, a 12th-level cleric could cast this spell to cause an undead creature with 15 HD to instead effectively have 24 HD for the purpose of controlling it.) If the targeted undead is under the control of another creature and this spell causes the target's effective Hit Dice to exceed the controller's maximum capability, the target creature is immediately freed from control. Any creature capable of controlling undead may attempt to control the target, provided the target's effective HD won't cause the would-be controller to exceed its HD limit. The target's former controller can attempt to regain control over the target by relinquishing command over other creatures until its HD limit is no longer exceeded (or the former controller can wait until the spell's duration expires to attempt this at the target's normal HD).}
        
\DeclareSpell{Undeath Inversion}{necromancy () []|V,  S,  F/DF (a gold piece with one scratched face)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone undead creature|1 round/level (D); see text|Will negates; see text|yes}[]
    \DeclareSpellDescription{Undeath Inversion}{You alter an undead creature's energy affinity so that it takes damage from negative energy and gains healing from positive energy, as if it were a living creature. If the target was able to channel negative energy or produce negative energy effects (such as inflict spells), these abilities produce positive energy instead, healing living targets and harming the undead. The target cannot impose negative levels on other creatures for the duration of the spell. The target's creature type does not change, and it is still considered an undead creature. Each round on its turn, the subject may attempt a new saving throw to end the effect. This is a fullround action that does not provoke attacks of opportunity.}
    