    
\DeclareSpell{Watchful Animal}{divination (scrying) []|V,  S,  M/DF (a desiccated fly)|10 minutes|medium (100 ft. plus 10 ft./level)|Effectmagical sensor|10 minutes/level|none|no}[]
    \DeclareSpellDescription{Watchful Animal}{You place a scrying sensor on your animal companion or familiar. This allows the animal companion or familiar to function as if it were an insect summoned by the greater insect spyUI spell. The animal companion or familiar does not change shape, nor does it lose the ability to make its own decisions, but it receives orders and gives answers as per insects summoned by that spell, and you can sense its direction and distance and receive sensory input from it as with that spell.}
        
\DeclareSpell{Trial By Fire}{evocation () [fire]|V,  S,  DF|1 standard action|touch|Targetscreature touched|instantaneous|None|yes}[]
    \DeclareSpellDescription{Trial By Fire}{You test a creature's purity of convictions by exposing it to a sheet of divine fire. Unless the target's alignment is within one step of your deity's, the spell deals 1d6 points of damage per 2 caster levels (maximum 5d6 points of damage). Half the damage is fire damage, but the other half results directly from divine power and is therefore not subject to being reduced by resistance to fire-based attacks. Additionally, if the target has an element of its alignment that is in direct opposition to your (chaos opposes law and evil opposes good), you can also attempt an Intimidate check to demoralize the target as a free action.}
        
\DeclareSpell{Claim Identity}{transmutation (polymorph) []|V,  S,  M (a needle and thread)|1 standard action|touch|Targetshumanoid creature touched|1 hour/level|Fortitude negates|yes}[]
    \DeclareSpellDescription{Claim Identity}{You steal the target's face, transforming yourself into a flawless imitation of it. All of the target's facial features, vocal cues, and identifying physical traits change, transforming it into an unremarkable member of its race and gender. You transform into a perfect likeness of the target's true form, as if affected by alter self, and gain a +10 bonus on Disguise checks to impersonate the original subject of this spell; you take no penalties on this check if the original target is of a different race, age, size, or gender.  Claim identity prevents any other polymorph effects from restoring the target's true face for the spell's duration, though the target can still assume other forms or faces via magic or any natural shapechanging ability.}
        
\DeclareSpell{Claim Identity, Greater}{transmutation (polymorph) []|V,  S,  M (a silver needle costing 100 gp)|1 standard action|touch|Targetshumanoid creature touched|1 hour/level|Fortitude negates|yes}[]
    \DeclareSpellDescription{Claim Identity, Greater}{This spell functions as per claim identity, except it transforms its target into  a helpless, inanimate porcelain mask for the spell's duration. The target remains aware of everything it can see or hear while transformed. The target can't speak or move, but can still take purely mental actions (such as casting certain spells) or be targeted by spells that affect its mind.  Any creature donning this mask is transformed into a flawless imitation of the spell's target, as if affected by claim identity, and reverts to its natural form upon removing the mask. Any damage dealt to the mask immediately ends this spell.}
        
\DeclareSpell{Egorian Diplomacy}{enchantment (compulsion) [mind-affecting]|V,  S,  M (a bent coin)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|instant; see text|Will negates|yes}[]
    \DeclareSpellDescription{Egorian Diplomacy}{As part of casting this spell, you can attempt a single Intimidate skill check to make a target act friendly toward you. If you succeed, the target assists you normally, but Egorian diplomacy clouds the memory of any threats or pressure you applied. The target remembers assisting you, but can't remember why, and its attitude toward you doesn't worsen as a result of being intimidated.  Whether a creature fails or succeeds at its saving throw, it becomes immune to further castings of Egorian diplomacy for 24 hours.}
        
\DeclareSpell{Garrulous Grin}{necromancy () [fear,  mind-affecting]|S|1 round|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 hour/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Garrulous Grin}{This Nidalese spell plants a seed of supernatural fear deep in a subject's mind, causing self-doubt, stuttering, and evasiveness. Affected creatures have difficulty meeting anyone's gaze and seem dishonest or guilty. The target takes a -4 penalty on Bluff and Diplomacy checks to  convince another of the truth of her words, and on Diplomacy or Intimidate checks to influence another creature's attitude.}
        
\DeclareSpell{Insect Scouts}{divination () []|S,  M (a drop of honey)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone insect scout/4 levels|1d6 hours, plus 1 hour/level; see text|none|no}[]
    \DeclareSpellDescription{Insect Scouts}{A favorite in the creaking courts of Ustalav, insect scouts summons one or more vermin to investigate a single location or building you can see. Your scouts must spend 1d6 hours investigating the target location, but need no oversight. When done, they return unerringly to you with their findings, traveling up to 1 mile per caster level you have to rejoin their master. Each insect's size is Fine. Each insect has 1 hit point, AC 20 (+2 Dexterity, +8 size), a movement speed of 5 feet, a climb speed of 5 feet, and a fly speed of 20 feet (perfect maneuverability). The insects use your saving throw bonuses, have a total Perception skill bonus equal to 5 + 1/2 your caster level, and can't attack. Because of their incredibly small size and magical nature, they can attempt Stealth checks to avoid being noticed even if they lack a source of cover or concealment, and they have a total Stealth skill bonus equal to 18 + 1/2 your caster level.  Each scout that returns passes along memories of specific structural flaws, defenses, and alarms, granting you the ability to reroll one failed skill check per scout, as long as the skill check involves that specific location's layout, such as a Stealth check to sneak in, a Disable Device check to silence an alarm, or a Perception check to notice a trap. If even one scout returns, you also gain a rough understanding of the building's layout (at least, any portions your scouts could access). All insight (and the associated rerolls) fades 1 hour per caster level you have after the scouts return. Your insects remember nothing about creatures, and so provide no information about guardians or any conversations they may overhear.}
        
\DeclareSpell{Passing Fancy}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone living creature|4d4 rounds (D)|Will negates|yes}[]
    \DeclareSpellDescription{Passing Fancy}{Taldor's infamous Lion Blades imported this spell from the ninja clans of Minkai, and both groups use it to great effect when maneuvering among the shallow upper classes. When you cast the spell, you dictate one specific topic or recent event and instill a magical obsession with that subject within the target. An affected creature becomes fascinated by the topic, and becomes  completely focused on discussing the event with anyone nearby, possibly wandering off or distracting unaffected creatures. Passing fancy has no effect on a creature with an Intelligence of 2 or less.  Because the target talks and interacts with its usual cadence, onlookers take a -10 penalty on Sense Motive checks to notice that anything is amiss with the target's behavior.}
        
\DeclareSpell{Passing Fancy, Mass}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone living creature/level, no two of which can be more than 30 ft. apart|4d4 rounds (D)|Will negates|yes}[]
    \DeclareSpellDescription{Passing Fancy, Mass}{This spell functions as per passing fancy except as noted above.}
        
\DeclareSpell{Scribe's Binding}{transmutation (polymorph) []|V,  S,  F (a book bound in precious metals and treated with rare oils,  worth 1, 000 gp per HD of the target)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetscreature touched|permanent|Fortitude negates|yes}[]
    \DeclareSpellDescription{Scribe's Binding}{Hermea's benevolent Council of Enlightenment uses this spell to humanely preserve their society's greatest minds from the ravages of time, though it has seen far more sinister employment when put to use by other organizations that have since discovered its utility. This spell binds a single creature into a prepared book, sustaining it in suspended animation and filling the book with its experience and knowledge. The tome weighs 10 pounds and has one page for every day of the subject's life. The cover and binding transform to reflect the subject's appearance, interests, and tastes. Every thought and memory-including those the target may have forgotten long ago-are perfectly transcribed within the enchanted pages, penned in excruciating detail in the language that the creature was thinking or speaking in when the event occurred. If a memory includes dialogue in a language the subject didn't understand, that dialogue is reproduced phonetically, and must be translated by a reader who knows that language. Any alterations to a subject's memories-such as by a modify memory spell-appear in a subtly different script; a successful DC 35 Linguistics check is needed to identify this.  Spells that modify or remove text-such as erase or secret page-also affect the target's memory if they persist after its release. Modify memory can be used to repair any changes to its original state, or alter the accounts recorded within the book. A creature imprisoned by scribe's binding automatically fails any saving throws against effects to change or modify its memories.  A target bound by this spell can be freed by only freedom, miracle, or wish. Polymorph any object restores the target's normal form for 24 hours. Scribe's binding makes the imprisoning tome supernaturally durable (hardness 20, 10 hp per HD the imprisoned creature had). Destroying the tome immediately slays the creature imprisoned within.}
    