    
\DeclareSpell{Guardian Armor}{conjuration (teleportation) []|V,  S,  F (armor worn)|1 immediate action|close (25 ft. + 5 ft./2 levels)|Targetsone willing creature; see below|instantaneous|none|yes}[]
    \DeclareSpellDescription{Guardian Armor}{This spell teleports the suit of armor you are wearing off of your body and onto an ally within range; the target must be the same size and general shape as you. This armor appears on the target's body fully formed and properly donned, granting the creature the immediate benefit of its protection. If the target of guardian armor was already wearing armor, the armor wearing it is removed from the target's body and falls undamaged into an adjacent square.}
        
\DeclareSpell{Revenant Armor}{transmutation () []|V,  S,  F (one suit of armor)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone suit of armor|1 day/level or 1 hour/level; see below|none|no}[]
    \DeclareSpellDescription{Revenant Armor}{This spell endows a suit of armor with a singular purpose realized only after its wearer goes unconscious or is killed; whenever the wearer of a suit of armor warded by revenant armor is brought below 0 hit points or otherwise rendered unconscious (but not paralyzed or held) in combat, the armor is immediately brought to life as a Medium animated object. This animated suit of armor still contains the unconscious (or dead) body of its former wearer and moves with a shambling gait at a speed of 20 feet. This animated object has average hit points and, if the armor is made from metal, it has the metal animated object extraordinary ability (plus additional abilities based on the type of metal, as indicated on page 14 of the Pathfinder RPG Bestiary). Once animated, the revenant armor remains standing (and stands if knocked prone, doing so without provoking attacks of opportunity), and prevents the wearer of the armor from being considered helpless. If an ally of the wearer is within range of the armor, she can direct it to move, though it refuses to go anywhere that requires a skill check. If grappled or otherwise restrained, it can attempt to break free with a Strength score equal to your caster level and a CMB equal to 1 + your caster level + the armor's Strength modifier. If the armor's wearer is reduced to dust, made conscious, or removed from the armor, the spell ends.}
        
\DeclareSpell{Shield Of Shards}{transmutation () []|V,  S,  F (a shield)|1 standard action|personal|Targetsone shield you wield|1 round/level|none|no}[]
    \DeclareSpellDescription{Shield Of Shards}{This defensive spell must be cast on a shield you are currently wielding, and fractures the shield into two shards, plus one additional shard per 2 caster levels (to a maximum of 12 shards at 20th level). While shield of shards is active, you lose your shield's bonus to AC as its broken pieces orbit you. On your turn, you can direct the shards to attack an adjacent opponent as a move action. The shards' attack bonus is equal to your caster level + the modifier for the ability score that determines your spell save DCs. The shards deal an amount of slashing and piercing damage equal to 1d4 points + 1 point per shard beyond the first, and have a threat range of 19-20. They are considered magic weapons for the purpose of bypassing damage reduction. Additionally, if your shield is made from a special material (such as adamantine), the shards penetrate damage reduction and hardness as if they were weapons made from the same material.  At the end of this spell's duration, the shards reform into their original shield form. You regain its shield bonus to AC, provided you still have a free hand in which to wield it. Otherwise, the shield falls at your feet in your square.}
    