    
\DeclareSpell{Spectral Scout}{conjuration (creation) []|V,  S|1 minute|1 mile|Effectone incorporeal animal of size Tiny or smaller|10 minutes/level (D)|none|no}[]
    \DeclareSpellDescription{Spectral Scout}{You summon a spectral creature in the shape of the Tiny or smaller animal of your choice, which always appears in your square. The creature emits a faint glow of a color you choose at the time of the spell's casting, providing the illumination of a candle. It has the same statistics as the creature after which it is modeled (including ability scores, Armor Class, feats, senses, skills, and speed), but is incorporeal and has only 1 hit point. A spectral scout cannot attack, but can otherwise follow any basic instructions that could be given to a pet or animal companion of similar intelligence but without the need to make Handle Animal skill checks.  A spectral scout can communicate verbally with the caster but can't be understood by others. A spectral scout can relay information it has directly witnessed with perfect clarity, including sights, sounds, and smells, but it cannot further interpret that information. For example, a spectral scout can report on how many individuals it sees, the direction they are going, and what equipment they carry; it can't tell the caster whether the people were friend or foe, or their objective.}
        
\DeclareSpell{Sylvan Hideaway}{conjuration (creation) []|V,  S,  M (one pound of unworked stone or wood)|1 standard action|touch|Targetsone 5-foot square of touched earth|2 hours/level (D)|none|no}[]
    \DeclareSpellDescription{Sylvan Hideaway}{When this spell is cast on a natural, unworked surface, it creates an extradimensional underground space large enough to comfortably hold two creatures of any size per caster level (maximum 12). The room is sealed by a 5-foot-square camouflaged trap door that can be locked from within. (This trap door has hardness 10 and 20 hit points per caster level; the Perception DC to see the hidden trap door equals the spell's save DC.) The door and room are made of the same material of the material component used to cast the spell. You can choose the shape and configuration of the room when you create it; however, any furnishings (tables, beds, etc.) in the room are made of the same material as the room and cannot be moved once created. When the spell ends, anything inside the space is ejected to the surface in the nearest available square.}
    