    
\DeclareSpell{Blightburn Weapon}{transmutation () []|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone weapon|1 round/level (D)|Will negates (object)|yes (object)}[]
    \DeclareSpellDescription{Blightburn Weapon}{You transform the target weapon into pure blightburn. The weapon functions as normal, but any creature that touches it, or that it strikes, takes 2d6 points of fire damage each round it remains in contact. In addition, the weapon emanates an aura of radiation that causes blightburn sickness. This is as the disease (see page 29), but with a 10-foot radius and a save DC equal to this spell's save DC.}
        
\DeclareSpell{Chameleon Scales}{transmutation () []|V,  S,  DF|1 standard action|personal|Targetsyou|10 minutes/level (D)||}[]
    \DeclareSpellDescription{Chameleon Scales}{You temporarily alter the color of your skin, hide, or scales to another option legal for your race. You take no penalty for using Disguise to appear as a member of a different race as long as that race has the same type and color of skin, hide, or scales as you.}
        
\DeclareSpell{Dark-Light}{evocation () [light]|V,  S,  M/DF (a pinch of Darklands earth)|1 standard action|medium (100 ft. + 10 ft./level)|Area20-ft.-radius burst|instantaneous|Fortitude partial|yes}[]
    \DeclareSpellDescription{Dark-Light}{You evoke a powerful light that affects all sighted creatures that do not posses light sensitivity. Those that succeed on their saves are dazzled for 1 round per level; those who fail are blinded for the same duration.}
        
\DeclareSpell{Enlarge Tail}{transmutation () []|V,  S|1 standard action|personal|Targetsyour tail|1 hour/level||}[]
    \DeclareSpellDescription{Enlarge Tail}{When attacking with your tail or tail weapons, you gain 5 feet of reach, a +1 bonus on attack rolls, and a +2 bonus on damage rolls.}
        
\DeclareSpell{Lead Plating}{conjuration (creation) []|V,  S,  F (an ounce of lead)|1 standard action|touch|Targetsa creature or object weighing up to 100 lbs./level|1 minute/level (D)|Will negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Lead Plating}{You enclose the target in a thin sheath of lead. This doesn't restrict the target's movement or functionality, but protects it from the effects of radiation and prevents the penetration of many divination spells. The lead doesn't coat the target's equipment.}
        
\DeclareSpell{Strip Scales}{transmutation () []|V,  S,  M/DF (a single reptile scale)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone living creature|1 minute/level|Fortitude|yes}[]
    \DeclareSpellDescription{Strip Scales}{You reduce the target's racial natural armor bonus by 1 point per 3 caster levels.}
        
\DeclareSpell{Unseen Engineers}{conjuration (creation) []|V,  S, M|1 standard action|long (400 ft. + 40 ft. level)|Effecta team of tiny, invisible engineers|1 minute/level|none|no}[]
    \DeclareSpellDescription{Unseen Engineers}{You conjure an invisible team of tiny engineers to construct a trap at alarming speed. Originating at your location, the team must remain within range of you or the spell ends. The engineers construct a mechanical trap of your choice. Construction takes a number of rounds equal to the trap's challenge rating. The engineers must have the materials available. At the end of the construction time, use your Craft (traps) skill with a +5 bonus to determine the success of their work. If the engineers succeed, the trap is complete and the spell ends. If they fail, the materials are deposited at that location and the spell ends. If the spell's duration ends before the trap is complete, the engineers automatically fail.  The engineers move at your base speed and can carry only materials required in the construction of the desired trap. They can't attack in any way or be killed, and dissipate if they take 12 points of damage from area attacks (they get no saves against attacks).}
    