    
\DeclareSpell{Cheetah's Sprint}{transmutation|V|1 swift action|personal|Targets: you|1 round||}[]
    \DeclareSpellDescription{Cheetah's Sprint}{A wild surge of energy courses through your body and propels you into a sprint. If you take a charge or run action before the end of your turn, you can move a total distance of up to 10 times your base land speed. This adjustment is an enhancement bonus. There is no effect on other modes of movement, such as burrow, climb, fly, or swim. As with other effects that increase your speed, this spell affects your jumping distance.}
        
\DeclareSpell{Clear Grove}{transmutation|V,  S,  M/DF (a miniature hoe)|10 minutes|close (25 ft. + 5 ft./2 levels)|Effect: 20-ft.-radius clearing|2 hours/level (D)|none|no}[]
    \DeclareSpellDescription{Clear Grove}{Trees, shrubs, and other thick vegetation move out of the spell's area. The affected area is cleared of all vegetation thick enough to provide cover or concealment. This also creates a hole in any tree canopy, allowing sunlight to pass through. Affected trees and undergrowth form a 5-foot-wide ring along the edge of the clearing, which may provide cover or concealment based on the thickness of the vegetation (at the GM's discretion).  This spell doesn't affect creatures of the plant type. The spell can affect vegetation altered with spells of equal or lower level (such as entangle or spike growth). When the spell ends, the trees and undergrowth move back to their original places unless they're destroyed or somehow restrained (the amount of time this takes is subject to the GM's discretion).}
        
\DeclareSpell{Globe Of Tranquil Water}{abjuration|V,  S,  M/DF (a glass globe)|1 standard action|20 ft.|Area: 20-ft.-radius emanation, centered on you|1 minute/level (D)|none|no}[]
    \DeclareSpellDescription{Globe Of Tranquil Water}{Upon casting this spell, a rippling bubble of calm water extends outward from you to a radius of 20 feet and remains centered on you when you move. The bubble blocks all natural and magical precipitation such as rain, snow, and hail (including spells such as ice storm). This bubble also pushes out any fog or mist within the area, though it does not affect temperature and can't block natural or magical lightning.  All water in this radius counts as calm water for the purposes of Swim checks, and the bubble prevents sprays and blasts of mundane and magic water from striking with enough force to deal damage, move creatures or halt their movement, or perform any action that requires an attack roll or combat maneuver check.  Water elementals are affected by a globe of tranquil water the same way creatures of the plant type are affected by an antiplant shell.}
        
\DeclareSpell{Oasis}{transmutation|V,  S,  M/DF (1 gallon of water)|30 minutes|close (25 ft. + 5 f t./2 levels)|Effect: water source similar to a natural spring|instantaneous|none|no}[]
    \DeclareSpellDescription{Oasis}{This spell functions in any natural terrain on the Material Plane. It redirects the flow of water in the ground toward the surface at the designated point, creating a permanent water source similar to a natural spring. The spring discharges 5 gallons of pure drinking water per caster level each hour. If the shape of the terrain is suitable, a pond forms around the spring. If there is already a natural spring within 1 mile, its water output is reduced by an amount equal to the water produced by this spell's spring. A spring that has its water output reduced to 0 gallons per hour dries up and ceases to be a spring.  This spell functions differently depending on the terrain in which it's cast. In a desert, you must succeed at a DC 25 caster level check to actually create the spring, and its output is 1 gallon of drinking water per caster level each day. Furthermore, in dry areas, erosion may cause the flow of water to be blocked if the affected area is left untended before a sufficient amount of vegetation has grown around it to keep the soil in place. In an arctic environment, low temperatures may cause the water to freeze. In a tropical environment, parasites may contaminate the water if the spring is created in a place where the water stands in a stagnant pool.}
        
\DeclareSpell{Planar Refuge}{conjuration (creation)|V,  S,  M (precious stones worth 500 gp)|1 hour|close (25 ft. + 5 ft./2 levels)|Effect: 50-ft.-radius area of safe environment|1 day/level|none|no}[]
    \DeclareSpellDescription{Planar Refuge}{This spell enforces the rules of the Material Plane on other planes of existence. Upon casting this spell on another plane, a spherical pocket of wilderness terrain forms around the designated point. The affected area defies the local climate and planar traits, suppressing any harmful environmental effects such as toxicity, extreme temperatures, or lack of air (though this spell doesn't affect gravity). The area also becomes lush with edible plants whose appearance, taste, and smell bear characteristics distinct to the environment. On a negative-dominant planeGMG, for example, the plants grow ghastly white leaves and taste bitter. Though planar refuge can be cast on any plane of existence other than the Material Plane, it requires a body of solid matter at least as large as its area to function.  Planar refuge can be made permanent with a permanency spell cast by a caster of 11th level or higher at a cost of 7,500 gp.}
        
\DeclareSpell{Raven's Flight}{transmutation|V|1 swift action|personal|Targets: you|1 round||}[]
    \DeclareSpellDescription{Raven's Flight}{You can cast this spell only if it is the first action you take on your turn. In a burst of shadowy feathers, you turn into a Tiny blurred shape reminiscent of a black raven until the beginning of your next turn. You gain a fly speed of 50 feet with good maneuverability, and apply appropriate size modifiers (though your ability scores don't change). Until the beginning of your next turn, you can take only the 5-foot step, move, run, or withdraw actions. If the spell is dispelled while you are still aloft, the power of flight dissipates slowly; you float downward 60 feet on your next turn, then fall any remaining distance.}
        
\DeclareSpell{Wild Instinct}{divination|V,  S,  DF|standard action|personal|Targets: you|8 hours||}[]
    \DeclareSpellDescription{Wild Instinct}{This spell sharpens your senses, allowing you to perceive threats you would otherwise miss. You become aware of sounds and smells you would normally overlook, and even retain the ability to detect threats when soundly asleep. For the duration of the spell, you gain a +5 bonus on Perception checks to act in a surprise round. Additionally, you don't take a penalty on Perception checks while sleeping, and can choose to wake if you notice a threat while asleep.}
    