    
\DeclareSpell{Alluring Light}{enchantment (compulsion) [light,  mind-affecting]|V,  S|1 standard action|30 ft.|Area30-ft.-radius emanation centered on you|instantaneous|Will negates (see text)|yes}[]
    \DeclareSpellDescription{Alluring Light}{You glow with a soft radiance that calls out to all who see it. Each enemy that fails its save is drawn to you and must use its move action to approach you at the beginning of each of its turns for 1 round per caster level. An affected target must move toward you in the most direct path it can, though it can step around obstacles or other creatures. This spell can't force a creature to walk into an area that might obviously harm or kill it (such as into a pit, over a patch of floor studded with caltrops, or through a wall of fire). An affected creature that loses sight of you is not compelled to move toward you, although if it later regains vision of you while still affected by this spell, it must again move toward you. Any hostile action against an affected creature (such an attack of opportunity due to its movement) cancels the spell's effect against that creature. Your initial flash of light also increases the light level within the spell's area by one step, up to normal light (darkness becomes dim light, and dim light becomes normal light) for 1 round per caster level.}
        
\DeclareSpell{Moonrise Arrow}{evocation () [light]|V,  S|1 standard action|touch|Targetsup to 50 pieces of ammunition, all of which must be together at the time of casting|10 minutes/level|Fortitude negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Moonrise Arrow}{You cause ammunition, including shuriken, to glow with faint silvery light. The ammunition counts as magic and silver for the purpose of overcoming damage reduction, in addition to the properties of any other special material the ammunition has. Incorporeal undead and shapechangers take an additional 1d8 points of damage from such ammunition. The targeted ammunition sheds dim light in a 5-foot radius for 1 round after it is fired or thrown.}
    