    
\DeclareSpell{Detect Relations}{divination () []|V,  S,  F/DF (a seed)|1 standard action||Targetsone creature per level, no two of which can be more than 30 ft. apart|concentration, up to 1 min./level (D)|Will negates; see text|no}[]
    \DeclareSpellDescription{Detect Relations}{You can determine whether or not two or more creatures are related by blood. The amount of information gleaned depends on how long you study a particular area or set of subjects.  1st round: Whether or not the subjects are related by blood.  2nd round: Number of related subjects and their general relation to one another (for example, this would reveal that one subject is a descendant of the other, but it would not specify "mother" or "grandmother").  3rd round: Precise relationship between subjects in the area. A target's Will save prevents you from determining its exact relationship with another creature, and only one subject needs to succeed at this save to prevent you from determining its relationship with another creature. (So, for instance, if two brothers are in the area and one succeeds at his Will save, you could tell that they are siblings, but could not distinguish whether they are full- or half-siblings.)  Each round, you can turn to detect relations in a new area. The spell can penetrate barriers, but 6 inches of stone, 1 inch of common metal, a thin sheet of lead, or 1 foot of wood or dirt will block it.  This spell functions by analyzing the blood and minds of creatures in the area, collectively examining these traits and comparing them to those of others in the area while looking for patterns. Thus, adoptive siblings and parents cannot be detected with this spell, since they share no blood.}
        
\DeclareSpell{Business Booms}{enchantment () []|V,  S, M|1 standard action|touch|Targetsone building|see text (D)|none|no}[]
    \DeclareSpellDescription{Business Booms}{You may cast this spell immediately prior to spending 1 day of downtime to promote a business (see page 85 of Ultimate Campaign). The spell is cast on a building you wish to promote, which is magically bestowed with magical decorations and other improvements that make it generally more appealing, and it is treated as seeing increased activity for the spell's duration. If the spell is cast on a building that you do not promote immediately thereafter, the spell is expended with no effect.  After the initial day of downtime spent promoting your building, the spell maintains the influx of activity for a number of days equal to half your caster level (maximum 5 days). During this time, you needn't spend additional downtime to promote the building, but you must spend capital as normal to promote the building. The capital the affected building generates for you is unaffected by the spell. If you spend 1 day promoting a different building than the target of this spell while this spell remains active, the spell immediately ends.}
        
\DeclareSpell{Prosperous Room}{enchantment () []|V,  S|1 day|touch|Targetsroom you own; see text|1 day/level (D)|none|yes}[]
    \DeclareSpellDescription{Prosperous Room}{The targeted room is enchanted to have magical appeal for customers, an increase in the workflow of its employees, or the generation of additional materials to work with. While this spell is in effect, the targeted room produces 1 more Goods, Labor, Influence, or Magic than it already does. If the room produces multiple types of capital, it produces an additional capital of each type. If the room generates gp, it generates 25\% more. Only the capital that the room normally generates increases- rooms that do not already generate Magic, for instance, do not generate Magic because of this spell.  While this spell is in effect, neither you nor your allies can further interact with the affected room or the spell's effects immediately end. You cannot spend downtime actions to run a business with a room that is affected by this spell, though any employees or workers that operate within the room may continue to do so normally.}
        
\DeclareSpell{Renovation}{transmutation () []|V,  S,  M (silver dust worth 1, 000 gp)|8 hours|touch|Targetsone unoccupied structure|instantaneous|none (object; see text)|no}[]
    \DeclareSpellDescription{Renovation}{Upon casting this spell, you permanently rearrange and resize the rooms in a building you constructed as a downtime activity (see page 84 of Ultimate Campaign). You may reorganize and remap the building however you please, as if each room had just been constructed and is being positioned for the first time. You cannot make any changes to a building that changes how much a room would cost to create or that alters the benefits a room provides. The structure also must remain in the same general position within the district. If you don't wholly own the structure, all of the structure's owners must consent to the changes being made before the spell is cast; otherwise, it fails immediately.}
        
\DeclareSpell{Teleport Structure}{conjuration (teleportation) []|V,  M (gold dust worth 50 gp)|8 hours|touch|Targetsone building|instantaneous|Will negates (object)|yes (object)}[]
    \DeclareSpellDescription{Teleport Structure}{You instantly teleport a building in a settlement you control to another lot or series of lots in the same settlement district. The building to be teleported must be unoccupied, and the area to which you wish to move the building must be cleared and unoccupied during the casting of this spell. A building cannot be teleported to an area it would not normally be able to occupy, such as an area adjacent to a prohibited building type. If you don't wholly own the structure, all of the structure's owners must consent to the structure's teleportation before the spell is cast; otherwise, it fails immediately.  This spell only functions on buildings that occupy a number of lots equal to one-fourth your caster level (so, for instance, a 16th-level caster could use this spell on a building that occupies up to 4 lots).}
        
\DeclareSpell{Bless Army}{enchantment (compulsion) [mind-affecting]|V,  S,  DF|1 standard action|1 hex|Targetsone army|1 battle|none|yes (harmless)}[]
    \DeclareSpellDescription{Bless Army}{Bless army fills an army with courage. The army gains a +1 bonus on OM and Morale checks.}
        
\DeclareSpell{Imbue Army Special Ability}{evocation () []|V,  S,  F (a silver mirror worth 100 gp)|10 minutes|1 hex|Targetsone army|1 battle|none or Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Imbue Army Special Ability}{You imbue the target with an army special ability (see page 242 of Ultimate Campaign) possessed by the army's commander. The army is treated as if it consists of units who all possess the chosen special ability. This special ability is in addition to any special abilities the army inherently possessed prior to the casting of the spell.}
        
\DeclareSpell{Tactical Insight}{divination () []|V,  S|1 standard action|1 hex|Targetsone army|1 battle|none|no}[]
    \DeclareSpellDescription{Tactical Insight}{Choose a single army tactic. You grant mastery of this tactic to the target army for the spell's duration. This tactic may bring an army's total known tactics to a number greater than normally allowed.}
        
\DeclareSpell{Ceremony}{transmutation () []|V,  S,  DF|8 hours|touch or medium (100 ft. + 10 ft./level) (see text)|Targetswilling, living creature or creatures touched or one creature/level (see text)|1 hour/level or 1 day/level (see text)|Will negates (see text)|yes}[]
    \DeclareSpellDescription{Ceremony}{You harness divine power to create one of four different ceremonies-a funeral, holiday fete, marriage, or naming-and can also create two domain-based ceremonies. Each ceremony provides a boon to two living, touched subjects for 1 hour per caster level, representing the divine gifts granted by your deity as well as the normal morale-boosting benefits of participating in an officiated ceremony. Bonuses granted by these boons are sacred bonuses if you channel positive energy or profane bonuses if you channel negative energy. (Bonuses in this section are referred to simply as sacred bonuses for ease of reading.) Only subjects whose alignments are within one step of your deity can be affected by this spell.  If you are using the downtime system from Pathfinder RPG Ultimate Campaign, you may use additional resources to augment the effect of a particular ceremony. You may spend 10 Goods, Labor, or Influence or 2 Magic to create a larger ceremony and grant an additional boon that lasts for 1 day per caster level (up to a maximum of 5 days). The type of capital spent should reflect the preparation required for the specific ceremony. Augmented boons affect the creatures touched as well as a number of intelligent, properly aligned creatures within medium range equal to your caster level (up to a maximum of 10 creatures), granting all subjects the benefits of the original boon as well as the benefits of an augmented boon, representing the divine gifts granted to these witnesses by your god.  Unless otherwise stated, use-activated abilities are supernatural abilities and abilities that emulate the effects of a spell are spell-like abilities; in either case, abilities granted by a boon are generally usable only once or until the duration of the spell ends, whichever comes first. Spell-like abilities are cast at a creature's highest caster level gained, or, if the creature has no caster level, CL 1st. Constant or passive effects and bonuses granted by this spell can be dispelled as normal, using your caster level to do so.  Funeral: A funeral service must involve a corpse and at least one willing companion or next of kin. The subject gains a +2 sacred bonus against death effects.  Holiday Fete: A holiday fete may involve up to two willing creatures. The subject gains a +1 sacred bonus on Fortitude saves.  Marriage: A marriage must involve two willing creatures. The subject gains a +1 sacred bonus on saves against fear and emotion effects.  Naming: A naming must involve a willing parent or parents and a newborn (who is touched but unaffected). The subject can use sanctuary once.  The augmented versions of these four ceremonies are identical, granting the subject a +2 sacred bonus on all saving throws.  In addition to these four ceremonies, each cleric gains two more ceremonies according to her domain. The names of domain ceremonies and their relevant boons are listed below. Unless otherwise noted, each of the following ceremonies requires at least two willing subjects.  Air: Celebration of Storms. The subject can use feather fall once. Augmented: The subject gains a +4 sacred bonus on saves against effects with the air descriptor.  Animal: Ritual of Beasts. The subject can use speak with animals once (this effect lasts 3 rounds). Augmented: The subject can use charm animal once.  Artifice: Apparatus's Observance. The subject can heal a construct creature with a touch, healing 1d3 points of damage. Augmented: The subject can heal a construct creature 1d6 points of damage.  Chaos: Anarchic Revelry. The subject can force a lawful-aligned foe within 30 feet to roll an attack roll twice and take the less favorable result. This ability must be announced before the first attack roll is made. Augmented: The first time the subject deals damage to a foe with a melee attack, the attack is treated as chaotic for the purpose of overcoming DR.  Charm: Jubilee of Delight. The subject gains a +2 sacred bonus on his next Bluff, Diplomacy, or Intimidate check. Augmented: The subject gains a +2 sacred bonus on saving throws against charm and compulsion effects.  Community: Celebration of Bonding. As a standard action, the subject can heal a touched creature 1d6 points of nonlethal damage. Augmented: The subject is cured of the fatigued, shaken, and sickened conditions.  Darkness: Glorify Shadows. The subject gains darkvision to a range of 30 feet (or increases current range of darkvision by 10 feet). Augmented: The subject increases range of darkvision by 30 feet.  Death: Dance of the Dead. The subject can use bleed up to three times. Augmented: The subject can use cause fear once.  Destruction: Day of Dismantling. The subject gains a +1 sacred bonus on attacks and damage rolls against inanimate objects. Augmented: The bonus becomes +2.  Earth: Festival of Soil. The subject can cast plant growth (enrichment) once. Augmented: The subject gains a +4 sacred bonus on saves against effects with the earth descriptor.  Evil: Unholy Gala. The subject can cause a good-aligned foe to become sickened for 1 round as a melee touch attack. Augmented: This boon can be used three times.  Fire: Fire Calling. Nonmagical fires the subject makes cannot be extinguished by nonmagical means, though spells and other magical effects function as normal. Augmented: The subject gains a +4 sacred bonus on saves against effects with the fire descriptor.  Glory: Resplendent Feast. The subject receives a +2 bonus on a single Charisma-based skill check. Augmented: This boon can be used three times.  Good: Festival of Benevolence. The subject gains a +1 sacred bonus on melee attacks and melee damage rolls against evil-aligned foes. Augmented: The bonus becomes +2.  Healing: Touch of Assuagement. The subject can heal a dying creature 1d4 hit points as a standard action. Augmented: This boon can be used three times.  Knowledge: Liturgy of Learning. The subject can attempt any Knowledge skill check untrained. Augmented: This boon can be used three times.  Law: Observance of Order. The subject gains a +5 sacred bonus on the next combat maneuver check she makes against a chaotic-aligned foe. Augmented: The subject gains a +2 sacred bonus to CMD against chaotic-aligned foes.  Liberation: Freedom Festival. The subject can use remove fear once. Augmented: The subject gains a +2 sacred bonus to CMD.  Luck: Fete of Fortune. The next time the subject rolls a d20, he may roll twice and take the more favorable result. Augmented: The subject may use this ability on any single d20 roll, not just the next one.  Madness: Rite of Insanity. The subject can, as a melee touch attack, cause a foe to become confused for 1d4 rounds (DC 13 Will negates). Augmented: This boon can be used twice.  Magic: Arcane Obeisance. The subject gains a +2 sacred bonus on Spellcraft checks made while researching a spell or crafting a magic item. Augmented: The subject gains a +2 sacred bonus on Knowledge (arcana) or (religion) checks made while researching a spell.  Nobility: Knighting Ceremony. The subject receives a +1 sacred bonus on attack and damage rolls with one weapon of her choice. Augmented: The bonus becomes +2.  Plant: Harvest Festival. The subject can use speak with plants once, but the duration is 1 minute. Augmented: This boon can be used three times.  Protection: Ceremony of Sanctuary. The subject can use sanctuary once. Augmented: The subject gains a +2 sacred bonus to AC.  Repose: Spirit Ward. The subject can attempt a melee touch attack against a flat-footed foe to put him to sleep for 1d4 rounds. Augmented: This boon can be used three times.  Rune: Ancestral Observance. The subject gains a +2 sacred bonus on saves against language-dependent effects. Augmented: The subject gains a +2 sacred bonus on Linguistics checks.  Scalykind: Song of Serpents. The subject gains a +2 sacred bonus on saves against gaze attacks. Augmented: The subject gains a +4 sacred bonus to AC against the distraction attack of swarms.  Strength: Ritual of Might. The subject gains a +1 sacred bonus on Strength-based skill checks and Strength checks. Augmented: The bonus becomes +2.  Sun: Solstice Celebration. The illumination radius of any torch or other mundane light source held by the subject increases by 10 feet. Augmented: The subject gains a +4 sacred bonus against effects with the light descriptor.  Travel: Festival of Journeys. The subject can choose to ignore the effects of difficult terrain for 1 round. Augmented: This boon may be used three times.  Trickery: Communion of Liars. The subject gains a +2 sacred bonus to AC the first time he is attacked while flanked. Augmented: This boon functions the first three times the subject is attacked while flanked.  Void: Celestial Observance. The subject knows the direction of north from her current position for the duration of this spell. Augmented: The subject is immune to confusion effects.  War: Call to Battle. The subject gains a +1 sacred bonus on attack rolls. Augmented: The subject gains a +1 sacred bonus on damage rolls.  Water: Water Blessing. The subject can use water breathing. Augmented: The subject gains a +4 sacred bonus on saves against effects with the water descriptor.  Weather: Song of the Tempest. The subject can call one 10-foot-by-10-foot rain cloud in an area within 30 feet, requiring creatures in the affected area attempting to cast spells to first succeed at DC 13 concentration checks for 1 round. Augmented: The DC is 15 for 3 rounds.}
    