    
\DeclareSpell{Black Spot}{necromancy|V,  S|1 standard action|touch|Targets: creature touched|permanent|Will negates|yes}[]
    \DeclareSpellDescription{Black Spot}{The black spot is a specific and feared pirate curse. An intangible, illusory black spot manifests above the target's head and remains until the target dies or the curse is lifted. The black spot cannot be covered or hidden by any means, including other illusions.

The black spot radiates a cursed aura in a 10-foot radius around its target. Anyone within the aura gains a +2 bonus on weapon attack and damage rolls against the target. In addition, the target has a -4 penalty on saving throws against death effects.

Every day in which a creature bears a black spot, it must make a Fortitude save. On a failed save, the creature takes 1 point of Constitution damage. The damage cannot be healed until the black spot is removed. If the creature's Constitution reaches 0, it dies. Pirates killed by this spell often return as ghosts, but that is not a direct effect of this spell.

The black spot cannot be dispelled, but it can be removed with break enchantment, limited wish, miracle, remove curse, or wish.}
        
\DeclareSpell{Salvage}{transmutation|V,  S,  M|1 standard action|long (400 ft. + 40 ft./level)|Targets: one shipwreck|see text|Fortitude negates (object)|yes (object)}[]
    \DeclareSpellDescription{Salvage}{An invisible force pulls together the remains of a shipwreck.

Bits of hull, tattered sails, broken masts, and smashed figureheads knit themselves back together. Rotten wood turns solid once more, and sails re-weave themselves as the rigging snakes across the masts.

It takes a variable amount of time for the ship to rebuild itself, depending on its size.

 SizeDurationRaft1 minuteRowboat1 minuteKeelboat10 minutesLongship1 hourSailing ship2 hoursWarship3 hoursGalleon4 hours  At the end of the duration, an air bubble forms around the repaired ship. If submerged, the ship shoots to the surface, erupting with a great splash before settling on the water.

Though the spell requires time to repair the ship, its effects are instantaneous. A salvaged ship cannot be dispelled to return it to a shipwreck. However, before the spell's duration ends and while the ship is still being repaired, salvage can be dispelled to interrupt the repair process. The ship remains in the condition it was in when the spell was interrupted until a new salvage spell is cast (but continues to age normally and suffers the effects of its environments). A new salvage spell's duration is modified by any repairs already begun.}
        
\DeclareSpell{Skeleton Crew}{necromancy|V,  S,  M|1 standard action|touch|Targets: one or more humanoid corpses touched|1 day/level|none|no}[]
    \DeclareSpellDescription{Skeleton Crew}{This spell turns corpses into skeletons (Pathfinder RPG Bestiary 250) that act as crew and obey your commands to the extent of their abilities.

The undead you create are 1 Hit Die skeletons that possess Profession (sailor) scores equal to half your character level plus your Wisdom modifier (for clerics), Intelligence modifier (for witches and wizards), or Charisma modifier (for sorcerers and summoners). Each skeleton can perform the duties of one crew member but has no other abilities. The created skeletons cannot speak, attack, or even defend themselves. The only orders they obey are ones pertaining to the operation of a ship. Skeletal crew members are not proficient with any weapons or armor.

You can't create more Hit Dice of skeletal crew members than twice your caster level with a single casting of skeleton crew. The desecrate spell doubles this limit.

The undead you create by casting skeleton crew remain under your control for the duration of the spell, and do not count against your limit of total Hit Dice worth of undead creatures you can control.

A skeletal crew member can only be created from a mostly intact humanoid corpse. The corpse must have bones. When you cast this spell, any flesh left on the corpses melts away into fog.}
        
\DeclareSpell{Track Ship}{divination (scrying) [travel]|V,  S,  F (piece of ship)|1 standard action|see text|Effect: magical icon|1 hour/level|Will negates (object)|yes (object)}[]
    \DeclareSpellDescription{Track Ship}{In order to cast this spell, you must have a piece of the ship you wish to track. Merchants often preserve slivers from their trade ships specifically for this purpose. You also need a nautical chart.

When you cast this spell, an icon of the targeted ship appears on the nautical chart. The icon moves as the ship moves for the duration of this spell. If the ship is not within the area delineated by the chart, the spell fails. If the ship is reduced to 0 or fewer hit points, its icon changes from a ship to a skull and crossbones.}
        
\DeclareSpell{Unseen Crew}{conjuration (creation)|V,  S,  M|1 standard action|long (400 ft. + 40 ft./level)|Effect: one invisible sailor per level|1 day/level|none|no}[]
    \DeclareSpellDescription{Unseen Crew}{An unseen crew member is an invisible, shapeless force that performs the duties of one crew member. It can tie off ropes, hoist sails, swab decks, and other such duties. An unseen crew member possesses no other skills. It cannot fight, speak, or even defend itself.

An unseen crew member has a Strength score of 10 and a Profession (sailor) score equal to half your character level plus your Intelligence modifier (for witches and wizards) or your Charisma modifier (for bards, sorcerers, and summoners). It cannot fly, but it can climb, swim, or walk with a base speed of 20 feet.

An unseen crew member cannot be killed, but it dissipates if it takes more than 1 point of damage per caster level you possess from area attacks (it gets no saves against attacks). If you attempt to send an unseen crew member beyond the spell's range (measured from your current position), the crew member ceases to exist.}
    