    
\DeclareSpell{Beanstalk}{conjuration (creation)|V,  S,  M (a small handful of beans)|1 minute|0 ft. (see text)|Effect: a 5-foot-radius beanstalk that grows to a height of 50 ft./caster level|24 hours|none|no}[]
    \DeclareSpellDescription{Beanstalk}{When casting this spell, you must plant the material components in soil. When you do, at the end of casting, a large beanstalk rises up from the ground. It's strong enough to support Huge or smaller creatures weighing no more than 2,000 pounds total, and has enough handholds and footholds that it can be climbed as if it were knotted rope (Climb DC 5). At the end of the spell's duration, the beanstalk withers and dies at an accelerated rate, leaving nothing more than a pile of compost.}
        
\DeclareSpell{Flaming Aura}{transmutation [fire]|V,  S,  M/DF (a small piece of charcoal)|1 standard action|personal|Targets: you (see text)|1 minute/level|none (harmless, see text)|no (harmless, see text)}[]
    \DeclareSpellDescription{Flaming Aura}{The spell allows you channel fire into your very being. If you don't already have the fire subtype, this spell grants you the fire subtype. If you already have the fire subtype, you instead channel the flames from your being outward, creating a 10-foot-radius aura of fire centered on you. Creatures who enter or end their turns in the aura must succeed at a Fortitude saving throw or take 1d8 points of fire damage.  Multiple castings of this spell stack; you can cast it once on yourself to gain the fire subtype, then again to manifest the aura of flames around you.}
        
\DeclareSpell{Frosty Aura}{transmutation [cold]|V,  S,  M/DF (a chunk of ice or a few drops of water melted from glacier ice)|1 standard action|personal|Targets: you (see text)|1 minute/level|none (harmless, see text)|no (harmless, see text)}[]
    \DeclareSpellDescription{Frosty Aura}{The spell allows you to channel cold into your very being. If you don't already have the cold subtype, this spell grants you the cold subtype. If you already have the cold subtype, you instead channel the frost from your being outward, creating a 10-foot-radius aura of cold centered on you. Creatures who enter or end their turns in the aura must succeed at a Fortitude saving throw or take 1d8 points of cold damage.  Multiple castings of this spell stack; you can cast it once on yourself to gain the cold subtype, then again to manifest the aura of frost around you.}
        
\DeclareSpell{Quick Throwing}{transmutation|V,  S,  M|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature/level, no two of which can be more than 30 ft. apart|1 round/level|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Quick Throwing}{Those under the effects of this spell become faster in the use of thrown weapons. They can draw thrown weapons (including rocks if they have the rock throwing ability) on their bodies or within their space without the need for the Quick Draw feat, allowing them to make their full normal rate of attacks with such weapons. This has no effects on other forms of ranged weapon ammunition.}
        
\DeclareSpell{Thunderous Footfalls}{transmutation|V,  S,  M|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one Large or larger creature|1 round/level|Fortitude negates (harmless)|no (harmless)}[]
    \DeclareSpellDescription{Thunderous Footfalls}{This spell makes the target creature's footfalls shake the ground violently as he trundles, which may knock down smaller creatures as he passes by, though it also makes the target slower on land. The target's land speed is reduced by half (round down to the nearest 5-foot increment), but each time he moves overland adjacent to a creature that is at least one size category smaller than he is, that creature must succeed at a Fortitude saving throw or be knocked prone.}
        
\DeclareSpell{Thanatotic Fury}{transmutation|V,  S,  M (shavings from a holy symbol)|1 standard action|personal|Targets: you (see text)|1 minute/level||}[]
    \DeclareSpellDescription{Thanatotic Fury}{You may cast this spell only if you have the giant subtype. When casting this spell, you channel the fury and the abilities of thanatotic titans, gaining some of their abilities for a short period of time. When you hit a creature capable of casting divine spells, that creature must succeed at a Will saving throw or be unable to cast divine spells for 1d4 rounds and be shaken for the same duration. If the save is successful, the target is instead shaken for only 1 round.  Additionally, your attacks are treated as epic and evil for the purposes of overcoming damage reduction.}
        
\DeclareSpell{Titanic Anchoring}{transmutation|V,  S,  M (a shaving of oak root)|1 standard action|personal|Targets: you|1 round/level||}[]
    \DeclareSpellDescription{Titanic Anchoring}{You become grounded and nearly immovable. You are immune to the pull and push special abilities, and all bull rush, grapple, overrun, reposition, and trip combat maneuvers made by creatures your size or smaller always fail. You gain a +10 bonus to your CMD against those combat maneuver checks made by creatures larger than you.}
    