    
\DeclareSpell{Kreighton's Perusal}{divination|V,  S|1 standard action|touch|Targets: book touched|instantaneous|Will negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Kreighton's Perusal}{You gain a brief but incomplete understanding of one book's contents, equivalent to having skimmed its pages for 1 hour. This insight is not sufficient to translate unknown languages, decipher codes, or memorize text, but it does allow the caster to learn what topics the book discusses- invaluable to a Pathfinder who must make a snap decision when performing research or deciding whether or not to abscond with a volume. In addition, you instantly benefit from any bonuses or effects the book would normally grant to anyone who reads it for 1 hour (such as the bonuses gained from reading volumes of the Pathfinder Chronicles; see pages 26-27).}
        
\DeclareSpell{Collaborative Thaumaturgy}{universal|V,  S,  F (a bronze tuning fork)|1 immediate action|close (25 ft. + 5 ft./2 levels)|Targets: one creature|instantaneous||}[]
    \DeclareSpellDescription{Collaborative Thaumaturgy}{You tap into the magical resonance between you and your allies to enhance one another's magic. Cast this spell when an ally casts a spell at least 1 level lower than the highest-level spell she can cast.

The ally casts her spell as if one of the following metamagic feats were applied to it without increasing the spell level or casting time: Enlarge Spell, Extend Spell, Silent Spell, or Still Spell. If the ally is the target of two collaborative thaumaturgy spells when casting a spell, the ally can instead apply the Empower Spell metamagic feat to a spell at least 2 levels lower than the highest-level spell she can cast. Finally, if the ally is the target of three collaborative thaumaturgy spells when casting a spell, she can instead apply the Maximize Spell or Widen Spell metamagic feat to a spell at least 3 levels lower than the highest-level spell she can cast. You can't target yourself with collaborative thaumaturgy.}
        
\DeclareSpell{Sure Casting}{divination|V,  F (a square of cloth and a needle)|1 standard action|personal|Targets: you|1 round (see text)||}[]
    \DeclareSpellDescription{Sure Casting}{You gain temporary insight into your enemies' magical defenses.

When you next cast a spell before the end of the next round, treat your caster level as 5 higher than normal for the purpose of overcoming spell resistance. This bonus doesn't increase any other effects that depend on caster level, such as the spell's damage or range, and affects only the first spell cast after sure casting.}
        
\DeclareSpell{Cauterizing Weapon}{transmutation|V,  S,  M (a gobbet of melted wax)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one weapon or 50 projectiles, all of which must be together at the time of casting|1 minute/level|Will negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Cauterizing Weapon}{You infuse a weapon with faint but pernicious energy that stymies accelerated healing. Damage dealt by the weapon or ammunition is treated as acid, cold, electricity, and fire, but only for the purpose of negating a creature's regeneration. The weapon is also treated as silver and cold iron at 8th level and is treated as chaotic, evil, good, and lawful at 11th level for the purpose of negating regeneration.}
        
\DeclareSpell{Tactical Miscalculation}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature|1 round/level|see text|yes}[]
    \DeclareSpellDescription{Tactical Miscalculation}{The target becomes fixated on avoiding damage and fails to spot even the most opportune moments to attack. Whenever a creature the target threatens would provoke an attack of opportunity from the target, the target must succeed at a Will save or be unable to make the attack of opportunity against that creature.}
    