    
\DeclareSpell{Ablative Barrier}{conjuration (creation) [force]|V,  S,  M (a piece of metal cut from a shield)|1 standard action|touch|Targetscreature touched|1 hour/level or until discharged|Will negates (harmless)|no}[Surrounds the target with layers of force.]
    \DeclareSpellDescription{Ablative Barrier}{Invisible layers of solid force surround and protect the target, granting that target a +2 armor bonus to AC. Additionally, the first 5 points of lethal damage the target takes from each attack are converted into nonlethal damage. Against attacks that already deal nonlethal damage, the target gains DR 5/-. Once this spell has converted 5 points of damage to nonlethal damage per caster level (maximum 50 points), the spell is discharged.}
        
\DeclareSpell{Absorb Toxicity}{necromancy () []|V,  S,  M (a thorn from a poisonous plant)|1 standard action|personal|Targetsyou|10 minutes/level or until discharged|see text|no}[You become immune to diseases and toxins, absorb one, and then spread it to others.]
    \DeclareSpellDescription{Absorb Toxicity}{You absorb the toxicity of your surroundings, becoming toxic as a result. While under the effect of this spell, you are immune to diseases and poisons with which you come into contact. When you are exposed to a disease or poison, you can choose to absorb it. Doing so ends the immunity due to this spell to any disease and poison other than the one you absorbed. You remain immune to the new affliction until this spell ends. Casting absorb toxicity on yourself a second time does not allow you to absorb a second toxin, but instead resets the duration of the effect to its full 10 minutes/level.  While you have a disease or poison absorbed, you can use a melee touch attack to transfer that affliction to another creature. A missed attack does not discharge the spell, and you can try to transfer the affliction again in subsequent rounds. If you hit, this spell is discharged, and your target must make a saving throw against the transferred affliction (DC equal to this spell's save DC or the affliction's save DC, whichever is higher) or suffer its effect or initial effect immediately. The target then continues to suffer from the affliction's normal effects.  If the spell's duration expires before you have transferred the affliction, you are exposed to any absorbed poison or disease as if you had transferred it to yourself, but you gain a +2 bonus on saves against that particular instance of the poison or disease.}
        
\DeclareSpell{Abundant Ammunition}{conjuration (summoning) []|V,  S,  M/DF (a single piece of ammunition)|1 standard action||Targetsone container touched|1 minute/level|none|no}[Replaces nonmagical ammunition every round.]
    \DeclareSpellDescription{Abundant Ammunition}{When cast on a container such as a quiver or a pouch that contains nonmagical ammunition or shuriken (including masterwork ammunition or shuriken, but not special materials, alchemical attributes, or nonmagical treatments on the ammunition), at the start of each round this spell replaces any ammunition taken from the container the round before. The ammunition taken from the container the round before vanishes. If, after casting this spell, you cast a spell that enhances projectiles, such as align weapon or greater magic weapon, on the same container, all projectiles this spell conjures are affected by that spell.}
        
\DeclareSpell{Adjuring Step}{abjuration () [force]|V,  S,  M (a rabbit's foot)|1 standard action|personal|Targetsyou|1 round/level or until discharged||}[You can move slowly and safely and still cast spells, until you move quickly, make an attack, or cast a harmful spell.]
    \DeclareSpellDescription{Adjuring Step}{This spell creates a subtle and complicated force effect that is most effective when used by a still or slow-moving spellcaster or formula user. While you are subject to this spell, you can take two 5-foot steps each round and still cast spells and use spell-like abilities without provoke attacks of opportunity. This spell automatically discharges as soon as you make an attack, cast a harmful spell against another creature, or move more than 5 feet with a single move action. If the action that discharges the spell also provokes attacks of opportunity, that action still provokes attacks of opportunity as normal.}
        
\DeclareSpell{Adoration}{enchantment () [emotion,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 minute/level|Will negates (harmless)|yes}[You gain a bonus on Diplomacy checks and performance combat checks.]
    \DeclareSpellDescription{Adoration}{The target of this spell is the subject of adoration by those whom it tries to affect with Diplomacy or during performance  combat. If the target is out of combat, it receives a +2 morale bonus on all Diplomacy checks it makes to influence creatures. If the creature is engaged in performance combat (see page 153), the target gains a +2 morale bonus on all performance combat checks.}
        
\DeclareSpell{Air Bubble}{conjuration (creation) []|S,  M/DF (a small bladder filled with air)|1 standard action|touch|Targetsone creature or one object no larger than a Large two-handed weapon|1 minute/level|Will negates (harmless)|yes (harmless)}[Creates a small pocket of air around your head or an object.]
    \DeclareSpellDescription{Air Bubble}{Air bubble creates a small pocket of breathable air that surrounds the touched creature's head or the touched object. The air bubble allows the creature touched to breathe underwater or in similar airless environments, or protects the object touched from water damage.  A firearm within an air bubble can be loaded-assuming the black powder comes from a powder horn, a cartridge, or some other airtight protective device-and fired. When shooting such a firearm underwater, the shot still takes the standard -2 penalty on attack rolls for every 5 feet of water the bullet passes through, in addition to normal penalties due to range. If a firearm within the air bubble explodes, the explosion occurs normally.}
        
\DeclareSpell{Air Walk, Communal}{transmutation () [air]|V,  S,  DF|1 standard action|touch|Targetscreatures touched|10 min./level|none|yes (harmless)}[As air walk, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Air Walk, Communal}{This spell functions like air walk, except divide the duration in 10-minute intervals among the creatures touched.}
        
\DeclareSpell{Animal Aspect}{transmutation (polymorph) []|V,  S,  M/DF (a part of the animal)|1 standard action|personal|Targetsyou|1 minute/level (D)|none|yes (harmless)}[You gain some of the beneficial qualities of an animal.]
    \DeclareSpellDescription{Animal Aspect}{You gain some of the beneficial qualities of an animal. Your base form is largely unchanged and your size is unaltered, but some of your body parts are altered. Armor or gear you are wearing adjusts to your new shape for the duration of the spell. When you cast animal aspect, choose one of the following animals to gain the associated benefits. You can only have one animal aspect or greater animal aspect spell active on you at a time.  Frog: Your legs become elongated and muscular. You gain a +4 competence bonus on Acrobatics checks, and you always jump as if you had a running start.  Gorilla: Your arms become long, flexible, and strong like those of a great ape. Your unarmed damage die type increases by one step, and you gain a +4 competence bonus on combat maneuver checks when making the grapple or reposition combat maneuver.  Monkey: Your hands and arms become dexterous like those of a simian. You gain a +4 competence bonus on Climb checks, and you can throw objects as if you had the Throw Anything feat.  Otter: Your hands and feet gain webbing, and your lungs gain capacity, allowing you to move through the water with ease. You gain a Swim speed equal to half your speed, and all the benefits of having a swim speed. Additionally, you can hold your breath for 4 rounds per point of Constitution before being forced to make Constitution checks to keep holding your breath.  Raccoon: Your hands become extremely dexterous, and your feet become padded. You gain a +2 competence bonus on Disable Device, Sleight of Hand, and Stealth checks.  Raptor: Your legs become built for running speed, like those of a deinonychus. You gain a enhancement bonus of +20 feet to your base speed.  Tree Lizard: Your hands and feet gain climbing claws and climbing pads. You gain a climb speed equal to half your normal speed and all the benefits of having a natural climb speed.}
        
\DeclareSpell{Animal Aspect, Greater}{transmutation (polymorph) []|V,  S,  M/DF (a part of the animal)|1 standard action|personal|Targetsyou|1 minute/level (D)|none|yes (harmless)}[As animal aspect, but you gain two animal qualities.]
    \DeclareSpellDescription{Animal Aspect, Greater}{This spell functions like animal aspect, except you can either gain two aspects at once or one aspect that adds effects to the aspects that animal aspect grants, as described below.  Frog: You gain a Swim speed equal to half your normal speed, and all the benefits of having a swim speed.  Gorilla: You gain a +2 competence bonus on Perception checks, and a +1 competence bonus on Fortitude saves.  Monkey: You gain a +4 competence bonus on Acrobatics checks.  Otter: Your swim speed increases to your full normal speed, and you need not make concentration checks to cast spells underwater.  Raccoon: Your competence bonuses on Disable Device, Sleight of Hand, and Stealth checks increase to +4.  Raptor: Your enhancement bonus to speed increases to +30 feet, and you gain the benefit of the Run feat.  Tree Lizard: You gain a +4 competence bonus on Stealth checks.}
        
\DeclareSpell{Ant Haul, Communal}{transmutation () []|V,  S,  M/DF (a small pulley)|1 standard action|touch|Targetscreatures touched|2 hours/level|Fortitude negates (harmless)|yes (harmless)}[As ant haul, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Ant Haul, Communal}{This spell functions like ant haul (see page 202 of the Pathfinder RPG Advanced Player's Guide), except you may divide the duration in 2-hour intervals among the creatures touched.}
        
\DeclareSpell{Arcane Cannon}{transmutation () []|V,  S,  F (an ornate miniature cannon forged with a drop of your blood that costs 5, 000 gp)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone magically animated cannon|1 round/level|none|no}[Your focus becomes a magical cannon that fires on its own.]
    \DeclareSpellDescription{Arcane Cannon}{Your focus becomes a Medium arcane cannon that appears in an unoccupied square within the spell's range. If no unoccupied square is within range, the spell fails. The cannon comes into existence loaded. Each round thereafter, the cannon can either fire or load. A cannon must be loaded to fire. You do not need to supply ammunition for the cannon.
On your turn, you can spend a move action to direct the cannon to wheel itself to a new location, moving the cannon up to 20 feet. If the arcane cannon ever leaves your line of sight, it winks out of existence, and the spell's duration ends.
The cannon has a range increment of 50 feet. It targets touch attack in the first range increment, and it has no misfire chance.
The cannon acts as a weapon with the conductive special weapon ability (see page 286 of the Advanced Player's Guide), which you can use to channel your spell-like or supernatural abilities as long as you are within the range of arcane cannon. The cannon's attack bonus is equal to your caster level + your Intelligence bonus or your Charisma bonus (for wizards or sorcerers, respectively) with an additional +1 per four caster levels (maximum +5 at 20th level). On a hit, the cannon deals 4d10 damage. The arcane cannon attacks have a critical modifier of x4.
The cannon has AC 10, hardness 10, and 80 hit points. If the cannon is subject to a spell or effect that requires a save, it uses your saving throw modifiers. The cannon never provokes attacks of opportunity. If the cannon is destroyed, so is your focus.}
        
\DeclareSpell{Bestow Weapon Proficiency}{enchantment (compulsion) [mind-affecting]|V,  S,  M (pieces of shaved metal)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 minute/level|Will negates (harmless)|yes (harmless)}[Grants a creature proficiency in a single weapon for short period of time.]
    \DeclareSpellDescription{Bestow Weapon Proficiency}{You bestow the subject with the ability to use a single type of weapon he is not proficient in as if he were proficient with that weapon. The weapon can be of any type, including an exotic weapon, but the subject of the spell must be holding the weapon.}
        
\DeclareSpell{Blistering Invective}{evocation () [fire,  language-dependent]|V,  S|1 standard action|personal|Area30-ft. radius|instantaneous|Reflex partial, see text|special, see below}[Make an Intimidate check against all foes within 30 feet; those demoralized also take fire damage.]
    \DeclareSpellDescription{Blistering Invective}{You unleash an insulting tirade so vicious and spiteful that enemies who hear it are physically scorched by your fury. When you cast this spell, make an Intimidate check to demoralize each enemy within 30 feet of you (see page 99 of the Pathfinder RPG Core Rulebook). Enemies that are demoralized this way take 1d10 points of fire damage and must succeed at a Reflex save or catch fire. Spell resistance can negate the fire damage caused by this spell, but does not protect the creature from the demoralizing effect.}
        
\DeclareSpell{Bowstaff}{transmutation () []|V|1 swift action|personal|Targetsone weapon (bow)|1 round/level (D)|Will negates (harmless, object)|yes (harmless, object)}[A shortbow may double as a club, or a longbow as a quarterstaff.]
    \DeclareSpellDescription{Bowstaff}{The bow that is touched takes on the rigidity and toughness of forged steel, allowing it to be used as a melee weapon. The spell allows a shortbow to be used as a club or a longbow to be used as a quarterstaff, although the bow retains its normal hit points and hardness. The bow's enhancement bonus, if any, applies on melee attack and damage rolls. Additional weapon special weapon qualities also apply to melee attacks if such qualities can be added to a melee weapon.}
        
\DeclareSpell{Brow Gasher}{necromancy () []|V,  S|1 standard action|touch|Areaone slashing melee weapon touched|1 round/level or until discharged|Will negates (harmless, object)|yes (harmless, object)}[Slashing weapon deals bleed damage to an opponent's head.]
    \DeclareSpellDescription{Brow Gasher}{You imbue a slashing melee weapon with the ability to deal a gruesome head wound. When the target weapon hits a living creature, in addition to the normal effects of that hit, the wielder can discharge this spell as a free action to open a gash on the target's forehead that deals bleed damage equal to half your caster level. At the start of each of the target's turns, when it takes bleed damage, it also takes a cumulative -1 penalty on all attack rolls. When that penalty reaches -3, the target also treats all targets as having concealment (20\% miss chance). When the penalty reaches -5, the target is blinded. Stopping the bleed damage ends the effects this spell imposes on the bleeding creature. A target that is immune to bleed damage is also immune to all this spell's effects.}
        
\DeclareSpell{Bullet Shield}{abjuration () []|V,  S,  M (a bullet)|1 standard action|touch|Targetscreature touched|10 minutes/level (D)|Will negates (harmless)|yes (harmless)}[You gain a +4 deflection bonus to AC against firearm attacks.]
    \DeclareSpellDescription{Bullet Shield}{The warded creature gains a +4 deflection bonus to AC against firearm and ranged attacks, with an additional +1 to the bonus for every five caster levels you have (to a maximum of +8 at 20th level). Though the spell is called bullet shield, it also grants this protection from attacks made from firearms with the scatter weapon quality.}
        
\DeclareSpell{Burst of Speed}{transmutation () []|V|1 swift action|personal|Targetsyou|see text||}[You gain increased speed, and your movement ignores attacks of opportunity and allows you to move through the space of creatures larger than you are.]
    \DeclareSpellDescription{Burst of Speed}{Until the end of your turn, you gain a +20-foot bonus to speed (or +10-foot bonus if you are wearing Medium or Heavy armor), your movement does not provoke attacks of opportunity, and you can move through the space of creatures that are larger than you are, but you cannot end your movement this round in a space occupied by a creature.}
        
\DeclareSpell{Caging Bomb Admixture}{evocation () [force]|V,  S|1 standard action|personal|Targetsyou|1 round/level||}[Your bombs create a cage of force that traps creatures inside the bomb's splash radius.]
    \DeclareSpellDescription{Caging Bomb Admixture}{Upon drinking an extract created with this formulae, you make a significant change to your magical reserve that modifies the nature of all bombs you create and throw during this extract's duration. This effect on your magical reserve has no effect on any discoveries that you use to modify your bombs, but you can only have one admixture effect (formulae with the word "bomb admixture" in its title) active at a time. If you drink another bomb admixture, the effects of the former bomb admixture end and the new one becomes active.
When you throw a bomb and hit a direct target, it creates an invisible cubical prison composed of a solid wall of force.
The prison is as large as the splash area of the bomb that you threw, and traps any creature that is entirely inside the area.
Creatures within the area are caught and contained unless any creature within the splash radius is too big to fit inside, in which case the effect automatically fails. Teleportation and other forms of astral travel provide means for escape, but the force walls extend into the Ethereal Plane, blocking ethereal travel.
Like a wall of force, the cage created by the caging bomb admixture resists dispel magic, although a mage's disjunction still functions. The walls of the cage can be damaged by spells as normal, except for disintegrate, which automatically destroys the cage. The walls of this cage can be damaged by weapons and supernatural abilities, but the cage has a hardness of 20 and a number of hit points equal to 20 per alchemist level.
Contact with a sphere of annihilation or a rod of cancellation instantly destroys this cage.
When using caging bomb admixture, an alchemist can only have one cage in effect at a time. If the alchemist throws another bomb during the duration of caging bomb admixture, any other cage created by the earlier admixture ends, and a new one is created. When the duration of the caging bomb admixture ends, so does any remaining cage created by this admixture's effect.}
        
\DeclareSpell{Certain Grip}{transmutation () []|V,  S,  M/DF (a tiny ball of tar)|1 standard action|touch|Targetscreature touched|10 minutes/level (D)|Will negates (harmless)|yes (harmless)}[You gain a +4 competence bonus on Acrobatics and Climb checks and to CMD.]
    \DeclareSpellDescription{Certain Grip}{The subject's grip and footing become sure, granting a +4 competence bonus on Climb checks, on Acrobatics checks to balance, and to CMD against bull rush, drag, reposition, and trip attempts. While affected by this spell, the target is also immune to the disarm combat maneuver.}
        
\DeclareSpell{Chain of Perdition}{evocation () [force]|V,  S,  M/DF (chain link)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effect10-ft. chain|1 round/level (D)|none|yes}[Creates a floating chain of force.]
    \DeclareSpellDescription{Chain of Perdition}{A floating chain of force with hooks at each end appears within an unoccupied space of your choosing within range. This chain is a Medium object that has a 10-foot reach. Physical attacks cannot hit or harm the chain of perdition, but dispel magic, disintegrate, a sphere of annihilation, or a rod of cancellation affects it normally. The chain's AC against touch attacks is 10 + your Charisma modifier (sorcerer), Intelligence modifier (wizard), or Wisdom modifier (cleric).
The chain can perform the dirty trick (blind or entangle), drag, reposition, and trip combat maneuvers, using your caster level in place of your Combat Maneuver Bonus, and your Charisma modifier (sorcerer), Intelligence modifier (wizard), or Wisdom modifier (cleric) in place of your Strength or Dexterity modifier. The chain does not provoke attacks of opportunity for making combat maneuvers. It suffers no penalty or miss chance due to darkness, invisibility, or other forms of concealment.
As a move action, you can move the chain up to 30 feet. If the chain goes beyond the spell's range or out of your sight, it returns to you.
If a creature that the chain attacks has spell resistance, you must make a caster level check (1d20 + caster level) against that spell resistance the first time the chain performs a successful maneuver against that creature. If the chain is successfully resisted, the spell is dispelled. If not, the weapon has its normal full effect on that creature for the duration of the spell.}
        
\DeclareSpell{Companion Mind Link}{enchantment (charm) [mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsyour animal companion|1 minute/level||}[You can talk with your animal companion, and can handle it with supernatural ease.]
    \DeclareSpellDescription{Companion Mind Link}{The link between you and your animal companion becomes stronger. As long as you are within line of sight of your animal companion, you can telepathically communicate with it as if you two shared a language. Also, as long as you are within line of sight of the animal companion, you can push your animal companion a swift action instead of a move action, and you do not need to succeed at Handle Animal checks to handle your animal companion. Such checks automatically succeed.}
        
\DeclareSpell{Compel Hostility}{enchantment (compulsion) [mind-affecting]|V,  S,  M (a drop of your blood)|1 standard action|personal|Targetsyou|1 round/level|see text|see text}[Compels opponents to attack you instead of your allies.]
    \DeclareSpellDescription{Compel Hostility}{Whenever a creature you can see that threatens you makes an attack against one of your allies, as an immediate action, you can compel that creature to attack you instead. When you compel a creature to attack you, you must first overcome that creature's spell resistance, and the creature can attempt a Will saving throw to ignore the compulsion.
A summoner casting this spell can choose his eidolon as the target of the spell.}
        
\DeclareSpell{Damp Powder}{transmutation () []|V,  S,  M/DF (a damp piece of cotton)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets1 loaded firearm|instantaneous|Will negates (object)|yes (object)}[Ruins ammunition loaded in the targeted firearm.]
    \DeclareSpellDescription{Damp Powder}{This spell causes ammunition already loaded into the target firearm is ruined with moisture. Any attempt to fire that ammunition fails, with no chance for misfire, and the user must then take a full-round action to clear the weapon before reloading and firing it. If aware of this spell's effect prior to firing the altered ammunition (a DC 16 Spellcraft check to identify the spell being cast or similar effect), the firearm's user can spend a standard action to clear the altered ammunition from the firearm. Doing so destroys that ammunition.}
        
\DeclareSpell{Darkvision, Communal}{transmutation () []|V,  S,  M (either a pinch of dried carrot or an agate)|1 standard action|touch|Targetscreatures touched|1 hour/level|Will negates (harmless)|yes (harmless)}[As darkvision, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Darkvision, Communal}{This spell functions like darkvision, except you may divide the duration in 1-hour intervals among the creatures touched.}
        
\DeclareSpell{Daybreak Arrow}{evocation () [light]|V,  S|1 standard action|touch|Targetsup to 50 pieces of ammunition, all of which must be together at the time of casting|10 minutes/level|Fortitude negates (harmless, object)|yes (harmless, object)}[Targeted ammunition exudes radiant energy.]
    \DeclareSpellDescription{Daybreak Arrow}{You cause ammunition, including shuriken, to exude radiant energy. Creatures that take penalties in bright light take these penalties for 1 round after being struck by such ammunition. Undead and creatures harmed by sunlight take an additional 1d6 points of damage from such projectiles. This extra damage and half of any other damage you deal with an affected projectile results directly from radiant energy and is not subject to damage resistance. Such a projectile sheds light as if it were a sunrod for 1 round after it is fired or thrown.}
        
\DeclareSpell{Deadly Juggernaut}{necromancy () [death]|V,  S|1 standard action|personal|Targetsyou|1 minute/level||}[Your might increases with every kill you make.]
    \DeclareSpellDescription{Deadly Juggernaut}{With every enemy life you take, you become increasingly dangerous and difficult to stop. During the duration of the spell, you gain a cumulative +1 luck bonus on melee attack rolls, melee weapon damage rolls, Strength checks, and Strength-based skill checks as well as DR 2/- each time you reduce a qualifying opponent to 0 or few hit points (maximum +5 bonus and DR 10/-) with a melee attack. A qualifying opponent has a number of Hit Dice equal to or greater than your Hit Dice -4.}
        
\DeclareSpell{Deadeye's Lore}{divination () []|V,  S|1 round|personal|Targetsyou|1 hour/level||}[Gain a +4 bonus on Survival and move full speed while tracking.]
    \DeclareSpellDescription{Deadeye's Lore}{While subject to this spell, you take upon yourself the mantle of the hunter, channeling the insights of the spirits of the wild. You gain a +4 sacred bonus on all Survival checks for the duration of the spell, and you do not have to move at half your speed while traveling through the wilderness or while tracking.}
        
\DeclareSpell{Debilitating Portent}{enchantment (compulsion) [mind-affecting]|V,  S,  DF|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone creature|1 round/level (D) see text|none|yes}[Inflicts an ill fate on a creature, halving its damage when it attacks or casts a spell]
    \DeclareSpellDescription{Debilitating Portent}{The target is surrounded by a glowing green aura of ill fate. Each time the spell's subject makes an attack or casts a spell, it must succeed at a Will saving throw with a DC = 10 + 1/2 caster level + Charisma (in the case of oracles), Intelligence (in the case of witches), or Wisdom (in the case of clerics). If it fails the saving throw, it deals half damage with the attack or spell. You can dismiss this spell as an immediate action when the target confirms a critical hit; doing so negates the critical hit. The attack that you negated still hits, but only deals half damage.}
        
\DeclareSpell{Delay Poison, Communal}{conjuration (healing) []|V,  S,  DF|1 standard action|touch|Targetscreatures touched|1 hour/level|Fortitude negates (harmless)|yes (harmless)}[As delay poison, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Delay Poison, Communal}{This spell functions like delay poison, except you divide the duration in 1-hour intervals among the creatures touched.}
        
\DeclareSpell{Destabilize Powder}{transmutation () []|V,  S,  M (a few drops of liquor)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets1 loaded firearm|instantaneous|Will negates (object)|yes (object)}[Ammunition in the targeted firearm is prone to misfire.]
    \DeclareSpellDescription{Destabilize Powder}{This spell makes the ammunition in the target firearm is prone to misfire. Increase the misfire range by 1 + 1 per five caster levels (maximum +5) for the ammunition currently loaded into that firearm. If aware of this spell's effect prior to firing the altered ammunition (a DC 17 Spellcraft check to identify the spell being cast or similar effect), the firearm's user can spend a standard action to clear the altered ammunition from the firearm. Doing so destroys that ammunition.}
        
\DeclareSpell{Discovery Torch}{evocation () [light]|V,  S|1 round|touch|Targetsobject touched|10 minutes/level|none|no}[Object touched emanates bright light, granting Perception and Sense Motive bonuses.]
    \DeclareSpellDescription{Discovery Torch}{An object you touch emanates a 20-foot radius of bright light. The effect looks like a regular flame but creates no heat and uses no oxygen. Allies within the area of this light gain a +2 enhancement bonus on Perception and Sense Motive checks, as well as on Knowledge checks to identify monsters that are also within the area and their special powers and vulnerabilities.  When an inquisitor casts this spell, the light emanation doubles (40-ft.-radius emanation) while that inquisitor has a judgment active.  Light spells counter and dispel darkness spells of an equal or lower level.}
        
\DeclareSpell{Divine Arrow}{transmutation () [good]|V,  S|1 standard action|touch|Targetsone projectile|1 round/level or until discharged|none|no}[Imbues a projectile with holy energy.]
    \DeclareSpellDescription{Divine Arrow}{You imbue a projectile, such as an arrow or shuriken, with holy energy so that it deals extra damage to undead equal to that dealt by your lay on hands feature. This extra damage is not multiplied on a critical hit. Although this spell does not expend a daily use of your lay on hands class feature, you must have at least one daily use available to cast this spell. If the projectile hits a target or is destroyed before the duration ends, the spell is discharged.}
        
\DeclareSpell{Dust Form}{transmutation (polymorph) []|V,  S,  M (a pinch of dust gathered from a gravestone or sacred shrine)|1 standard action|personal|Targetsyou|1 round/level||}[You become an incorporeal creature of dust for a short period of time.]
    \DeclareSpellDescription{Dust Form}{Upon casting this spell, you keep your relative form, but you and your equipment become composed entirely of dust. While in this dust form, you take no penalties for squeezing, and can move through spaces as if you were a creature three size categories smaller without penalty. You are also considered incorporeal, though any nonmagical attack you make deals half damage (50\%). Magic attacks are unaffected, and you can still use your magic items and other equipment as normal.  If the duration ends in a square that your normal space cannot occupy, you take 3d6 damage and are shunted to the nearest open space that you can normally occupy.}
        
\DeclareSpell{Effortless Armor}{transmutation () []|V,  S|1 standard action|personal|Targetsyou|1 minute/level||}[Armor you wear no longer slows your speed.]
    \DeclareSpellDescription{Effortless Armor}{Armor you wear no longer reduces your speed. You also reduce the armor's armor check penalty by 1 + 1 per five caster levels (maximum 5).}
        
\DeclareSpell{Endure Elements, Communal}{abjuration () []|V,  S|1 standard action|touch|Targetscreatures touched|24 hours|Will negates (harmless)|yes (harmless)}[As endure elements, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Endure Elements, Communal}{This spell functions like endure elements, except you divide the duration in 1-hour increments among the creatures touched.}
        
\DeclareSpell{Energy Siege Shot}{transmutation () [variable]|V,  S,  M (a ball of pitch)|10 minutes|close (25 ft. + 5 ft./2 levels)|Targetsone Large siege engine|10 minute/level|Fortitude negates (harmless, object)|yes (harmless/object)}[A Large siege engine deals energy damage that you designate with other effects depending on the type of energy you choose.]
    \DeclareSpellDescription{Energy Siege Shot}{This spell transforms any ammunition fired by the target ranged siege engine into ammunition made of pure energy. When casting the spell, the caster picks a one of the following energy types: acid, cold, electricity, fire, sonic, or force. The ammunition within the siege weapon now deals that type of energy damage on a hit, though the amount of damage dealt by the ammunition does not change, nor does it change any of the other effects of the ammunition. Unlike other forms of energy damage, this energy damage does full damage to objects. Based on the type of energy the caster chose while casting, the ammunition also gains one of the following effects.  Acid: The ammunition deals half its damage in a splash to all creatures and unattended objects within 15 feet of the target hit by the siege engine. Creatures can halve the splash damage with a Reflex saving throw. The DC of the splash is the same as the DC of the spell.  Cold: The ammunition creates an ice sheen within a 20-foot-radius burst around the target of the siege engine's attack. That sheen lasts 1d6 rounds. Creatures within the ice sheen are entangled. Any creature within the area of the ice sheen at the start of its turn takes 2d6 cold damage.  Electricity: Creatures hit by the siege engine attack or within 15 feet of the attack are staggered for 1 round.  Fire: Creatures and wood objects within 15 feet of the attack may catch on fire (Core Rulebook 444 and page 164 of this book).  Sonic: Creatures hit by the attack or within 20 feet of the attack must succeed at a Fortitude saving throw or be deafened for one hour. The DC of this effect is the same as the spell DC.  Force: No extra effect.}
        
\DeclareSpell{Energy Siege Shot, Greater}{transmutation () [variable]|V,  S,  M (a ball of pitch)|10 minutes|close (25 ft. + 5 ft./2 levels)|Targetsone siege engine of any size|10 minute/level|Fortitude negates (harmless, object)|yes (harmless/object)}[As energy siege shot, but you can affect any size siege engine.]
    \DeclareSpellDescription{Energy Siege Shot, Greater}{This spell functions like energy shot, except it can target siege engines of any size, not just Large siege engines.}
        
\DeclareSpell{Fabricate Bullets}{transmutation () []|V,  S,  M (1 pound of lead or other soft metal worth 2 gp)|1 round|touch|Targets1 pound of soft metal|instantaneous|none|no}[Converts 1 pound of metal into ammunition.]
    \DeclareSpellDescription{Fabricate Bullets}{You convert 1 pound of lead into bullets. When you cast this spell, you decide whether you create normal sling bullets, firearm bullets, or firearm pellets. The spell creates two sling bullets, 30 firearm bullets, or 10 uses of pellets.}
        
\DeclareSpell{Fiery Shuriken}{conjuration (creation) [fire]|V,  S,  M (a pinch of sulfur and a single shuriken worth 2 sp)|1 standard action|close (25 ft. + 5 ft./2 levels)|EffectTwo or more fiery shuriken|1 round/level (D)|none|yes}[Calls forth several fiery projectiles ready to be flung at opponents.]
    \DeclareSpellDescription{Fiery Shuriken}{You call forth two fiery projectiles resembling shuriken, plus one more for every two caster levels beyond 3rd (to a maximum of eight shuriken at 15th level), which hover in front of you. When these shuriken appear, you can launch some or all of them at the same target or different targets. Each shuriken requires a ranged touch attack roll to hit and deals 1d8 points of fire damage. You provoke no attacks of opportunity when launching them.  Any shuriken you do not launch as part of casting this spell remains floating near you for the spell's duration. On rounds subsequent to your casting of this spell, you can spend a swift action to launch one of these remaining shuriken or a standard action to launch any number of these remaining shuriken. If you fail to launch a shuriken before the duration ends, that shuriken disappears and is wasted.}
        
\DeclareSpell{Find Quarry}{divination () []|V,  S,  DF|1 standard action|personal|Targetsyou|instantaneous|none|no}[You can sense whether a particular creature is within 20 miles of your location.]
    \DeclareSpellDescription{Find Quarry}{You sense whether a well-known creature you can clearly visualize is within a 20-mile radius of your current location, as well as the distance and direction to the creature in relation to you. You also discern whether the creature is moving, and its direction, speed, and mode of movement. The radius you can sense increases by 5 miles for every two caster levels you have above 10th (to a maximum of a 45-mile radius at 20th level). Anything that would prevent locate creature from finding a creature also prevents find quarry from doing so.}
        
\DeclareSpell{Flash Fire}{transmutation () []|V,  S,  M (a pinch of powdered fool's gold)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets1 firearm|instantaneous|Will negates (object); see text|yes (object); see text}[Ammunition in the targeted firearm creates a tremendous flash capable of blinding the weapon's bearer and those around him.]
    \DeclareSpellDescription{Flash Fire}{The firearm fires with a blinding flash, even if the firearm is not currently loaded. Every creature within 15 feet of the creature carrying the weapon must succeed at a Fortitude save or be blinded for 1d4 rounds. The creature carrying the firearm takes a -4 penalty on this saving throw. If the firearm is loaded, the ammunition is wasted.}
        
\DeclareSpell{Forest Friend}{abjuration () []|V,  S,  M (a pinch of manure)|1 round|close (25 ft. + 5 ft./2 levels)|Targetsone willing living creature per three levels, no two of which may be more than 30 ft. apart.|1 minute/level|none|no}[Plants in a forested area become helpful instead of hindering you and your allies.]
    \DeclareSpellDescription{Forest Friend}{While subject to this spell, the targets find that forested areas become helpful instead of hindering. The targets suffer no hindrances to movement and suffer no penalties on Acrobatics and Stealth checks from undergrowth in forested terrain. Furthermore, forested overgrowth imposes a miss chance 10\% lower than normal.  When moving in and among trees, those subject to the spell gain a +5 circumstance bonus on Acrobatics checks and Climb checks. Rangers in their favored terrain can also add their favored terrain bonus on such Acrobatics and Climb checks.}
        
\DeclareSpell{Frightful Aspect}{transmutation (polymorph) []|V,  S,  M (the skin of a toad)|1 standard action|personal|Targetsyou|1 minute/level||}[You take on a terrifying, Large-sized form of yourself and emit an aura that causes creatures to become shaken or frightened.]
    \DeclareSpellDescription{Frightful Aspect}{You become a larger, awful version of yourself. You grow to size Large, and take on features that horrify your enemies. You gain the following abilities: a +6 size bonus to Strength, a +4 size bonus to Constitution, a +6 natural armor bonus, DR 10/magic, and spell resistance equal to 10 + half your caster level. You also emit an aura that emanates 30 feet from you. Enemy creatures within the aura are shaken. Each time a creature shaken by this aura hits you with a melee attack, that creature becomes frightened for 1d4 rounds, though at the end of that duration it is no longer affected by this aura. The aura's effect is a fear and mind-affecting effect.}
        
\DeclareSpell{Frost Fall}{evocation () [cold]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Area5-foot radius burst|1 round/2 levels|Fortitude partial|yes}[The area is covered in a chilling frost.]
    \DeclareSpellDescription{Frost Fall}{The area of this spell is covered in chilling frost, dealing 2d6 points of cold damage to all creatures within it. Creatures that the spell initially damages must succeed at a Fortitude save or become staggered for 1 round. The area remains chilled for the spell's duration. Any creature that starts your turn within the spell's area takes 1d6 points of cold damage (Fortitude saving throw for half) but does not become staggered even on a failed saving throw.}
        
\DeclareSpell{Haunted Fey Aspect}{illusion (glamer) []|S|1 standard action|Personal|TargetsYou|1 round/level (D)||}[You surround yourself with disturbing illusions.]
    \DeclareSpellDescription{Haunted Fey Aspect}{You surround yourself with disturbing illusions, making you look and sound like a bizarre, insane fey creature. You gain DR 1/cold iron against a single opponent until the end of the spell, or until you take damage.}
        
\DeclareSpell{Healing Thief}{necromancy () []|V,  S,  M (a bit of sponge,  damp with tears)|1 standard action|touch|Targetscreature touched|1 round/level or until discharged|none|yes}[You siphon half of all magical healing that the targeted creature receives.]
    \DeclareSpellDescription{Healing Thief}{With this spell you can steal the healing of the target creature. You must succeed at a melee touch attack to strike the target. If you do, until the effect ends, whenever your target is subject to a healing spell or a supernatural effect that heals hit points, the target only receives half the healing (rounded down) and you receive the other half (also rounded down). You must remain within 25 feet (plus 5 feet per two caster levels) of the target to gain this benefit. If you move outside that range, the spell is discharged. Once you steal 5 hit points per your caster level (maximum 50 hit points) of healing from this spell's effect, the spell is discharged.}
        
\DeclareSpell{Heroic Invocation}{enchantment (compulsion) [mind-affecting]|V,  S|10 minutes|close (25 ft. + 5 ft./2 levels)|Targetsone or more creatures, no two of which can be more than 30 ft. apart|10 minutes /level|Will negates (harmless)|yes (harmless)}[Grants a number of creatures bonuses on attacks and damage, temporary hit points, and immunity to fear and charm effects.]
    \DeclareSpellDescription{Heroic Invocation}{Using worlds of ancient power, you bestow heroic powers on all creatures subject to this spell. They gain a +4 morale bonus on attack and damage rolls, gain 2d8+4 temporary hit points, and become immune to both fear and charm effects for the spell's duration.  At the end of the spell's duration, the subjects become fatigued.}
        
\DeclareSpell{Hostile Juxtaposition}{conjuration (teleportation) []|V,  S,  M (a coin)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature of your size or smaller|1 round/level or until discharged|Will negates|yes}[You create a dimensional link with a targeted creature, and switch spots with it.]
    \DeclareSpellDescription{Hostile Juxtaposition}{You create a dimensional link to the target creature. When attacked or the subject of a spell that deals damage to you, you can spend an immediate action to cause yourself and the target creature to teleport and switch places. The target then becomes the target of the triggering attack or spell instead of you. If you fail to teleport out of the area of an effect, that effect might still affect you. If the target creature cannot fit safely into the new space without squeezing, or you try to teleport the target into an occupied space or a space it could not normally stand within, the juxtaposition fails. Further, if the target is unconscious or dead when you attempt to switch places, the juxtaposition fails. Once you have used it to teleport once, this spell is discharged.}
        
\DeclareSpell{Hostile Juxtaposition, Greater}{conjuration (teleportation) []|V,  S,  M (a coin)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature/4 levels|1 round/level or until discharged|Will negates|yes}[You may target one creature for every four of your caster levels.]
    \DeclareSpellDescription{Hostile Juxtaposition, Greater}{This spell functions like hostile juxtaposition, except you can target one creature for every four caster levels you have or you can target a single creature that is larger than you are. You can switch places with each target only once while the effect lasts. Once you have used it to teleport and switch places with each affected target, the spell is discharged.}
        
\DeclareSpell{Hostile Levitation}{transmutation () []|V,  S,  M (a leather loop studded with lodestones)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round/level|Will negates|yes}[Levitates the targeted creature up off the ground.]
    \DeclareSpellDescription{Hostile Levitation}{You levitate the target a few inches off the ground, removing solid footing and halving the target's speed. The target also takes a -4 penalty to CMD against bull rush, drag, and reposition attempts. A targeted creature that attacks with a melee or ranged weapon finds itself increasingly unstable; the first attack has a -1 penalty on attack rolls, the second -2, and so on, to a maximum penalty of -5. A full-round action spent stabilizing allows the creature to begin again at -1.  This spell fails if cast on a flying creature.}
        
\DeclareSpell{Illusion of Calm}{illusion (figment) []|V,  S|1 standard action|personal|Targetsyou|1 minute/level|Will disbelieve (on hit; see below)|no}[You appear to be standing still, even when you take some actions.]
    \DeclareSpellDescription{Illusion of Calm}{When casting this spell, you create an illusory double that takes the same space of you. That double makes it look like you are standing still, even when you are not. While under the effects of this spell, you do not provoke attacks of opportunity when you cast a spell, make a ranged attack with a thrown weapon, or move out of your first square during a move action. It does not hide ranged attacks made with any type of projectile weapon.  When a creature hits you with an attack of any type, it gains a saving throw to disbelieve the figment. On a successful saving throw, it successfully disbelieves and the spell's effect ends for that creature.}
        
\DeclareSpell{Instrument of Agony}{transmutation () []|V,  S|1 standard action|touch|Targetsweapon touched|1 minutes/level|Will negates (harmless, object), see text|yes (harmless, object), see text}[Weapon exudes divine fury, granting a bonus on Intimidate checks.]
    \DeclareSpellDescription{Instrument of Agony}{You cause a weapon to exude a palpable aura of divine fury. While wielding this weapon, a creature gains a +2 morale bonus on Intimidate checks. When an attack made using the targeted weapon hits, the wielder can spend a free action to discharge the effect to inflict agony on the creature the weapon hit. If that creature has spell resistance, it applies against this effect. If the creature fails a Will save, it is nauseated for 1d4+1 rounds. If it succeeds at the saving throw, the creature is instead sickened for 1 round. The sickened condition created by the instrument is a mind-affecting effect.}
        
\DeclareSpell{Jolting Portent}{evocation () [electricity]|V,  S,  DF|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone creature|1 round/level (D) see text|none|yes}[You inflict a vengeful fate on a creature, dealing electricity damage each time it attacks or casts a spell.]
    \DeclareSpellDescription{Jolting Portent}{The creature you designate is surrounded by a glowing red aura of vengeful fate. Once per round when the target makes an attack or casts a spell, it must succeed at a Fortitude saving throw with a DC = 10 + 1/2 caster level + Charisma (in the case of oracles) or Wisdom (in the case of clerics). If the target fails the saving throw, it takes 4d6 + your Charisma modifier (in the case of oracles) or Wisdom modifier (in the case of clerics) electricity damage. It takes no damage on a successful saving throw. You can dismiss this spell as an immediate action when its subject confirms a critical hit to negate the critical hit and daze the creature for 1 round. The attack still hits its target and deals normal damage. The effects of the daze occur after the attack.}
        
\DeclareSpell{Judgment Light}{evocation () [light]|V,  S|1 standard action|personal|Area30-ft.-radius burst|instantaneous, see text|see text|yes}[You gain an additional effect while a judgment is active.]
    \DeclareSpellDescription{Judgment Light}{An inquisitor may only cast this spell while she has a judgment active. When she does cast this spell, it causes one or more of the following effects based on the inquisitor's active judgments.  Destruction: Red light erupts from the caster. Enemies in the area take 4d8 points of damage and become shaken for 1d4 rounds. A successful Will saving throw halves the damage and negates the shaken effect.  Healing: Green light erupts from the caster. Allies in the area regain a number of hit points equal to 1d8 + the caster's Wisdom modifier.  Justice: Blue light erupts from the caster, revealing hidden and invisible creatures to all. The light outlines such creatures for 1 round per caster level, imposing a -20 penalty on Stealth checks on those creatures.  Piercing: Violet light erupts from the caster, reducing the spell resistance of enemies within the burst by 5 for 1 round per caster level.  Protection: Amber light erupts from the caster, granting allies in the burst a +2 sacred bonus to AC and CMD, and a +4 bonus to AC against critical confirmation attack rolls for 1 round per caster level.  Purity: White light erupts from the caster, allowing each ally within the burst to attempt a saving throw against a single effect that allows a saving throw with a +2 sacred bonus on the roll.  Resiliency: Golden light erupts from the caster, granting allies within the burst DR 3/magic or the alignment your judgment allows for 1 round per caster level.  Resistance: Copper light erupts from the caster, granting allies within the burst resistance 5 against the energy the judgment protects the inquisitor against when she casts this spell for 1 round per caster level.  Smiting: Silver light erupts from the caster, making allies' weapons within the burst count as magic, the alignment her weapon is, and adamantine for purposes of overcoming damage reduction for 1 round per caster level.}
        
\DeclareSpell{Jury-Rig}{transmutation () []|V,  S,  M (a pinch of tree resin)|1 standard action|touch|Targetsone broken object of up to 2 lbs./level|1 round/level|Will negates (harmless, object)|yes (harmless, object)}[Removes the broken condition from the targeted object.]
    \DeclareSpellDescription{Jury-Rig}{When you cast this spell, a spectral force binds a broken weapon together, relieving the broken condition for a short time. While under the effects of this spell, an item with the broken condition suffers no adverse effects from that condition, and is treated as if it is not broken. The object regains no hit points, and damage can still destroy the object.}
        
\DeclareSpell{Kinetic Reverberation}{transmutation () []|V,  S,  M (rubber tree sap)|1 standard action|touch|Targetscreature touched|1 round/level|Fortitude negates (object)|yes (object)}[Channels the force of an enemy's attack back into its weapon.]
    \DeclareSpellDescription{Kinetic Reverberation}{This spell converts the momentum and force from melee attacks made against the target of the spell, reflecting them back upon the attacker's weapon. After making a successful melee attack against the target, an attacker must make a Fortitude saving throw for the weapon used. If the weapon fails the save, it takes damage equal to the damage rolled against the target. Creatures using natural attacks or unarmed strikes are unaffected by this spell.}
        
\DeclareSpell{Languid Bomb Admixture}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|personal|Targetsyou|1 round/level|Will negates (special, see below)|yes}[Empowers bombs you throw to cause fatigue in those directly hit or splashed by the bomb.]
    \DeclareSpellDescription{Languid Bomb Admixture}{Upon drinking an extract created with this formula, you make a significant change to your magical reserve that modifies the nature of all bombs you create and throw during this extract's duration. This effect on your magical reserve has no effect on any discoveries that you use to modify your bombs, but you can only have one admixture effect (formulae with the words "bomb admixture" in their titles) active at a time. If you drink another bomb admixture, the effects of the former bomb admixture end and the those of the new one become active.  When you throw a bomb and hit a direct target, it affects up to four creatures-the creature the bomb hit directly, and up to three other creatures damaged by the splash (alchemist's choice). Those creatures must succeed at a Will saving throw or become fatigued.}
        
\DeclareSpell{Liberating Command}{transmutation () []|V|1 immediate action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|instantaneous|Will negates (harmless)|yes (harmless)}[Target makes an Escape Artist check as an immediate action and gains a bonus on it.]
    \DeclareSpellDescription{Liberating Command}{If the target is bound, grappled, or otherwise restrained, he may make an Escape Artist check to escape as an immediate action. He gains a competence bonus on this check equal to twice your caster level (maximum +20). This spell has no effect if the target could not get free by using the Escape Artist skill (for example, if he were under the effects of a hold person spell or paralyzed by Strength damage).}
        
\DeclareSpell{Life Conduit}{conjuration (healing) []|V,  S|1 standard action|personal|Targetsyou|1 round/level||}[You are bound even tighter to your eidolon than normal, and may share hit points with it through your life link ability.]
    \DeclareSpellDescription{Life Conduit}{You utilize life conduit to share hit points with your eidolon. While this spell is active, you can spend a swift action to transfer 1d6 hit points between you and your eidolon, either taking damage yourself and healing your eidolon or healing yourself and damaging your eidolon. If your eidolon moves farther than 50 feet from you, this spell ends.}
        
\DeclareSpell{Life Conduit, Greater}{conjuration (healing) []|V,  S|1 standard action|personal|Targetsyou|1 round/level||}[You transfer 3d6 hit points to your eidolon as a swift action.]
    \DeclareSpellDescription{Life Conduit, Greater}{This spell functions like life conduit, except you can transfer 3d6 hit points as a swift action.}
        
\DeclareSpell{Life Conduit, Improved}{conjuration (healing) []|V,  S|1 standard action|personal|Targetsyou|1 round/level||}[Transfers 2d6 hit points to your eidolon as a swift action.]
    \DeclareSpellDescription{Life Conduit, Improved}{This spell functions like life conduit, except you can transfer 2d6 hit points as a swift action.}
        
\DeclareSpell{Lightning Lash Bomb Admixture}{evocation () [electricity]|V,  S|1 standard action|personal|Targetsyou|1 round/level|special, see below|special, see below}[Empowers bombs you throw with a ward that deals lightning damage each time those damaged by the bomb move more than 5 feet.]
    \DeclareSpellDescription{Lightning Lash Bomb Admixture}{Upon drinking an extract created with this formula, you make a significant change to your magical reserve that modifies the nature of all bombs you create and throw during this extract's duration. This effect on your magical reserve has no effect on any discoveries that you use to modify your bombs, but you can only have one admixture effect (formulae with the word "bomb admixture" in its title) active at a time. If you drink another bomb admixture, the effects of the former bomb admixture end and those of the new one become active.  When you throw a bomb and hit a direct target, lashes of electrical energy are released from the bomb, coalescing on the bomb's direct target and up to three creatures that take damage from the bomb's splash (alchemist's choice). Those affected by the electricity must succeed at a Reflex saving throw or take 1d6 points of electrical damage each time they take a move action to move more than 5 feet for the duration of the effect. This effect does not ignore spell resistance.}
        
\DeclareSpell{Litany of Defense}{transmutation () []|V,  S,  DF|1 swift action|personal|Targetsyou|1 round|no|yes}[Doubles armor's enhancement bonus.]
    \DeclareSpellDescription{Litany of Defense}{Invoking this litany strengthens your defenses. Any enhancement bonus your armor has is doubled and you are immune to fear.  While subject to this spell, the target cannot be the target of another spell that has the word "litany" in the title.}
        
\DeclareSpell{Litany Of Eloquence}{enchantment (charm) [language-dependent,  mind-affecting]|V,  S,  DF|1 swift action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round|no|yes}[Fascinates a single creature for 1 round.]
    \DeclareSpellDescription{Litany Of Eloquence}{Your litany is a fascinating diatribe of grace, causing your target to do nothing but listen. The target is fascinated. As usual, obvious danger prevents fascination and potential danger grants a save.  While subject to this spell, the target cannot be the target of another spell that has the word "litany" in the title.}
        
\DeclareSpell{Litany of Entanglement}{conjuration (calling) [language-dependent]|V,  S,  DF|1 swift action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round|Will negates|yes}[Entangles a creature for 1 round.]
    \DeclareSpellDescription{Litany of Entanglement}{Your litany conjures chains of energy that lash upward from the ground and hamper the target's movement. The target is entangled. This spell has no effect on flying creatures, or creatures not standing upon solid ground.  While subject to this spell, the target cannot be the target of another spell that has the word "litany" in the title.}
        
\DeclareSpell{Litany Of Escape}{conjuration (teleportation) [language-dependent]|V,  S,  DF|1 swift action|close (25 ft. + 5 ft./2 levels)|Targetsone willing creature that is grappled|instantaneous|no|yes}[Teleports a friend out of a grapple.]
    \DeclareSpellDescription{Litany Of Escape}{With a powerful prayer, you call upon the servants of your god to whisk a friend out of a grapple. The target loses the grappled and pinned conditions and is teleported 10 feet. If there is no available space for the target to teleport to, the spell fails.}
        
\DeclareSpell{Litany Of Madness}{enchantment (charm) [language-dependent,  mind-affecting]|V,  S,  DF|1 swift action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 or more rounds (see below)|no, see below|yes}[A single target is confused for at least 1 round.]
    \DeclareSpellDescription{Litany Of Madness}{This litany is a sermon of madness. The target is confused. At the start of each of its turns, it can make a Will saving throw against the confused effect (DC of the spell). If the target fails the save, it continues to be confused. If it makes the save, the effect ends.  While subject to this spell, the target cannot be the target of another spell that has the word "litany" in the title.}
        
\DeclareSpell{Litany Of Righteousness}{evocation () [good,  language-dependent]|V,  S,  DF|1 swift action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round|Will negates|yes}[A single evil creature takes more damage from creatures with a good aura.]
    \DeclareSpellDescription{Litany Of Righteousness}{Calling down a litany of anathema, you make an evil more susceptible to the attacks of good creatures. If the target is evil, it takes double damage from attacks made by creatures with a good aura (from a class feature or as a creature with the good subtype). If the target also has the evil subtype; when it is hit with attacks made by creatures with a good aura, it is also dazzled for 1d4 rounds. If this spell targets a nonevil creature (or one that lacks the evil subtype), it has no effect, and the spell is wasted.  While subject to this spell, the target cannot be the target of another spell that has the word "litany" in the title.}
        
\DeclareSpell{Litany of Sight}{divination () []|V,  S,  DF|1 swift action|personal|Targetsyou|1 round|no|yes}[You can see invisible creatures and objects within 30 feet of you.]
    \DeclareSpellDescription{Litany of Sight}{This litany reveals the unseen to you. You can see invisible creatures and objects within 30 feet.  While subject to this spell, the target cannot be the target of another spell that has the word "litany" in the title.}
        
\DeclareSpell{Litany of Sloth}{enchantment (compulsion) [language-dependent,  mind-affecting]|V,  S,  DF|1 swift action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round|no|yes}[Single target cannot make attacks of opportunity for 1 round.]
    \DeclareSpellDescription{Litany of Sloth}{With a litany against the wages of sloth, you slow the target's defenses. The target cannot make attacks of opportunity or cast spells defensively.  While subject to this spell, the target cannot be the target of another spell that has the word "litany" in the title.}
        
\DeclareSpell{Litany of Thunder}{evocation () [language-dependent,  sonic]|V,  S,  DF|1 swift action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round|Fortitude negates|yes}[A single target is deafened until the condition is removed, and is confused for 1 round.]
    \DeclareSpellDescription{Litany of Thunder}{You call down a thunderous boom upon your enemy. The target becomes deafened until the condition is removed, and is confused for 1 round.  While subject to this spell, the target cannot be the target of another spell that has the word "litany" in the title.}
        
\DeclareSpell{Litany Of Vengeance}{transmutation () [language-dependent]|V,  S,  DF|1 swift action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round|no|yes}[Allies attacking the target of the spell gain a +5 bonus on damage rolls for 1 round.]
    \DeclareSpellDescription{Litany Of Vengeance}{This litany causes your enemy to feel the pain of blows more sharply. Anyone who hits the target with an attack gains a +5 sacred or profane bonus (depending on the alignment of the caster) to that attack's damage.  While subject to this spell, the target cannot be the target of another spell that has the word "litany" in the title.}
        
\DeclareSpell{Litany of Warding}{transmutation () []|V,  S,  DF|1 swift action|personal|Targetsyou|1 round||}[You gain two additional attacks of opportunity for 1 round.]
    \DeclareSpellDescription{Litany of Warding}{With this litany, you become more aware of your opponents. You can make two additional attacks of opportunity this round. Furthermore, you gain a +2 sacred bonus to AC against attacks of opportunity.  While subject to this spell, the target cannot be the target of another spell that has the word "litany" in the title.}
        
\DeclareSpell{Litany of Weakness}{necromancy () [language-dependent]|V,  S,  DF|1 swift action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round|no|yes}[Single target is fatigued for 1 round.]
    \DeclareSpellDescription{Litany of Weakness}{Your litany proclaims your target weak, sapping its strength. The target is fatigued for 1 round.  While subject to this spell, the target cannot be the target of another spell that has the word "litany" in the title.}
        
\DeclareSpell{Locate Weakness}{divination () []|V,  S,  M/DF (a pickled predator's eye)|1 standard action|personal|Targetsyou|1 minute/level||}[You roll damage twice when you roll damage for a critical hit and take the best damage.]
    \DeclareSpellDescription{Locate Weakness}{You can sense your foes' weak points, granting you greater damage with critical hits. Whenever you score a critical hit, roll the attack's damage dice (but not extra or precision damage dice) twice and take the highest result.}
        
\DeclareSpell{Lock Gaze}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round/level|Will negates|yes}[Compels the target to look only at you for the duration of the spell.]
    \DeclareSpellDescription{Lock Gaze}{You compel the target to look at you and only you for the spell's duration or until the spell is discharged. While staring at you, the target is considered to be averting its eyes from every creature but you, granting creatures other than you concealment against the target's attacks. If the target willingly leaves your line of sight, it is blinded for 1 round and the spell ends. If you willingly leave the target's line of sight or become unconscious or dead, the spell creature suffers no ill effects. Blind creatures and creatures immune to gaze attacks are immune to this spell.}
        
\DeclareSpell{Longshot}{transmutation () []|V,  S,  M/DF (a piece of fletching)|1 standard action|personal|Targetsyou|1 minute/level||}[Grants a +10 foot bonus to the range increment for any ranged weapon fired.]
    \DeclareSpellDescription{Longshot}{This spell reduces the effect of range, granting a +10-foot bonus to the range increment of any weapon used by the subject.}
        
\DeclareSpell{Magic Siege Engine}{transmutation () []|V,  S,  DF|1 standard action|touch|Targetsone siege engine touched|1 minutes/level|Will negates (harmless, object)|yes (harmless, object)}[Siege engine gains +1 on targeting and damage rolls.]
    \DeclareSpellDescription{Magic Siege Engine}{This spell permits an indirect fire siege engine to bombard its targets with greater accuracy, delivering more damage. The siege weapon receives a +1 enhancement bonus on targeting rolls and damage rolls. If used on a direct fire siege weapon, this spell acts a magic weapon.}
        
\DeclareSpell{Magic Siege Engine, Greater}{transmutation () []|V,  S,  M/DF (black powder)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone siege engine touched|1 hour/level|Will negates (harmless, object)|yes (harmless, object)}[Siege engine gains +1 on targeting and damage rolls for every four caster levels.]
    \DeclareSpellDescription{Magic Siege Engine, Greater}{This spell functions like magic siege weapon, except it gives an indirect fire siege weapon an enhancement bonus on targeting and damage rolls of +1 per four caster levels (maximum +5). If used on a direct-fire siege weapon, this spell functions as greater magic weapon.}
        
\DeclareSpell{Mask Dweomer, Communal}{illusion (glamer) []|V,  S,  M (a piece of gauze)|1 standard action|touch|Targetscreatures or objects touched|1 day/level (D)|none; see text|no}[As mask dweomer, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Mask Dweomer, Communal}{This spell functions like mask dweomer (Advanced Player's Guide 232), except you divide the duration in 1-day increments among the creatures or objects touched.}
        
\DeclareSpell{Mind Blank, Communal}{abjuration () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|24 hours|Will negates (harmless)|yes (harmless)}[As mind blank, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Mind Blank, Communal}{This spell functions like mind blank, except you divide the duration in 1-hour increments among the creatures touched.}
        
\DeclareSpell{Mirror Strike}{transmutation () []|V,  S,  M (a shard of mirror)|1 standard action|personal|Targetsyou|see text||}[You may strike multiple opponents with a single attack.]
    \DeclareSpellDescription{Mirror Strike}{You briefly alter the flow of time to split a melee attack into two attacks. Before the end of your next turn, when you make your next melee attack roll, compare the result to the AC of two opponents within your reach. If the selected opponents are flanking you, you gain a +2 bonus on your attack roll (and confirmation attack roll, see below). If you hit both enemies, you can deal half damage to each. Hitting only one opponent allows you to deal that opponent normal damage for your attack. On a critical threat, you can make only one attack roll to confirm the critical hit against both opponents. If you confirm against both, you deal half your critical hit damage to each. Your hit is a normal hit rather than a critical if you confirm against only one opponent. If you fail to use the effect before the end of your next turn, the spell ends.}
        
\DeclareSpell{Moment of Greatness}{enchantment (compulsion) [mind-affecting]|V,  S,  M/DF (rabbit fur)|1 standard action|50 ft.|TargetsThe caster and allies within a 50-ft. burst centered on the caster|1 minute/level or until discharged|none|yes (harmless)}[Doubles a morale bonus.]
    \DeclareSpellDescription{Moment of Greatness}{Each creature affected by this spell is given the potential for greater success and glory. If the affected creature is benefiting from a morale bonus of any type, it can double that morale bonus on one roll or check, before making the roll. Once an affected creature uses this spell's effect, the spell is discharged for that subject.}
        
\DeclareSpell{Mount, Communal}{conjuration (summoning) []|V,  S,  M (a bit of horse hair)|1 round|close (25 ft. + 5 ft./2 levels)|Effectup to six mounts|2 hours/level (D)|none|no}[As mount, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Mount, Communal}{This spell functions like mount, except you can summon up to six light horses or ponies, and you divide the duration in 2-hour increments among the steeds summoned.}
        
\DeclareSpell{Mutagenic Touch}{transmutation () []|V,  S,  M (a whole fingernail)|1 standard action|touch|Targetscreature touched|special (see below)|Fortitude negates (harmless)|yes (harmless)}[You can pass a weaker version of your mutagen to another creature.]
    \DeclareSpellDescription{Mutagenic Touch}{When you are under of the effects of your  mutagen, you can cast this spell to safely pass it to another creature with a touch. You must make a successful touch attack against the target. On a hit, the effect of the mutagen passes to the target touched, though in a lesser form. The mutagen's effect ends for you, and passes on to the creature touched, but the target only gets half of the alchemical bonus to the physical ability modifier you chose when took the mutagen, and twice the penalty to the corresponding mental ability score. If the target's mental ability score drops below 3, the target is also confused for the remaining duration of the mutagen. The mutagen continues until the duration has ended. It can be ended earlier if the target drinks or is fed the contents of a vial of antitoxin, but with only 50\% chance of success.  You can use this spell on a mutagen with either the greater mutagen or advance mutagen discoveries. When you do, you always pass on half the alchemical bonus to physical abilities and twice the penalty to the mental ability score.}
        
\DeclareSpell{Named Bullet}{divination () []|V,  S,  M/DF (an item from the selected creature or creature type)|1 standard action|touch|Targetsone piece of ammunition or one thrown weapon|10 minutes/level or until discharged|Will negates (harmless, object)|yes (harmless, object)}[Imbues ammunition with accuracy against a specific creature type.]
    \DeclareSpellDescription{Named Bullet}{You imbue the target with deadly accuracy against a selected creature type (and subtype for humanoids or outsiders) or a specific creature you know and can name. When used against the selected creature, the ammunition never misfires and is unaffected by concealment (but not total concealment), and at a range of 30 feet or less, the attack targets the selected creature's touch AC. When the target hits the selected creature, you must overcome that creature's spell resistance, or this spell has no effect. A normal hit scored using the target against the selected creature is considered to be a critical threat and deals 1 extra point of damage per caster level (maximum 20), which is not multiplied on a critical hit. A natural critical hit deals the same extra damage, but that damage is multiplied due to the critical.  Once the target is used to attack the selected creature, successfully or not, this spell is discharged.}
        
\DeclareSpell{Named Bullet, Greater}{divination () []|V,  S,  M/DF (an item from the selected creature or creature type)|1 standard action|touch|Targetsone piece of ammunition or one thrown weapon|10 minutes/level or until discharged|Will negates (harmless, object)|yes (harmless, object)}[As named bullet, but deals 2 points of damage for every caster level.]
    \DeclareSpellDescription{Named Bullet, Greater}{This spell functions like named bullet, except it deals 2 extra points of damage per caster level (maximum 40).}
        
\DeclareSpell{Negative Reaction}{illusion (glamer) []|S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round/level|Will negates|yes}[Targeted creature may not positively influence anyone.]
    \DeclareSpellDescription{Negative Reaction}{The target's actions and words fail to impress. The target of this spell takes a -10 penalty on any Bluff, Diplomacy, and Intimidate checks as well as any performance combat checks it attempts.}
        
\DeclareSpell{Nondetection, Communal}{abjuration () []|V,  S,  M (diamond dust worth 25 gp per target)|1 standard action|touch|Targetscreatures or objects touched|1 hour/level|Will negates (harmless, object)|yes (harmless, object)}[As nondetection, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Nondetection, Communal}{This spell functions like nondetection, except you divide the duration in 1-hour increments among the creatures or objects touched.}
        
\DeclareSpell{Obsidian Flow}{transmutation () [earth,  fire]|V,  S,  M/DF (a small piece of obsidian)|1 standard action|close (25 ft. + 5 ft./2 levels)|Area20-ft.-radius burst|instantaneous|Reflex partial, see text|no}[Converts the surface of the ground into molten glass.]
    \DeclareSpellDescription{Obsidian Flow}{You convert a thin layer of the ground to molten glass that cools quickly. Creatures in the area take 1d6 points of fire damage per two caster levels (maximum of 10d6) and become entangled. Any creature within the area that makes a successful Reflex save takes half damage and is not entangled. An entangled creature can attempt to free itself by spending a move action to attempt a Strength check or Escape Artist check (the DC equals the spell's saving throw DC).  The ground is covered with slippery expanses and sharp shards of obsidian. The area of effect is difficult terrain, and the DC of Acrobatics checks within the area of effect increases by 5. A successful DC 15 Acrobatics check is required to run or charge across the area. A creature that falls prone in the area takes 1d6 points of damage from sharp obsidian.}
        
\DeclareSpell{Peacebond}{abjuration () []|S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone sheathed or slung weapon|1 minute/level|Will negates (object)|yes (object)}[Locks a weapon in place on the target's body.]
    \DeclareSpellDescription{Peacebond}{You lock a weapon in place on its owner's body, or within the weapon's sheath or holster. Anyone who then tries to draw the weapon must spend a standard action and succeed at a Strength check (DC equal to the saving throw DC) to do so, provoking attacks of opportunity whether the attempt succeeds or fails.}
        
\DeclareSpell{Pellet Blast}{conjuration (creation) []|V,  S,  M (a handful of metal pellets or handful of cold iron,  silver,  or adamantine pellets; see descriptions for cost)|1 standard action|30 ft.|Areacone-shaped burst|instantaneous|Reflex half|no}[Creates an explosion of conjured metal pellets.]
    \DeclareSpellDescription{Pellet Blast}{This spell creates an explosion of conjured metal pellets, striking everything within its area and dealing 1d8 points of piercing damage per two caster levels, maximum 5d8. This damage is subject to damage reduction. If the material component is made of cold iron (costing 50 gp), silver (costing 20 gp), or adamantine (costing 100 gp), the resulting blast can overcome damage reduction of the appropriate type. The pellets disappear after the spell is cast and the damage is dealt.}
        
\DeclareSpell{Phantom Chariot}{conjuration (creation) []|V,  S|10 minutes|0 ft.|Effectone quasi-real chariot and draft team|1 hour/level (D)|none|no}[Conjures a quasi-real heavy chariot pulled by four horses.]
    \DeclareSpellDescription{Phantom Chariot}{You conjure a quasi-real heavy chariot with four horselike creatures in a team to pull it. (The exact description can be customized as you wish.) The chariot has all the normal qualities of a heavy chariot (see page 182). You or a person you designate while casting the spell must drive the chariot, which can carry up to six passengers (including the driver). The team and chariot make no sound and the team does not fight, although the driver can use the chariot like any normal chariot.  The chariot and team are essentially a single entity with an AC of 19 (-2 size, +6 natural armor, +5 Dex), and 10 hit points + 2 hit points per caster level (maximum 50). If the entity loses all its hit points, it disappears, possibly subjecting all aboard to a crash (treat as wrecked). The entity gains certain powers according to caster level, just like a mount does in the phantom steed spell.}
        
\DeclareSpell{Phantom Driver}{conjuration (creation) []|V,  S|10 minutes|10 ft.|Effectone quasi-real, humanlike creature|1 hour/level (D)|none|no}[Conjures a phantom to drive vehicles.]
    \DeclareSpellDescription{Phantom Driver}{You conjure a Small or Medium, quasi-real, humanlike creature (the exact physical features can be customized as you wish). This creation can drive any vehicle you command it to. This phantom creature does not fight, and while animals that power a muscle-propelled vehicle driven by the creature do respond to its commands, animals otherwise shun the creature and refuse to attack it.  The rider has an AC of 20 (+1 size, +4 natural armor, +5 Dex) if it is a Small creature or an AC of 19 (+4 natural armor, +5 Dexterity) if it is a Medium creature. It has 7 hit points + 1 hit point per caster level. If it loses all its hit points, the phantom driver disappears. A phantom driver has a land speed of 30 feet, and makes all driver skill checks (no matter what skills are needed to drive the vehicle) as your caster level + your Intelligence modifier.}
        
\DeclareSpell{Phantom Steed, Communal}{conjuration (creation) []|V,  S|10 minutes|close (25 ft. + 5 ft./2 levels)|Effectup to six quasi-real, horselike creatures|1 hour/level (D)|none|no}[As phantom steed, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Phantom Steed, Communal}{This spell functions like phantom steed, except you can summon up to six steeds, and you divide the duration in 1-hour intervals among the steeds summoned.}
        
\DeclareSpell{Pilfering Hand}{evocation () [force]|S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone object|see text|none|yes (object)}[You may seize an object or manipulate it from afar.]
    \DeclareSpellDescription{Pilfering Hand}{You create and control an invisible telekinetic force, manipulating it with either startling abruptness or careful deliberateness, allowing you to seize an object from an opponent or remotely manipulate an object. You can utilize this force to one of two ends.  Abrupt Maneuver: You instantaneously attempt a disarm or steal combat maneuver against a target within range. Use your caster level as your Combat Maneuver Bonus, adding your Charisma modifier (bard, oracle, sorcerer), Intelligence modifier (magus, wizard), or Wisdom modifier (cleric) in place of your Strength or Dexterity modifier. This combat maneuver attempt does not provoke an attack of opportunity from its target, but casting this spell might. If you are successful, you pull the target object to you, and if you have enough hands free, you can catch it. Otherwise, the object lands in your square as if you dropped it.  Careful Maneuver: You attempt a Disable Device check or a Sleight of Hand check to pick-pocket a target within range. This spell lasts as long as you need to accomplish the task, requiring your full concentration for that duration. Once you resolve the skill check, the spell ends. If you are successful on your Sleight of Hand check, you pull the target object to you as with an abrupt maneuver. The target gains a +2 bonus on its Perception check to notice the successful attempt.}
        
\DeclareSpell{Protection from Arrows, Communal}{abjuration () []|V,  S,  F (a piece of tortoiseshell or turtle shell)|1 standard action|touch|Targetscreatures touched|1 hour/level or until discharged|Will negates (harmless)|yes (harmless)}[As protection from arrows, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Protection from Arrows, Communal}{This spell functions like protection from arrows, except you divide the duration in 1-hour intervals among the creatures touched. Once the spell absorbs 10 points of damage per caster level (maximum 100 points) for a subject, the spell's effects end for that subject.}
        
\DeclareSpell{Protection from Chaos, Communal}{abjuration () [lawful]|V,  S,  M/DF|1 standard action|touch|Targetscreatures touched|1 min./level (D)|Will negates (harmless)|no; see text}[As protection from chaos, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Protection from Chaos, Communal}{This spell functions like protection from chaos, except you divide the duration in 1-minute intervals among the creatures touched.}
        
\DeclareSpell{Protection from Energy, Communal}{abjuration () []|V,  S,  DF|1 standard action|touch|Targetscreatures touched|10 min./level or until discharged|Fortitude negates (harmless)|yes (harmless)}[As protection from energy, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Protection from Energy, Communal}{This spell functions like protection from energy, except you divide the duration in 10-minute intervals among the creatures touched. Once the spell absorbs 12 points of energy damage per caster level (maximum 120 points) for a subject, the spell's effects end for that subject.}
        
\DeclareSpell{Protection from Evil, Communal}{abjuration () [good]|V,  S,  M/DF|1 standard action|touch|Targetscreatures touched|1 min./level (D)|Will negates (harmless)|no; see text}[As protection from evil, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Protection from Evil, Communal}{This spell functions like protection from evil, except you divide the duration in 1-minute intervals among the creatures touched.}
        
\DeclareSpell{Protection from Good, Communal}{abjuration () [evil]|V,  S,  M/DF|1 standard action|touch|Targetscreatures touched|1 min./level (D)|Will negates (harmless)|no; see text}[As protection from good, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Protection from Good, Communal}{This spell functions like protection from good, except you divide the duration in 1-minute intervals among the creatures touched.}
        
\DeclareSpell{Protection from Law, Communal}{abjuration () [evil]|V,  S,  M/DF|1 standard action|touch|Targetscreatures touched|1 min./level (D)|Will negates (harmless)|no; see text}[As protection from law, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Protection from Law, Communal}{This spell functions like protection from law, except you divide the duration in 1-minute intervals among the creatures touched.}
        
\DeclareSpell{Pup Shape}{transmutation (polymorph) []|V,  S,  M (a rag doll)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone animal|1 round/level|Fortitude negates (and Will special, see text)|yes}[Transforms a single animal or magical beast into a younger and cuter version of itself for a short time.]
    \DeclareSpellDescription{Pup Shape}{You transform the subject animal into a Small magical beast (or a magical beast one size category smaller than the original creature, whichever is smaller), creating a young magical version of itself for a short period of time. While in this form, the target has only 1 HD (maximum hit points), and the target takes a -4 penalty to Strength, Constitution, Intelligence and Wisdom (minimum 1). The creature also gains a +4 size bonus to Dexterity and a +2 natural armor bonus.  Any nonevil creature that attempts to attack a creature in this form must succeed at a Will saving throw (using the DC of the spell) to overcome feelings of guilt and protectiveness toward the young and innocent-seeming creature. On a failed saving throw, it cannot follow through with the attack, that part of the action is lost, and it can't directly attack the transformed creature for the duration of the spell or until the spell's target attacks it. This part of the spell is a mind-affecting emotion effect. Evil creatures have no qualms about attacking the target of this spell, in fact, some particularly heinous creatures might go out of their ways to do the target harm.}
        
\DeclareSpell{Qualm}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 minute/level or until discharged|Will negates|yes}[Target gains penalties on ability checks, skill checks, and concentration checks until it spends an entire round doing nothing.]
    \DeclareSpellDescription{Qualm}{The target is suddenly beset with unexplainable doubts about the effectiveness of its actions and the righteousness of its cause. The creature takes a -10 penalty on its ability checks, skill checks, and concentration checks, until the duration ends, or until it spends its entire turn doing absolutely nothing (it spends a full-round action gaining focus). Spending an entire turn doing nothing discharges the spell.}
        
\DeclareSpell{Recoil Fire}{transmutation () []|V,  S,  M (hoof shavings from a mule)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets1 firearm|instantaneous|Will negates (object)|yes (object)}[Ammunition in the targeted firearm generates excessive recoil.]
    \DeclareSpellDescription{Recoil Fire}{The target firearm suddenly fires of its own volition, even if it is unloaded, generating a recoil so great that the wielder or carrier of the firearm must scramble to hold onto it and becomes flat-footed until the start of his next turn. If the wielder is already flat-footed, he is instead knocked prone. If the firearm was loaded, that ammunition is wasted.}
        
\DeclareSpell{Reinforce Armaments}{transmutation () []|V,  S,  M/DF (a metal pin)|1 standard action|touch|Targetsone armor suit or weapon touched|10 minutes/level|Will negates (harmless, object)|yes (harmless, object)}[Temporarily mitigates the fragile quality in targeted weapon or armor.]
    \DeclareSpellDescription{Reinforce Armaments}{You reinforce a weapon or armor suit to give it a temporarily upgrade or mitigate the fragile quality (see page 146). A suit of armor or weapon touched that has the fragile quality is not considered to have the fragile quality for the spell's duration. Normal armor suits or weapons subjected to this spell instead gain the masterwork quality for the spell's duration and their hardness is doubled. If this spell is cast on masterwork or magical armor or weapons, their hardness is doubled for the duration of the spell.}
        
\DeclareSpell{Reinforce Armaments, Communal}{transmutation () []|V,  S,  M/DF (a metal pin)|1 standard action|touch|Targetsarmor suits or weapons touched|10 minutes/level|Will negates (harmless, object)|yes (harmless, object)}[As reinforce armaments, but you may divide the duration among objects touched.]
    \DeclareSpellDescription{Reinforce Armaments, Communal}{This spell functions like reinforce armaments, except you divide the duration in 10-minute intervals among the objects touched.}
        
\DeclareSpell{Reloading Hands}{conjuration (creation) []|V,  S|1 standard action|touch|Targetsprojectile weapon touched|1 round/caster level (D)|Will negates (object, harmless)|yes (object, harmless)}[Loads a single shot into your weapon every round.]
    \DeclareSpellDescription{Reloading Hands}{Once per round, phantom hands load a single ranged weapon or firearm with conjured ammunition. This ammunition counts as magical for overcoming damage reduction and attacking incorporeal creatures, but is the standard for its type (a normal bullet or pellets and black powder in the case of firearms). Conjured ammunition ceases to exist 1 round after it is removed from the weapon, or at the end of the duration, whichever comes first.}
        
\DeclareSpell{Resinous Skin}{transmutation () []|V,  S|1 standard action|personal|Targetsyou|10 minutes/level|see text|no}[You gain DR 5/piercing and +4 to CMD against disarm attempts.]
    \DeclareSpellDescription{Resinous Skin}{You coat your body with a resinous substance, protecting you from attacks and binding weapons that strike you. You gain DR 5/piercing, as well as a +4 circumstance bonus to your CMD against disarm attempts and on saving throws against effects that cause you to drop something you are holding. Additionally, you gain a +2 circumstance bonus on combat maneuver checks to initiate a grapple, maintain a grapple, and pin a foe. Any enemy you grapple takes a -2 penalty on attempts to break the grapple and to escape the grapple using Escape Artist. Any weapon, that strikes you becomes stuck unless its wielder succeeds at a Reflex saving throw. Such a weapon can be pulled free of you only with a successful Strength check (DC = your saving throw DC for this spell). This spell has no effect on unarmed strikes or natural weapons.}
        
\DeclareSpell{Resist Energy, Communal}{abjuration () []|V,  S,  DF|1 standard action|touch|Targetscreatures touched|10 min./level|Fortitude negates (harmless)|yes (harmless)}[As resist energy, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Resist Energy, Communal}{This spell functions like resist energy, except you divide the duration in 10-minute intervals among the creatures touched.}
        
\DeclareSpell{Returning Weapon}{conjuration (teleportation) []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone weapon that can be thrown|1 minute/level|Will negates (harmless, object)|yes (harmless, object)}[Grants a weapon the returning special weapon quality.]
    \DeclareSpellDescription{Returning Weapon}{For the duration of the spell, the target weapon acts as if it had the returning weapon special ability (see page 471 of the Core Rulebook).  This spell can be used as the prerequisite for the returning weapon special ability.}
        
\DeclareSpell{Returning Weapon, Communal}{conjuration (teleportation) []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsweapons that can be thrown|1 minute/level|Will negates (harmless, object)|yes (harmless, object)}[As returning weapon, but you may divide the duration among weapons touched.]
    \DeclareSpellDescription{Returning Weapon, Communal}{For the duration of the spell, the target weapon acts as if it had the returning weapon special ability (see page 471 of the Core Rulebook).  This spell can be used as the prerequisite for the returning weapon special ability.}
        
\DeclareSpell{Ricochet Shot}{evocation () []|V,  S,  M (a wishbone)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone projectile weapon|1 round/level or until discharged|Will negates (harmless, object)|yes (harmless, object)}[Imbues a projectile weapon to give its ammunition the ability to ricochet.]
    \DeclareSpellDescription{Ricochet Shot}{You imbue a projectile weapon with the ability to ricochet any projectiles that hit one target so that they also hit another. When the wielder ricochets a projectile, she selects a primary target to attack. If she hits the primary target, the projectile ricochets instead of being destroyed. The wielder can then select a secondary target that is within 20 feet of the primary target. She makes an attack roll against the secondary target at the same base attack bonus, but does not gain the benefit from any enhancement bonuses or magic qualities on the projectile. If the shot comes from a firearm, the ricochet targets normal AC rather than touch AC.  While the spell lasts, the target weapon's wielder can ricochet one projectile per three caster levels you possess, to a maximum of six at caster level 18th. Once the target weapon's wielder ricochets that many shots, the spell is discharged. If the weapon's wielder fails to use all the ricochets before the spell end, those ricochets are wasted.}
        
\DeclareSpell{See Alignment}{divination () []|V,  S,  M (eye of newt)|1 standard action|personal|Targetsyou|1/round per level||}[Pick an alignment; in your sight, creatures and items with that alignment emit a ghostly radiance.]
    \DeclareSpellDescription{See Alignment}{When you cast this spell, select a single alignment (such as lawful good or chaotic evil). Creatures of that alignment glow with a ghostly radiance while they are within your vision. Though you can see this radiance, other creatures cannot.  Spells and effects that obscure alignment, like undetectable alignment, also obscure the effects of this spell.}
        
\DeclareSpell{Shadow Bomb Admixture}{conjuration (creation) []|V,  S|1 standard action|personal|Targetsyou|1 round/level|special, see below|special, see below}[Empowers bombs you throw to cover the target with a shadowy substance that grants it concealment and limits its vision.]
    \DeclareSpellDescription{Shadow Bomb Admixture}{Upon drinking an extract created with this formula, you make a significant change to your magical reserve that modifies the nature of all bombs you create and throw during this extract's duration. This effect on your magical reserve has no effect on any discoveries that you use to modify your bombs, but you can only have one admixture effect (formula with the word "bomb admixture" in its title) active at a time. If you drink another bomb admixture, the effects of the former bomb admixture end and the new one becomes active.  When you throw a bomb and hit a direct target, a shadowy substance is released from the bomb covering the direct target and up to three creatures that take damage from the bomb's splash (alchemist's choice). The affected creatures must successfully make a Fortitude saving throw, or they gain concealment but treat all other creatures as having concealment for the duration of the shadow bomb admixture. This effect does not ignore spell resistance.}
        
\DeclareSpell{Share Language, Communal}{divination () []|V,  S,  M (a page from a dictionary)|1 standard action|touch|Targetscreatures touched|24 hours|Will negates (harmless)|yes (harmless)}[As share language, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Share Language, Communal}{This spell functions like share language (Advanced Player's Guide 243), except you divide the duration in 1-hour increments among the creatures touched.}
        
\DeclareSpell{Shock Shield}{abjuration () [electricity,  force]|V,  S|1 standard action|personal|Targetsyou|1 minutes/level (D)||}[A shield of force protects you until you dismiss it in an explosion of electricity.]
    \DeclareSpellDescription{Shock Shield}{This spell creates an invisible shield similar to but not as strong as the shield spell. This shield hovers in front of you and negates magic missile attacks directed at you. The disk provides a +2 shield bonus to AC. This bonus applies against incorporeal touch attacks.  At any time, as a free action, you may dismiss your shield, at which point it deals 1d6 points of electrical damage to all creatures within a 5-foot burst, including you. A Reflex saving throw halves the damage.}
        
\DeclareSpell{Shocking Image}{illusion (figment) [electricity]|V,  S|1 standard action|personal|Targetsyou|1 minute/level|none|see text}[As mirror image, but the duplicates emit electrical damage when destroyed.]
    \DeclareSpellDescription{Shocking Image}{This spell works like mirror image, except the illusory doubles it creates discharge an electric shock when destroyed. An opponent that uses a melee attack to destroy one of your images takes 2d6 points of electricity damage. You must overcome a target's spell resistance the first time you deal this electricity damage to it. Failure renders the target immune to damage from this spell.}
        
\DeclareSpell{Siege Of Trees}{transmutation () []|V,  S,  DF|10 minutes|close (25 ft. + 5 ft./2 levels)|Targetsone Large plant per three caster levels|1 hour/level (D)|none|no}[Transforms Large trees into arboreal catapults of the same size.]
    \DeclareSpellDescription{Siege Of Trees}{You imbue inanimate plants with limited mobility and a semblance of life. Each plant targeted acts as a light catapult (see page 162) until the end of the spell's duration, though you must spend a standard action to aim each of these tree catapults before the first time they fire, and anytime thereafter when you want the trees to fire at a new target. The catapult uses your caster level as its targeting bonus. With a free action, you can command one or all of the trees under your command to stop firing. You do not need to supply ammunition to these tree catapults; they will automatically load themselves with rocks and boulders in the area, digging them deep from the ground if need be. You can supply the trees ammunition if you desire. The tree will not load flaming ammunition, and these catapult trees cannot be affected by energy siege shot (see page 228) if the energy selected is fire.}
        
\DeclareSpell{Siege of Trees, Greater}{transmutation () []|V, S|10 minutes|close (25 ft. + 5 ft./2 levels)|Targetsone Gargantuan, Huge, or Large plant per three caster levels|1 hour/level (D)|none|no}[As siege of trees, but can transform Huge and Gargantuan trees into arboreal catapults of the same size.]
    \DeclareSpellDescription{Siege of Trees, Greater}{As siege of trees, but you can affect larger-sized plants. Each plant acts as a catapult of its size.}
        
\DeclareSpell{Spell Immunity, Communal}{abjuration () []|V,  S,  DF|1 standard action|touch|Targetscreatures touched|10 min./level|Will negates (harmless)|yes (harmless)}[As spell immunity, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Spell Immunity, Communal}{This spell functions like spell immunity, except you divide the duration in 10-minute intervals among the creatures touched.}
        
\DeclareSpell{Spell Immunity, Greater Communal}{abjuration () []|V,  S,  DF|1 standard action|touch|Targetscreatures touched|10 min./level|Will negates (harmless)|yes (harmless)}[As greater spell immunity, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Spell Immunity, Greater Communal}{This spell functions like greater spell immunity, except you divide the duration among the creatures in 10-minute intervals among the creatures touched.}
        
\DeclareSpell{Spider Climb, Communal}{transmutation () []|V,  S,  M (a live spider)|1 standard action|touch|Targetscreatures touched|10 min./level|Will negates (harmless)|yes (harmless)}[As spider climb, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Spider Climb, Communal}{This spell functions like spider climb, except you divide the duration in 10-minute intervals among the creatures touched.}
        
\DeclareSpell{Spontaneous Immolation}{evocation () [fire]|V,  S,  M (pinch of saltpeter)|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone creature|instantaneous|Fortitude half and Reflex (see description)|yes}[Target takes 3d6 points of fire damage and catches on fire.]
    \DeclareSpellDescription{Spontaneous Immolation}{You point your finger at a creature, causing it to spontaneously burst into flame. The target takes 3d6 points of fire damage and catches on fire (Pathfinder RPG Core Rulebook 444). A successful Fortitude save reduces this damage by half and prevents the target from catching on fire. Each round on your turn, a burning target can attempt a new save to extinguish the flames (DC equal to the DC of the spell); otherwise it takes another 1d6 fire damage.}
        
\DeclareSpell{Stabilize Powder}{transmutation () []|V,  S,  M (a few drops of liquor)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets1 loaded firearm|instantaneous|Will negates (harmless, object)|yes (harmless, object)}[Ammunition in the targeted firearm is less likely to misfire.]
    \DeclareSpellDescription{Stabilize Powder}{Ammunition currently loaded in the target firearm is less prone to misfire. Decrease the misfire range by 1 + 1 per five caster levels (maximum +5, minimum misfire 0) for the ammunition currently loaded into that firearm.}
        
\DeclareSpell{Stoneskin, Communal}{abjuration () []|V,  S,  M (granite and diamond dust worth 250 gp per creature affected)|1 standard action|touch|Targetscreatures touched|10 min./level or until discharged|Will negates (harmless)|yes (harmless)}[As stoneskin, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Stoneskin, Communal}{This spell functions like stoneskin, except you divide the duration in 10 minute intervals among the creatures touched. Once the spell has prevented 10 points of damage per caster level (maximum 150 points) for a subject, the spell's effects end for that subject.}
        
\DeclareSpell{Summoner Conduit}{necromancy () []|V,  S,  M (two flies)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone summoned creature or eidolon|1 minute/level|Will negates|yes}[The target takes damage whenever its summoned creature does.]
    \DeclareSpellDescription{Summoner Conduit}{You exploit the invisible, mystic connection between the target creature and its summoner to harm that summoner. Whenever the target's summoned creature is the target of a spell that deals damage, the target's summoner is also considered to be a target of that spell. Such a summoner gains his normal defenses against the spell, such as a saving throw and spell resistance, and cannot be affected if he is on another plane of existence.}
        
\DeclareSpell{Sun Metal}{transmutation () [fire]|V,  S|1 standard action|touch|Targetsone melee weapon|1 round/level (see text)|Fortitude negates (object)|yes (object)}[Weapon touched bursts into flames.]
    \DeclareSpellDescription{Sun Metal}{The target weapon ignites into flame that does not hurt the weapon or the wielder, but damages those hit by the weapon. When the weapon's wielder hits with this weapon, it deals an additional 1d4 points of fire damage. This damage is not multiplied in the case of a critical hit. This effect immediately ends if the weapon is submerged in water. This effect does not stack with the flaming or flaming burst weapon special ability or any other effect that grants the weapon extra fire damage. It does not function on weapons with the frost or icy burst weapon special ability or any other effect that grants a weapon extra cold damage.}
        
\DeclareSpell{Symbol Of Striking}{illusion (shadow) []|V,  S,  M (a masterwork melee weapon costing at least 300 gp)|10 minutes|0 ft.; see text|Effectone symbol|see text|Will half, see text|yes, see text}[As symbol of death, but fills a 5-foot square.]
    \DeclareSpellDescription{Symbol Of Striking}{This spell functions like symbol of death, except that using the material component, you scribe a symbol of striking so it fills a 5-foot square. Once triggered, the symbol of striking glows and  lasts for 10 minutes per caster level or until it has made a number of attacks of opportunity equal to your level, whichever comes first. When triggered, the symbol threatens its area and the area around it as if it were a Medium creature wielding a magic version of the weapon you used as the material component. Using your caster level + 1 + your Intelligence modifier (magus, witch, wizard) or Wisdom modifier (cleric) or Charisma modifier (oracle, sorcerer) as its attack bonus, the symbol can make a number of attacks of opportunity each round equal to 1 + the same ability score modifier you used to determine its attack bonus. It gains a bonus on damage rolls equal to the same ability score modifier you used to determine its attack bonus. A shadowy version of you wielding the material component appears to make these attacks.  The symbol attacks any non-attuned creature that provokes an attack of opportunity from the symbol. However, when the symbol first attacks a creature, the symbol must overcome that creature's spell resistance or be rendered unable to harm it. The symbol never again attacks such creatures. Further, when the symbol first attacks a creature, a successful Will saving throw allows the creature to see the shadow nature of the attacks and take half damage when such attacks hit.  Symbol of striking can be made permanent with a permanency spell by a caster of 13th level or higher for the cost of 10,000 gp.}
        
\DeclareSpell{Tactical Acumen}{enchantment (compulsion) [mind-affecting]|V,  S,  M/DF (a small piece of a map)|1 standard action|30 ft.|AreaThe caster and all allies within a 30-ft.-radius burst, centered on the caster|1 round/level (D)|Will negates (harmless)|yes (harmless)}[You gain an additional +1 on attack rolls or to AC due to battlefield positioning.]
    \DeclareSpellDescription{Tactical Acumen}{Tactical acumen grants you and your allies a mastery of battlefield tactics. Whenever you would gain a bonus on attack rolls or to AC due to battlefield position, such as flanking, higher ground, or cover, you gain an additional +1 insight bonus. This bonus increases by +1 for every five caster levels above 5th you possess (maximum +4).}
        
\DeclareSpell{Tar Pool}{transmutation () [earth,  fire]|V,  S,  M/DF (a ball of hardened tar)|1 standard action|close (25 ft. + 5 ft./2 levels)|Area20-ft.-radius burst|1 round/level|Reflex partial, see text|no}[Converts the top layer of the ground into hot tar.]
    \DeclareSpellDescription{Tar Pool}{You convert a layer of the ground to hot tar. Creatures in the area when the tar appears take 1d6 points of fire damage per two caster levels (maximum of 10d6) and must succeed at a Reflex save or become entangled. An entangled creature receives a saving throw each round to free itself from the tar, and can also attempt to free itself by spending a move action to attempt a Strength check or Escape Artist check (DC = spell saving throw DC).  It costs 2 squares of movement to enter a square in the area of effect, and the DC of Acrobatics checks within the area of effect increases by 5. The area is difficult terrain. A creature that moves into or starts its turn in the area takes 2d6 points of fire damage and must reattempt this Reflex save or become entangled. A creature that falls prone in the area takes a -4 penalty on its Reflex save against the tar and on Strength and Escape Artist checks to escape the tar.  A creature that escapes the tar still takes fire damage from the tar until the spell ends or that creature spends a full-round action removing the tar. A creature with tar on it takes a -4 penalty on Acrobatics and Fly checks made to fly with wings or similar appendages.}
        
\DeclareSpell{Targeted Bomb Admixture}{transmutation () []|V,  S|1 standard action|personal|Targetyou|1 round/level||}[Empowers bombs you throw to deal more damage to a single creature.]
    \DeclareSpellDescription{Targeted Bomb Admixture}{Upon drinking an extract created with this formula, you make a significant change to your magical reserve that modifies the nature of all bombs you create and throw during this extract's duration. This effect on your magical reserve has no effect on any discoveries that you use to modify your bombs, but you can only have one admixture effect (formula with the word "bomb admixture" in its title) active at a time. If you drink another bomb admixture, the effects of the former bomb admixture end and the new one becomes active.  When you throw bombs, they can only hit a direct target; they do not splash. However, the bomb deals its base damage plus double your Intelligence modifier instead of just its base damage plus your Intelligence modifier.}
        
\DeclareSpell{Telekinetic Assembly}{transmutation () []|V,  S,  F (a miniature of the target siege engine,  costing 10 gp)|Casting time 1 minute|close (25 ft + 5 ft./2 levels)|Targetsone disassembled siege engine|instantaneous|none|no}[Assembles a siege engine using 1 fewer worker for every two caster levels.]
    \DeclareSpellDescription{Telekinetic Assembly}{You assemble a siege engine, using up to one fewer worker per two caster levels you possess. You can do without one additional worker if you have any ranks in Knowledge (engineering), plus one additional worker per 5 ranks you have in that skill. If your  caster level combined with Knowledge (engineering) fails to eliminate the need for workers, this spell fails.}
        
\DeclareSpell{Telekinetic Charge}{evocation () [force]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone willing creature|instantaneous|Will negates (harmless)|yes (harmless)}[Launches an ally through the air.]
    \DeclareSpellDescription{Telekinetic Charge}{You telekinetically launch an ally across the battlefield to anywhere within this spell's range. While moving, your ally is flying just above the ground unless you wish otherwise. Movement from this spell provokes attacks of opportunity as normal, although you can lift your ally over objects or out of enemy reach, as long as your ally remains within this spell's range. If your ally lands adjacent to an opponent, he can spend an immediate action to make a melee attack against that opponent with a +2 bonus on the attack roll.}
        
\DeclareSpell{Terrain Bond}{enchantment (compulsion) [mind-affecting]|V,  S,  M (a pinch of earth taken from your most favored terrain)|1 standard action|personal|Targetsyou|1 hour/2 levels (D)||}[Treat the terrain you are in as a favored terrain for the spell's duration.]
    \DeclareSpellDescription{Terrain Bond}{You call upon the spirits of nature to help you adapt to your environment. You treat the terrain you are in as your most favored terrain until this spell ends.  If you do not have the favored terrain class feature, you gain no benefit from this spell.}
        
\DeclareSpell{Thunder Fire}{transmutation () []|V,  S,  M (a piece of spent thunderstone)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets1 loaded firearm|instantaneous|Will negates (object), see text|yes (object), see text}[Ammunition in the targeted firearm deafens opponents.]
    \DeclareSpellDescription{Thunder Fire}{The firearm targeted creates a thunderous report, even if the firearm is not loaded. Every creature within 15 feet of the creature wielding or carrying the firearm must succeed at a Fortitude save or be deafened for 1 minute. The creature wielding or carrying the firearm takes a -4 penalty on this saving throw, and his misfire range increases by 1 for 1d4 rounds. If the firearm was loaded when it was targeted by this spell, that ammunition is wasted.}
        
\DeclareSpell{Tongues, Communal}{divination () []|V,  M/DF (a clay model of a ziggurat)|1 standard action|touch|Targetscreatures touched|10 min./level|Will negates (harmless)|no}[As tongues, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Tongues, Communal}{This spell functions like tongues, except you divide the duration in 10-minute intervals among the creatures touched.}
        
\DeclareSpell{Touch Injection}{transmutation () []|V,  S|1 standard action|personal|Targetsyou|1 hour/level|none|no}[You can deliver an infusion, elixir, poison, or potion as a touch attack.]
    \DeclareSpellDescription{Touch Injection}{You must hold an elixir, infused extract, poison, or potion in hand as you cast this spell. The held substance drains from its container into a magical sac in your body. While the spell lasts, you can deliver the substance with a mere touch. To do so to an opponent, you must make a successful melee touch attack. If you hit, the substance takes effect immediately, despite any onset period, and that opponent receives the normal saving throw (if any) against the substance. In the case of a personal infused extract, the opponent receives both a Fortitude save and spell resistance. If you miss, the substance remains in the magical sac for you to use later.  This spell protects you from poison in the sac, but unless you have the poison use class feature, you suffer a 5\% chance of exposing yourself to the poison when you first cast the spell. If you roll a natural 1 while attempting to inject the poison into an enemy, you are exposed to it.}
        
\DeclareSpell{Twisted Space}{transmutation () []|V,  S,  M (a length of wire bent into a circle)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round|Will negates|yes}[Targeted creature's attacks target a random square instead of the intended target.]
    \DeclareSpellDescription{Twisted Space}{You distort the space around a creature, twisting the path of its melee attacks unpredictably, but always toward a nearby creature that the target threatens. Until the start of your next turn, melee attacks made by the target creature affect a random target instead of their intended target.}
        
\DeclareSpell{Unerring Weapon}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone weapon or 20 projectiles, all of which must be together at the time of casting|1 round/level|Will negates (harmless, object)|yes (harmless, object)}[Grants a +2 bonus, +1 per four caster levels, on attack rolls to confirm a critical hit.]
    \DeclareSpellDescription{Unerring Weapon}{This spell causes a weapon to veer closer to vital areas, improving the result of a critical threat. This transmutation grants a +2 bonus on attack rolls to confirm critical hits plus 1 additional bonus point per four caster levels (maximum total bonus +7). If the spell is cast on projectiles, the effect ends on a specific projectile whenever that projectile is used to make an attack, regardless of whether the attack hits. For this spell, shuriken are considered projectiles.}
        
\DeclareSpell{Viper Bomb Admixture}{conjuration (creation) []|V,  S|1 standard action|personal|Targetsyou|1 round/level||}[Empowers bombs you throw to summon poisonous biting vipers that bite those hit or splashed by the bomb.]
    \DeclareSpellDescription{Viper Bomb Admixture}{Upon drinking an extract created with this formula, you make a significant change to your magical reserve that modifies the nature of all bombs you create and throw during this extract's duration. This effect on your magical reserve has no effect on any discoveries that you use to modify your bombs, but you can only have one admixture effect (formula with the word "bomb admixture" in its title) active at a time. If you drink another bomb admixture, the effects of the former bomb admixture end and the new one becomes active.  When you throw a bomb and hit a target directly, up to four vipers are released from the bomb. One viper attacks the target of the direct hit, and the other vipers attack up to three creatures that take damage from the splash damage. The vipers make melee touch attacks (using your base attack bonus + Intelligence modifier) and on a hit deal 1d4 + your Intelligence modifier damage, and the target is poisoned as if by a venomous snake (Pathfinder RPG Bestiary 255). Hit or miss, the conjured vipers disappear after they make the attack. The conjured snakes are not damaged or adversely affected by the bombs you throw.}
        
\DeclareSpell{Walk Through Space}{conjuration (teleportation) []|V,  S,  M (a wren's egg)|1 standard action|personal|Targetsyou|1 round/level||}[You can spend a move action to teleport 30 feet or to stand while prone without provoking attacks of opportunity.]
    \DeclareSpellDescription{Walk Through Space}{When under the effects of this spell, you can teleport up to 30 feet as a move action. You must end this movement in an unoccupied space that you can stand on within line of sight. Alternatively, you can spend a move action to teleport to a standing position from lying prone. Teleporting does not provoke attacks of opportunity.}
        
\DeclareSpell{Warding Weapon}{abjuration () []|V,  S,  F (one melee weapon you are proficient in and you are holding)|1 standard action|personal|Targetsyou|1 round/level||}[The weapon you use for the focus of this spell defends you, allowing you to cast spells without provoking attacks of opportunity.]
    \DeclareSpellDescription{Warding Weapon}{The focus of this spell flies upward above your head and takes a defensive position within your space. It lunges at opponents, as if guided by a martially trained hand, parrying and turning back melee attacks aimed at you, but does not strike back at any opponent nor does it damage them. The weapon serves only as a defense. While it protects you, you can cast spells without provoking attacks of opportunity, without the need to cast them defensively.  A creature with the Disruptive feat (Core Rulebook 122) can easily bypass this spell's defenses. You provoke attacks of opportunity for casting spells against these creatures even when subject to this spell, though you can still choose to cast defensively.}
        
\DeclareSpell{Water Walk, Communal}{transmutation () [water]|V,  S,  DF|1 standard action|touch|Targetscreatures touched|10 min./level (D)|Will negates (harmless)|yes (harmless)}[As water walk, but you may divide the duration among creatures touched.]
    \DeclareSpellDescription{Water Walk, Communal}{This spell functions like water walk, except you divide the duration in 10-minute intervals among the creatures touched.}
        
\DeclareSpell{Weaken Powder}{transmutation () []|V,  S,  M/DF (an empty paper cartridge)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets1 loaded firearm|instantaneous|Will negates (object)|yes (object)}[Targeted firearm's ammunition halves the firearm's range and imposes a 2 penalty on damage rolls.]
    \DeclareSpellDescription{Weaken Powder}{Ammunition in the target firearm generates less of an explosive charge when fired. With such ammunition, the firearm's range increment is halved and the firer takes a -2 penalty on damage rolls. If aware of this spell's effect prior to firing the altered ammunition (a DC 16 Spellcraft check to identify the spell being cast or similar effect), the firearm's user can spend a standard action to clear the altered ammunition from the firearm. Doing so destroys that ammunition.}
        
\DeclareSpell{Wilderness Soldiers}{transmutation () []|V,  S|1 standard action|30 ft.|Area30-ft.-radius emanation, centered on you|1 round/level|none|no}[Nearby plants aid you in combat.]
    \DeclareSpellDescription{Wilderness Soldiers}{You call on the plants nearby to aid you in combat. This spell is ineffective if no plants you can direct are within the area. You can spend a swift action and/or a standard action on each of your turns to direct one of the following attacks. The attack bonus or CMB for these attacks equals your base attack bonus + your Wisdom modifier. You grant a +1 bonus per three caster levels (maximum +5) on damage rolls due to this spell. Your wilderness soldiers never provoke attacks of opportunity, and they do not count as allies for flanking or other purposes.  Tree: A tree makes a melee attack with a 10-foot reach from its trunk. A hit deals an amount of damage equal to 1d8 points + your Wisdom modifier. The tree can instead attempt a bull rush, drag, or reposition combat maneuver with the same reach, but the tree cannot move itself.  Undergrowth or Hedgerow: Acting as a Medium creature, one square of undergrowth or hedgerow attempts a grapple combat maneuver against an opponent within or adjacent to that square. Heavy undergrowth gains a +2 bonus to its CMD. Undergrowth cannot move the grapple or pin a foe, but it can deal an amount of damage equal to 1d4 points + your Wisdom modifier by making a successful grapple check against a foe it is grappling. The undergrowth's CMD is 5 + its CMB. If you fail to direct the undergrowth to maintain the grapple, it releases its opponent.}
        
\DeclareSpell{Wreath of Blades}{abjuration () []|V,  S,  F (four mithral daggers,  each worth at least 502 gp each)|1 standard action|personal|Area5-foot-radius emanation centered on you|1 round/level|Reflex half (special, see below)|no (special, see below)}[Four mithral daggers speed around you, attacking nearby creatures and protecting your spellcasting from attacks of opportunity.]
    \DeclareSpellDescription{Wreath of Blades}{The daggers serving as focus of this spell take on a deadly sharpness as they animate and spin around you, creating a 5-foot-radius emanation of spinning mithral blades that moves with you. Any creature that starts its turn within the area of the spinning blades takes 1d4 points of damage for every two caster levels (maximum 10d4 at 20th level) and the damage bypasses DR/silver.  Furthermore, the daggers ward off some attacks, in a way similar to the warding weapon spell (see page 48). While subject to this spell, you do not provoke attacks of opportunity for casting spells, even from creatures with the Disruptive feat. Creatures with the Spellbreaker feat (Core Rulebook 134) can easily bypass this defensive property, though they still take damage from the spell. Your casting (even failing to cast defensively) still provokes attacks of opportunity from creatures with that feat.  Lastly, the blades that serve as the focus for this spell can be enchanted for greater effect. When all of the blades share the same enhancement bonus and special weapon qualities, a creature that is damaged by this spell is also treated as if hit by one of these weapons. For example, if a 12th-level magus casts this spell using four +1 frost mithral daggers as focus, the damage dealt by the blades would be 6d4+1 plus 1d6 cold damage, as long as the daggers were commanded to be sheathed in ice. No matter the modifications made to the focus weapons, they must always be mithral daggers. No other type of weapons can serve as a focus for this spell.}
    