    
\DeclareSpell{Aura Of Distraction}{enchantment () [mind-affecting]|V,  S|1 standard action||Area20-ft.-radius emanation centered on you|1 minute/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Aura Of Distraction}{You emit an aura of subsonic noise and mental imagery that makes concentrating difficult. Any creature within the aura that fails its save takes a -5 penalty on concentration checks. A creature must attempt the Will save upon entering the area of the aura, and the penalty ends as soon as the creature leaves the aura. A creature that succeeds at its save is immune to the effects of the aura for this casting of the spell, even if it leaves and reenters the aura, but must attempt another Will save each additional time this spell is cast. You are immune to your own aura of distraction.}
        
\DeclareSpell{Burst Of Force}{evocation () [force]|V|1 standard action||Area20-ft.-radius burst centered on you|instantaneous|Fortitude half (see text)|yes}[]
    \DeclareSpellDescription{Burst Of Force}{With a burst of telekinetic force, you deal 1d6 points of force damage per caster level (maximum 15d6 points of damage) to all other creatures in the affected area. A successful Fortitude save reduces the damage taken by half. A creature that fails its Fortitude save must also succeed at a Reflex save or be knocked prone.}
        
\DeclareSpell{Debilitating Pain}{enchantment (compulsion) [mind-affecting,  painUM]|V,  S,  M|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round/3 levels|Will partial (see text)|yes}[]
    \DeclareSpellDescription{Debilitating Pain}{The target is overcome with intense pain, causing it to be stunned on a failed save or dazed for 1 round on a successful save.}
        
\DeclareSpell{Debilitating Pain, Mass}{enchantment (compulsion) [mind-affecting,  painUM]|V,  S,  M|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature/4 levels|1 round/3 levels|Will partial (see text)|yes}[]
    \DeclareSpellDescription{Debilitating Pain, Mass}{This spell functions as per debilitating pain, except you can target one creature for every 4 caster levels you have.}
        
\DeclareSpell{Glimpse Of The Akashic}{divination () []|V,  S|1 full-round action|personal|Targetsyou|1 day or until discharged (see text)||}[]
    \DeclareSpellDescription{Glimpse Of The Akashic}{You expand your consciousness in an attempt to tap into the perfect knowledge contained within the Akashic Record. Such a connection is incredibly difficult to create and maintain, and it can be almost impossible to know at the time of the casting what knowledge will be gained. The information contained within the Akashic Record can be overwhelming when accessed in this fashion, so your mind partitions it away until needed. For the next day, you can activate the knowledge gained from the Akashic Record as a free action; when you do so, you gain a circumstance bonus equal to your caster level on all skill checks, ability checks, attack rolls, damage rolls, saving throws, and combat maneuver checks for 1 minute. At the end of this time, the overwhelming nature of the Akashic Record assaults your psyche, causing you to be stunned for 2 rounds and then sickened for 1 minute.}
        
\DeclareSpell{Reflexive Barrier}{evocation () [force]|V,  S|1 immediate action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round (see text)|none (harmless)|no (harmless)}[]
    \DeclareSpellDescription{Reflexive Barrier}{In the blink of an eye, you erect a deflective barrier of force to protect one target. The target gains a deflection bonus to its AC equal to half your caster level. This bonus lasts until the beginning of your next turn. You can cast this spell as a reaction to an attack, but you must do so before the result of the attack is revealed.}
        
\DeclareSpell{Rend Body I}{evocation () []|S|1 full-round action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|instantaneous|Fortitude partial (see text)|yes}[]
    \DeclareSpellDescription{Rend Body I}{You lacerate the body of the target creature with telekinetic force, rending it limb from limb. The target creature takes 1d6 points of damage per caster level you have (maximum 10d6 points of damage). If this spell deals an amount of damage to the target equal to more than half its maximum hit point total, one of the target's limbs (determined randomly) is gruesomely ripped from the target's body and flies 15 feet away from the creature in a random direction. The target then takes 1 point of bleed damage per 2 caster levels you have. The bleeding can be stopped by a successful DC 15 Heal check or the application of any effect that heals hit point damage, but the limb can be restored only by powerful healing effects such as heal or regeneration. If the damage reduces the target's hit points to below 0, all of its limbs are affected in this fashion.  Creatures without discernible anatomy or limbs are unaffected by rend body.}
        
\DeclareSpell{Rend Body II}{evocation () []|S|1 full-round action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|instantaneous|Fortitude partial (see text)|yes}[]
    \DeclareSpellDescription{Rend Body II}{This spell functions as per rend body I, but the target takes 1d8 points of damage per caster level you have (maximum 10d8). This spell can be undercast.}
        
\DeclareSpell{Rend Body III}{evocation () []|S|1 full-round action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|instantaneous|Fortitude partial (see text)|yes}[]
    \DeclareSpellDescription{Rend Body III}{This spell functions as per rend body I, but the target takes 1d8 points of damage per caster level you have (maximum 15d8), and if a limb is ripped from its body, the target is sickened for as long as the bleed damage persists. This spell can be undercast.}
        
\DeclareSpell{Rend Body IV}{evocation () []|S|1 full-round action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|instantaneous|Fortitude partial (see text)|yes}[]
    \DeclareSpellDescription{Rend Body IV}{This functions as per rend body III, but the target takes 1d8 points of damage per caster level (maximum 20d8), and one of the target's limbs is ripped off if the amount of damage dealt is greater than 1/4 of its maximum hit point total. This spell can be undercast.}
        
\DeclareSpell{Sensory Overload}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets1 creature|1 round /level|Will negates (see text)|yes}[]
    \DeclareSpellDescription{Sensory Overload}{You overload the target creature's senses, making it difficult for the target to concentrate. For the duration of the effect, the target must succeed at a Will save at the same DC as the original effect to perform any standard or full-round action. On a failure,  the creature loses the action that triggered the saving throw. If successful, the creature is able to take the action, but this spell effect is not negated.}
        
\DeclareSpell{Telekinetic Strikes}{evocation () [force]|V,  S|1 standard action|touch|Targetsone creature|1 minute/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Telekinetic Strikes}{The touched creature's limbs are charged with telekinetic force. For the duration of the spell, the target's unarmed attacks or natural weapons deal an additional 1d4 points of force damage on each successful unarmed melee attack.}
        
\DeclareSpell{Thought Worm I}{enchantment (compulsion) [mind-affecting]|S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Thought Worm I}{You implant a minor suggestion within the target creature's psyche that makes it less inclined to resist mental intrusion. The target creature takes a -2 penalty on Will saves against all mind-affecting spells and effects for the duration of the spell.}
        
\DeclareSpell{Thought Worm II}{enchantment (compulsion) [mind-affecting]|S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Thought Worm II}{This spell functions as per thought worm I, but the penalty on Will saves is -4. This spell can be undercast.}
        
\DeclareSpell{Thought Worm III}{enchantment (compulsion) [mind-affecting]|S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round/level|Will partial (see text)|yes}[]
    \DeclareSpellDescription{Thought Worm III}{This functions as per thought worm II, except a target that succeeds at its Will save still takes a -2 penalty on Will saves against your mind-affecting spells and effects for the same duration. This spell can be undercast.}
        
\DeclareSpell{Thought Worm IV}{enchantment (compulsion) [mind-affecting]|S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round/level|Will partial (see text)|yes}[]
    \DeclareSpellDescription{Thought Worm IV}{This functions as per thought worm III, except that the penalty on Will saves is -6 and a target that succeeds at its Will save still takes a -3 penalty on Will saves against your mind-affecting spells and effects for the same duration. This spell can be undercast.}
    