    
\DeclareSpell{Ascension}{universal () []|V,  S,  F (minor artifact),  M (10, 000 gp in rare herbs,  gems, M|1 hour|close (25 ft. + 5 ft./2 levels)|Targetsone non-mythic creature/3 levels|2 hours/level; see text|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Ascension}{You imbue a number of creatures with mythic power, granting each of them 1st tier in a mythic path of its choice. The creatures immediately gain the benefits of their chosen paths. Divide the duration evenly among all targets.  The targets retain their mythic tier only while they're within 100 feet of the spell's focus component. A target that goes outside this range loses its mythic tier, but instantly regains it if it moves into range again. If the focus component is destroyed while the spell is in effect, the spell immediately ends and all targets gain 1d4 permanent negative levels.}
        
\DeclareSpell{Bleed Glory}{necromancy () [curse]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone mythic creature|1 minute/level|Will negates|yes}[]
    \DeclareSpellDescription{Bleed Glory}{The mythic power cost for all path abilities, feats, spells, and other effects used by the target increases by 1.}
        
\DeclareSpell{Deathless}{necromancy () []|V,  S|1 standard action|touch|Targetsliving creature touched|1 round/level|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Deathless}{The target's soul is strongly anchored to its body, preventing death from hit point damage. No matter how low the target's hit points get, it remains alive (though not necessarily conscious).  This spell doesn't prevent death from sources other than hit point damage-such as Constitution damage or drain, death effects, or energy drain. Spells that cure hit points affect the creature normally.}
        
\DeclareSpell{Lend Path}{transmutation () []|V,  S|1 standard action|touch|Targetscreature touched|10 minutes/level (D)|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Lend Path}{You temporarily transfer one of your mythic path abilities to another creature, which can use it as if it were part of the creature's own path. If the target is unable to expend mythic power, it can't activate any part of the ability that requires expending uses of mythic power, but the ability otherwise functions as if the creature were 1st tier.  While your path ability is transferred in this way, you can't use it yourself (even if it's an automatic ability or one that doesn't require expending uses of mythic power).}
        
\DeclareSpell{Mythic Severance}{necromancy () [curse]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|permanent|Will negates|yes}[]
    \DeclareSpellDescription{Mythic Severance}{You restrict the target's access to its mythic power. Each time the target attempts to cast a mythic spell, expend mythic power to activate a path ability, or use any other effect that requires expending uses of mythic power, it must attempt a Will saving throw against the DC of this spell. If it fails this saving throw, the creature loses its action and the ability it was attempting to use has no effect.  This spell has no effect on mythic abilities that don't require the target to expend mythic power.}
        
\DeclareSpell{Restore Mythic Power}{transmutation () []|V,  S|1 standard action|touch|Targetsyou and one mythic creature|instantaneous|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Restore Mythic Power}{By laying your hands on the target, you're able to transfer some of your mythic essence to the target. You expend three uses of your mythic power to restore one use of the target's mythic power.}
        
\DeclareSpell{Share Glory}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone non-mythic creature/3 levels|1 minute/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Share Glory}{You imbue the targets with a fraction of your mythic nature. They count as mythic creatures for the purpose of path abilities, spells, and other effects that function differently for mythic creatures. This doesn't grant the targets mythic tiers or any uses of mythic power; it merely gives them a greater advantage when others use abilities that work differently for mythic creatures. You must be at least a 1st-tier mythic character to cast this spell.}
        
\DeclareSpell{Steal Power}{necromancy () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone mythic creature|instantaneous|Will negates|yes}[]
    \DeclareSpellDescription{Steal Power}{You sap the power from a mythic creature, using it to restore your own. The target loses 1d4 uses of mythic power. If you have the ability to expend mythic power, you regain one use for each use the target loses.}
        
\DeclareSpell{Terraform}{transmutation () []|V,  S,  M (10, 000 gp worth of precious minerals,  see text)|1 hour|100 feet|Area100-foot-radius emanation, centered on you|1 day/level (see text)|none|no}[]
    \DeclareSpellDescription{Terraform}{You alter the area's terrain and climate to a new terrain and climate type appropriate to the planet or plane. For example, you might transform a desert to plains. To cast this spell, you must expend 10 uses of mythic power along with the material cost. This magically alters the area's climate and normal plants to those appropriate to the new terrain, but doesn't affect creatures or the configuration of the earth. Transforming rocky hills into forested areas converts grasses into shrubs and small trees, but doesn't flatten the hills or change the animals to suit the new environment.  You can alter the climate by one step (warm, temperate, or cold). The maximum extent of the terrain change is up to the GM, but in general is to a similar terrain type or one step within that terrain type (such as from a typical forest to a forest with massive trees or light undergrowth, from a shallow bog to a deep bog, and so on). You might be able to shift the land to a similar terrain type, such as turning a sparse forest into a relatively dry swamp. Local creatures adversely affected by these alterations either flee the area or quickly die, depending on their mobility and awareness of the change.  Multiple castings of the spell in the same area can create an area with radically different terrain and climate than the surrounding land. The GM can decide that certain terrain shifts are unsustainable and shorten the duration, or that some are suitable for the area and extend the duration.  This spell could have many secondary effects based on the nature of the change, the type of bordering terrain, and so on; these should be determined by the GM on a case-by-case basis. For example, transforming a desert requires drawing water up from underground to sustain the plants, which could deplete the water table in nearby areas. Creating a warm desert in the middle of a snowy tundra will create a bordering area of mud and frequent storms from the clash of hot and cold air fronts.  If you're at least 8th tier, you can expend 20 uses of mythic power instead of 10 to increase the range to 1 mile, the area to a 1-mile-radius emanation centered on you, and the duration to 1 month per caster level.}
    