    
\DeclareSpell{Guarding Knowledge}{abjuration () []|V,  S,  M/DF (see text)|1 standard action|personal|Targetsyou|1 minute/level (D)||}[]
    \DeclareSpellDescription{Guarding Knowledge}{Upon casting this spell, choose a specific variety of monster (red dragon rather than dragon) and one of its special attacks that you have successfully identified with a Knowledge check or otherwise researched, such as a cockatrice's petrification ability or a spider swarm's poison. You gain a +4 insight bonus on saving throws against the selected special attack. The bonus does not apply to saves against other monsters' abilities of the same name, spell-like abilities, or special attacks derived from class levels or equipment. If you use a trophy from a monster of the exact same variety as an optional material component, the bonus increases to +6.}
        
\DeclareSpell{Huntmaster's Spear}{transmutation () []|V,  S,  M/DF (see text)|10 minutes|touch|Targetsnonmagical spear touched|24 hours or until discharged|Will negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Huntmaster's Spear}{Choose one creature type (and subtype, if applicable) from the ranger's favored enemy list. When you cast this spell, the targeted spear hums with destructive energy and functions as a +1 spear against creatures of the selected type.  You can discharge this spell in order to make an especially powerful attack with the spear. The spear's critical range becomes 18-20 and its critical multiplier becomes x3. If you make this attack as part of a charge action, you gain an enhancement bonus of +30 feet to your base speed while performing the charge. If you throw the spear as part of this attack, its range increment increases to 80 feet. If you cast this spell on a masterwork spear, it also gains the bane special ability against the selected creature type and automatically bypasses any damage reduction (except DR/-) regardless of the creature's type. After resolving the attack, the spear is completely destroyed in a burst of energy.  Any creature other than you treats the spear as a normal weapon of its type. You can have only one huntmaster's spear in effect at a time. If you cast the spell again, any previous instance of the spell immediately ends. If you expend a monster trophy of the type selected as an optional material component for this spell, you reduce the casting time to 1 round.}
        
\DeclareSpell{Protection From Natural Attacks}{abjuration () []|V,  S,  M/DF (a scale from a lizard)|1 standard action|touch|Targetscreature touched|1 minute/level|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Protection From Natural Attacks}{Upon casting this spell, select one type of natural attack from the following: bite, claw, gore, hoof, pincers, slam, sting, swarm, tail slap, talon, tentacle, or wing. For the duration of the spell, the target gains DR 5/- against all attacks from natural weapons of the selected type.}
        
\DeclareSpell{Repugnant Taste}{transmutation () [poison]|V,  S,  M/DF (mustard seed)|1 standard action|touch|Targetscreature touched|10 minute/level|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Repugnant Taste}{The target creature begins sweating a foul liquid that makes it repugnant to most living creatures. When a creature deals damage to the affected creature with a bite attack or the swallow whole ability, it must succeed at a Fortitude saving throw or become nauseated until the end of its next turn. After a creature has become nauseated by this spell, each subsequent failed saving throw against the spell instead gives it the sickened condition until the end of its next turn.}
    