    
\DeclareSpell{Aura Of Inviolate Ownership}{abjuration () []|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature/level, no two of which can be more than 30 ft. apart|1 round/level|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Aura Of Inviolate Ownership}{This spell wards the attended items of all creatures it targets (items held, securely fastened to their person, or in containers on their person), enhancing each creature's grip and protecting items from loss or theft. The DC of Sleight of Hand checks to remove items warded by the spell is increased by 20, and affected creatures gain a +20 bonus to their CMDs against disarm and steal combat maneuvers.}
        
\DeclareSpell{Blade Tutor's Spirit}{conjuration (creation) []|V,  S|1 standard action|personal|Targetsyou|1 minute/level||}[]
    \DeclareSpellDescription{Blade Tutor's Spirit}{You summon an insubstantial spirit of force that resembles a cloudy vapor hovering around your fists or any melee weapons you wield. The spirit compensates for your defensive or reckless melee attacks, nudging your weapons in the proper direction. When you voluntarily use one or more actions or feats that apply penalties to attack rolls with your melee weapons (such as a charge, fighting defensively, or using the Power Attack feat), the spirit reduces the total penalty on affected attacks by 1 (to a minimum penalty of 0). The penalty is reduced by an additional 1 for every 5 caster levels you possess (to a minimum penalty of 0). Only penalties incurred by voluntary use of feats or maneuvers are reduced by this spell.  The spirit can't be attacked or harmed by physical attacks, but disintegrate, dispel magic, a rod of cancellation, or a sphere of annihilation can affect it. A protective spirit's AC against touch attacks is equal to 10 + your Dexterity modifier.}
        
\DeclareSpell{Darting Duplicate}{illusion (figment) []|V,  S|1 swift action|5 ft.|Effectvisual figment of the caster|instantaneous|Will negates|yes}[]
    \DeclareSpellDescription{Darting Duplicate}{An illusory duplicate of you steps clumsily into an adjacent square, presenting a tempting target before winking out of existence. Any creature that threatens that square must succeed at a Will save or make an attack of opportunity against the image. The image's AC is equal to 10 + 1/2 your caster level, but as a figment, the image is unaffected by any attack.}
        
\DeclareSpell{Dimensional Blade}{transmutation () []|V,  S|1 swift action|personal|Targetsyou|1 round||}[]
    \DeclareSpellDescription{Dimensional Blade}{This spell gives you the power to turn one melee weapon in your hand into a two-dimensional object with length and height but no width. A sword becomes a flat image of a sword, a mace is reduced to a flat outline, and so on. The magic of the spell allows the weapon to be wielded by you normally, creating just enough depth to grasp it.  Attacks made with the weapon are melee touch attacks that ignore all armor. Force effects, such as mage armor and shield, still apply their AC against attacks made with a dimensional blade. Bludgeoning weapons used to make attacks with this spell deal half damage and are treated as slashing weapons. If the weapon leaves your hand before the end of the spell, the effect ends.}
        
\DeclareSpell{Fiery Runes}{evocation () [fire]|V,  S|1 standard action|touch|Targetsmelee weapon touched|1 minute/level or until discharged (see text)|none|yes (see text)}[]
    \DeclareSpellDescription{Fiery Runes}{You charge a weapon with a magic rune of fire. When the wielder of the weapon successfully strikes a foe in melee with the weapon, the wielder can discharge the rune as a swift action to deal 1d4+1 points of fire damage to the target. This damage isn't multiplied on a critical hit. If the target has spell resistance, you attempt a caster level check (1d20 + caster level) against that spell resistance when the rune is discharged. If the rune is successfully resisted, the spell is dispelled; otherwise, the rune deals damage normally.  For every 2 caster levels beyond 3rd the caster possesses, the rune deals an additional 1d4+1 points of fire damage (2d4+2 at caster level 5th, 3d4+3 at 7th, and so on) to a maximum of 5d4+5 points of fire damage at caster level 11th.}
        
\DeclareSpell{Instant Weapon}{conjuration (creation) [force]|V,  S|1 standard action|0 ft.|Effectmelee weapon of opaque force|1 minute/level||}[]
    \DeclareSpellDescription{Instant Weapon}{You create a melee weapon sized appropriately for you from opaque force. You are considered proficient with this weapon, which acts in all ways as a masterwork weapon typical of its type. The instant weapon has hardness 20 and the same number of hit points as a typical weapon of its type. As a force effect, it can strike and damage incorporeal creatures. If the instant weapon leaves your hand at any time, the spell ends at the beginning of your next turn.}
        
\DeclareSpell{Reaper's Coterie}{necromancy () [evil]|V,  S,  DF|1 standard action|touch|Targetsweapon touched|1 round/level|none|no}[]
    \DeclareSpellDescription{Reaper's Coterie}{The target weapon becomes a reservoir of spiritual energy, fueling its destructive power by drawing in a tiny fragment of the essence of each creature it is used to defeat. When the targeted weapon is used to reduce a living creature to 0 or fewer hit points, it gains a +1 profane bonus on damage rolls. This bonus increases by 1 for each creature reduced to 0 hit points or fewer with that weapon, up to a maximum bonus equal to 1/2 your caster level.}
        
\DeclareSpell{Umbral Weapon}{illusion () [cold,  shadow]|V,  S,  M (a pair of miniature swords)|1 standard action|touch|Targetsmelee weapon touched|1 round/level|none|yes}[]
    \DeclareSpellDescription{Umbral Weapon}{A shadowy afterimage trails behind the targeted weapon, potentially damaging foes even when the weapon misses. Once per round, when the weapon's wielder misses a creature with the target weapon, the wielder can reroll the attack. If the reroll hits, the spell hits the targeted creature and deals 1d8 points of cold damage, plus 1 additional point per 2 caster levels (maximum +10). If an attacked creature has spell resistance, you must attempt a caster level check (1d20 + caster level) against that spell resistance the first time the spell damages the target. If the creature successfully resists umbral weapon, the spell is dispelled. If not, the creature takes damage as normal.}
    