    
\DeclareSpell{Alleviate Addiction}{conjuration (healing) []|V,  S,  DF|1 standard action|touch|Targetscreature touched|1 hour/level|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Alleviate Addiction}{The subject ignores the effects of addictions. The subject can naturally recover from damage dealt by the drug if she is under the effects of this spell for the entire duration of her rest.}
        
\DeclareSpell{Contact High}{transmutation () []|V,  S|1 standard action|touch|Targetsliving creatures touched (up to one per level)|1 round/level|Fortitude negates|yes}[]
    \DeclareSpellDescription{Contact High}{While under the effects of a drug, you can duplicate those effects in others. You can touch another creature once per round (this requires a melee touch attack if the target is unwilling). When touched, the target begins experiencing the effects of the same drug by which you are currently affected (select one, if you are under the influence of more than one drug). The target doesn't take any ability damage or risk addiction from the drug.  You cannot impart the effects of any potion, poison, elixir, or mutagen currently affecting you.}
        
\DeclareSpell{Imbue With Addiction}{transmutation () []|V,  S,  M (a dose of an addictive drug or substance)|1 standard action|touch|Targetsone living creature|instantaneous|Fortitude negates|yes}[]
    \DeclareSpellDescription{Imbue With Addiction}{The target immediately becomes addicted to the drug used as the material component during the casting of the spell. If the target was ever addicted to the drug at any point in the past, it takes a -4 penalty on its saving throw.}
        
\DeclareSpell{Night Blindness}{necromancy () [curseUM]|V|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone living creature|1 day/level (D)|Will negates (harmless)|no}[]
    \DeclareSpellDescription{Night Blindness}{Your target's vision becomes impaired as if the light level were one step lower, treating bright light as normal light, normal light as dim light, and dim light as darkness. In addition, the subject gains no benefit from darkvision, low-light vision, or the see in darkness ability. The subject gains a +4 bonus on saving throws to resist the blind or dazzled condition caused by bright light (such as flare). Remove blindness/deafness dispels night blindness.}
        
\DeclareSpell{Pesh Vigor}{transmutation () []|V,  S,  M (a dose of pesh worth 15 gp)|1 standard action|touch|Targetsliving creature touched|1 round/level; see text|Will negates|yes}[]
    \DeclareSpellDescription{Pesh Vigor}{The target gains a +2 enhancement bonus to its Strength. Once per round as a free action, the target can choose to increase the enhancement bonus by 2 for 1 round; if it does so, it takes 1d6 points of nonlethal damage and the spell's duration decreases by 1 additional round. For every 5 caster levels you have, the target can choose to increase the enhancement bonus by an additional 2, taking an additional 1d6 points of nonlethal damage and decreasing the duration by 1 additional round per increase to the Strength bonus, to a maximum enhancement bonus of +10 and 4d6 points of nonlethal damage at caster level 15th. The subject can't spend more rounds than remain in the duration. When the spell ends, the subject becomes fatigued.}
        
\DeclareSpell{Compel Tongue}{enchantment (compulsion) [mind-affecting]|V,  S,  M (a wooden block carved with a letter)|1 standard action|touch|Targetsone creature|1 hour/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Compel Tongue}{This spell functions as share language (Pathfinder RPG Advanced Player's Guide 243), granting a creature the ability to read, understand, and communicate to the best of its ability in any one language you know. For the spell's entire duration, the target can speak and write only in the language imparted, but its ability to understand other languages is unaffected.}
        
\DeclareSpell{Compel Tongue, Mass}{enchantment (compulsion) [mind-affecting]|V,  S,  M (a wooden block carved with a letter)|1 standard action|touch|Targetsone creature/level, no two of which can be more than 30 ft. apart|1 hour/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Compel Tongue, Mass}{This spell functions as compel tongue, except it affects multiple creatures. The same language restriction applies to all creatures, and the same language must be imparted to all creatures affected by the same casting of this spell.}
        
\DeclareSpell{Fleeting Memory}{enchantment (compulsion) [mind-affecting]|V|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round/level (D)|Will partial|yes}[]
    \DeclareSpellDescription{Fleeting Memory}{You create a gap in the target's memory, preventing the target from remembering anything that happens from the moment you cast this spell until the moment its complete duration ends. Fleeting memory doesn't wipe out its target's memories until the end of its duration, so the target can remember the preceding rounds until the spell's duration ends. If the spell ends prematurely, either because you dismiss it or because it is dispelled, it disperses without affecting its target's memory.  Whether or not the target's save is successful, the target forgets that you cast a spell.}
        
\DeclareSpell{Fleeting Memory, Mass}{enchantment (compulsion) [mind-affecting]|V|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature/level, no two of which can be more than 30 ft. apart|1 round/level (D)|Will partial|yes}[]
    \DeclareSpellDescription{Fleeting Memory, Mass}{This spell functions as fleeting memory, except that it affects multiple creatures.}
        
\DeclareSpell{Secret Sign}{illusion (glamer) []|V,  S,  M (a lemon peel)|1 standard action|touch|Targetsone creature or object|1 day/level|Will negates (object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Secret Sign}{You invisibly inscribe a small mark or short message (no more than 25 words) on a creature or object, similar to the way arcane mark works. The sign can be no more than 6 inches across, and if it's a written message, it can be in any language you can read and write at the time of the spell's casting. As you cast the spell, you can define one auditory, olfactory, tangible, or visual criterion-such as all creatures wearing green bands on their left arms or only creatures who smell of lavender or only orcs-that allows designated creatures within 30 feet to see the secret sign.  Disguises and illusions that mimic the set criterion can fool this spell. Normal darkness doesn't conceal a visual trigger, but magical darkness or invisibility does. Auditory criteria (such as a password) and tangible criteria (such as pressing your hand against a specific object or wall) can be performed by anyone who learns of them. A secret sign cannot distinguish alignment, level, Hit Dice, or class except by external garb, but can differentiate apparent races, genders, and garments. See invisibility and invisibility purge reveal the sign, but glitterdust does not.  A caster of at least 10th level can make secret sign permanent on an object with a permanency spell using 5,000 gp of diamond dust as a material component.}
        
\DeclareSpell{Venomous Promise}{transmutation () [language-dependent,  poisonUM]|S,  M (a vial of poison)|1 standard action|touch|Targetsone creature|permanent or until triggered|yes|yes}[]
    \DeclareSpellDescription{Venomous Promise}{You guard your words and person with poisonous power. You can impart a short amount of information-up to 25 words-as you cast this spell, entwining your words with the poison provided as a material component. If your target reveals the information you impart (verbally, in writing, with gestures, or by having its mind read with spells like detect thoughts), the target is immediately exposed to the poison (and is allowed any saving throw the poison allows).  Your target instinctively knows that revealing this information will endanger it, but doesn't automatically understand why or how. Neutralize poison removes the effect of this spell; the spellcaster must succeed at a caster level check against the spell's save DC rather than the poison's.}
        
\DeclareSpell{Arcane Pocket}{conjuration (creation) []|V,  F (a pocket and a silver button)|1 standard action|touch|Effectextradimensional space up to 1 cu. ft./level|1 hour/level|none|no}[]
    \DeclareSpellDescription{Arcane Pocket}{With a touch, you conjure an extradimensional space inside a pouch or pocket. The pocket acts as a bag of holding, except it can hold only 10 pounds per caster level. Regardless of what is placed into the pocket, it weighs 3 pounds. Unlike a bag of holding, the pocket created by this ability cannot be overloaded or ruptured-any additional material simply spills out of the top-nor does it have any special interaction with other kinds of extradimensional spaces.  An arcane pocket grants you a +1 bonus on Sleight of Hand checks to conceal its contents. The pocket becomes nonmagical, spilling all of its contents onto the ground unharmed, if it leaves your possession or you create a new arcane pocket.}
        
\DeclareSpell{Vacuous Vessel}{illusion (glamer) []|V|1 swift action|touch|Targetscontainer touched|1 round/level (D)|Will negates; see text|yes; see text}[]
    \DeclareSpellDescription{Vacuous Vessel}{This spell makes a single bag, chest, sack, or other container look and feel empty. The container must be no larger than 1 cubic foot per caster level or the spell fails. Anyone peering into or reaching into the container must succeed at a Will save or perceive the container as being completely empty. All items within the container when the spell was cast are still present, but they can't be noticed unless removed from the bag-such as by someone who can perceive them, or who upends the container.  Casting vacuous vessel on another container or placing a new item in the existing container immediately dismisses the currently active spell.}
        
\DeclareSpell{Adroit Retrieval}{transmutation () []|V,  S|1 standard action|touch|Targetscreature touched|1 minute/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Adroit Retrieval}{You instill the target with the ability to withdraw small items from her pockets or packs with supernatural swiftness. When the target retrieves an item stored on itself, it can retrieve  the item either as a move action without provoking attacks of opportunity, or as a swift action that provokes attacks of opportunity. This effect functions only when the target attempts to retrieve a stored item that weighs less than 1 pound per caster level (maximum 15 pounds).}
        
\DeclareSpell{Curse Of Keeping}{enchantment (compulsion) [curseUM]|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 day/level|Will negates|yes}[]
    \DeclareSpellDescription{Curse Of Keeping}{You curse the target with the inability to sell, barter, or give away any item it owns, other than ordinary currency, for as long as the spell remains in effect. The target cannot sell, trade, drop, or give away possessions. The target can purchase items using ordinary currency but can't then sell the purchased items. The target can accept gifts from others but can't offer anything in exchange. A curse of keeping can be ended by break enchantment, limited wish, remove curse, miracle, or wish. Dispel magic does not affect a curse of keeping.}
        
\DeclareSpell{Fleeting Defect}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone solid object that does not have the broken condition, or one construct|1 minute/level (D)|Fortitude negates (harmless, object); see text|no}[]
    \DeclareSpellDescription{Fleeting Defect}{You cause a single object to temporarily gain the broken condition. The target must be a single solid object, regardless of its composition, weighing up to 10 pounds per caster level. Attended objects are allowed a Fortitude save. When this spell ends, the object reverts to its original quality. An item destroyed while under the effects of this spell remains destroyed when this spell ends.  This spell can be cast on a single construct to disrupt its animating force. A construct that fails its saving throw takes a -2 circumstance penalty on attack rolls, saving throws, skill checks, and ability checks for the duration of the spell.}
        
\DeclareSpell{Incendiary Runes}{abjuration () [fire]|V,  S|1 standard action|touch|Targetsone touched object weighing no more than 10 lbs.|permanent until discharged (D)|Reflex partial|yes}[]
    \DeclareSpellDescription{Incendiary Runes}{This spell functions as explosive runes, except it creates a small surge of flames rather than an explosion of force. The runes automatically deal 1d6 points of fire damage to any creatures and objects in adjacent squares, and those creatures and objects catch fire unless they succeed at Reflex saves.}
        
\DeclareSpell{Peerless Integrity}{illusion (glamer) []|V,  S,  DF|1 standard action|personal|Area10-ft.-radius emanation centered on you|10 minutes/level|none or Will negates; see text|none}[]
    \DeclareSpellDescription{Peerless Integrity}{Peerless integrity conceals the alignment of creatures from divination magic. All creatures within the spell's area, including you, appear to have lawful good auras for the purposes of divination spells and effects that reveal alignments (such as detect law and see alignmentUC), instead of their actual alignments. If the caster of such divination magic succeeds at a Will save, the caster recognizes whether the readings are true or false. Any creature under the effects of this spell gains a +2 circumstance modifier on Bluff and Diplomacy checks.  This spell does not affect other types of divination magic (such as detect thoughts or discern lies) and does not protect against spells or effects that cause harm based on targeted creatures' alignments.}
        
\DeclareSpell{Remarkable Legerdemain}{transmutation () []|V,  S|1 standard action|personal|Targetsyou|1 minute/level (D)||}[]
    \DeclareSpellDescription{Remarkable Legerdemain}{While this spell is in effect, your body and clothing flutter and distort subtly, allowing you to conceal items with uncanny skill. You treat any object you can hold in one hand as a coin-sized object for the purposes of Sleight of Hand checks to palm the object or make it disappear; however, you can hide only one such item per caster level on your person at one time. This effect does not change the actual sizes of the objects.}
        
\DeclareSpell{Secret Coffer}{conjuration (summoning) []|V,  S,  F (the chest and its replica)|10 minutes|see text|Targetsone small chest or coffer and up to 1 cu. ft. of goods|60 days or until discharged|none|no}[]
    \DeclareSpellDescription{Secret Coffer}{This spell functions like secret chest, except the coffer is only 1 foot square and can contain only 1 cubic foot of goods, and the container can remain safely hidden on the Ethereal Plane for only 14 days before it risks becoming lost. The spell automatically fails if a living creature enters the coffer. The coffer used as a focus for secret coffer must cost at least 500 gp, and its replica costs 5 gp.}
        
\DeclareSpell{Secret Vault}{conjuration (summoning) []|V,  S,  F (the chest and its replica)|10 minutes|see text|Targetsone chamber and up to 10 cu. ft. of goods/caster level|60 days or until discharged|none|no}[]
    \DeclareSpellDescription{Secret Vault}{This spell functions like secret chest, except it affects a small structure, vault, or oversized chest. Living creatures within a secret vault don't cause the spell to fail. While the vault is stored on the Ethereal Plane, living creatures within the vault don't need to eat, drink, or breathe, but they can't leave the vault except via magic such as plane shift. The vault used as a focus for secret vault must cost at least 25,000 gp, and its replica costs 250 gp. A secret vault has only a 1\% cumulative chance per day of becoming irretrievably lost after 360 days.}
    