    
\DeclareSpell{Alter River}{transmutation () [water]|S,  V,  M (silt from a dry riverbed)|1 standard action|medium (100 ft. + 10 ft./level)|Targetsarea of river up to 5 ft. wide/2 levels and 10 ft. long/level|1 minute/level (D)|none|no}[]
    \DeclareSpellDescription{Alter River}{You alter the flow of water in a natural freshwater channel such as a river, stream, or waterfall. The first version of this spell alters the speed of a river's flow. The second diverts the course of the targeted river.
Alter Current: The river's current increases or decreases in speed by up to 1 mile per hour per 2 caster levels you possess. A typical placid river travels at a rate of up to 2 mph (no effect on local movement); a swift river travels 2-4 mph, moving creatures and objects 10 to 40 feet downstream per round; and an area of river rapids travels 7-10 mph, moving creatures and objects 60 to 90 feet downstream per round. Altering the speed of the current alters the difficulty of swimming in the water accordingly.
Divert River: The river diverts its course in a direction of your choosing. The river flows in the general direction indicated, but otherwise conforms to the shape of the local terrain. This spell cannot cause a river to flow uphill, though the river surges over its natural banks and inundates terrain lower than its average depth. Creatures in the path of the redirected river are in danger of being swept away; if directed properly, this spell causes a flood. See Aquatic Terrain on page 432 of the Core Rulebook for more details.
Alter river can be made permanent with a permanency spell.
Clever application of spells such as move earth can be combined with this spell to likewise make the river's new course permanent.}
        
\DeclareSpell{Detect Metal}{divination () []|V,  S,  F (a magnetized nail or nugget of ore)|1 standard action|60 ft.|Areacone-shaped emanation|concentration, up to 1 minute/level (D)|none|no}[]
    \DeclareSpellDescription{Detect Metal}{You detect any metal objects or creatures within a 60-foot cone.
You can specify all metal objects or one or more specific types of metal (such as silver, cold iron, or a type of skymetal) when you cast this spell; in the case of the latter, you detect only objects or creatures made of the specified metal.}
        
\DeclareSpell{Hanspur's Flotsam Vessel}{conjuration (creation) []|V,  S,  M (driftwood branch or river rat's tail)|1 minute|close (25 ft. + 5 ft./2 levels)|Effectraft large enough for caster and one passenger/2 levels|1 hour/level (D)|none|no}[]
    \DeclareSpellDescription{Hanspur's Flotsam Vessel}{This spell assembles a sturdy raft and oars from driftwood, reeds, and other river detritus. The smallest raft created by the spell is roughly 5 feet square, increasing by an additional 5 feet square for every 2 caster levels you possess. Each 5-foot section of the raft can carry two Medium passengers or 300 pounds of cargo. The vessel functions as a normal raft, except it is not slowed or damaged by nonmagical river hazards such as rapids or shallows, and it is always considered to be traveling downstream for the purpose of calculating travel speed, regardless of its actual direction.}
        
\DeclareSpell{Magnetic Field}{abjuration () []|V,  S|1 standard action|30 ft.|Area30-ft.-radius emanation|1 round/2 levels (D)|Reflex negates (object; see text)|yes (object)}[]
    \DeclareSpellDescription{Magnetic Field}{You create a spherical magnetic field that surrounds you to a range of 30 feet and follows you for the duration of the spell.
Unattended metal objects in range-including weapons, armor, and anything made primarily out of metal-are pulled violently toward you, stopping just short of your space and falling harmlessly to the ground. Objects secured to a nonmetallic fixture remain where they are unless a forceful tug would be enough to detach them. Loose objects weighing more than 500 pounds are not affected. If the magnetic field would cause a dangerous metal object such as a sword or anvil to intersect a square occupied by a creature, that creature must succeed at a Reflex save or take damage as if from an improvised weapon of the object's size (or smaller or larger, at the GM's discretion).
A creature in the area wearing metal armor, wielding a metal weapon, or holding a metal object must succeed at a Reflex save or be dragged 5 feet closer to you in a straight line, as if affected by the pull universal monster rule (Bestiary 303). A creature can drop a metal object it's holding as a free action to avoid the effect if it's not wearing metal armor; a creature being dragged by its shield can loosen it as a move action and drop it as a free action. Creatures made entirely or mostly of metal take a -2 penalty on their Reflex saves. Creatures that fail their saves by 5 or more are pulled an additional 5 feet closer for every increment of 5 by which they failed their saves.}
        
\DeclareSpell{Resounding Clang}{transmutation () []|S,  F (bell,  chimes,  gong,  or cymbals)|1 standard action|30 ft.|Area30-ft.-radius burst, centered on you|1 round/level|Reflex negates|yes (object)}[]
    \DeclareSpellDescription{Resounding Clang}{You create a loud, resonating clangor that causes metallic objects to vibrate wildly. Affected creatures wielding metal weapons take a -1 penalty on attack rolls, while creatures using metallic tools take a -1 penalty on associated skill checks.
Creatures wearing metal armor increase the armor check penalty of their armor by 1. These penalties increase by 1 at 8th caster level and every 4 caster levels thereafter (to a maximum of -4 at 16th level).
To be affected by the spell, an item must be composed primarily of metal. Nonmetallic objects with metal components (such as studded leather armor or padded armor with armor spikes) are not affected. Creatures made of metal take the penalties described above on attack rolls, damage rolls, skill checks, and Reflex saves.}
        
\DeclareSpell{Riversight}{divination (scrying) []|V,  S,  F/DF (a smooth river stone)|1 minute|see text|Effectmagical sensor|1 minute/level (D)|none|no}[]
    \DeclareSpellDescription{Riversight}{You can view events transpiring along a natural watercourse you touch. You can see anything on or within the river as if you were present at that location, or you can observe anything happening within 15 feet of the river's banks as if peering from the water's surface. Moving your point of view to a different location along the river is a standard action, though your perception can follow something moving along the river as a free action.
The range of this spell is affected by whether you are attempting to gaze up or downriver-if viewing a location downriver, you can view any spot within 2 miles per caster level; if viewing upriver, you can view any spot within 1/2 mile per caster level. The magical sensor created by this spell can travel only as far along the river as your range and the river permits; obstructions such as dams and reservoirs halt the sensor, as does an estuary flowing into the sea or other body of saltwater.}
    