    
\DeclareSpell{Abadar's Truthtelling}{enchantment (compulsion) [mind-affecting]|V,  S,  DF|1 standard action|touch|Targets: creature touched|1 min./level|Will negates|yes}[]
    \DeclareSpellDescription{Abadar's Truthtelling}{This spell functions identically to the spell zone of truth, except as noted above. The target momentarily takes on the semblance of a being of perfect order, like an archon or inevitable, so that all who can see the target know it is affected by the spell. This divine guise flickers over the target for only an instant and does not allow it to pass as a member of a different race.}
        
\DeclareSpell{Abstemiousness}{transmutation|V|1 standard action|touch|Targets: a handful of berries, grains, nuts, or rice|1 hour|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Abstemiousness}{Sometimes Irori smiles on his worshipers, granting them a reprieve from physical hunger. This spell magically enhances a handful of simple food, imbuing it with enough nutrition to satisfy a Medium or smaller creature for a full day. The spell does not create food, and thus will not alone prevent someone from starving, but it can extend even limited reserves for lengthy periods.}
        
\DeclareSpell{Baphomet's Blessing}{transmutation (polymorph)|V,  M/DF (powdered bull's horn)|1 standard action|touch|Targets: one living creature|1 round/level|Fortitude negates|yes}[]
    \DeclareSpellDescription{Baphomet's Blessing}{You change the target's head into that of a bull. The creature's Intelligence becomes 2, and it gains a gore melee attack that it can use as a primary or secondary attack. The gore attack uses the creature's base attack bonus, and the creature gains a +2 bonus on attack and damage rolls with the gore attack.

The gore attack deals a number of points of damage equal to 1d6 + Strength modifier if the target is Small, 1d8 + Strength modifier if the target is Medium, and 2d6 + Strength modifier if the target is Large or larger.

The affected creature still retains its type, class, levels, and Hit Dice. The creature's base attack bonus, base save bonuses, and hit points remain unmodified. It retains all of its class features and may still cast spells, though it must do so using its newly modified Intelligence score. Any items equipped in the creature's head slot meld into its body. Affected items that grant passive bonuses continue to do so, though items that require activation become nonfunctional for the duration of the spell.

If the target fails to resist Baphomet's blessing, it also becomes immune to polymorph spells (except for this one) for the duration of the spell's effect. Undead, incorporeal, or gaseous creatures are immune to Baphomet's blessing.}
        
\DeclareSpell{Beacon Of Luck}{divination|V,  S,  M/DF (a tuft of rabbit fur)|1 standard action|personal; see text|Targets: you|1 minute/level (D)||}[]
    \DeclareSpellDescription{Beacon Of Luck}{You send out a burst of luck with a 30-foot radius centered around you. While the beacon of luck  is in effect, you gain a +2 sacred bonus on all saving throws. As an immediate action before a saving throw is made, allies within the area can choose to benefit from this luck, rolling twice for a saving throw and taking the better result. Once a creature benefits from the beacon of luck in this way, it cannot gain the benefit of this spell for 24 hours.}
        
\DeclareSpell{Blade Snare}{abjuration|V,  S|1 standard action|personal|Targets: you|1 round/level|none|no}[]
    \DeclareSpellDescription{Blade Snare}{This spell creates an invisible magic field that does not stop weapons (whether manufactured or natural) from moving toward you, but impedes their motion when they are retracted.

When you are hit with a melee attack, attempt a caster level check against your opponent's CMD. If your check succeeds, your opponent's attacking weapon or body part becomes caught in the field, as if magically affixed to your body. If your check fails, your opponent may retract its weapon.

If your opponent's melee weapon becomes trapped in the field, the opponent may release the weapon and move away from you. If your opponent attacked with a part of its body (such as a fist, a horn, a tail, etc.) or it attacked with a weapon but refuses to release it, your opponent gains the grappled condition. Because you are not using any part of your body to maintain control over your opponent, you do not gain the grappled condition.

Once an opponent's weapon is snared, you may attempt a new caster level check against that opponent's CMD on each of your subsequent turns to maintain the grapple. This is a standard action, during which you may make any of the usual grappling actions, but if you choose to pin the opponent, you gain the grappled condition as well. On your opponent's turn, it may try to retract its weapon or limb by attempting a combat maneuver check or Escape Artist check, the DC of which is equal to the spell's saving throw.

While blade snare is active, you may make melee attacks and cast spells as normal, though you may not make ranged weapon attacks; the magic field thwarts such attacks. You may not snare more than one limb or weapon in the field at a time.

If you already have an opponent's weapon or limb stuck in the field and you are hit by a second melee attack, you must choose which weapon or limb to snare. The other limb or weapon is unaffected by the spell.}
        
\DeclareSpell{Blessing Of The Watch}{enchantment (compulsion) [mind-affecting]|V,  S,  DF|1 standard action|50 ft.|Area: The caster and all allies within a 50-ft. burst, centered on the caster|1 hour/level|none|yes (harmless)}[]
    \DeclareSpellDescription{Blessing Of The Watch}{This spell functions like bless, except as noted. It works only in the caster's home city, and in areas under the jurisdiction of the city watch. For example, if the watch patrols a shantytown outside the city walls but not the ruined subterranean tunnels that lie beneath the city, the spell works in the former area but not the latter.\\\\

{\centering\bf Bless\hrule}

Bless fills your allies with courage. Each ally gains a +1 morale bonus on attack rolls and on saving throws against fear effects.

Bless counters and dispels bane.}
        
\DeclareSpell{Brittle Portal}{transmutation|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Area: 5-ft.-radius spread|1 round/level|Will negates (object)|yes (object)}[]
    \DeclareSpellDescription{Brittle Portal}{This spell weakens the bonds of existence, and reduces the hardness of any nonmagical surface within its area of effect by 2 per caster level. The spell is centered on a flat surface chosen by the caster, and the hardness reduction effect persists for the duration of the spell.}
        
\DeclareSpell{Burst Of Glory}{enchantment (compulsion) [mind-affecting]|V,  S,  DF|1 standard action||Area: 10-ft.-radius burst, centered on you|1 round/level (D; see text)|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Burst Of Glory}{Allies in the area of this spell at the time of casting gain a +1 sacred bonus on attack rolls and saves against fear effects, plus 1 temporary hit point per caster level (maximum 20). You shine with a white or golden radiance equal to a torch for the spell's duration, though you can dismiss the glow effect as a free action.}
        
\DeclareSpell{Caustic Blood}{transmutation [acid]|V,  S,  M (vial of black adder venom)|1 standard action|personal|Targets: you|1 round/level|Reflex half or negates; see text|no}[]
    \DeclareSpellDescription{Caustic Blood}{You imbue your blood with corrosive acid. Any time you take piercing or slashing damage, a spray of acidic blood spurts from your body in the direction of the opponent who inflicted the wound, dealing 1d6 points of acid damage per caster level (maximum 15d6, Reflex half). This spurt travels in a 10-foot line, damaging the first creature or object it touches, with no splash damage. After it contacts a creature or object, your acidic blood continues to burn that creature for 1 round, dealing 1d6 points of acid damage per 2 caster levels (maximum 7d6). A second successful Reflex save negates this additional damage.}
        
\DeclareSpell{Channel The Gift}{evocation|V,  S,  DF|1 standard action|touch|Targets: ally spellcaster touched|1 round or see text|Will negates (harmless) or none|yes (harmless) or no}[]
    \DeclareSpellDescription{Channel The Gift}{You channel your magical power to fuel the target's spellcasting.

The next spell the target casts of 3rd level or lower does not expend a spell slot; in effect, you are using your spell slot to power the target's spell. The target must start casting this spell before your next turn, and the spell cannot have a casting time longer than 1 full round. Your alignment, prohibited wizard school, and other restrictions on your own spellcasting do not affect the target, nor do you suffer any backlash from the target's choice of spell.

If you target yourself with this spell, you may spontaneously cast any prepared spell of 3rd level or lower without expending its spell slot on your next turn (this aspect of the spell has no effect if you are a spontaneous caster). The spell that's cast after channel the gift cannot have a casting time longer than 1 full round.}
        
\DeclareSpell{Channel Vigor}{transmutation|V,  S|1 standard action|personal|Targets: you|1 round/level||}[]
    \DeclareSpellDescription{Channel Vigor}{You focus the energy of your mind, body, and spirit into a specific part of your being, granting yourself an exceptional ability to perform certain tasks. When you cast the spell, choose one of the following portions of your self as your focus target. Thereafter, you may change the focus target as a move action. You can gain the benefit of only one channel vigor spell at a time.

Limbs: You gain the benefits of a haste spell.

Mind: You gain a +4 competence bonus on Knowledge and Perception skill checks and on ranged attack rolls.

Spirit: You gain a +6 competence bonus on Will saving throws and Bluff and Intimidate checks.

Torso: You gain a +6 competence bonus on Fortitude saving throws and concentration checks.}
        
\DeclareSpell{Dead Eye's Arrow}{evocation [electricity]|V,  S,  M (one arrow)|1 standard action|Medium (100 ft. + 10 ft./level) or see text|Effect: arrow of electricity|instantaneous or 1 round (see text)|none|yes}[]
    \DeclareSpellDescription{Dead Eye's Arrow}{You create an arrow made of crackling electricity, which you may use for one of two effects.

Attack: You may throw the arrow up to Medium range or fire it from a bow up to the bow's maximum range. Either use is a ranged touch attack. The arrow deals 1d6 points of electricity damage + 1 point per level (maximum +5).

Beacon: You throw or fire the arrow straight up. When it reaches maximum range or a solid surface (such as the roof of a cave) it explodes in a peal of thunder and forms a forked bolt of electricity resembling Erastil's holy symbol, which lingers for 1 round. The thunder and lightning are as loud and bright as natural thunder and lightning, but they do not harm any nearby creatures.}
        
\DeclareSpell{Defending Bone}{necromancy|V,  S,  F (a Medium creature's skull or femur),  DF|1 standard action|personal|Targets: you|1 hour/level or until discharged||}[]
    \DeclareSpellDescription{Defending Bone}{You animate a bone with necromantic energy, giving it the power to float near your body and interpose itself against physical attacks. This gives you damage reduction 5/bludgeoning.

Once the bone has prevented a total of 5 points of damage per caster level (maximum 50 points), it is destroyed and the spell is discharged. This spell has no effect if you have damage reduction from another source.}
        
\DeclareSpell{Dream Feast}{conjuration (creation)|V,  S,  DF|1 standard action|touch|Targets: creature touched|instantaneous|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Dream Feast}{The next time the target sleeps (within the next 8 hours), she dreams of a rich feast with her favorite foods and drinks. When she awakens, she is sated as if she had eaten a nutritious meal, regardless of what she dreamed she ate. The target must sleep for at least 1 hour to gain the benefits of this spell. Being awakened during this period interrupts the spell and cancels its effects.

If you sleep with this spell prepared, you may automatically expend it while you sleep to gain the spell's benefit. This expenditure does not count as spellcasting for the purpose of determining available spell slots (you could go to sleep at midnight, expend this spell during an 8-hour period of sleep, and still prepare your full allotment of spells in the morning).}
        
\DeclareSpell{Early Judgment}{divination|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one humanoid creature|1d4 rounds|Will negates|yes}[]
    \DeclareSpellDescription{Early Judgment}{You show one creature the effect of its life so far and what it might expect when it passes under Pharasma's impartial gaze at the end of its life. Depending on the creature's alignment and its adherence to its ethos, you can provide it a brief glimpse of the reward or punishment that waits for it when it dies by showing it a mental image of its destined plane in the Great Beyond. If the target is good-aligned, it is fascinated for 1d4 rounds on a failed save. If the target is neutral-aligned, it is confused for 1d4 rounds on a failed save. If the target is evil-aligned, it is shaken for 1d4 rounds on a failed save.}
        
\DeclareSpell{Enhance Water}{transmutation|V,  S|1 round|touch|Targets: 1 pint of water/level|instantaneous|Fortitude negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Enhance Water}{This spell transforms water into an alcoholic beverage, typically ale, beer, mead, or wine. The alcohol is of middling quality but perfectly drinkable. The spell also serves to remove poisons, diseases, minerals, and other toxins from the water as it transforms. The more contaminants that exist in the water, the darker the ale or the more full-bodied the wine becomes. The beverage's alcohol content is not affected by the presence or absence of contaminants.

This spell does not work on unholy water, potions, or other liquids with magical power.}
        
\DeclareSpell{Face Of The Devourer}{transmutation (polymorph)|V,  S|1 standard action|touch|Targets: creature touched|1 minute/level|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Face Of The Devourer}{You transform the target's face into a hideous shape, such as a half-melted visage with insect legs instead of teeth, seeping pits instead of eyes, and suckered tongues dangling from its misshapen mouth. You do not choose what shape the target's face takes, and the shape is different every time you cast the spell. This transformation does not interfere with the target's senses or its ability to breathe, though it might prevent it from speaking. The target gains a +4 circumstance bonus on Intimidate checks.

If the target does not normally have a bite attack, it gains a bite attack as a natural weapon for the duration of the spell. This bite attack deals 1d6 points of damage if the target is Medium, 1d4 points of damage if the target is Small, or 1d8 points of damage if the creature is Large. The target may use this bite as a primary attack or a secondary attack.}
        
\DeclareSpell{Fairness}{enchantment (compulsion) [mind-affecting]|V,  S,  DF|1 round|close (25 ft. + 5 ft./2 levels)|Targets: one humanoid creature per level|1 minute/level|Will negates|yes}[]
    \DeclareSpellDescription{Fairness}{Humanoid creatures affected by this spell must trade fairly with others to the best of their knowledge. If they know the fair value (or even an estimated fair value) of a good or service, they cannot participate in a trade if it would benefit one side unfairly, and must attempt to stop such trades from occurring, preventing them from cheating another while under the influence of this spell. The symbol of Abadar appears above the heads of those affected by this spell, making those affected and unaffected by the spell immediately apparent.}
        
\DeclareSpell{Fallback Strategy}{abjuration|V,  S,  DF|1 standard action|personal|Targets: you|1 minute/level or until discharged; see text||}[]
    \DeclareSpellDescription{Fallback Strategy}{While this spell is active, you may reroll one attack roll, combat maneuver check, or skill check before the result of the roll or check is known. You must take the result of the reroll, even if it's worse than the original roll. Once the reroll is used, the spell ends.

You can have no more than one fallback strategy active on you at the same time.}
        
\DeclareSpell{False Alibi}{enchantment (compulsion) [mind-affecting]|V,  S,  M (emerald dust worth 100 gp)|1 round|close (25 ft. + 5 ft./2 levels)|Targets: one living creature|permanent; see text|Will negates|yes}[]
    \DeclareSpellDescription{False Alibi}{This spell functions similarly to modify memory, except you can modify the target's memory only in a specific way. In response to a triggering condition you determine, up to the last 5 minutes of the target's memory are eliminated and replaced with a memory of your choosing (or no memory at all). For example, you could cast this on an assassin, set it to trigger when he completes his kill, and replace his memory of the murder with the memory of him discovering the body and picking up the murder weapon. You can cast this spell multiple times on the same target, even with the same trigger, affecting different memories. A single casting of false alibi affects a creature only until the specified condition has been triggered; once a condition has been triggered and the target's memory altered, that condition no longer triggers this spell unless the victim is subject to another casting of false alibi that specifies the same trigger.}
        
\DeclareSpell{Firebelly}{abjuration|V,  S,  DF|1 standard action|personal|Targets: you|1 minute/level|Reflex half; see text|yes; see text}[]
    \DeclareSpellDescription{Firebelly}{A magical fire warms your belly, granting fire resistance 5 and making your gut hot to the touch (but not enough to damage you or anything else). As a standard action, you can breathe a 15-foot cone of flame that deals 1d4 points of fire damage (Reflex half, SR applies). Each time you use this breath weapon, reduce the remaining duration of the spell by 1 minute.}
        
\DeclareSpell{Fractions Of Heal And Harm}{transmutation|V,  S|1 swift action|personal|Targets: you|instantaneous||}[]
    \DeclareSpellDescription{Fractions Of Heal And Harm}{This spell channels a portion of the next spell you cast into magic that heals you. The next instantaneous area damage spell of 3rd level or lower that you cast deals only 75\% of its damage, but heals you of a number of hit points equal to the remaining 25\% of the spell's damage. For example, if you cast this spell and followed it with a fireball that would normally deal 40 hit points of damage, the fireball instead deals 30 hit points of damage and heals you of 10 hit points of damage. The spell affected by this spell must be cast before the end of your next turn. This spell has no effect on spells that do not deal damage or spells higher than 3rd level. This healing is treated as if you had been affected by a cure or inflict spell (whichever would heal you), and is treated as the same spell level as the area-affecting spell for the purpose of effects that relate to the spell level of cure or inflict spells.}
        
\DeclareSpell{Freedom's Toast}{conjuration (teleportation)|V,  S,  M/DF (a small amount of ale in a flagon)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature|instantaneous|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Freedom's Toast}{When the caster hoists a flagon and delivers a toast to freedom, the target is transported up to 15 feet from its position to a space of your choice, though that space must be within your line of sight. If the target was prone at the time of casting, you can choose for the target to be standing upon reaching the destination. Furthermore, if the target was bound with nonmagical ropes, manacles, or other restraints, those restraints are not transported with the target, effectively freeing the target from those restraints. If the target is bound by magical restraints, you can bar those restraints from being transported with the target with a successful caster level check against a DC based on the restraints' caster level (DC = 11 + the restraining magic item's or spell's caster level).}
        
\DeclareSpell{Ghoul Hunger}{necromancy [evil,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one humanoid creature|1 round/level; see text|Will negates; see text|yes}[]
    \DeclareSpellDescription{Ghoul Hunger}{You awaken an unnatural hunger in the target, compelling it to fall upon a nearby helpless or dead humanoid creature and begin eating its flesh. The target defends itself normally but takes no other actions while eating. The target does not take extraordinary risks to satisfy this urge (it wouldn't jump over a pit or swim through lava to reach a suitable victim). If the target can't fulfill this urge on its next turn, the spell fails. Each round on its turn, the target can attempt a new saving throw to end the effect.}
        
\DeclareSpell{Gozreh's Trident}{evocation [electricity]|V,  S,  DF|1 standard action|0 ft.|Effect: trident-like bolt of electricity|1 minute/level (D)|none|yes}[]
    \DeclareSpellDescription{Gozreh's Trident}{A 4-foot-long, blazing, forked bolt of electricity springs forth from your hand. You wield this spear-like bolt as if it were a trident (you are considered proficient with the bolt). Attacks with Gozreh's trident are melee touch attacks. The bolt deals 1d8 points of electricity damage + 1 point per 2 caster levels (maximum +10). Since the bolt is immaterial, your Strength modifier does not apply to the damage. The bolt can ignite combustible materials such as parchment, straw, dry sticks, and cloth.}
        
\DeclareSpell{Hairline Fractures}{transmutation [earth]|V,  S,  M (a broken twig)|1 standard action|touch|Targets: 5-foot-square section of stone or a creature with the  earth subtype|1 round/level|Fortitude negates (object)|yes (object)}[]
    \DeclareSpellDescription{Hairline Fractures}{With a single touch, you create temporary hairline fractures in a piece of stone or a creature with the earth subtype. If you cast this spell on a section of stone, you reduce its hardness to 5 and its hit points to 10/inch of thickness. If you cast this spell on a creature with the earth subtype, that creature takes a -2 penalty to AC for the spell's duration. Make whole reverses this spell's effect.}
        
\DeclareSpell{Hammer Of Mending}{transmutation|V,  S,  F (a small mithral hammer worth 300 gp),  DF|1 standard action||Area: 30-ft.-radius burst centered on you|instantaneous|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Hammer Of Mending}{Upon striking a piece of solid ground with the spell's focus or a holy symbol, you let out a wave of energy that repairs items within its burst. All objects or constructs within the burst are repaired of 1d6 points of damage per level. When this spell affects constructs, the spell bypasses any immunity to magic as if the spell did not allow spell resistance.

Hammer of mending can fix destroyed magic items (items with 0 hit points or fewer), and restores the magic properties of the item if your caster level is at least twice that of the item.

Items with charges (such as wands) and single-use items (such as potions and scrolls) cannot be repaired in this way.}
        
\DeclareSpell{Haze Of Dreams}{enchantment (charm) [emotion,  mind-affecting]|V,  M (pinch of sand)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Haze Of Dreams}{You fill an enemy's head with waking dreams, a reminder of the pleasures, delights, and terrors to be found in the dream world. While in this strange dream state, the target moves at half its normal speed (round down to the next 5-foot increment), which affects the creature's jumping distance as normal for decreased speed.

Multiple haze of dreams effects do not stack, nor does this spell's effect stack with slow.}
        
\DeclareSpell{Hunter's Blessing}{transmutation|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature/level, no two of which can be more than 30 ft. apart|1 hour/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Hunter's Blessing}{When casting this spell, you designate a type or type and subtype of creature (using the ranger's favored enemy categories; Pathfinder RPG Core Rulebook 6 4) and a type of terrain (using the list of ranger's favored terrain categories, Core Rulebook 65). Targets of the spell gain a +2 sacred bonus on Bluff, Perception, Sense Motive, and Survival checks attempted against creatures of the selected type, and a +2 sacred bonus on attack rolls and damage rolls made against creatures of that type. Furthermore, they gain a +2 sacred bonus on initiative checks, Perception, Stealth, and Survival checks while they are in the type of terrain you designate. Lastly, when tracking the designated creature type in the chosen terrain, the targets can follow the tracks of such creatures untrained, even if the DC for the task is 11 or higher.}
        
\DeclareSpell{Ice Armor}{transmutation [cold,  water]|V,  S,  F (5 gallons of water)|1 minute|0 ft.; see text|Effect: a suit of armor made of ice|1 hour/level or until destroyed|none|no}[]
    \DeclareSpellDescription{Ice Armor}{You create a suit of armor made of ice. While cold to the touch, it does not harm the wearer, especially if worn over normal clothing (though it can hasten the effects of exposure in cold environments). It offers the same protection as a breastplate, except it has hardness 0 and 30 hit points. If the intended wearer is immersed in water when you cast this spell, you may form the armor around the wearer (who may be you); otherwise the wearer must don the armor normally. Attacks against the wearer that create heat or fire degrade the armor, reducing its armor bonus by 1 for every 5 points of fire damage the wearer takes; when the armor's bonus to AC reaches 0, the armor is destroyed and the spell ends. Because the ice is slightly buoyant, the wearer gains a +2 circumstance bonus on Swim checks, except when swimming downward. Druids can wear ice armor without penalty.}
        
\DeclareSpell{Inheritor's Smite}{transmutation|V,  S,  DF|1 swift action|personal|Targets: you|see text||}[]
    \DeclareSpellDescription{Inheritor's Smite}{You channel the power of righteousness into your weapon arm, allowing you to strike with great force. Your next melee attack (if made before the end of your next turn) gains a +5 sacred bonus on the attack roll. If the attack hits, you may immediately attempt a bull rush combat maneuver (with a +5 sacred bonus on your combat maneuver check) against the target without provoking an attack of opportunity; if your combat maneuver check exceeds the defender's CMD by more than 5, you do not need to move with the target to push it back more than 5 feet.}
        
\DeclareSpell{Light Prison}{evocation [light]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature/2 levels|1 round/level (D)|Reflex negates|yes}[]
    \DeclareSpellDescription{Light Prison}{Rays of light burst forth from your outstretched hand, encircling each target's space with a cage of light. If a target fails its Reflex save, it becomes enclosed in the light prison. A creature enclosed in a light prison can attack, cast spells, and otherwise act normally as long as it stays within the light prison. However, if a creature passes through the walls of a light prison enclosing it, it takes 1d6 points of damage and is blinded for 1 round.

Creatures do not receive saves to negate these effects. Once a creature passes through the walls of a light prison surrounding it, the effect ends for that creature.}
        
\DeclareSpell{Lighten Object}{transmutation|V,  M (goose down)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: 1 object of up to 1 cubic ft./level|1 minute/level|Will negates (object)|yes (object)}[]
    \DeclareSpellDescription{Lighten Object}{The target's weight decreases by half. If this spell is cast on armor, the armor's armor check penalty decreases by 1, though its categorization as light, medium, or heavy does not change.}
        
\DeclareSpell{Mass Lighten Object}{transmutation|V,  M (goose down)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: multiple objects totaling up to 1 cubic ft./level, no two of which can be more than 30 ft. apart|10 minutes/level|Will negates (object)|yes (object)}[]
    \DeclareSpellDescription{Mass Lighten Object}{This spell functions like lighten object, except that it affects a number of objects equal to half your caster level.\\\\

{\centering\bf Lighten Object\hrule}

The target's weight decreases by half. If this spell is cast on armor, the armor's armor check penalty decreases by 1, though its categorization as light, medium, or heavy does not change.}
        
\DeclareSpell{Lose The Trail}{illusion (glamer)|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature/level|1 hour/level (D)|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Lose The Trail}{The target or targets of this spell can obscure their tracks when fleeing from a pursuer. This increases the DC of any Survival checks made to track the spell's targets by 2 per level of the caster.}
        
\DeclareSpell{Maddening Oubliette}{conjuration (teleportation)|V,  S,  M (the powdered bones of a creature that died in prison)|1 round|close (25 ft. + 5 ft./2 levels)|Targets: one creature|special; see text|Will negates; see text|yes}[]
    \DeclareSpellDescription{Maddening Oubliette}{The target is transported to a dark and dank prison in some unspecified horrific demiplane, where tentacles writhe around, clawed fingers grab at the creature (though they deal no damage), and harsh, whispering voices speak blasphemies and maddening secrets. At the end of each round within this terrifying oubliette, the target can attempt a Will saving throw in order to escape the prison. The saving throw has a penalty equal to the number of rounds the target has spent in the oubliette (minimum -1 and maximum -5). If the target succeeds at its saving throw, it returns to its former space. If that space is occupied or otherwise unavailable, the target is shunted to the nearest available space. When the target returns from the oubliette, it is confused for a number of rounds equal to the number of rounds of imprisonment (minimum 1), unless it was confined in the oubliette for 10 or more rounds, in which case the target is affected as if it were subject to an insanity spell instead.}
        
\DeclareSpell{Monstrous Extremities}{transmutation (polymorph)|V,  S|1 minute|touch|Targets: creature touched|1 hour/level|Will negates|yes}[]
    \DeclareSpellDescription{Monstrous Extremities}{You change one of the extremities of the creature touched-arms or legs only-into another shape of approximately the same size and mass. You can choose a tentacle, a hoof, or a wing.

The subject must take approximately 10 minutes to familiarize itself with the function and movement of the new extremity to use it properly. These new forms do not allow the subject to fly, run faster, or swim better; however, they do act as natural weapons of the appropriate type, and the subject can use them to make secondary attacks while making attacks with weapons as a full-attack action. The secondary attacks are made using the creature's base attack bonus -5 and adding only 1/2 the creature's Strength bonus on damage rolls. The subject cannot hold a weapon or use any item that would ordinarily fit into the slot of the changed extremity. The subject can receive the benefits of this spell multiple times.}
        
\DeclareSpell{Night Of Blades}{evocation|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Effect: wall of blades up to 10 ft. long/level and 10 ft. tall|1 minute/level (D)|Reflex half|yes}[]
    \DeclareSpellDescription{Night Of Blades}{Useful primarily to those who skulk in the darkness, this spell is a temporary trap for the unwary. You create an immobile wall of tiny black blades that whirl and tear into creatures like a cyclone.

Anyone who enters this space takes 1d4 points of damage per caster level (maximum 10d4), though a successful Reflex save halves the damage. The spell cannot be cast so that it appears in a space already occupied by Small or larger creatures.}
        
\DeclareSpell{Pick Your Poison}{conjuration (healing) [mind-affecting]|V,  S,  DF|1 standard action|touch|Targets: creature touched|10 minute/level|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Pick Your Poison}{This spell temporarily converts even the deadliest poison affecting a creature into an intoxicating alcohol. If the subject is affected by a poison effect while under the effects of this spell, instead of the poison's normal effect, she feels intoxicated as if she'd just had a very strong drink and takes a -2 penalty on attacks, saves, and checks for the duration of the spell.

When the spell's duration expires, the penalty ends and the poison's normal effects apply. Pick your poison does not affect any poison effects that occurred before the spell was cast.}
        
\DeclareSpell{Plague Bearer}{necromancy [disease,  evil]|V,  S|1 standard action|touch|Targets: one living creature|1 round/level; see text|Fortitude negates; see text|yes}[]
    \DeclareSpellDescription{Plague Bearer}{You make the target an asymptomatic carrier for a host of virulent diseases. Creatures that end their turn adjacent to the target must succeed at a Fortitude save or be affected as if by the spell contagion. The target itself does not become diseased, and suffers no ill effects from this spell. Once plague bearer ends, the target is no longer contagious, though any creature it infected remains diseased.}
        
\DeclareSpell{Poisoned Egg}{transmutation [poison]|V,  S,  DF|1 standard action|touch|Targets: one egg|1 minute/level|none (object)|no (object)}[]
    \DeclareSpellDescription{Poisoned Egg}{You transform the contents of a normal egg into a single dose of small centipede poison (injury; save DC 11; frequency 1/round for 4 rounds; effect 1 Dex; cure 1 save). The poison reverts to a normal egg at the end of the spell's duration (the reverted egg substance is harmless unless the poisoned creature is vulnerable to eggs). The egg may be raw or cooked but must be whole and not empty when you cast the spell. When applying the poisoned egg's contents to a weapon, the wielder has no chance of poisoning herself, as though she had the poison use class feature.}
        
\DeclareSpell{Read Weather}{divination|V,  S,  F (a set of marked sticks or bones worth at least 25 gp)|1 minute|personal|Targets: you|instantaneous||}[]
    \DeclareSpellDescription{Read Weather}{This spell allows you to forecast the weather at your location for the next 48 hours, providing you with advance warning of storms, tornadoes, and so on. This forecast reveals only the weather that would arise naturally, and does not take into account any magical occurrences that might change the weather.}
        
\DeclareSpell{Replenish Ki}{conjuration (healing)|V,  S,  DF|1 minute|touch|Targets: creature touched|instantaneous|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Replenish Ki}{You attune the target's internal store of supernatural energy to the cosmos, replenishing its ki pool. If you are the target, you regain 2 ki points. If another creature is the target, it regains 1 ki point. This does not allow the target to exceed its ki pool's maximum. This spell has no effect if the target does not have a ki pool.}
        
\DeclareSpell{Rovagug's Fury}{transmutation|V,  S|1 standard action|30 ft.|Area: cone-shaped burst|instantaneous|none|yes}[]
    \DeclareSpellDescription{Rovagug's Fury}{You create a minor earthquake that can trip creatures. Attempt a single combat maneuver check and apply the result against the CMD of every creature in the area. If your roll equals or exceeds a creature's CMD, that creature is knocked prone. This trip attack does not provoke an attack of opportunity (though you do provoke one for casting the spell), nor are you knocked prone if you fail the check by 10 or more. Unlike with a regular trip attack, you can trip any creature touching the ground, regardless of size. Improved Trip does not affect this spell in any way. Though the earthquake is small and focused on the ground, if the area is particularly unstable, the spell might cause items to topple, stones to shake loose from the walls or ceiling, and so on at the GM's discretion.}
        
\DeclareSpell{Secret Speech}{divination|V,  S|1 standard action|touch|Targets: creature touched|10 minutes/level|Will negates (harmless)|no (harmless)}[]
    \DeclareSpellDescription{Secret Speech}{This spell grants the target the ability to send secret messages embedded within normal speech. This is similar to the secret messages ability of the Bluff skill, but no check is needed; the speaker's intended recipient always understands the hidden message perfectly, but other listeners cannot perceive the message at all. The target can send only one message at a time, though it can send that message to multiple listeners.

The secret message is considered to be in the same language the target is speaking, and intended recipients hear and understand both the actual speech and the secret message. The target can make itself understood as far as its voice carries.

For example, at a fancy noble's wedding, a jealous former suitor casts this spell on himself before making a speech.

Everyone hears his glowing words of praise, but only his allies hear his secret message instructing them to attack the groom.}
        
\DeclareSpell{Seducer's Eyes}{enchantment (charm) [mind-affecting]|V,  S,  DF|1 standard action|personal|Targets: you|10 minutes/level (D)||}[]
    \DeclareSpellDescription{Seducer's Eyes}{You gain a bonus on Charisma-based skill checks equal to 1 + 1 for every 4 caster levels you possess (to a maximum of +5), but only when interacting with those who might conceivably find you sexually attractive. You do not gain this bonus against those you or your allies are attacking or threatening.}
        
\DeclareSpell{Shared Sacrifice}{necromancy [evil]|V,  S|1 round|close (25 ft. + 5 ft./2 levels)|Targets: one creature|1 round/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Shared Sacrifice}{You create a link to a target and can direct pain and damage through this link. You take only half damage from effects and attacks that deal hit point damage.

The target of this spell takes the remainder of the damage.

Forms of harm that do not involve hit points, such as charm effects, temporary ability damage, level drain, and death effects cannot be shared through this link. If you suffer a reduction in hit points because of a lowered Constitution score, the reduction is not split with the target of this spell because it is not hit point damage. When the spell ends, subsequent damage is no longer divided between the subject and you, but damage already split is not reassigned back to you.

If you and the target of the spell move out of range of each other, the spell immediately ends.}
        
\DeclareSpell{Greater Shield Of The Dawnflower}{evocation [fire,  good,  light]|V,  S,  DF|1 standard action|personal|Targets: you|1 round/level||}[]
    \DeclareSpellDescription{Greater Shield Of The Dawnflower}{You create a disk of sunlight on one arm. Any creature that strikes you with a melee attack deals normal damage, but also takes 1d6 points of damage + 1 point per caster level. Half of this damage is fire damage and half is holy damage (as the spell flame strike). An undead creature or a creature particularly vulnerable to light that hits you instead takes 2d6 points of damage +1 point per caster level. Creatures with reach weapons are not subject to this damage if they attack you. The shield provides illumination equivalent to a daylight spell. You can have only one instance of this spell in effect at a time. It does not stack with similar damaging aura spells such as fire shield or shield of the Dawnflower (The Inner Sea World Guide 296).}
        
\DeclareSpell{Sky Swim}{transmutation [air]|V,  S,  DF|1 standard action|touch|Targets: Large or smaller creature touched|1 minute/level|none (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Sky Swim}{This spell grants the target the ability to swim through the air.

If the target has a swim speed, it can move through the air at that speed. Otherwise, it must succeed at Swim checks to move as normal. Still air is treated as calm water, light or moderate wind is treated as rough water, strong or severe wind is treated as stormy water, and the target cannot swim through stronger winds (Core Rulebook 439). This spell does not grant the ability to breathe air to creatures that normally can't.}
        
\DeclareSpell{Smite Abomination}{evocation|V,  S,  DF|1 standard action|personal|Targets: you|1 round/level||}[]
    \DeclareSpellDescription{Smite Abomination}{Drawing upon positive energy, you emulate some of a paladin's power to smite undead. Choose one undead creature as your target.

Your melee attacks against that target gain a bonus equal to your Charisma or Wisdom modifier, whichever is higher, on your attack rolls, and a bonus equal to your caster level on damage rolls. Your melee attacks also bypass the target's damage reduction. These bonuses do not stack with the bonuses from a paladin's smite.}
        
\DeclareSpell{Spell Gauge}{divination [mind-affecting]|V,  S,  F (a silver piece)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature|instantaneous|Will negates|yes}[]
    \DeclareSpellDescription{Spell Gauge}{You immediately discover some of the spells that the target knows or has prepared. The number of spells revealed to you is equal to your caster level. The target's lowest-level spells are revealed first-ignoring 0-level spells-in a random order. Once all of the target's 1st-level spells are revealed, the spell begins revealing 2nd-level spells, then 3rd-level spells. This spell does not reveal spells of 4th level or higher, nor does it reveal spelllike abilities or other special abilities. If cast on a creature that is not a spellcaster, that has only 0-level spells or spells of 4th level or higher prepared, that has expended all of its spells, or that has not prepared any spells that day, the spell has no effect.}
        
\DeclareSpell{Spell Scourge}{abjuration|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature|instantaneous or 1d4 rounds; see text|Will negates|yes}[]
    \DeclareSpellDescription{Spell Scourge}{A whip of cracking magical might appears in your hand, allowing you lash spells from the mind of enemy spellcasters. With a lash of bluish-purple energy, you strip many protective spells and effects from a single creature. If the target of this spell is currently under the effects of any harmless spells or effects, it must succeed at a Will save or all of those spells and effects end, stripping the target of the benefit of those spells. If the target is not currently under the effect of least one harmless spell, the target is instead confused for 1d4 rounds.}
        
\DeclareSpell{Symbol Of Debauchery}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S,  M (a set of bull genitals and powdered ruby worth 5, 000 gp)|10 minutes|0 ft.; see text|Effect: one symbol|see text|Will negates|yes}[]
    \DeclareSpellDescription{Symbol Of Debauchery}{You conjure a sizable symbol into being, a rune suggestive of bloated bodies, flung food, and flowing wine. This spell functions as symbol of death, except that all creatures within 60 feet of the symbol of debauchery are instead filled with lust for the nearest conscious creature. This effect lasts for 1 round per caster level, even after creatures leave the symbol's area of effect. Affected creatures are compelled to rush to the nearest creature in order to caress and kiss it, and may take no other actions. Each creature receives a single Will save when the symbol of debauchery is triggered to negate the effect. If no other creatures are visible, an affected creature may act normally.}
        
\DeclareSpell{Symbol Of Dispelling}{abjuration|V,  S,  M (pure grain alcohol and powdered diamond worth 5, 000 gp)|10 minutes|0 ft.; see text|Effect: one symbol|instantaneous|none|no}[]
    \DeclareSpellDescription{Symbol Of Dispelling}{This spell functions as symbol of death, except that all creatures within 40 feet of the symbol of dispelling are instead affected as if by the area dispel function of greater dispel magic.

Attempt a dispel check when casting symbol of dispelling.

Once the symbol is triggered, apply the result of that check to each creature in the area, as well as each object that is the target of one or more spells. Unlike symbol of death, symbol of dispelling grants no saving throws, and it is not subject to spell resistance.}
        
\DeclareSpell{Tap Inner Beauty}{divination|V,  M (a tiny mirror)|1 standard action|personal|Targets: you|1 minute/level||}[]
    \DeclareSpellDescription{Tap Inner Beauty}{This spell allows you to tap into the natural beauty of your soul and let it shine from your eyes and your speech. While the spell is active, you gain a +2 insight bonus on all Charisma ability checks and Charisma-based skill checks.}
        
\DeclareSpell{Touch Of Bloodletting}{necromancy|V,  S|1 standard action|touch|Targets: living creature touched|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Touch Of Bloodletting}{This spell causes any existing wounds that the target possesses to bleed profusely. If the creature's current total hit points are less than its maximum, this spell causes the creature to take 1 point of bleed damage each round and become exhausted for the duration of the spell. A successful DC 15 Heal check or any spell that cures hit point damage negates the effects of this spell.}
        
\DeclareSpell{Tracking Mark}{evocation|S,  DF|1 standard action|long (400 ft. + 40 ft./level)|Targets: one creature|10 minutes/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Tracking Mark}{You gain a supernatural ability to detect tracks and other clues left behind by the target. You treat the DCs of all Survival checks made to track the target as if they were 5 lower than normal, and you gain a +5 bonus on Perception checks made to notice the target if it is using Stealth or recognize it if it is using Disguise.}
        
\DeclareSpell{Transplant Visage}{transmutation [evil]|V,  S,  M (one corpse)|1 round|personal|Targets: you|permanent||}[]
    \DeclareSpellDescription{Transplant Visage}{This spell allows you to add a creature's stolen face to or remove such a face that you've already applied from your own. Before casting this spell, you must remove the face and eyes of a creature that has been dead no longer than 1 minute per caster level and place it over your own. Once you cast transplant visage, the creature's stolen skin magically melds with your own, making the expressions and eye color on your new face seem perfectly natural. Your new appearance grants you a +10 bonus on Disguise checks. Because the alteration made by transplant visage is permanent, there is no residual magical aura, and your new appearance is not recognized by detect spells. Transplant visage may be cast innumerable times, allowing a single caster to wear layers upon layers of stolen faces. However, only the topmost face is visible at any one time.

Transplant visage may also be used to remove a previously stolen face. This is the only way to remove a face short of using greater polymorph, miracle, or wish. When used in this way, transplant visage c auses t he t opmost f ace t o fl ake o ff a nd crumble into dust. A face so removed may not be reused. If the caster is wearing several stolen faces when the topmost face is removed, the next face down is revealed, and may be used as normal.}
        
\DeclareSpell{Unwelcome Halo}{evocation [light]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targets: one nongood creature|1 minute/level|Will negates|yes}[]
    \DeclareSpellDescription{Unwelcome Halo}{This spell causes the target to glow as if surrounded by a halo of light. This halo sheds normal light in a 20-foot radius from the creature, and increases the light level by one step for an additional 20 feet. This halo makes it impossible for the creature to gain concealment in nonmagical darkness, and in dim or darker conditions, the creature's glow can be seen even if it is not within direct line of sight.

If unwelcome halo is brought into an area of magical darkness (or vice versa), the effects of both spells are temporarily negated, so that the otherwise prevailing light conditions exist within the overlapping fields of effect.}
        
\DeclareSpell{Vengeful Stinger}{transmutation (polymorph) [poison]|V,  S,  M (a living wasp),  DF|1 standard action|personal|Targets: you|1 round/level|Fortitude negates; see text|no}[]
    \DeclareSpellDescription{Vengeful Stinger}{You grow a long, wasp-like tail complete with stinger that can strike those who dare attack you. While you are under the effects of this spell, when a creature adjacent to you hits you with a melee attack, you can make an attack of opportunity with your stinging tail, even if your opponent's attack would not otherwise provoke an attack of opportunity. You must otherwise be eligible to make an attack of opportunity to use this ability. The attack is made with your full attack bonus, and with a +2 sacred bonus on the attack roll. The stinging tail is considered a light weapon with a critical range of 19-20/x2.

On a successful hit, the target takes 1d8 points of damage plus an amount of damage equal your Strength modifier and must succeed at a Fortitude save or it takes 1d4 points of Dexterity damage. This poison damage is also modified on a confirmed critical hit.}
        
\DeclareSpell{Vexing Miscalculation}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature|1 minute/level or until discharged|Will negates|yes}[]
    \DeclareSpellDescription{Vexing Miscalculation}{You frustrate an opponent with ill fortune that leads even its most accurate attacks astray. The target is unable to score critical threats for the duration of this spell, even if the result of its roll would normally be a critical threat. If the creature rolls a natural 20, the attack still hits regardless of its opponent's AC, but the hit is not eligible for a critical confirmation roll. Once a critical threat has been foiled by vexing miscalculation, the spell is discharged.}
        
\DeclareSpell{Weapons Against Evil}{transmutation|V,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one weapon/level, no two of which can be more than 20 ft. apart|1 round/level|Fortitude negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Weapons Against Evil}{Each weapon this spell affects each shines with pale light that dimly illuminates a 5-foot square. These weapons also ignore the DR of evil creatures that have DR 5 or lower, as long as the damage reduction is not DR/epic.}
    