    
\DeclareSpell{Blood Song}{evocation|V,  S,  M (the caster's blood)|2 minutes|touch|Targets: creature touched; see text|1 day or until discharged (D)|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Blood Song}{This spell functions as imbue with spell ability, with the following exceptions: only bard spells of the conjuration (healing), enchantment, and transmutation schools can be transferred; the imbued spells last for 1 day; and the subject isn't beholden to any principles regarding the imbued spells' use.  As part of the casting, the caster must shed some of his blood (or an equivalent humor). If the caster isn't susceptible to bleed damage, regardless of the reason, he can't cast blood song. For each spell that is imbued using blood song, the caster loses 5 hit points, which can't be regained by any means until the spell ends or is discharged.}
        
\DeclareSpell{Hallucinogenic Smoke}{conjuration [poison]|S,  M (tobacco leaves,  ingested)|1 standard action|personal|Targets: you|3 rounds/level or until discharged; see text|Fortitude partial|yes}[]
    \DeclareSpellDescription{Hallucinogenic Smoke}{Dark gray smoke seeps from your eyes, ears, and mouth for the spell's duration, though the smoke doesn't significantly hamper your vision. Upon casting the spell, you may immediately exhale the smoke in a 30-foot cone or do so in a later round as a standard action, ending the spell. Each living creature caught within the cone must succeed at a Fortitude save or be nauseated for 1 round per caster level as it is wracked with waves of nausea and disorienting visions. If it succeeds at its Fortitude save, the creature is instead sickened for 1d4 rounds.  If you don't expel the smoke by the end of the spell's duration, you suffer the spell's effects instead.  If you cast augury during the duration of hallucinogenic smoke, treat your caster level as 5 higher when determining the chance for a meaningful reply. Additionally, you know whether a result of "nothing" resulted from a failed or successful augury.}
        
\DeclareSpell{Jungle Mind}{divination (scrying)|V,  S,  DF|1 minute|personal|Targets: you|10 minutes/level|Will negates (see text)|no}[]
    \DeclareSpellDescription{Jungle Mind}{You merge your mind into the jungle's social hierarchy, mystically establishing yourself as a master of wild beasts and an apex predator. You attain knowledge about the general animal population in a radius of 1 mile as commune with nature, and you then select one type of animal (such as birds, cats, snakes, or fish). For the duration of the spell, you can sense the location, movement, and size of creatures of this type in the area, though you can't discern species or individual identity. In addition, you improve the starting attitude of animals of the chosen type by one step for the duration of the spell.  As a full-round action, you may focus on a single animal that you can sense with this spell to establish a mental link. You can read the animal's surface thoughts as detect thoughts, and can see, hear, and smell what the animal is experiencing using your own Perception skill. If you target another creature's animal companion, the spell ends if the animal succeeds at a Will save. Using this ability reduces the spell's remaining duration to 1 round/level, and the selected animal is treated as the scrying sensor.  Despite the name, jungle mind functions within any terrain.}
        
\DeclareSpell{Lay Of The Land}{divination|V,  S,  M (a piece of soil from the land to be memorized)|1 minute|personal|Targets: you|1 day|none|yes}[]
    \DeclareSpellDescription{Lay Of The Land}{In a flash of recognition, you learn about the geography of your surroundings within a radius of 1 mile per 2 caster levels (minimum 1 mile). This instant familiarity grants you an insight bonus equal to your caster level (maximum +5) on Knowledge (geography) checks and Survival checks to avoid getting lost so long as you remain in the affected area.  Additionally, for the duration of the spell you can make Knowledge (geography) checks regarding the affected area as though you were trained in that skill.}
        
\DeclareSpell{Source Severance}{abjuration|V,  S,  M (an unworked lodestone)|1 standard action|5 feet|Area: 5-ft.-radius emanation, centered on you|10 minutes/level (D)|none|see text}[]
    \DeclareSpellDescription{Source Severance}{You create an invisible barrier that surrounds you and moves with you, inhibiting one category of magic. When you cast this spell, choose either arcane or divine magic. This spell functions like antimagic field, but it suppresses only spells of the chosen type and supernatural and spell-like class abilities from classes that grant spellcasting of the selected type. Magic items, other spell-like abilities, and other supernatural abilities are unaffected.  While this spell is in effect, you must succeed at a concentration check (DC 20 + twice the spell level) to cast any spell, whether arcane or divine. If you fail at the check, you lose the spell as if you had cast it to no effect.}
        
\DeclareSpell{Tectonic Communion}{divination|V,  S,  DF|1 hour|personal|Targets: you|Instantaneous||}[]
    \DeclareSpellDescription{Tectonic Communion}{Tectonic communion functions as commune with nature with an even greater range. In outdoor or natural underground settings, the spell operates on a radius of 100 miles per caster level, extending even underground without penalty.  For every 2 caster levels above 13th, you may glean an additional fact from the list presented in commune with nature. Communities, dungeons, and signs of civilization (such as roads, farms or other constructions and settlements) exist as dark and unknowable blots in your perception of the spell's area; you're aware of their location and existence, but can't discern any information regarding them.}
    