    
\DeclareSpell{Abeyance}{abjuration|V,  S,  M (a flask of holy water worth 25 gp),  DF|1 minute|touch|Targets: creature touched|24 hours|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Abeyance}{Abeyance suppresses the effects of a single  curse on a creature. It does not restore any damage or drain that might have been caused by the curse. Abeyance cannot suppress curses that cannot be removed by remove curse, but it can suppress curses such as lycanthropy that require remove curse along with additional measures. An individual curse can be suppressed only once by abeyance, even if cast by a different caster.  Abeyance does not allow a creature to divest itself of cursed objects, though it can suppress a curse contracted from an object.}
        
\DeclareSpell{Aggravate Affliction}{necromancy|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature|instantaneous|see text|yes}[]
    \DeclareSpellDescription{Aggravate Affliction}{All recurring afflictions (those with a frequency,including curses, diseases, and poison) possessed by the targeted creature immediately trigger, requiring an immediate saving throw (as described in the affliction) to avoid suffering their effects. A successful saving throw does not count toward ending the affliction, and this extra save does not change the timing of the next save against the affliction. Afflictions without a frequency are unaffected by this spell.}
        
\DeclareSpell{Greater Bestow Curse}{necromancy|V,  S|1 standard action|touch|Targets: creature touched|permanent|Will negates|yes}[]
    \DeclareSpellDescription{Greater Bestow Curse}{You place a curse on the subject. Choose one of the following.   -12 penalty to an ability score, or -6 penalty to two ability scores (to a minimum ability score of 1).   -8 penalty on attack rolls, saves, ability checks, and skill checks.   Each turn, the target has a 25\% chance to act normally; otherwise, it takes no actions.   Bestow one of the curses or variants in this article.   Bestow curse of the ages or unluck (Core Rulebook 557).  If a specific affliction is bestowed, the save DC of the spell replaces the usual save DC of the affliction. You can also invent your own curse, but it should be no more powerful than those described above.  The curse bestowed by this spell cannot be dispelled, but it can be removed with a break enchantment, limited wish, miracle, or wish spell. It cannot be removed with remove curse or suppressed with abeyance. The DC to remove the curse with break enchantment increases by 5.}
    