\defineSphere{Alteration}{You have the ability to change the physical makeup of creatures.}{You have the ability to change the physical makeup of creatures.}
\newCounter{charshapeshifttraitsCount}
\def\charshapeshiftrange{Touch}
\defineBaseAbility{Alteration}{Shapeshift}{Change the shape of a target within \charshapeshiftrange{} range for as long as you concentrate, or spend 1 SP for changes to last \arabic{charCLCount} minute\s{} without concentration.  You may add up to \addToCounter{charshapeshifttraitsCount}{\value{charCLCount} / 5 + 1}\arabic{charshapeshifttraitsCount} trait\s[charshapeshifttraitsCount] to the creature.}{
	As a standard action you may \textit{shapeshift} yourself or a touched creature, changing their form for as long as you concentrate. If the target is unwilling, this costs a spell point, and they are allowed a Fortitude save to negate. You may spend a spell point to allow a \textit{shapeshift} to remain for 1 minute per caster level without concentration. You may dismiss your \textit{shapeshift} as a free action.\par
	\textit{Shapeshift} is a polymorph effect. A target may only be affected by one \textit{shapeshift} at any one time. If a caster attempts to place a second \textit{shapeshift} on a target, he must succeed at a magic skill check. If he succeeds, the second \textit{shapeshift} is successfully placed on the target, dismissing and dispelling the first.\par
	When \textit{shapeshifting} a target, the caster must choose a form and a series of traits for them. Forms constitute a creature's basic physical makeup (humanoid, draconic, animalistic, avian, etc.) while traits are special characteristics or alterations (natural attacks, creature size, monster special abilities, etc.). A caster may grant up to 1 trait + 1 per 5 caster levels and cannot grant the same trait more than once unless the trait indicates it may be granted multiple times.\par
	With the exception of Blank Form (detailed below), placing a form on a creature causes that creature's physical body to change into that of another creature. The target gains the listed number of limbs and loses all others. The target loses any extraordinary or supernatural abilities, natural attacks, and movement types dependent on their original form (darkvision, scent, wings, claws, etc.) and gains the listed benefits in their place. Alternate sources of physical traits (such as a dragon sorcerer's ability to grow claws) still function. In addition, the target's equipment melds into their new form, causing them to lose their armor and shield bonuses and the ability to pull any item from a backpack or belt. They also cannot activate magic items (although constant bonuses from magic items still remain).\par
	This cannot be used to assume the guise of a specific individual creature, but otherwise adds a +10 bonus to Disguise checks made to appear as a different race, gender, or species. The caster may cause the target to cosmetically appear as whatever type of creature he desires, although if the target is not granted the right physical attributes (for example, granting the right size category or number of legs), the disguise may fail completely.\par
	When a caster first gains the Alteration sphere, they may grant creatures the Blank Form and the traits listed below. Additional forms and traits may be gained by taking Alteration talents. Any trait may be granted to any form.\par
	\textbf{Blank Form:} Unlike other forms, the Blank Form does not change the creature's basic makeup. They do not gain the +10 bonus to Disguise checks, nor do they lose their abilities, equipment, natural attacks, or any other aspect of their unaltered form. The Blank Form allows a caster to add traits to a creature without fundamentally changing the target first.\\\\
	A caster may grant the following traits to a creature affected by their shapeshift. A target must possess the appropriate limb where listed, and cannot grant a natural attack to a limb that already possesses a natural attack.\par
	$\bullet$ Darkvision 60 ft\par
	$\bullet$ Low-light vision\par
	$\bullet$ 2 claw attacks (Primary attacks, 1d4, 1d3 small, requires arms). You may grant this trait multiple times.\par
	$\bullet$ 1 bite attack (Primary attack, 1d6, 1d4 small, requires head). You may grant this trait multiple times.\par
	$\bullet$ 1 gore attack (primary, 1d6, 1d4 small, requires head). You may grant this trait multiple times.\par
	$\bullet$ 2 slam attacks (primary, 1d4, 1d3 small, requires arms). You may grant this trait multiple times.\par
	$\bullet$ 2 pincers (secondary, 1d6, 1d4 small, requires arms). You may grant this trait multiple times.\par
	$\bullet$ You change the target's cosmetic appearance. This could include changing the target's apparent age, making an elf into an orc, disguising a large dog as a small pony, changing a male into a female, or some other such alteration. This grants the target a +10 bonus to Disguise checks. This trait may only be applied to the Blank Form, as such changes are assumed with other forms.
}
\defineTalent{Additional Limbs}{Add extra limbs as part of a \textit{shapeshift}}{
	You may apply the following traits to any form. You may grant	each trait multiple times.\par
	$\bullet$ An extra pair of arms.\par
	$\bullet$ A prehensile tail, which may be used to hold objects as if it were a hand, and retrieve objects from a belt or pouch as a swift action.\par
	$\bullet$ Tail slap (Secondary, 1d6, 1d4 small, requires tail)\par
	$\bullet$ Stinger (Primary, 1d4, 1d3 small, requires tail)\par
	$\bullet$ A pair of legs. This grants a 20 ft land speed if the target didn't possess one. If this is not the form's first pair of legs, the target gains a +4 CMD bonus against trip attempts. If this causes the target to become a quadruped, they gain the related increase to carrying capacity and may serve as a mount for creatures smaller than itself.\par
	$\bullet$ An extra head.}{}
\defineTalent{Animal Mind}{Target of \textit{shapeshift} makes will save or gains animal intelligence.}{
	You may apply the following trait to your \textit{shapeshifts}:\par
	$\bullet$ The target must pass a Will save or have their mind become bestial. Their Intelligence is reduced to 2, and they are treated as an animal for skills such as Handle Animal and Diplomacy. They cannot use any spells, sphere abilities, supernatural or extraordinary abilities, although they retain other aspects of their class levels such as BAB and any other abilities.}{}
\defineTalent{Animalistic Transformation}{\textit{Shapeshift} into animals or gain Scent, hooves, and/or a fast land speed}{
	You may grant the form of a land animal or magical beast with your shapeshift. The form has a head and 4 legs with all the benefits of being a quadruped. The target gains a 40 ft land speed, which increases by 20 ft per 5 caster levels. The target also gains the Scent ability, a bite attack (Primary, 1d6, 1d4 small) and a +2 natural armor bonus which increases by 1 per 5 caster levels.\\\\
	In addition, you may grant the following traits to any form:\par
	$\bullet$ A land speed as that granted by Animalistic form (grants 2 legs if the target lacked a land speed).\par	
	$\bullet$ Scent.\par
	$\bullet$ 2 hoof attacks (Secondary, 1d4, 1d3 small). This may be granted once per pair of legs beyond the first.
}{}
\defineTalent{Anthropomorphic Transformation}{\textit{Shapeshift} into humanoids, or into a hybrid form that gives humanoid abilities and retains those of the natural form.}{
	You may grant a humanoid form with your \textit{shapeshift}. The humanoid form has 2 legs and 2 arms with hands that can manipulate objects as a human's can. The target can speak and gains knowledge of one language you also speak. It gains a land speed of 30 ft, and if the target's Intelligence is lower than 6 it is increased to 6.\par
	If you so choose, you may forgo applying additional traits to the
	target to instead allow the target to retain its natural attacks,
	special abilities, and movement types that were dependent on
	its previous form, in essence making the target a hybrid between a humanoid and its previous form.
}{}
\defineTalent{Aquan Transformation}{\textit{Shapeshift} into a sea creature or add a swim speed, Amphibious, and/or aquatic blindsense}{
	You may grant the form of a swimming animal or magical beast with your \textit{shapeshift}. The form has a head, fins, and no arms or legs. The target gains low-light vision and a 20 ft Swim speed which improves by 20 ft for every 5 caster levels. The target gains the Amphibious subtype and the ability to breath underwater. The target also gains a bite attack (Primary, 1d6, 1d4 small), Blindsense 30 ft (which only functions in water), and a +2 natural AC bonus, which increases by 1 for every 5 caster levels.\\\\
	In addition, you may add the following traits to any form:\par
	$\bullet$ The Amphibious subtype with the ability to breathe underwater.\par
	$\bullet$ A swim speed as that granted by the Aquan form.\par
	$\bullet$ Blindsense 30 ft (only in water)
}{}
\defineTalent{Avian Transformation}{\textit{Shapeshift} into a birdlike creature, or add wings and talons}{
	You may grant the form of a flying animal or magical beast with	your \textit{shapeshift}. The target gains a head, 2 legs, 2 wings, and a 30 ft land speed. The target gains low-light vision and 2 talon attacks (Primary, 1d4, 1d3 small) and a +2 natural AC bonus, which increases by 1 for every 5 caster levels. The target takes no damage when falling and may glide, moving with a speed of 30 ft with maneuverability (poor), but falling 1 ft for every 5 ft traveled. At 5th caster level, the target gains a fly speed of 30 ft with maneuverability (poor). This improves by 20 ft for each 5 additional caster levels.\\\\
	In addition, you may add the following traits to any form:\par
	$\bullet$ 2 talon attacks as those granted by the Avian form. This may be granted once per pair of legs the creature possesses. The target must possess wings or another means of being airborne to attack with talons.\par
	$\bullet$ 2 wings and its benefits or flight speed as that granted by the Avian form.\par
	$\bullet$ 2 wing attacks (Secondary, 1d4, 1d3 small) May be given once per pair of wings possessed.\par
}{}
\defineTalent{Bestial Reflexes}{Add Lunge, Leaping Attack, Pounce, and/or Trample to a form}{
	You may add the following traits to your forms:\par
	$\bullet$ Lunge: Choose one natural attack. As a full-attack action, you may make a single attack at double your normal reach with that weapon with a +4 bonus to your attack roll.\par
	$\bullet$ Leaping attack: As a standard action, you may jump, making a single attack at any point during the leap. You do not provoke an attack of opportunity for leaving a threatened square.\par
	$\bullet$ Pounce: You may make a full-attack after a charge.\par
	$\bullet$ Trample: As a full-round action, you may move up to your move speed, moving over and dealing slam damage (1d6+1-1/2 Str modifier, 1d4+1-1/2 Str modifier small) to any creatures smaller than yourself. Targets of a trample can make an attack of opportunity, but at a –4 penalty. If targets forgo an attack of opportunity, they may attempt to avoid you, making a Reflex save for half damage (DC 10 +1/2 your HD + your Str modifier). A trampling creature can only deal trampling damage to each target once per round, no matter how many times it moves over that creature.
}{}
\defineTalent{Bestial Spirit}{Add Trip, Ferocity, Animal Speech, and/or Rend to a form}{
	You may add the following traits to your forms:\par
	$\bullet$ Trip: Choose one natural attack. You may attempt a trip as a free action that does not provoke an attack of opportunity when you successfully hit with that attack.\par
	$\bullet$ Ferocity: You may stay conscious and continue to fight when at negative hit points, but lose 1 hit point per round you do so.\par
	$\bullet$ The ability to speak with animals and vermin.\par
	$\bullet$ Rend: target must possess claws; deals damage equal to 1 claw + 1 1/2 times Strength when successfully striking a target with 2 or more claw attacks in the same round.
}{}
\defineTalent{Dragon Transformation}{\textit{Shapeshift} into a dragon, or add a breath weapon}{
	You may grant the form of a dragon with your \textit{shapeshift}. The target gains a head, 4 legs with all the benefits of being a quadruped, a 40 ft move speed and a tail. The target gains a +2 natural armor bonus which increases by 1 per 5 caster levels, Darkvision 60 ft, a bite attack (Primary, 1d6, 1d4 small) and a breath weapon. This breath weapon is either a 60 ft line or a 30 ft cone, and deals either fire, electricity, acid, or cold damage as chosen at the time it is gained. The breath weapon deals 1d8 damage per 2 caster levels, and allows a Reflex save for half damage. The target must wait at least 1d4 rounds between uses of their breath weapon. A target may only possess one breath weapon at a time.\\\\
	In addition, you may grant the following traits to your forms:\par
	$\bullet$ A breath weapon, as that given by the dragon base form. \par
	$\bullet$ Double the size of a breath weapon (must possess a breath weapon to gain this trait).
}{}
\defineTalent{Elemental Transformation}{\textit{Shapeshift} into an elemental, or add energy resistance}{
	You may spend an additional spell point to grant the form of an elemental with your shapeshift. As an elemental's body is mutable, additional limbs or natural attacks cannot be added to this form through traits. The target gains a 30 ft move speed and a 25\% ability to ignore critical hits and precision damage, which increases by 25\% per 5 caster levels to a maximum of 100\%. The target gains 2 slam attacks (Primary, 1d6, 1d4 small), natural armor equal to 2 +1 per 5 caster levels, and one of the following packages depending on which elemental is being mimicked:\par
	\textit{Earth}\\
	You gain Darkvision 60 ft, a 30 ft burrow speed, and Earth Glide. You also gain a +2 Strength bonus, and Resistance to acid equal to your caster level.\par
	\textit{Fire}\\
	You gain Darkvision 60 ft, a +2 bonus to Dexterity, and the Burn special quality (1d4, increases by 1 die size per 5 caster levels). You also gain Resistance to fire equal to your caster level.\par
	\textit{Air}\\
	You gain a flight speed of 30 ft with Perfect maneuverability, which increases by 30 ft per 5 caster levels. You also gain Resistance to electricity equal to your caster level and the ability to create a Whirlwind (as an air elemental of the same size).\par
	\textit{Water}\\
	You gain waterbreathing and a 30 ft Swim speed which increases by 30 ft per 5 caster levels. You also gain Resistance to cold equal to your caster level, a +2 Constitution bonus, and the ability to create a Vortex (as a water elemental of the same size).\\\\
	You may also grant the following traits to your forms:\par
	$\bullet$ Elemental Resistance to either cold, electricity, fire, or acid equal to your caster level. You can take this trait multiple times, but Resistance to the same element does not stack with itself.
}{}
\defineTalent{Giant Traits}{Add rock catching and throwing to a form.}{
	You may add the following additional traits to your forms:\par
	$\bullet$ Rock catching.\par
	$\bullet$ Rock throwing (2d6, 2d4 small): this deals 1.5 times Strength damage, and has a range of 20 ft, + 10 ft per 2 caster levels.
}{}
\defineTalent{Greater Transformation}{Increase the number of traits you may apply with your shapeshift by 1.}{Increase the number of traits you may apply with your shapeshift by 1.}{	\addToCounter{charshapeshifttraitsCount}{1}}
\defineTalent{Mass Alteration}{You may spend an additional spell point to \textit{shapeshift} an additional 1 creature per 2 caster levels.}{When bestowing a \textit{shapeshift}, you may spend an additional spell point to \textit{shapeshift} an additional 1 creature per 2 caster levels at the same time. Each target must be within range and must gain the same \textit{shapeshift} form and traits.}{}
\defineTalent{Plant Transformation}{\textit{Shapeshift} into a plant creature, or increase a form's natural armor}{
	You may grant the form of a plant creature with your shapeshift. The creature has 2 ‘arms', which may be tree limbs or vines (adding limbs to a plant creature adds more appendages), has a move speed of 20 ft, 2 Slam attacks (Primary, 1d6, 1d4 small), and a +4 natural armor bonus that increases by 1 for every 5 caster levels.\\\\
	You may grant the following traits to your forms:\par
	$\bullet$ You may grant the target a +2 natural armor bonus, which stacks with other sources of natural armor.
}{}
\defineTalent{Ranged Alteration}{Increases the range of \textit{shapeshift} by one step}{
	You may shapeshift creatures at Close range instead of Touch range. You may take this talent multiple times. Each time it is selected, increase the range by 1 step (Close to Medium, Medium to Long).
	}
	{
	\ifnum 1 = #1
		\def\charshapeshiftrange{Close}
		\else\ifnum #1 = 2
			\def\charshapeshiftrange{Medium}
			\else\ifnum #1 > 2
				\def\charshapeshiftrange{Long}
			\fi
		\fi
	\fi
}

\defineTalent{Size Change}{Change a creature's size with \textit{shapeshift}}
	{\begin{wraptable}[9]{r}{90\unitlength}
		\raggedright\textbf{Table: Size and Reach}
		\rowcolors{2}{gray!25}{white}\small
		\begin{tabular}{@{}c@{~~~}c@{~~}c}
		\rowcolor{gray!50}
			\textbf{\textit{Size Category}} &\textbf{\textit{Space}}&\textbf{\textit{Reach}}\\
			Diminutive& 1 ft& 0\\
			Tiny &2.5 ft&0\\
			Small &5 ft&5 ft\\
			Medium &5 ft&5 ft\\
			Large &10 ft&10 ft\\
			Huge &15 ft&15 ft
		\end{tabular}
	\end{wraptable}
	As a trait, you may change a creature's size. You may enlarge or reduce a creature's size by one category, plus an additional size category per 5 caster levels. You cannot enlarge beyond Huge size, nor reduce a creature beyond Diminutive size. Creatures gain a +1 bonus to attack rolls and to AC, as well
	as a +2 bonus to Fly checks and a +4 bonus to Stealth checks for every size category they are reduced, and suffer a -1 penalty to attack rolls and AC, as well as a -2 penalty to Fly checks and a -4 to Stealth checks for every size category they are enlarged. (These numbers are doubled when moving to or from Diminutive size.) Ability scores are also adjusted according to the charts below; these increases and decreases are cumulative for each category increased or decreased (thus, moving from Medium to Huge would cumulate in a +8 bonus to Strength and	a -4 to Dexterity)\\
	\begin{tabular}{@{}l@{}l}
		\textbf{Table: Enlarge} & \textbf{Table: Reduce}\\
		\rowcolors{2}{gray!25}{white}
		\small\begin{tabular}{cccc}
			\rowcolor{gray!50}
			\textbf{\textit{Adjusted Size}} &\textbf{\textit{Str}}&\textbf{\textit{Dex}}&\textbf{\textit{Con}}\\
			Diminutive&-&-2&-\\
			Tiny &+2&-2&-\\
			Small &+4&-2&-\\
			Medium &+2&-2&-\\
			Large &+4&-2&+2\\
			Huge &+4&-2&+2
		\end{tabular}~ &
		\rowcolors{2}{gray!25}{white}
		\small\begin{tabular}{cccc}
			\rowcolor{gray!50}
			\textbf{\textit{Adjusted Size}} &\textbf{\textit{Str}}&\textbf{\textit{Dex}}&\textbf{\textit{Con}}\\
			Diminutive& -2& +2& -\\
			Tiny &-4&+2&-\\
			Small &-2&+2&-\\
			Medium &-4&+2&-2\\
			Large &-4&+2&-2\\
			Huge &-4&-&-2
		\end{tabular}
	\end{tabular}
}{}
\defineTalent{Subterranean Transformation}{\textit{Shapeshift} into a burrowing creature, or add a burrow speed and/or tremorsense}{
	You may grant the form of a subterranean animal or magical beast with your shapeshift. The form has a head, 4 legs, a 30 ft land speed, and a 15 ft burrow speed that increases by 15 ft per 5 caster levels. The target also gains Darkvision 60 ft, Tremorsense 20 ft, a bite attack (Primary, 1d6, 1d4 small), and a +2 natural armor bonus that increases by 1 per 5 caster levels.\\\\
	In addition, you may grant the following traits to any form:\par
	$\bullet$ A burrow speed as granted by the Subterranean form.\par
	$\bullet$ Tremorsense 20 ft.
}{}
\defineTalent{Tentacles}{Add tentacles, grab, or constrict to a form.}{
	You may add the following traits to your forms:\par
	$\bullet$ A tentacle attack (Secondary, 1d4, 1d3 small). You may grant this trait multiple times. The effects stack.\par
	$\bullet$ Grab: must be placed on a natural attack. On a successful attack, allows you to make a free grapple check. Does not provoke an attack of opportunity. You may grant this trait once per natural attack.\par
	$\bullet$ Constrict: Deal 1d6 damage (1d4 small) plus your Strength modifier on every successful grapple check.
}{}
\defineTalent{Undead Traits}{Add DR, undead resistances, blood drain (CL 10), fear aura (CL 10), and/or incorporeal (CL 15) to a form. Incorporeal costs an extra spell point.}{
	You may grant the following traits to your forms:\par
	$\bullet$ DR 5/bludgeoning or DR 5/slashing. This improves by 1 per 5 caster levels. At 1oth caster level, this may be changed to DR/Silver or Magic.\par
	$\bullet$ The subject counts as an undead creature when determining if it is healed or harmed by positive or negative energy, such as from a Cleric's channel energy class feature or the Life sphere.\par
	$\bullet$ A bonus on saving throws against mind-affecting effects, disease, poison, sleep, and stunning equal to half the caster level (minimum 1).\par
	$\bullet$ At 10th level, the target may be granted the blood drain special quality (1d2 Constitution; this improves by 1 die size for each 5 caster levels beyond 10th).\par
	$\bullet$ At 10th level, the target may be granted the fear aura special quality (30 ft, always active, creatures entering the area must pass a Will save against a DC of 10 + 1/2 HD + Charisma modifier or be shaken for as long as they are inside the aura; once a creature saves against this effect, they are immune for 24 hours).\par
	$\bullet$ At 15th level, the target may be made incorporeal. You must spend an additional spell point to apply this trait.
}{}
\defineTalent{Vermin Transformation}{\textit{Shapeshift} into a spider or insect, or add poison, climb spped, and/or webs to a form}{
	You may grant the form of a spider, insect, or other such creature with your shapeshift. The form has a head and either 6 or 8 legs, and a bite attack (Primary, 1d6, 1d4 small). You gain Darkvision 60 ft, a +2 natural armor bonus that increases by 1 per 5 caster levels, and a 30 ft Climb speed and land speed that improve by 15 ft per 5 caster levels.\\\\
	In addition, you may grant the following traits to your forms:\par
	$\bullet$ One natural attack deals poison on a successful attack. \textit{Poison:} Injury, DC 10 + 1/2 Hit Dice + Constitution modifier, frequency 1/round for 6 rounds, 1d2 Constitution damage, cure 1 save.\par
	$\bullet$ A Climb speed, as that granted by the vermin form.\par
	$\bullet$ Web: once per minute as a standard action, the creature may throw a web, as a net with a 10 ft range increment (total range 50 ft), which is effective against targets up to 1 size larger than the creature. The Escape Artist or Strength check DC to escape is 10 + 1/2 the creator's Hit Dice + Constitution modifier, with targets already caught suffering a -4 penalty. These webs may also be laid as a trap (Perception DC 20), covering an area up to 3x larger than the creature creating it. A 5 ft section of web has hp equal to the creator's Hit Dice and DR 5/-. A creature can move across its own web at its climb speed and can pinpoint the location of any creature touching its web. A web may support up to twice the weight of the creating creature.
}{}