\defineSphere{Conjuration}{You have made contracts with outsiders, calling them to	your side when you are in need.}{You have made contracts with outsiders, calling them to your side when you are in need.}
\def\summonduration{\arabic{charCLCount} minute\s}
\def\summonrange{adjacent to you}
\defineBaseAbility{Conjuration}{Summon}{Summon one companion \summonrange , which remains for as long as you concentrate. Spending 1 SP allows a companion to remain for \summonduration{} without concentration.}{
	As a standard action, you may spend a spell point to \textit{summon} a creature you have made a contract with (called a companion) causing it to appear in an adjacent square, ready to act on your following turn. You must concentrate to maintain the companion's presence, but may always spend an additional spell point to allow the summoned creature to remain for 1 minute per caster level without concentration.\par
	Companions can take many forms; a caster could contract with sympathetic angels or demons, elemental spirits, or primordial beings only given form after the contract is made. Thus, a companion could have the form of a knight in armor, a demonic dog, a flying anthropomorphic cat, or indeed virtually any other form. You cannot choose a companion with the exact same appearance as another creature.\par
	When you gain the Conjuration sphere, you automatically gain a single companion of your choice. If a companion is conjured multiple times during a day, they do not regain hit points or other resources spent. If a companion is reduced to 0 hp, they instantly disappear and cannot be summoned until the following day. A companion only recovers hp and resources (unless restored through the Heal skill or magical means) when the caster rests to recover spell points. A companion may be dismissed as a free action.\par
	Companions may not carry equipment or items back and forth when summoned and so cannot be used to store items in their home plane or bring items to the caster's plane. The exception to this rule is equipment gained through Conjuration talents.\par
	Whenever you gain a companion, they immediately gains 1 (form) talents of your choice. Whenever you select a (form) talent as a magic talent, apply its effects to only a single companion. You may select (form) talents multiple times, but no more than once per companion, unless the talent says otherwise.\par
	Every companion comes with one of the following base forms, chosen by the caster. Once made, this choice cannot be altered. Companions also gain power as their caster's power grows, according to \textbf{Table: Companion}.	
	}
\defineTalent{Additional Limbs (form)}{Add more limbs to a companion}{
	Your companion gains one of the following sets of limbs: a head, 2 arms, 2 legs, a tail. This does not automatically grant any additional attacks. See the alteration sphere for descriptions of bonuses gained from these limbs. A companion may gain this talent multiple times. The effects stack.}{}
\defineTalent{Aligned Creature (form)}{Companion gains Smite Alignment once per day plus once more per day per 7 HD}{
	Your companion is connected to great forces of alignment, such as angels, devils, or other extraplaners. Choose one end of the alignment spectrum your companion possesses (good, evil, lawful, chaotic). Your companion becomes connected to that alignment, and may smite a target of its opposed alignment once per day, as the Paladin class feature. Your companion may smite its opposed alignment an additional time per day for every 7 Hit Dice possessed.}{}
\defineTalent{Altered Size (form)}{Companion size changes}{
	Your companion increases or decreases permanently by 1 size category. A companion may gain this talent multiple times. The effects stack. A companion cannot become smaller than Diminutive or larger than Huge. Size changes cause the following changes to ability scores, which are cumulative:
	\begin{wraptable}{l}{90\unitlength}
		\rowcolors{2}{gray!25}{white}\small
		\begin{tabular}{ccccc}
			\rowcolor{gray!50}
			\textit{\textbf{Original Size}} & \textit{\textbf{New Size}} & \textit{\textbf{Str}} & \textit{\textbf{Dex}} & \textit{\textbf{Con}} \tabularnewline
			Small & Tiny & -4 & +2 & \tabularnewline
			Tiny & Diminutive & -2 & +2 & \tabularnewline
			Medium & Large & +4 & -2 & +2 \tabularnewline
			Large & Huge & +4 & -2 & +2 \tabularnewline
		\end{tabular}
	\end{wraptable}
}{}
\defineTalent{Animal Creature (form)}{Companion gains Scent and +20 ft +10 ft/2HD increase to base land speed}{
	Your companion has the qualities of a great beast. It gains a +20 ft bonus to its land speed, as well as the scent property. It gains an additional +10 ft bonus to its land speed for every 2 Hit Dice.}{}
\defineTalent{Armored Companion (form)}{Companion gains armor bonus of +1 +1 per odd HD}{Your companion gains armor as appropriate for its form and	appearance (a suit of armor, a tougher hide, buffeting winds, etc.). Your companion gains a +2 armor bonus, +1 at every odd Hit Die beyond 1st.}{}
\defineTalent{Avian Creature (form)}{Companion gains a 30 ft. + 10 ft/2 HD fly speed}{Your companion gains wings and a 30 ft fly speed with a maneuverability of average. This increases by 10 ft per 2 Hit Dice. Alternately, your companion may gain flight through magical means: it does not gain wings, instead gaining a maneuverability of perfect. This then becomes a supernatural ability, and is subject to anti-magic fields and other such limitations.}{}
\defineTalent{Battle Creature (form)}{Your companion gains weapon proficiencies and is summoned with two weapons with a +1 / 3 HD enhancement bonus.}
{Your companion is learned in the ways of war. It gains proficiency with all simple weapons and when summoned, appears with up to 2 weapons it is proficient with (masterwork, but of unremarkable composition). These weapons gain a +1 enhancement bonus for every 3 Hit Dice possessed to a maximum of +5. A companion may gain this form talent twice. If gained a second time, it gains proficiency with all martial weapons and treats its Hit Dice as fighter levels when meeting the prerequisites for feats.}{}
\defineTalent{Bestial (form)}{Companion gains additional natural attacks}{
	Your companion gains a new set of natural attacks chosen from the list below. A companion must possess the prerequisite limbs and cannot already have a natural attack attached to that limb. A companion may gain this talent multiple times. Each time they gain this talent, they gain a new set of natural attacks.\par
	$\bullet$ 2 claw attacks (primary, 1d4, 1d3 small, requires arms).\par
	$\bullet$ 2 hoof attacks (secondary, 1d4, 1d3 small, requires 2 legs,
	but creature must possess at least 4).\par
	$\bullet$ 1 tentacle attack (secondary, 1d4, 1d3 small, no requirement).\par
	$\bullet$ 2 wing buffets (secondary, 1d4, 1d3 small, requires wings).\par
	$\bullet$ 1 tail slap (secondary, 1d6, 1d4 small, requires tail).\par
	$\bullet$ 1 bite attack (primary, 1d6, 1d4 small, requires head).\par
	$\bullet$ 1 gore attack (primary, 1d6, 1d4 small, requires head).\par
	$\bullet$ 2 slam attacks (primary, 1d4, 1d3 small, requires arms).\par
	$\bullet$ 2 pincers (secondary, 1d6, 1d4 small, requires arms).\par
	$\bullet$ 1 sting (primary, 1d4, 1d3 small, requires tail).\par
	$\bullet$ 2 talons (primary, 1d4, 1d3 small, requires 2 legs and creature must be airborne to use).}{}
\defineTalent{Boon Companion (form)}{Companion stats determined as if your CL was 5 higher, max of your character level}{Your companion's abilities and Hit Dice are determined as if your caster level were 5 higher, to a maximum effective caster level equal to your character level.}{}
\defineTalent{Draconic Creature (form)}{Companion gains a breath weapon dealing 1d8/2 HD}{
	Your companion is draconic in nature. It gains a breath weapon which it may use once per 1d4 rounds. You must decide when this talent is gained whether your companion will breath a 30 ft cone or a 60 ft line and whether it deals fire, cold, acid, or electricity damage. It deals 1d8 damage per 2 Hit Dice (minimum: 1d8), and creatures may make Reflex saves (DC 10 + 1/2 Hit Dice + Constitution modifier) for half damage.}{}
\defineTalent{Earth Creature (form)}{Companion gains tremorsense 10 ft + 5 ft/2HD and a burrow speed of 15 ft + 5 ft/2HD}{Your companion is a creature used to living in the ground. It gains a 15 ft Burrow speed and Tremorsense 10 ft. Its Burrow speed and Tremorsense increase by 5 ft per 2 Hit Dice.}{}
\defineTalent{Elemental Creature (form)}{Your companion deals energy damage with all its natural attacks}{Your companion is a being attuned to a particular element. Choose either cold, fire, acid, or electricity. Your companion deals 1d3 damage of that element's type with all of its natural attacks. This damage increases by one die size per 5 Hit Dice.}{}
\defineTalent{Extra Companion}{Gain another companion}{You gain an additional companion. Whenever you summon a companion, you must select only one of your companions, although you may have multiple companions summoned at once. You may select this talent multiple times. Each time it is selected, gain another companion.}{}
\defineTalent{Fortified Companion (form)}{Your companion's Constitution increases by 2, +1 per 2 Hit Dice.}{Your companion's Constitution increases by 2, +1 per 2 Hit Dice.}{}
\defineTalent{Greater Summoning}{\textit{Summon} duration is increased to 10 minutes per caster level.}{When you spend a spell point to allow a companion to remain for 1 minute per caster level without concentration, it instead remains for 10 minutes per caster level.}{\def\summonduration{\domath{\value{charCLCount} * 10} minutes}}
\defineTalent{Lingering Companion (form)}{This companion remains for \ifinlist{Greater Summoning}{\charConjurationTalentsList}{1 day}{1 hour/level}.}{When you spend a spell point to allow this companion to	remain for 1 minute per caster level without concentration,	you may spend an additional spell point to allow it to remain	for 1 hour per level instead. If you also possess the Greater Summoning talent, your companion instead remains for 1 day, only disappearing when you rest to regain spell points. Once you have spent a spell point to summon such a creature for a full day, you may dismiss and re-summon this companion at will	without having to spend any additional spell points that day.}{}
\defineTalent{Link}{You gain a telepathic link to each of your companions. So long as you are on the same plane as one of your companions, you may communicate with that creature over any distance.}{You gain a telepathic link to each of your companions. So long as you are on the same plane as one of your companions, you may communicate with that creature over any distance.}{}
\defineTalent{Magic Attacks (form)}{Your companion's natural attacks are treated as magic weapons for the purpose of overcoming damage reduction, as cold iron at 7 Hit Dice, and adamantine at 14 Hit Dice}{Your companion's natural attacks are treated as magic weapons for the purpose of overcoming damage reduction. At 7 Hit Dice they are treated as cold iron for this purpose, and at 14 Hit Dice they are treated as adamantine.}{}
\defineTalent{Magical Companion (form)}{Companion gains +1 CHA /2 HD, spell pool equal to it's CHA modifier, and caster level of 1/2 HD.}{Your companion's Charisma increases by 1/2 its Hit Dice (minimum: +1). It also gains a spell pool equal to its Charisma modifier and a caster level equal to 1/2 its Hit Dice. The companion may select magic talents with its feats and treats Charisma as its casting ability modifier. With GM permission, your companion may also gain a casting tradition. A companion can never possess the Conjuration sphere.}{}
\defineTalent{Monstrous attacks (form)}{Companion gains trip, grab, pull, lunge, constrict, or poison}{Your companion gains one of the following traits. This trait applies an effect or ability to one of its natural attacks. See the Alteration sphere for details on these abilities. A companion may gain this talent multiple times, gaining a new trait each time. It cannot attach the same trait multiple times to the same natural attack.\par Trip, grab, pull, lunge, constrict, poison.}{}
\defineTalent{Natural Aspect (form)}{Companion gains pounce, leaping attack, rend, trample, rock catching, rock throwing, or fast healing.}{Your companion gains one of the following special monster qualities. A companion may gain this talent multiple times. Each time it is gained, they gain a new trait from the list. See the Alteration sphere for a description of each ability.\par Pounce, leaping attack, rend, trample, rock catching, rock throwing, Fast Healing 1.}{}
\defineTalent{Powerful Companion (form)}{Your companion's Strength increases by 2, +1 per 2 Hit Dice.}{Your companion's Strength increases by 2, +1 per 2 Hit Dice.}{}
\defineTalent{Quick Companion (form)}{Your companion's Dexterity increases by 2, +1 per 2 Hit Dice.}{Your companion's Dexterity increases by 2, +1 per 2 Hit Dice.}{}
\defineTalent{Ranged Summoning}{You can summon companions within Close range}{When you summon a companion, they may appear in any square within Close range, rather than only in an adjacent square.}{\def\summonrange{within Close range}}
\defineTalent{Resistance (form)}{Companion gains energy resistance equal to 5 + HD}{Choose one energy type from the following list: fire, acid, cold, electricity, or sonic. Your companion gains Resistance to that element equal to 5+ its Hit Dice. You may select this talent multiple times, granting Resistance against a different element each time.}{}
\defineTalent{Roguish Creature (form)}{Companion gains sneak attack and can take rogue talents as feats}{Your companion is a creature of guile. Your companion deals +1d6 sneak attack damage as the rogue class feature, which increases to +2d6 at 7 Hit Dice and +3d6 at 14 Hit Dice. In addition, your companion may select rogue talents as feats. At 10 Hit Dice, it can select advanced talents as feats.}{}
\defineTalent{Shadow Creature (form)}{Companion gains darkvision, +8 to stealth in darkness, low-light vision, and deals and takes half damage to and from corporeal creatures and full damage to and from incorporeal creatures}{Your companion is a being made of shadow. It gains Darkvision 60 ft, low-light vision, and a +8 racial bonus to Stealth checks made in dim light or darkness. Your companion takes half damage from attacks and magic originating from corporeal creatures and only deals half damage to corporeal creatures with its own attacks and magic. However, your companion deals full damage to incorporeal creatures and suffers full damage from incorporeal creatures.}{}
\defineTalent{Shield Bearer (form)}{Your companion gains a shield with a +1 / 3 HD enhancement bonus}{Your companion gains the shield proficiency feat, and when summoned, appears carrying a type of shield it is proficient with. If the creature possesses the Tower Shield Proficiency feat, this may be a tower shield. The shield is masterwork, but of unremarkable composition. This shield gains a +1 enhancement bonus for every 3 Hit Dice your companion possesses, to a maximum of +5.}{}
\defineTalent{Skillful Companion (form)}{Companion's intelligence becomes 10, gains +1 skill point per HD, and 3 more class skills}{Your companion's Intelligence increases by 3 (raising its base Intelligence to 10), and it gains an additional skill point per Hit Die (raising its total to 3 per level). In addition, it gains 3 new class skills of your choice.}{}
\defineTalent{Transformative (form)}{Companion can change appearance at will}{Your companion can change its appearance at will. It gains Disguise as a class skill and can make Disguise checks as a standard action. This is a spell-like ability, with a caster level equal to its Hit Dice.}{}
\defineTalent{Undead Creature (form)}{Companion gains undead-like traits}{
	Your companion mimics the properties of undead. It is healed by negative energy and harmed by positive energy. While it is still an Outsider, magical effects and spells that specifically target undead may affect the Companion as if it were undead. The companion also gains +2 Channel Resistance, as well as a +2 bonus on saves against disease, exhaustion, fatigue, paralysis, poison, sleep effects, and stunning. These bonuses and channel resistance increase by +1 per 2 Hit Dice.\par
	You may take this talent twice. If taken twice, your companion gains immunity to disease, exhaustion, fatigue, paralysis, poison, sleep effects, and stunning, and your companion no longer needs to breath, granting it immunity to drowning, suffocation, or gas-based effects.}{}
\defineTalent{Water Creature (form)}{Companion gains a swim speed of 30 ft + 10 ft / 2 HD, water breathing, and aquatic blindsense 15 ft + 5 ft / 2 HD.}{Your companion gains a 30 ft Swim speed, the ability to breathe underwater, and Blindsense 15 ft (only in water). For every 2 Hit Dice, the Swim speed increases by 10 ft and the Blindsense increases by 5 ft.}{}
\defineTalent{Willful Companion (form)}{Companion gains +2 WIS +1 / 2 HD and rolls twice and takes the better result on all will saves}{Your companion's Wisdom increases by 2, +1 per 2 Hit Dice. In addition, whenever your companion rolls a Will saving throw, it may roll twice and take the higher result. If it may already roll twice and take the higher result, it instead rolls three times.}{}