\defineSphere{Destruction}{You can summon pure energy to strike down foes.}{You can summon pure energy to strike down foes.}
\newCounter{chardestructiveblastdamage}
\def\chardestructiveblastrange{Close}
\defineBaseAbility{Destruction}{Destructive Blast}{Deals \setCounter{chardestructiveblastdamage}{(\value{charCLCount} + 1) / 2}\arabic{chardestructiveblastdamage}d6 bludgeoning damage within \chardestructiveblastrange{} range, can be modified by blast type and blast shape talents; Spend one spell point to increase damage to \CLMinTwo d6.}{
	As a standard action, you may deliver a burst of blunt magical force as a melee touch attack or a ranged touch attack within Close range. A\textit{detructive blast} deals 1d6 bludgeoning damage, plus 1d6 for every two caster levels after 1st. This damage bypasses DR/magic, but being bludgeoning in nature, does not automatically bypass other forms of damage resistance.\par
	When augmenting a\textit{detructive blast} with Destruction talents, you may only apply 1 blast type talent and 1 blast shape talent to each individual\textit{detructive blast}.\par
	You may spend 1 spell point when making a\textit{detructive blast} to increase the damage dealt to one damage die per caster level (minimum: 2d6).}

\defineTalent{Acid Blast (blast type)}{You may change your \textit{detructive blast} from bludgeoning damage to acid damage, and deal 1 point per die extra damage next round}{You may change your\textit{detructive blast} from bludgeoning damage to acid damage. Any creature damaged by your acid blast suffers 1 point of acid damage per damage die the following round.}{}
\defineTalent{Air Blast (blast type)}{Change \textit{detructive blast} damage to nonlethal and bull rush with CMB of +\domath{\value{charCLCount}+\value{charCastingModCount}}}{You may change your\textit{detructive blast} into a blast of air. An air blast deals nonlethal damage. You may make a Bull Rush at range against the target or targets affected by your air blast. Only a target successfully struck by the blast (or one that fails their Reflex saving throw if one was required) is affected. Your CMB for this check is equal to your caster level + your casting stat modifier, and all targets are pushed from the point of origin of the effect (usually yourself, but if using a talent such as Explosive Orb, it would be the center of the blast. If using Energy Wall, each square of wall is considered the center of effect for those who enter that section. If using Guided Strike, you may choose from which direction you want to push the target, even pushing them up or down if you should desire. Pushing a target into the ground knocks them prone if the Bull Rush is successful.). If the target is knocked into a solid object, they suffer 1d6 bludgeoning damage, + 1d6 for every 5 ft they would have continued past the barrier. You do not move with the targets of your Bull Rush.}{}
\defineTalent{Blast Trap (blast shape)}{Place a \textit{detructive blast} as a trap in a 5-ft square which triggers when entered..  You may only have \arabic{charblasttraps} trap\s[charblasttraps]{} trap active at once}{You may place a\textit{detructive blast} onto an adjacent, unoccupied 5 ft square. Any creature who steps onto that square is affected by your\textit{detructive blast}, and is allowed a Reflex save for half damage. A blast trap lasts for 10 minutes per caster level before becoming inert. This is a magical trap with a Perception DC and Disable Device DC equal to the blast's save DC. You may only have one active blast trap at a time; placing a second trap	deactivates the first. You may select this talent multiple times. Each time it is taken, increase the number of blast traps you may have active at once by 1.}{\newCounter{charblasttraps}\setCounter{charblasttraps}{#1}}
\defineTalent{Crafted Blast}{\textit{Destructive blasts} without a (blast type) do your choice of bludgeoning, piercing, or slashing, and rolled 1's and 2's change to 3's}{When making a\textit{detructive blast} unaltered by a (blast type) talent, you may change the damage of the\textit{detructive blast} to be either bludgeoning, piercing, or slashing, and may change all rolled 1's and 2's to 3's.}{}
\defineTalent{Crystal Blast (blast type)}{\textit{Destructive blast} does piercing damage, uses d4s instead of d6s, creates difficult terrain, and target must make  a reflex save or be entangled and can't move.}{Your\textit{detructive blast} becomes an explosion of crystal, growing where it strikes. A crystal blast uses d4's instead of d6's as its damage die and deals piercing damage. The target of your crystal blast must pass a Reflex save or be entangled and unable to move. In addition, the target's square (or the blast's affected area) becomes overgrown with crystal and counts as difficult terrain. Breaking free of the entangled condition is a move action, requiring either a Strength check or an Escape Artist check against the crystal blast's save DC. A target may also destroy the crystal on a square or creature by dealing 3 damage per caster level to the crystal. This removes the entangled condition from the creature and destroys the difficult terrain. Crystal disappears after 1 minute.}{}
\defineTalent{Electric Blast (blast type)}{\textit{Destructive blast} deals electricity damage and enemies wearing metal armor take -3 to AC or saves against this blast}{You may change the damage type of your \textit{destructive blast} to electricity. Targets wearing metal armor or primarily comprised of metal suffer a -3 penalty to AC and to saving throws against an electric blast. An electric blast can ignite combustibles, and melt metals with a low melting point, such as lead, gold, copper, silver, or bronze.}{}
\defineTalent{Energy Sphere (blast shape)}{Spend a spell point to shape \textit{destructive blast} into a lasting sphere that fills a 5 ft square, lasts \arabic{charCLCount} round\s and you can move \domath{\value{charCLCount} / 2 * 5 + 20} ft as a move action.}{
	You may spend a spell point to shape your \textit{destructive blast} into a non-instantaneous sphere that fills a 5 ft square. Any creature within this space is dealt damage from your \textit{destructive blast} (Reflex negates). This sphere lasts for 1 round per caster level and has a 20 ft fly speed +5 ft per 2 caster levels and Perfect maneuverability. Wind does not affect its course. As a move action, you may direct this sphere to move to a new location and strike a new target. Your sphere stops to attempt to deal damage whenever it enters a space with a creature. Your sphere has no mass and does not impede movement, and your sphere must stay within your \textit{destructive blast} range or disappear.}{}
\defineTalent{Energy Wall (blast shape)}{Spend a spell point to shape \textit{destructive blast} into a \domath{20 * \value{charCLCount}} ft long, 20 ft high wall, or a \domath{5 * \HalfCLMinOne} ft radius hemispherical shell, either of which lasts \arabic{charCLCount} round\s.}{
	You may spend a spell point to shape your \textit{destructive blast} into either a wall up to 20 ft per caster level or a hemisphere with a radius up to 5 ft per 2 caster levels (minimum: 5 ft). This wall extends up to 20 ft high and lasts for 1 round per caster level. The wall does not block line of effect, line of sight, projectiles, or thrown objects. Creatures passing through your wall suffer your \textit{destructive blast}'s damage and effects as normal. Creatures standing in the wall's space when it is created are allowed a Reflex save to avoid damage.}{}
\defineTalent{Energy Blade (blast shape)}{As a standard action, you may make a single weapon attack in conjunction with making a \textit{destructive blast}. Any creature damaged by the attack is also struck by the \textit{destructive blast}.}{As a standard action, you may make a single weapon attack in conjunction with making a \textit{destructive blast}. Any creature damaged by the attack is also struck by the \textit{destructive blast}.}{}
\defineTalent{Explosive Orb (blast shape)}{You may spend a spell point to make a \textit{destructive blast} as a \domath{\value{charCLCount} / 5 * 5 + 10} ft radius burst effect centered anywhere within range. Reflex for half damage}
{You may spend a spell point to make a \textit{destructive blast} as a burst effect centered anywhere within range. This burst has up to a 10 ft radius, + 5 ft per 5 caster levels. Affected creatures are allowed a Reflex saving throw for half damage.}{}
\defineTalent{Extended Range}{Increase the range of your \textit{destructive blast} to \chardestructiveblastrange.}{Increase the range of your \textit{destructive blast} by 1 range level (Close to Medium, Medium to Long). You may select this talent multiple times. The effects stack.}{
	\ifnum 1 = #1
		\def\chardestructiveblastrange{Medium}
		\else\ifnum #1 > 1
		\def\chardestructiveblastrange{Long}
		\fi\fi
	}
\defineTalent{Force Blast (blast type)}{Spend a spell point to change \textit{destructive blast} to force damage and knock targets prone if they fail a Reflex save.}{You may spend a spell point to change the damage type of your \textit{destructive blast} to force. Any creature damaged by a force blast must pass a Reflex save or fall prone.}{}
\defineTalent{Fire Blast (blast type)}{\textit{Destructive blast} deals fire damage and targets must make a reflex save or catch fire.}{You may change the damage type of your \textit{destructive blast} to fire. Targets who take damage from your fire blast must make a Reflex save or catch fire. A burning creature takes 1d6 damage the following round, plus 1d6 per round until the flames are extinguished. Each round the target may make another Reflex save to attempt to extinguish the flames. Rolling on the ground or using a blanket to smother the flames (a full-round action) grants the target a +4 bonus to that round's saving throw.}{}
\defineTalent{Frost Blast (blast type)}{\textit{Destructive blast} deals cold damage and targets must make a fortitude save or be staggered for 1 round}{You may change the damage type of your \textit{destructive blast} to cold. Targets who take damage from your frost blast must make a Fortitude save or be staggered for 1 round.}{}
\defineTalent{Guided Strike (blast shape)}{You may spend a spell point to add a +20 circumstance bonus to your \textit{destructive blast}'s attack roll.}{You may spend a spell point to add a +20 circumstance bonus to your \textit{destructive blast}'s attack roll.}{}
\defineTalent{Nether Blast (blast type)}{\textit{Destructive blast} deals negative energy damage and must make a will save or be shaken 1 round. Undead take no damage but are frightened 1 round on a failed will save.}{You may change the damage type of your \textit{destructive blast} to negative energy. Targets damaged by your nether blast must pass a Will saving throw or be shaken for 1 round. A nether blast does not damage undead; instead, the undead must make a Will save or become frightened for 1 round.}{}
\defineTalent{Rebuff (blast shape)}{
	Instead of doing damage, \textit{destructive blast} gives target a +\domath{\value{charCLCount} / 5 * 2 + 2} cover bonus to AC and a +\domath{\value{charCLCount} / 5 + 1} cover bonus to Reflex saves.  Spend a spell point to use as an Immediate action, or to affect all targets within \domath{\value{charCLCount} / 5 * 5 + 10} ft of you. Spend two spell points for both effects.}{
	You may use your \textit{destructive blast} to shield a target within range from ranged weapons, area effects, or even other \textit{destructive blast}s for 1 round, giving them the benefits of evasion, a +2 cover bonus to AC, and a +1 cover bonus to their Reflex saves. Multiply these bonuses by 2 at 5th caster level, by 3 at 10th caster level, by 4 at 15th caster level, and by 5 at 20th caster level.\par
	By spending a spell point, you may perform a rebuff as an immediate action, or provide the benefits to all targets within 10 ft of you plus 5 ft per 5 caster levels. You may spend 2 spell points to gain both of these benefits with the same rebuff.}{}
\defineTalent{Sculpt Blast (blast shape)}{Spend a spell point make a \textit{destructive blast} as a Medium range line or a Close range cone. Reflex save for half damage.}{You may spend a spell point to create a \textit{destructive blast} as an area effect, affecting your choice of either a Close-range cone or a Medium-range line, each emanating from yourself. You do not need to make any attack roll for area attacks, but creatures in the effect are allowed a Reflex saving throw for half damage.}{}
\defineTalent{Stone Blast (blast type)}{\textit{Destructive Blast} deals slashing, piercing, and bludgeoning damage and is treated as nonmagical for purposes of spell resistance, AMF, or other antimagic defenses.}{You may change the damage type of your destructive blast to slashing, piercing, and bludgeoning. A stone blast ignores spell resistance, spell turning, and can penetrate a globe of invulnerability, anti-magic field, or antimagic circle, and is not treated as a spell or magical effect for creatures or classes that gain a bonus to saving throws against magic. These stones disappear after 1 minute.}{}
\defineTalent{Thunder Blast (blast type)}{You may change the damage type of your destructive blast to sonic. Targets who take damage from your thunder blast must pass a Fortitude saving throw or be deafened for 2d4 rounds.}{You may change the damage type of your destructive blast to sonic. Targets who take damage from your thunder blast must pass a Fortitude saving throw or be deafened for 2d4 rounds.}{}