\defineSphere{Divination}{You can predict the future and gain information not available to the usual 5 senses.}{You can predict the future and gain information not available to the usual 5 senses.}
\def\chardivinerange{Medium}
\def\chardivinecastingtime{10 minutes}
\defineBaseAbility{Divination}{Divine}{Spend \chardivinecastingtime{} casting to activate, or one standard action if you spend a spell point. Duration is concentration, and you must spend a full-round action to concentrate.  You can \textit{divine} for magical auras\ifinlist{Death}{\charSpheresList}{, undead}{}\ifinlist{Mind}{\charSpheresList}{, charms}{}\ifinlist{Nature}{\charSpheresList}{, elements}{}\ifinlist{Fate}{\charSpheresList}{, alignment}{}\ifinlist{Life}{\charSpheresList}{, living creatures}{}\ifinlist{Illusion}{\charSpheresList}{, illusions}{}\ifinlist{Weather}{\charSpheresList}{, weather}{}\ifinlist{Conjuration}{\charSpheresList}{, unnatural creatures}{}. This detects the desired phenomena out to \chardivinerange{} range. You may only \textit{divine} for one thing at once.}{
	You may \textit{divine} to gain information. To \textit{divine}, you must spend 10 minutes meditating, although you may spend a spell point to decrease this time to a single standard action.  \textit{Divining} always has a duration of concentration, but you must spend a full-round action concentrating (you can take no other action, not even walking); you are flat-footed while  \textit{divining}. \par
		\begin{wraptable}[7]{l}{90\unitlength}
			\raggedright\textbf{Table: Aura Strength}
			\rowcolors{2}{gray!25}{white}\small
			\begin{tabular}{cc}
				\rowcolor{gray!50}
				\textit{\textbf{Caster Level}} & \textit{\textbf{Aura Strength}}\tabularnewline
				1 - 5 & Faint \tabularnewline
				6 - 11 & Moderate \tabularnewline
				12 - 20 & Strong\tabularnewline
				21+ & Overwhelming \tabularnewline
			\end{tabular}
		\end{wraptable}
	When you \textit{divine}, you detect the strength and location of all magical auras within Medium range. You do not know the exact caster level of an item or spell, but you may sense the aura's general strength according to the chart below. To determine the spell school or sphere of the effect, you must pass a Knowledge (arcana) check with a DC equal to 15 + 1/2 the caster level.\par
	\begin{wraptable}[7]{l}{145\unitlength}
		\raggedright\textbf{Table: Lingering Aura}
		\rowcolors{2}{gray!25}{white}\small
		\begin{tabular}{cc}
			\rowcolor{gray!50}
			\textit{\textbf{Original Strength}} & \textit{\textbf{Duration of Lingering Aura}}\tabularnewline
			Faint & 1d6 rounds \tabularnewline
			Moderate & 1d6 minutes \tabularnewline
			Strong & 1d6$\times$10 minutes \tabularnewline
			Overwhelming & 1d6 days \tabularnewline
		\end{tabular}
	\end{wraptable}
	A magical aura lingers after its original source dissipates (in the case of a spells and sphere effects) or is destroyed (in the case of a magic item). In such a case, \textit{divining} reveals an aura strength of dim (even weaker than a faint aura). How long the aura lingers at this dim level depends on its original power.\par
	When using Spellcraft to identify the properties of a magic item, you may use \textit{divine} in place of the detect magic spell. Outsiders and elementals are not magical in and of themselves, but if they are summoned, the conjuration effect registers.  \textit{Divining} can penetrate most barriers, but 1 foot of stone, 1 inch of common metal, a thin sheet of lead, or 3 feet of wood or dirt blocks it.\par
	Alternate Divinations: If you possess certain other spheres,
	you may \textit{divine} for information other than magical auras. These
	alternate divinations are detailed below.
	\begin{wraptable}[7]{l}{90\unitlength}
		\raggedright\textbf{Chart: Undead}
		\rowcolors{2}{gray!25}{white}\small
		\begin{tabular}{cc}
			\rowcolor{gray!50}
			\textit{\textbf{HD}} & \textit{\textbf{Aura Strength}}\tabularnewline
			1 or lower & Faint \tabularnewline
			2 - 4 & Moderate \tabularnewline
			5 - 10 & Strong\tabularnewline
			11 or higher & Overwhelming \tabularnewline
		\end{tabular}
	\end{wraptable}
	\par\textit{Divine Undead:} If you possess the Death sphere, you may \textit{divine} for undead creatures. The strength of an undead aura is determined according to Chart: Undead. \par
	\textit{Divine Charm:} If you possess the Mind sphere, you may \textit{divine} for the presence of charm, compulsion, possession, and mind sphere effects. You do not need to make a Knowledge (arcana) check to identify the school or sphere of these abilities.\par
	\textit{Divine Elements:} If you possess the Nature Sphere, you may \textit{divine} for the elements. If you possess the fire package you may \textit{divine} the presence and strength of fires. If you possess the water package you may \textit{divine} the location and size of bodies of water. If you possess the earth package you may \textit{divine} and identify the presence of ore deposits, gems, stone, and metals. If you possess the plant package you may \textit{divine} the location of plantlife and plant creatures, as if detecting undead.\par
	\textit{Divine Alignment:} If you possess the Fate sphere, you may \textit{divine} for a specific part of the alignment spectrum: evil, good, lawful, or chaotic. The strength of these auras are determined according to Chart: Alignment.\\\\
		{\textbf{Chart: Alignment}\rowcolors{2}{white}{gray!25}\small\\
		\begin{tabular}{>{\centering}p{45\unitlength}>{\centering}p{15\unitlength}>{\centering}p{15\unitlength}c>{\centering}p{15\unitlength}c}
			\rowcolor{gray!50}
			\textit{\textbf{Creature/Object}} & \multicolumn{5}{c}{\textit{\textbf{Aura Power}}}		\tabularnewline
			\rowcolor{gray!50}
			& \textit{None} & \textit{Faint} & \textit{Moderate} & \textit{Strong} & \textit{Overwhelming} \tabularnewline
			Aligned Creature (HD) & 4 or lower & 5-10 & 11-25 & 26-50 & 51 or higher\tabularnewline
			Aligned Undead (HD) & -- & 2 or lower & 3-8 & 9-20 & 21 or higher\tabularnewline
			Aligned Outsider (HD) & -- & 1 or lower & 2-4 & 5-10 & 11 or higher\tabularnewline
			Cleric of aligned deity (class levels) & -- & 1 & 2-4 & 5-10 & 11 or higher\tabularnewline
			Aligned magic item or spell (caster level) & 5 or lower & 6-10 & 11-15 & 16-20 & 21 or higher
		\end{tabular}}\\\par
	Traps, poisons, and other potential perils have no alignment. Creatures with aligned intents (killing in anger, aiding those in need for their own sakes, etc.) may temporarily detect according to their actions.\par
	\textit{Divine Life:} If you possess the Life sphere, you may \textit{divine} the location of nearby living creatures. These creatures do not have auras; you instead determine their condition according to the list below:
		\par$\bullet$ Normal: Has at least 90% of full normal hit points,
		free of disease.
		\par$\bullet$ Fair: 30\% to 90\% of full normal hit points remaining.
		\par$\bullet$ Poor: Less than 30\% of full normal hit points remaining, afflicted with a disease, or suffering from a debilitating injury.
		\par$\bullet$ Weak: 0 or fewer hit points remaining, afflicted with a disease that has reduced an ability score to 5 or less, or crippled.\par
	\textit{Divine Illusions:} If you possess the Illusion Sphere, you may \textit{divine} for illusions. This grants you a free Will save or Perception check (in the case of illusionary disguises or invisibility) against any illusions or invisibility within the area.\par
	\textit{Divine Weather:} If you possess the Weather sphere, you may \textit{divine} the weather at your location for the next 24 hours, providing you with advance warning of storms, tornadoes, and so on. This reveals only the weather that would arise naturally and does not take into acCount any magical occurrences that might change the weather.\par
	\textit{Divine Unnaturals:} If you possess the Conjuration Sphere, you may \textit{divine} the presence of outsiders and aberrations. In all other ways, this functions as  \textit{divining} for undead.\par
	Some talents are marked (divine). These talents give you additional things you may \textit{divine} for other than magical auras. Only one such talent can be applied to an individual use of \textit{divine}.}
\defineBaseAbility{Divination}{Sense}{You may grant yourself\ifinlist{Grant Sense}{\charDivinationTalentsList}{ or a touched ally}{} a new sense for \arabic{charCLCount} hour\s. You can grant yourself \textit{Read Magic}, and gain new options for senses when you take (sense) talents.}{As a standard action, you may grant yourself paranormal senses for 1 hour/level. When you gain the Divination sphere, you gain the following \textit{sense}.
	\par\textit{Read Magic:} You may spend a spell point to gain a \textit{sense} that allows you to decipher all magical writings, such as those found in books, scrolls, on weapons, or in other places intelligible to you. This does not invoke the magic contained in the writing, although it may do so in the case of a cursed or trapped scroll. Furthermore, once you have read a magical inscription through this ability, you are thereafter able to read that particular writing even without this \textit{sense}. You can read at the rate of one page (250 words) per minute. You can identify glyphs, runes, and symbol spells with a Spellcraft check (DC 10 + 1/2 caster level).
	\par Some talents are marked (sense). These talents grant you additional \textit{senses} you may bestow upon yourself. There is no limit to the number of different \textit{senses} you may have active at a time.\newpage}
\defineTalent{Battlefield Sense (sense)}{Spend a spell point to grant yourself immunity to flanking, except by creatures with at least \domath{\value{charCLCount}+4} rogue levels.}{You may spend a spell point to grant yourself greater perception. You can no longer be flanked, except by a creature with 4 more rogue levels than your caster level.}{}
\defineTalent{Blindfolded Oracle (sense)}{Spend a spell point to gain Blindsense 30 ft. while your eyes closed, or spend two spell points to instead gain Blindsight.}{You may spend a spell point to grant yourself Blindsense 30 ft. You must close your eyes to use this ability. For the purpose of this ability, opening and closing your eyes is a free action you may take once per round. You may spend an additional spell point to upgrade this ability to Blindsight.}{}
\defineTalent{Detect Scrying (sense)}{You detect all attempts to scry targeted within 30 ft of you, and all such attempts fail unless the caster succeeds at a magic skill check against you or you allow the attempt to succeed. You also detect creatures using divination spells or the \textit{divine} ability within 30 ft of you.}{
	You may spend a spell point to detect the scryings of others. Any attempt to scry or \textit{divine} on a location or creature within 30 ft of you (unless you purposefully lower this defense) becomes impossible unless the caster succeeds in a magic skill check against you. In addition, you sense if any creature within range is using the \textit{divine} ability or a divination spell, as well as the location of any sensors in the area (such as with the viewing talent or the clairaudience/clairvoyance spell).
	\par You become aware of any attempt to scry on you, such as with a divination (scrying) school spell or the scrying advanced divination talent. If these spells and effects originate within your \textit{sense}'s area, you immediately know their location. Otherwise, if you match or exceed the other caster in an opposed magic skill check, you gain a visual image of the diviner and know their direction and distance from you.
	\par You may suppress or resume this \textit{sense} as a free action.}{}
\defineTalent{Detect Secrets (divine)}{Spend a spell point to \textit{divine} things designed to be hidden (secret doors, hidden caches, etc.) This does not detect normal doors.}{You may spend a spell point to \textit{divine} for things expressly designed to be hidden. This includes secret doors, hidden caches, and secret compartments. Not only does this detect the presence of such secrets, but it also gives you knowledge of their trigger mechanisms. This only detects doors, passages, and openings specifically designed to avoid detection.}{}
\defineTalent{Divine Future (divine)}{Divine the future, granting you a +1d4 \newCounter{chardivinefuturebonus}\setCounter{chardivinefuturebonus}{\value{charCLCount} / 5} \ifnum \value{chardivinefuturebonus} < 1 \else + \arabic{chardivinefuturebonus}\fi insight bonus to \arabic{chardivinefutureuses} d20 roll\s[chardivinefutureuses] you make within the next day. You may instead apply the bonus to an ally's roll as an immediate action if they can see and hear you.}{
	You may \textit{divine} for a glimpse of the future, giving yourself insight into the happenings of that day. At any time during that day, you may add an insight bonus equal to 1d4 +1 per 5 caster levels to one attack roll, skill check, saving throw, ability check, or combat maneuver roll you are about to make. As an immediate action, you may grant this benefit to an ally who can both see and hear you.
	\par You can only have one use of this ability waiting to be used at a time. You may take this talent multiple times, to a maximum of 5 times. Every time you gain this talent beyond the first, you may use this ability an additional time during that day. Every time you \textit{divine} for the future, you regain all your uses of this ability for that day.}{\newCounter{chardivinefutureuses}\setCounter{chardivinefutureuses}{#1}}
\defineTalent{Divine Information (divine)}{Spend a spell point to make a knowledge check untrained, or reroll a failed knowledge check\ifnum \value{HalfCL} > 0 , either way with a +\arabic{HalfCL} bonus\fi.}{You may spend a spell point to \textit{divine} for information. This grants you the ability to reroll a failed Knowledge check (or to make a Knowledge check untrained), with an insight bonus equal to 1/2 your caster level. You may only \textit{divine} for information once per Knowledge check.}{}
\defineTalent{Dowsing (divine)}{Spend a spell point to \textit{divine} the location of a creature or object. This can be specific or general--in the latter case you only locate the nearest such creature or object.}
{You may spend a spell point to \textit{divine} the location of a creature or object within range. This may be a specific creature or object or a kind of creature or object, but either way you must have a clear mental image of the creature or object to \textit{divine} for it (thus, you could not \textit{divine} broadly for traps, creatures of a broad creature type, etc.). If  \textit{divining} for a kind of creature or object, you only locate the closest item of that kind. This method of using \textit{divine} is not blocked by wood or stone, but is still blocked by lead.}{}
\defineTalent{Fast Divinations}{\textit{Divining} takes 1 minute instead of 10 minutes.}{\textit{Divining} takes 1 minute instead of 10 minutes.}{\def\chardivinecastingtime{1 minute}}
\defineTalent{Foreshadow (sense)}{You can spend a spell point to \textit{sense} the future, warning you of danger. This grants a +\domath{\value{charCLCount} / 10 + 1} dodge bonus to AC and a +\domath{\value{charCLCount} / 10 + 2} bonus to Reflex saves and Initiative checks, and you are not flat-footed during the surprise round.}{You may spend a spell point to gain a \textit{sense} that warns you of impending danger. You are not flat-footed during the surprise round, and gain a +1 dodge bonus to AC, and a +2 bonus to Reflex saves and Initiative checks. These bonuses increase by 1 for every 10 caster levels possessed.}{}
\defineTalent{Ghost Sight (sense)}{Spend a spell point to gain a +\arabic{charCLCount} bonus on Perception checks to notice invisible creatures, and if you detect an invisible creature they gain no advantages from that invisibility.}{You may spend a spell point to gain a \textit{sense} that adds your caster level to Perception checks made to notice invisible or ethereal creatures. If you succeed at this check, the creature's outline becomes visible to you. This negates both the usual penalties you would suffer attacking an invisible creature, and the bonuses the creature would normally gain against you. This continues until you lose line of sight to the creature, in which case you must succeed at a new Perception check to see them.}{}
\defineTalent{Grant Sense}{You may grant your \textit{senses} to a touched target instead of only yourself.}{You may grant your \textit{senses} to a touched target instead of only yourself.}{}
\defineTalent{Greater Divine}{Your \textit{divine} ability works out to Long range instead of Medium range.}{Your \textit{divine} ability works out to Long range instead of Medium range.}{\def\chardivinerange{Long}}
\defineTalent{Logos (sense)}{Spend a spell point to understand all language. You may spend an additional spell point to be understood by any creature with a language}{You may spend a spell point to understand all spoken and written words, regardless of language. You may spend an additional spell point to also be understood by any creature with a language. You do not learn the creature's language, but instead every creature hears you speak in whatever language is most comfortable for it.}{}
\defineTalent{See Hazard (sense)}{You may spend a spell point to gain a free Perception check to notice traps when within 10 ft of them.}{You may spend a spell point to gain a free Perception check to notice traps and hazards when you are within 10 ft of them, be they mechanical (trip wires, dart throwers, etc.) magical (rune spells, sigils, etc.) or natural (quick sand, pit falls, etc.). This does not give you insight into disabling such traps or hazards.}{}
\defineTalent{Sense Magic (sense)}{You may spend two spell points to \textit{sense} magic, as the base \textit{divine} ability out to 30 ft. without concentration}{You may spend 2 spell points to grant yourself the ability to \textit{sense} magic, as if using your basic \textit{divine} ability as a constant ability, but only to a distance of 30 ft.}{}
\defineTalent{True Sight (sense)}{You may spend a spell point to gain a \textit{sense} that grants you a +\HalfCLMinOne to all Will saves against illusions.}{You may spend a spell point to gain a \textit{sense} that grants you a bonus equal to 1/2 your caster level (minimum: 1) to all Will saves against illusions.}{}
\defineTalent{Viewing (divine)}{You may spend a spell point to see and hear a location within range.}{
	You may spend a spell point to \textit{divine}, transferring your point of view to any point within range. You may see and hear from this location. You do not need line of sight or line of effect, but the locale must be known—a place familiar to you, or an obvious one such as a distance and direction. Once you have selected the locale, the sensor doesn't move, but you can rotate it in all directions to view the area as desired, in all ways as if you were standing where your sensor is located.
	\par This ability creates a scrying sensor, which can be detected (Perception DC 20 + caster level) and dispelled.}{}