\defineSphere{Fate}{You command cosmic forces including luck, destiny, and alignment.}{You command cosmic forces including	luck, destiny, and alignment.}
\defineBaseAbility{Fate}{Word}{Invoke a word of power, affecting a single creature within Close range. You can use the \textit{Hallow} word to give the target a +\domath{\value{charCLCount} / 10 + 1} sacred bonus to attack rolls, AC, and saving throws against creatures of a chosen alignment opposed to yours, and immunity to possession and mind control by targets of the same alignment, for \arabic{charCLCount} minute\s.}{
	As a standard action, you may invoke a word of power, affecting a single creature within Close range. When you gain the Fate sphere, you gain the following \textit{word}: 
	\par \textit{Hallow:} You may spend a spell point to hallow a target for 1 minute per caster level. Choose an end of the alignment spectrum (good, evil, lawful, chaotic); you must choose an alignment that you possess. The target of this \textit{word} gains a +1 sacred bonus (profane bonus if you are evil; if you are neither good nor evil you must choose whether you grant sacred or profane bonuses with this sphere) to attack rolls, AC, and saving throws made against targets of your opposed alignment (evil for good, lawful for chaotic, etc.). This bonus increases by 1 for every 10 caster levels possessed.
	\par The target also gains immunity to any spell or sphere effect that possesses or exercises mental control over them (including enchantment [charm] effects and enchantment [compulsion] effects), so long as that effect originates from a creature who possesses your opposed alignment. If the target is already under the influence of such an effect, the target is allowed to make a new saving throw against the controlling effect. Success means the effect is suppressed for the duration of this \textit{word}, but resumes when this \textit{word} expires. This does not expel a controlling life force (such as a ghost or projected spirit), but it does prevent them from controlling the target.
	\par Some Fate talents are marked (word). These talents grant you additional \textit{words}.}
\defineBaseAbility{Fate}{Consecration}{You may create a 20 ft radius aura centered on you that has various effects. You can use \textit{serendipity} to give all allies in this aura a +1 luck bonus to attack rolls, skill checks, ability checks, and saving throws\ifinlist{Greater Serendipity}{\charFateTalentsList}{, and impose a -1 penalty to your enemies' rolls}{} for as long as you concentrate, or for \arabic{charCLCount} round\s{} without concentration if you spend a spell point.}{
	As a standard action, you may affect a 20 ft radius centered on you with a \textit{consecration}. This aura moves as you do. When you gain the Fate sphere, you gain the following \textit{consecration}:
	\par\textit{Serendipity:} You may bestow luck upon your allies. All allies within range gain a +1 luck bonus to attack rolls, skill checks, ability checks, and saving throws. This bonus lasts as long as you concentrate. You may spend a spell point as a free action to allow this effect to continue for 1 round per caster level without concentration.
	\par Fate talents marked (consecration) grant you additional \textit{consecrations}.}
\defineTalent{Bless (word)}{As an immediate action, spend a spell point to allow yourself or an ally to roll a single attack roll, ability check, skill check, or saving throw twice and take the better result.}{When you or one of your allies is making an attack roll, skill check, ability score check, or saving throw, you may spend a spell point as an immediate action to allow them to make the roll twice and take the highest roll. You must use this \textit{word} before the roll in question is made.}{}
\defineTalent{Close (word)}{Closes and locks (if possible) a door, or other closable object, and increases the DC to pick the lock or force the portal by 10 until it is successfully picked or forced.}{Rather than targeting creatures, this \textit{word} targets doors, chests, windows, and other objects that can open or close. You may spend a spell point and speak a \textit{word} that magically holds shut a door, gate, chest, window, or shutter of wood, metal, or stone. The portal closes and, if a lock is present, becomes locked. The DC to open the lock or force open the portal both increase by 10. Once the opening or portal has been forced or picked open, this effect ends.}{}
\defineTalent{Curse (word)}{As an immediate action, spend a spell point to force an enemy to roll twice and take the worst result on a single attack, skill check, ability check, or saving throw.}{When an enemy within range is making an attack roll, skill check, ability score check, or saving throw, you may spend a spell point as an immediate action to force that target to make the roll twice and take the lower result. You must use this \textit{word} before the roll in question is made.}{}
\defineTalent{Divine Force (consecration)}{Creatures of a chosen alignment opposed to yours suffer randomly determined conditions.}{
	You may fill an area with the influence of an alignment type you are connected to (good, evil, lawful, or chaotic). You must possess this alignment type. Creatures of that alignment’s opposite (good for evil, lawful for chaotic, etc.) within this area suffer one of the following detriments, chosen at random (Fortitude negates):
	\par 1. blind 1 round
	\par 2. deaf 2d4 rounds
	\par 3. staggered 1d4 round
	\par 4. sickened 1d4 round
	\par 5. dazed 1 round
	\par 6. shaken 1d4 round
	\par As this power is cosmic in origin, it can affect undead, even though undead are usually immune to some of these conditions. If you are True Neutral, you may choose neutrality with this \textit{consecration}, in which case all creatures at the extremes of the alignment spectrum (Lawful Good, Lawful Evil, Chaotic Good, and Chaotic Evil) suffer the ill effects.}{}
\defineTalent{Echoing Word}{Spend a spell point to affect \HalfCLMinOne additional target\s[HalfCL] with your \textit{word}}{When using a \textit{word}, you may spend an additional spell point to affect additional creatures, up to 1 extra creature per 2 caster levels (minimum: 1). Every target must be affected by the same \textit{word}.}{}
\defineTalent{Freedom (word)}{Spend a spell point to grant immunity to any sort of physical restraint, including paralysis, grapples, etc. for as long as you concentrate, up to \arabic{charCLCount} round\s, or spend an additional spell point to allow the effect to continue \arabic{charCLCount} round\s without concentration}{
	You may spend a spell point to speak a \textit{word} that frees the target from physical bondage. You must concentrate to maintain this ability, to a maximum of 1 round per caster level. You may spend an additional spell point as a free action to allow this ability to continue for 1 round per caster level without concentration.
	\par The target may move and attack normally, even when under the influence of magic and effects that would otherwise impede movement. This includes paralysis, slow effects, entanglement, etc. All combat maneuver checks made to grapple the target automatically fail, and the subject automatically succeeds on any combat maneuver checks and Escape Artist checks made to escape a grapple or a pin. The subject may even move and attack normally while underwater, provided that the weapon is wielded in the hand rather than hurled. This does not, however, grant waterbreathing.}{}
\defineTalent{Greater Consecration}{You may spend an additional spell point when using a \textit{consecration} to double the effected area, creating an aura with a 40 ft radius instead of a 20 ft radius.}{You may spend an additional spell point when using a \textit{consecration} to double the effected area, creating an aura with a 40 ft radius instead of a 20 ft radius.}{}
\defineTalent{Greater Serendipity}{Serendipity also imposes a -1 penalty to your enemies attack rolls, skill checks, ability checks, and saving throws.}{When you use your serendipity \textit{consecration}, in addition to bestowing a luck bonus upon your allies, all enemies within the area of effect also suffer a -1 penalty to their own attack rolls, skill checks, ability checks, and saving throws.}{}
\defineTalent{Harm (word)}{Whenever the target takes damage, they take an additional \HalfCLMinOne{} damage. This lasts as long as you concentrate, or for \arabic{charCLCount} round\s{} without concentration if you spend a spell point.}{Whenever the target of this \textit{word} suffers damage, they suffer an additional amount of damage equal to 1/2 your caster level (minimum: 1). This effect lasts as long as you concentrate, but you may always spend a spell point as a free action to allow this \textit{word} to continue for 1 round per caster level without concentration.}{}
\defineTalent{Judgment (consecrate)}{You declare a single-sentence course of action, which everyone in the area must follow (will save to act freely) for as long as you concentrate, up to \arabic{charCLCount} minute\s, or \arabic{charCLCount} minute\s{} without concentration if you spend a spell point. You cannot resist your own judgment.}{
	You may spend a spell point to create a \textit{consecration} that dictates the actions of all creatures within its area of effect. When you create this \textit{consecration}, you must declare a course of action that is at most one sentence long and whether this action is to be avoided or emulated. Example judgments include ``No one can attack'', ``everyone must trade fairly'', etc. If your judgment would cause a creature to attack itself or perform another obviously suicidal action, they are immune to that judgment. For as long as you maintain this \textit{consecration}, all creatures within this area must obey this judgement. Each individual creature is allowed a Will save to negate this requirement and allow itself to act normally. If a creature succeeds at their saving throw, they become immune to that judgment for the rest of its duration. You must always follow your own judgment.
	\par You must concentrate to maintain this \textit{consecration}, to maximum of 1 minute per caster level. You may always spend a spell point as a free action to allow this \textit{consecration} to continue for 1 minute per caster level without concentration.}{}
\defineTalent{Mercy (word)}{Spend a spell point to force target must make a will save or all damage it deals with weapon attacks is nonlethal for \arabic{charCLCount} round\s.}{You may spend a spell point to reduce the target’s ability to deal lethal damage. The target is allowed a Will save, and on a failure, deals nonlethal damage with all of its weapon attacks for 1 round per caster level. Damage taken by creatures or objects that are not subject to nonlethal damage is not converted to nonlethal and remains lethal damage.}{}
\defineTalent{Open (word)}{Opens doors or other openable objects. If locked or stuck, make a magic skill check with a +10 bonus instead of a disable device or strength check to unlock or force the portal.}{
	Rather than targeting creatures, this \textit{word} targets doors, chests, and other objects that can open or close. You may spend a spell point to open a door or container, as if you were making a Disable Device check to unlock it or, if the opening is stuck and no lock is present, a Strength check to force it open. Make a magic skill check with a +10 bonus against the lock’s Disable Device DC or the door’s Stuck DC. If the check is successful, the portal unlocks and opens. This \textit{word} may open doors, chests, shackles, and chains, and any other type of fastening. It cannot, however, raise a barred gate, lift a portcullis, or otherwise provide force in and of itself.}{}
\defineTalent{Pain (word)}{Causes the target pain, dealing 1d4\ifnum \value{HalfCL} > 0 { + \arabic{HalfCL}}\fi{} nonlethal damage each round, imposing a -4 penalty to mental skill checks, and requiring concentration checks as normal for continuing damage for one round\ifnum \value{charCLCount} > 1 or \arabic{charCLCount} round\s if you spend a spell point}{
	The target suffers debilitating pain. The target suffers 1d4 + 1/2 your caster level in nonlethal damage (no save). You may spend a spell point to cause this target to suffer this damage each round for a total number of rounds equal to your caster level. For 1 round (or as long as this \textit{word} is in effect) the target suffers a -4 penalty to all mental skill checks (such as Bluff, Spellcraft, Sense Motive, or Survival), and must pass a magic skill check (DC 10 + 1/2 the damage dealt + 1/2 the caster level) to use a sphere effect or spell.}{}
\defineTalent{Truth (word)}{For as long as you concentrate, or \arabic{charCLCount} minut\s{} if you spend a spell point, the target cannot speak deliberate lies (Will negates). You are aware of whether they fail their saving throw.}{The target cannot speak deliberate or intentional lies (Will negates). They are always aware of this \textit{word} being placed on them and the caster always knows if the target made its saving throw. An effected target may still be evasive, refuse to answer, or word their responses carefully. This effect lasts as long as you concentrate, but you may always spend a spell point to allow the effect to endure for 1 minute per caster level without concentration.}{}
\defineTalent{Tug Fate (consecrate)}{Any time a creature within this \textit{consecration} rolls a 10 on an attack roll, initiative roll, skill check, ability check, or saving throw, you can apply a +\domath{4+\value{HalfCL}} luck bonus or -\domath{4+\value{HalfCL}} penalty to the roll (your choice). This lasts for as long as you concentrate, or \arabic{charCLCount} round\s{} without concentration if you spend a spell point.}{For as long as this \textit{consecration} is in effect, any creature within the area who rolls a 10 on an attack roll, initiative roll, skill check, ability check, or saving throw receives either a +4 luck bonus or a -4 penalty to their roll (your choice). This does not apply when the creature takes 10; only a d20 roll will do. This bonus and penalty increase by 1 per 2 caster levels. You must concentrate to maintain this \textit{consecration}, but you may spend a spell point as a free action to allow this effect to continue for 1 round per caster level without concentration.}{}