\defineSphere{Life}{You wield the powers of life.}{You wield the powers of life.}
\defineBaseAbility{Life}{Invigorate}{\ifinlist{Ranged Healing}{\charLifeTalentsList}{Grant a target in Close range}{Touch a target and grant it} \ifinlist{Greater Invigorate}{\charLifeTalentsList}{\domath{\value{charCLCount} + \value{charCastingModCount}}} {\arabic{charCLCount}} temporary hit points which last for \ifinlist{Greater Invigorate}{\charLifeTalentsList}{\arabic{charCLCount} hour\s}{1 hour}. These cannot raise a target's total hit points plus temporary hit points above their hit point maximum.}{As a standard action, you may invigorate a touched creature, granting them temporary hit points equal to your caster level (minimum: 1). Unlike normal temporary hit points, this ability can only be used on an injured target and cannot raise a target’s current hit points plus their temporary hit points to be higher than their total hit points. This benefit lasts for 1 hour. Temporary hit points, even from different sources, do not stack; only the highest bonus applies.}
\newCounter{charCureDice}
\setCounter{charCureDice}{1}
\newCounter{charCureMult}
\setCounter{charCureMult}{1}
\defineBaseAbility{Life}{Cure}{Spend a spell point to \ifinlist{Ranged Healing}{\charLifeTalentsList}{heal a target in Close range}{touch a target and heal it} \arabic{charCureDice}d8+\domath{\value{charCLCount}*\value{charCureMult}} points of damage. This can harm undead (will half)}{As a standard action, you may spend a spell point to	touch a target and heal it an amount of damage equal to 1d8	+ your caster level. This is a positive energy effect, and as such may be used to harm undead (Will half).}
\edef\charLifeRestorelist{}
\edef\charRestoreMSCheckList{}
\ifinlist{Greater Restore}{\charLifeTalentsList}
{\forcsvlist{\listadd\charLifeRestorelist}{fatigued,exhausted,sickened,nauseated,shaken,frightened,panicked,staggered,dazzled, stunned}}
{\forcsvlist{\listadd\charLifeRestorelist}{fatigued,sickened,shaken,staggered,dazzled}}
%%
\defineBaseAbility{Life}{Restore}{Spend a spell point to \textit{restore} the health of \ifinlist{Ranged Healing}{\charLifeTalentsList}{a touched target}{a target in Close range}, \ifinlist{Greater Restore}{\charLifeTalentsList}{healing all ability damage\ifinlist{Restore Soul}{\charLifeTalentsList}{ and ability drain}{}}{healing 1d4 ability damage to an ability score of your choice\ifinlist{Restore Soul}{\charLifeTalentsList}{ and all ability drain}{}, lessening the exhausted, nauseated, frightened, and panicked conditions to fatigued, sickened, shaken, and frightened, respectively, }and removing \PrintList[, ][and ]{\charLifeRestorelist}. Conditions that are part of an ongoing effect are instead suppressed for \arabic{charCLCount} round\s.%
	\ifthenelse{\equal{\charRestoreMSCheckList}{}}{}{ You may also make a magic skill check against the DC of any\PrintList[, ][or ]{\charRestoreMSCheckList} to remove it from the target.}
	\ifinlist{Restore Movement}{\charLifeTalentsList}{ The target may immediately make an Escape Artist check with a +\arabic{charCLCount} bonus to escape an entanglement, grapple, or other such situation.}{}
	}
{As a standard action, you may touch a target and spend a spell point to \textit{restore} their physical and mental health. This accomplishes all of the following:
	\par$\bullet$ Heals 1d4 points of ability damage to one ability score
	of your choice.
	\par$\bullet$ Removes the fatigued condition or lessens exhaustion
	to fatigued.
	\par$\bullet$ Removes the sickened condition or lessens nauseated
	to sickened.
	\par$\bullet$ Removes the shaken condition or lessens frightened to
	shaken, or panicked to frightened.
	\par$\bullet$ Removes the staggered condition.
	\par$\bullet$ Removes the dazzled condition.
	\par If the condition targeted is part of an on-going effect, this suppresses the effect for a number of round equal to your caster level. This cannot be used to remove curses or instantaneous effects.}
\defineTalent{Break Enchantment}{You may spend an additional spell point to allow \textit{Restore} to also remove any noninstantaneous magic you desire.}{
	You may spend an additional spell point to allow your \textit{restore} ability to removes all magic from the target that has a duration. This may be used against curses including cursed equipment, although it does not remove the curse from the equipment, but instead suppresses the effect long enough for the item to be removed. You must succeed at a magic skill check against each magical effect in order to remove it. You may choose not to remove certain effects if you so desire (for example, you may target only harmful effects and not beneficial ones). This counts as using the break enchantment or remove curse spell against those spells and effects that specify they can only be removed through those spells. This has no effect on instantaneous effects.}{}
\defineTalent{Fount of Life}{You may store the effect of \textit{cures}, up to \domath{10 * \value{charCLCount}} points of healing, within yourself. You can then heal targets using this stored healing exactly as if using \textit{cure}, except that you don't spend a spell point and can decide the exact amount of stored healing to use.}{
	You may store a \textit{cure} within yourself, allowing you to access that healing as needed throughout the day. You spend a spell point and roll the damage healed as normal, except rather than healing by the given amount, that amount of healing is stored. You may store multiple \textit{cure}s in this manner to increase the amount of stored healing, but you cannot store more healing within you than 10 x your caster level. Stored healing is lost when you rest to recover spell points.
	\par You may draw on this stored healing to heal targets exactly as if using your \textit{cure} ability, except you do not need to spend a spell point; you may choose the amount of healing granted (to a maximum amount equal to your stored healing), and any healing granted to a target is subtracted from your stored healing.}{}
\defineTalent{Greater Healing}{Your \textit{cure} heals an additional \domath{\value{charCureMult}*\value{charCLCount}-\value{charCLCount}} hit points.}{Your \textit{cure} effect heals 2 points per caster level instead of 1 point per caster level. You may take this talent a total of 4 times. Each time this talent is taken, increase the amount healed by 1 hit point per caster level, to a maximum of 5 hit points per caster level.}{\addToCounter{charCureMult}{#1}}
\defineTalent{Greater Invigorate}{\textit{Invigorate} adds an additional \arabic{charCastingModCount} temporary hit point\s[charCastingModCount]\ifnum \value{charCLCount} > 1{} and lasts for \arabic{charCLCount} hour\s\fi.}{When placing an \textit{invigorate} on a target, add your casting ability modifier to the amount of temporary hit points granted, and increase the duration to 1 hour per caster level.}{}
\defineTalent{Greater Restore}{When \textit{restoring} a target, instead of lessening the exhausted, nauseated, frightened, and panicked conditions, they are completely removed. This also heals all ability damage and the stunned condition.}{When \textit{restoring} a target, instead of lessening the exhausted, nauseated, frightened, and panicked conditions, they are completely removed. This also heals all ability damage and the stunned condition.}{}
\defineTalent{Healthy Invigorate}{Spend a spell point when \textit{invigorating} a target to allow temporary hit points to exceed their usual hit point maximum.}{You may spend a spell point when using \textit{invigorate} to allow your \textit{invigorate }to increase a target’s effective hit point total to reach beyond their usual hit point total, as is normal with temporary hit points. This means you may use this talent to grant an \textit{invigorate} to a creature already at its maximum hit points.}{}
\defineTalent{Mass Healing}{Spend a spell point when using \textit{cure} or \textit{invigorate} to affect an extra \HalfCLMinOne target\s[HalfCL] within range}{You may spend an additional spell point when using a \textit{cure} or invigorate to affect an additional creature per 2 caster levels (minimum: 1). All targets must be within range.}{}
\defineTalent{Ranged Healing}{Your \textit{cure}, \textit{invigorate}, and \textit{restore} abilities have a range of Close rather than Touch.}{Your \textit{cure}, \textit{invigorate}, and \textit{restore} abilities have a range of Close rather than Touch.}{}
\defineTalent{Restorative Cure}{When using your \textit{cure} or \textit{invigorate} abilities on a target or targets, you may spend an additional spell point to \textit{restore} them as well.}{When using your \textit{cure} or \textit{invigorate} abilities on a target or targets, you may spend an additional spell point to \textit{restore} them as well.}{}
\defineTalent{Restore Health}{Your \textit{Cure} heals an additional 1d8 hit points. When \textit{restoring} a target you may attempt a magic skill check to remove poison and disease.}{
	Your \textit{cure} ability heals an additional 1d8 hit points. When \textit{restoring} a target, you may make a magic skill check against the DC of any poison or disease the target is suffering from. On a success, this removes that poison or disease from the target. This does not reverse damage the target may have suffered from the poison or disease (such as ability damage), but it does stop the poison or disease from causing any more.}{\stepCounter{charCureDice}\listadd{\charRestoreMSCheckList}{poison}\listadd{\charRestoreMSCheckList}{disease}}
\defineTalent{Restore Mind}{Your \textit{cure} ability heals an additional 1d8 hit points. When \textit{restoring} a target, the target is also cured of the confused and dazed conditions.}{Your \textit{cure} ability heals an additional 1d8 hit points. When \textit{restoring} a target, the target is also cured of the confused and dazed conditions.}{\listadd{\charLifeRestorelist}{confused}\listadd{\charLifeRestorelist}{dazed}\stepCounter{charCureDice}}
\defineTalent{Restore Movement}{Your \textit{cure} ability heals an additional 1d8 hit points. When \textit{restoring} a target, the target is freed from movement-impairing	effects.}{Your \textit{cure} ability heals an additional 1d8 hit points. When \textit{restoring} a target, the target is freed from movement-impairing	effects. The target may make an immediate Escape Artist check with a bonus equal to your caster level against any applicable condition (for example, if it is entangled or grappled), and you may make a magic skill check against any spell or effect that causes paralysis, removing the condition if you succeed.}{\stepCounter{charCureDice}\listadd{\charRestoreMSCheckList}{effect that causes paralysis}}
\defineTalent{Restore Senses}{Your \textit{cure} ability heals an additional 1d8 hit points. When \textit{restoring} a target, the target is also cured of all temporary or magical removal of their senses.}{Your \textit{cure} ability heals an additional 1d8 hit points. When \textit{restoring} a target, the target is also cured of all temporary or magical removal of their senses. This includes blindness, deafness, loss of Tremorsense, Blindsense, etc.}{\stepCounter{charCureDice}\listadd{\charLifeRestorelist}{blindness}\listadd{\charLifeRestorelist}{deafness}\listadd{\charLifeRestorelist}{other lost senses}}
\defineTalent{Restore Soul}{Your \textit{cure} ability heals an additional 1d8 hit points. When \textit{restoring} a target, the target is also cured of all ability drain and temporary negative levels.}{Your \textit{cure} ability heals an additional 1d8 hit points. When \textit{restoring} a target, the target is also cured of all ability drain and temporary negative levels.}{\stepCounter{charCureDice}\listadd{\charLifeRestorelist}{temporary negative levels}}
\defineTalent{Resuscitate}{\textit{Cure} and \textit{invigorate} can heal creatures dead for just one round to bring them back to life.}{Your \textit{cure} and \textit{invigorate} abilities function on creatures who have died within no more than 1 round. If the target’s new hit point total is at a negative amount greater than its Constitution score, then it comes back to life and stabilizes at its new hit point total. Otherwise the target remains dead. Creatures brought back to life in this manner gain a temporary negative level.}{}
\defineTalent{Revitalize}{When you use \textit{cure} you can instead grant fast healing \arabic{charCureMult} for \arabic{charCLCount} minute\s}{When \textit{curing} a target or targets, you may choose to grant the target Fast Healing instead of directly healing damage. This grants the target Fast Healing 1 for 1 minute per caster level. Increase the amount of Fast Healing granted by the number of times you have taken the Greater Healing talent. (Thus, if you had gained the Greater Healing talent twice, you could grant a target Fast Healing 3.)}{}