\defineSphere{Light}{You may create and manipulate light.}{You may create and manipulate light.}
\defineBaseAbility{Light}{Glow}{
	You may cause an object or creature within \ifinlist{Ranged Light}{\charLightTalentsList}{Long}{Medium} range to \textit{glow} for \ifinlist{Lasting Light}{\charLightTalentsList}{\domath{10 * \value{charCLCount}} minutes}{\arabic{charCLCount} minute\s}, imposing a -20 penalty on stealth checks and negating invisibility, darkness, or similar effects. You may choose as a free action to switch the light level emitted by a \textit{glowing} target between candlelight (5 ft. increased one step up to normal) and torchlight (20 ft. normal light, 20 ft. increased one step up to normal). You may cause a \textit{glow} effect within \ifinlist{Ranged Light}{\charLightTalentsList}{Long}{Medium} range to \textit{glow} brightly for as long as you concentrate or for \arabic{charCLCount} minute\s{} without concentration if you spend a spell point, producing bright light for \domath{30 + \value{HalfCL}*5} ft and increasing light levels by one step up to normal for another \domath{30 + \value{HalfCL}*5} ft.}{
	As a standard action, you may cause an object or creature to \textit{glow} for 1 minute per caster level, outlining it with light as a candle, which may be of any color you wish. This requires a touch attack or ranged touch attack. The object or creature becomes outlined with light, giving it a -20 penalty on Stealth checks and negating all bonuses usually bestowed by invisibility, blink effects, darkness, or similar effects.
	\par As a free action, you may cause any creature or object you have caused to \textit{glow} that is within Medium range to shed light as a torch, shedding normal light to 20 ft and increasing the light level by one step to a maximum of normal for 20 ft beyond this. Reducing this light is also a free action.
	\par As a standard action, you may cause one of your \textit{glow} effects within Medium range to shed bright light for as long as you concentrate. This produces bright light for 30 ft +5 ft per 2 caster levels, and increasing the light level by one step to a maximum of normal for 30 ft +5 ft per 2 caster level beyond this. As a free action, you may spend a spell point to allow the creature or object to continue \textit{glow}ing brightly without concentration for 1 minute per caster level, or until the \textit{glow} effect expires, whichever comes first. The bright light produced by this effect is not the equivalent of daylight for the purposes of creatures that are damaged or destroyed by daylight, but it may affect creatures with Light Blindness or other conditions.
	\par Whenever a \textit{glow} effect interacts with a magical darkness effect (such as from the Dark sphere) the caster of the \textit{glow} effect must pass a magic skill check against the MSD of the darkness effect’s caster. If he succeeds, the Light effect functions normally. If he fails, the Dark effect functions normally (outlines are swallowed, light sources are hampered, etc.) An area filled with normal or bright light from a \textit{glow} effect is no longer considered an area of darkness for Dark sphere abilities.
	\par Some talents are designated (light), which add additional effects to your \textit{glow} ability. You may only apply the benefits of one (light) talent to any individual \textit{glow} effect. While you may only apply one such talent to an individual \textit{glow} effect, areas of bright light from different \textit{glow} effects can overlap. 
	\par When augmenting a \textit{glow} effect with a (light) talent, the effect is applied once per round, at the end of the caster’s turn. For example, if a \textit{glow}ing object is thrown into a large group of enemies, it would only affect those within the area where it landed, not those targets it passed by to arrive in that area.}
\defineTalent{Area Glow}{You may spend a spell point to cause all creatures and objects within \domath{\value{charCLCount} / 5 * 5 + 10} ft. to \textit{glow}}{You may spend a spell point to create an eruption of light, causing all creatures and objects within a 10 ft +5 ft per 5 caster levels radius centered within range to \textit{glow}. You needn’t make a ranged touch attack against any creature within this area. Making targets glow brightly must still be done individually.}{}
\defineTalent{Beacon of Hope (light)}{When you place a \textit{glow} on a creature, you can choose to grant that creature a +\domath{\value{charCLCount} / 5 + 1} morale bonus on saves against fear. You can spend a spell point to create bright light that grants this bonus to all creatures within it.}{When you place a \textit{glow} effect on a creature, you may choose to grant that creature a +1 morale bonus on saves against fear. This bonus increases by 1 for every 5 caster levels possessed.
	\par You may spend a spell point to create bright light that empowers those within it. All creatures within the area of bright light gain a +1 morale bonus on saves against fear, +1 per 5 caster levels.}{}
\defineTalent{Blinding Light (light)}{When you place a \textit{glow} on a creature, you may choose to dazzle that target, giving it a -1 penalty to attack rolls and Perception checks. You may spend a spell point to create bright light that blinds the \textit{glowing} target and all creatures within the area of bright light. All such creatures must make a Fortitude save each round or be blinded for 1 round. Creatures who succeed at their saving throw are still dazzled for that round.}{When you cause a creature to \textit{glow}, you may choose to make that target dazzled, giving it a -1 penalty to attack rolls and Perception checks. You may spend a spell point to create bright light that blinds the \textit{glowing} target and all creatures within the area of bright light. All creatures must make a Fortitude save or be blinded for 1 round. They must make this saving throw each round they are within this area. Creatures who succeed at their saving throw are still dazzled for that round.}{}
\defineTalent{Bound Light (light)}{You may create bright light that causes the \textit{glowing} target to be entangled and make a Fortitude save each round or also be staggered for that round. In addition, the target must pass a magic skill check to use any form of dimensional travel.}{You may create bright light that binds the \textit{glowing} target inside a prison of light. The target is entangled and must pass a Fortitude save each round or also be staggered for that round. In addition, the target must pass a magic skill check to use any form of dimensional travel, such as the dimension door spell or the teleport ability from the Warp sphere.}{}
\defineTalent{Dancing Lights}{You can create \textit{glow} effects without attaching them to anything. These \textit{glows} can be directed as a free action, can follow simple commands, and can fly up to 60 ft per round.}{You may create a glow effect without the need for a creature or object. This allows you to create a floating ball of light that may fly up to 60 ft per round and may be directed as a free action. You may give these lights simple commands, such as following a creature you can see or traveling in a specified pattern.}{}
\defineTalent{Encompassing Light (light)}{You can create a bright light that gives the \textit{glowing} creature the damage and reach of a creature \ifnum \value{charCLCount} > 19 3 \else\ifnum \value{charCLCount} > 9 2 \else 1\fi\fi{} size categor\ifnum\value{charCLCount} > 9 ies\else y\fi{} larger.}{You may create bright light that encompasses the glowing creature, allowing it to function as if it were larger than it is. The glowing creature deals damage and gains reach as if it were 1 size category larger than it is. This improves to 2 size categories at 10th caster level, and 3 size categories at 20th caster level.}{}
\defineTalent{Guiding Light (light)}{When you cause a creature to \textit{glow}, you may choose to grant all creatures a +1 circumstance bonus to attack rolls against that target. When causing that creature to shed bright light, this bonus increases to \domath{\value{charCLCount} / 5 + 2}}{When you cause a creature to \textit{glow}, you may choose to grant all creatures a +1 circumstance bonus to attack rolls against that target. When causing that creature to shed bright light, you may increase this bonus by 1, +1 per 5 caster levels. This has no effect on other creatures within the area of bright light.}{}
\defineTalent{Hypnotic Pattern (light)}{You may spend a spell point when creating bright light to fascinate all creatures within the area (will negates).}{You may spend a spell point when creating bright light to fascinate creatures. All creatures within this area of bright light that can see become fascinated (Will negates) for as long as they remain within this area of bright light. These targets take no action on their turn but to stare into the light, and suffer a -4 penalty to all Perception checks. A target is allowed a new saving throw each round to throw off the effect, and on a successful save, may make their actions as normal. Once a target has saved against this effect, they are immune to the effect for the rest of its duration. Hostile action taken against a hypnotized target automatically breaks the effect, as if the target had succeeded at their saving throw. If the target was already in combat when this ability is used, they gain a +2 bonus to their initial saving throw.}{}
\defineTalent{Illuminate}{When causing an object to shed normal light or bright light, you may focus this light into a cone as a free action, doubling the affected distance, to a 40 ft cone for normal light, or \domath{5 * \value{charCLCount} + 60} ft cone for bright light. This also doubles the distance to which light is increased one step.}{When causing an object to shed normal light or bright light, you may focus this light into a cone as a free action, doubling the affected distance. For normal light this creates a 40 ft cone, while bright light creates a 60 ft cone + 5 ft per caster level. This also doubles the distance to which light is increased one step to a maximum of normal light. Returning the effect to normal is also a free action. You may change the light’s direction as a free action, but for the purpose of (light) talents you may only affect one area per round.}{}
\defineTalent{Lasting Light}{Increase the duration of \textit{glow} effects to \domath{\value{charCLCount}*10} minutes}{When you produce a \textit{glow}, it lasts for 10 minutes per caster level instead of 1 minute per caster level. Spending a spell point to make bright light self-sustaining still only lasts for 1 minute per caster level.}{}
\defineTalent{Light Link}{You always know the direction and distance to any creature or object under the effect of your \textit{glow}, as long as it is on the same plane as you.}{You always know the direction and distance to any creature or object under the effect of your \textit{glow}. This has no effect if the creature or object is on another plane.}{}
\defineTalent{Ranged Light}{You may target creatures and objects within Long range rather than Medium range when applying a \textit{glow}, and when causing a \textit{glowing} object to shed normal or bright light.}{You may target creatures and objects within Long range rather than Medium range when applying a \textit{glow}, and when causing a \textit{glowing} object to shed normal or bright light.}{}
\defineTalent{Repelling Light (light)}{You may spend a spell point to create a bright light that repels one type (or subtype for humanoids or outsiders) of creature. Creatures of that type within the bright light or be unable to move closer to the source of the light. If a creature succeeds, it must make a new save each round.}{You may spend a spell point to create light that repels unwanted creatures. Choose one creature type. In the case of humanoids and outsiders, you must instead choose one subtype. Any creature of this type or subtype within the area of bright light must pass a Fortitude save or be unable to move closer to the source of the light. Affected creatures may move sideways or backwards, but cannot move closer, although the source of the light may move closer to them. Creatures who make their saving throw but remain within the area of bright light must make a new saving throw every round to avoid being affected.
	\par If a creature enters this area of bright light (or if the source of bright light moves close to them), they must immediately save or be affected.}{}
\defineTalent{Revealing Light (light)}{You may spend a spell point to create bright light that reveals all invisible creatures and objects within the area.}{You may spend a spell point to create bright light that reveals all invisible creatures and objects. These creatures and objects lose all the benefits of invisibility for as long as they are within the area of bright light.}{}
\defineTalent{Searing Light (light)}{You may create a bright light that deals \arabic{charCLCount} points of fire damage each round to all creatures within it, or \domath{\value{charCLCount} * 2} points of fire damage each round if they are undead, an ooze, or harmed by daylight.}{You may create bright light that burns creatures in its area. All creatures in the area suffer 1 point of fire damage per caster level per round they are within this area of bright light. Undead, oozes, and creatures harmed by daylight take 2 points of fire damage per caster level.}{}