\defineSphere{Mind}{You gain the ability to alter the minds of others, causing them to act as you see fit.}{You gain the ability to alter the minds of others, causing them to act as you see fit. All mind sphere abilities are Enchantment (compulsion) mind-affecting abilities.%
	\par \textit{Note:} Some Mind sphere abilities allow the caster to make a request of the target creature and have different effects depending on the particular request made. While the final decision on what request falls into what category is up to the GM, the examples in Table: Example Requests are a shorthand for players and GMs hoping to quickly determine what an enchanted creature might or might not be asked to do.}
\newcommand{\LesserCharm}[1]{\par \textit{Lesser Charm:} #1}
\newcommand{\GreaterCharm}[1]{\par \textit{Greater Charm:} #1}
\newcommand{\PowerfulCharm}[1]{\ifinlist{Powerful Charm}{\charMindTalentsList}{\par \textit{Powerful Charm:} #1}{}}
\def\charcharmrange{Close}
\defineBaseAbility{Mind}{Charm}{%
	Charms can be placed on a target
	\ifinlist{Expanded Charm}{\charMindTalentsList}{with a living mind}{of your own creature type} within \charcharmrange{} range.
	\textit{Lesser Charms} are free, but cannot be used more than once per day per target.
	\ifinlist{Powerful Charm}{\charMindTalentsList}%
		{\textit{Greater Charms} cost one spell point to use, and \textit{Powerful Charms} cost two spell points to use.}%
		{\textit{Greater Charms} cost one spell point to use.}
	You have the \textbf{Suggestion} charm, which allows you to implant thoughts in another's mind.%
	\LesserCharm{You plant a very simple request in the target's mind, which the target follows for \arabic{charCLCount} hour\s{} or until the task is complete. (will negates)}%
	\GreaterCharm{As the \textit{lesser charm}, but you may make basic requests. Very simple requests impose a -2 penalty to the target's will save.}%
	\PowerfulCharm{As the \textit{lesser charm}, save that any request that is not obviously fatal or against the creature's nature may be made. Very simple requests impose a -4 penalty to the target's will save, and basic requests impose a -2 penalty to the will save.}%
	}{
	You may place \textit{charms} on creatures. \textit{Charms} require a standard action to use and have a range of Close. You may only use \textit{charms} on targets that possess your own creature type (humanoid for humanoids, etc.) although the Expanded Mind talent changes this. Each \textit{charm} has three strengths; lesser, greater, and powerful. \textit{Lesser charms} are at-will abilities, but you may not target an individual creature more than once in a day with any individual \textit{lesser charm}. \textit{Greater charms} cost a spell point to use and \textit{powerful charms} cost 2 points to use. You must possess the Powerful Charm talent before you may use any \textit{powerful charms}. When you gain the Mind sphere, you gain the following charm:\\\\
	\textbf{Suggestion:} You may plant thoughts into a target's mind. 
	\par \textit{Lesser Charm:} You may plant a suggestion in a target's mind, which they obey as if the thought had been their own (Will negates). The suggested course of activity must be limited to a sentence or two and must be a very simple request. The creature performs the suggested action until it finishes, or for 1 hour per caster level, whichever comes first. If you choose, you can instead specify conditions the creature should look for, (e.g., ``you should search the next person who enters this room, looking for weapons.'') If the condition is not met before this duration expires, the activity is not performed.
	\par \textit{Greater Charm:} This is the same as the Suggestion \textit{lesser charm}, but may be up to a basic request. Very simple requests cause the save to be made with a -2 penalty. The target cannot be asked to do anything it would not normally do.
	\par \textit{Powerful Charm:} This is the same as the Suggestion \textit{lesser charm}, but the creature obeys any course of action given, so long as the suggestion is not obviously fatal or against the target's nature. Basic requests cause the save to be made with a -2 penalty, while very simple requests cause the save to be made with a -4 penalty.
	\par Some mind talents are designated (charm) talents. These talents grant you additional \textit{charms} you may place on targets.}
\defineTalent{Command (charm)}{You may directly control another creature's body.%
	\LesserCharm{You may force the target to perform one move, swift, or free action on its next turn (will negates).}%
	\GreaterCharm{You take control of the target for as long as you concentrate, up to \arabic{charCLCount} round\s{}. (will negates) You may force the target to take a single move, standard, or charge action each round, and cannot take actions of its own apart from speaking. It gets a new save at the end of each round to shake off your control.}
	\PowerfulCharm{As the \textit{Greater Charm}, but the target is not restricted to a single move or standard action each round.}
	}{
	You may directly control another creature's body.
	\par \textit{Lesser Charm:} You may force the target to perform one move, swift, or free action of your choice on its next turn (Will negates). This could include yelling loudly, falling to the ground, dropping its weapon, or moving in a generalized direction (away, toward, left, right, etc.) For the purpose of this talent, standing still is a free action. The target cannot use its other actions on that turn to undo the effect of this lesser charm (pick up a dropped weapon, move back to its old square, stand up if it fell down, etc.).
	\par \textit{Greater Charm:} You take control of the target for as long as you concentrate, to a maximum of 1 round per caster level. (Will negates). The target is allowed a new saving throw as a free action each round at the end of its turn to throw off this control. Other than verbal actions, the target cannot perform an action of its own choice on its turn. While under your control, the target mentally fights you, and so can only be made to perform a single move action or standard action each round. The creature can move up to its speed and attack in the same round as a charge action. While you may command a target to use an item or perform magic, this does not grant you knowledge of the target's magical abilities or inventory. While you can command a creature to stand still and take no action, you cannot command a creature to become helpless or give up its Dex bonus to AC.
	\par \textit{Powerful Charm:} This is the same as the Command \textit{greater charm}, except the target is not limited to a single standard action or move action each round.}{}
\defineTalent{Confusion (charm)}{You may unravel a creature's mind and make them behave erratically.%
	\LesserCharm{The target becomes confused for 1 round (Will negates).}%
	\GreaterCharm{The target becomes confused for \arabic{charCLCount} minute\s (Will negates).}%
	\PowerfulCharm{As the \textit{greater charm}, and the target suffers a -2 penalty to their caster level and a -4 penalty to all mental ability scores.}}{
	You may unravel a creature's mind and make them behave erratically.%
	\par \textit{Lesser Charm:} The target becomes confused for 1 round (Will negates).%
	\par \textit{Greater Charm:} The target becomes confused for 1 minute per caster level (Will negates).%
	\par \textit{Powerful Charm:} This is the same as the Confusion \textit{greater charm}, except in addition to being confused, the target also suffers a -2 penalty to their caster level and a -4 penalty to all their mental ability scores.}{}
\defineTalent{Courage (charm)}{You inspire the target to great action%
	\LesserCharm{The target may choose one attack roll, saving throw, ability check, or skill check it makes within the next minute. It gains a +\domath{\value{charCLCount} / 5 + 2} morale bonus on that roll.}%
	\GreaterCharm{The target gains a \domath{\value{charCLCount} / 5 + 1} morale bonus to all attack rolls, saving throws, ability checks, and skill checks for \arabic{charCLCount} round\s.}%
	\PowerfulCharm{As the \textit{Greater Charm}, but the target is also immune to fear and gains \arabic{charCLCount} temporary hit points, and the duration is increased to \arabic{charCLCount} minute\s.}%
	}{You inspire the target to great action.%
	\par\textit{Lesser Charm:} The target may choose one attack roll, saving throw, ability check, or skill check it makes within the next minute. The target gains a morale bonus equal to 2 + 1 per 5 caster levels on that roll. If no roll is selected before 1 minute passes, this effect ends.
	\par \textit{Greater Charm:} The target gains a morale bonus equal to 1 + 1 per 5 caster levels to all attack rolls, saving throws, ability checks, and skill checks for 1 round per caster level.
	\par \textit{Powerful Charm:} This is the same as the Courage \textit{greater charm}, except the duration increases to 1 minute per level. The target also becomes immune to fear and gains temporary hit points equal to your caster level}{}
\defineTalent{Enthrall (charm)}{The target regards you as a friend. If you or your allies are hostile to the creature, it gets a +5 bonus to its saving throw.
	\LesserCharm{The target's disposition toward you increases one step, to a maximum of friendly for \arabic{charCLCount} minute\s. (will negates)}
	\GreaterCharm{The target becomes friendly toward you for \arabic{charCLCount} minute\s. (will negates). You may make an opposed Charisma check to make a request of the target.}
	\PowerfulCharm{As the \textit{greater charm}, but the duration is \arabic{charCLCount} hour\s.}}{
	You cause a creature to regard you as its friend. If you or your allies are attacking or threatening the creature, they gain a +5 bonus to their saving throw against this charm. A DC 25 Sense Motive check reveals the target of this charm has been enchanted. This is an enchantment (charm) effect instead of an enchantment (compulsion) effect.
	\par \textit{Lesser Charm:} You increase the target's disposition toward you by 1 step to a maximum of friendly for 1 minute per caster level (Will negates).
	\par \textit{Greater Charm:} You increase the target's disposition toward you to friendly for 1 minute per caster level (Will negates). You may make requests of the target, but asking it to do anything it would not normally do requires an opposed Charisma check, and it never obeys requests that are obviously fatal or against its nature, although the target may be convinced dangerous things are worth doing.
	\par \textit{Powerful Charm:} This functions as the Enthrall greater charm, except the duration increases to 1 hour per caster level.
	}{}
\defineTalent{Expanded Charm}{Your \textit{charms} may affect any creature with a mind susceptible to mind-altering effects.}{Your \textit{charms} may affect any creature with a mind susceptible to mind-altering effects. Creatures without living minds (constructs, undead, oozes, vermin) are still immune.}{}
\defineTalent{Fear (charm)}{You may warp a target's mind with fear.
	\LesserCharm{You cause the target to become shaken for \arabic{charCLCount} round\s{} (Will negates).}
	\GreaterCharm{You cause a target to become frightened for \arabic{charCLCount} round\s{} (Will negates). On a successful save, they are shaken for \arabic{charCLCount} round\s.}
	\PowerfulCharm{As the Fear greater charm, except the target becomes panicked instead of frightened. On a successful save, they are frightened for 1 round and shaken for \arabic{charCLCount} round\s{}.}}{
	You may warp a target's mind with fear.
	\par \textit{Lesser Charm:} You cause the target to become shaken for 1 round per caster level (Will negates).
	\par \textit{Greater Charm:} You cause a target to become frightened for 1 round per caster level (Will negates). On a successful save, they are still shaken for 1 round per caster level.
	\par \textit{Powerful Charm:} This is the same as the Fear greater charm, except the target becomes panicked instead of frightened. On a successful save, they are still frightened for 1 round and shaken for 1 round per caster level.}{}
\defineTalent{Group Charm}{You may spend a spell point when using a charm to affect up to \HalfCLMinOne additional creature\s[HalfCL]}{You may spend a spell point when using a charm to affect up to 1 additional creature per 2 caster levels (minimum: 1). Each target must be within range and must be affected by the same charm effect.}{}
\defineTalent{Hostility (charm)}{You cause the target to enter a blinding rage.
	\LesserCharm{You compel the target to attack the nearest creature on it next turn (Will negates). The target moves until this creature is within range and makes at least one attack. If no creature can be reached, the target instead deals 1d8 + its Strength modifier damage to itself.}
	\GreaterCharm{The target enters a rage for \arabic{charCLCount} round\s, (Will negates if unwilling) gaining a +2 morale bonus to Strength and Constitution, a +1 bonus to Will saves, a -2 penalty to AC, and it cannot use any spells, nor any skills or class features based off of Intelligence, Wisdom, or Charisma.}
	\PowerfulCharm{Same as the \textit{greater charm}, but you may grant one of the following packages to the target as well:
	\par ~~~Heroic Rage: The bonuses to strength, constitution, and will saves double, and the target may still use spells andclass features and skills based off of Intelligence, Wisdom, and Charisma.
	\par ~~~Brutal Rage: The target is compelled to hostility, as the \textit{lesser charm} for the duration.}}{
	You cause the target to enter a blinding rage.
	\par \textit{Lesser Charm:} You compel the target to attack the nearest creature on it next turn (Will negates). The target moves until this creature is within range and makes at least one attack with a weapon, natural attack, or unarmed strike. If no such creature can be reached, the target instead deals damage to itself equal to 1d8 + its Strength modifier with whatever it has in hand.
	\par \textit{Greater Charm:} The target enters a rage for 1 round per caster level (Will negates if unwilling). The target gains a +2 morale bonus to Strength and Constitution, a +1 bonus to Will saves, and a -2 penalty to AC. In addition, the target cannot use any spells, nor any skills or class features based off of Intelligence, Wisdom, or Charisma. This counts as a Barbarian's rage, except the target is not fatigued at the end.
	\par \textit{Powerful Charm:} Same as the greater charm, but you may grant one of the following packages to the target as well:
	\par ~~~Heroic Rage: the target's bonus to Strength and Constitution increases to +4, and their bonus to Will saves increases to +2. The target may still use spells, as well as class features and skills based off of Intelligence, Wisdom, or Charisma.
	\par ~~~Brutal Rage: The target is compelled to hostility and each round attacks the nearest target to itself, be it friend or foe. If the creature cannot attack something during its turn, it deals 1d8 + its Strength modifier damage to itself with whatever it has in hand.}{}
\defineTalent{Inspiration (charm)}{You inspire competence in the target.
	\LesserCharm{As an immediate action, you may add a +2 competence bonus to a skill check or attack roll the target has just made, after the roll has been made, but before the results are revealed.}
	\GreaterCharm{As the \textit{lesser charm}, except it adds +2d4 instead of +2.}
	\PowerfulCharm{As the \textit{lesser charm}, except it adds +2d4+\HalfCLMinOne instead of +2.}}{
	You inspire competence in the target.
	\par \textit{Lesser Charm:} As an immediate action, you may add a +2 competence bonus to a skill check or attack roll the target has just made. This can change a failure into a success. You must choose to use this charm after the roll has been made, but before the results are revealed.
	\par \textit{Greater Charm:} This is the same as the Inspiration lesser charm, except it adds +2d4 to the attack roll or skill check instead of +2.
	\par \textit{Powerful Charm:} This is the same as the Inspiration greater charm, except it adds +2d4 +1 per 2 caster levels (minimum: 1) to the roll instead of only +2d4.}{}
\defineTalent{Paralyze (charm)}{You freeze the target in place.
	\LesserCharm{The target is dazed for 1 round (Will negates).}
	\GreaterCharm{The target is stunned for \arabic{charCLCount} round\s{} (Will negates). The target is allowed a new Will save each round to end this effect early.}
	\PowerfulCharm{As the \textit{greater charm}, except the target is paralyzed instead of stunned.}}{
	You freeze the target in place.
	\par \textit{Lesser Charm:} The target is dazed for 1 round (Will negates).
	\par \textit{Greater Charm:} The target is stunned for 1 round per caster level (Will negates). The target is allowed a new Will save each round to end this effect early. This is a full-round action that does not provoke an attack of opportunity.
	\par \textit{Powerful Charm:} This is the same as the Paralyze \textit{greater charm}, except the target is paralyzed instead of stunned.}{}
\defineTalent{Powerful Charm}{You may spend 2 spell points to use the Powerful charm version of any charm you possess.}{You may spend 2 spell points to use the Powerful charm version of any charm you possess.}{}
\defineTalent{Project Thoughts (charm)}{You can communicate directly into the mind of another.
	\LesserCharm{You project an empathic message into the mind of the target. The target knows what you are feeling, but they are not able to communicate back. There is no limit to the number of times you may use this lesser charm on a target in a day.}
	\GreaterCharm{You may project a message to a target consisting of no more than 25 words.}
	\PowerfulCharm{You can send messages to the target for as long as you concentrate, even without a shared language.}}{
	You can communicate directly into the mind of another.
	\par \textit{Lesser Charm:} You project an empathic message into the mind of the target. The target knows what you are feeling (fear, anger, anxiety, rage, etc.), although they are not able to communicate back. Unlike other \textit{lesser charms}, there is no limit to the number of times you may use this lesser charm on a target in a day.
	\par \textit{Greater Charm:} You may project a telepathic message to a target consisting of no more than 25 words. If you and the target do not possess a shared language, this form of communication is impossible.
	\par \textit{Powerful Charm:} Your projected telepathic message does not have a word limit, although communication is carried out in real time and you must concentrate for as long as you communicate. You can communicate with the target even without a shared language.}{}
\defineTalent{Ranged Mind}{Increase the range you may charm targets to \charcharmrange.}{Increase the range you may charm targets by 1 step (Close to Medium, Medium to Long). You may select this talent multiple times. The effects stack.}{%
	\ifnum 1 = #1%
		\def\charcharmrange{Medium}%
	\else\ifnum #1 > 1%
		\def\charcharmrange{Long}%
	\fi\fi}
\defineTalent{Read Mind (charm)}{You can pull information from a target's mind.
	\LesserCharm{You may detect a creature's emotional state (Will negates if unwilling). There is no limit to the number of times you may use this \textit{charm} on a target in a day.}
	\GreaterCharm{You may read the surface thoughts of a creature (Will negates if unwilling) for as long as you concentrate.}
	\PowerfulCharm{You may pull a specific piece of information out of a creature's mind (Will negates). This is usually enough information to answer a single, specific question, in no more than 25 words. A creature who successfully saves may choose to provide no answer to your question or attempt to lie. If you use this powerful charm twice on the same creature to ask the same question, the same answer is given again.}}{
	You can pull information from a target's mind.
	\par \textit{Lesser Charm:} You may detect a creature's emotional state (Will negates if unwilling). Unlike other \textit{lesser charms}, there is no limit to the number of times you may use this \textit{lesser charm} on a target in a day.
	\par \textit{Greater Charm:} You may read the surface thoughts of a creature (Will negates if unwilling) for as long as you concentrate.
	\par \textit{Powerful Charm:} You may pull a specific piece of information out of a creature's mind (Will negates). This is usually enough information to answer a single, specific question to the best of that creature's knowledge, in no more than 25 words. A creature who successfully saves against this powerful charm may choose to provide no answer to your question or attempt to lie with their Bluff skill. If you use this powerful charm twice on the same creature to ask the same question, the same answer (correct, no answer or lie) is given again.}{}
\defineTalent{Sleep (charm)}{You put the target to sleep.
	\LesserCharm{The target is staggered for 1d4 rounds (Will negates).}
	\GreaterCharm{You put the target to sleep for \arabic{charCLCount} minute\s{} (Will negates).}
	\PowerfulCharm{As the \textit{greater charm}, but when the target takes damage or another creature attempts to wake it, the target gets a new Will save with a +4 bonus instead of automatically waking}}{
	You put the target to sleep.
	\par \textit{Lesser Charm:} You make the target lethargic, making it staggered for 1d4 rounds (Will negates).
	\par \textit{Greater Charm:} You put the target to sleep for 1 minute per caster level (Will negates). Targets who take damage automatically wake up, and other creatures may wake a sleeping creature as a standard action.
	\par \textit{Powerful Charm:} The target is placed into a deeper slumber. Whenever the sleeping target takes damage or another creature attempts to wake it as a standard action, the target does not automatically awaken, but instead makes a new Will save to wake up with a +4 bonus.}{}
\defineTalent{Subtlety}{If a target succeeds on their save against one of your charms, they must immediately pass a second Will save. If they fail this second save, they do not realize they were the subject of an attempted mental assault.}{If a target succeeds on their save against one of your charms, they must immediately pass a second Will save. If they fail this second save, they do not realize they were the subject of an attempted mental assault.}{}
\defineTalent{Vision (charm)}{You may make someone see things that are not there.
	\LesserCharm{You may alter a creature's perception of a single creature, object, sound, or effect for \arabic{charCLCount} round\s{} (Will negates). You may alter only one sense's perception of the object. If used to cover up pain, the target gets a +4 bonus to its Will save. If the target interacts with the object of the spell, they are allowed a new save each round.}
	\GreaterCharm{As the \textit{lesser charm}, except you may affect all five senses.}
	\PowerfulCharm{As the \textit{greater charm}, except you may change the target's perception of everything around them.}}{
	You may make someone see things that are not there.
	\par \textit{Lesser Charm:} You may alter a creature's perception of a single creature, object, sound, or effect for 1 round per caster level (Will negates). You may alter 1 sense (sight, sound, touch/pain, taste, smell); for example, you could make a thief appear to be an alley cat, make a scratch appear as a gaping knife wound, or make the sound of footsteps seem like the wind. You cannot use this to replicate speech or sights and sounds you have never enCountered before, nor to make something invisible. If used to cover up pain (such as hiding the target taking damage) the target gains a +4 bonus to their Will save.
	\par If the target interacts with the object of their altered perception, they are allowed an additional save every round they continue to do so.
	\par \textit{Greater Charm:} This functions as the Vision \textit{lesser charm}, except you may affect all 5 senses in relation to the chosen creature, object, sound, or effect. 
	\par \textit{Powerful Charm:} This functions as the Vision \textit{greater charm}, except you may change the target's perception of everything around them. This grants the target a new saving throw each round they interact with any part of the altered surroundings.}{}