\defineSphere{Protection}{You are a user of the magics of preservation.}{You are a user of the magics of preservation.}
\defineBaseAbility{Protection}{Ward}{You can create a \textit{ward} centered \ifinlist{Distant Protection}{\charProtectionTalentsList}{within Close range}{on yourself} with a radius of your choice up to \domath{\value{charCLCount} * 5 + 10} ft, which remains for so long as you concentrate or for \arabic{charCLCount} round\s{} without concentration if you spend a spell point. \textit{Wards} remain where they were created and do not move with you.
	\par \textit{Barrier:} You may create a \textit{ward} which creates force barrier with \domath{\value{charCLCount} + 4} hit points and a break DC of \domath{15 + \value{HalfCL}}. If you maintain the barrier through concentration, its hit points are refreshed each round.}{
	As a standard action, you may create an \textit{ward} centered on yourself with a radius of up to 10 ft + 5 ft per caster level, but can also be made so small as to only cover yourself. \textit{Wards} remain as long as you concentrate, but you may spend a spell point to allow them to remain for 1 round per caster level without concentration. \textit{Wards} remain in the location they were created, even if you move. When you gain the Protection sphere, you gain the following \textit{ward}:
	\par \textit{Barrier:} You may create a \textit{ward} that creates a mostly-transparent wall at its perimeter, stopping attacks, movement, breath weapons, and any spells or sphere effects that must travel to their destination (such as destructive blasts, ghost strikes, or spells that require ranged touch attacks). Other spells or sphere effects, however, such as teleportation effects, mind-altering magic, and gaze attacks may all bypass this \textit{ward}. Ethereal creatures are technically stopped by the barrier, but can usually find a way around it (as the barrier does not cut through objects, and so usually stops at ground level).
	\par A barrier has hit points equal to 4 + your caster level and a Break DC of 15 + 1/2 your caster level. If an attack is directed at a target through the barrier, the attack first deals its damage to the barrier itself. If this damage is enough to destroy the barrier, the attack continues on to its intended target, although damage dealt to the barrier is subtracted from any damage done to the target or targets. Burst-effect attacks such as splash weapons, fireball spells, or others attempting to travel through the barrier explode at the barrier's edge and also must overcome the barrier's hp to damage targets on the other side.
	\par If you maintain your barrier through concentration, its HP is renewed each round on your turn.
	\par Certain protection talents grant you additional \textit{aegis}, and are marked (aegis)}
\defineBaseAbility{Protection}{Aegis}{
	You may spend a spell point to grant \ifinlist{Distant Protection}{\charProtectionTalentsList}{a target within Close range}{a touched target} an \textit{aegis} for \arabic{charCLCount} hour\s. (Will negates if unwilling)
	\par \textit{Deflection:} You grant the target a +\domath{\value{charCLCount} / 5 + 1} Deflection bonus to AC.}{
	As a standard action, you may touch a creature and spend a spell point, granting them an \textit{aegis} for 1 hour per caster level. Unwilling targets are allowed a Will save to resist gaining an \textit{aegis}. You gain the following \textit{aegis} when you gain the Protection sphere:
	\par \textit{Deflection:} You grant the target a +1 Deflection bonus to AC, +1 per 5 caster levels.
	\par Certain protection talents grant you additional \textit{aegis}, and are marked (aegis).}
\defineTalent{Armored Magic (aegis)}{You grant the target either a +\domath{\value{charCLCount} / 5 + 3} armor bonus or +\domath{\value{charCLCount} / 5 + 1} shield bonus to AC. These apply against incorporeal attacks.}{You may create an \textit{aegis} that wraps the target in protective barriers, granting them either a +3 armor bonus or a +1 shield bonus to AC (your choice). This does not stack with other armor or shield bonuses, but does apply against attacks made by incorporeal creatures. These bonuses increase by +1 for every 5 caster levels you possess.}{}
\defineTalent{Breathless (aegis)}{The target does not need to breathe.}{You may create an \textit{aegis} that allows a creature to survive without air. The creature becomes immune to effects that require breathing (such as inhaled poison), can survive underwater, or even in a vacuum. This does not give immunity to cloud or gas attacks that do not require breathing.}{}
\defineTalent{Community}{Whenever a creature under your \textit{aegis} takes damage, you may spend a spell point to transfer up to half of that damage to any other creature under one of your \textit{aegis}.}{Whenever a creature under your \textit{aegis} takes damage, you may spend a spell point to transfer up to half of that damage to any other creature under one of your \textit{aegis} as a free action. This damage cannot be resisted or redirected further.}{}
\defineTalent{Deathless (aegis)}{Target gains a +4 morale bonus on saves against death spells, Death sphere effects, negative energy, and other death effects, and make make a saving throw to negate such effects even if not normally allowed.}{You may create an \textit{aegis} that grants the subject a +4 morale bonus on saves against all death spells, Death sphere abilities, channeled negative energy, and other magical death effects. The subject is granted a save to negate such effects even if one is not normally allowed. This \textit{aegis} does not protect against other sorts of attacks, even if those attacks might be lethal.}{}
\defineTalent{Distant Protection}{You may place your \textit{aegis} and center your \textit{wards} anywhere within Close range.}{When creating a \textit{ward}, you may center it anywhere within	Close range. When granting an \textit{aegis}, you may grant it to a target within Close range.}{}
\defineTalent{Energy Resistance (ward, aegis)}{You may create a \textit{ward} that reduces damage dealt within it of a chosen energy type (fire, cold, electricity, sonic, or acid) by \domath{\value{charCLCount} + 10}. You may grant an \textit{aegis} that provides energy resistance \domath{\value{charCLCount} + 10} to an energy type of your choice.}{
	You may create a \textit{ward} that suppresses one energy type of your choice (fire, cold, electricity, sonic, or acid). Any damage of that energy type dealt within this area is reduced by 10 + your caster level. You may also create an \textit{aegis} that grants energy resistance 10 + your caster level to either fire, cold, electricity, sonic, or acid. These effects only absorb damage and may not protect from other side effects of an attack.
}{}
\defineTalent{Guardian (aegis)}{Hostile targets within 10 ft of the bearer of this \textit{aegis} take a -\domath{\value{charCLCount} / 5 + 1} penalty to attack rolls against targets other than the bearer.}{
	You may create an \textit{aegis} that draws harmful attention to its bearer and away from their allies. Any hostile target within 10 ft of the bearer of this \textit{aegis} who decides to target any creature other than the bearer of this \textit{aegis} suffers a -1 penalty to their attack roll. This penalty increases by 1 for every 5 caster levels possessed. Multiple Guardian \textit{aegis} do not stack; if a creature attacks one creature with this \textit{aegis} while within the area of another creature with this \textit{aegis}, they suffer no penalty for their attack.}{}
\defineTalent{Healing Aegis}{As an immediate action, you may spend a spell point and dismiss one or more \textit{aegis} on a target to heal that target for \domath{\value{charCLCount} + \value{charCastingModCount}} per \textit{aegis} dismissed.}{As an immediate action, you may spend a spell point to dismiss one or more of your \textit{aegis} on a target, healing that target for an amount equal to your casting ability modifier + your caster level per \textit{aegis} dispelled. This may keep the target from dying.}{}
\defineTalent{Greater Barrier}{You may shape barriers into a flat wall that must begin \ifinlist{Distant Protection}{\charProtectionTalentsList}{within Close range of you and may extend out to Medium range from you}{adjacent to you and can extend out to Close range from you} and can cover \arabic{charCLCount} 10 ft square\s. When creating a barrier, you may spend an additional spell point to increase its hit points to \domath{\value{charCLCount} * 10} and break DC to \domath{\value{HalfCL} + 25}. If you do so, the barrier's hit points do not replenish if maintained through concentration.}{
	You may fashion your barrier into a flat plane if you so choose. This wall must be contiguous and must begin adjacent to you, although it may extend as far out as Close range (if you possess the Distant Protection talent, it must begin within Close range and be contained within Medium range), and can cover up to 1 10 ft square per caster level. In addition, when creating a barrier, you may spend an additional spell point to increase its Hit Points to 10 per caster level and increase the Break DC by 10. The barrier's hit points do not replenish, even if maintained through concentration.}{}
\defineTalent{Luck}{As an immediate action, you may dismiss an \textit{aegis} on a target to allow them to reroll a saving throw they have just made.}{As an immediate action, you may dismiss an \textit{aegis} on a target to allow them to reroll a saving throw they have just made. They must take the second result, even if it is worse.}{}
\defineTalent{Obstruction (aegis)}{The target gains DR \HalfCLMinOne/-. Once this \textit{aegis} has absorbed \domath{\value{charCLCount} * 10} points of damage it ends.}{You may create an \textit{aegis} that absorbs damage. The target gains DR/- equal to 1/2 the caster level (minimum: 1). Once this \textit{aegis} has absorbed damage equal to 10 $\times$ the caster level, the \textit{aegis} ends even if its duration has not yet expired.}{}
\defineTalent{Painful Aegis (aegis)}{When the bearer is struck by an attack, the attacker takes \HalfCLMinOne{} points of nonlethal damage.}{You may create an \textit{aegis} that inflicts pain on creatures that hurt its bearer. Whenever a creature successfully hits the bearer of this \textit{aegis} with a melee or ranged attack, that creature suffers 1 point of nonlethal damage per 2 caster levels (minimum: 1).}{}
\defineTalent{Peacebound (ward, aegis)}{You may create a \textit{ward} that prevents violence. Any attempt to cause violence from within the \textit{ward} fails and the action is wasted (will negates). If any target succeeds on this save, the entire \textit{ward} ends. You may grant an \textit{aegis} that protects the bearer against violence. Any attempt to cause violence to the target fails and the action is wasted (will negates). If a creature makes this save or the bearer takes a violent action, the \textit{aegis} immediately ends.}{
	You may create a \textit{ward} that renders all creatures within incapable of causing violence. Any violent action or targeted offensive magical effect created within the \textit{ward} fails and the target's action is wasted (Will negates). If any target succeeds at this Will save, the \textit{ward}'s effect immediately ends for all. When a peacebound \textit{ward} is broken in this fashion, all creatures within become immune to that caster's peacebound \textit{ward} for 24 hours.
	\par You may also create an \textit{aegis} that makes the target immune to violent actions or magic. Any such action made against the target requires the attacker to pass a Will save or lose that action. If a creature succeeds at this Will save (or the bearer of the peace bound \textit{aegis} takes an offensive action against any creature) the \textit{aegis} immediately ends.}{}
\defineTalent{Protected Health (aegis)}{The bearer gains a +4 morale bonus on saving throws against poison and disease}{You may create an \textit{aegis} that grants the target a +4 morale bonus to saving throws against all poisons and diseases, both magical and mundane.}{}
\defineTalent{Repel Evil/Good/Law/Chaos (ward)}{You may create a \textit{ward} that repels creatures of one end of the alignment spectrum. Such creatures cannot cross the edge of the \textit{ward} unless they succeed at a Will save, in which case they become immune for 24 hours.}{
	You may create a \textit{ward} that repels creatures of one end of the alignment spectrum (good, evil, lawful, chaotic), chosen by you when this \textit{ward} is created. All creatures of that alignment cannot cross the edge of this \textit{ward} unless they succeed at a Will save. Once a creature has succeeded at this Will save, they may cross the barrier without trouble and are immune to your repel \textit{ward} for 24 hours. If a creature is already within this \textit{warded} area when it is created, or if the \textit{ward} is moved into their space, they instantly become immune to the \textit{ward}, as if they had succeeded at their saving throw. You cannot repel an alignment that you yourself possess.}{}
\defineTalent{Resistance (aegis)}{The bearer of this \textit{aegis} gains a +\domath{\value{charCLCount} / 5 + 1} Resistance bonus on all saving throws.}{You may create an \textit{aegis} that grants +1 resistance bonus to all saving throws. This increases by 1 for every 5 caster levels you possess.}{}
\defineTalent{Slippery (aegis)}{The bearer of this \textit{aeigs} is slippery, gaining a +\domath{\value{charCLCount} / 5 + 2} enhancement bonus to Acrobatics and Escape Artist checks and to CMD.}{You may create an \textit{aegis} that protects a creature from being physically restrained or manipulated. The bearer of this \textit{aegis} gains a +2 enhancement bonus to Acrobatics checks, Escape Artist checks, and to CMD. These bonuses increase by 1 for every 5 caster levels you possess.}{}
\defineTalent{Spell Ward (ward, aegis)}{You may spend a spell point to create a \textit{ward} that suppresses magic. Make a magic skill check against each magical effect or item in the area. A successful check suppresses the magic for the duration of the \textit{ward}. Casters attempting to use magic within or targeted into the area and summoned creatures entering the area must pass a magic skill check against your MSD or the effect fails or creature banished. You may spend two spell points instead of one to grant an \textit{aegis} that grants spell resistance \domath{10 + \value{charCLCount}}}{
	You may spend a spell point to create a \textit{ward} that represses all magic within its area of effect. Make one magic skill check against each magical effect, magic item, or summoned creature within the area. Magic items have a MSD of 10 + their caster level. If your check exceeds the MSD of the magical effect, item, or caster who summoned the creature, the effect is suppressed, the magic item ceases to function, or the summoned creature temporarily disappears. Time spent suppressed counts to\textit{ward} a magical effect’s total duration. Any caster attempting to use a magical ability in or targeted within this area, or any summoned creature attempting to enter this area, must pass a magic skill check against your MSD. On a success, the magical effect is unimpeded, and the summoned creature is not banished by that spell \textit{ward}.
	\par You may also spend 2 spell points instead of 1 to create an \textit{aegis} that grants the target Spell Resistance equal to 10 + your caster level.}{}
\defineTalent{Status}{You always know the direction and distance to all creatures benefiting from your \textit{aegis} and are aware of any conditions affecting them.}{You always know the direction and distance to all creatures benefiting from your \textit{aegis} and are aware of any conditions affecting them (unharmed, wounded, disabled, staggered, unconscious, dying, nauseated, panicked, stunned, poisoned, diseased, confused, etc.). If the target dies or moves to another plane of existence, this effect ceases to function.}{}