\defineSphere{Telekinesis}{You can lift and move objects through magic.}{You can lift and move objects through magic.}
\def\chartelekinesisrange{Close}
\newCounter{chartelekinesissize}
\setCounter{chartelekinesissize}{1}
\defineBaseAbility{Telekinesis}{Telekinesis}{You can use \textit{telekinesis} to lift \ifinlist{Divided Mind}{\charTelekinesisTalentsList}{up to \domath{\value{charCLCount} + 1}\ifinlist{Steal}{\charTelekinesisTalentsList}{}{ unattended} objects or willing creatures whose combined size does not exceed}{an\ifinlist{Steal}{\charTelekinesisTalentsList}{}{ unattended} object or willing creature whose size does not exceed}
	\ifnum \value{charCLCount} > 2 \stepCounter{chartelekinesissize}%
	\ifnum \value{charCLCount} > 4 \stepCounter{chartelekinesissize}%
	\ifnum \value{charCLCount} > 7 \stepCounter{chartelekinesissize}%
	\ifnum \value{charCLCount} > 10 \stepCounter{chartelekinesissize}%
	\ifnum \value{charCLCount} > 14 \addToCounter{chartelekinesissize}{\value{charCLCount} / 5 - 2}%
	\fi\fi\fi\fi\fi%
	%%%
	%%%
	\ifnum \value{chartelekinesissize}		 = 1 Diminutive%
	\else \ifnum \value{chartelekinesissize} = 2 Tiny%
	\else \ifnum \value{chartelekinesissize} = 3 Small%
	\else \ifnum \value{chartelekinesissize} = 4 Medium%
	\else \ifnum \value{chartelekinesissize} = 5 Large%
	\else \ifnum \value{chartelekinesissize} = 6 Huge%
	\else \ifnum \value{chartelekinesissize} = 7 Gargantuan%
	\else \ifnum \value{chartelekinesissize} = 8 Colossal%
	\else \ifnum \value{chartelekinesissize} > 8 Colossal\forloop[-1]{@i}{\value{chartelekinesissize}}{\value{@i} > 5}{+}%
	\fi\fi\fi\fi\fi\fi\fi\fi\fi{}
	within \chartelekinesisrange{} range and move \ifinlist{Divided Mind}{\charTelekinesisTalentsList}{them}{it} up to \ifinlist{Greater Speed}{\charTelekinesisTalentsList}{\domath{\value{charCLCount} / 2 * 5 + 30}}{\domath{\value{charCLCount} / 5 * 5 + 20}} ft.\ifinlist{Steal}{\charTelekinesisTalentsList}{ The bearer of an attended object gets a Will save to resist.}{} The effect continues for as long as you concentrate and the object\ifinlist{Divided Mind}{\charTelekinesisTalentsList}{s}{} remains within range and sight. Objects you control with \textit{telekinesis} have touch AC \domath{10 + \value{charCastingModCount}} and CMD \domath{10 + \value{charCLCount} + \value{charCastingModCount}}, both modified by their respective size modifiers. You have the following special uses of \textit{telekinesis}:
	\par \textbf{Sustained Force:} You may spend a spell point to continue to lift an object without having to concentrate for \arabic{charCLCount} minute\s. You can give a sustained force simple orders, and change orders with a move action.
	\par \textbf{Hostile Lift:} You may spend a spell point to lift an unwilling creature (will negates). The target gets an additional save each round to end the effect.
	\par \textbf{Bludgeon:} You can strike creatures with controlled objects, making attacks with an attack bonus of \domath{\value{charBABCount} + \value{charCastingModCount}} and doing damage according to the bludgeon's size to both the bludgeon and the target. Weapons instead deal their normal damage and do not take damage themselves.\ifinlist{Dancing Weapon}{\charTelekinesisTalentsList}{ Add \arabic{charCastingModCount} to the damage dealt by a bludgeon. You may treat your bludgeons as melee weapons under your control, allowing allies to flank with it\ifinlist{Flair}{\charTelekinesisTalentsList}{ and allowing you to apply either melee feats or ranged feats to your attacks}{}.}{\ifinlist{Flair}{\charTelekinesisTalentsList}{ You may apply ranged feats to your attacks with a bludgeon.}{}\ifthenelse{\value{charBABCount} > 4}{\ifinlist{Divided Mind}{\charTelekinesisTalentsList}{ If you are lifting multiple objects, you may attack with each up to your normal number of attacks allowed by your BAB\ifinlist{Flair}{\charTelekinesisTalentsList}{ and relevant combat feats}{}.}{}}{}}
	\par \textbf{Catch:} You can stop projectiles using \textit{telekinesis} as a readied \ifinlist{Quick Catch}{\charTelekinesisTalentsList}{or immediate action}{}. The attacker is allowed a will save to negate this ability.
}{
As a standard action you can use \textit{telekinesis} to lift one unattended object or willing creature within Close range and move it up to 20 ft, + 5 ft per 5 caster levels. The object levitates as long as you concentrate, have line of sight, and the object remains within Close range. The objects and creatures you may lift are restricted by size; the largest object you can lift is given in the chart below. This assumes the object is made from a dense material, such as stone. Objects made of lighter materials, mostly open space, or reduced to 1/2 weight with the lighten talent of the enhancement sphere count as being one size category smaller, while weightless objects count as being 2 size categories smaller for this purpose.
\begin{wraptable}[11]{l}{135\unitlength}
	\raggedright\textbf{Table: Object Size}
	\rowcolors{2}{gray!25}{white}\small
	\begin{tabular}{ccc}
		\rowcolor{gray!50}
		\textbf{\textit{Caster Level}}& \textbf{\textit{Object Size}} & \textbf{\textit{Sample Object}}\\
		1st	& Diminutive& Dagger		\\
		3rd	& Tiny		& Candelabra	\\
		5th	& Small		& Heavy Shield	\\
		8th	& Medium	& Cage			\\
		11th& Large		& Statue		\\
		15th& Huge		& Wagon			\\
		20th& Gargantuan& Catapult		\\
		25th& Colossal	& Ship
	\end{tabular}
\end{wraptable}	
\par Your \textit{telekinesis} is simple and cannot perform dexterous actions (tying a knot, opening a book, turning a key, etc.). Any object you control with \textit{telekinesis} has a touch AC of 10 + your casting ability modifier + any size modifier, and a CMD of 10 + your caster level + your casting ability modifier + the object's size modifier.
\par You gain the following special uses of \textit{telekinesis} when you gain this sphere:
\par \textbf{Sustained Force:} You may, as a free action, spend a spell point to no longer need to concentrate to maintain lifting a particular object for up to 1 minute per caster level. You may give a sustained force simple orders (float in the air, go north, follow a target) that it obeys to the best of its ability. Changing a sustained force's orders is a move action. You cannot sustain combat-related uses of \textit{telekinesis} (combat maneuvers, bludgeons, etc.), nor complicated tasks (make a wagon load itself with stones and move them to another location, etc.).
\par \textbf{Hostile Lift:} You may spend a spell point to lift an unwilling creature with \textit{telekinesis}. The target is allowed a Will save to negate this effect, plus an additional Will save each round the effect is maintained. If a hostile lift is sustained with Sustained Force, it only lasts until the target succeeds at its save. A creature may suffer falling damage if they successfully save while floating high in the air.%
\begin{wraptable}{r}{90\unitlength}%
	\raggedright \textbf{Table: Object Damage}
	\rowcolors{2}{gray!25}{white}\small
	\begin{tabular}{cc}
		\rowcolor{gray!50}
		\textbf{\textit{Object Size}} & \textbf{\textit{Damage Dealt}}\\
		Fine		& 1		\\
		Diminutive	& 1d2	\\
		Tiny		& 1d3	\\
		Small		& 1d4	\\
		Medium		& 1d6	\\
		Large		& 1d8	\\
		Huge		& 2d6	\\
		Gargantuan	& 3d6	\\
		Colossal	& 4d6	
	\end{tabular}
\end{wraptable}%
\par \textbf{Bludgeon:} When you use a lifted creature or object to strike another creature or object (moving the object into the target's square and ramming them), you must succeed at an attack roll using your base attack bonus plus your casting ability modifier against the target. On a successful hit, the target and the bludgeon take damage depending on the bludgeon's size. If the bludgeon is a weapon, the attack deals appropriate damage for that weapon (bolts and arrows are treated as daggers for this purpose). Since weapons are designed to deal damage, it does not suffer damage if used as a bludgeon.
\par \textbf{Catch:} If using \textit{telekinesis} on a projectile or thrown object within your size limit (often as a readied action), you may stop the attack from dealing damage. The originator of the attack (the creature who threw the projectile, etc.) is allowed a Will save to negate this ability. After catching an object, you may move it as normal for your \textit{telekinesis}.
}
\defineTalent{Dancing Weapon}{Objects lifted with \textit{telekinesis} count as melee weapons under your control, allowing allies to flank with them\ifinlist{Flair}{\charTelekinesisTalentsList}{ and allowing you to apply melee attack feats to your bludgeons}{}. You also add \arabic{charCastingModCount} to all damage rolls with a bludgeon.}{
	When using \textit{telekinesis} to lift an object, that object counts as a melee weapon under your control. Allies may use it to flank, and if you possess the Flair talent, you may apply melee feats such as Power Attack to your actions with that bludgeon (you cannot treat a bludgeon as both a melee and a ranged weapon at the same time; you may apply either melee attack feats or ranged attack feats to an individual bludgeon, but not both). In addition, you may also add your casting ability modifier to all damage rolls made with a bludgeon.}{}
\defineTalent{Divided Mind}{You may lift up to \domath{\value{charCLCount} + 1} targets at once so long as their combined size does not exceed
	\ifnum \value{chartelekinesissize}		 = 1 Diminutive%
	\else \ifnum \value{chartelekinesissize} = 2 Tiny%
	\else \ifnum \value{chartelekinesissize} = 3 Small%
	\else \ifnum \value{chartelekinesissize} = 4 Medium%
	\else \ifnum \value{chartelekinesissize} = 5 Large%
	\else \ifnum \value{chartelekinesissize} = 6 Huge%
	\else \ifnum \value{chartelekinesissize} = 7 Gargantuan%
	\else \ifnum \value{chartelekinesissize} = 8 Colossal%
	\else \ifnum \value{chartelekinesissize} > 8 Colossal\forloop[-1]{@i}{\value{chartelekinesissize}}{\value{@i} > 5}{+}%
	\fi\fi\fi\fi\fi\fi\fi\fi\fi.
	\ifnum \value{charBABCount} > 4 This allows you to make multiple attacks with different bludgeons as a full attack.\fi}{
	You may lift multiple targets at once (up to 1 + 1 per caster level) whose combined size does not exceed your maximum \textit{telekinesis} size. You may treat these objects as one effective object for the purpose of bludgeoning a creature, or you may make multiple bludgeons per round (although you cannot make more attacks in a round than would otherwise be allowed with your BAB and any respective feats if you possess the Flair or Dancing Weapon talents). If you spend a spell point to use Hostile Lift or Sustained Force, it may apply it to as many of these objects as applicable. You may also spend a spell point when using the Steal, Telekinetic Maneuver, or Telekinetic Push talents to affect multiple targets at once (up to one additional target per 2 caster levels, minimum: 1), although you cannot affect an individual target more than once per round with any combat maneuver.}{}
\defineTalent{Finesse}{You have fine control over your \textit{telekinesis}. You can make Craft, Profession, \ifinlist{Flair}{\charTelekinesisTalentsList}{}{\ifinlist{Steal}{\charTelekinesisTalentsList}{}{and }} Perform\ifinlist{Flair}{\charTelekinesisTalentsList}{\ifinlist{Steal}{\charTelekinesisTalentsList}{, Disable Device, and Sleight of Hand}{, and Disable Device}}{\ifinlist{Steal}{\charTelekinesisTalentsList}{, and Sleight of Hand}{}} checks at \chartelekinesisrange{} range with a -5 penalty, and when doing so may use your spellcasting ability modifier instead of the usual ability modifier for that skill. Sustained Force can maintain complicated noncombat procedures.}{
	You may use \textit{telekinesis} to perform fine manipulations, such as turning a key in a lock, unrolling a scroll, or tying a knot. You may make appropriate skill checks (such as Craft, Profession, or Performance checks that involve objects or instruments) at a distance, as well as Heal checks to perform first aid. When performing a skill at a distance you may use your casting ability modifier in place of the normal ability modifier, but you also suffer a -5 penalty to the skill check. You may use Sustained Force to maintain complicated, non-combat procedures such as making knives prepare dinner, make a lute play itself, or making a shovel dig a ditch. When combined with the Flair talent, you may also perform Disable Device checks at a distance. When combined with the Steal talent, you may also perform Sleight of Hand checks to steal objects at a distance.}{}
\defineTalent{Flair}{You may add the effects of feats you possess to your \textit{telekinesis}, treating your Bludgeons as \ifinlist{Dancing Weapon}{\charTelekinesisTalentsList}{melee or }{}ranged weapons.}{
	You may use \textit{telekinesis} with a greater degree of detail. If you possess the Finesse talent, you may perform Disable Device checks at a distance with a -5 penalty. You may add the effects of feats you possess to the actions you perform with \textit{telekinesis} (adding the benefits of Point-Blank Shot or Weapon Focus to bludgeons, using improved trip or improved steal to maneuvers made with the Telekinetic Maneuver talent or Steal talent, etc.). Bludgeons count as ranged weapons for this purpose.}{}
\defineTalent{Flight}{When lifting a creature, you can grant it a fly speed of \ifinlist{Greater Speed}{\charTelekinesisTalentsList}{\domath{\value{charCLCount} / 2 * 5 + 30}}{\domath{\value{charCLCount} / 5 * 5 + 20}} ft (perfect) for as long as your lift continues.}{
	When using \textit{telekinesis} to lift a creature or creatures and spending a spell point to create a Sustained Force on them, you may grant that creature the ability to control their own movement for the duration of the Sustained Force. They gain a fly speed equal to your \textit{telekinesis} speed, with maneuverability (perfect). An affected creature does not need to remain within your \textit{telekinesis} range while flying in this manner.}{}
\defineTalent{Greater Speed}{The distance you can move things with \textit{telekinesis} increases to \domath{5 * \value{HalfCL} + 30} ft per round.}{The distance you can move things with \textit{telekinesis} increases to 30 ft + 5 ft per 2 caster levels per round.}{}
\defineTalent{Increased Range}{Increase the range of your \textit{telekinesis} to \chartelekinesisrange.}{Increase the range of your \textit{telekinesis} by one step (Close to Medium, Medium to Long). You may select this talent multiple times. The effects stack.}{
	\ifnum 1 = #1
	\def\chartelekinesisrange{Medium}
	\else\ifnum #1 > 1
	\def\chartelekinesisrange{Long}
	\fi
	\fi}
\defineTalent{Powerful Telekinesis}{Increase the maximum sized object or creature you may affect with \textit{telekinesis} by 1 size category.}{Increase the maximum sized object or creature you may affect with \textit{telekinesis} by 1 size category.}{\addToCounter{chartelekinesissize}{1}}
\defineTalent{Quick Catch}{You may spend a spell point to make a telekinetic catch\ifinlist{Telekinetic Push}{\charTelekinesisTalentsList}{ or push}{} as an immediate action.}{You may spend a spell point to make a telekinetic catch as an immediate action. If you possess the Telekinetic Push talent, you may spend a spell point to perform pushes as an immediate action.}{}
\defineTalent{Steal}{%
	You may use \textit{telekinesis} on attended objects. The owner is allowed a Will saving throw to negate this effect. If they fail, you may perform a Steal or Disarm combat maneuver against them at a distance with a CMB of \domath*{\value{charCLCount} + \value{charCastingModCount} - 5}. If successful, you may move the object up to \ifinlist{Greater Speed}{\charTelekinesisTalentsList}{\domath{\value{charCLCount} / 2 * 5 + 30}}{\domath{\value{charCLCount} / 5 * 5 + 20}} ft in any direction.}{%
	You may use \textit{telekinesis} on attended objects. The owner is allowed a Will saving throw to negate this effect. If they fail, you may perform a Steal or Disarm combat maneuver against them at a distance, using your caster level -5 plus your casting ability modifier as your CMB. On a successful maneuver, you may move the object up to your \textit{telekinesis} distance in any direction.}{}
\defineTalent{Telekinetic Maneuver}{You may use your \textit{telekinesis} to bull rush, pull, reposition, trip, grapple, or dirty trick a target at range with a CMB of \domath*{\value{charCLCount} + \value{charCastingModCount} - 5} and a CMD of \domath{\value{charCLCount} + \value{charCastingModCount}} }{
	You can use \textit{telekinesis} to manipulate a target. As a standard action, you may perform a bull rush, pull, reposition, trip, dirty maneuver, or grapple (upgrades to pin if the target is already grappled) combat maneuver against a target. Use your caster level -5 plus your casting ability modifier as your CMB. If grappling, your CMD is your CMB +5 and the target is allowed to make a new Will save each round to negate the effect. These maneuvers do not provoke an attack of opportunity from the target. If grappling, you do not gain the grappled condition, and you cannot be knocked prone by failing a trip check.}{}
\defineTalent{Telekinetic Push}{As a readied  \ifinlist{Quick Catch}{\charTelekinesisTalentsList}{or immediate action}{} you may increase a projectile or bludgeon's range increment by \ifinlist{Greater Speed}{\charTelekinesisTalentsList}{\domath{\value{charCLCount} / 4 * 5 + 15}}{\domath{\value{charCLCount} / 10 * 5 + 10}} ft and effective size by \domath{\value{charCLCount} / 5 + 1} size categor\ifthenelse{\value{charCLCount} > 4}{ies}{y}, increase a creature's speed by \ifinlist{Greater Speed}{\charTelekinesisTalentsList}{\domath{\value{charCLCount} / 4 * 5 + 15}}{\domath{\value{charCLCount} / 10 * 5 + 10}} ft, increase falling damage by \domath{\value{charCLCount} / 5 + 1}d6, or decrease a creature's speed and damage by half and prevent it from taking falling damage. (Will negates if unwilling)% 
	}{%
	You may throw your telekinetic power at an object, aiding or impeding its natural movement. As a readied action, you may push a projectile, creature, thrown object, or another caster's bludgeon up to one size larger than your telekinesis limit. If aiding, you may increase a weapon's range increment by half your telekinesis speed and increase its effective size by 1 size category +1 per 5 caster levels for the purposes of dealing damage or determining if another caster may catch the object with their own telekinesis. If aiding a creature, you may choose to instead grant it an enhancement bonus to its movement equal to 1/2 your telekinesis speed. You may also add 1d6 damage + 1d6 per 5 caster levels to the falling damage a target suffers. This ability may be used to cause damage to a target that was successfully tripped.
	\par Alternately, you may slow down a creature or object, cutting its movement speed and damage in half. If the target is falling, this decreases their falling speed to 60 ft per round, allowing them to fall great distances without being hurt.
	\par Telekinetic pushes don't require a spell point even when used on hostile targets, but do allow a Will save to negate.}{}