\defineSphere{Time}{You can alter the flow of time itself.}{You can alter the flow of time itself.}%
%
\def\charaltertimerange{touch}
\defineBaseAbility{Time}{Alter Time}{All \textit{alter time} abilities have a range of \charaltertimerange, and those maintained through concentration can be maintained out to \ifinlist{Ranged Time}{\charTimeTalentsList}{Close range}{the same range}. You have access to the Haste and Slow \textit{alter time} effects:
	\par \textit{Haste:} The target may make an extra attack at its highest BAB whenever it makes a full attack\ifinlist{Improved Haste}{\charTimeTalentsList}{, gains a +30 ft. enhancement bonus (max double) to all movement, and gains +1 to attack rolls, AC, and Reflex saves}{}. This lasts for as long as you concentrate, or \arabic{charCLCount} round\s without concentration if you spend a spell point.
	\par \textit{Slow:} The target is staggered (Will negates)\ifinlist{Improved Slow}{\charTimeTalentsList}{, has all movement rates halved, and suffers a -1  penalty to attack rolls, AC, and Reflex saves}{}. This lasts for as long as you concentrate, or \arabic{charCLCount} round\s{} without concentration if you spend a spell point.}{%
	The base Time sphere grants you two ways to \textit{alter time}. All \textit{alter time} effects require a standard action to activate unless otherwise stated and have a range of touch. Effects that target an area are centered on you. Effects maintained through concentration require you to remain within Close range of the target or location after placing the effect.
	\par \textit{Haste:} You grant the target the ability to make an extra attack at its highest BAB whenever it makes a full attack action. This effect is not cumulative with similar effects, such as that provided by a speed weapon, nor does it actually grant an extra action, so it cannot be used to cast a second sphere effect or otherwise take an extra action in the round. You must concentrate to maintain this effect, but may spend a spell point as a free action to allow it to remain for 1 round per caster level without concentration.
	\par \textit{Slow:} You cause the target to become staggered, allowing it to only take a single move action or standard action on its turn, but not both (Will negates). You must concentrate to maintain this effect, but may spend a spell point as a free action to increase its duration to 1 round per caster level without concentration.
	\par If a slow and haste ability are used on the same creature, the second caster must pass a magic skill check. On a failure the target is unaffected. On a success, the effects counter each other, leaving neither in place.
	\par Some Time talents are marked (time). These talents grant you additional \textit{alter time} abilities.}
\defineTalent{After Image (time)}{You blur the target, giving them a \domath{\minof{\value{charCLCount} / 3 * 5 + 20}{50}}\% miss chance for as long as you concentrate, or for \arabic{charCLCount} minute\s{} without concentration if you spend a spell point.}{
	You may cause a target to bleed through time, blurring their image so that they appear to be in multiple places at once. This grants the target concealment (20\% miss chance) against attacks, +5\% per 3 caster levels to a maximum of 50\%. This is a blur effect, and may be counteracted by abilities that specify they can see through them. Opponents that cannot see the subject ignore this penalty, although fighting an unseen opponent carries penalties of its own.
	\par This effect lasts as long as you concentrate, although you may spend a spell point as a free action to allow this effect to remain for 1 minute per caster level without concentration.}{}
\defineTalent{Age (time)}{You may spend a spell point to change the target's age category by \domath{\value{charCLCount} / 5 + 1} step\ifnum \value{charCLCount}>4 {s}\fi{} (Will negates) for as long as you concentrate, or for \arabic{charCLCount} minute\s{} without concentration if you spend an additional spell point.}{%
		\begin{wraptable}[11]{4}{137\unitlength}
			\raggedright\textbf{Table: Age Categories}
			\rowcolors{2}{gray!25}{white}\small
			\begin{tabular}{c>{\centering}p{85\unitlength}}
				\rowcolor{gray!50}
				\textbf{\textit{Age Category}}& \textbf{\textit{Physical Penalties\\(Age Penalties Accumulate)}}\tabularnewline
				Child		& -1 size category, -2 to all physical ability scores\tabularnewline
				Youth		& -1 to all physical ability scores\tabularnewline
				Young Adult	& none\tabularnewline
				Middle Age	& -1 to all physical ability scores\tabularnewline
				Old Age		& -2 to all physical ability scores\tabularnewline
				Venerable	& -3 to all physical ability scores
			\end{tabular}
		\end{wraptable}	
	\par You may spend a spell point to increase or decrease a target's age by 1 category (Unwilling creatures make a Fortitude save to negate). This adds or removes penalties to physical ability scores but does not add or remove bonuses to mental ability scores. You may move the target 1 age category older or younger, plus an additional category for every 5 caster levels possessed. This cannot cause the target to die of old age, nor become so young they were never born. This effect lasts as long as you concentrate, but you may always spend a spell point as a free action to allow this effect to continue for 1 minute per caster level without concentration. The effects of different age categories are cumulative (thus, a target moved from young adult to venerable would suffer a -6 penalty to all physical ability scores).}{}
\defineTalent{Eject (time)}{You may spend a spell point to eject a target from time (Will negates). They vanish from existence for \arabic{charCLCount} round\s, then return exactly as they were.}{
	You may spend a spell point to attempt to eject a target from time itself for 1 round per caster level (Will negates). The target disappears completely and cannot be the target of any damage or effect while it is vanished. When the effect ends, the target returns in the exact spot it disappeared from (or the closest unoccupied square). From the target's perspective no time has passed, and any effect already on the target with a duration (such as magic or poison) continues as if the time spent ejected simply hadn't happened.
}{}
\defineTalent{Fast Time (time)}{You may spend a spell point to accelerate time within a \domath{\value{charCLCount} / 5 * 5 + 10} ft radius burst centered \ifinlist{Ranged Time}{\charTimeTalentsList}{within \charaltertimerange{} range}{on you}. All effects within the area have their duration decreased by \arabic{charCLCount} round\s. Targets are allowed a Will save to prevent this from affecting effects on or originating from them.}{
	You may spend a spell point to accelerate time within a 10 ft radius burst, + 5 ft per 5 caster levels.
	\par All effects that are in effect within this area or on a creature within this area have their duration decreased by 1 round per caster level. This affects magic (spells, sphere abilities, etc.), poisons, diseases, etc., but does not grant extra actions to the targets within this area or provide any other benefit. In the case of effects that target areas, only the effect contained within fast time's area is accelerated. Unwilling targets (including allies if they choose) are allowed a Will save to negate this effect for themselves or area effects originating from them. You can choose whether or not to affect yourself with your own fast time.}{}
\defineTalent{Group Time}{When targeting creatures with an \textit{alter time} effect, you may spend an extra spell point to affect up to \HalfCLMinOne additional creature\s[HalfCL] within range. You may spend an extra spell point to double the size of an \textit{alter time} effect that targets an area.}{When targeting creatures with an \textit{alter time} effect, you may spend an extra spell point to affect up to 1 additional creature per 2 caster levels (minimum: 1) within range. All targets must be affected by the same \textit{alter time} effect. Alternately, you may spend an extra spell point to double the size of an \textit{alter time} effect that targets an area.}{}
\defineTalent{Improved Haste}{Haste also grants a 30 feet enhancement bonus (to a maximum of twice the subject's normal speed) to all movement, a +1 bonus to attack rolls, and a +1 Dodge bonus to AC and Reflex saves.}{When you use haste on a target, that target also gains a 30 feet enhancement bonus (to a maximum of twice the subject's normal speed) o all forms of movement. The target also gains a +1 bonus to attack rolls, as well as a +1 Dodge bonus to AC and Reflex saves.}{}
\defineTalent{Improved Slow}{When you use slow on a target, that target also has its movement speed halved and suffers a -1 penalty to attack rolls, AC, and Reflex saves.}{When you use slow on a target, that target also has its movement speed halved and suffers a -1 penalty to attack rolls, AC, and Reflex saves.}{}
\defineTalent{Ranged Time}{You increase the range of your \textit{alter time} to \charaltertimerange.}{
	Your \textit{alter time} effects gain a range of Close. You may select this talent multiple times. Each time it is selected, you may increase the range by one level (Close to Medium, Medium to Long). Increasing the range beyond Close also increases the range at which you may maintain an effect through concentration.}{
	\ifnum 1 = #1
	\def\charaltertimerange{Close}
	\else\ifnum 2 = #1
	\def\charaltertimerange{Medium}
	\else\ifnum #1 > 2
	\def\charaltertimerange{Long}
	\fi
	\fi
	\fi
}
\defineTalent{Repetition (time)}{You spend a spell point to give a target extra time. The target can take 20 on a Strength or Dexterity-based skill check that can be completed in one round without taking extra time, even if stress or distractions would otherwise prevent it. When used on yourself and only yourself you may do so as a swift action.}{
	You may spend a spell point to momentarily extend time for a target, allowing them to take extra care when performing an action. This allows the target to take 20 on a Strength or Dexterity-based skill check without increasing the time required to perform the action, even if stress or distractions would normally prevent the target from taking 10 or taking 20. This may only be used on skill checks that take no more than 1 round to perform. If using this ability on yourself and only yourself, you may use this ability as a swift action. You cannot use this ability as a swift action in this manner if combining it with the Group Time talent.}{}
\defineTalent{Retry (time)}{You may spend 2 spell points as an immediate action to force a taret to redo their turn (will negates if unwilling).}{
	As an immediate action, you may spend 2 spell points to force a target to redo their turn (Will negates if unwilling). The target is returned to where their turn began, and any skill checks, attack rolls, movement, attacks of opportunity, etc. that occurred during their turn become as if they never happened. The target may perform the same actions again (remaking any rolls required by such actions), or they may choose completely different actions. If you choose to redo your own turn in this manner, you do not recover the action or spell points spent using this ability.}{}
\defineTalent{Shift Time (time)}{You may spend a spell point to grant the target a single standard, move, or swift action of their choice, and they lose that action next turn. When used on yourself and only yourself you may do so as a swift action or as a free action if gaining a swift action.}{
	You may spend a spell point to grant the target the ability to immediately take a standard, move, or swift action if they choose. Any target who takes an action with this ability loses that action for their next turn. You may use this ability on yourself and only yourself as a swift action, or a free action if you choose to take a swift action with this ability. You cannot use this ability as a swift or free action in this manner if combining it with the Group Time talent.}{}
\defineTalent{Steal Time (time)}{You may spend a spell point to daze a target for 1 round (Will negates) and you immediately gain a standard action if they fail their save.}{
	You may spend a spell point to attempt to erase a target's turn from existence. The target is dazed for 1 round (Will negates). If successful, you immediately gain an additional standard action. An individual target cannot suffer the effects of this ability more than once per round. Even if you successfully target multiple creatures in the same round with this ability (such as through the Group Time talent), you cannot gain more than a single standard action in a round in this manner.
	}{}
\defineTalent{Time Freeze (time)}{
	You may spend a spell point to freeze all activity within a \domath{\value{charCLCount} / 5 * 5 + 10} ft radius burst centered \ifinlist{Ranged Time}{\charTimeTalentsList}{within \charaltertimerange{} range}{on you} for one round. If used as a readied action, this can stop ranged attacks and instantaneous magical effects. Unwilling targets are allowed a Will save to negate the effect for themselves and effects originating from them. You may choose whether or not to affect yourself. Affected objects and creatures cannot act, nor can they be acted upon.}{
	You may spend one spell point to freeze all activity within a 10 ft radius burst, + 5 ft per 5 caster levels.
	\par If used as a readied action, this can stop ranged attacks or instantaneous magical effects (such as destructive blasts), but in the case of effects that target areas, only the effect contained within the time freeze's area is stopped. Unwilling targets (including allies if they choose) are allowed a Will save to negate this effect for themselves or effects originating from them (attacks, magic, etc.). You can choose whether or not to affect yourself with your own time freeze.
	\par All affected objects and creatures within this area cannot act for 1 round, neither can they be acted upon (moved, dealt damage to, etc.). Once the effect is in place, non-affected creatures can enter the area of effect without incident, so long as they don't disturb an affected creature or object. After one round has passed, everything within the area is unfrozen; creatures resume moving, ranged attacks hit the square they were targeting, and blast effects resolve as normal.}{}