\defineSphere{War}{You can alter a battlefield, affecting both allies and enemies with your magic.}{You can alter a battlefield, affecting both allies and enemies with your magic.}
\defineBaseAbility{War}{Totem}{You may place a \textit{totem}, which is a \domath{\value{charCLCount} / 2 * 5 + 50} ft radius centered \ifinlist{Ranged Totem}{\charWarTalentsList}{within \chartotemrange{} range}{on you, but does not move with you}. A \textit{totem} lasts as long as you concentrate from within Long range, or for \arabic{charCLCount} round\s{} at any distance without concentration if you spend a spell point. You have access to the \textit{Totem of War}.\par \textit{Totem of War:} You and your allies gain a +\domath{\value{charCLCount} / 5 + 2} circumstance bonus to all weapon damage rolls.}{%
	As a standard action, you may place a \textit{totem}. A \textit{totem} is an effect on a 50 ft + 5 ft per 2 caster level radius area, centered on you, but does not move as you do. Creatures who leave this area lose the effects of your \textit{totem}. You must concentrate to maintain a \textit{totem}, but may always spend a spell point as a free action to allow a \textit{totem} to remain for 1 round per caster level without concentration.
	\par You must remain within Long range of the center of your \textit{totems} when maintaining them through concentration. If you move beyond this range, the \textit{totem} ends.
	\par When you gain the war sphere, you gain the following \textit{totem}:
	\par \textit{Totem of War:} You and your allies gain a +2 circumstance bonus to all weapon damage rolls. This bonus increases by 1 for every 5 caster levels.
	\par Talents marked (totem) grant you new \textit{totems}.}
\defineBaseAbility{War}{Rally}{Some talents are marked (rally) and grant you methods of \textit{rallying} targets. \textit{Rallying} a target is an immediate action, and may only be used on a target within the area of effect of one of your \textit{totems}. You must be within Long range of a target to \textit{rally} that target.}{Some talents are marked (rally) and grant you methods of \textit{rallying} targets. \textit{Rallying} a target is an immediate action, and may only be used on a target within the area of effect of one of your \textit{totems}. You must be within Long range of a target to \textit{rally} that target.}
\defineTalent{Absorb (rally)}{When an enemy deals damage to an ally within the area of effect of one of your \textit{totems}, you may spend a spell point to transfer half of this damage to another ally within the area of effect of one of your \textit{totems}. This damage cannot be reduced or divided further.}{
	When an enemy deals damage to an ally within the area of effect of one of your \textit{totems}, you may spend a spell point to transfer half of this damage to another ally within the area of effect of one of your \textit{totems}. This damage cannot be reduced or divided further.}{}
\defineTalent{Blood Totem (totem)}{You may spend a spell point to create a blood \textit{totem}. Whenever an enemy within this \textit{totem}'s area deals damage to an ally within this \textit{totem}'s area, the damage is reduced by \domath{\value{charCLCount} / 5 + 1}, and the attacker takes \domath{\value{charCLCount} / 5 + 1} damage.}{
	You may spend a spell point to create a blood \textit{totem}. Whenever an enemy within this \textit{totem}'s area deals damage to an ally within this \textit{totem}'s area, the damage roll is reduced by 1 (to a minimum of 0), and the attacker takes 1 damage that bypasses all damage resistance. The damage reduced and the damage dealt by this \textit{totem} increases by 1 for every 5 caster levels you possess.}{}
\defineTalent{Greater Rally}{When \textit{rallying} a target, you may spend an extra spell point to \textit{rally} up to \HalfCLMinOne creature\s[HalfCL].}{When \textit{rallying} a target, you may spend an extra spell point to \textit{rally} up to 1 additional creature per 2 caster levels (minimum: 1). You must affect every selected creature with the same \textit{rally}.}{}
\defineTalent{Hallowed Totem (totem)}{All creatures within the area of this \textit{totem} suffer a -\domath{\value{charCLCount} / 10 + 1} penalty to saving throws made to resist channeled positive energy and positive energy effects.}{
	All creatures within the area of this \textit{totem} suffer a -1 penalty to saving throws made to resist channeled positive energy and positive energy effects such as cure spells and Life sphere effects. This penalty increases by 1 for every 10 caster levels. If you place an hallowed \textit{totem} in a location that already has a unhallowed \textit{totem} present, you must succeed at a magic skill check to place your \textit{totem}. On a success, the two \textit{totems} cancel each other, leaving neither hallowing \textit{totem} nor unhallowed \textit{totem} in place.
}{}
\defineTalent{Invigorating Totem (totem)}{You and your allies gain 1 temporary hit point, +1 temporary hit point every subsequent round at the end of your turn. These temporary hit points stack with themselves, to a maximum of \arabic{charCLCount} temporary hit points. These temporary hit points only remain as long as you remain within the area of effect of this \textit{totem}.}{
	You and your allies gain 1 temporary hit point, +1 temporary hit point every subsequent round at the end of your turn. These temporary hit points stack with themselves, to a maximum number of temporary hit points equal to your caster level. These temporary hit points only remain as long as you remain within the area of effect of this \textit{totem}.
}{}
\defineTalent{Position (rally)}{You may spend a spell point to rally a target, allowing it to immediately move up to \domath{\HalfCLMinOne * 5} ft. This movement does not provoke attacks of opportunity and must end within the area of effect of one of your \textit{totems}.}{
	You may spend a spell point to rally a target, allowing it to immediately move up to 5 ft per 2 caster levels (minimum: 5 ft). This movement does not provoke attacks of opportunity and must end within the area of effect of one of your \textit{totems}.}{}
\defineTalent{Ranged Totem}{When placing a \textit{totem}, you may center it anywhere within \chartotemrange range.}{When placing a \textit{totem}, you may center it anywhere within Close range. You may select this talent multiple times. Each time it is taken, increase the range by one range increment (Close to Medium, Medium to Long).}{
	\ifnum 1 = #1
	\def\chartotemrange{Close}
	\else\ifnum 2 = #1
	\def\chartotemrange{Medium}
	\else\ifnum #1 > 2
	\def\chartotemrange{Long}
	\fi
	\fi
	\fi}
\defineTalent{Retribution (rally)}{
	When an enemy deals damage to an ally and both are within the area of one of your \textit{totems}, you may spend a spell point to deal \HalfCLMinOne{}d6 damage to the attacker. This damage may be either acid, electricity, cold, or fire.}{When an enemy deals damage to an ally and both ally and enemy are within the area of effect of one of your \textit{totems}, you may spend a spell point to deal 1d6 damage to the attacker for every 2 caster levels you possess (minimum: 1d6). This damage may be either acid, electricity, cold, or fire.}{}
\defineTalent{Revitalize (rally)}{You may spend a spell point to rally a target, allowing them to reroll a saving throw they just failed.}{You may spend a spell point to rally a target, allowing them to reroll a saving throw they just failed. They must take the second result, even if it is worse.}{}
\defineTalent{Safety (rally)}{When a target confirms a critical hit against a target within one of your \textit{totems}, you may spend a spell point to cause that critical hit to resolve as a normal hit instead.}{When a target confirms a critical hit against a target within one of your \textit{totems}, you may spend a spell point to cause that critical hit to resolve as a normal hit instead.}{}
\defineTalent{Scourging Totem (totem)}{This \textit{totem} deals \HalfCLMinOne{} energy damage to every enemy within range each round. This damage may be acid, electricity, cold, or fire, as chosen when the \textit{totem} is created.}{
	This \textit{totem} emits pulses of energy, damaging every enemy within your \textit{totem}'s range for an amount per round equal to 1/2 your caster level (minimum: 1). This damage may be acid, electricity, cold, or fire, as chosen when the \textit{totem} is created. Creatures who enter the area of effect of this \textit{totem} suffer damage immediately. Creatures who remain within the area of this \textit{totem} suffer damage each round at the end of your turn.}{}
\defineTalent{Totem of Allegiance (totem)}{Choose an end of the alignment spectrum which matches your own. Creatures of that alignment within the area of this \textit{totem} gain a +\domath{\value{charCLCount} / 10 + 1} bonus on attack rolls and saving throws. If you are True Neutral you may choose True Neutral, and this affects only True Neutral creatures.}{
	You may spend a spell point to create a \textit{totem} that aids creatures of a particular alignment. Choose an end of the alignment spectrum (good, evil, lawful, or chaotic) when you create this \textit{totem}. Creatures within the area of this \textit{totem} who possess that alignment gain a +1 bonus to all saving throws and attack rolls. This bonus increases by 1 per 10 caster levels.
	\par You must select an alignment that you possess. If you are True Neutral, you may select neutrality with this \textit{totem}. This only benefits True Neutral creatures; Neutral Good, Neutral Evil, Lawful Neutral, and Chaotic Neutral creatures are unaffected.}{}
\defineTalent{Totem of Courage (totem)}{Create a \textit{totem} which grants a +\domath{\value{charCLCount} / 10 + 1} bonus to attack rolls and \ifnum \value{charCLCount} > 4 a +\domath{\value{charCLCount} / 5 + 1} bonus on \fi{} saving throws vs fear.}{
	You must spend a spell point to create a \textit{totem} of courage. You and your allies gain a +1 morale bonus to attack rolls and saves vs fear. The bonus to attack rolls increases by 1 for every 10 caster levels you possess, and the bonus to saves vs fear increases by 1 for every 5 caster levels you possess.}{}
\def\chartotemofdoomstacking{ This does not stack with other fear effects.}
\defineTalent{Totem of Doom (totem)}{You may spend a spell point to create a \textit{totem} that causes all enemies in the area to become shaken (no save) for as long as they remain in the area.\chartotemofdoomstacking}{
	You must spend a spell point to place a \textit{totem} that causes all enemies in the area to become shaken (no save). This effect lasts as long as they remain within the \textit{totem}'s effect area. The effects of this \textit{totem} are not cumulative with itself or other sources of fear.
	You may take this talent a total of three times. If taken twice, your \textit{totem} of doom becomes cumulative; if a creature comes into contact with your \textit{totem} of doom who is already shaken from another effect, the effect of your \textit{totem} of doom is changed to frightened for that specific creature. If you gain this talent three times, a creature who comes into contact with your \textit{totem} of doom who is already frightened from another effect becomes panicked. Multiple \textit{totems} of doom do not stack with each other for this purpose.}{%
	\ifthenelse{2 = #1}{\def\chartotemofdoomstacking{ If an enemy is already shaken they become frightened instead.}}{%
	\ifthenelse{#1 > 2}{\def\chartotemofdoomstacking{ If an enemy is already shaken they become frightened instead. If an enemy is already frightened they become panicked instead.}}{}}%
	}
\defineTalent{Totem of Enemies (totem)}{You may spend a spell point to create a \textit{totem} that hinders creatures of a particular alignment. Choose an end of the alignment spectrum. Creatures with that alignment within the area of this \textit{totem} suffer a -\domath{\value{charCLCount} / 10 + 1} penalty to all saving throws and attack rolls. You must select an alignment that you do not possess. If you are not Neutral, you may select True Neutral.}{
	You may spend a spell point to create a \textit{totem} that hinders creatures of a particular alignment. Choose an end of the alignment spectrum (good, evil, lawful, or chaotic) when you create the \textit{totem}. Creatures within the area of this \textit{totem} who possess that alignment suffer a -1 penalty to all saving throws and attack rolls. This penalty increases by 1 per 10 caster levels. You must select an alignment that you do not possess. If you are Lawful Good, Lawful Evil, Chaotic Good, or Chaotic Evil, you may select True Neutral with this \textit{totem}.}{}
\defineTalent{Totem of Iron (totem)}{Spend a spell point to create a \textit{totem} which grants you and your allies a +\domath{\value{charCLCount} / 10 + 1} natural armor bonus.}{
	You may spend a spell point to create a \textit{totem} of iron. This grants you and your allies a +1 natural armor bonus. This bonus increases by +1 for every 10 caster levels you possess.}{}
\defineTalent{Totem of Liberation (totem)}{You may spend a spell point to create a \textit{totem} which grants a \domath{\value{charCLCount} / 5 + 1} insight bonus on saves against mind-affecting effects.}{
	You may spend a spell point to create a \textit{totem} of liberation. You and your allies gain a +1 insight bonus against all mind-altering effects, enchantment (charm) effects, enchantment (compulsion) effects, and Mind sphere abilities. This bonus increases by 1 for every 5 caster levels you possess.}{}
\defineTalent{Totem of Mobility (totem)}{You may spend a spell point to create a \textit{totem}. Allies within the area may make a 5 ft step as a swift action, which does not prevent other movement.}{
	You may spend a spell point to create a \textit{totem} of mobility. As a swift action, allies within this area may make a 5 ft step. This is in all ways similar to a normal 5 ft step, except this does not prohibit them from taking their usual 5 ft step, nor using a move action to move normally.}{}
\defineTalent{Totem of Speed (totem)}{You can create a \textit{totem} that grants you and your allies a +\domath{\value{charCLCount} / 5 * 5 + 5} ft bonus to all movement speeds.}{You and your allies gain a +5 bonus to all movement speeds, + 5 ft per 5 caster levels.}{}
\defineTalent{Totem of Stability (totem)}{You can create a \textit{totem} that grants you and your allies a +\domath{\value{charCLCount} / 5 + 2} bonus to CMD.}{You and your allies gain a +2 bonus to CMD. This bonus increases by +1 for every 5 caster levels you possess.}{}
\defineTalent{Totem of Stumbling (totem)}{You can create a \textit{totem} that gives your enemies a -\domath{\value{charCLCount} / 5 + 2} penalty to CMD.}{All enemies suffer a -2 penalty to their CMD. This penalty increases by 1 for every 5 caster levels.}{}
\defineTalent{Totem of Tactical Prowess (totem)}{Whenever you or your allies gain a tactical bonus to an attack roll or AC, such as from flanking, high ground, or cover, that bonus increases by \domath{\value{charCLCount} / 5 + 1}}{Whenever you or your allies would gain a bonus to attack rolls or to AC due to battlefield positioning, such as flanking, higher ground, or cover, that bonus is increased by 1, +1 per 5 caster levels.}{}
\defineTalent{Unhallowed Totem (totem)}{All creatures within the area of the totem suffer a -\domath{\value{charCLCount} / 10 + 1} penalty to saving throws against negative energy effects.}{
	All creatures within the area of this totem suffer a -1 penalty to saving throws made to resist channeled negative energy and negative energy effects such as inflict spells and Death sphere effects. This penalty increases by 1 for every 10 caster levels. If you place an unhallowed totem in a location that already has a hallowed totem present, you must succeed at a magic skill check to place your totem. On a success, the two totems cancel each other, leaving neither hallowed totem nor unhallowed totem in place.}{}