    
\DeclareSpell{Bed Of Iron}{necromancy|V,  S,  M (a feather or swatch of soft fabric)|1 standard action|touch|Targets: one creature touched/level|8 hours|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Bed Of Iron}{This spell makes even the clunkiest armor feel soft as silk to the wearer. The subjects of this spell are able to sleep comfortably in medium or heavy armor without suffering from fatigue the following day.}
        
\DeclareSpell{Carry Companion}{transmutation|V,  S,  M (a pinch of sand or limestone dust)|1 standard action|touch|Targets: one willing creature touched|permanent; see text|none|yes (harmless)}[]
    \DeclareSpellDescription{Carry Companion}{You touch an animal or magical beast that has a helpful attitude toward you, instantly transforming the creature into a miniature figurine of stone, small enough to fit into the palm of your hand. Creatures with an attitude of less than helpful will not tolerate this spell, and it automatically fails to work on them. An intelligent animal or magical beast must be a willing subject in order for this spell to take effect. Any items that the creature wears (such as a harness or saddle) or carries (such as those stowed in saddlebags) are transformed along with the creature.  While miniaturized, the creature is under an effect similar to that of a flesh to stone spell: It is mindless and inert, and does not seem alive when viewed with spells like deathwatch. However, you may return the creature to its normal form at any time simply by placing the figurine on the ground, touching it, and uttering a word of command. Otherwise, the creature remains in miniature form unless the spell is broken, such as by dispel magic or stronger magic. Unlike a flesh to stone spell, a creature affected by carry companion is unaffected by stone to flesh. If the miniature figurine is broken or damaged, the creature (if returned to its original state) has similar damage or deformities.}
        
\DeclareSpell{Clarion Call}{illusion|V,  S,  M (a piece of brass)|1 standard action|touch|Targets: creature touched|10 minutes/level|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Clarion Call}{The subject of this spell gains two benefits. First, the affected creature gains the ability to create a sound like the blast of a mighty horn or trumpet simply by miming the action of sounding one. Second, the subject can speak in a booming voice that carries easily over great distances, lowering the DC of any check to hear what is said by -15. This spell is particularly prized by battlefield commanders and champions who wish to make themselves clearly heard or gain the attention of their allies or foes.}
        
\DeclareSpell{Emblazon Crest}{transmutation|S,  F (an example of the crest or coat of arms)|1 standard action|touch|Targets: creature touched|1 hour/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Emblazon Crest}{This spell ensures the subject touched is always able to display her proper crest and coat of arms. Any tabard or tunic worn and any shield carried by the subject while this spell is active can be made to display a coat of arms when the spell is cast. For example, even if the subject picks up a different shield, it still displays the subject's crest, regardless of the shield's normal appearance.}
        
\DeclareSpell{Keep Watch}{enchantment|V,  S|1 standard action|touch|Targets: one creature touched/2 levels|8 hours or less; see text|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Keep Watch}{This spell enables the subjects to stand watch or keep vigil throughout the night without any ill effects. The subjects suffer no fatigue and gain all the usual benefits of a full night's rest. The subjects gain hit points as though from resting, wizards may prepare their spells as though they had slept for 8 hours, and so on. Effects that rely on actual sleep or dreaming are ineffective, though the subjects are still susceptible to effects that would put them to sleep, such as sleep or deep slumber. Any vigorous activity, including fighting, immediately ends the effect, and the affected creatures must either have the spell cast on them again or sleep for the remaining hours to avoid fatigue and gain the benefits of a full night's rest.}
        
\DeclareSpell{Serren's Armor Lock}{transmutation|V,  S,  M (a pinch of rust)|1 standard action|medium (100 ft. + 10 ft./level)|Targets: one armored creature|1 round/level (D)|Reflex partial; see text|yes}[]
    \DeclareSpellDescription{Serren's Armor Lock}{Upon pointing at an armored foe, you cause all of the joints of the target's armor to stiffen as otherworldly chains wrap around the target. On a failed Reflex save, a target in heavy metal armor becomes staggered. A target in light or medium metal armor instead becomes entangled. Targets wearing no armor or nonmetallic armor are unaffected. If the target is wearing heavy metal armor and succeeds at its Reflex save, it becomes entangled instead of staggered; a target in light or medium metal armor that succeeds at its saving throw is unaffected by the spell.}
        
\DeclareSpell{Serren's Swift Girding}{transmutation|V,  S,  M (the armor to be worn)|1 standard action|close (25 feet + 5 feet/level)|Targets: one willing creature/level|instantaneous|none|yes (harmless)}[]
    \DeclareSpellDescription{Serren's Swift Girding}{With a sweep of your hand, you select a number of targets and the same number of suits of armor. The targets of this spell are immediately clad in the armor that you choose. The subjects of the spell must be capable of wearing the chosen armor, cannot be wearing other armor, and must be able to properly fit into the chosen armor. The chosen armor must be empty and cannot be currently worn by another creature (thus you cannot move armor from one wearer to another with this spell). Creatures armored with this spell are considered to have donned the armor properly.}
        
\DeclareSpell{Ward Shield}{abjuration|V,  S|1 standard action|touch|Targets: shield touched|1 minute/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Ward Shield}{With a touch, you enchant a shield and enable it to protect its wielder from hostile spells. The shield grants spell resistance 10 + your caster level against spells so long as the shield can be interposed between the wielder and the spell effect. A spell shield does not provide spell resistance against area effect spells such as fireball, but does provide a +5 bonus on Reflex saving throws against such spells.}
    