    
\DeclareSpell{Aquatic Trail}{divination [water]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Area: circle centered on you, with a radius of 100 feet + 10 feet per level|1 hour/level|none|no}[]
    \DeclareSpellDescription{Aquatic Trail}{You use divination magic to enhance the underwater trails in the area around you, allowing you to track creatures through the water as if across soft ground as long as they passed through the area less than 1 week ago (this lets you notice trails that are much older than normal underwater trails). The spell's area moves with you, so you can follow the trail through the water over long distances. Other creatures can also follow the trail as long as they move with you. Because of the plethora of sea creatures in the higher zones, it's possible that the trail that most interests you will be covered by the trails of other aquatic creatures, making this spell even more useful than normal in the Abyssal and Abaddonian zones.}
        
\DeclareSpell{Extreme Buoyancy}{evocation|V,  S,  M (a bag of air),  DF|1 standard action|touch|Targets: creature touched|10 minutes/level|Will negates|yes}[]
    \DeclareSpellDescription{Extreme Buoyancy}{The target's buoyancy becomes and stays swiftly rising, regardless of how dense the target and its gear are. Among other effects, the target needs to succeed at a DC 20 Swim check to submerge itself and to stay submerged (see Buoyancy on page 43).}
        
\DeclareSpell{Free Swim}{abjuration|V,  S,  M (a strip of kelp bound to the target),  DF|1 standard action|touch|Targets: creature touched|10 minutes/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Free Swim}{The target can move and attack underwater normally without the usual penalties involved with underwater combat, as if under the effects of freedom of movement. However, the target doesn't gain any protections against grapple, paralysis, and magical effects that impede movement (such as solid fog, slow, and web).}
        
\DeclareSpell{Invisibility Bubble}{illusion (glamer)|V,  S,  M (a needle from a sea urchin)|1 standard action|touch|Area: touched creature's space, up to one 5-foot-cube|1 minute/level (D)|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Invisibility Bubble}{A glamered bubble surrounds the target's space, rendering her completely invisible underwater by hiding both the target and any water she displaces. Because of the bubble's size limit, this spell works only on Medium or smaller targets. Other objects and creatures within the bubble's space are also invisible while they stay in the space, which could reveal the spell's existence to a canny observer who notices fish disappearing into the bubble and reappearing on the other side. Creatures inside the bubble can see each other, which allows foes who can pinpoint the bubble's location (such as dragons) to stick their heads into the bubble in order to see the target. Any creature on the inside of the bubble that takes any action that would break invisibility pops the bubble and ends the spell early. On land, the bubble is clearly visible, acting much as invisibility does in the water. Unlike with invisibility, the inside of the bubble blocks light from escaping the bubble, meaning that light sources inside the bubble don't illuminate past its edges, but also don't reveal a telltale glow.}
        
\DeclareSpell{Giant Invisibility Bubble}{illusion (glamer)|V,  S,  M (a needle from a sea urchin)|1 standard action|touch|Area: 10-ft.-radius emanation centered on the touched creature's space|1 minute/level (D)|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Giant Invisibility Bubble}{This functions as per invisibility bubble, but the bubble is larger, which allows you to target a creature of up to size Gargantuan, or allows more creatures into the bubble.}
        
\DeclareSpell{Mass Invisibility Bubble}{illusion (glamer)|V,  S,  M (a needle from a sea urchin)|1 standard action|long (400 ft. + 40 ft./level)|Area: 10-ft.-radius emanation centered on the touched creature's space|1 minute/level (D)|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Mass Invisibility Bubble}{This functions as per invisibility bubble, but the spell affects the areas of each target creature, regardless of the creature's size. The effect moves with the group and is broken when anyone in the group attacks. Individuals in separate bubbles can't see each other. The spell is broken for any individual who moves more than 180 feet from the nearest member of the group. If only two individuals are affected, the one moving away from the other one loses its invisibility. If both are moving away from each other simultaneously, they both become visible when the distance between them exceeds 180 feet.}
        
\DeclareSpell{Lead Anchor}{evocation|V,  S,  M (a bag of air),  DF|1 standard action|touch|Targets: creature touched|10 minutes/level|Will negates|yes}[]
    \DeclareSpellDescription{Lead Anchor}{The target's buoyancy becomes and stays swiftly sinking, regardless of how dense the target and its gear are. Among other effects, the target can walk on the bottom, but she also needs to succeed at a DC 20 Swim check to swim towards the surface and to stay above the bottom (see Buoyancy on page 43). This makes lead anchor a useful spell both for exploring the sea floor and for drowning an air-breathing foe in the water.}
        
\DeclareSpell{Life Current}{conjuration (healing) [water]|V,  S,  DF|1 standard action|medium (100 ft. + 10 ft./level)|Area: current or portion of current up to 20 feet wide and 100 feet long|1 round|Will half|yes}[]
    \DeclareSpellDescription{Life Current}{You infuse the current with positive energy. At the start of their turn when the current moves them, living creatures in the current's area heal 1d6 hit points per 10 feet of the current's speed (maximum 6d6). Undead creatures in the current instead take an equal amount of damage.}
        
\DeclareSpell{Neutral Buoyancy}{evocation|V,  S,  M (a bag of air),  DF|1 standard action|touch|Targets: creature touched|10 minutes/level|Will negates|yes}[]
    \DeclareSpellDescription{Neutral Buoyancy}{The target's buoyancy becomes and stays neutral, regardless of how dense the target and its gear are. Among other effects, the target neither sinks nor rises when it doesn't attempt a Swim check, making it easier to stay put while performing demanding actions or when helpless or disabled, and the target can swim up and down with equal ease.}
        
\DeclareSpell{Pressure Adaptation}{abjuration|V,  S,  M (slime from a cephalopod)|1 standard action|touch|Targets: creature touched|1 hour/level|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Pressure Adaptation}{The target adapts incredibly quickly to changes in pressure, adjusting to 100 feet of new pressure (or the entire shift, in the case of an instantaneous shift within its native range; see page 48) after just one successful Fortitude saving throw instead of the usual five.}
        
\DeclareSpell{Stabilize Pressure}{abjuration|V,  S,  M (a piece of shell)|1 standard action|touch|Targets: creature touched|instantaneous|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Stabilize Pressure}{You instantly stabilize the target's pressure, causing it to adjust to its current pressure all at once. This doesn't help it readjust to future pressure changes.}
        
\DeclareSpell{Steam Ray Fusillade}{evocation [fire,  water]|V,  S,  M (a scraping from a hydrothermal vent)|1 standard action|personal|Targets: you|1 round/level||}[]
    \DeclareSpellDescription{Steam Ray Fusillade}{For the duration of the spell, you can fire three rays of steam once per round as a standard action (and you also fire three such rays as part of casting the spell). These rays function similarly to the rays from scorching ray (you can fire them at close range, they're ranged touch attacks, they deal 4d6 points of fire damage each, and spell resistance negates  them) except that they work both underwater and above water without a caster level check for being a fire spell.}
        
\DeclareSpell{Unlife Current}{conjuration (healing) [water]|V,  S,  DF|1 standard action|medium (100 ft. + 10 ft./level)|Area: current or portion of current up to 20 feet wide and 100 feet long|1 round|Will half|yes}[]
    \DeclareSpellDescription{Unlife Current}{This functions as life current except you infuse the current with negative energy, so it heals undead and harms living creatures.}
    