    
\DeclareSpell{Burning Disarm}{transmutation () [fire]|V,  S|1 standard action|Short (25 ft. + 5 ft./2 levels)|TargetsHeld metal item of one creature or 15 lbs. of unattended metal|Instantaneous|Reflex negates (object, see text)|Yes (object)}[]
    \DeclareSpellDescription{Burning Disarm}{This spell causes a metal object to instantly become red hot. A creature holding the item may attempt a Reflex save to drop it and take no damage (even if it is not their turn), otherwise the hot metal deals 1d4 points of fire damage per caster level (maximum 5d4). Circumstances that prevent the creature from dropping the item (such as a locked gauntlet) mean the creature gets no saving throw. The heat does not harm the item, and it does not get hot enough or last long enough to ignite flammable objects. The item cools to its previous temperature almost instantly. If cast underwater, burning disarm deals half damage and boils the surrounding water.}
        
\DeclareSpell{Dweomer Retaliation}{abjuration () []|V|1 immediate action|Long (400 ft. + 40 ft./level)|Targetsone creature you counterspelled since your last turn|instantaneous|none|yes}[]
    \DeclareSpellDescription{Dweomer Retaliation}{You may only cast this spell immediately after successfully counterspelling an opponent. Drawing upon the residual energy of the countered spells, you gain a number of temporary hit points equal to the level of the countered spell plus your Charisma or Intelligence modifier (for sorcerers and wizards, respectively); your counterspelled opponent takes damage equal to this amount.
If the countered spell was at least 4th level, you and your opponent make opposed concentration checks. If you beat your opponent by 10 or more, you retain this spell (or its spell slot, if you are a sorcerer) as if you had not cast it.}
        
\DeclareSpell{Emergency Force Sphere}{evocation () [force]|V|1 immediate action|5 ft.|Effect5-ft.-radius hemisphere of force centered on you|1 round/level|None|No}[]
    \DeclareSpellDescription{Emergency Force Sphere}{As wall of force, except you create a hemispherical dome of force with hardness 20 and a number of hit points equal to 10 per caster level. The bottom edge of the dome forms a relatively watertight space if you are standing on a reasonably flat surface. The dome shape means that falling debris (such as rocks from a collapsing ceiling) tend to tumble to the side and pile up around the base of the dome. If you make a DC 20 Craft (stonemasonry), Knowledge (engineering), or Profession (architect or engineer) check, the debris is stable enough that it retains its dome-like configuration when the spell ends, otherwise it collapses.
Normally this spell is used to buy time for dealing with avalanches, floods, and rockslides, though it is also handy in dealing with ambushes.}
        
\DeclareSpell{Signifer's Rally}{conjuration (teleportation) [evil]|V,  S,  M (100 gp worth of bloodstone for every ally teleported)|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone willing ally/5 levels|instantaneous|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Signifer's Rally}{You teleport up to one ally per five caster levels to your location.
You determine which allies you want to teleport at the time of casting; these allies have 1 round to decide to allow or refuse your spell, and they teleport immediately upon accepting. Allies are teleported as if you had cast teleport on them (your current location is at least "studied carefully" for this purpose), appearing in a puff of brimstone in a space adjacent to you. If you are in combat and your allies were not, your allies may roll initiative upon arrival but are not considered flat-footed even though they have not taken any actions. The spell does not function in areas warded against intrusion by evil creatures (such as a magic circle against evil effect).}
        
\DeclareSpell{Twine Double}{illusion (shadow) []|V,  S,  M (cloth and twine)|10 minutes|0 ft.|EffectOne duplicate creature|1 minute/level|None|No}[]
    \DeclareSpellDescription{Twine Double}{As simulacrum, except you can only duplicate yourself, and the duplicate is created from cloth and twine rather than ice and snow. The double looks exactly like you except its eyes are balls of twine (DC 10 Perception check to recognize double's strange eyes). It wears clothing and gear that appear exactly like what you are wearing at the time of casting. Its copies of your magic items are nonfunctional but radiate magic and have the same auras as your items. Its aura is identical to yours. Attempts to scry you while the double exists have a 50\% chance of targeting the double instead of you.
The double cannot attack, has no special abilities, and has a +0 bonus on all saves and checks. You may verbally give the double orders as a free action, or control it telepathically as a standard action. You know what the double is experiencing, and when controlling it telepathically you can see and hear everything it sees and hears, though events at your location may drown out the sensory inputs from the double. The double has hit points equal to half your hit points at the time of casting. If brought to 0 hit points, it is destroyed, reverting to cloth and twine. The double is an animated object.}
    