    
\DeclareSpell{Balance Of Suffering}{conjuration (healing) [death]|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone living creature and another single living or undead creature|instantaneous|Will half; see text|yes; see text}[]
    \DeclareSpellDescription{Balance Of Suffering}{You borrow life force from a living creature and infuse it into another living creature, potentially wreaking destruction on the former and bolstering the life of the latter.  Choose an initial target, which must be alive, and a secondary target, which must be alive or undead. The initial target is dealt a number of points of damage equal to 9d6 + 1 point per caster level. A successful Will saving throw halves the damage dealt. The target might die from damage even if it succeeds on its saving throw.  If the secondary target is a living creature, it regains a number of hit points equal to the amount of damage taken by the initial target. If the secondary target is undead, it instead takes an amount of damage equal to that dealt to the initial target. The secondary target can halve the healing imparted or harm inflicted to it with a successful Will saving throw (although a secondary target receiving healing can forgo this saving throw as normal).  This spell is subject to the spell resistance of the initial target; if the secondary target is unwilling, this spell is also subject to the secondary target's spell resistance. If the spell does not penetrate the initial target's spell resistance, it fizzles with no effect. If it does not penetrate the secondary target's spell resistance, the initial target is still harmed as described, but the secondary target is not healed or harmed.}
        
\DeclareSpell{Curative Distillation}{conjuration (healing) []|V,  S,  M (healing herb,  alchemical remedy,  or potion of a healing spell worth at least 50 gp)|1 standard action|touch|Targetsone living creature touched|instantaneous|Will half (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Curative Distillation}{You concentrate the healing potential of the material component so that it's exceptionally potent and restorative. This spell restores a number of hit points equal to 1d8 + 1 point per caster level (maximum +10) to the target, and also grants the target the benefits of the material component. Roll the hit points restored separately when determining how many total hit points this spell and the material component restore.}
        
\DeclareSpell{Healing Flames}{conjuration (healing) [fire,  good]|V,  S,  DF|1 standard action||Area10-ft.-radius burst, centered on you|instantaneous|Reflex half; see text|yes}[]
    \DeclareSpellDescription{Healing Flames}{You unleash a blast of holy flames that washes over all creatures in the area in a glorious display of divine power. This deals damage to evil creatures and heals good creatures in the area. The amount of damage dealt and the number of hit points restored in each case is 1d8 points per 2 caster levels (maximum 5d8).  Half of the damage this spell deals to evil creatures is fire damage, and half of the damage is pure divine power that is therefore not subject to reduction by energy resistance to fire-based attacks.  Neutral enemies within the spell's area of effect also take the fire damage, but do not take the divine damage. Neutral allies within the area are healed by half as much as good creatures. A successful Reflex saving throw halves the damage taken in all cases.}
        
\DeclareSpell{Healing Token}{conjuration (healing) []|V,  S,  DF|1 standard action|touch|Targetsone touched holy symbol per 3 caster levels|10 minutes/level|Will negates (object)|yes (object)}[]
    \DeclareSpellDescription{Healing Token}{You imbue one touched holy symbol per 3 caster levels with a connection to your own divine power, turning the touched holy symbols into tokens of healing. Each of the targeted holy symbols can represent any deity regardless of the deity's actual alignment.  As long as you wear or carry your divine focus, any creature carrying a token of healing can make a plea for healing in a language you understand as a standard action. When they do this, you are silently alerted to the plea for healing and can magically heal the target as an immediate action anytime before the end of your next turn.  The magical healing you use to do this can be either a supernatural ability that heals damage (if you have uses available) or a spell or spell-like ability that belongs to the healing subschool (if you can cast any). In either case, to use the ability or cast the spell through this spell, you must be able to include or target that creature, and the ability's activation time or spell's casting time must be no longer than one standard action.  If the ability or healing spell you use through a token would affect multiple creatures, such as mass cure light wounds, the ability or spell affects the creature that pleaded for healing as well as any other creatures within the healing spell's normal range that are also holding a holy symbol imbued with this spell.  So, for example, when you use mass cure light wounds through a holy symbol that has been turned into a token of healing, that spell would heal the creature holding the token that pleaded for healing as well as one creature per level that is also holding a token (no two of which can be more than 30 feet apart). However, the mass cure light wounds spell would heal only creatures within range that are holding tokens.}
        
\DeclareSpell{Inspiring Recovery}{conjuration (healing) [mind-affecting]|V,  S,  DF|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone target creature and all its allies within 60 feet; see text|instantaneous and 1 minute|Will half (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Inspiring Recovery}{You can heal a creature, harm an undead creature, or call upon a very recently dead creature to fight beyond death's reach. The target creature regains 1d8 hit points per 2 caster levels (maximum 10d8).  This healing can even bring back to life creatures that have been dead within the previous 1 round (but they cannot have been dead for any longer). If you apply this spell's healing to such a creature and its hit point total is at a negative amount less than its Constitution score, it comes back to life and stabilizes at its new hit point total. If you awaken a dead creature in this way, all allies of that creature within 60 feet who can see it regain consciousness gain a +2 morale bonus on attack rolls, damage rolls, and saving throws for 1 minute thereafter, as the healing powers of your deity have imbued them with renewed vigor.  Creatures killed by death effects cannot be revived this way. This spell deals damage to undead creatures rather than curing them, and it cannot bring them back to life.}
        
\DeclareSpell{Purify Body}{conjuration (healing) []|V,  S|1 standard action|touch|Targetsliving creature touched|instantaneous and 1 hour or until discharged|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Purify Body}{You align the target's chakras and soothe any unwanted imperfections found within its physical form, leaving its body pristine and without any pain or weakness.  You restore a number of hit points to the creature equal to 3d8 + 1 per caster level (maximum +20). If the healing would cause the target to exceed its maximum hit points, the target immediately gains half the excess healing from this spell as temporary hit points that last for 1 hour. These temporary hit points are lost first when the target takes damage (although some temporary hit points are lost even before these temporary hit points, such as the temporary hit points from the shell of succor oracle mystery, described on page 21, or the shell of succor hex granted by the restoration spirit specialization and described on page 27).  This spell also ends any painUM effects, removes all physical ability score damage (from Strength, Dexterity, and Constitution), and removes the following conditions: blinded, dazzled, deafened, nauseated, paralyzed, and sickened.}
        
\DeclareSpell{Befuddled Combatant}{enchantment (compulsion) [curse,  mind-affecting]|V,  S,  M (cooked noodles)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 hour/level|Will negates|yes}[]
    \DeclareSpellDescription{Befuddled Combatant}{As a way to befuddle your target, you fill its mind with all manner of swirling images as well as baffling and incoherent thoughts, making the target an ineffective combatant and rendering its spellcasting and other such abilities much more feeble.  For the spell's duration, the DCs of all of the target's spells, spell-like abilities, supernatural abilities, and extraordinary abilities are reduced by 4. Any of its attacks that would deal hit point damage, including its melee and ranged physical attacks, deal minimum damage for the duration of this spell.  This curse applies only to effects created by the creature while this spell is actively affecting the target; applying or removing this curse doesn't alter the ongoing damage of effects previously created by the target (such as an incendiary cloud spell that was cast before the target became affected by this spell).}
    