    
\DeclareSpell{Daywalker}{necromancy|V,  S,  M (a black glass vial containing unholy water)|1 standard action|touch|Targets: undead creature touched|24 hours (D)|none|yes (harmless)}[]
    \DeclareSpellDescription{Daywalker}{You reshape the substance of a willing undead creature to resemble a living, breathing creature of the same size. This is a physical change to the undead creature's bone, flesh, or incorporeal ectoplasm, adding new flesh or bone and even hair, teeth, and blood, all of which demonstrate false signs of life that mimic a living creature's breathing and other physiological processes. An incorporeal undead creature using daywalker ceases to be incorporeal for the duration of the spell, gaining a physical corpse body. Creatures interacting with the undead can attempt a Perception check (DC = 30 or DC = 21 + the undead's Disguise modifier, whichever is higher) to realize that the signs of life are false, and a close examination with a Heal check always reveals the truth of the dead flesh.  If the undead has the frightful presence, incorporeal, light blindness, light sensitivity, stench, sunlight powerlessness, or unnatural aura abilities, the spell suppresses them. An undead creature whose touch normally deals damage, ability drain, or energy drain doesn't do so while under the spell's effects. The target of this spell may end its duration at any time as a standard action.}
        
\DeclareSpell{Plant Voice}{transmutation|V,  S,  M (a small root cutting)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one plant creature|10 minutes/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Plant Voice}{You grant one plant creature the ability to speak, hear, and understand any of the languages you know. If you know more than one language, you may grant the plant creature up to one language per 2 caster levels and you decide which languages to grant when the spell is cast. This spell does not cause the plant creature to be predisposed toward you in any way, but allows you to interact with them with Charisma-based skills normally. Plant creatures with an Intelligence score of 2 or lower can communicate and understand only the simplest of concepts, such as "friend," "food," and "danger." This spell has no effect on ordinary plants and fungus.}
        
\DeclareSpell{Spore Burst}{conjuration [poisonUM]|V,  S,  M (a tiny puffball mushroom)|1 standard action|touch|Targets: one plant creature; see text|see text|special; see text|no}[]
    \DeclareSpellDescription{Spore Burst}{You cause a willing plant creature's body to sprout small, puffy mushrooms that remain for 1 round per caster level or until the creature uses them. As a standard action, the target can cause these mushrooms to burst open, releasing a cloud of toxic spores that affect all creatures in a 20-foot-radius spread. Those in the area must succeed at Fortitude saves or be sickened for 1d6 rounds as they are overcome by sneezing and coughing. The caster is immune to this poison effect, as are all creatures of the plant type.}
    