    
\DeclareSpell{Martyr's Last Blessing}{conjuration (healing)|V,  S,  DF|1 minute|personal (see text)|Targets: you and one ally/level, no two of which can be more than 30 ft. apart (see text)|1 hour/level or instantaneous (see text)|Will half (harmless, see text)|yes (harmless)}[]
    \DeclareSpellDescription{Martyr's Last Blessing}{You charge your body with healing energy, which erupts from you if you are dying or are killed before 1 hour per level has passed. If you're brought below 0 hit points or killed (including by effects that kill without dealing damage, such as phantasmal killer and power word kill), the eruption of healing energy acts as mass cure light wounds on allies (other than you). Allies with the fewest Hit Dice are affected first. Among allies with equal HD, those closest to you are affected first. If the duration ends, the stored healing energy dissipates with no effect.}
        
\DeclareSpell{Peasant Armaments}{transmutation|V,  S,  DF|1 standard action|touch|Targets: 1 improvised weapon/level|1 minute/level (D)|Will negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Peasant Armaments}{You transform one or more improvised weapons into equivalent simple or martial weapons. The bearer of such a weapon can wield it with proficiency (no penalty for using an improvised weapon or not having the required proficiency). This does not alter the weapon's shape or appearance in any way. For example, if cast on a chair leg, butter knife, and pitchfork, the weapons function as a club, dagger, and trident, respectively, and anyone who wields them does so without a nonproficiency penalty, but the weapons look no different than they were before the spell.  The spell has no effect on items that are not improvised weapons. For example, if cast on a short sword, it does not grant proficiency to anyone wielding it.}
    