    
\DeclareSpell{Conjure Deadfall}{conjuration (creation)|V,  S,  M (fistful of mithral tacks)|1 standard action|medium (100 ft. + 10 ft./level)|Area: see text|instantaneous|Reflex negates (see text)|yes}[]
    \DeclareSpellDescription{Conjure Deadfall}{You conjure a large metal cube covered in sharp spikes. If you conjure the block so that it appears in midair, it immediately plummets downward onto all creatures below it. When you cast this spell, you select the size of the square area you wish it to affect. If you choose to create a deadfall over a single 5-foot square, the block deals 1d6 points of bludgeoning damage per caster level (maximum 15d6) to each creature in the area. A deadfall over a 10-foot square deals 1d6 points of bludgeoning damage per 2 caster levels (maximum 7d6), a deadfall over a 15- foot square deals 1d6 points of bludgeoning damage per 3 caster levels (maximum 5d6), and so on, to a maximum size of a 25- foot square. Only creatures that are on the outer edge of the area affected by a conjure deadfall spell can attempt Reflex saves to avoid the effect; creatures whose space does not touch the edge of the deadfall do not receive a save.  In order to deal damage, the conjured deadfall must start at least 10 feet above the tallest creature in the area to be affected. A conjured deadfall is as tall as it is wide, and the spell fails if you attempt to conjure a deadfall in an area already occupied by a creature or object (including the ceiling). Regardless, a deadfall conjured by this spell disappears as soon as it deals damage or strikes the ground.}
        
\DeclareSpell{Create Holds}{transmutation|V,  S,  M (handful of pebbles)|1 standard action|medium (100 ft. + 10 ft./level)|Effect: path of handholds|1 hour/level (D)|none|no}[]
    \DeclareSpellDescription{Create Holds}{You create a path of handholds on earthen, plaster, stone, or wooden walls (not on walls made of metal or other, harder materials). The handholds are created in pairs and are approximately 3 feet apart, located in a specific path indicated by your gestures while casting the spell. The handholds' path can span up to 30 feet out from you plus an additional 10 feet per 3 caster levels (maximum 90 feet at 18th level). The handholds protrude approximately 6 inches from the wall, measure 10 inches lengthwise, and are perfectly suited for gripping with fingers or claws. At the end of the spell's duration, any creature being supported by the handholds immediately begins to fall.}
        
\DeclareSpell{Determine Depth}{divination|V,  S|1 standard action|touch|Targets: solid surface touched|concentration, up to 1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Determine Depth}{With a touch, you can determine the exact thickness of a wall, ceiling, or other solid barrier, measuring from the point you are touching to the direct opposite side of the barrier in a straight line. You can only detect depths or widths of up to 10 feet per caster level (maximum 200 feet at 20th level); amounts in excess of this limit are detected as being the maximum you are able to detect. So, for example, a 5th-level wizard using this spell on a 60-foot-thick wall would detect that the wall is 50 feet thick.  Determine depth can be used on earthen, plaster, stone, or wooden surfaces, but not on walls made of metal or other, harder materials. This spell is useful to casters who want to get an idea of their surroundings, and as a preliminary measure to casting spells such as passwall or dimension door.}
        
\DeclareSpell{Discern Value}{divination|V,  S,  F (platinum monocle worth 100 gp)|1 standard action|60 ft.|Area: cone-shaped emanation|concentration, up to 1 minute/level (D)|none|no}[]
    \DeclareSpellDescription{Discern Value}{You can quickly analyze the monetary value of objects and identify which are most valuable to an average trader. You must specify a minimum value to detect when you cast this spell (such as 1 gp, 100 gp, or 1,000 gp). The amount of information revealed depends on how long you study a particular area or subject.  1st Round: Presence or absence of objects worth at least the specified amount.  2nd Round: The most valuable object in range glows brighter than all of the others. If an aura is outside your line of sight, then you discern its direction but not its exact location.  3rd Round: Objects whose values are within 10\% of the most valuable item in range glow slightly.  The spell's effect does not indicate whether an item has magical properties and does not detect artifacts or items that are priceless.}
        
\DeclareSpell{Nature's Ravages}{necromancy|V,  S,  M/DF (dried maggots)|1 minute/HD of target|close (25 ft. + 5 ft./level)|Targets: corpse of creature whose total number of HD does not exceed your caster level|instantaneous|none|no}[]
    \DeclareSpellDescription{Nature's Ravages}{You greatly speed up the decomposition process of a nearby corpse and warp the fibers of time that permeate it, aging the corpse an additional amount of time equal to up to 1 day per 2 caster levels (maximum 10 days at 20th level). This spell prompts all the natural effects of the intended decomposition period, including crumbled clothing, rotted or liquefied flesh, maggot infestations, and the infiltration of any surrounding vegetation.  In addition to hindering mundane autopsies and investigations, this spell may effectively prohibit the use of raise dead on the target, though more powerful magic such as resurrection or true resurrection may still work.}
        
\DeclareSpell{Greater Nature's Ravages}{necromancy|V,  S,  M/DF (dried maggots)|10 minute/HD of target|close (25 ft. + 5 ft./level)|Targets: corpse of creature whose total number of HD does not exceed your caster level|instantaneous|none|no}[]
    \DeclareSpellDescription{Greater Nature's Ravages}{This spell functions like nature's ravages, except the target corpse ages a number of years equal to up to 1 year per caster level (maximum 20 years at 20th level).}
    