    
\DeclareSpell{Burdened Thoughts}{enchantment (compulsion) [mind-affecting]|V,  S,  M (a lead bearing wrapped in clay)|1 standard action|medium (100 ft. + 10 ft./level)|Targets: one creature|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Burdened Thoughts}{You fill a creature's mind with the realization of its earthly weight and responsibilities. Disheartened and wearied by these thoughts, the creature gains heavy encumbrance and is unable to fly (if already flying, it must land as soon as possible). If the creature is three or more size categories larger than you, it's also staggered.}
        
\DeclareSpell{Hollow Blades}{transmutation|V,  S|1 round|medium (100 ft. + 10 ft./level)|Targets: one creature|1 round/level|Fortitude negates|yes}[]
    \DeclareSpellDescription{Hollow Blades}{All melee and natural attacks from the target deal damage as if the target were one size category smaller than it actually is. While the target is under the effects of this spell, weapons dropped by the target function normally for other creatures, while any melee weapons picked up by the target deal damage as if one size smaller. Ranged attacks and weapons are unaffected by this spell.}
        
\DeclareSpell{Runic Overload}{evocation [sonic]|V,  S,  M (a small rune carved from stone)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature or object|instantaneous|see text|see text}[]
    \DeclareSpellDescription{Runic Overload}{This spell charges magical runes to an explosive degree. If cast on a creature with magical runes on its body, such as a rune giant or a runescarred creature (Pathfinder Campaign Setting: Lost Cities of Golarion 60), it deals 1d6 points of sonic damage per caster level (maximum 20d6) to the target and stuns the target for 1 round. When the spell is cast in this way, it must overcome the target's spell resistance. A successful Will save halves the damage and negates the stun effect.  The spell can also be cast on other magical runes, such as those from arcane mark or explosive runes. In this case, the resulting explosion deals 1d8 points of sonic damage per  2 caster levels (maximum 10d8) to all creatures within a 5-foot radius. Creatures in the area that succeed at a Reflex save take half damage. This spell doesn't destroy runes; targeted runes continue to function normally. Mundane runes, such as ones in writing or runic tattoos, cannot be affected by this spell.}
        
\DeclareSpell{Siphon Might}{necromancy|V,  S|1 round|close (25 ft. + 5 ft./2 levels)|Targets: one creature|1 round/level|Fortitude half|yes}[]
    \DeclareSpellDescription{Siphon Might}{You drain the might of the target and transfer that power to another creature. The subject takes a penalty to Strength equal to 1d6 + 1 per 2 caster levels (maximum 1d6 + 5). This effect can't cause the subject's Strength score to drop below 1. A successful Fortitude save halves this penalty. This penalty doesn't stack with itself or the penalty applied from ray of enfeeblement.  You can grant any one creature adjacent to you (including yourself) an enhancement bonus to Strength equal to the Strength penalty imposed by this spell.}
        
\DeclareSpell{Stone Throwing}{transmutation|V,  S,  M (powdered stone)|1 standard action||Targets: creature touched|1 minute/level|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Stone Throwing}{The subject gains the rock throwing and rock catching abilities (Pathfinder RPG Bestiary 303). It can use these abilities with any solid, mostly inflexible object with a hardness of at least 5.  The subject can hurl rocks up to two categories smaller than its own size. The range increment for this attack is 20 feet, and rocks can be hurled a maximum of 5 range increments. Damage is based on the size of the subject-1d8 points of damage for a Large creature, 1d6 for a Medium creature, or 1d4 for a Small creature-plus 1-1/2 times the thrower's Strength bonus.  For every size category smaller than Large the subject is, it receives a cumulative -5 penalty on Reflex saves to catch rocks (or similar projectiles) thrown at it.}
        
\DeclareSpell{Steal Size}{transmutation|V,  S,  M (a piece of iron shaped like a scale tray)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one humanoid creature larger than you|1 minute/level (D)|Fortitude negates|yes}[]
    \DeclareSpellDescription{Steal Size}{This spell reduces the target's size by one size category, as if it were affected by reduce person. You grow in size by one category, as if affected by enlarge person ( if y ou c an b e targeted by that spell). If the spell is dispelled or otherwise ends for either you or the target, both you and the target return to your normal sizes.}
        
\DeclareSpell{Twisted Futures}{divination|V,  S,  M (a small die with the faces scratched off)|1 standard action|close (25 ft. + 5ft./2 levels)|Targets: one creature/level, no two of which can be more than 30 ft. apart|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Twisted Futures}{By rearranging the threads of fate, you disrupt fortunate outcomes for other creatures. A creature affected by this spell is unable to benefit from effects that grant the ability to roll multiple times and take the higher result (like the swashbuckler's charmed life ability) or to choose the die result in lieu of rolling (like the wizard's prescience school power or the cyclops's flash of insight ability). This doesn't affect abilities that force a creature to take the lower of two rolls, such as ill omen or a pugwampi's unluck aura (Pathfinder RPG Bestiary 2 144). A cyclops can't use its flash of insight ability to save against this spell.}
    