    
\DeclareSpell{Storm Of Blades}{conjuration (creation) []|V,  S,  M (a sword)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|instantaneous|none|no}[]
    \DeclareSpellDescription{Storm Of Blades}{You create floating swords of the type used as the material component for this spell (such as a rapier or scimitar) and magically propel them at your target. You can create one sword for every 2 caster levels that you possess, up to a maximum of five swords at 10th level. You must have line of effect between you and the target, and the target must be within the spell's range. You make a ranged attack roll for each sword (with no penalties for range increments or using melee weapons as ranged weapons); each attack has the same threat range and critical modifier and deals the same damage as a standard sword of the type expended. Swords created by this spell disappear after striking (or missing) their targets.}
        
\DeclareSpell{Summon Genie, Lesser}{conjuration (summoning) []|V,  S,  F/DF (an oil lamp worth at least 50 gp)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone summoned genie|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Genie, Lesser}{This spell functions like summon monster I, except you can summon one janni.}
        
\DeclareSpell{Summon Genie}{conjuration (summoning) []|V,  S,  F/DF (an oil lamp worth at least 50 gp)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone summoned genie|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Genie}{This spell functions like lesser summon genie, except you can summon one djinni or 1d3 jann.}
        
\DeclareSpell{Summon Genie, Greater}{conjuration (summoning) []|V,  S,  F/DF (an oil lamp worth at least 50 gp)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone summoned genie|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Genie, Greater}{This spell functions like lesser summon genie, except you can summon one shaitan, 1d3 djinn, or 1d4+1 jann.}
        
\DeclareSpell{Inner Focus}{illusion (glamer) []|V,  S,  DF|1 standard action|personal|Targetsyou|10 minutes/level|none (harmless)|no}[]
    \DeclareSpellDescription{Inner Focus}{For the duration of this spell, you may ignore any divine focus components of your spells, allowing you to cast such spells without holding or revealing your holy or unholy symbol.}
    