    
\DeclareSpell{Planar Aegis}{abjuration () []|V,  S, M|1 standard action|personal|Targetsyou|1 round/level (D)||}[]
    \DeclareSpellDescription{Planar Aegis}{You draw motes of essence from material native to a plane that has elemental or energy essence traits (Pathfinder RPG Planar Adventures 60), weaving the essence together into a shield of force. Choose an essence trait from the list below; the material component for this spell must come from a plane that has the essence trait you chose. Each essence trait has an associated damage type (see the table below). Any creature that hits you with a non-reach melee weapon, natural weapon, or unarmed attack takes 3d6 points of damage plus 1 point per caster level you have (maximum +20) of a type corresponding to the essence trait you chose. In addition, you take only half damage from attacks or effects of the associated damage type, and if such an attack or effect allows a saving throw for half damage, you take no damage on a successful saving throw.  Essence Trait Damage Type  Air-Dominant Electricity  Earth-Dominant Acid  Fire-Dominant Fire  Positive-Dominant Positive  Negative-Dominant Negative  Water-Dominant Cold}
        
\DeclareSpell{Speak With Plane}{divination () []|V,  S,  F/DF (a small glass bead)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone plane with a sentient structure|1 minute/level|Will negates (see text)|yes}[]
    \DeclareSpellDescription{Speak With Plane}{You tap into the awareness and consciousness of a plane with a sentient structure (Planar Adventures 60), allowing it to answer questions. A tangible manifestation of the plane (such as the ground) must be within the spell's range upon casting.  You can ask the sentient plane one question per 2 caster levels. If the plane's alignment is at least one step away from yours, the plane can attempt a Will save to resist the spell. A plane typically has a +20 bonus on Will saves, and a demiplane typically has a +15 bonus on Will saves. A plane's traits can further affect these bonuses: a mildly aligned plane receives a +2 bonus, and a strongly aligned plane or a plane with the wild magic trait receives a +4 bonus on its save.  If a plane has been subject to this spell within the past week, a new casting of this spell targeting the same plane fails. If speak with plane targets a plane that does not have a sentient structure, the spell fails.}
        
\DeclareSpell{Talisman Of Reprieve}{abjuration () []|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets20-ft.-radius emanation centered on an item|10 minutes/level||}[]
    \DeclareSpellDescription{Talisman Of Reprieve}{You imbue an item with an aura of divine amnesty, allowing all allies within the aura's area to ignore penalties to Intelligence-, Wisdom-, and Charisma-based checks resulting from a plane's mildly or strongly aligned traits (Planar Adventures 62), regardless of the allies' alignments. In addition, the item grants a +4 circumstance bonus on checks with one Intelligence-, Wisdom-, or Charisma-based skill determined by you at the time of casting.}
        
\DeclareSpell{Celestial Companion}{transmutation () []|V,  S,  DF/M|1 standard action|touch|Targetsanimal companion, eidolon, familiar, or mount|1 minute/level (D)|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Celestial Companion}{You bestow divine protection on your companion. The target gains spell resistance equal to 5 plus half your caster level against spells and spell-like effects produced by evil creatures. The target also gains a +1 sacred bonus on saving throws and DR 5/evil or silver. Creatures under the effects of this spell often take on a celestial appearance, such as golden feathers or a radiant aura, but they are not truly celestial creatures.}
        
\DeclareSpell{Righteous Condemnation}{abjuration () [good,  law]|V,  S,  DF|1 standard action|personal|Targetsyou|1 round/per level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Righteous Condemnation}{Any creature of chaotic, neutral, or evil alignment who targets you with a spell must succeed at a Will save or take a -4 penalty on Intelligence-, Wisdom-, and Charisma-based checks for the spell's duration. Creatures with only neutral alignment components receive a +4 bonus on their Will saves against this spell. The penalties for alignment components stack (therefore, a chaotic evil spellcaster would take a -8 penalty).}
        
\DeclareSpell{Fiendish Wrath}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone willing living creature per 3 levels, no two of which can be more than 30 ft. apart|concentration + 1 round/level (D)|none|yes}[]
    \DeclareSpellDescription{Fiendish Wrath}{Each affected creature flies into a combat frenzy. The target gains a +2 morale bonus to Strength and Constitution, and a +1 morale bonus on Will saves. If an affected creature strikes an enemy with two claw attacks or two unarmed strikes while in this frenzy, it can use the rend ability, dealing an additional amount of damage equal to its claw or unarmed strike damage plus 1-1/2 times its Strength bonus.}
        
\DeclareSpell{Healing Leak}{necromancy () []|V,  S,  M/DF (a piece of muslin)|1 standard action|touch|Targetscreature touched|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Healing Leak}{Whenever the target is affected by a spell or effect that heals hit point damage through the use of positive or negative energy, it regains only half the number of hit points it normally would recover. If the target employs a spell or effect that heals itself or other creatures through the use of positive or negative energy, the target must succeed at a concentration check (DC = this spell's save DC) or the effect restores only half of the normal number of hit points. Other forms of healing (such as from the Heal skill) are not affected by this spell.}
        
\DeclareSpell{Greater Reversion}{conjuration (healing) []|V,  S|20 minutes|personal|Targetsself|24 hours||}[]
    \DeclareSpellDescription{Greater Reversion}{You create a fine-tuned replica of yourself within the Akashic Record at the time the spell is cast. You must currently have a number of hit points equal to or greater than half your maximum hit points to cast the spell. If at any time during the duration of the spell you are brought below half your maximum hit points, you can end this spell as an immediate action to absorb strength from your replica and immediately regain a number of hit points equal to 3d8 plus 1 point per caster level (maximum +15).}
        
\DeclareSpell{Minor Reversion}{conjuration (healing) []|V,  S|10 minutes|personal|Targetsself|24 hours||}[]
    \DeclareSpellDescription{Minor Reversion}{You create an imperfect replica of yourself within the Akashic Record at the time the spell is cast. You must currently have a number of hit points equal to or greater than half your maximum hit points to cast the spell. If at any time during the duration of the spell you are brought below half your maximum hit points, you can end this spell as an immediate action to absorb strength from your replica and immediately regain a number of hit points equal to 1d8 plus 1 point per caster level (maximum +5).}
        
\DeclareSpell{Minor Reversion, Mass}{conjuration (healing) []|V,  S|30 minutes|close (25 ft. + 5 ft./2 levels)|Targetsone creature/level, no two of which can be more than 30 ft. apart|24 hours||}[]
    \DeclareSpellDescription{Minor Reversion, Mass}{You create a replica within the Akashic Record of each target at the time the spell is cast. Each targeted creature must currently have at least half its hit points. If at any time during the duration of the spell a target is brought below half her maximum hit points, that target can end the spell on herself as an immediate action to absorb strength from her replica and immediately regain a number of hit points equal to 1d8 plus 1 point per caster level (maximum +25).}
        
\DeclareSpell{Eroding Ray}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectray|instantaneous|none|no}[]
    \DeclareSpellDescription{Eroding Ray}{You channel a fraction of the tumultuous ecosystem of the Hao Jin Tapestry and redirect it through your hands as a beam of deteriorating energy. You can fire one ray, plus one additional ray for every 4 levels beyond 3rd (to a maximum of three rays at 11th level). Each ray requires a ranged touch attack to hit and can target only a construct or an object. If a ray hits, the target begins to crumble, taking 2d6 points of damage. This damage ignores hardness and damage reduction.}
    