    
\DeclareSpell{Borrowed Time}{transmutation|V,  S|1 standard action|personal|Targets: you|1 round/level (D)||}[]
    \DeclareSpellDescription{Borrowed Time}{A creation of the archmage Nex, this spell allows you to reach ahead in time and draw alacrity from the future at the expense of your own health. For the duration of this spell, you gain an extra swift action you can use only during your turn. You can't use this swift action to take a second immediate action between turns, but you can use it to take a swift action the turn after you've taken an immediate action. Each time you take an extra swift action in this fashion you take 1 point of Constitution damage. If you're immune to ability damage, you take 5 points of hit point damage instead.

When the spell ends, you are staggered for 1d4+1 rounds from the temporal backlash.}
        
\DeclareSpell{Elemental Bombardment}{conjuration (summoning) [see text]|V,  S|1 round|long (400 ft. + 100 ft./level)|Effect: one or more summoned elementals|1 round/2 levels (D)|none|no}[]
    \DeclareSpellDescription{Elemental Bombardment}{You summon elementals from their elemental planes and hurl them onto your enemies with great force. You must have line of effect to a point at least 60 feet above your intended targets and within the spell's range. You can summon one greater elemental, two Huge elementals, four Large elementals, or eight Medium elementals. You aim the elementals at targets within 60 feet of each other, no more than one elemental per target.

Each elemental can strike only a single target, regardless of its size. When an elemental strikes a target, it makes a single slam attack at its full attack bonus with a +4 circumstance bonus. The elemental deals damage according to the table below. The type and amount of damage dealt varies by the size and type of elemental (see the table). Some elementals inflict an additional special ability upon successfully hitting a target; these additional special abilities are detailed in the elemental's full stat block and are denoted with an asterisk (*). Whether or not it hits, the elemental takes bludgeoning damage according to its size. A summoned elemental acts on the same turn that it lands, starting prone in the nearest available space adjacent to its target.

You must select one type of elemental to summon when casting this spell (see the table).

When you use a summoning spell to summon a creature with an elemental subtype, it is a spell of that type.}
        
\DeclareSpell{Imbue With Flight}{transmutation|V,  M (handful of down)|1 standard action|touch|Targets: object touched|1 hour/level (D)|Will negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Imbue With Flight}{You grant a touched Large or smaller object the ability to fly at a speed of 40 feet with average maneuverability. It can ascend at half speed and descend at double speed. The targeted object flies as you direct it, using your Fly skill for any difficult maneuvers. You must be within close range (25 ft. + 5 ft./2 levels) of the object to direct it, and moving it requires a move action. If not directed, the object hovers in place (no Fly check required). The maximum weight of the object and anything carried by it is 500 pounds per caster level (maximum 10,000 pounds).}
        
\DeclareSpell{Soulreaver}{necromancy [death]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: living creatures in a 20-ft.-radius spread|instantaneous|Fortitude half|yes}[]
    \DeclareSpellDescription{Soulreaver}{Favored by the necromancer Geb as a tool to turn his enemies' armies against themselves, this potent death spell deals 1d6 points of damage per caster level (maximum 20d6) to living creatures in the area of effect.}
        
\DeclareSpell{Sustaining Legend}{conjuration (healing)|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature/level, no two of which can be more than 30 ft. apart|1 round/level|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Sustaining Legend}{The rulers of Azlant are thought to have used this spell to amplify the mythic power of themselves and their most gifted lieutenants. You amplify the mythic power of the target creatures, bolstering them with healing energy each time they draw upon their mythic abilities. When a creature affected by this spell expends uses of mythic power for any ability, it immediately heals 2d8 points of damage + 1 point per caster level (maximum +25). In addition, the creature benefits from one of the following additional effects.

 Remove any one of the following conditions: dazzled, fatigued, shaken, sickened, or staggered.

 Reduce the dazed or stunned condition to staggered.

 Reduce the exhausted condition to fatigued.

 Reduce the frightened condition to shaken, or the panicked condition to frightened.

 Reduce the nauseated condition to sickened.

A target can benefit from the effects of sustaining legend only once per round, even if the target expends multiple uses of mythic power during that time.}
    