    
\DeclareSpell{Shared Suffering}{necromancy () [evil]|V,  F (a silver dagger inlaid with onyx and jade worth 100 gp)|1 standard action|long (400 ft. + 40 ft./level)|Targetsone living creature|instantaneous|none|yes}[]
    \DeclareSpellDescription{Shared Suffering}{You infuse a dagger with necromantic energy, then plunge the dagger into your own body. You take 1d6 points of negative energy damage plus 1d6 points of damage for every 2 caster levels you possess beyond 1st (to a maximum of 5d6 at 9th level). The target takes an amount of damage equal to the damage you took this way, plus an amount equal to your Intelligence modifier (if you're a witch or wizard), Wisdom modifier (if you're an inquisitor), or Charisma modifier (if you're an antipaladin or sorcerer).  Damage from this spell cannot be divided by effects such as shield other or unwilling shieldAPG; it cuts through such protections completely.}
        
\DeclareSpell{Wracking Ray}{necromancy () [evil,  pain]|V,  M (an old bone,  broken in the casting)|1 standard action|medium (100 ft. + 10 ft./level)|Effectray|instantaneous|Fortitude half|yes}[]
    \DeclareSpellDescription{Wracking Ray}{A ray of sickly greenish-gray negative energy issues forth from the palm of your hand. Make a ranged touch attack against the target. A creature hit by this spell is wracked by painful spasms as its muscles and sinews wither and twist. The subject takes 1d4 points of Dexterity and Strength damage per 3 caster levels you possess (maximum 5d4 each). This spell cannot reduce an ability score below 1. A successful Fortitude save halves the damage.}
    