    
\DeclareSpell{Daemon Ward}{necromancy () []|V,  S,  M (50 gp worth of powdered silver)|1 standard action|touch|Targetsliving creature touched|1 min./level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Daemon Ward}{This spell functions like death ward, except as noted above and it only protects against these attacks from daemons.}
        
\DeclareSpell{Death Knell Aura}{necromancy () [death,  evil]|V,  S|1 standard action|20 ft.|Area20-ft.-radius emanation, centered on you|1 round/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Death Knell Aura}{You gain a shimmering gray aura that feeds on the souls of creatures who die within it. The aura sheds light as a candle. If a creature at -1 or fewer hit points is within the aura at the start of its turn, it must save or die, granting you the benefits of death knell.}
        
\DeclareSpell{Death Knell Aura, Greater}{necromancy () [death,  evil]|V,  S|1 standard action|20 ft.|Area20-ft.-radius emanation, centered on you|1 round/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Death Knell Aura, Greater}{This spell functions as death knell aura, except a dying creature in the area cannot stabilize on its own and automatically takes 1 point of bleed damage on its turn each round. An incorporeal undead or living spirit traveling outside the body (such as a person using astral projection or magic jar) within the aura at the start of its turn takes 1d8 points of damage.}
        
\DeclareSpell{Scourge of the Horsemen}{necromancy () [acid,  evil]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Area30-ft. burst|instantaneous|Fortitude half|yes}[]
    \DeclareSpellDescription{Scourge of the Horsemen}{This spell blasts the area with a horrific combination of soul-rending energy and physical corrosion. Creatures in the area of effect gain 1d4 negative levels, and take 1d6 points of acid damage per caster level (maximum 20d6).}
        
\DeclareSpell{Summon Cacodaemon}{conjuration (summoning) [evil]|V,  S,  F (a silver hook)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone summoned creature|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Cacodaemon}{This spell functions like summon monster, except it summons a single cacodaemon.}
        
\DeclareSpell{Summon Cacodaemon, Greater}{conjuration (summoning) [evil]|V,  S,  F (a silver hook)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone summoned creature|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Cacodaemon, Greater}{This spell functions like summon cacodaemon, except it summons 1d4+1 cacodaemons.}
        
\DeclareSpell{Summon Ceustodaemon}{conjuration (summoning) [evil]|V,  S,  F (ashes of a dead animal)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone summoned creature|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Ceustodaemon}{This spell functions like summon monster, except it summons a single ceustodaemon.}
        
\DeclareSpell{Summon Derghodaemon}{conjuration (summoning) [evil]|V,  S,  F (a handful of bug carapaces)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone summoned creature|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Derghodaemon}{This spell functions like summon monster, except it summons a single derghodaemon.}
        
\DeclareSpell{Summon Erodaemon}{conjuration (summoning) [evil]|V,  S,  F (a bent or tarnished wedding band)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone summoned creature|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Erodaemon}{This spell functions like summon monster, except it summons a single erodaemon.}
        
\DeclareSpell{Summon Meladaemon}{conjuration (summoning) [evil]|V,  S,  F (an empty wooden bowl)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone summoned creature|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Meladaemon}{This spell functions like summon monster, except it summons a single meladaemon.}
        
\DeclareSpell{Summon Thanadaemon}{conjuration (summoning) [evil]|V,  S,  F (two silver coins)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone summoned creature|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Summon Thanadaemon}{This spell functions like summon monster, except it summons a single thanadaemon. You can only use this spell in an area with enough open water to accommodate the daemon's skiff, or when on the Astral Plane or Ethereal Plane.}
    