    
\DeclareSpell{Book Ward}{abjuration|V,  S,  M/DF (a drop of clear oil)|1 standard action|touch|Targets: one touched object of up to 10 pounds/level|1 day/level or until discharged (see text)|Will negates (harmless, object)|Yes (harmless, object)}[]
    \DeclareSpellDescription{Book Ward}{As protection from energy, except as noted above and that the spell only protects against acid and fire damage. While the energy protection remains, the item is also completely waterproof (this protection extends to other liquids as well, such as alcohol and oil).}
        
\DeclareSpell{Questing Stone}{divination|V,  S,  F|10 minutes|touch and unlimited|Targets: one ioun stone touched|1 minute/level (D)|none|no}[]
    \DeclareSpellDescription{Questing Stone}{This spell functions like arcane eye, except that it uses an ioun stone as a visible scrying sensor. The ioun stone moves at the same rate as an arcane eye, and may pass through holes or spaces as small as 2 inches in diameter. It can enter another plane of existence using a gate or similar portal, but the caster loses contact with the sensor should this occur. The enhanced ioun stone has AC 24, 10 hp, hardness 5, fly speed 30 (perfect), and a +16 Stealth bonus. The stone does not provide you with its normal benefits while you are using it as a scrying sensor.\\\\

{\centering\bf Arcane Eye\hrule}

You create an invisible magical sensor that sends you visual information. You can create the arcane eye at any point you can see, but it can then travel outside your line of sight without hindrance. An arcane eye travels at 30 feet per round (300 feet per minute) if viewing an area ahead as a human would (primarily looking at the floor) or 10 feet per round (100 feet per minute) if examining the ceiling and walls as well as the floor ahead. It sees exactly as you would see if you were there.

The eye can travel in any direction as long as the spell lasts. Solid barriers block its passage, but it can pass through a hole or space as small as 1 inch in diameter. The eye can't enter another plane of existence, even through a gate or similar magical portal.

You must concentrate to use an arcane eye. If you do not concentrate, the eye is inert until you again concentrate.}
        
\DeclareSpell{Revelation}{divination|V,  S|1 round|personal|Targets: you|1 round/level; see text||}[]
    \DeclareSpellDescription{Revelation}{You gain a brief understanding of the workings of a single puzzle, device, or trap, gaining an insight bonus equal to your caster level (maximum +10) on checks to disable, manipulate or solve the object in question. Your insight is ineffable; you are unable to communicate your understanding to others.

At the GM's option, this spell may instead give you a clue or other piece of useful information. In this case you may communicate the clue to others and retain knowledge of it after the spell's duration has expired.}
        
\DeclareSpell{Scrivener's Chant}{transmutation|V,  S,  M (fine sand and a vial of ink)|1 standard action|5 ft.|Targets: one or more written objects|concentration, up to 1 minute/level|Will (harmless, object)|yes (object)}[]
    \DeclareSpellDescription{Scrivener's Chant}{This spell imbues a quill with animate energy and rapidly transcribes words from one page to another. The quill copies a written work at the rate of one normal-sized page per minute.

The Linguistics skill can be used to make a convincing copy, but otherwise the reproduction is written in the hand of the caster.

You must concentrate upon the material being duplicated for the spell's duration and provide new blank pages as required.

The scrivener's chant requires blank paper and a quill or other writing materials, in addition to the material components.

This spell cannot duplicate magical writing (including spells and magical scrolls), though it can duplicate non-magical writing from a magical source.}
    