    
\DeclareSpell{Barghest Feast}{transmutation [evil]|S|1 standard action|touch|Targets: creature touched|10 minutes/level; see text|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Barghest Feast}{The target gains the ability to absorb power from devouring a humanoid corpse. To use this ability, the target must feed on the corpse of one nonevil humanoid creature, a process that takes 1 full round per Hit Die the creature had and provokes attacks of opportunity. For every 2 rounds it feeds on the corpse in this way, the target gains a +1 profane bonus on attack rolls, saving throws, and skill checks (to a maximum of +5).}
        
\DeclareSpell{Hobbling Bomb Admixture}{transmutation|V,  S|1 standard action|personal|Targets: you|1 round/level||}[]
    \DeclareSpellDescription{Hobbling Bomb Admixture}{Upon drinking an extract created with this formula, you make a significant change to your magical reserve that modifies the nature of all bombs you create and throw during this extract's duration. This effect on your magical reserve has no effect on any discoveries that you use to modify your bombs, but you can have only one admixture effect (formula with the words "bomb admixture" in its title) active at  a time. If you drink another bomb admixture, the effects of the former bomb admixture end and the new one becomes active.  When you throw a bomb and hit a target directly, it affects up to three targets-the creature the bomb hit directly, and up to two other creatures that take damage from the splash damage (alchemist's choice). Each targeted creature must succeed at a Fortitude saving throw or have its speed reduced by 20 feet (minimum 0 feet).}
    