    
\DeclareSpell{Die For Your Master}{enchantment (compulsion) []|V,  S|1 immediate action|touch|Targetsyour animal companion, familiar, or fiendish servant|instantaneous|none|no}[]
    \DeclareSpellDescription{Die For Your Master}{This spell functions as bleed for your master, but it allows your companion or familiar to intercept any attack that targets you, including those that do not require attack rolls (e.g., chain lightning, hold monster, and magic missile). Your companion or familiar cannot intercept effects that do not affect creatures of its type (e.g., dominate person).}
        
\DeclareSpell{Familiar Figment}{illusion (figment) []|V,  S|1 standard action|touch|Targetsyour familiar|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Familiar Figment}{You create an illusory duplicate of your familiar that moves erratically around your familiar's space, frequently moving through the familiar's body with a blurring effect that makes it indistinguishable from the real creature. Attacks against the familiar have a 50\% miss chance; attacks that miss instead target the familiar figment, which reacts as if damaged as appropriate to the attack but unlike a mirror image is not destroyed when struck. This spell does not grant your familiar concealment or prevent it from being targeted by spell effects that do not require an attack roll.  In addition, as a swift action, your familiar can direct the familiar figment to attempt a melee touch attack, using your base attack bonus and the familiar's Dexterity modifier. If this attack hits, your familiar (but not other creatures) treats that target as flanked until the end of its turn.}
        
\DeclareSpell{Hunter's Friend}{transmutation () []|V,  S,  DF|1 standard action|touch|Targetsyour animal companion|1 hour/level (D)|Will negates (harmless)|no}[]
    \DeclareSpellDescription{Hunter's Friend}{Your animal companion works in perfect harmony with your mastery of nature. You share one of the following class abilities with your companion for every 4 caster levels you possess: camouflage, favored enemy, favored terrain, hide in plain sight, resist nature's lure, swift tracker, trackless step, venom immunity, and woodland stride. You must have the ability in question to share it with your companion, and it functions for your companion just as it functions for you, save that each favored enemy or favored terrain you share counts as a separate class ability for the purpose of this spell.  At the GM's discretion, you may instead share an ability granted by an archetype that substitutes for one of the above abilities, such as the arctic endurance, arctic native, icewalking, and snowcaster abilities of an arctic druidAPG.}
    