    
\DeclareSpell{Acid Maw}{transmutation [acid]|V,  S,  DF|1 standard action|close (25 ft. + 2 ft./level)|Targets: your animal companion|1 minute/level|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Acid Maw}{Your animal companion's bite attack deals an additional 1d4 points of acid damage, and the acid deals another 1d4 points of acid damage to the target on the next round. The acid continues to deal damage for 1 additional round per 4 caster levels (to a maximum of 6 total rounds at caster level 20th). This ongoing acid damage doesn't stack from multiple attacks, but the duration resets if a newer bite would cause the ongoing damage to last longer than the duration remaining from a previous one. The acid does not harm the animal companion.}
        
\DeclareSpell{Arcane Disruption}{enchantment (compulsion) [curse,  mind-affecting]|V,  S,  M (a pinch of pepper)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Arcane Disruption}{This spell makes it difficult for the subject to cast arcane spells, use spell-like abilities, and use some abilities granted by arcane spellcasting classes. The subject must succeed at a concentration check (DC = 10 + 1/2 its caster level) in order to cast an arcane spell, use any spell-like ability (even those that come from a divine source), use arcane spell completion or spell trigger magic items, or use any of the following class features that come from an arcane spellcasting class: arcane school powers, arcanist exploits, bardic performances, magus arcana, or witch hexes. Spells, spell-like abilities, or class features that take a free, swift, or immediate action aren't affected by this spell, nor are mythic spells or mythic powers.  While under the effect of this spell, if the subject must attempt a concentration check to cast an arcane spell or use an arcane spell-like ability for any reason other than the effect of this spell (such as casting defensively, being injured while casting, and so on), it takes a penalty on that check equal to 1/2 its caster level.}
        
\DeclareSpell{Blood Salvation}{abjuration|V,  S|1 standard action|personal|Targets: you|1 round/level (D; see below)||}[]
    \DeclareSpellDescription{Blood Salvation}{While under the effect of this spell, you're immune to any damaging area spells you cast. You can dismiss this spell as an immediate action when you are caught within the area of someone else's damaging area spell; if you do, you're immune to that particular casting of that spell as well. If you have the blood casting class feature, you can cast this spell as a swift action instead of a standard action while you're in a bloodrage.}
        
\DeclareSpell{Energy Hack}{transmutation [acid,  cold,  electricity,  or fire; see below]|V|1 immediate action|personal|Targets: you|1 round/level (see below)||}[]
    \DeclareSpellDescription{Energy Hack}{You can cast this spell only when you take 10 or more points of acid, cold, electricity, or fire damage from a spell or spell-like ability-this spell has the same energy descriptors as the damaging effect. When you use a spell or spell-like ability with the acid, cold, electricity, or fire descriptor or use an arcanist exploit, arcane school power, bloodline power, magus arcana, or hex that deals acid, cold, electricity, or fire damage, you can choose to change the energy type and descriptor to match one of the descriptors of energy hack. Any other effect of that spell or power remains the same.  If you have the arcane reservoir class feature, if you take another 10 points of acid, cold, electricity, or fire damage while under the effect of energy hack, as a free action you can expend 1 point from your arcane reservoir to reset the duration of energy hack to 1 round per level and add the new type of damage you took to the list of energy types you can choose to substitute. You can expend points in this way multiple times as long as you do so before the duration expires.}
        
\DeclareSpell{Imbue Hex}{evocation|V,  S,  DF or M (a hag's whisker)|10 minutes|touch|Targets: creature touched; see text|permanent or until discharged|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Imbue Hex}{You transfer a single hex you know to the target, and give that target the ability to use the hex. The transferred hex's variable characteristics function according to your level, not the level of the recipient. Only a creature with Intelligence and Wisdom scores of at least 9 can receive this effect. To use this hex, the target must be able to speak and move freely. Once it uses the hex, the spell ends (though any effects of the hex still last for  the full duration). You can transfer only a hex-not a major or grand hex-with this ability.  Once you cast imbue hex, you cannot use the transferred hex until the spell is discharged, dispelled, or dismissed.}
        
\DeclareSpell{Phantom Hunt}{transmutation|V,  S,  DF|1 standard action|personal (see text)|Targets: you and one animal companion within 30 ft.|1 hour/level (D)||}[]
    \DeclareSpellDescription{Phantom Hunt}{You affect yourself and a single animal companion within 30 feet of you. Both you and the animal companion gain darkvision to 100 feet, tremorsense to 20 feet, and a 40-foot enhancement bonus to movement. Furthermore, you can track while moving at full speed without taking any penalty. If you already have the ability to track at full speed, you gain a +4 bonus on Survival checks while tracking instead.  The duration of this spell immediately ends if you or the animal companion attack another creature or are attacked by another creature.}
        
\DeclareSpell{Spirit Call}{enchantment|V,  S,  DF|1 full round|100 ft.|Effect: 100-ft.-radius spread centered on you|1 minute/level||}[]
    \DeclareSpellDescription{Spirit Call}{You call out to nature spirits associated with your spirit (not your wandering spirit) if you are a shaman, or your domain if you are a druid, beckoning them forth to pay attention to your current location. For the duration of the spell, all spells from your spirit magic list or domain list that are cast within the affected area have their caster level increased by 1, and all spellcasters casting such spells receive a +4 insight bonus on their concentration checks for those spells only.}
        
\DeclareSpell{Wrathful Weapon}{transmutation [see text]|V,  S,  DF|1 standard action|touch|Targets: melee weapon touched (see text)|1 minute/level|Will (harmless, object)|yes (object)}[]
    \DeclareSpellDescription{Wrathful Weapon}{You grant the targeted weapon one of the following weapon special abilities: anarchic, axiomatic, holy, or unholy. If anarchic, this spell has the chaos descriptor; if axiomatic, the law descriptor; if holy, the good descriptor; and if unholy, the evil descriptor. If the caster attempts to place a special ability on a weapon that already has that special ability, the spell fails.  If a warpriest casts this spell on his sacred weapon, the duration doubles. Warpriests with unarmed strike as a sacred weapon can cast this spell on their unarmed strike.}
    