    
\DeclareSpell{Accept Affliction}{conjuration (healing) [good]|V,  S,  M/DF (dove's heart)|1 standard action|touch|Targetscreature touched|instantaneous|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Accept Affliction}{The caster can transfer the effects of afflictions such as curses, diseases, and poisons from the target creature to himself. This spell can also transfer the blinded, deafened, fatigued, nauseated, shaken, and sickened conditions. All aspects of the transferred afflictions (save DCs, remaining duration, removal conditions, and so on) remain the same, but affect the caster instead of the original target. After transferring the affliction or condition, the caster is free to cure it in any way he can.}
        
\DeclareSpell{Angelic Aspect, Lesser}{transmutation () [good]|V,  S|1 standard action|personal|Targetsyou|1 minute/level (D)|none|no}[]
    \DeclareSpellDescription{Angelic Aspect, Lesser}{You take on an aspect of an angelic being, including some of its physical characteristics. You gain low-light vision, resistance to acid 5, resistance to cold 5, and the benefits of protection from evil.}
        
\DeclareSpell{Angelic Aspect, Greater}{transmutation () [good]|V,  S|1 standard action|personal|Targetsyou|1 minute/level (D)|none|no}[]
    \DeclareSpellDescription{Angelic Aspect, Greater}{This spell functions like lesser angelic aspect, except you gain low-light vision; darkvision 60 feet; DR 10/evil; immunity to acid, cold, and petrification; resistance to electricity 10 and fire 10; a +4 racial bonus on saves against poison; and protective aura and truespeech as supernatural abilities for the duration of the spell. Also, your wings give you a fly speed of 60 feet with good maneuverability.  Protective aura provides a +4 deflection bonus to AC and a +4 resistance bonus on saving throws against attacks made or effects created by evil creatures to anyone within 20 feet. Otherwise, it functions as a magic circle against evil and a lesser globe of invulnerability, both with a radius of 20 feet.  Truespeech allows you to speak with any creature that has a language, as though using the tongues spell.}
        
\DeclareSpell{Angelic Aspect}{transmutation () [good]|V,  S|1 standard action|personal|Targetsyou|1 minute/level (D)|none|no}[]
    \DeclareSpellDescription{Angelic Aspect}{This spell functions like lesser angelic aspect, except you gain low-light vision, darkvision 60, resistance to acid 10, resistance to cold 10, and DR 5/evil, and you sprout white feathered wings allowing you to fly at a speed of 30 feet with average maneuverability. In addition, your natural weapons and any weapons you wield are considered good-aligned for the purpose of overcoming damage reduction.}
        
\DeclareSpell{Archon's Trumpet}{evocation () [good,  sonic]|V,  S|1 standard action|30 ft.|Areacone-shaped burst|instantaneous|Fortitude negates|yes}[]
    \DeclareSpellDescription{Archon's Trumpet}{Upon hearing a booming report, as if from a trumpet archon's mighty horn, all creatures in the area of the burst are paralyzed for 1d4 rounds.}
        
\DeclareSpell{Burst Of Radiance}{evocation () [good,  light]|V,  S,  M/DF (a piece of flint and a pinch of silver dust)|1 standard action|long (400 ft. + 40 ft./level)|Area10-ft.-radius burst|instantaneous|Reflex partial|yes}[]
    \DeclareSpellDescription{Burst Of Radiance}{This spell fills the area with a brilliant flash of shimmering light. Creatures in the area are blinded for 1d4 rounds, or dazzled for 1d4 rounds if they succeed at a Reflex save. Evil creatures in the area of the burst take 1d4 points of damage per caster level (max 5d4), whether they succeed at the Reflex save or not.}
        
\DeclareSpell{Chains Of Light}{conjuration (creation) [good]|V,  S,  F (a length of fine golden chain)|1 standard action|short (25 ft. + 5 ft./level)|Targetsone creature|1 round/level (D)|Reflex negates|no}[]
    \DeclareSpellDescription{Chains Of Light}{A creature targeted by this spell is held immobile by glowing golden chains composed of pure light. The creature is paralyzed and held in place, but may attempt a new saving throw each round to end the effect. While held by the golden chains, a creature cannot use any sort of extradimensional travel, such as astral projection, blink, dimension door, ethereal jaunt, etherealness, gate, maze, plane shift, shadow walk, teleport, and similar spells and spell-like abilities. The spell does not affect creatures that are already in ethereal or astral form when the spell is cast.}
        
\DeclareSpell{Touch Of Mercy}{enchantment (compulsion) [good,  mind-affecting]|V,  S,  DF|1 standard action|touch|Targetsone creature|1 round/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Touch Of Mercy}{The target creature deals only nonlethal damage with all of its weapon attacks. Damage taken by creatures or objects that are not subject to nonlethal damage is not converted to nonlethal and remains lethal damage. The weapon retains all of its other normal properties.}
        
\DeclareSpell{Hymn Of Mercy}{enchantment (compulsion) [good,  mind-affecting]|V,  S|1 standard action|30 ft.|Area30-ft.-radius burst centered on you|1 round/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Hymn Of Mercy}{This spell functions like touch of mercy, except as noted above.}
        
\DeclareSpell{Hymn Of Peace}{abjuration () [good]|V,  S|1 standard action|40 ft.|Area40-ft.-radius burst centered on you|1 round/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Hymn Of Peace}{Each time a subject of this spell attempts to attack another creature or object, or otherwise perform an aggressive or damaging action toward a creature or object, it must attempt a Will save. If the save succeeds, the subject can attack normally. If the save fails, the subject cannot follow through with the attack and loses that part of its action. Creatures not taking violent actions are unaffected by this spell.}
    