    
\DeclareSpell{Allied Cloak}{abjuration () []|V,  S,  F (cloak or outer garment)|1 standard action|personal|Targetsyou|1 round/level|none|no}[]
    \DeclareSpellDescription{Allied Cloak}{You cause a cloak, shawl, poncho, or other outer garment you are wearing to animate to aid and defend you. The cloak provides a +2 shield bonus to your AC. In addition, once each round during your turn, you can take a free action to direct your cloak to use the aid another action to assist your skill check, attack roll, or AC. The cloak has an attack bonus or a total skill bonus equal to your caster level plus your key spellcasting ability score modifier (Charisma for bards, Intelligence for wizards, and so on). If another creature dons the cloak during the duration, the cloak provides its protection and aid to the wearer, but it still uses the same bonus on the aid another actions as if you were the wearer. The cloak cannot take any other type of action.}
        
\DeclareSpell{Billowing Skirt}{transmutation () []|V,  S,  F (a skirt,  kilt,  or gown)|1 standard action|personal|Targetsyou|1 minute/level|none|no}[]
    \DeclareSpellDescription{Billowing Skirt}{A skirt, kilt, or gown you are wearing enables you to control your falls through the air. A creature wearing the enchanted item of clothing falls slowly as if affected by feather fall and can attempt a DC 15 Fly skill check as a move action to hover in place for 1 round.}
        
\DeclareSpell{Grappling Scarf}{transmutation () []|V,  S,  F (scarf)|1 standard action|personal|Targetsyou|1 minute/level|none|no}[]
    \DeclareSpellDescription{Grappling Scarf}{A scarf you are wearing frays at the end into hook-like shapes  and can extend to incredible lengths. Although your scarf retains its weight, its frayed ends function as a grappling hook that can be thrown with a range increment of 20 feet. Your scarf elongates to 100 feet the first time it is thrown during the spell duration. Regardless of its apparent material, the scarf is as strong and easy to climb as a knotted silk rope. At the end of the duration, the scarf detaches and returns to its former shape, fluttering down from its position if you haven't already retrieved it.}
        
\DeclareSpell{Restful Cloak}{conjuration (healing) []|V,  S,  F (cloak)|1 standard action|personal|Targetsyou|1 hour/level|none|no}[]
    \DeclareSpellDescription{Restful Cloak}{A cloak you are wearing transforms into a canvas tent large enough to hold four Medium creatures, firmly pitched in a flat area adjacent to you (if there is no such area, this spell simply fails). A creature regains 1 hit point for each hour it rests in the tent, in addition to any other benefits of resting. Additionally, a fatigued creature resting within the tent for 1 hour loses the fatigued condition, but a creature cannot recover from being fatigued more than once per casting of restful tent. At the end of the spell's duration, the tent transforms back into a cloak. If the tent is moved prior to the expiration of the spell's duration, the spell immediately ends.}
        
\DeclareSpell{Sculpted Cape}{transmutation () []|V,  S,  F (cape or loose outer garment)|1 standard action|personal|Targetsyou|1 minute/level|none|no}[]
    \DeclareSpellDescription{Sculpted Cape}{Your cape, cloak, or shawl stiffens and maintains its shape even if removed. A sculpted cape has hardness 2 and a number of hit points equal to your caster level, and it can support 1 pound of weight per caster level. An unworn sculpted cape can provide cover.}
        
\DeclareSpell{Surefoot Boots}{transmutation () []|V,  S,  F (footwear)|1 standard action|personal|Targetsyou|1 round/level|none|no}[]
    \DeclareSpellDescription{Surefoot Boots}{You touch your boots, shoes, or other footwear and imbue them with the ability to find purchase on even the most treacherous ground. While the spell is in effect, the footwear's wearer treats any Acrobatics skill check to balance as though the wearer had rolled a 20.}
    