    
\DeclareSpell{Bereave}{enchantment (compulsion) [mind-affecting]|V,  S,  M/DF (a broken chain link)|1 standard action|medium (100 ft. + 10 ft./level)|Targets: all creatures in a 15-ft.-radius burst|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Bereave}{An overwhelming feeling of loss overcomes the targets, and their allies' words sound bleak and hollow. Regardless of actual allegiances, affected creatures no longer count as allies for other creatures and always count as enemies for the purposes of abilities, effects, and spells that differentiate between allies and enemies, such as flanking or spells such as bane or bless. Allies of an affected creature must succeed at a melee touch attack to affect the subject with touch spells, and an affected creature cannot voluntarily fail a saving throw even if the effect is harmless (such as cure light wounds). An affected creature still counts as her own ally and can target herself with abilities, effects, and spells normally.}
        
\DeclareSpell{Overstimulate}{transmutation|V,  S,  M/DF (smelling salts)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature|1 round/level|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Overstimulate}{You deprive a creature of the blissful oblivion of unconsciousness, either to keep it going despite grievous injuries or to prolong its suffering. For the duration of the spell, the target gains the ferocity ability (Pathfinder RPG Bestiary 300), allowing it to remain conscious and continue fighting even if its hit point total is below 0. The target is still staggered and loses 1 hit point each round, and the target still dies when its hit point total reaches a negative amount equal to its Constitution score.}
        
\DeclareSpell{Scarify}{necromancy|V,  S|1 standard action|touch|Targets: creature touched|instantaneous|Fortitude negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Scarify}{Your touch causes a single creature's skin to produce fibrous tissue that sutures the creature's wounds, rapidly closing them and leaving jagged scars where the wounds were. The process is painful, and converts 2d6 points of damage + 1 point per caster level (maximum +5) into nonlethal damage. If the target creature is immune to nonlethal damage, the spell fails. Damage resistance against nonlethal damage reduces the amount of damage converted. This effect counts as healing for the purpose of stopping bleed damage. Kuthites are especially fond of this spell, as it gives them permanent physical reminders of the all too brief pain they endured.}
        
\DeclareSpell{Shroud Of Darkness}{evocation [darkness]|V,  S,  M/DF (a pinch of black sand)|1 standard action|medium (100 ft. + 10 ft./level)|Targets: one creature/3 levels, no two of which can be more than 30 ft. apart|1 round/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Shroud Of Darkness}{With a dark incantation and a gesture of your hand over your eyes, you cause a shroud of darkness to descend upon the targets of this spell. The subjects treat the light level as two steps lower than normal for the duration of this spell. Bright light becomes dim light, normal light becomes darkness, and areas of dim light and darkness become supernaturally dark (as darkness, but even creatures with darkvision cannot see).}
        
\DeclareSpell{Ferment}{transmutation|V,  S,  M (a drop of ale,  mead,  or wine)|1 standard action|touch|Targets: object touched|10 minutes/level|Fortitude negates (object)|yes (object)}[]
    \DeclareSpellDescription{Ferment}{This spell temporarily imbues a potable liquid (including elixirs, extracts, potions, and poisons) with an intoxicant. The caster must succeed at a caster level check in order to affect magic liquids and poisons (DC = 10 + item level for magic liquids, DC equal to the poison's save DC for a poison); otherwise, the spell fails. If the caster succeeds, the liquid also assumes a flavor according to what the caster desires,  but the effect on the imbiber is the same. An imbiber of a liquid affected by ferment must succeed at a Fortitude saving throw at the spell's save DC or take a -2 penalty on attack rolls, saves, ability checks, and skill checks for the remaining duration of the spell. Additionally, the DC of any skill check to identify a magic liquid or poison under the effects of this spell increases by 5.}
        
\DeclareSpell{Free Spirit}{abjuration|V,  S|1 standard action|personal|Targets: you|1 minute/level||}[]
    \DeclareSpellDescription{Free Spirit}{This spell allows you to channel the essence of Cayden Cailean's philosophy, giving you the benefits of a freedom of movement spell and granting you a +4 bonus on saving throws against fear effects. The spell also makes you drunk. For the duration of the spell, you take a -2 penalty on attack rolls, ability checks, skill checks, and concentration checks. If you somehow remove or avoid these penalties, the spell's duration ends.}
        
\DeclareSpell{Mass Knock}{transmutation|V|1 standard action|close (25 ft. + 5 ft./level)|Targets: one means of closure/level, no two of which can be more than 30 feet apart|instantaneous|none|no}[]
    \DeclareSpellDescription{Mass Knock}{Also known as "unshackle," this spell functions as knock, but works on multiple means of closure at once.}
        
\DeclareSpell{Spirit Share}{transmutation|V,  S,  F (liquid to be shared)|1 standard action|personal|Targets: you|1 round/level||}[]
    \DeclareSpellDescription{Spirit Share}{This spell was first created as a minor parlor trick, but adventuring Caydenites have repurposed and improved on it for use on their travels. For the duration of the spell, as a standard action you can touch a willing target to deliver 1 dose of a potable liquid (including alcoholic drinks and potions and elixirs, but not poisons or other liquids that are primarily harmful when drunk) in your possession (though not necessarily held in hand) into her.}
        
\DeclareSpell{Soul Vault}{abjuration|V,  S,  DF|1 standard action|touch|Targets: creature touched|10 minutes/level|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Soul Vault}{This spell protects the target's soul by briefly enveloping the target in an ethereal vault. The target gains a +4 bonus on saving throws against spells and effects that would trap or redirect its soul (such as magic jar, soul bind, and trap the soul) and effects that would transform the target into an undead creature. The target is granted a save to negate such effects even if one is not normally allowed. If it's cast on a living creature that then dies, the target's body and spirit are protected by the spell for its duration. If it's cast on a corpse within 1 round of death, the target's body and soul are both protected. Otherwise, only the body receives the protection.  Any spellcaster that worships Abadar may learn and cast soul vault as a 4th level spell, if it isn't normally on her class spell list. Soul vault can be made permanent with the permanency spell at a cost of 7,500 gp and a minimum caster level of 11th.}
        
\DeclareSpell{True Appraisal}{divination|V,  F (gold coin)|1 standard action|personal|Targets: you|8 hours|none|no}[]
    \DeclareSpellDescription{True Appraisal}{You gain temporary insight into the value of objects. You gain a +5 competence bonus on Appraise checks, can attempt an Appraise check to determine an object's value as a move action, and can take 10 on an Appraise check even if stress or distractions would normally prevent you from doing so. You know if you fail an Appraise check, and you never determine a wildly inaccurate price.}
        
\DeclareSpell{Funereal Weapon}{transmutation|V,  S,  DF|1 standard action|touch|Targets: weapon touched or 50 projectiles (all of which must be together at the time of casting)|1 minute/level|Will negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Funereal Weapon}{You imbue a weapon with a faint silvery glow that dimly illuminates a 5-foot square. An affected weapon also easily bypasses the physical defenses of undead creatures, ignoring 5 points of an undead creature's damage reduction, as long as the damage reduction is not DR/epic. For example, attacks with a weapon affected by this spell completely ignore a zombie's DR 5/slashing or reduce a lich's damage reduction to DR 10/bludgeoning and magic.  You can't cast this spell on a natural weapon, such as an unarmed strike. Funereal weapon affects the DR of only undead creatures.}
        
\DeclareSpell{Necrostasis}{necromancy|V,  S,  M/DF (a finger bone)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one undead creature|1 round/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Necrostasis}{You drain necromantic energy from an undead creature, inducing a sluggish stupor. The target becomes staggered. For the duration of the spell, dark wisps of energy seep out of the target creature. If the target already has the staggered condition (as a zombie does), it becomes dazed for 1 round instead.}
        
\DeclareSpell{Preserve}{necromancy|V,  S,  M/DF (a pinch of salt)|1 standard action|touch|Targets: one or more objects touched, up to 1 lb./level|1 week|Will negates (object)|yes (object)}[]
    \DeclareSpellDescription{Preserve}{You imbue one or more objects with magic that dramatically slows down natural processes that lead to decay and spoilage. For the duration of the spell, food, water, plants, and other perishable objects affected by the spell remain as fresh as they were when the spell was cast. The spell also protects these objects against spells of the same level or lower that cause spoilage, such as putrefy food and drinkAPG. When the duration of preserve expires, the objects resume aging at their normal rate.  The spell also works on severed body parts and the bodies of small creatures as per gentle repose, provided that the weight of the creature or part does not exceed the spell's limit.  Preserve can be made permanent with a permanency spell by a caster of 9th level or higher for 500 gp.}
        
\DeclareSpell{Spiral Ascent}{conjuration (teleportation)|V,  S|1 standard action|long (400 ft. + 40 ft./level)|Targets: you and touched objects|instantaneous|Will negates (object)|yes (object)}[]
    \DeclareSpellDescription{Spiral Ascent}{You transform yourself into a helical beam of divine energy that instantly transports you upward to a spot within range. The destination must be a square in the spell's range that's within 10 feet of a point directly above you. The destination must be within your line of sight or familiar to you. After using this spell, you can't take any other actions until your next turn. You can bring along objects as long as their weight doesn't exceed your maximum load.  If you arrive in a place that is already occupied by a solid body, you are teleported to a random open space on a suitable surface within the range and other limitations of the spell. If no such space is available, the spell simply fails. This spell  does not function on a plane lacking gravity. On a plane with subjective directional gravity, you can use this spell to teleport in any direction.}
        
\DeclareSpell{Spiral Descent}{conjuration (teleportation)|V,  S|1 standard action|long (400 ft. + 40 ft./level)|Targets: you and touched objects|instantaneous|Will negates (object)|yes (object)}[]
    \DeclareSpellDescription{Spiral Descent}{This spell functions as spiral ascent, except the destination and direction of travel is downward from your current location.}
        
\DeclareSpell{Betraying Sting}{evocation|V|1 standard action|long (400 ft. + 40 ft./level)|Targets: one creature|instantaneous|Will partial|yes}[]
    \DeclareSpellDescription{Betraying Sting}{You unleash divine power to smite those who wrongly trusted you. The power takes the form of a yellow-and-black bolt of energy that makes the sound of a thousand angry, swarming wasps. This spell affects only creatures that have an attitude toward you of indifferent, friendly, or helpful. The spell deals 1d8 points of damage per 2 caster levels you have.}
        
\DeclareSpell{Harvest Knowledge}{divination [mind-affecting]|V,  S,  M (a piece of lodestone)|1 standard action|touch (see text)|Targets: one creature or object; see text|concentration, up to 1 minute/level|Will negates; see text|no}[]
    \DeclareSpellDescription{Harvest Knowledge}{You touch a creature and temporarily absorb its knowledge for yourself. If the target fails its saving throw, you can sort through its lore and memories. You can retrieve one answer to a specific question per minute, as through sifting through the creature's surface thoughts with detect thoughts. Alternatively, you can tap into the target's learned experiences and attempt one Knowledge check in a skill in which the target has at least 1 rank, using the target's total skill modifier. Each Knowledge check requires 1 minute and allows the target another Will save to resist the effect. If the target successfully resists, the spell does not end, but you are unable to attempt another Knowledge check for that skill using this spell. You can also use this spell against targets trapped in magic items or spells that hold their bodies or souls, such as an iron flask or the spell trap the soul, by touching the associated receptacle.}
        
\DeclareSpell{Incessant Buzzing}{illusion (figment)|V,  S,  M/DF (insect wing)|1 standard action|medium (100 ft. +10 ft./level)|Effect: 10-ft.-diameter sphere|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Incessant Buzzing}{You summon an illusory swarm of angry wasps that fills a 10-foot-diameter sphere. You can summon it so that it shares an area with other creatures, and you can move it up to 40 feet each round as a move action. Creatures caught inside the swarm's area of effect cannot use skills that require patience or concentration. Additionally, spellcasters within the area must succeed at a caster level check (DC =  20 + level of spell to be cast) in order to cast spells. On a failed caster level check, the spell is lost. While the buzzing is unpleasant, it is not so loud as to drown out other noises or make communication difficult.}
        
\DeclareSpell{Painful Revelation}{abjuration [mind-affecting,  painUM]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one ongoing illusion effect|1 hour/level or until discharged|Will partial|no}[]
    \DeclareSpellDescription{Painful Revelation}{You augment an ongoing illusion effect to strike out painfully at creatures that see through it. When a creature successfully disbelieves an illusion that is the target of painful revelation, it takes 1d6 points of nonlethal damage for every 2 caster levels you have (maximum 10d6) and is staggered for 1d4 rounds. A successful Will save reduces the nonlethal damage by half and negates the staggered effect. Once painful revelation has been triggered, the spell ends.  However, creatures under the effect of spells such as true seeing that automatically pierce illusions are not subject to this effect.}
        
\DeclareSpell{Pillow Talk}{enchantment (compulsion) [language-dependent,  mind-affecting]|S|10 minutes|touch|Targets: sleeping, living creature touched|1 minute/level|Will negates; see text|yes}[]
    \DeclareSpellDescription{Pillow Talk}{This spell can be cast only on a sleeping creature, which must be present for the full duration of the casting time. You grant the semblance of wakefulness to the target, allowing it to answer questions. You can ask one question per 2 caster levels. The target's knowledge is limited to what it normally knows, including the languages it speaks. Answers are brief, cryptic, or repetitive, especially if the creature would have opposed you when awake. If the target succeeds at a Will save, it awakens (unless some force is  preventing it from being awake, such as magic or drugs), and it remains aware of the first question you asked. If the target has been subject to pillow talk within the past week, the new spell fails. While your questions don't otherwise wake the target, this spell does nothing to prevent other sounds or stimulus from waking the target. A target who sleeps through the spellcasting and duration of the spell has no memory of it taking place, but a target who awakens before the spell ends remembers every question asked and what answers it gave.}
        
\DeclareSpell{Reveal Secrets}{enchantment (compulsion) [language-dependent,  mind-affecting]|V,  S,  M (a drop of alcoholic liquid)|1 standard action|touch|Targets: creature touched|1 round|Will negates|yes}[]
    \DeclareSpellDescription{Reveal Secrets}{When you cast this spell, you ask the target whether it has a secret about a specific topic that can be described in 10 words or fewer. This can concern a person, place, or thing (such as a town's mayor, the ring worn by a traveling merchant, or the bridge spanning a nearby river) or an easily distinguished event (such as a historic battle or a recent rash of disappearances). If the target knows a secret about the topic (information it believes isn't common knowledge and which it would not normally tell you), it states it has a secret. The target doesn't mention anything about the secret and doesn't remember telling you it has a secret. If the target succeeds at its saving throw, it isn't compelled to reveal whether it knows a secret and is aware that you asked.}
    