    
\DeclareSpell{Agonize}{evocation () [evil]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone conjured outsider or elemental (see text)|1 full round|Fortitude negates|yes}[Pain encourages an outsider to obey you.]
    \DeclareSpellDescription{Agonize}{You afflict a creature you have conjured via planar ally (or a similar spell) with bolts of vicious energy. These foul energies inflict terrible pain upon the summoned creature, torturing it to make it more pliant to your will. The targeted creature must make a Fortitude save or take a -1 penalty for every 2 levels you possess (maximum -10) on all saves and checks made against you for the next hour. In addition, creatures that demand payment for their services reduce the payment by 20\% for every 4 levels you possess (maximum 60\% reduction). However, beings tortured by this spell quickly come to resent you, making them more likely to try to pervert your orders to malicious ends or try to seek retribution after their release. This spell has no effect on creatures that are immune to nonlethal damage.}
        
\DeclareSpell{Acidic Spray}{conjuration (creation) [acid]|V,  S,  M (a vial of acid worth 10 gp)|1 standard action|60 ft.|Effect60-ft. line|instantaneous|Reflex partial (see text)|yes}[1d6/level acid damage plus 1 round of acid.]
    \DeclareSpellDescription{Acidic Spray}{A spray of acid erupts from your outstretched hand, dealing 1d6 points of acid damage per caster level (maximum 15d6) to each creature within its area (Reflex half ). This acid continues to burn for 1 round, dealing 1d6 points of acid damage per two caster levels (maximum 7d6) to any creature that failed its saving throw against the spell (a second Reflex save on the creature's turn negates this additional damage).}
        
\DeclareSpell{Acute Senses}{transmutation () []|V,  S,  M (a glass lens)|1 standard action|touch|Targetscreature touched|1 minute/level|Will negates (harmless)|yes}[Subject gains a bonus on Perception checks.]
    \DeclareSpellDescription{Acute Senses}{The target gains a +10 enhancement bonus on Perception checks. The bonus increases to +20 at caster level 8th, and +30 (the maximum) at caster level 16th.}
        
\DeclareSpell{Age Resistance, Lesser}{transmutation () []|V,  S|1 standard action|personal|Targetsyou|24 hours||}[Ignore penalties from middle age.]
    \DeclareSpellDescription{Age Resistance, Lesser}{You ignore the physical detriments of being middle-aged. This spell does not cause you to look younger, nor does it prevent you from dying of old age, but as long as the spell is in effect, you ignore the -1 penalties to Strength, Dexterity, and Constitution that accrue once you become middle-aged. You retain the agerelated bonuses to Intelligence, Wisdom, and Charisma while under the effects of this spell. Additional penalties that you accrue upon becoming old or venerable apply in full.}
        
\DeclareSpell{Age Resistance, Greater}{transmutation () []|V,  S|1 standard action|personal|Targetsyou|24 hours||}[Ignore penalties from venerable age.]
    \DeclareSpellDescription{Age Resistance, Greater}{This spell functions as lesser age resistance, except you ignore all Strength, Dexterity, and Constitution penalties gained from middle age, old age, and venerable age.}
        
\DeclareSpell{Age Resistance}{transmutation () []|V,  S|1 standard action|personal|Targetsyou|24 hours||}[Ignore penalties from old age.]
    \DeclareSpellDescription{Age Resistance}{This spell functions as lesser age resistance, except you ignore the Strength, Dexterity, and Constitution penalties gained at middle age and old age.}
        
\DeclareSpell{Allegro}{transmutation () []|V|1 standard action|personal|Targetsyou|1 round/level (D) or until discharged||}[Gain haste while maintaining bardic performance.]
    \DeclareSpellDescription{Allegro}{This spell allows you to act more swiftly while maintaining a bardic performance. You must already be maintaining a bardic performance before you can cast allegro. You gain the benefits of the spell haste for as long as you maintain that bardic performance. If you cease maintaining the bardic performance or it is interrupted, this spell's duration ends. As an immediate action while you are maintaining a bardic performance, you can dismiss allegro to reroll a Reflex save or Dexterity-based skill check-you must choose to reroll before the result of the original roll is known. You must take the result of the reroll, even if it's worse than the original roll. Allegro dispels and is dispelled by slow.}
        
\DeclareSpell{Animate Dead, Lesser}{necromancy () [evil]|V,  S,  M (an onyx gem worth at least 25 gp per Hit Die of the undead)|1 standard action|touch|Targetsone corpse|instantaneous|none|no}[Create one skeleton or zombie.]
    \DeclareSpellDescription{Animate Dead, Lesser}{This spell functions as animate dead, except you can only create a single Small or Medium skeleton or zombie. You cannot create variant skeletons or zombies with this spell.}
        
\DeclareSpell{Anthropomorphic Animal}{transmutation (polymorph) []|V,  S,  M (a humanoid thumb bone)|1 standard action|touch|Targetsanimal touched|1 hour/level|Fortitude negates|yes}[Animal becomes bipedal.]
    \DeclareSpellDescription{Anthropomorphic Animal}{You transform the touched animal into a bipedal hybrid of its original form with a humanoid form, similar to how a lycanthrope's hybrid form is a mix of a humanoid and animal form. The animal's size, type, and ability scores do not change. It loses its natural attacks except for bite (if it had one as an animal), all types of movement other than its land speed, and special attacks that rely on its natural attacks. One pair of its limbs is able to manipulate objects and weapons as well as human hands do; limbless animals like snakes temporarily grow a pair of arms. The creature's Intelligence increases to 3, and it gains the ability to speak one language you know. It is not considered proficient in any manufactured weapons. It can attack with unarmed strikes, dealing unarmed strike damage for a creature of its size (unless it has a bite attack, which is a natural attack).
Anthropomorphic animal can be made permanent with a permanency spell cast by a caster of 11th level or higher at a cost of 7,500 gp.}
        
\DeclareSpell{Anticipate Peril}{divination () []|V,  S|1 standard action|touch|Targetscreature touched|1 minute/level or until activated|Will negates|yes}[Target gains a bonus on one initiative check.]
    \DeclareSpellDescription{Anticipate Peril}{A creature affected by anticipate peril gains a preternatural sense of danger. The first time during this spell's duration that the target has to make an initiative check, the creature adds an insight bonus on that initiative check equal to the spell's caster level (maximum +5). Once this bonus applies, the effects of the spell end.}
        
\DeclareSpell{Arboreal Hammer}{transmutation () []|V,  S,  DF|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone Huge or larger tree|1 round/level (D)|none|no}[Tree branches attack opponents.]
    \DeclareSpellDescription{Arboreal Hammer}{This spell animates a tree's branch and directs it against your foes. At caster level 10th or lower, you can target a Huge tree. At caster level 11th-15th, you can target a Gargantuan tree, and at caster level 16th or higher you can target a Colossal tree. The animated branch makes slam attacks with a Strength score equal to 10 + your caster level. The branch strikes once per round with an attack bonus equal to your caster level + the branch's Strength modifier, adjusted by the appropriate size modifier (-2 for Huge, -4 for Gargantuan, -8 for Colossal). A Huge tree's slam deals 2d6 points of damage, a Gargantuan tree's slam deals 3d6 points of damage, and a Colossal tree's slam deals 4d6 points of damage; the tree adds 1-1/2 times its Strength modifier to this damage. A Huge tree has reach 15 feet, a Gargantuan has reach 20 feet, and a Colossal has reach 30 feet. The tree attacks the creature you designate when you cast the spell, and is unable to move. You can direct the tree against a new target as a move action. The tree does not gain a bonus for flanking, nor can it help another combatant flank. It cannot attack a foe you cannot see.}
        
\DeclareSpell{Arcana Theft}{abjuration () []|V,  S|1 standard action|touch|Targetscreature touched|instantaneous|none|yes}[Targeted dispel transfers an effect to you.]
    \DeclareSpellDescription{Arcana Theft}{This spell functions as a targeted dispel magic spell, except it only affects creatures and it requires a melee touch attack. If the melee touch attack is successful and the spell successfully dispels one spell affecting the target, that spell is instead transferred to you, treating you as the original target. You do not receive a new saving throw or spell resistance check against this spell and must accept its affects even if they are not beneficial. This does not alter the spell's duration; for example, if the spell only has 4 rounds of duration remaining when it is stolen, it only affects you for 4 rounds. If the spell or effect has a duration of permanent, its duration continues for 1 hour per caster level of the original caster, after which it ends. The stolen spell does not revert to the original target.}
        
\DeclareSpell{Archon's Aura}{evocation () [good,  lawful]|V,  S|1 standard action|20 ft.|Area20-ft. radius centered on you|1 minute/level|Will negates|yes}[Aura penalizes enemy attacks and AC.]
    \DeclareSpellDescription{Archon's Aura}{You gain a powerful aura, similar to an archon's aura of menace.
Any hostile creature within a 20-foot radius of you must make a Will save to resist the effects of this aura. If the creature fails, it takes a -2 penalty on attack rolls and saving throws and to Armor Class for the duration of this spell, or until it successfully hits you with an attack. A creature that has resisted or broken the cannot be affected again by this particular casting of archon's aura.}
        
\DeclareSpell{Arrow of Law}{evocation () [lawful]|V,  S,  DF (a holy symbol)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectarrow-shaped projectile of lawful energy|instantaneous (1 round); see text|Will partial (see text)|yes}[Harm and possibly daze chaotic creatures.]
    \DeclareSpellDescription{Arrow of Law}{You fire a shimmering arrow of pure order from your holy symbol at any one target in range as a ranged touch attack.
A chaotic creature struck by an arrow of law takes 1d8 points of damage per two caster levels (maximum 5d8). A chaotic outsider instead takes 1d6 points of damage per caster level (maximum 10d6) and is dazed for 1 round. A successful Will save reduces the damage to half and negates the daze effect.
This spell deals only half damage to creatures that are neither chaotic nor lawful, and they are not dazed. The arrow has no effect on lawful creatures.}
        
\DeclareSpell{Ash Storm}{conjuration (creation) [fire]|V,  S,  M/DF (a pinch of ash)|1 standard action|long (400 ft. + 40 ft./level)|Areacylinder (40-ft. radius, 20 ft. high)|1 round/level|none|no}[Hamper vision and movement.]
    \DeclareSpellDescription{Ash Storm}{Driving ash blocks all sight (even darkvision) within the spell's area of effect, and falling cinders cause the ground in the area to become difficult terrain.}
        
\DeclareSpell{Astral Projection, Lesser}{necromancy () []|V,  S,  M (1, 000 gp jacinth)|30 minutes|touch|Targetsyou plus one additional willing creature touched per two caster levels|see text|none|yes}[Limited astral travel.]
    \DeclareSpellDescription{Astral Projection, Lesser}{This spell functions as astral projection, except you cannot leave the Astral Plane and explore other planes (though you can still return to the plane you were on when you cast this spell).}
        
\DeclareSpell{Atavism}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone animal|1 minute/level|Fortitude negates|yes}[Animal gains advanced creature simple template.]
    \DeclareSpellDescription{Atavism}{By bringing forth the primeval ancestry of the target animal, you awaken a savage engine of destruction. The animal immediately gains the advanced creature simple template.
It gains a +2 bonus on all rolls, including damage rolls and special ability DCs, a +4 bonus to AC and CMD, and +2 hit points per HD. The animal's primal instincts take hold for the duration of this spell-if the animal knows tricks granted by the Handle Animal skill, it loses access to all of those tricks save for "attack." This spell has no effect on animals that already have the advanced creature template.}
        
\DeclareSpell{Atavism, Mass}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone animal/level, no two of which can be more than 30 ft. apart|1 minute/level|Fortitude negates|yes}[One animal/level gains advanced template.]
    \DeclareSpellDescription{Atavism, Mass}{This spell functions as atavism, except it affects multiple creatures.}
        
\DeclareSpell{Aura of Doom}{necromancy () [emotion,  fear,  mind-affecting]|V,  S,  M/DF (powdered bone)|1 standard action|personal|Area20-ft.-radius emanation centered on you|10 minute/level|Will negates|yes}[Creatures in your aura become shaken.]
    \DeclareSpellDescription{Aura of Doom}{You emanate an almost palpable aura of horror. All non-allies within this spell's area, or that later enter the area, must make a Will save to avoid becoming shaken. A successful save suppresses the effect. Creatures that leave the area and come back must save again to avoid being affected by the effect.}
        
\DeclareSpell{Badger's Ferocity}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone weapon/3 levels|concentration|Will negates (harmless)|yes (harmless)}[Weapons are keen while you concentrate.]
    \DeclareSpellDescription{Badger's Ferocity}{This functions like keen edge, except it affects multiple weapons and requires your concentration. You select the weapons to be affected, and can only affect one weapon per creature. If a creature's weapon exceeds the spell's range, the spell ends for that weapon.}
        
\DeclareSpell{Battlemind Link}{divination () [mind-affecting]|V,  S|1 standard action|personal and close (25 ft. + 5 ft./2 levels)|Targetsyou and 1 ally|1 minute/level|Will negates (harmless)|yes (harmless)}[You and an ally gain attack and AC bonuses.]
    \DeclareSpellDescription{Battlemind Link}{You fuse your thoughts with an ally's, allowing the two of you to fight in tandem, perfectly coordinated. You and the ally each roll initiative in combat and use the higher die result before adding modifiers. This has three effects.
 Melee: If you both make melee attacks against the same creature, you both make attack rolls and both use the higher of the two dice for your attack rolls (plus bonuses).
 Ranged: If you both make ranged attacks against the same creature, you both make attack rolls and both use the higher of the two dice for your attack roll (plus bonuses).
 Spell: If you both cast spells and target the same area or same creature, affected creatures take a -2 penalty on their saving throw against the spells.
 You and the target lose these benefits if you cannot see each other or if you or the target is unconscious or helpless.}
        
\DeclareSpell{Bestow Grace of the Champion}{transmutation () [good,  law]|V,  S,  DF|1 standard action|touch|Targetslawful good creature touched|1 round/level (see text)|yes (harmless)|yes (harmless)}[Target gains paladin abilities for 1 round/level.]
    \DeclareSpellDescription{Bestow Grace of the Champion}{You channel the power of good and law into the target, temporarily giving it powers similar to those of a paladin.
The target gains the ability to use detect evil at will as a spell-like ability, immunity to disease (suppressing any diseases currently affecting it), and immunity to fear (ending any fear effects currently affecting it); can lay on hands (on itself only) once as a paladin of 1/2 your caster level; and can smite evil once as a paladin of 1/2 your caster level. It adds its Charisma bonus to all its saving throws. It can use spell completion, spell trigger, or other magic items that require the ability to cast spells as a paladin. Any abilities not used by the time the spell expires are lost. This spell has no if cast on a paladin.}
        
\DeclareSpell{Blade of Bright Victory}{transmutation () [good]|V,  S|1 standard action|touch|Targetsyour paladin bonded weapon|1 minute/level|Will negates (harmless)|no}[Bonded weapon gains ghost touch.]
    \DeclareSpellDescription{Blade of Bright Victory}{You strengthen the bond between your divine bond weapon and its celestial spirit. The weapon gains the ghost touch property. You may change your weapon's damage type (bludgeoning, piercing, slashing) as a swift action. You gain a sacred bonus to your CMD against disarm and sunder attacks directed at your bonded weapon; this bonus is equal to half your caster level.}
        
\DeclareSpell{Blade of Dark Triumph}{transmutation () [evil]|V,  S|1 standard action|touch|Targetsyour fiendish boon weapon|1 minute/level|Will negates (harmless)|no}[Bonded weapon gains ghost touch.]
    \DeclareSpellDescription{Blade of Dark Triumph}{You strengthen the bond between your fiendish boon weapon and its unholy spirit. The weapon gains the ghost touch property.
You may change your weapon's damage type (bludgeoning, piercing, slashing) as a swift action. You gain a profane bonus to your CMD against disarm and sunder attacks directed at your boon weapon; this bonus is equal to half your caster level.}
        
\DeclareSpell{Blessing of the Mole}{transmutation () []|V,  S|1 round|close (25 ft. + 5 ft./2 levels)|Area1 creature/level|1 minute/level|none (harmless)|yes (harmless)}[1 ally/level gains darkvision and a +2 Stealth bonus.]
    \DeclareSpellDescription{Blessing of the Mole}{The targets gain darkvision 30 feet and a +2 competence bonus on Stealth checks.}
        
\DeclareSpell{Blood Crow Strike}{evocation () [fire]|V,  S|1 round|medium (100 ft. + 10 ft./level)|Targetsone creature|instantaneous|none|yes}[Unarmed strikes create crows that deal fire and negative energy damage.]
    \DeclareSpellDescription{Blood Crow Strike}{Your unarmed strikes release blasts of energy in the form of bolts of fire or glowing red crows, which fly instantaneously to strike your target. You can make unarmed strike or flurry of blows attacks against the target as if it were in your threatened area; each successful attack deals damage as if you had hit it with your unarmed strike, except half the damage is fire and half is negative energy (this negative energy does not heal undead). For example, if you are a 14th-level monk, you can use a flurry of blows to attack five times, creating one energy crow for each successful attack against the target, and dealing 2d6 points of damage (plus appropriate unarmed strike modifiers) with each crow.}
        
\DeclareSpell{Blood Mist}{conjuration (creation) [poison]|V,  S,  M (a pinch of dried red algae)|1 standard action|medium (100ft. +10ft./level)|Area60-ft. radius|1 minute/level|Fortitude negates (see text)|yes}[Mist causes Wisdom damage and rage.]
    \DeclareSpellDescription{Blood Mist}{This spell summons forth a misty cloud of rust-red toxic algae. Any creature within the mist is coated by it, turning the creature the same reddish color. All targets within the mist gain concealment. Any creature within the mist must save or take 1d4 points of Wisdom damage and become enraged, attacking any creatures it detects nearby (as the "attack nearest creature" result of the confused condition). An enraged creature remains so as long as the spell is in effect. A creature only needs to save once each time it is within the mist (though leaving and returning requires another save).}
        
\DeclareSpell{Blood Transcription}{divination () [evil]|V,  S|1 standard action|touch|Targetsone dead spellcaster|24 hours|none|no}[Learn a spell from the target's blood.]
    \DeclareSpellDescription{Blood Transcription}{By consuming 1 pint of blood from a spellcaster killed within the last 24 hours, you can attempt to learn a spell that spellcaster knew. Select one spell available to the dead  spellcaster (this must be a spell on your spell list); you gain the knowledge of this spell for 24 hours. During this time, you may write it down (or teach it to your familiar, if you are a witch) using the normal rules for copying a spell from another source. Once you have learned it, you may prepare the spell normally.}
        
\DeclareSpell{Boiling Blood}{transmutation () []|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone creature per three levels, no two of which may be more than 30 ft. apart|concentration + 1 round/level (D)|Fortitude negates (see text)|yes}[Targets take fire damage; orcs get +2 Strength.]
    \DeclareSpellDescription{Boiling Blood}{The blood of the targeted creatures begins to boil. If a target fails its save, it takes 1 point of fire damage per round. This spell has no effect on creatures that don't have blood.  If a target has the orc subtype, it doesn't take fire damage and instead gains a +2 morale bonus to Strength.}
        
\DeclareSpell{Bungle}{enchantment (compulsion) []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone humanoid|concentration + 2 rounds or until triggered|Will negates|yes}[Target takes a –20 penalty on its next attack roll or check.]
    \DeclareSpellDescription{Bungle}{The target takes a -20 penalty on its next attack roll or check that requires a d20 roll. The action must be one deliberately taken by the target on its turn. Creatures with more than 10 HD are unaffected by this spell.}
        
\DeclareSpell{Burrow}{transmutation () []|V,  S|1 standard action|touch|Targetscreature touched|1 minute/level|Will negates (harmless)|yes (harmless)}[Target gains a burrow speed of 15.]
    \DeclareSpellDescription{Burrow}{The subject can burrow at a speed of 15 feet (or 10 feet if it wears medium or heavy armor, or if it carries a medium or heavy load) through sand, loose soil, or gravel, or at a speed of 5 feet through stone. Using burrow requires only as much concentration as walking, so the subject can attack or cast spells normally. The burrowing creature cannot charge or run. Loose material collapses behind the target 1 round after it leaves the area. This spell does not give the target the ability to breathe underground, so when passing through loose material, the creature must hold its breath and take only short trips, or else it may suffocate.}
        
\DeclareSpell{Burst of Nettles}{conjuration () [acid]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Area10-ft.-radius burst|instantaneous|Reflex half|yes}[Burst deals 3d6 damage and 1d6 acid.]
    \DeclareSpellDescription{Burst of Nettles}{You release a burst of barbed, acid-filled nettles. Creatures caught in the burst take 3d6 points of damage plus 1d6 points of acid damage on the next round. Those that save take half damage from the initial burst and no damage on the next round.}
        
\DeclareSpell{Cackling Skull}{illusion (glamer) []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone skull|permanent until discharged|Will negates|yes}[Skull acts as magic mouth, listeners are shaken.]
    \DeclareSpellDescription{Cackling Skull}{This spell functions as magic mouth, except rather than creating an illusory mouth on any surface, it affects a skull.
In addition, when the skull's magic is triggered, it releases wild and unnerving cackles before speaking its message.
All creatures that can hear the cackles must save or become shaken for 1d4 rounds.}
        
\DeclareSpell{Call Construct}{conjuration (teleportation) []|V,  S,  M (a sapphire worth 1, 000 or 5, 000 gp; see text)|10 minutes|touch|Targetsconstruct touched|permanent until discharged|none|no}[Summon your construct to you.]
    \DeclareSpellDescription{Call Construct}{This spell functions as instant summons, except it can only summon a construct you control. For constructs such as golems that are immune to magic, the value of the specially inscribed sapphire must be at least 5,000 gp. For other constructs, a 1,000 gp sapphire suffices.
If the construct is no longer under your control or destroyed, the spell fails, but you know roughly where the construct or its remains are located.}
        
\DeclareSpell{Cape Of Wasps}{conjuration (summoning) []|V,  S|1 standard action|personal|Targetsyou|1 round/level (D)||}[Wasp swarm defends or carries you.]
    \DeclareSpellDescription{Cape Of Wasps}{You summon a wasp swarm (Bestiary 275), which fills your space (up to 5 feet by 5 feet) but does not attack you. The dense cloud of vermin gives you partial concealment against ranged attacks. Any creature that makes a successful melee attack against you takes 2d6 points of swarm damage and poison from the wasp swarm, but is not affected by the swarm's distraction ability. As a free action on your turn, you may have the swarm cling to you tightly, giving you a fly speed of 20 feet (poor maneuverability); when using the swarm to fly, it does not provide concealment or harm creatures that strike you. You can return the swarm to its protective shape as a free action on your turn.}
        
\DeclareSpell{Caustic Eruption}{conjuration (creation) [acid]|V,  S|1 standard action|30 ft.|Area30-ft.-radius burst|instantaneous and 2 rounds; see text|Reflex half (see text)|no}[Burst deals 1d6 acid/level and lingers.]
    \DeclareSpellDescription{Caustic Eruption}{Acid erupts from your space in all directions, causing 1d6 points of damage per caster level (maximum 20d6) to creatures and unattended objects in the area. On your turn in each of the next 2 rounds, creatures and objects that failed their saves against the initial burst take an additional 1d6 points of acid damage per 2 caster levels (maximum 10d6) unless the acid is neutralized, dispelled, or washed away.}
        
\DeclareSpell{Chord Of Shards}{evocation () []|V,  S|1 standard action|15 ft.|Areacone-shaped burst|instantaneous|Reflex negates|no}[Performance deals 2d6 piercing damage.]
    \DeclareSpellDescription{Chord Of Shards}{During your bardic performance, you can strike a chord whose notes transform into a shower of razor sharp, crystalline shards. The shards deal 2d6 points of piercing damage to all creatures caught in the area of effect.}
        
\DeclareSpell{Circle Of Clarity}{abjuration () []|V,  S,  F (a crystal lens worth 100 gp)|1 standard action|medium (100 ft. + 10 ft./level)|Effect20-ft.-radius emanation centered on a creature, object, or point in space|1 round/level (D)|Will negates (harmless)|yes (harmless)}[Emanation hampers illusions and stealth.]
    \DeclareSpellDescription{Circle Of Clarity}{You create a magical emanation that interferes with all figments and glamers within it, giving creatures a +4 bonus on saving throws to recognize them as illusions. The emanation negates concealment less than total concealment within the area. Perception checks to notice creatures or objects within the area gain a bonus equal to half your caster level (maximum +10). The spell is stationary if cast on a point in space. It is mobile if centered on a creature or object, though creatures or attended objects can negate the spell with a saving throw or spell resistance.}
        
\DeclareSpell{Cold Ice Strike}{evocation () [cold]|V,  S|1 swift action|30 ft.|Area30-ft. line|instantaneous|Reflex half|yes}[Cone of ice slivers deals 1d6 cold/level.]
    \DeclareSpellDescription{Cold Ice Strike}{You create a shredding flurry of ice slivers, which blast from your hand in a line. The line deals 1d6 points of cold damage per caster level (maximum 15d6).}
        
\DeclareSpell{Compassionate Ally}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round/level|Will negates|yes}[Target is compelled to help injured ally.]
    \DeclareSpellDescription{Compassionate Ally}{At the sight of an injured ally, the target immediately disengages from its current course of action and rushes to provide aid. If the target possesses curative spells or magic items, it utilizes them to help the injured ally. If not, the target provides aid by performing a Heal check. The target remains with the injured ally to assure her safety and refuses to leave the ally's side until her wounds are fully treated or the spell ends, but can otherwise defend itself and make attacks.}
        
\DeclareSpell{Conjure Black Pudding}{conjuration (summoning) [acid]|V,  S,  M (a flask of acid worth 10 gp)|1 round|close (25 ft. + 5 ft./2 level)|Effectone summoned black pudding|1 round/level (D)|none|no}[Summon a black pudding.]
    \DeclareSpellDescription{Conjure Black Pudding}{You summon a black pudding (Bestiary 35) that immediately attacks creatures near it. You have no control over the creature, and it may attack you if there are no more obvious opponents. The black pudding is treated as a summoned creature and has the extraplanar subtype. The black pudding's split ability works normally, but all puddings derived from the summoned one disappear when the spell ends.}
        
\DeclareSpell{Contagion, Greater}{necromancy () [disease,  evil]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone living creature|instantaneous|Fortitude negates|yes}[Infect a subject with a magical disease.]
    \DeclareSpellDescription{Contagion, Greater}{This spell functions as contagion, except the victim cannot overcome the disease without magic-making the required number of saves does not cure it. The DC to remove the disease with magic is equal to the save DC + 5.}
        
\DeclareSpell{Control Construct}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone construct|concentration|none (see text)|no}[Take control of a construct.]
    \DeclareSpellDescription{Control Construct}{You wrest the control of a construct from its master. For as long as you concentrate, you can control the construct as if you were its master. You must make a Spellcraft check each round to maintain control. The DC of the Spellcraft check is (10 + the construct's HD). If the construct's creator or master is present and trying to control the construct, you both must make opposed Spellcraft checks each round to control the construct.}
        
\DeclareSpell{Control Summoned Creature}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone summoned creature|1 round/level|Will negates|yes}[Direct a summoned monster as if you had summoned it.]
    \DeclareSpellDescription{Control Summoned Creature}{You seize control of a summoned creature by disrupting the bond between it and the caster who summoned it. If the creature fails its save, you may command it as if you had summoned it. The original caster can attempt to regain control of the creature as a standard action by making an opposed Spellcraft check against you. When your spell ends, control reverts to the original summoner. If the summoning spell ends before this spell ends, the remaining duration of this spell is lost.}
        
\DeclareSpell{Corrosive Consumption}{conjuration (creation) [acid]|V,  S|1 standard action|touch|Targetscreature touched|3 rounds|none|yes}[Acidic patch damages an opponent.]
    \DeclareSpellDescription{Corrosive Consumption}{With a touch, this spell causes a small, rapidly growing patch of corrosive acid to appear on the target. On the first round, the acid deals 1 point of acid damage per caster level (maximum 15). On the second round, the acid patch grows and deals 1d4 points of acid damage per caster level (maximum 15d4). On the third and final round, the acid patch covers the entire creature and deals 1d6 points of acid damage per caster level (maximum 15d6). The target can spend a full-round action to scrape off the acid, or can wash it off with at least 1 gallon of liquid to halve the damage for that round and negate the remaining rounds of the spell.}
        
\DeclareSpell{Corrosive Touch}{conjuration (creation) [acid]|V,  S|1 standard action|touch|Targetscreature or object touched|instantaneous|none|yes}[Touch attack deals 1d4 acid/level.]
    \DeclareSpellDescription{Corrosive Touch}{Your successful melee touch attack deals 1d4 points of acid damage per caster level (maximum 5d4).}
        
\DeclareSpell{Countless Eyes}{transmutation () []|V,  S|1 standard action|touch|Targetscreature touched|1 hour/level|Will negates (harmless)|yes (harmless)}[Extra eyes give all-around vision.]
    \DeclareSpellDescription{Countless Eyes}{The target sprouts extra eyes all over its body, including on the back of its head. It gains all-around vision (Bestiary 2 294) and cannot be flanked.}
        
\DeclareSpell{Create Demiplane}{conjuration (creation) []|V,  S,  F (a forked metal rod worth at least 500 gp)|4 hours|0 ft.|Effectextradimensional demiplane, up to 10 10-ft. cubes/level (S)|1 day/level or instantaneous (see text)|none|no}[As lesser create demiplane, but larger and with planar traits.]
    \DeclareSpellDescription{Create Demiplane}{This spell functions as create lesser demiplane, except the area is larger and you can add more features to the plane. You can use this spell to expand a demiplane you created with create lesser demiplane (you do not need to create an entirely new plane using this spell), in which case it has a duration of 1 day/level. Alternatively, when cast within your demiplane, you may add (or remove) one of the following features to your demiplane with each casting of the spell, in which case it has an instantaneous duration.
Alignment: Your plane gains the (mildly) chaos-, good-, evil-, law-, or neutral-aligned alignment trait (see Alignment Traits, GameMastery Guide 187). You cannot give your demiplane an alignment trait for an alignment you do not have.
Bountiful: Your demiplane gains a thriving natural ecology, with streams, ponds, waterfalls, and plants. The demiplane provides enough plant-based food (nuts, grains, fruit, fungi, and so on) to support one Medium creature for every 10-foot cube of the demiplane. The demiplane does not have any animals unless you transport them there, but the ecology can sustain itself for as long as the demiplane exists without requiring watering, gardening, pollination, and so on, and dead organic material decays and returns to the soil in the normal manner. If your demiplane has ambient light, these plants are normal, familiar surface plants; if it is a realm of twilight or darkness, these plants are fungi and other plants adapted to near-darkness or underground locations.
Elemental: Your plane gains the air-, earth-, fire-, or water-elemental dominant trait (see Elemental and Energy Traits, GameMastery Guide 186).
Gravity: By default a demiplane's gravity is normal and oriented in one direction, like what most creatures are used to on the Material Plane. By selecting this feature, the plane's gravity is heavy, light, none, objectively directional, or subjectively directional (see Gravity, GameMastery Guide 184).
Seasonal: The demiplane has a seasonal cycle and a light cycle, usually similar to those of a land on the Material Plane, but customizable as you see fit (for example, your demiplane could always be winter, day and night could alternate every 4 hours, and so on).
Shape: By default, the demiplane has a fixed shape and borders. By selecting this feature, you may make your plane self-contained so it loops upon itself when a creature reaches one edge (see Shape and Size, GameMastery Guide 185). You may designate areas or locations on the edges of your plane where this occurs (such as a pair of secret doors or a path in the woods) or apply it to the entire plane.
Structure: Your demiplane has a specific, linked physical structure, such as a giant tree, floating castle, labyrinth, mountain, and so on. (This option exists so you can pick a theme for your plane without having to worry about the small details of determining what spells you need for every hill, hole, wall, floor, and corner).
You can make this spell permanent with the permanency spell, at a cost of 20,000 gp. If you have cast create demiplane multiple times to enlarge the demiplane, each casting's area requires its own permanency spell.}
        
\DeclareSpell{Create Demiplane, Lesser}{conjuration (creation) []|V,  S,  F (a forked metal rod worth at least 500 gp)|2 hours|0 ft.|Effectextradimensional demiplane, up to three 10-ft. cubes/level (S)|1 day/level|none|no}[Create your own demiplane.]
    \DeclareSpellDescription{Create Demiplane, Lesser}{You create a small, finite demiplane. You must be on the Astral or Ethereal Plane or on a plane that has access to one of those planes (such as the Material Plane) to cast this spell.
When you cast the spell, you decide whether the demiplane is within the Astral or the Ethereal Plane. It is filled with air or water (decided by you). The plane is generally flat and featureless, such as an earth, stone, water, or wood floor. The "walls" and "ceiling" of the plane may appear like solid earth, stone, wood, or water, or they may end in mist, a featureless void, or a similar unreal-looking border. The plane's environmental conditions are those of a temperate spring day on the Material Plane. You determine the plane's light level (bright, normal, dim, or darkness), which affects the entire plane.
There are no native creatures or plants on this plane, though you may bring some there (if the plane's light is bright or normal, it counts as sunlight for growing plants). The environment of the plane counts as normal terrain for the purpose of effects that target earth, stone, wood, and so on.
For example, you could use move earth to create a hill or wall of stone to create a barricade.
When you finish casting this spell, you may bring yourself and up to seven other creatures to the plane automatically by joining hands in a circle. The demiplane is another plane of existence, and therefore is outside the range of any spell or ability that cannot affect or reach other planes. Creatures can only enter the plane by the use of planar travel magic such as astral projection, etherealness, or plane shift. You are considered "very familiar" with your entire demiplane.
As a standard action, you may eject a creature from your demiplane. The creature may resist with a Will saving throw. An ejected creature goes to the closest plane to your demiplane (usually the Astral Plane or the Ethereal Plane, but if you cast this spell on the Material Plane, the creature is sent to the Material Plane). When the spell ends, the plane dissolves, and all creatures in the plane are ejected in this manner with no saving throw. The plane cannot be dispelled, but a creature on the plane can destroy it by using limited wish, mage's disjunction, miracle, or wish and making a successful dispel check.
If you are within the demiplane, you can add to its area by casting the spell again. Alternatively, you may cast this spell again to reset the duration of an existing area to that of your latest casting. If the duration on one area of the demiplane ends and other parts remain, creatures in the expiring area are shunted to remaining areas. If a collapsing portion of the demiplane would leave one section cut off from other sections of the demiplane (for example, if there were three areas connected in a straight line and the center part expired), the stranded sections count as separate demiplanes under your control. You may reconnect these stranded sections by the spell again to create a linked area between the two.
You can make this spell permanent with the permanency spell, at a cost of 17,500 gp. If you have cast create lesser demiplane multiple times to enlarge the demiplane, each casting's area requires its own permanency spell.}
        
\DeclareSpell{Create Demiplane, Greater}{conjuration (creation) []|V,  S,  F (a forked metal rod worth at least 500 gp)|6 hours|0 ft.|Effectextradimensional demiplane, up to 20 10-ft. cubes/level (S)|1 day/level or instantaneous (see text)|none|no}[As create demiplane, but larger and with more planar traits.]
    \DeclareSpellDescription{Create Demiplane, Greater}{This spell functions as create demiplane, except the area is larger and you can add more features to the plane. You can use this spell to expand a demiplane you created with lesser create demiplane or create demiplane (you do not need to create an entirely new plane using this spell), in which case it has aduration of 1 day/level. Alternatively, when cast within your demiplane, you may add to your demiplane (or remove from it) one of the following features (or any of the features described in create demiplane) with each casting of the spell, in which case it has an instantaneous duration.
Energy: Your plane gains the (minor) negative- or positivedominant energy trait (see Elemental and Energy Traits, GameMastery Guide 186). A plane cannot have both the negative-dominant and positive-dominant energy traits.
Magic: Your plane gains the dead magic, enhanced magic, impeded magic, or wild magic planar trait (see Magic Traits, GameMastery Guide 187). If you selected dead magic, you are trapped within your plane unless it has a permanent planar portal (such as the portal feature, below). If you selected enhanced or impeded magic, choose one type of magic to be enhanced or impeded, such as "effects with the fire descriptor or that manipulate fire" or "death spells and spells from the Death or Repose domains." A plane cannot be enhanced and impeded for the same kinds of spells.
Morphic: You may use move earth at will in your demiplane at one-tenth of the spell's normal casting time, and can reshape normal plants in the same manner (such as by twisting trees into a fence or humanlike shapes). You are even able to affect rock formations with this ability, though the casting time for this is only half normal.
Portal: Your demiplane gains a permanent gate to one location on another plane, which can only be used for planar travel. This location must be very familiar to you.
This gate is always open and usable from both sides, but you can secure it using normal means (such as by building a door around it).
Time: By default, time passes at the normal rate in your demiplane. By selecting this feature, you may make your plane have the erratic time, flowing time (half or double normal time), or timeless trait (see Time, GameMastery Guide 185).
You can make this spell permanent with the permanency spell, at a cost of 22,500 gp. If you have cast create greater demiplane multiple times to enlarge the demiplane, each casting's area requires its own permanency spell.}
        
\DeclareSpell{Curse, Major}{necromancy () [curse]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|permanent|Will negates|yes}[As bestow curse, but harder to remove.]
    \DeclareSpellDescription{Curse, Major}{This spell functions as bestow curse, except the DC to remove the curse is equal to the save DC + 5.}
        
\DeclareSpell{Curse Of Disgust}{enchantment (compulsion) [curse,  emotion,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|permanent|Will negates|yes}[Target is sickened when viewing a trigger.]
    \DeclareSpellDescription{Curse Of Disgust}{You place a curse upon a creature, causing it to avoid the sight of a specific trigger, which is a kind of creature, object, or condition designated by you. When the target is within 30 feet of a trigger and is aware of the trigger, it gains the sickened condition and feels an urge to leave. A successful Will save negates the urge to leave, but the sickened condition persists as long as the target is within 30 feet of a trigger and aware of it. Example triggers include beggars, filthy clothing, diseased creatures, the king, blood, spiders, rats, corpses, and sewage.}
        
\DeclareSpell{Curse of Magic Negation}{abjuration () [curse]|V,  S,  M (powdered lead and platinum worth 250 gp)|1 round|medium (100 ft. + 10 ft./level)|Targetsone creature|10 minute/level|Will negates|no}[Target gains the negated spellblight.]
    \DeclareSpellDescription{Curse of Magic Negation}{You disrupt the target creature's ability to draw upon magical energies. For the duration of the spell, it gains the negated spellblight (see page 97). Dispel checks to remove the spellblight take a -5 penalty due to this spell's interference with magical energies.}
        
\DeclareSpell{Cursed Earth}{necromancy () [curse,  evil; see text]|V,  S,  M (powdered onyx 10, 000 gp),  DF|10 minutes|touch|Area1-mile radius emanating from the touched point|permanent|none (see text)|no}[Plants die, living creatures catch diseases, or dead creatures rise as zombies.]
    \DeclareSpellDescription{Cursed Earth}{You lay a terrible curse upon the land, blighting those who live and die there. Choose one of the following effects.
Famine: All normal plants in the area reduce their growth and food production by half, as if affected by the stunt growth effect of diminish plants.
Living Death: Any creatures of Small size or larger killed in the area rise as uncontrolled zombies 24 hours after their death, as do corpses buried in the area. Burning or dismembering the corpses prevents them from rising as zombies.
Plague: Every day at sundown, all creatures in the area must make a Fortitude save or catch one of the following diseases (your choice, decided at the time of casting): blinding sickness, bubonic plague, cackle fever, filth fever, leprosy, mindfire, red ache, shakes, or slimy doom. The disease is contracted immediately (the onset period does not apply). Use the disease's listed frequency and save DC to determine further effects. This is a disease effect.}
        
\DeclareSpell{Cushioning Bands}{conjuration (creation) [force]|V,  S, |1 standard action|touch|Targetscreature touched|1 hour/level or until discharged (D)|Will negates (harmless)|yes}[Force bands protect against crushing.]
    \DeclareSpellDescription{Cushioning Bands}{Invisible bands of force encircle vital areas of the target. The bands resist crushing forces and impacts without interfering with movement. The target gains DR 2/piercing or slashing and takes half damage from constriction, falling, and being buried, as well as from similar crushing effects such as crushing hand. Grapple checks for attacks other than constricting (such as pinning or swallowing whole) are not affected. Once the spell has blocked 12 points of damage per caster level (to a maximum of 120 points at 10th level), it is discharged. The bands have no effect on incorporeal attacks unless they deal damage from constriction or crushing, or unless the attacks would be subject to damage reduction.}
        
\DeclareSpell{Dance of a Hundred Cuts}{transmutation () []|V|1 standard action|personal|Targetsyou|1 round/level||}[Gain +1 combat bonus/3 levels.]
    \DeclareSpellDescription{Dance of a Hundred Cuts}{You become a lethal combat dancer, swirling and spinning with grace and precision. You gain a morale bonus on melee attack rolls, melee damage rolls, and Acrobatics checks, and to Armor Class. This bonus is equal to +1 per 3 caster levels (maximum +5 at 15th level). The bonus to AC is lost under any circumstances that would cause you to lose your Dexterity bonus to AC. You must remain moving for the spell to stay in effect. If in any round you do not either move at least 10 feet or make a melee attack, the spell's duration ends.}
        
\DeclareSpell{Dance of a Thousand Cuts}{transmutation () []|V|1 standard action|personal|Targetsyou|1 round/level||}[As dance of a hundred cuts, plus the benefits of haste.]
    \DeclareSpellDescription{Dance of a Thousand Cuts}{This spell functions as dance of a hundred cuts, except you also gain the benefits of haste.}
        
\DeclareSpell{Darkvision, Greater}{transmutation () []|V,  S,  M (either a pinch of dried carrot or an agate)|1 standard action|touch|Targetscreature touched|1 hour/level|Will negates (harmless)|yes (harmless)}[See 120 ft. in total darkness.]
    \DeclareSpellDescription{Darkvision, Greater}{This spell functions as darkvision, except the target's darkvision has a range of 120 feet.}
        
\DeclareSpell{Daze, Mass}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone or more humanoid creatures, no two of which  may be more than 30 ft. apart|1 round|Will negates|yes}[As daze, but affecting multiple creatures.]
    \DeclareSpellDescription{Daze, Mass}{This spell functions as daze, except as noted above.}
        
\DeclareSpell{Decompose Corpse}{necromancy () []|V,  S,  M (a pinch of dried toadstool)|1 standard action|touch|Targetsone corpse or corporeal undead|instantaneous or 1 minute; see text|Fortitude negates (object)|yes (object)}[Turn a corpse into a clean skeleton.]
    \DeclareSpellDescription{Decompose Corpse}{Using this spell, the caster rapidly decomposes the flesh from a single corpse of size Huge or smaller, leaving behind a perfectly cleaned skeleton. If it is cast on a non-skeletal corporeal undead, the creature takes a -2 penalty on all rolls and to its Armor Class and CMD for 1 minute.}
        
\DeclareSpell{Defensive Shock}{evocation () [electricity]|V,  S,  M (a hollow metal sphere)|1 standard action|personal|Targetsyou|1 minute/level or until discharged||}[Electricity damages your attackers.]
    \DeclareSpellDescription{Defensive Shock}{Electrical energy floods your body, shocking the next creature that touches you. Any creature striking you with its body or a handheld weapon takes 1d6 points of electricity damage per two caster levels (maximum 6d6). If the attacker has spell resistance, it applies against this damage. Each time the spell discharges, the number of damage dice it deals is halved (rounded down); when the spell's damage dice reach 0, the spell ends.}
        
\DeclareSpell{Delay Pain}{enchantment () [emotion]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 hour/level|Will negates|yes}[Ignore pain for 1 hour/level.]
    \DeclareSpellDescription{Delay Pain}{You override the target's ability to feel pain. Pain effects (such as pain strike** and symbol of pain) do not affect the target until this spell's duration has expired. This does not negate any physical damage, ability damage, or ability drain that a pain effect has already done, but it does negate ongoing penalties from pain while the spell lasts.}
        
\DeclareSpell{Delusional Pride}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 minute|Will negates|yes}[Target is penalized on attacks and checks but gains bonus against charms and compulsions.]
    \DeclareSpellDescription{Delusional Pride}{The target becomes so distracted by an overblown sense of its worth that it takes a -2 penalty on attacks and skill checks.
However, this feeling also gives the target a +2 morale bonus on saves against charm and compulsion effects.}
        
\DeclareSpell{Diagnose Disease}{divination () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Areaone creature, one object, or a 5-ft. cube|instantaneous|none|no}[Detect and identify diseases.]
    \DeclareSpellDescription{Diagnose Disease}{You determine whether a creature, object, or area carries any sort of disease or infestation (including molds, slimes, and similar hazards), or any exceptional or supernatural effects causing the sickened or nauseated effects. If there is disease present, you know what disease it is and its effects. If the target is a creature, you gain a +4 bonus on Heal checks to treat the creature's disease. The spell can penetrate many barriers, but 1 foot of stone, 1 inch of common metal, a thin sheet of lead, or 3 feet of wood or dirt blocks it.}
        
\DeclareSpell{Disfiguring Touch}{transmutation () [curse]|V,  S|1 standard action|touch|Targetscreature touched|1 day/level|Will negates|yes}[Target becomes disfigured.]
    \DeclareSpellDescription{Disfiguring Touch}{With a touch, you cause the victim of this spell to suffer a painful curse that causes it to grow hideously disfigured. The physical appearance of the deformity is subject to the caster's whim (most demon worshipers choose deformities that reflect their Abyssal patron's shape or form). The target takes one of the following penalties.   -2 decrease to an ability score (minimum 1).   -2 penalty on attack rolls or saving throws.   Land speed reduced by 5 feet.  You may also invent other effects, but they should be no more powerful than those described above.}
        
\DeclareSpell{Disguise Other}{illusion (glamer) []|V,  S|1 standard action|touch|Targetscreature touched|10 minute/level (D)||}[As disguise self, but affects you or another.]
    \DeclareSpellDescription{Disguise Other}{This spell functions as disguise self, except you can disguise either yourself or another creature.}
        
\DeclareSpell{Distracting Cacophony}{evocation () [sonic]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Area20-ft. spread|1 round/level (D)|none|yes}[Noise makes it difficult to cast.]
    \DeclareSpellDescription{Distracting Cacophony}{The air fills with loud and discordant noise, making concentration difficult. Casting a spell in this area of cacophony requires a concentration check (DC 15 + the level of the spell being cast). Any other concentration checks in the area have their DCs increased by 5. The DC of Perception checks involving hearing is likewise increased by 5.}
        
\DeclareSpell{Distressing Tone}{evocation () [sonic]|V,  S|1 round|close (25 ft. + 5 ft./2 levels)|Targets1d4 living creatures|1 round/level|Fortitude negates|yes}[Sound sickens 1d4 creatures.]
    \DeclareSpellDescription{Distressing Tone}{You create a powerful tone that vibrates living flesh. Targets must save or gain the sickened condition. Creatures that are immune to critical hits are immune to this spell.}
        
\DeclareSpell{Divine Pursuit}{transmutation () []|V,  S|1 standard action|personal|Targetsyou|1 minute/level; see text||}[Gain a movement type of your prey.]
    \DeclareSpellDescription{Divine Pursuit}{Select one creature within 60 feet that you have damaged. If that creature has a burrow, climb, fly, or swim speed, you gain that form of movement for the duration of the spell at the same speed and maneuverability as the selected creature. If this gives you the burrow or swim speed, you can breathe while burrowing or swimming. If the creature moves 1,000 feet or more from you, the spell ends. If the creature has more than one of these types of movement, you select one from the types available to the creature.}
        
\DeclareSpell{Dread Bolt}{evocation () [evil]|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectarrow-shaped projectile of evil energy|instantaneous (1d4 rounds)|Will partial (see text)|yes}[Harm and possibly sicken good creatures.]
    \DeclareSpellDescription{Dread Bolt}{You unleash a crackling missile of darkness from your unholy symbol at any one target in range as a ranged touch attack.
A good creature struck by dread bolt takes 1d8 points of damage per two caster levels (maximum 5d8). A good outsider instead takes 1d6 points of damage per caster level (maximum 10d6) and is sickened for 1 round. A successful Will save reduces the damage to half and negates the sickened effect. This spell deals only half damage to creatures that are neither good nor evil, and they are not sickened. The bolt has no effect on evil creatures.}
        
\DeclareSpell{Eagle Aerie}{conjuration (summoning) [good]|V,  S,  DF|1 round|long (400 ft. + 40 ft./level)|Effectsummoned eagles|1 hour/level|none|no}[Summon 1 giant eagle/3 levels.]
    \DeclareSpellDescription{Eagle Aerie}{You summon a flight of giant eagles (one per three caster levels, maximum of six; Bestiary 118) to ferry you and your allies across the skies. The eagles avoid combat if possible but defend themselves if attacked; if the eagles attack, the remaining duration of the spell changes from 1 hour per level to 1 round per level (so if the spell had 5 full hours left, the eagles remain in combat for 5 rounds before the spell ends).}
        
\DeclareSpell{Ear-Piercing Scream}{evocation () [sonic]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|instantaneous; see text|Fortitude partial (see text)|yes}[Deal sonic damage and daze target.]
    \DeclareSpellDescription{Ear-Piercing Scream}{You unleash a powerful scream, inaudible to all but a single target. The target is dazed for 1 round and takes 1d6 points of sonic damage per two caster levels (maximum 5d6). A successful save negates the daze effect and halves the damage.}
        
\DeclareSpell{Echolocation}{transmutation () [sonic]|V|1 standard action|personal|Targetsyou|10 minutes/level||}[Sonic sense gives you blindsight 40 ft.]
    \DeclareSpellDescription{Echolocation}{You can perceive the world by creating high-pitched noises and listening to their echoes. This gives you blindsight to a range of 40 feet. The echo-producing noises are too highpitched to be heard by most creatures, and can only be detected by dragons, other creatures with this ability (such as bats), and creatures with hearing-based blindsense or blindsight. You cannot use this ability if you are deaf, and cannot detect anything in an area of silence.}
        
\DeclareSpell{Eldritch Fever}{necromancy () [curse,  disease,  evil]|V,  S|1 standard|close (25 ft. + 5 ft./2 levels)|Targetsone creature|instantaneous|Fortitude negates|yes}[Target gains the eldritch ague spellblight.]
    \DeclareSpellDescription{Eldritch Fever}{The target gains the eldritch ague spellblight (see page 96).}
        
\DeclareSpell{Envious Urge}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone creature/level, no two of which can be more than 30 ft. apart|1 round/level|Will negates|yes}[Targets steal from or disarm others.]
    \DeclareSpellDescription{Envious Urge}{You fill creatures with feelings of seething envy. Affected targets turn upon the nearest creature (whether an ally or enemy) and attempt to disarm it of a valuable weapon, steal something it is holding, or grapple it and strip it of something it prizes (your choice). Affected targets can attempt a new Will save each round as a free action to end this effect.}
        
\DeclareSpell{Epidemic}{necromancy () [disease,  evil]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsliving creature|instantaneous|Fortitude negates|yes}[Infect a subject with a highly contagious disease.]
    \DeclareSpellDescription{Epidemic}{The target contracts one of the following diseases: blinding sickness, bubonic plague, cackle fever, filth fever, leprosy, mindfire, red ache, shakes, or slimy doom (Core Rulebook 557), as the spell contagion. However, the disease is highly contagious, and any creature that touches the infected target, is touched by the target, or spends more than an hour in a confined space with the target must make a save against the disease's normal DC (not the spell DC) or contract the disease. If the initial target overcomes the disease by making the required number of saving throws, it remains a carrier of the disease for a length of time equal to the disease's frequency, and can continue to infect others during this time.}
        
\DeclareSpell{Eruptive Pustules}{transmutation () [acid]|V,  S|1 standard action|personal|Targetsyou|1 minute/level (D)|Fortitude partial (see text)|yes}[Acid boils burst when you are attacked.]
    \DeclareSpellDescription{Eruptive Pustules}{Your skin erupts in swollen, pus-filled bumps that burst open if you are struck. Any creature that strikes you with its body or a hand-held weapon deals normal damage, but at the same time the attacker takes 1d6 points of acid damage and must save or be sickened for 1 round. If the attack against you is a critical hit, the attacker must save or be nauseated instead of sickened. This damage can harm a swarm.}
        
\DeclareSpell{Excruciating Deformation}{transmutation (polymorph) [evil,  pain]|V,  S|1 standard action|touch|Targetscreature touched|1 round/level|Fortitude partial (see text)|yes}[Target takes Dex and Con damage.]
    \DeclareSpellDescription{Excruciating Deformation}{Your touch attack causes your target to become painfully malformed. Its limbs twist and buckle, while its body contorts uncontrollably, shifting and warping. Each round the target suffers excruciating pain and takes 2d6 points of nonlethal damage, 1 point of Dexterity damage, and 1 point of Constitution damage, and its speed is reduced by 10 feet. Once per round as a free action on its turn, the target can attempt a new Fortitude saving throw to resist the spell for 1 round.}
        
\DeclareSpell{Exquisite Accompaniment}{illusion (shadow) [shadow]|V,  S|1 standard action|personal|Effectphantom instrument|1 round/level (D)|none|no}[Instrument maintains bardic performance for you.]
    \DeclareSpellDescription{Exquisite Accompaniment}{You create a phantom instrument, a glowing construct of magic in the form of a portable musical instrument of your choice. The instrument floats beside you, moving as you move (even if you teleport). It cannot be damaged, but can be dispelled. The instrument plays as you direct, and as long as it plays, you do not have to expend rounds of bardic performance from your daily allotment to maintain an effect.
Activating a bardic performance or switching to a new still costs a round of your overall bardic performances per day.}
        
\DeclareSpell{False Life, Greater}{necromancy () []|V,  S,  M (a drop of blood)|1 standard action|personal|Targetsyou|1 hour/level or until discharged; see text||}[Gain 2d10 temporary hp + 1/level.]
    \DeclareSpellDescription{False Life, Greater}{This spell functions as false life, except you gain temporary hit points equal to 2d10 + 1 point per caster level (maximum +20). The effects of this spell do not stack with those of false life.}
        
\DeclareSpell{Familiar Melding}{necromancy () []|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targetsyour familiar|1 hour/level or until you return to your body|Will negates (harmless)|yes}[Possess your familiar.]
    \DeclareSpellDescription{Familiar Melding}{You project your soul into your familiar, taking over its body while leaving its consciousness intact. When you transfer your soul upon casting, your body is, as near as anyone can tell, dead.
While possessing your familiar, you can communicate with it telepathically. You keep your Intelligence, Wisdom, Charisma, level, class, base attack bonus, base save bonuses, alignment, and mental abilities. The familiar's body retains its own Strength, Dexterity, Constitution, hit points, natural abilities, and automatic abilities. A body with extra limbs does not allow you to make more attacks (or more advantageous twoweapon attacks) than normal. You may use any abilities the familiar has, including spells and spell-like abilities. You cannot speak unless your familiar has the ability to speak a language. You cannot cast spells with somatic components if your familiar does not have anthropomorphic limbs that can perform the appropriate motions.
As a standard action, you can return to your body as long as it is within range. If your familiar is slain while your soul is in it and your body is within range, your soul returns to your own body, unharmed. If your familiar is out of range when slain, you die.
The spell ends when you shift from the familiar to your own body.}
        
\DeclareSpell{Fickle Winds}{transmutation () [air]|V,  S|1 standard action||Targetsone or more Medium creatures/level, no two of which can be more than 30 ft. apart|1 minute/level (D)|none (see text)|yes}[Wind walls selectively block attacks.]
    \DeclareSpellDescription{Fickle Winds}{You create a mobile cylinder of wind encompassing every target of the spell and protecting them as wind wall, but not interfering with them in any way. For example, arrows and bolts fired at the targets are deflected upward and miss, but the targets' own arrows or bolts pass through the wall as if it were not there.
A Large creature counts as 4 Medium creatures for the purpose of how many targets you can effect with the spell; a Huge creature counts as 8, a Gargantuan creature as 16, and a Colossal creature as 32. This spell has no effect within the area of a higher-level wind or weather spell.}
        
\DeclareSpell{Fleshworm Infestation}{conjuration (summoning) [evil]|V,  S|1 standard action|touch|Targetscreature touched|1 round/level (D)|Fortitude partial (see text)|yes}[Worms deal hp and Dex damage.]
    \DeclareSpellDescription{Fleshworm Infestation}{With a touch, you cause an infestation of ravenous worms to manifest in the target's flesh. The target must make a Fortitude save every round. Failure means it takes 1d6 hit points of damage and 2 points of Dexterity damage, and is staggered for 1 round. If it makes the save, it takes no hit point or Dexterity damage and is only sickened for 1 round rather than staggered. Fleshworm infestation cannot be ended early by remove disease or heal, as the infestation starts anew if the current worms are slain. Protection from evil negates this spell's effects for as long as the two durations overlap.
Dispel evil automatically ends a fleshworm infestation.}
        
\DeclareSpell{Forbid Action}{enchantment (compulsion) [language-dependent,  mind-affecting]|V|1 standard action|close (25 ft. +5 ft./2 levels)|Targetsone creature|1 round|Will negates|yes}[Target obeys your command to not do something.]
    \DeclareSpellDescription{Forbid Action}{You forbid the target a single course of action, which it avoids to the best of its ability. You may demand the target not take actions that fall into one of the following options.
Attack: The target cannot take any action that involves an attack roll, or uses a spell or ability that targets a foe or an area that includes a foe.
Cast: Target cannot cast spells or use spell-like abilities.
Communicate: The target cannot take any actions that allow it to communicate with anyone. This includes such acts as speaking, Bluff checks to pass secret messages, writing, and using telepathy. It does not prevent verbalizations made for purposes other than communication, such as command words or the verbal component of spellcasting.
Draw: Target cannot ready or prepare any item, weapon, component, or equipment.
Move: The target can take no act that would cause it to end up in a different location. The target does not resist being moved by others (and thus can be picked up or dragged, or can float along on a raft), but does not consciously attempt to move (including not directing a mount to move).
The target is free to take any actions not forbidden by the caster. For example, a target affected by this spell's demand to not move is still free to cast spells, make attacks, or shout for help.}
        
\DeclareSpell{Forbid Action, Greater}{enchantment (compulsion) [language-dependent,  mind-affecting]|V|1 standard action|close (25 ft. +5 ft./2 levels)|Targetsone creature/level, no two of which can be more than 30 ft. apart|1 round/level|Will negates|yes}[As forbid action, but 1 creature/level.]
    \DeclareSpellDescription{Forbid Action, Greater}{This spell functions as forbid action, except up to one creature per level may be affected. Each creature must receive the same forbidden action.}
        
\DeclareSpell{Force Hook Charge}{evocation () [force]|V,  S|1 standard action|close (25 feet + 5 feet/2 levels)|Targetsone creature or object within range and you|instantaneous|none|yes}[Hook of force drags you to the target.]
    \DeclareSpellDescription{Force Hook Charge}{You create a hook of force that strikes the target and drags you to a space adjacent to it. Make a ranged touch attack against the target; if the touch attack succeeds, the target takes 1 point of force damage per caster level. Whether or not the touch attack hits, the force hook drags you in a straight line to a square adjacent to the target. This movement provokes attacks of opportunity as normal. The pulling hook keeps you from falling as part of this movement; therefore you can use it to cross a pit or chasm, or reach a higher or lower elevation. If the line of effect from you to the target passes through an area that is too small to fit your body (such as a portcullis or arrow slit), the hook pulls you to that location and you take damage as if you had fallen the distance from your starting point to that location. If you are restrained, such as being chained to a wall, the hook pulls you to the maximum extent of your restraints but does not break the restraints.
If your travel to the destination is not blocked, you land on your feet, unharmed by the sudden motion. However, the spell does not guarantee you a safe landing space when you arrive. For example, if your target is flying or on a ledge with no room for you to stand, once the hook pulls you adjacent to the target, you begin to fall.
If you use this spell with your spell combat class ability, you can make your melee attack from your starting position or your ending position.}
        
\DeclareSpell{Force Punch}{evocation () [force]|V,  S|1 standard action|touch|Targetscreature touched|instantaneous|Fortitude partial|yes}[Target takes 1d4 force damage per level and is pushed away.]
    \DeclareSpellDescription{Force Punch}{This spell charges your hand with telekinetic force. Your successful melee touch attack deals 1d4 points of force damage per level (maximum 10d4) and causes the target to be pushed away from you in a straight line up to 5 feet per two caster levels. For every size category of the target above Medium, reduce the distance pushed by 5 feet (-5 feet for Large, -10 feet for Huge, -15 for Gargantuan, and -20 feet for Colossal) to a minimum of 0 feet. A successful Fortitude save negates the movement but not the damage.}
        
\DeclareSpell{Forced Quiet}{transmutation () [sonic]|S|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone creature|1 round/level|Will negates|yes}[Target cannot make loud noises.]
    \DeclareSpellDescription{Forced Quiet}{With a gesture, you muffle sound around the target, making it unable to yell or otherwise make loud noises. This does not affect spellcasting by the target. The target can still use sonic effects, but the DC of these effects decreases by 2. The target gains a +2 bonus on saving throws against sonic effects. The target gains a +4 circumstance bonus on Stealth checks.}
        
\DeclareSpell{Frigid Touch}{evocation () [cold]|V,  S|1 standard action|touch|Targetscreature touched|instantaneous|none|yes}[Target takes cold damage and is staggered.]
    \DeclareSpellDescription{Frigid Touch}{This spell causes your hand to glow with a pale blue radiance. Your melee touch attack deals 4d6 points of cold damage and causes the target to be staggered for 1 round.
If the attack is a critical hit, the target is staggered for 1 minute instead.}
        
\DeclareSpell{Frostbite}{transmutation () [cold]|V,  S|1 standard action|touch|Targetscreature touched|instantaneous|none|yes}[Target takes cold damage and is fatigued.]
    \DeclareSpellDescription{Frostbite}{Your melee touch attack deals 1d6 points of nonlethal cold damage + 1 point per level, and the target is fatigued. The fatigued condition ends when the target recovers from the nonlethal damage. This spell cannot make a creature exhausted even if it is already fatigued. You can use this melee touch attack up to one time per level.}
        
\DeclareSpell{Fumbletongue}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|close (25 ft. +5 ft./2 levels)|Targetsone creature|1d4 rounds|Will negates|yes}[Target cannot speak intelligently.]
    \DeclareSpellDescription{Fumbletongue}{This enchantment causes a creature to be unable to speak intelligibly. Any effort the target makes to talk, in any language, comes out as a useless mix of unconnected words and noises. Even magic words are affected to some extent; the target has a 20\% spell failure chance for any spell it attempts to cast with verbal components, and a 20\% chance to incorrectly use a command word to activate a magic item.
This spell has no effect on telepathic communication, or the vocalizations of creatures that lack a spoken language.}
        
\DeclareSpell{Fungal Infestation}{necromancy () [disease]|V,  S|1 standard action|touch|Targetscreature touched|1d3 days|Fortitude negates|yes}[Target takes bleed from attacks.]
    \DeclareSpellDescription{Fungal Infestation}{You coat the target in necrotic fungus that makes its flesh soft and fragile. Toadstools, ringworm, and other disgusting fungal growths sprout from its skin. The target takes 1d3 points of Charisma damage. Any physical attack against the target automatically adds 1d6 points of bleed damage.}
        
\DeclareSpell{Ghostly Disguise}{illusion (glamer) []|V,  S|1 standard action|personal|Targetsyou|10 minute/level (D)||}[You look like a ghost of yourself.]
    \DeclareSpellDescription{Ghostly Disguise}{You make yourself-including clothing, armor, weapons, and equipment-appear translucent like a ghost. Any mundane or magical disguise on you is affected by this illusion as well; for example, if you are disguised as the king or a sahuagin, you look like a ghostly version of the king or a sahuagin. Your ghostly form may have a pale green, blue, or violet coloration, or a muted version of your normal appearance.
The spell does not actually make you ghostly or provide any incorporeal abilities. If you choose, the illusion can make you appear to float slightly above the ground, though you are actually still on the ground. A creature that interacts with the glamer gets a Will save to recognize it as an illusion.}
        
\DeclareSpell{Haunting Choir}{necromancy () [mind-affecting,  pain]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Area30-ft.-radius emanation|concentration + 2 rounds|Will negates|yes}[Spirits cause wracking pain to listeners.]
    \DeclareSpellDescription{Haunting Choir}{You create a spectral choir and conduct its tortured, ghostly moans, deluding listeners into believing they are suffering the torments of the dead.
The transparent singers occupy a 10-foot cube, but they are intangible and do not interfere with creatures in any physical way, nor can they be attacked.
Creatures within 30 feet of the choir experience wracking pain that causes them to take a -2 penalty on attack rolls, skill checks, and ability checks.
Individuals who exit the area of effect take these penalties for an additional 2 rounds before the delusion wears off.}
        
\DeclareSpell{Haunting Mists}{illusion (figment) [fear,  shadow]|V,  S|1 standard action|20 ft.|Effectcloud spreads in 20-ft. radius, 20 ft. high|1 minute/level (D)|Will partial (see text)|no}[Creatures are shaken and take Wis damage.]
    \DeclareSpellDescription{Haunting Mists}{An illusion of misty vapor inhabited by shadowy shapes arises around you. It is stationary. The illusory mist obscures all sight, including darkvision, beyond 5 feet. A creature 5 feet away has concealment (attacks have a 20\% miss chance).
Creatures farther away have total concealment (50\% miss chance, and the attacker cannot use sight to locate the target).
All creatures within the mist must save or take 1d2 points of Wisdom damage and gain the shaken condition. The shaken condition lasts as long as the creature remains in the mist.}
        
\DeclareSpell{Hex Ward}{abjuration () []|V,  S|1 standard action|touch|Targetscreature touched|1 hour/level|Will negates (harmless)|yes (harmless)}[Target gains +4 on saves against witch hexes.]
    \DeclareSpellDescription{Hex Ward}{You give the target a +4 resistance bonus on saving throws against witch hexes.}
        
\DeclareSpell{Holy Ice}{transmutation () [cold,  good,  water]|V,  S,  M (a flask of holy water or 5 pounds of powdered silver worth 25 gp)|1 standard action|medium (100 ft. + 10 ft./level)|Effectwall of ice or flying ice javelins (see text)|1 minute/level, instantaneous, or until expended (see text)|Reflex negates or none (see text)|yes}[Create wall or javelins of frozen holy water.]
    \DeclareSpellDescription{Holy Ice}{This spell creates a large mass of frozen holy water that can be used for one of two effects.
Holy Ice Wall: This functions like wall of ice (hemisphere or plane). Any creature that takes damage from holy water takes 1 point of damage every time it touches or attacks the ice wall with melee attacks; extended contact with the wall (such as standing or walking on it) deals 1d6 points of damage. Even when the ice has been broken through, a sheet of frigid holy air remains. Any creature that steps through it (including the one who broke through the wall) takes 1d6 points of damage + 1 point per caster level (no save); half of this damage is cold damage, half is damage from holy water (creatures unharmed by holy water do not take the damage).
Holy Ice Javelins: The spell creates a number of javelins of frozen holy water in your square equal to your caster level (maximum 15), which hurl themselves toward one or more targets that are no more than 10 feet away from each other.
You must succeed on attack rolls (one per javelin) to hit the target with the javelin, using your base attack bonus + your Wisdom modifier. The javelins deal 1d6 damage each, plus 1 point of cold damage and 1 point of damage from holy water.
The javelins are destroyed by this attack.}
        
\DeclareSpell{Holy Shield}{abjuration () []|V,  S|1 standard action|personal|Targetsyou|10 minutes/level|none|no}[Lend your shield's protection to another.]
    \DeclareSpellDescription{Holy Shield}{You gain the ability to magically project the defense of your shield to protect another creature at a distance. As a swift action, you designate one target within 30 feet. The target gains your shield's shield bonus and enhancement bonus to Armor Class until your next turn; you gain no benefit from the shield's shield bonus or enhancement bonus while using this spell and cannot use any of the shield's other properties or abilities (such as magical abilities, making a shield bash, or providing cover with a tower shield). As a swift action, you may move the protection to another target (including yourself); if you move the protection to yourself, you may use any of the shield's properties or abilities as normal. If the shielded creature exceeds the 30-foot range, your shield's protection automatically reverts to you. Any circumstance that would make you lose your shield bonus (such as an enemy breaking the shield, you dropping the shield, or you becoming helpless or unconscious) means the protected creature loses the shield's benefit.}
        
\DeclareSpell{Horn of Pursuit}{evocation () [sonic]|S|1 standard action|personal|Effect3 peals of a horn|1 round|none|no}[Create three notes heard miles away.]
    \DeclareSpellDescription{Horn of Pursuit}{You create the sound of a large hunting horn, blowing up to three notes as loud as a roaring dragon. These notes can be heard up to 2 miles away in typical outdoor conditions.
You can make these sounds at any point during the spell's duration as a free action, and each sounding can be short or long, allowing you to send very simple coded messages.}
        
\DeclareSpell{Howling Agony}{necromancy () [death,  pain]|V,  S,  M (a needle and a dried eyeball)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone living creature/level, no two of which can be more than 30 ft. apart|1 round/level|Fortitude negates|yes}[Screaming pain limits the target's actions.]
    \DeclareSpellDescription{Howling Agony}{You send wracking pains through the targets' bodies. Because of the pain, affected creatures take a -2 penalty to AC, attacks, melee damage rolls, and Reflex saving throws, and must succeed at a concentration check (DC equal to the DC of this spell) to cast spells. However, if an affected creature spends a move action screaming as loudly as possible, it can act without any other penalties for the remainder of its turn. "Screaming," for the purposes of this spell, includes any vocalization of pain or its telepathic equivalent; creatures that cannot scream (such as creatures without the natural ability to communicate or vocalize) suffer the full effect of the spell.}
        
\DeclareSpell{Ice Body}{transmutation () [cold]|V,  S|1 standard action|personal|Targetsyou|1 minute/level (D)||}[Your body becomes living ice.]
    \DeclareSpellDescription{Ice Body}{Your form transmutes into living ice, granting you several abilities. You gain the cold subtype and damage reduction 5/ magic. You are immune to ability score damage, blindness, critical hits, deafness, disease, drowning, electricity, poison, stunning, and all spells or attacks that affect your physiology or respiration, because you have no physiology or respiration while this spell is in effect. You cannot drink (and thus can't use potions) or play wind instruments.
Your unarmed attack deals damage equal to a club sized for you (1d4 for Small characters or 1d6 for Medium characters) plus 1 point of cold damage, and you are considered armed when making unarmed attacks. You may burrow through nonmagical ice or snow at your base speed as easily as a fish swims through water. You can move through magical ice and snow if you succeed on a caster level check (1d20 + caster level) against a DC of 11 + the caster level of the effect; you automatically succeed on caster level checks against effects that you created. Your passage through snow and ice in this fashion leaves behind no tunnel or hole.}
        
\DeclareSpell{Ice Crystal Teleport}{conjuration (teleportation) [cold]|V|1 standard action|long (400 ft. + 40 ft./level)|Targetsone creature|1d4 rounds and instantaneous|Will negates|yes}[Target is frozen, then teleported.]
    \DeclareSpellDescription{Ice Crystal Teleport}{This spell functions as teleport, except you use it to teleport yourself or one other creature to a safe location you specify (the target can bring along objects as long as their weight doesn't exceed the target's heavy load). You can only send the target to a location with which you are very familiar. The target is first trapped in ice (hardness 0, 3 hit points per inch of thickness, 1 inch thick per caster level) for 1d4 rounds, during which time it is paralyzed, aware but unable to take any physical actions, and begins to fade away as the teleportation aspect takes effect. At the end of the 1d4 rounds, the target teleports to the specified location, and the ice's hit points drop to 0 and it quickly melts away. If the ice is destroyed before the target teleports, the spell ends and the teleport doesn't occur.}
        
\DeclareSpell{Icicle Dagger}{conjuration (creation) [cold]|V,  S|1 standard action|0 ft.|Effectone icicle|1 minute/level|none|no}[Masterwork ice dagger deals +1 cold damage.]
    \DeclareSpellDescription{Icicle Dagger}{You create a masterwork dagger out of ice. The dagger deals 1 point of cold damage in addition to normal dagger damage.
If the dagger leaves your hand for more than 1 round, it melts and the spell ends. At 6th level, the dagger functions as a +1 frost dagger. At 11th level, it gains the returning property when thrown, melting away and reforming in your hand just before your next turn.}
        
\DeclareSpell{Icy Prison}{evocation () [cold]|V,  S|1 standard action|medium (10 ft. + 10 ft./level)|Targetsone creature|1 minute/level; see text|Reflex partial|yes}[Thick ice holds and damages the target.]
    \DeclareSpellDescription{Icy Prison}{You trap the target in solid ice 1 inch thick per caster level. If the creature fails its save, it is helpless, but can still breathe (the ice blocks line of effect to the target). If the target makes its save, it gains the entangled condition but can otherwise act normally. Whether or not the target saves, it takes 1 point of cold damage per caster level each round it is helpless or entangled in the ice. The ice has hardness 0 and 3 hit points per inch of thickness; if broken, the creature is freed. A creature can break the ice as a full-round action with a successful Strength check (DC 15 + your caster level).}
        
\DeclareSpell{Icy Prison, Mass}{evocation () [cold]|V,  S|1 standard action|medium (10 ft. + 10 ft./level)|Targetsone creature/level, no two of which can be more than 30 ft. apart.|1 minute/level; see text|Reflex partial|yes}[As icy prison, but it affects 1 creature/level.]
    \DeclareSpellDescription{Icy Prison, Mass}{This spell functions as icy prison, except as noted above.}
        
\DeclareSpell{Imbue with Aura}{transmutation () []|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 minute/level|Will negates (see text)|yes}[Target emulates your cleric aura.]
    \DeclareSpellDescription{Imbue with Aura}{You infuse another creature with your divine aura, causing the target to radiate an aura identical to your own clerical aura. The target's actual alignment is not changed, but spells like detect evil or detect good detect only the aura, not the creature's actual alignment. For the duration of this spell, effects influenced by the target's alignment function according to the imposed aura, not the creature's actual aura. When the spell ends, the target's aura returns to normal, and alignmentaffecting magic affects it according to its actual alignment.}
        
\DeclareSpell{Interplanetary Teleport}{conjuration (teleportation) []|V|1 standard action|personal and touch|Targetsyou and touched objects or other touched willing creatures|instantaneous|none and Will negates (object)|no and yes (object)}[Teleport to another planet.]
    \DeclareSpellDescription{Interplanetary Teleport}{This spell functions as teleport, except there is truly no range limit and you do not need to have seen your destination, though you must have a solid grasp of which world you wish to travel to ("the third planet from the sun" is an acceptable destination, but "a habitable world near that bright star" is not). If you have a specific location on a planet in mind, you arrive there without a chance of failure; otherwise you arrive at a location that would not immediately be life-threatening.
If no such safe landing zone exists on the world, such as someone attempting to travel into the sun without the proper precautions in place, the spell simply fails.}
        
\DeclareSpell{Interrogation}{necromancy () [evil,  pain]|V,  S|1 round|touch|Targetsliving creature touched|1 minute/level|Fortitude negates|yes}[Target answers questions or suffers pain.]
    \DeclareSpellDescription{Interrogation}{You question the target, backed up by the threat of magical pain. You may ask one question per two caster levels. The target can either answer the question or take 1d4 points of damage plus your Wisdom bonus. The target is not compelled to answer truthfully, but the threat of pain gives it a -4 penalty on Bluff checks to convince you when it is lying.}
        
\DeclareSpell{Interrogation, Greater}{necromancy () [evil,  pain]|V,  S|1 round|touch|Targetsliving creature touched|1 minute/level|Fortitude negates|yes}[As interrogation, except with more pain and more questions.]
    \DeclareSpellDescription{Interrogation, Greater}{This spell functions as interrogation, except you may ask one question per caster level and the spell deals damage equal to 1d8 points plus your Wisdom bonus if the target doesn't answer a question.}
        
\DeclareSpell{Joyful Rapture}{conjuration (healing) [emotion]|V,  S|1 standard action|60 ft.|Areaall allies and opponents within a 60-ft.-radius burst centered on you|instantaneous|no|yes}[Negate harmful emotions.]
    \DeclareSpellDescription{Joyful Rapture}{Your inspired words overwhelm others with transcendental bliss. All allies within the area of effect are freed from any harmful emotion effects. The spell also cures 1d4 points of Intelligence, Wisdom, or Charisma damage (your choice) to all allies in the area.}
        
\DeclareSpell{Ki Arrow}{conjuration () []|S|1 standard action|touch|Targets1 arrow touched|instantaneous|Fortitude (object)|yes (object)}[Arrow deals damage as your unarmed strike.]
    \DeclareSpellDescription{Ki Arrow}{You imbue an arrow with your power and throw it at a target up to 100 feet away. Make a ranged attack roll. If it hits, the target takes damage from the arrow as if you had hit it with a single unarmed strike (including your Strength bonus).}
        
\DeclareSpell{Ki Leech}{necromancy () [evil]|V,  S|1 standard action|personal|Targetsyou|1 minute/level (D)||}[Add to your ki pool when you critically hit.]
    \DeclareSpellDescription{Ki Leech}{You place your spirit in a receptive state so when you confirm a critical hit against a living enemy or reduce a living enemy to 0 or fewer hit points, you can steal some of that creature's ki. This replenishes 1 point of ki as long as you have at least 1 ki point in your ki pool. This does not allow you to exceed your ki pool's maximum. This ability does not stack with similar abilities (such as the steal ki ability of the hungry ghost monk in the Advanced Player's Guide).
This spell has no effect if you do not have a ki pool.}
        
\DeclareSpell{Ki Shout}{evocation () [sonic]|V,  S|1 standard action|close (25 ft + 5 ft./2 levels)|Targetsone living creature|instantaneous|Fortitude partial (see text)|yes}[Target takes 1d6 sonic/level and is stunned.]
    \DeclareSpellDescription{Ki Shout}{With a guttural bark, you unleash a sudden blast of sonic energy that strikes your opponent. The target takes 1d6 points of sonic damage per level (maximum 20d6) and is stunned for 1 round; a successful Fortitude save reduces the damage by half and negates the stun.}
        
\DeclareSpell{Know The Enemy}{divination () []|S,  V,  DF|1 minute|personal|Targetsyou|instantaneous|none|no}[Gain +10 on a monster Knowledge check.]
    \DeclareSpellDescription{Know The Enemy}{You commune with the divine, reflecting on one type of creature you encountered in the last day. You may make a Knowledge check regarding that creature type with a +10 insight bonus.}
        
\DeclareSpell{Leashed Shackles}{evocation () [force]|V,  S|1 standard action|medium (100 ft. +10 ft./level)|Targetsone creature|1 minute/level|Reflex negates|yes}[Target is restricted to a specific location.]
    \DeclareSpellDescription{Leashed Shackles}{You create shackles of force that attach to the target's limbs. You designate an object or location within 30 feet of the target for the shackles to anchor themselves to; this must be the ground, a wall, or a sturdy structure for the anchoring to occur. The target is entangled, and cannot move more than 30 feet from the anchor point of the spell. The shackle itself cannot be attacked (though it can be dispelled), but if the object or area it is attached to is broken, the target is free to move away (though it is still entangled).}
        
\DeclareSpell{Lend Judgment}{divination () []|V,  DF|1 standard action|touch|Targetsone ally|1 round/level|Will negates (harmless)|yes (harmless)}[Ally gains the benefit of one judgment.]
    \DeclareSpellDescription{Lend Judgment}{You create a conduit of divine knowledge and outrage between you and an ally. That ally gains the benefit of one of your active judgments (as do you). If you cannot use a judgment (for example, if you are not in combat, are frightened or unconscious, and so on) or change judgments, the ally loses the benefit of the judgment. If you have multiple judgments active, the ally gains only one, chosen when you cast this spell.}
        
\DeclareSpell{Lend Judgment, Greater}{divination () []|V,  DF|1 standard action|touch|Targetsone ally|1 round/level|Will negates (harmless)|yes (harmless)}[Ally receives all your judgments.]
    \DeclareSpellDescription{Lend Judgment, Greater}{This functions as lend judgment, except the ally gains the benefit of all your active judgments.}
        
\DeclareSpell{Lightning Arc}{evocation () [electricity]|V,  S,  M (fur and two glass figurines)|1 standard action|long (400 ft. + 40 ft./level)|Targetstwo creatures or objects which must be no more than 60 ft. apart|instantaneous|Reflex half|yes (see text)}[Targets in a line take 1d6 electricity/level.]
    \DeclareSpellDescription{Lightning Arc}{You generate an arc of lightning between two targets. The lightning deals 1d6 points of electricity damage per caster level (maximum 15d6) to both targets and any creatures in a line connecting them. The spell fails if there is no line of effect between the targets. Lightning arc sets fire to combustibles and damages objects in its path. It can melt metals that have a low melting point, such as lead, gold, copper, silver, or bronze.}
        
\DeclareSpell{Loathsome Veil}{illusion (pattern) [mind-affecting]|V,  S,  M (a tangle of multicolored threads)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effecttransparent pattern 40 ft. long, 20 ft. high|concentration + 1 round/level (D)|Will negates|yes}[Nauseate and/or sicken weak creatures.]
    \DeclareSpellDescription{Loathsome Veil}{This spell creates a transparent veil of shifting, multicolored strands of light that form into endlessly varied and alien patterns. One side of the veil, chosen by you at the time of casting, is harmless. The other side twists and turns into impossible shapes, affecting any creature with 60 feet who views the veil. The veil affects a maximum of 24 Hit Dice of creatures. Creatures with the fewest HD are affected first.
Among creatures with equal HD, those who are closest to the spell are affected first. The effect is according to the creature's HD.
4 HD or fewer: The creature is nauseated while it can see the veil, nauseated for 1d4 rounds after it last saw the veil, then sickened for 2d4 rounds after it last saw the veil.
8 HD or fewer: The creature is nauseated for 1d4 rounds, sickened while it can see the veil, then sickened for 1d4 rounds after it last saw the veil.
9 or more HD: The creature is sickened while it can see the veil.
A successful saving throw ignores all effects of the veil.
Sightless creatures are not affected by loathsome veil.
Affected creatures can avert or close their eyes to avoid seeing the veil, similar to avoiding a gaze attack.
Loathsome veil can be made permanent with the permanency spell by a caster of 10th level or higher for the cost of 7,500 gp.}
        
\DeclareSpell{Lunar Veil}{illusion (shadow) [darkness,  shadow]|V,  S|1 standard action|long (400 ft. + 40 ft./level)|Area120-ft.-radius emanation|10 minute/level|Will negates, see text|no}[Dispel light and revert lycanthropes.]
    \DeclareSpellDescription{Lunar Veil}{You conjure a tremendous area of shadow to obscure moonlight within the area, creating something akin to a lunar eclipse. The light level is lowered by two steps (though unlike deeper darkness, areas of normal light or dimmer become normal darkness rather than supernaturally dark).
Lycanthropes in the area must make a Will save every round or revert to their humanoid forms. In addition, lycanthropes attempting to assume animal or hybrid form within the affected area take a -5 penalty on Constitution checks to do so.}
        
\DeclareSpell{Mad Hallucination}{illusion (phantasm) []|V,  S|1 standard action|close (20 ft.)|Targetsone humanoid creature|5 minute/level (maximum 1 hour)|Will negates|yes}[Target takes penalties to mental actions.]
    \DeclareSpellDescription{Mad Hallucination}{This spell induces a hallucinogenic reality in the mind of your target. Surfaces seem to swim, and movement constantly distracts the eye. The target takes a -2 penalty on Will saving throws, caster level checks, Intelligence-based skill checks, and Wisdom-based skill checks.}
        
\DeclareSpell{Mad Monkeys}{conjuration (summoning) []|V,  S,  DF|1 round|close (25 ft. + 5 ft./2 levels)|Effectswarm of monkeys|1 round/level|none|no}[Summon a swarm of mischievous monkeys.]
    \DeclareSpellDescription{Mad Monkeys}{You summon a swarm of screeching, mischievous monkeys. The swarm understands and obeys your commands and has the statistics of a monkey swarm (Bestiary 2 212). Creatures failing a saving throw against the mad monkeys' distraction attack are deafened for 1 minute as well as nauseated. The monkeys attempt one disarm or steal combat maneuver each turn as a free action against any creature that begins its turn in the swarm, using your caster level plus your casting ability score bonus (Intelligence for wizards; Wisdom for druids; Charisma for bards, sorcerers, and summoners) for its CMB. Recovering an item from the monkeys requires a successful disarm or steal attempt against that CMB + 10. An object stolen by the monkeys takes swarm damage each round the swarm is in possession of the object.}
        
\DeclareSpell{Malfunction}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Areaone construct|1 round/level (D)|Fortitude negates|yes}[Construct behaves oddly for 1 round/level.]
    \DeclareSpellDescription{Malfunction}{This functions as confusion, except it only affects constructs, and instead of babbling incoherently, the construct takes no actions on its turn (but may still make attacks of opportunity).}
        
\DeclareSpell{Malicious Spite}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S,  M (powdered turquoise worth 150 gp)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 day/level|Will negates|yes}[Target is compelled to plot against another.]
    \DeclareSpellDescription{Malicious Spite}{You invoke feelings of a driving malicious intent. The target's malice is directed at a second individual as designated by you at the time of casting. Thereafter, the target attempts to slander, abuse, and even plot murder against the target of its spite. This loathing is not overt, and the target's actions against the object of its spite remain subtle and indirect.
The enchanted target remains within its financial and ethical means when acting against the second individual, though the malice toward this other person pushes the target to the limit of what it would do to a hated individual.
Each day, the target takes 2 points of Wisdom damage as the all-encompassing spite dominates its thoughts. The target can only alleviate the ability damage by acting upon the emotion and performing a spiteful act. Examples of spiteful acts are spiking the target's drink to make it an easier target for thugs, damaging the target's property, starting foul rumors about the target, framing the target for a crime, paying lepers or beggars to accost the target, extorting or blackmailing the target, or arranging for others to physically harm the target.
When the spell ends, the target remembers the spiteful behavior, but not the motivation for it.}
        
\DeclareSpell{Marionette Possession}{necromancy () []|V,  S,  F (a piece of paper with the target's name)|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone willing creature|10 minutes/level or until you return to your body|Will negates (see text)|yes}[As magic jar, but limited to line of sight.]
    \DeclareSpellDescription{Marionette Possession}{You project your soul out of your body and into the body of a willing creature. This possession is blocked by protection from evil or a similar ward. The target's soul shares its body with you; it is helpless but can still use its senses. You and the target's soul can communicate telepathically as if using a common language.
You keep your Intelligence, Wisdom, Charisma, level, class, base attack bonus, base save bonuses, alignment, and mental abilities. The body retains its Strength, Dexterity, Constitution, hit points, natural abilities, and natural attacks (such as a bite or sting). A body with extra limbs does not allow you to make more attacks (or more advantageous two-weapon attacks) than normal. You can't choose to activate the body's extraordinary, spell-like, or supernatural abilities.
As a standard action, you can return to your own body, ending the spell. While your soul is possessing the target, your body is helpless. If the host body is slain, you return to your own body if it is within range, and the life force of the host departs (it is slain). If the host body is slain beyond the range of the spell, both you and the host die. Any life force with nowhere to go is treated as slain.}
        
\DeclareSpell{Masterwork Transformation}{transmutation () []|V,  S,  M (see below)|1 hour|touch|Targetsone weapon, suit of armor, shield, tool, or skill kit touched|instantaneous|none|no}[Make a normal item into a masterwork one.]
    \DeclareSpellDescription{Masterwork Transformation}{You convert a non-masterwork item into its masterwork equivalent. A normal sword becomes a masterwork sword, a suit of leather armor becomes a masterwork suit of leather armor, a set of thieves' tools becomes masterwork thieves' tools, and so on. If the target object has no masterwork equivalent, the spell has no effect. You can affect 50 pieces of ammunition as if they were one weapon. You decide if the object's appearance changes to reflect this improved quality.
The material component for the spell is magical reagents worth the cost difference between a normal item and the equivalent masterwork item (typically 300 gp for a weapon, 150 gp for armor, or 50 gp for a tool). If an object has multiple masterwork options (such as a double weapon, or a spiked shield that could be made masterwork as a weapon or armor), you choose one option of the object to affect (though you can cast the spell again to affect another option).}
        
\DeclareSpell{Miserable Pity}{abjuration () [emotion,  mind-affecting]|V,  S|1 standard action|touch|Targetscreature touched|1 round/level and 1 minute; see text|Will negates (see text)|yes}[Opponents cannot attack a pathetic creature.]
    \DeclareSpellDescription{Miserable Pity}{This spell functions as sanctuary, except creatures attempting to attack the target who fail their saves also feel a strong sense of pity toward the target, as if it were weak, pathetic, and not a threat. If the target breaks the spell by attacking, any creature that failed its save against the spell gains a +2 morale bonus on attack rolls against the target for 1 minute.}
        
\DeclareSpell{Monstrous Physique I}{transmutation (polymorph) []|V,  S,  M (a piece of the creature whose form you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)||}[Take the form and some of the powers of a Small or Medium monstrous humanoid.]
    \DeclareSpellDescription{Monstrous Physique I}{When you cast this spell, you can assume the form of any Small or Medium creature of the monstrous humanoid type. If the form you assume has any of the following abilities, you gain the listed ability: climb 30 feet, fly 30 feet (average maneuverability), swim 30 feet, darkvision 60 feet, low-light vision, and scent. If the form you assume has the aquatic subtype, you gain the aquatic and amphibious subtypes.  Small monstrous humanoid: If the form you take is that of a Small monstrous humanoid, you gain a +2 size bonus to your Dexterity and a +1 natural armor bonus.  Medium monstrous humanoid: If the form you take is that of a Medium monstrous humanoid, you gain a +2 size bonus to your Strength and a +2 natural armor bonus.}
        
\DeclareSpell{Monstrous Physique II}{transmutation (polymorph) []|V,  S,  M (a piece of the creature whose form you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)||}[Take the form and some of the powers of a Tiny or Large monstrous humanoid.]
    \DeclareSpellDescription{Monstrous Physique II}{This spell functions as monstrous physique I, except it also allows you to assume the form of a Tiny or Large creature of the monstrous humanoid type. If the form you assume has any of the following abilities, you gain the listed ability: climb 60 feet, fly 60 feet (good maneuverability), swim 60 feet, darkvision 60 feet, low-light vision, scent, freeze, grab, leap attack, mimicry, pounce, sound mimicry, speak with sharks, and trip. If the creature has the undersized weapons special quality, you gain that quality.  Tiny monstrous humanoid: If the form you take is that of a Tiny monstrous humanoid, you gain a +4 size bonus to your Dexterity, a -2 penalty to your Strength, and a +1 natural armor bonus.  Large monstrous humanoid: If the form you take is that of a Large monstrous humanoid, you gain a +4 size bonus to your Strength, a -2 penalty to your Dexterity, and a +4 natural armor bonus.}
        
\DeclareSpell{Monstrous Physique III}{transmutation (polymorph) []|V,  S,  M (a piece of the creature whose form you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)||}[Take the form and some of the powers of a Diminutive or Huge monstrous humanoid.]
    \DeclareSpellDescription{Monstrous Physique III}{This spell functions as monstrous physique II, except it also allows you to assume the form of a Diminutive or Huge creature of the monstrous humanoid type. If the form you assume has any of the following abilities, you gain the listed ability: burrow 30 feet, climb 90 feet, fly 90 feet (good maneuverability), swim 90 feet, all-around vision, blindsense 30 feet, darkvision 60 feet, low-light vision, scent, blood frenzy, cold vigor, constrict, ferocity, freeze, grab, horrific appearance, jet, leap attack, mimicry, natural cunning, overwhelming, poison, pounce, rake, sound mimicry, speak with sharks, trample, trip, and web. If the creature has the undersized weapons special quality, you gain that quality.  Diminutive monstrous humanoid: If the form you take is that of a Diminutive monstrous humanoid, you gain a +6 size bonus to your Dexterity, a -4 penalty to your Strength, and a +1 natural armor bonus.  Huge monstrous humanoid: If the form you take is that of a Huge monstrous humanoid, you gain a +6 size bonus to your Strength, a -4 penalty to your Dexterity, and a +6 natural armor bonus.}
        
\DeclareSpell{Monstrous Physique IV}{transmutation (polymorph) []|V,  S,  M (a piece of the creature whose form you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)||}[As monstrous physique III, with more abilities.]
    \DeclareSpellDescription{Monstrous Physique IV}{This spell functions as monstrous physique III except it allows you to use more abilities. If the form you assume has any of the following abilities, you gain the listed ability: burrow 60 feet, climb 90 feet, fly 120 feet (good maneuverability), swim 120 feet, blindsense 60 feet, darkvision 90 feet, low-light vision, scent, tremorsense 60 feet, blood frenzy, breath weapon, cold vigor, constrict, ferocity, freeze, grab, horrific appearance, jet, leap attack, mimicry, natural cunning, overwhelming, poison, pounce, rake, rend, roar, sound mimicry, speak with sharks, spikes, trample, trip, and web. If the creature has immunity or resistance to any energy types, you gain resistance 20 to those energy types. If the creature has vulnerability to an energy type, you gain that vulnerability. If the creature has immunity to poison, you gain a +8 bonus on saves against poison.}
        
\DeclareSpell{Murderous Command}{enchantment (compulsion) [mind-affecting]|V|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone living creature|1 round|Will negates|yes}[Target is compelled to kill its ally.]
    \DeclareSpellDescription{Murderous Command}{You give the target a mental urge to kill its nearest ally, which it obeys to the best of its ability. The target attacks its nearest ally on its next turn with a melee weapon or natural weapon. If necessary, it moves to or charges to the nearest ally in order to make this attack. If it is unable to reach its closest ally on its next turn, the target uses its turn to get as close as possible to the ally.}
        
\DeclareSpell{Oppressive Boredom}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round/level or until broken (see text)|Will negates (see text)|yes}[Target loses its next action.]
    \DeclareSpellDescription{Oppressive Boredom}{You fill your target with boredom. The target loses all interest in its current task and must make a Will save against the spell's effect in order to perform its next action. If the target fails, it takes no action that round. The boredom lasts until the duration expires or the target breaks the spell's effect with a successful Will save.}
        
\DeclareSpell{Oracle's Vessel}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 minute/level|Will negates (harmless)|yes (harmless)}[Oracle only. Target gains the benefits of your oracle's curse.]
    \DeclareSpellDescription{Oracle's Vessel}{The target gains all the benefits of your oracle's curse, with none of the penalties. In some cases, this has no effect (for example, a fighter with your haunted curse can't cast spells and doesn't gain any benefit from having additional spells known).}
        
\DeclareSpell{Orb Of The Void}{necromancy () []|V,  S,  M (a black gemstone of any kind worth 50 gp)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effect1-ft.-diameter sphere|1 round/level (D)|Fortitude negates|yes}[Sphere inflicts negative levels.]
    \DeclareSpellDescription{Orb Of The Void}{You create a small weightless sphere of pure negative energy. As a move action, you can move it up to 30 feet per round in any direction. If it enters a space with a living creature, it stops moving for the round and that creature gains one negative level (Fortitude negates). Any creature passing through or ending its turn in the space occupied by the sphere gains one negative level (Fortitude negates). Twenty-four hours after gaining a negative level from the sphere, the subject must make a Fortitude saving throw (the DC of this save is equal to the DC of this spell) for each negative level. If the save succeeds, that negative level is removed. If it fails, that negative level becomes permanent.  If more than one orb (from different castings of the spell) enters the same space, the orbs automatically fuse together. The resulting orb uses the higher of the two orbs' DCs as its DC and whichever duration has more time left. If the orbs are from different casters, each must make an opposed Intelligence check to move the sphere.  An undead creature that passes through or ends its turn in the space occupied by the orb gains 2d4 x 5 temporary hit points for 1 hour.}
        
\DeclareSpell{Overwhelming Grief}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round/level|Will negates (see text)|yes}[Grieving target can take no actions and is denied its Dex bonus.]
    \DeclareSpellDescription{Overwhelming Grief}{You cause a single opponent to become profoundly stricken with intense grief. He can take no actions, takes a -2 penalty to Armor Class, and loses his Dexterity bonus (if any). He can attempt a new save each round to break the spell's effect.}
        
\DeclareSpell{Overwhelming Presence}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S,  M (a swan feather)|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone creature/level, no two of which can be more than 30 ft. apart|1 round/level|Will negates, see text|yes}[Creatures bow before you as if you were divine.]
    \DeclareSpellDescription{Overwhelming Presence}{Your presence inspires incredible awe in those nearby. A creature that fails a save against this spell falls to the ground and prostrates itself before you, believing it bows before a divine presence. A flying creature incapable of hovering must land immediately in order to prostrate itself. These creatures are considered to be helpless for the duration of the spell.
Each round on its turn, a target of this spell may attempt a new saving throw to end the effect; this is a full-round action that does not provoke attacks of opportunity. A creature that recovers from this spell early after being affected by it for at least 1 round takes 1d6 points of Wisdom drain and is staggered for 1d4 rounds. A creature that makes the initial save to resist this spell is merely staggered for 1 round.}
        
\DeclareSpell{Pernicious Poison}{necromancy () [poison]|V,  S,  DF|1 standard action|touch|Targetscreature touched|10 minute/level|none|yes}[Target takes a –4 penalty against poison.]
    \DeclareSpellDescription{Pernicious Poison}{You weaken the target's defenses against poison. The target gains a -4 penalty on saves against poison, and poisons affecting the target continue for another 2 frequency increments (for example, black adder venom lasts 8 rounds instead of 6, and arsenic lasts for 6 minutes instead of 4). Attempts to cure the poisoned target with skill or magic take a -4 penalty.}
        
\DeclareSpell{Persuasive Goad}{necromancy () [pain]|V,  S|1 standard action|close (25 ft. +5 ft./2 levels)|Targetsone creature|instantaneous and 1 minute|Fortitude negates|yes}[Target takes 1d6 nonlethal damage; you gain an Intimidate bonus.]
    \DeclareSpellDescription{Persuasive Goad}{Your eyes flash and the target takes 1d6 points of nonlethal damage. For the next minute, you gain a +4 circumstance bonus on Intimidate checks against the target.}
        
\DeclareSpell{Piercing Shriek}{evocation () [pain,  sonic]|V|1 standard action|medium (100 ft. + 10ft./level)|Targetsone creature|1 round/level|Fortitude negates|yes}[Target is staggered by a painful sound.]
    \DeclareSpellDescription{Piercing Shriek}{You emit an ear-splitting shriek which can be heard only by the target of this spell; all other observers merely see you screaming silently. The target suffers wracking pain from the scream, gaining the staggered condition. This spell has no effect on deaf creatures and cannot penetrate an area of silence.}
        
\DeclareSpell{Plague Carrier}{necromancy () [disease,  evil]|V,  S|1 standard action|touch|Targetscreature touched|1 hour/level|Fortitude negates (harmless)|yes}[Target's attacks carry filth fever.]
    \DeclareSpellDescription{Plague Carrier}{The target's natural attacks carry filth fever (DC 10 + 1/2 of the creature's Hit Dice + creature's Con modifier)}
        
\DeclareSpell{Plague Storm}{necromancy () [disease,  evil]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Effectcloud spreads in 20-ft. radius, 20 ft. high|1 minute/level and instantaneous (see text)|Fortitude negates|no}[Cloud infects creatures like contagion.]
    \DeclareSpellDescription{Plague Storm}{You create a hideous gray cloud, similar to fog cloud, that occasionally crackles with foul-smelling bolts of sickly green lightning. Creatures in the area must save or contract one of the following diseases: blinding sickness, bubonic plague, cackle fever, demon fever, devil chills, filth fever, leprosy, mindfire, red ache, shakes, or slimy doom (the disease is chosen by you when you cast the spell and applies to all creatures that fail the save). The disease is contracted immediately (the onset period does not apply) and is an instantaneous effect. Use the disease's listed frequency to determine further effects, but the disease's save DC increases by +2. For more information see page 557 of the Core Rulebook.
Unlike a fog cloud, the plague storm moves away from you at 10 feet per round, rolling along the surface of the ground.
Figure out the cloud's new spread each round based on its new point of origin, which is 10 feet farther away from the point of origin where you cast the spell.
Because the vapors are heavier than air, they sink to the lowest level of the terrain, even pouring down den or sinkhole openings. The cloud cannot penetrate liquids, nor can it be cast underwater.}
        
\DeclareSpell{Play Instrument}{divination () []|V,  S|1 standard action|personal|Targetsyou|10 minute/level||}[Play instrument as if you were skilled.]
    \DeclareSpellDescription{Play Instrument}{You may play one instrument of your choice as if you had 1 rank in the appropriate Perform skill. Instead of a conventional instrument, you may use an object as an improvised instrument, such as using a barrel as a drum or a bow as a harp, playing it as if it were crafted to make music.}
        
\DeclareSpell{Polar Midnight}{transmutation () [cold,  darkness]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Effect30-ft. spread|1 round/level|Fortitude partial|yes}[Cold darkness paralyzes and deals damage.]
    \DeclareSpellDescription{Polar Midnight}{You plunge an area into the brutal chill of the arctic night.
Illumination conditions are dropped by two steps (though only to darkness, not supernatural darkness), and all creatures in the area take 5d6 points of cold damage and 1d6 points of Dexterity damage per round. A successful Fortitude save each round negates the Dexterity damage but not the cold damage.
Any creature that doesn't move on its turn becomes encased in a sheath of ice equivalent to wall of ice, is helpless, and cannot breathe. Corpses in the area for longer than 1 round are transmuted into solid ice; reviving the icy corpse requires true resurrection, miracle, or wish. As a move action, you may move the area of effect up to 10 feet in any direction.}
        
\DeclareSpell{Polypurpose Panacea}{transmutation () []|S|1 standard action|personal|Targetsyou|see below||}[Gain a relaxing or entertaining effect.]
    \DeclareSpellDescription{Polypurpose Panacea}{This creates one of several cantrip-level effects relating to your health, well-being, and entertainment. The panacea has no side effects (for example, the intoxication panacea does not cause a hangover). When you use polypurpose panacea, choose one of the following effects.
Analgesic: You do not feel minor aches and pains, such as from arthritis, a cold, or a hangover, for 1 hour. For the duration, you gain a +2 resistance bonus against pain-related spells.
Clarity: You get a +1 competence bonus on a single attack roll, saving throw, or skill check within 1 minute. You must choose to use the bonus before making the roll to which it applies.
Hallucination: You have pleasant hallucinations for 1 hour, such as wandering lights, music, playful surreal animals, and so on. You can tell these are not real, but they are distracting, and you take a -2 penalty on Perception checks for the duration.
Intoxication: You feel comfortably intoxicated for 1 hour, as if you had a few alcoholic beverages.
Lucid Dream: If you take this panacea within 1 hour of going to sleep, you have a lucid dream that is under your control and lasts for an hour.
Resistance: You gain a +1 resistance bonus on saves for 1 minute.
Sleep: You enter a pleasant and restful sleep for at least 1 hour unless wakened. If you would normally begin sleeping at this time, when the panacea ends you continue sleeping normally.
Sobriety: You become completely sober for 1 hour, negating any penalties to your actions for being drunk (GameMastery Guide 237). Magical and alchemical methods (such as detect poison) still detect you as inebriated. Time spent under the effect of this panacea do not count toward the time necessary to sober up (it merely delays your intoxication).
Tenacity: You gain 1 temporary hit point for 1 minute.
Wakefulness: You remain awake for 2 hours without feeling sleepy, and without side effects such as jitteriness. You gain a +5 resistance bonus against sleep-related spells such as lullaby and sleep. This use of the panacea merely delays your need for sleep and does not count as rest or sleep. You can use it multiple times in succession, but as each effect wears off, you are as tired as you would be had you not used the panacea.}
        
\DeclareSpell{Possess Object}{necromancy () []|V,  S,  F (a gem or crystal worth at least 100 gp)|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone object; see text|1 hour/level or until you return to your body||}[Possess and animate one object.]
    \DeclareSpellDescription{Possess Object}{This spell functions as magic jar, except you transfer your mind to a single object, animating it as if using animate objects, except your mind controls the object as if it were your own body. You cannot speak or cast spells while possessing the object. Because your original body is effectively dead while under the effect of this spell, this temporarily suspends disease, poisons, and other afflictions affecting you.}
        
\DeclareSpell{Prediction of Failure}{divination () [curse,  fear,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|permanent or 1 round/level (see text)|Will partial|yes}[Target is permanently shaken and sickened, and may gain a spellblight.]
    \DeclareSpellDescription{Prediction of Failure}{You wrack the target's body and mind with the anguish and suffering of every bitter failure it will ever experience, rendering it permanently shaken and sickened. A successful Will save reduces the duration to 1 round per level. If the target is a spellcaster, failing this saving throw means it also gains a random minor spellblight (see page 95).}
        
\DeclareSpell{Primal Scream}{abjuration () [mind-affecting,  sonic]|V|1 standard action|personal|Targetsyou|1 round/level||}[Free yourself from enchantments and paralysis effects.]
    \DeclareSpellDescription{Primal Scream}{You voice a mighty yell from the depths of your soul, invigorating yourself and dispelling enchantment and paralysis effects. This functions as break enchantment, except it only affects you and only frees you from enchantment and paralysis effects. If the caster level check to break the hostile effect succeeds, you give voice to your scream and the spell takes effect normally; if not, this spell fails without further effect. You can cast this spell even when paralyzed or unable to speak because of an enchantment effect, but not in an area of silence , if you are unable to speak for reasons other than enchantments or paralysis (for example, if you are gagged), or if cast in an environment where speaking is not possible.}
        
\DeclareSpell{Protective Penumbra}{evocation () [darkness]|V,  S, |1 standard action|touch|Targetscreature touched|10 minutes/level|Will negates (harmless)|yes}[Shadow protects the target from light.]
    \DeclareSpellDescription{Protective Penumbra}{This spell keeps the target slightly in shadow. A target with light blindness, light sensitivity, or vulnerability to sunlight (such as vampires and wraiths) may ignore penalties from those qualities. The spell gives the target a +2 bonus on saving throws against nonmagical hazards related to bright light, such as glare or sunburn.}
        
\DeclareSpell{Rain of Frogs}{conjuration (summoning) []|V,  S,  M/DF (a square of red cloth)|1 round|close (25 ft. + 5 ft./2 levels)|Effectone swarm of poisonous frogs|concentration + 2 rounds|none|no}[Summon a swarm of poisonous frogs.]
    \DeclareSpellDescription{Rain of Frogs}{This spell functions as summon swarm, except you summon a swarm of poisonous frogs. This swarm has the statistics of a centipede swarm (Bestiary 43), except it has the animal type and its poison deals Constitution damage instead of Dexterity damage.}
        
\DeclareSpell{Raise Animal Companion}{conjuration (healing) []|V,  S,  M (a diamond worth 1, 000 gp)|1 minute|touch|Targetsdead animal companion or bonded mount|instantaneous|none, see text|yes (harmless)}[As raise dead, but on an animal.]
    \DeclareSpellDescription{Raise Animal Companion}{This spell functions as raise dead, but it only affects an animal companion, familiar, or paladin's bonded mount.}
        
\DeclareSpell{Rapid Repair}{transmutation () []|V,  S,  DF|1 standard action|touch|Targetsconstruct touched|1 round/level|Fortitude negates (harmless)|yes (harmless)}[Construct gains fast healing 5.]
    \DeclareSpellDescription{Rapid Repair}{The targeted construct gains fast healing 5. This does not stack with any fast healing the construct already has. Fast healing has no effect on a construct that has been brought to 0 hit points or destroyed.}
        
\DeclareSpell{Ray of Sickening}{necromancy () []|V,  S,  M (a drop of sweat)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectray|1 min./level|Fortitude partial; see text|yes}[Ray makes the subject sickened.]
    \DeclareSpellDescription{Ray of Sickening}{This spell functions as ray of exhaustion, except the target is sickened if it fails its save and unaffected if it makes its save.}
        
\DeclareSpell{Reckless Infatuation}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 day/level|Will negates|yes}[Target is compelled to stay near another.]
    \DeclareSpellDescription{Reckless Infatuation}{You fill your target with feelings of intense infatuation for a specific individual known to the target. At the time of the casting, you designate a single creature as the focus of the target's desire.
Thereafter, the target does all it can to remain within 30 feet of the object of its desire. If the target moves outside this range, it gains the staggered condition until it is again near the focus of its desire. If remaining within 30 feet of the focus of its affection would place the target in obvious physical danger, the target can attempt a second save to break the spell's effect.
Reckless infatuation counters unadulterated loathing.}
        
\DeclareSpell{Remove Sickness}{conjuration (healing) []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|10 minutes/level; see text|Fortitude negates (harmless)|yes (harmless)}[Suppress disease, nausea, and the sickened condition.]
    \DeclareSpellDescription{Remove Sickness}{You quell feelings of illness and nausea in the target, giving it a +4 morale bonus on saving throws against disease, nausea, and sickened effects. If the subject is already under the influence of one of these effects when receiving the spell, that effect is suppressed for the duration of the spell.}
        
\DeclareSpell{Reprobation}{transmutation () [curse,  see text]|V,  S,  DF|1 minute|close (25 ft. + 5 ft./2 levels)|Targetsone creature of your faith|permanent|none|yes}[Marked target is shunned by your religion.]
    \DeclareSpellDescription{Reprobation}{You cast the target out of your religion as a curse and punishment for acts or misdeeds against the tenets of your faith. This has three effects.
First, the target is marked with a magical symbol visible only to members of your faith. This symbol indicates that the target has transgressed and that the faithful should not help it. Likewise, the target is not to be persecuted because of the mark (though this would not keep members of a lawful faith from imprisoning a known criminal if these crimes were known to have taken place after he gained the mark).
Second, the target is no longer affected by helpful spells cast by the faithful and is always treated as an enemy for the purpose of other spells cast by those of your faith. For example, cure light wounds cast by a member of your faith has no effect on the target. If the target were traveling with a cleric of your faith who cast prayer, that spell would penalize rather than aid the target, despite the target's friendship with the cleric.
Third, if the target is a divine spellcaster, a member of a prestige class of your faith, or otherwise has some ability because the target belongs to your faith, it cannot use those abilities while the mark remains in place. For example, a paladin of your faith would be unable to cast paladin spells or use lay on hands or other class abilities. The target can join another faith to regain the use of these abilities, but the mark remains visible to those of your faith, even if those of the new faith accept the target.
This powerful spell with no saving throw is used to punish severe transgressions that do not deserve death or when you prefer to be merciful rather than meting out a more severe punishment. However, the spell has one drawback that prevents it from being overused. If the target did not commit any acts or misdeeds against your faith, the spell does not affect it but affects you instead, even if you are innocent of the charges.
This potential backlash prevents inquisitions run by corrupt members of the faith, and it means that most accusations of misconduct are carefully investigated (and usually verified with magic) before this sentence is handed down.
This mark can be removed like any other curse effect. In addition, a member of your faith can use atonement to break the curse if he makes a caster level check against your caster level; remove curse also requires a caster of your faith and a caster level check to end the reprobation.}
        
\DeclareSpell{Resonating Word}{transmutation () [sonic]|V|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone creature|3 rounds|Fortitude partial|yes}[Target is damaged, staggered, and stunned.]
    \DeclareSpellDescription{Resonating Word}{You speak a terrible word of power, setting up potentially lethal vibrations in the chosen target. The target must save once each round on your turn, and the effects grow stronger for each saving throw the creature fails.  On the first round, the target takes 5d6 points of sonic damage and is staggered for 1 round. A successful save halves the damage and negates the staggered effect.  On the second round, the target takes 5d6 points of damage and is stunned for 1 round. A successful save halves the damage and negates the stunning effect.  On the third round, the target takes 10d6 points of damage and is stunned for 1d4+1 rounds. A successful save halves the damage and negates the stunning effect.  The resonating word has no power after the third round, even if the spell's duration is increased.}
        
\DeclareSpell{Restore Corpse}{necromancy () []|V,  S|1 standard action|touch|Targetscorpse touched|instantaneous|none|no}[Skeletal corpse grows flesh.]
    \DeclareSpellDescription{Restore Corpse}{You grow flesh on a decomposed or skeletonized corpse of a Medium or smaller creature, providing it with sufficient flesh that it can be animated as a zombie rather than a skeleton. The corpse looks as it did when the creature died. The new flesh is somewhat rotted and not fit for eating.}
        
\DeclareSpell{Restore Eidolon}{conjuration (healing) []|V,  S,  M (diamond dust worth 100 gp or 1, 000 gp,  see text)|1 minute|touch|Targetseidolon touched|instantaneous|Will negates (harmless)|yes (harmless)}[Restoration for an eidolon.]
    \DeclareSpellDescription{Restore Eidolon}{This spell functions as restoration, except it only affects an eidolon.}
        
\DeclareSpell{Restore Eidolon, Lesser}{conjuration (healing) []|V,  S|3 rounds|touch|Targetseidolon touched|instantaneous|Will negates (harmless)|yes (harmless)}[Lesser restoration for an eidolon.]
    \DeclareSpellDescription{Restore Eidolon, Lesser}{This spell functions as lesser restoration, except it only affects an eidolon.}
        
\DeclareSpell{Ride the Lightning}{evocation () [electricity]|V,  S|1 swift action|personal|Targetsyou|1 round/level (D)||}[Transform into electricity.]
    \DeclareSpellDescription{Ride the Lightning}{You may transform into lightning as a standard action and instantly travel in a straight line to a distance of up to 120 feet, rematerializing in the new location as a free action. This movement does not provoke attacks of opportunity. Creatures in this line take 10d6 points of electrical damage and are staggered for 1 round (a successful Reflex save halves the damage and negates the staggered condition, spell resistance applies).
Objects in your path are damaged as well, with combustible objects being set ablaze and metals with low melting points melted. If your path is interrupted by a barrier or otherwise deflected, you materialize short of your final destination in the nearest open space; targets in the line to that point take damage as normal. You are immune to electricity while this spell lasts.}
        
\DeclareSpell{Ride The Waves}{transmutation () [water]|V,  S|1 standard action|touch|Targetscreature touched|1 hour/level (D)|Will negates (harmless)|yes (harmless)}[Target can breathe water and swim.]
    \DeclareSpellDescription{Ride The Waves}{The target gains the ability to breathe water and a swim speed of 30 feet. This swim speed means the target also gains the standard +8 bonus on Swim checks and the ability to take 10 on Swim checks even while distracted or endangered. The target can use the run action while swimming, provided it swims in a straight line. The spell does not make the target unable to breathe air.}
        
\DeclareSpell{Sanctify Corpse}{evocation () [good]|V,  S,  DF,  M (a pinch of silver dust)|1 standard action|touch|Areacorpse touched|24 hours|none|no}[Prevent a corpse from becoming an undead creature.]
    \DeclareSpellDescription{Sanctify Corpse}{This spell blesses a corpse with positive energy, preventing it from being turned into an undead creature. Attempts to raise the corpse as an undead automatically fail. If the corpse is of a person slain by a creature that creates undead out of its slain foes (such as a shadow, vampire, or wraith), that is delayed until the end of this spell. It is possible to protect a corpse for an extended time by casting this spell each day.
Sanctify corpse can be made permanent with a permanency spell by a caster of 9th level or higher for the cost of 500 gp.}
        
\DeclareSpell{Sands of Time}{necromancy () []|V,  S|1 standard action|touch|Targetstouched creature or object|10 minutes/level or instantaneous (see text)|none|yes}[Target temporarily ages.]
    \DeclareSpellDescription{Sands of Time}{You temporarily age the target, immediately advancing it to the next age category. The target immediately takes the age penalties to Strength, Dexterity, and Constitution for its new age category, but does not gain the bonuses for that category.
A creature whose age is unknown is treated as if the spell advances it to middle age. Ageless or immortal creatures are immune to this spell.
If you cast this on an object, construct, or undead creature, it takes 3d6 points of damage + 1 point per caster level (maximum +15) as time weathers and corrodes it. This version of the spell has an instantaneous duration.}
        
\DeclareSpell{Scouring Winds}{evocation () [air,  earth]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Effectsandstorm in 20-ft. radius, 20 ft. high|1 round/level (D)|none|yes (see text)}[Winds block vision and deal 3d6 damage.]
    \DeclareSpellDescription{Scouring Winds}{This spell brings forth a windstorm of stinging sand that blocks all vision. You can move the storm up to 30 feet each round as a move action.  Any creature in the area takes 3d6 points of piercing damage each round. The area is considered a windstorm (see Table 13-10: Wind Effects, Core Rulebook 439).  If a creature with spell resistance successfully resists this spell, it is unaffected by the winds and sand, but still unable to see within the area of the spell.}
        
\DeclareSpell{Sculpt Simulacrum}{transmutation () []|V,  S|1 standard action|touch|Targetssimulacrum touched|instantaneous|Fortitude negates|yes}[Alter a simulacrum's appearance.]
    \DeclareSpellDescription{Sculpt Simulacrum}{You create cosmetic changes to a simulacrum, similar to disguise self, except the changes are physical rather than illusory. This does not change any of the simulacrum's abilities.}
        
\DeclareSpell{Serenity}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone creature/level, no two of which can be more than 30 ft. apart|1 round/level|Will negates|yes}[Peaceful feelings harm those attempting violence.]
    \DeclareSpellDescription{Serenity}{You fill the targets' minds with feelings of tranquility. Those attempting to commit violence become stricken with wracking pain and take 3d6 points of nonlethal damage each round they attempt to harm another creature. If attacked, affected individuals can defend themselves and may participate in combat by using Combat Expertise, fighting defensively, or taking the total defense action without triggering the spell's nonlethal damage.}
        
\DeclareSpell{Shadowbard}{illusion (shadow) [shadow]|V,  S,  M|1 standard action|close (25 ft. +5 ft./2 levels)|Effectphantom singer|1 round/level (D)|none|no}[Shadowy duplicate starts a bardic performance.]
    \DeclareSpellDescription{Shadowbard}{You conjure up a quasi-real phantom singer that is visible as a shifting, shadowy duplicate of yourself. The singer follows you automatically, moving as you move even if you teleport.
The singer cannot be damaged, but can be dispelled. When a shadowbard comes into being, it immediately begins a bardic performance of your choice-it has access to all of the bardic performances that you do. It continues that bardic performance until you direct it as a move action to switch to a different performance. Rounds spent by a shadowbard creating a bardic performance do not decrease the number of rounds you can use your own bardic performance, nor can a shadowbard's bardic performance be used to trigger spells that require you to begin or cease a bardic performance.}
        
\DeclareSpell{Shadow Step}{illusion (shadow) [shadow]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targetsyou|instantaneous|none|no}[Teleport from one shadow to another.]
    \DeclareSpellDescription{Shadow Step}{To use this spell, you must be in an area of dim light or darkness. You enter a shadow or area of darkness, which transports you along a coiling path of shadowstuff to another dim or dark location within range.}
        
\DeclareSpell{Shadow Weapon}{illusion (shadow) [shadow]|V,  S|1 standard action|0 ft.|Effectone shadow weapon|1 minute/level|Will disbelief (if interacted with)|yes}[Create a quasi-real masterwork weapon.]
    \DeclareSpellDescription{Shadow Weapon}{Drawing upon the Plane of Shadow, you shape a quasi-real masterwork melee weapon of a type you are proficient with. You may use this weapon to make attacks as if it were a real weapon, dealing normal damage for a weapon of its type. The first time you hit a creature with the weapon, it may make a Will save to disbelieve; failure means the weapon deals damage normally, success means it only takes 1 point of damage from the weapon's attacks. The weapon only deals 1 point of damage to objects.  If an attacked creature has spell resistance, you make a caster level check (1d20 + caster level) against that spell resistance the first time the shadow weapon strikes it. If the weapon is successfully resisted, the spell is dispelled. If not, the target may save to disbelieve as normal.  At 5th level, the weapon gains a +1 enhancement bonus. At 10th-level, you may increase the enhancement bonus to +2 or add the frost or keen weapon property. The frost and keen properties have no effect if the target makes its disbelief save.  The spell ends if the weapon leaves your possession.}
        
\DeclareSpell{Shard of Chaos}{evocation () [chaos]|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectdart-shaped projectile of chaotic energy|instantaneous (1d6 rounds)|Will partial (see text)|yes}[Harm and possibly slow lawful creatures.]
    \DeclareSpellDescription{Shard of Chaos}{You hurl a multicolored shard of congealed chaos from your holy symbol, affecting any one target in range as a ranged touch attack.
A lawful creature struck by the shard takes 1d8 points of damage per two caster levels (maximum 5d8). A lawful outsider instead takes 1d6 points of damage per caster level (maximum 10d6) and is slowed (as slow) for 1 round. A successful Will save reduces the damage to half and negates the slow effect. The bolt has no effect on chaotic creatures. This spell deals only half damage to creatures that are neither lawful nor chaotic, and they are not slowed.}
        
\DeclareSpell{Share Memory}{divination () []|V,  S|1 standard action|touch|Targetsyou and one creature touched|instantaneous|Will negates|yes}[Share one memory with the target.]
    \DeclareSpellDescription{Share Memory}{You momentarily link your mind with the target and share a single memory of no longer than 1 minute. You can show the target one of your memories, show the target one of its own memories, or view one of the target's memories.}
        
\DeclareSpell{Simulacrum, Lesser}{illusion (shadow) []|V,  S,  M (an ice sculpture of the target plus powdered rubies worth 50 gp per HD of the simulacrum)|1 hour|0 ft.|Effectone duplicate creature|1 hour/level|none|no}[Creates a double of a weak creature.]
    \DeclareSpellDescription{Simulacrum, Lesser}{This spell functions as simulacrum, except you can't create a simulacrum of a creature whose HD or levels exceed your caster level, and it has no magical abilities. The creature is not under your control, though it recognizes you are its creator.}
        
\DeclareSpell{Skinsend}{necromancy () []|V,  S|1 minute|personal|Targetsyou|1 hour/level (D)||}[Animate and possess your own skin as if it were a separate creature.]
    \DeclareSpellDescription{Skinsend}{You cause your own skin to peel off your body and animate as a magical creature you control. You may project your consciousness to your animated skin or return it to your actual body as a standard action. When your consciousness is in your body, you are helpless (except for transferring your will to your skin, or dismissing the spell).
Your possessed skin is identical to you in all ways, except the following: It has only half the number of hit points you had at the time you cast the spell, and cannot be healed above this maximum; construct type, traits, and immunities; Str 3, Con -; DR 10/piercing or slashing; and compression (as the universal monster ability, Bestiary 2 295). Your skin can take any actions you could normally take in your own body (such as to fight or cast spells).
When your skin leaves your body, your body's hit points drop to 0. Your body cannot heal damage naturally while you have no skin, nor do spells that cure hit point damage work on your body; only regeneration (from a regenerate spell, ring of regeneration, the regeneration monster ability, or any other effect that can regrow missing limbs) or heal can regrow your skin and allow you heal above 0 hit points.
If your body is regenerated before your skin returns to it, the skin dies and your consciousness returns automatically to your body. Your skin can be preserved with gentle repose and is suitable for any purpose that requires some of your flesh (such as a resurrection spell) or any magic or ritual that requires a creature's skin.
When your skin returns to your body, you regain hit points equal to your skin's remaining hit points. If the spell ends before you reunite with your skin or if your skin is killed while you are in your body, you remain helpless and at 0 hit points until your full body is restored to you (requiring powerful magic, as described above). If your body dies while you are possessing your skin, you die when the spell ends, regardless of how many hit points the skin has left. If your body or skin is slain with your consciousness in it, the spell ends and you are instantly killed.
This spell leaves long scars on your skin where it split apart, although these fade normally with the use of healing magic.}
        
\DeclareSpell{Smug Narcissism}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S,  M (a tiny shard of a mirror)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|10 minute/level (D)|Will negates|yes}[Target is distracted by its sense of self.]
    \DeclareSpellDescription{Smug Narcissism}{You cause your target to become overwhelmed by its own importance, talents, and attractiveness. The target cannot help but look at itself in every reflective surface at every possible opportunity. In social situations, the target always tries to comment about how attractive it is or how ugly someone else is by comparison. The target remains constantly distracted, always looking for a reflective surface to gaze upon (such as a mirror, pool of water, a polished shield, and so on). The distraction gives the target a -2 penalty on all skill checks. In combat, the target worries about enemies damaging its appearance, and focuses on defense rather than offense (casting defensive spells rather than offensive spells, using the fight defensively or total defense action, and so on).}
        
\DeclareSpell{Snapdragon Fireworks}{transmutation () [fire,  light]|S,  V,  M (a bundle of sulfur wrapped in cloth)|1 standard action|long (400 ft. + 40 ft./level)|Effectdragon-shaped fireworks|1 round/level|Reflex negates|yes}[Create 1 dragon firework/level.]
    \DeclareSpellDescription{Snapdragon Fireworks}{A favorite display at halfling midsummer festivals, this spell lets you create fireworks in the shape of tiny dragons.
Once per round, as a move action, you may designate a target 5-foot-square within range and launch a pyrotechnic in that direction. The pyrotechnic takes a zigzag path from you to that square, always missing creatures and objects in its path, and detonates in that square with a bang and a colorful burst of fire and light. Creatures in the target square take 1d4 points of fire damage and are dazzled for 1 round (Reflex half, a successful save negates the dazzled condition).
Normally when this spell is used as part of a festival, the chosen target is high in the sky to increase visibility and protect observers.}
        
\DeclareSpell{Sonic Thrust}{evocation () [sonic]|V,  S|1 standard action|long (400 ft. + 40 ft./level)|Targetssee text|instantaneous|Will negates (object) or none (see text)|yes (object) (see text)}[Sound moves targets away from you.]
    \DeclareSpellDescription{Sonic Thrust}{You produce a sweeping rush of sound that can hurl creatures or objects away from you, like the violent thrust version of telekinesis. You can hurl one object or creature per caster level (maximum 15) that is within range; it flies in a straight line away from you. Any objects of creatures thrown must be within 10 feet of each other. You can hurl a total weight of up to 25 pounds per caster level (maximum 375 pounds at 15th level).
You can use this spell to hurl an object or creature toward a particular target. You must succeed on attack rolls (one per creature or object thrown) to hit the target with the items, using your base attack bonus + your Intelligence modifier (if a wizard) or Charisma modifier (if a bard or sorcerer). Hurled weapons cause standard damage (with no Strength bonus; note that arrows or bolts deal damage as daggers of their size when used in this manner). Other objects cause damage ranging from 1 point per 25 pounds (for less dangerous objects) to 1d6 points of damage per 25 pounds (for hard, dense objects). Objects and creatures that miss their target land in a square adjacent to the target.
Creatures that fall within the weight capacity of the spell can be hurled, but they are allowed Will saves (and spell resistance) to negate the effect, as are those whose held possessions are targeted by the spell.
If a hurled creature is thrown against a solid surface, it takes damage as if it had fallen 10 feet (1d6 points).}
        
\DeclareSpell{Soothe Construct}{abjuration () []|V,  S|1 round|close (25 ft. + 5 ft./2 levels)|Targetsone construct|instantaneous|none|no}[Reduce the berserk chance of a construct.]
    \DeclareSpellDescription{Soothe Construct}{You soothe the elemental spirit of a targeted construct, reducing its chance of going berserk by 1d4\% per four caster levels (maximum 5d4\%). If cast on a construct that has already gone berserk and you are its master, you may immediately roll d\% to end the construct's berserk state, it returns to normal functioning, and its berserk chance returns to 0\%.}
        
\DeclareSpell{Spear Of Purity}{evocation () [good]|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectspear-shaped projectile of good energy|instantaneous (1 round)|Will partial (see text)|yes}[Harm and possibly blind evil creatures.]
    \DeclareSpellDescription{Spear Of Purity}{You hurl a pure white or golden spear of light from your holy symbol, affecting any one target within range as a ranged touch attack.  An evil creature struck by the spear takes 1d8 points of damage per two caster levels (maximum 5d8). An evil outsider instead takes 1d6 points of damage per caster level (maximum 10d6) and is blinded for 1 round. A successful Will save reduces the damage to half and negates the blinded effect. This spell deals only half damage to creatures that are neither evil nor good, and they are not blinded. The spear has no effect on good creatures.}
        
\DeclareSpell{Spit Venom}{transmutation () [poison]|V|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectone stream of venom|instantaneous; see text|Fortitude partial|no}[Spit blinding black adder venom.]
    \DeclareSpellDescription{Spit Venom}{You spit a stream of venom at a target using a ranged touch attack. If the venom hits, it causes blindness for 1 round. The target must also save or be poisoned by black adder venom; the DC in successive rounds of the poison is equal to the spell's DC.}
        
\DeclareSpell{Steal Voice}{necromancy () []|V|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone creature|permanent (D)|Fortitude negates|yes}[Target gains the croaking spellblight.]
    \DeclareSpellDescription{Steal Voice}{The target's throat constricts, giving it the caster croak spellblight (see page 95).}
        
\DeclareSpell{Strangling Hair}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|concentration, up to 1 round/level|none|yes}[Your hair animates and grapples.]
    \DeclareSpellDescription{Strangling Hair}{Your hair animates and extends to grapple and constrict an opponent. Make a grapple check against the target using your caster level as the base attack bonus plus a bonus equal to your Intelligence bonus (if a witch or wizard) or Charisma bonus (if a sorcerer). This grapple check does not provoke attacks of opportunity. If your hair succeeds in grappling a foe, that creature takes 1d6 points of damage or your unarmed strike damage, whichever is greater, and gains the grappled condition. Your hair receives a +5 bonus on grapple checks made against opponents it is already grappling, but cannot move foes or pin foes. Each round that your hair succeeds on a grapple check, it deals an additional 1d6 points of damage. The CMD of your hair, for the purposes of escaping the grapple, is equal to 10 + its CMB.  Once you choose a target, your hair continues to attack that target independently of your own actions. You may designate a new target as a move action, which causes your hair to release its current target (if any) and attack the new target that round. Your hair cannot be targeted as a separate creature, but it can be dispelled.}
        
\DeclareSpell{Summon Elder Worm}{conjuration (summoning) []|V,  S|1 round|close (25 ft. + 5 ft./2 levels)|Effectone summoned creature|1 round/level (D)|none|no}[Summon a giant purple worm.]
    \DeclareSpellDescription{Summon Elder Worm}{This spell functions as summon nature's ally VIII, except you summon a purple worm with the giant creature simple template (Bestiary 295).}
        
\DeclareSpell{Summon Froghemoth}{conjuration (summoning) []|V,  S|1 round|close (25 ft. + 5 ft./2 levels)|Effectone summoned creature|1 round/level (D)|none|no}[Summon a froghemoth.]
    \DeclareSpellDescription{Summon Froghemoth}{This spell functions as summon nature's ally IX, except you summon a froghemoth (Bestiary 136).}
        
\DeclareSpell{Summon Minor Ally}{conjuration (summoning) []|V,  S,  DF|1 round|close (25 ft. + 5 ft./2 levels)|Effect1d3 summoned creatures|1 round/level (D)|none|no}[Summon 1d3 Tiny animals.]
    \DeclareSpellDescription{Summon Minor Ally}{This spell functions as summon nature's ally I, except you can summon 1d3 Tiny or smaller animals, such as bats, lizards, monkeys, rats, ravens, toads, or weasels. The summoned animals must all be the same type of creature.}
        
\DeclareSpell{Summon Minor Monster}{conjuration (summoning) []|V,  S,  F/DF (a tiny bag and a small candle)|1 round|close (25 ft. + 5 ft./2 levels)|Effect1d3 summoned creatures|1 round/level (D)|none|no}[Summon 1d3 Tiny animals.]
    \DeclareSpellDescription{Summon Minor Monster}{This spell functions as summon monster I, except you can summon 1d3 Tiny or smaller animals, such as bats, lizards, monkeys, rats, ravens, toads, or weasels. The summoned animals must all be the same type of creature. As with animals summoned with summon monster I, you may apply one alignment-appropriate template to these animals.}
        
\DeclareSpell{Surmount Affliction}{abjuration () []|V,  S|1 standard action|you|Targetspersonal|1 round/level||}[Temporarily suppress one condition.]
    \DeclareSpellDescription{Surmount Affliction}{You temporarily overcome one harmful condition. This does not end the effect causing the condition; it just suspends that condition's effect for the duration of the spell. You can surmount any one of the following conditions: blinded, confused, dazed, dazzled, deafened, fatigued, frightened, paralyzed, shaken, or sickened.}
        
\DeclareSpell{Symbol of Healing}{conjuration (healing) []|V,  S,  M (mercury and phosphorous,  plus powdered diamond and opal worth a total of 500 gp)|10 minutes|0 ft.; see text|Effectone symbol|see text|Will half (harmless) (see text)|yes (harmless) (see text)}[Triggered rune heals living creatures.]
    \DeclareSpellDescription{Symbol of Healing}{This spell functions as symbol of death, except all creatures within 60 feet of the symbol of healing instead are bathed in positive energy and heal 2d8 points + 1 point of damage per caster level (maximum +15). Undead and other creatures harmed by positive energy instead take 2d8 points of damage + 1 point per caster level (maximum +15); a Will save reduces this damage by half. A creature can only be healed or harmed by the symbol once in any 24-hour period. Once triggered, the symbol remains active for 10 minutes per caster level.
Symbol of healing can be made permanent with a permanency spell by a caster of 10th level or higher for the cost of 10,000 gp.}
        
\DeclareSpell{Symbol of Mirroring}{illusion (figment) []|V,  S,  M (mercury and phosphorous,  plus powdered diamond and opal worth a total of 100 gp)|10 minutes|0 ft.; see text|Effectone symbol|see text|Will partial (harmless)|yes}[Triggered rune creates mirror images.]
    \DeclareSpellDescription{Symbol of Mirroring}{This spell functions as symbol of death, except it instead creates one illusory duplicate of each creature within 60 feet of the symbol. These duplicates function as mirror image, moving with the original creatures and mimicking their movements, sounds, and actions exactly. If an illusory double is destroyed, a new one appears on the creature's turn. The images last for as long as a creature remains within 60 feet of the symbol, and for 1 round/level thereafter. Once triggered, the symbol remains active for 10 minutes per caster level.
Symbol of mirroring can be made permanent with a permanency spell by a caster of 10th level or higher for the cost of 5,000 gp.}
        
\DeclareSpell{Symbol of Revelation}{divination () []|V,  S,  M (mercury and phosphorous,  plus powdered diamond and opal worth a total of 1, 000 gp)|10 minutes|0 ft.; see text|Effectone symbol|see text|none|yes}[Triggered symbol reveals illusions.]
    \DeclareSpellDescription{Symbol of Revelation}{This spell functions as symbol of death, except it is only activated by invisible creatures, creatures affected by an illusion (glamer) effect, creatures with the shapechanger subtype, or creatures that have magically changed their shape. These creatures are outlined by a pale light that functions like faerie fire, except it lasts for 10 minutes per caster level; the symbol does not otherwise reveal their true form. Once triggered, a symbol of revelation remains active for 10 minutes per caster level.
Symbol of revelation can be made permanent with a permanency spell by a caster of 12th level or higher for the cost of 10,000 gp.}
        
\DeclareSpell{Symbol of Scrying}{divination (scrying) []|V,  S,  M (mercury and phosphorous,  plus powdered diamond and opal worth a total of 1, 000 gp)|10 minutes|0 ft.; see text|Effectone symbol|see text|none|no}[Triggered rune activates scrying sensor.]
    \DeclareSpellDescription{Symbol of Scrying}{This spell functions as symbol of death, except that, when triggered, it creates a scrying sensor linked to you and centered on the symbol, even if you are on a different plane than the symbol. You are immediately aware that the symbol has been triggered if you are conscious, and are awakened from normal sleep if sleeping. The symbol does not otherwise disturb your concentration. You may observe the area through the symbol as if using a scrying spell with the sensor as the target creature. Once triggered, the symbol remains active for 10 minutes per caster level.
Unlike symbol of death, a symbol of scrying is not considered a magical trap. Symbol of scrying can be made permanent with a permanency spell by a caster of 13th level or higher for the cost of 10,000 gp.}
        
\DeclareSpell{Symbol of Sealing}{abjuration () [force]|V,  S,  M (mercury and phosphorous,  plus powdered diamond and opal worth a total of 5, 000 gp)|10 minutes|0 ft.; see text|Effectone symbol|permanent|none|no}[Create triggered wall of force.]
    \DeclareSpellDescription{Symbol of Sealing}{This spell allows you to scribe a potent rune of power upon or above a door or other opening measuring no more than 20 square feet/level in size. When the casting is completed, the symbol immediately triggers, glowing visibly and sealing the door or opening with an invisible barrier of force equivalent to a wall of force. Destroying the symbol ends the effect, though destroying it once the symbol has been activated requires destroying the wall of force first. Once triggered, the wall remains for 10 minutes per caster level.
When scribing a symbol of sealing, you can specify a password or phrase that allows a creature speaking it to bypass the seal and pass through the opening. You can also attune any number of creatures to the symbol of sealing, but doing this extends the casting time as described under symbol of death (Core Rulebook 355). However, the force wall created by the symbol blocks attacks and line of effect even for creatures that know the password or are attuned-the password only prevents them from triggering the symbol, not from ignoring its effects if triggered.
A disintegrate spell or similar effect can destroy the wall of force created by the symbol if the caster makes a caster level check against a DC of 11 + your caster level. A knock spell has no effect on a symbol of sealing or its force wall. A symbol of sealing cannot be dispelled, but mage's disjunction automatically destroys it.}
        
\DeclareSpell{Symbol of Slowing}{transmutation () []|V,  S,  M (mercury and phosphorous,  plus powdered diamond and opal worth a total of 1, 000 gp)|10 minutes|0 ft.; see text|Effectone symbol|see text|Will negates|yes}[Triggered rune slows creatures.]
    \DeclareSpellDescription{Symbol of Slowing}{This spell functions as symbol of death, except all creatures within 60 feet of a symbol of slowing are slowed (as the slow spell) for 1 round per caster level.
Symbol of slowing can be made permanent with a permanency spell by a caster of 11th level or higher for the cost of 10,000 gp.}
        
\DeclareSpell{Symbol of Strife}{enchantment (compulsion) [mind-affecting]|V,  S,  M (mercury and phosphorous,  plus powdered diamond and opal worth a total of 15, 000 gp)|10 minutes|0 ft.; see text|Effectone symbol|see text|Will negates|yes}[Triggered rune makes creatures attack.]
    \DeclareSpellDescription{Symbol of Strife}{This spell functions as symbol of death, except all creatures within the radius of a symbol of strife are compelled to attack the nearest conscious creaturefor 1 round per caster level (similar to the "attack nearest creature" result of the confusion spell), even after leaving the symbol's area of effect. If no other creatures are visible, an affected creature can act normally. Once triggered, the symbol remains active for 10 minutes per caster level.
Symbol of strife can be made permanent with a permanency spell by a caster of 18th level or higher for the cost of 25,000 gp.}
        
\DeclareSpell{Symbol of Vulnerability}{abjuration () []|V,  S,  M (mercury and phosphorous,  plus powdered diamond and opal worth a total of 15, 000 gp)|10 minutes|0 ft.; see text|Effectone symbol|see text|none|no}[Triggered rune gives penalties.]
    \DeclareSpellDescription{Symbol of Vulnerability}{This spell functions as symbol of death, except it saps the defenses of all creatures within 60 feet. Affected creatures receive a -4 penalty to spell resistance and a -4 penalty on saving throws, and energy resistances and damage reduction (if any) are reduced by 10 each (to a minimum of 0). Once triggered, the symbol remains active for 10 minutes per level.
The effects last as long as the creature is within 60 feet of the symbol, and for 1 round per caster level afterward.
Symbol of vulnerability can be made permanent with a permanency spell by a caster of 18h level or higher for the cost of 25,000 gp.}
        
\DeclareSpell{Tar Ball}{transmutation () []|V,  S,  M (a tiny ball of bitumen)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectranged attack|instantaneous|none|no}[Burning tar harms target and penalizes its Dex.]
    \DeclareSpellDescription{Tar Ball}{You create a sticky ball of burning tar that you can hurl at your enemies as a ranged attack. If the tar ball strikes, it deals 1d4 points of fire damage + your Strength modifier, and splashes the target with hot, sticky tar. The tar deals 1d4 points of fire damage each round on the creature's turn for the next 1d4 rounds and gives the target a -2 penalty to Dexterity for that duration. If desired, the target can use a full-round action to attempt to extinguish or cool the tar before taking this additional damage.
Extinguishing or cooling the tar requires a DC 15 Reflex save or at least 1 gallon of nonflammable liquid. Rolling on the ground provides the target a +2 bonus on the save. Leaping into a lake or magically cooling the target automatically ends the effect.}
        
\DeclareSpell{Temporary Resurrection}{necromancy () []|V,  S,  M (diamond dust worth 500 gp)|10 minutes|touch|Targetsdead creature touched|24 hours||}[Bring a creature to life for 24 hours, after which it dies again.]
    \DeclareSpellDescription{Temporary Resurrection}{You restore temporary life to a body that has been dead for less than 48 hours. The spell lasts for 24 hours, after which the target dies again. The target gains 1 permanent negative level while under the effect of this spell; this negative level goes away when the target dies or is permanently raised from the dead (such as with raise dead). The target still counts as a dead corpse (but not undead) for the purpose of spells that revive dead creatures, so a cleric can cast raise dead or a similar spell on the target even while this spell is active. Once a creature has been revived with temporary resurrection, this spell cannot be used on it again until it is permanently raised from the dead.}
        
\DeclareSpell{Terrible Remorse}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets1 living creature|1 round/level|Will partial (see text)|yes}[Creature is compelled to harm itself.]
    \DeclareSpellDescription{Terrible Remorse}{You fill a target with such profound remorse that it begins to harm itself. Each round, the target must save or deal 1d8 points of damage + its Strength modifier to itself using an item held in its hand or with unarmed attacks. If the creature saves, it is staggered for 1 round and takes a -2 penalty to Armor Class, after which the spell ends.}
        
\DeclareSpell{Touch of Slime}{conjuration (creation) [disease]|V,  S,  M (a drop of acid and a black glass sphere)|1 standard action|touch|Targetsliving creature touched|instantaneous|Fortitude negates|yes}[Touch infests a target with green slime.]
    \DeclareSpellDescription{Touch of Slime}{You create a coating of slime on your hand. When you make a successful melee touch attack with the slime, it pulls free of you and sticks to the target, at which point it acts like green slime (Core Rulebook 416), dealing 1d3 points of Constitution damage per round. Anything that destroys green slime (scraping, freezing, burning, cutting, sunlight, or remove disease) destroys this slime. If the slime kills a creature, it consumes the body and then dies. It cannot transfer to a creature other than the original target, and dies if separated from the original target.}
        
\DeclareSpell{Toxic Gift}{necromancy () [poison]|V,  S|1 standard action|touch|Targetsliving creature touched|instantaneous; see text|Fortitude negates (see text)|yes}[Target suffers the effect of the poison in you.]
    \DeclareSpellDescription{Toxic Gift}{You can cast this spell only if you are currently poisoned. You draw upon the poison in your body and duplicate its effects in the target, which is affected by the same poison you are, except it uses this spell's DC instead of the poison's normal DC. If you are affected by more than one poison, you must choose one to afflict upon the target.}
        
\DeclareSpell{Transmute Blood To Acid}{transmutation () [acid,  pain]|V,  S,  M (a wax doll and a vial of acid worth 10 gp)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone living creature|concentration (maximum 1 round/5 levels)|Fortitude half|yes}[Target takes acid damage each round, and its attackers take acid damage.]
    \DeclareSpellDescription{Transmute Blood To Acid}{You transmute blood in the target's body to acid, dealing 1d6 points of acid damage/2 levels (maximum 12d6) each round.
The creature is staggered and sickened by the debilitating pain. A successful Fortitude save each round halves the damage and negates the staggered condition for 1 round. If this damage reduces the creature to 0 or fewer hit points, it dissolves, leaving only the barest trace of remains. A dissolved creature's equipment is unaffected.
Anyone who strikes the target with a non-reach melee weapon, natural weapon, or unarmed attack takes 3d6 points of acid damage as the acidic blood sprays on the attacker. If the attack is from a piercing or slashing manufactured weapon, the weapon also takes this damage.
This spell has no effect on creatures immune to critical hits or bleed effects.}
        
\DeclareSpell{Unadulterated Loathing}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S,  M|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 day/level|Will negates|yes}[Target is compelled to avoid another creature.]
    \DeclareSpellDescription{Unadulterated Loathing}{You fill the target with a terrible loathing aimed at a specific creature. At the time of the casting, you designate a single creature as the object of the target's revulsion. Thereafter, the target does all it can to remain at least 60 feet away from the object of its loathing. As soon as the target moves within this range, it becomes nauseated until it can again get away from the object of its revulsion. If traveling beyond 60 feet of the object of its loathing would place the target in obvious physical danger, the target can attempt a second save to break the spell's effect.
Unadulterated loathing counters reckless infatuation.}
        
\DeclareSpell{Unbreakable Construct}{abjuration () []|V,  S,  M (powdered adamantine worth 100 gp)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone construct|1 round/level|Will negates (harmless)|no}[Increase construct hardness or DR.]
    \DeclareSpellDescription{Unbreakable Construct}{This spell increases the target's DR/adamantine by 5 or its hardness by 5. If the target does not have DR/adamantine or hardness, this spell has no effect.}
        
\DeclareSpell{Undead Anatomy I}{transmutation (polymorph) []|V,  S,  M (a piece of the creature whose form you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)||}[Take the form and some of the powers of a Small or Medium undead.]
    \DeclareSpellDescription{Undead Anatomy I}{When you cast this spell, you can assume the form of any Small or Medium corporeal creature of the undead type, which must be vaguely humanoid-shaped (like a ghoul, skeleton, or zombie). You gain a bite attack (1d6 for Medium forms, 1d4 for Small forms), two claw or slam attacks (1d6 for Medium forms, 1d4 for Small forms), and darkvision 60 feet. If the form you assume has any of the following abilities, you gain the listed ability: climb 30 feet, fly 30 feet (average maneuverability), swim 30 feet, low-light vision, and scent.
In this form, you detect as an undead creature (such as with detect undead, but not with magic that reveals your true form, such as true seeing) and are treated as undead for the purposes of channeled energy, cure spells, and inflict spells, but not for other effects that specifically target or react differently to undead (such as searing light).
Small undead: If the form you take is that of a Small undead, you gain a +2 size bonus to your Dexterity and a +1 natural armor bonus.
Medium undead: If the form you take is that of a Medium undead, you gain a +2 size bonus to your Strength and a +2 natural armor bonus.}
        
\DeclareSpell{Undead Anatomy II}{transmutation (polymorph) []|V,  S,  M (a piece of the creature whose form you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)||}[Take the form and some of the powers of a Tiny or Large undead.]
    \DeclareSpellDescription{Undead Anatomy II}{This spell functions as undead anatomy I, except it also allows you to assume the form of a Tiny or Large corporeal creature of the undead type. If the form you assume has any of the following abilities, you gain the listed ability: climb 60 feet, fly 60 feet (good maneuverability), swim 60 feet, darkvision 60 feet, low-light vision, blood drain, DR 5/bludgeoning, scent, freeze, grab, mimicry, pounce, shadowless, sound mimicry, and trip.
In this form, you gain a +4 bonus on saves against mindaffecting effects, disease, poison, sleep, and stunning. If the form has a vulnerability to an attack (such as sunlight), you gain that vulnerability.
Tiny undead: If the form you take is that of a Tiny undead, you gain a +4 size bonus to your Dexterity, a -2 penalty to your Strength, and a +1 natural armor bonus.
Large undead: If the form you take is that of a Large undead, you gain a +4 size bonus to your Strength, a -2 penalty to your Dexterity, and a +4 natural armor bonus.}
        
\DeclareSpell{Undead Anatomy III}{transmutation (polymorph) []|V,  S,  M (a piece of the creature whose form you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)||}[Take the form and some of the powers of a Diminutive or Huge undead.]
    \DeclareSpellDescription{Undead Anatomy III}{This spell functions as undead anatomy II, except it also allows you to assume the form of a Diminutive or Huge corporeal creature of the undead type. If the form you assume has any of the following abilities, you gain the listed ability: burrow 30 feet, climb 90 feet, fly 90 feet (good maneuverability), swim 90 feet, all-around vision, blindsense 30 feet, darkvision 60 feet, low-light vision, scent, constrict, disease, DR 5/-, fear aura, grab, jet, natural cunning, overwhelming, poison, pounce, rake, trample, trip, unnatural aura, and web.
If the creature has immunity or resistance to any energy types, you gain resistance 20 to those energy types. If the creature has vulnerability to an energy type, you gain that vulnerability. In this form, you gain a +8 bonus on saves against mind-affecting effects, disease, poison, sleep, and stunning. If the form has a vulnerability to an attack (such as sunlight), you gain that vulnerability.
Diminutive undead: If the form you take is that of a Diminutive undead, you gain a +6 size bonus to your Dexterity, a -4 penalty to your Strength, and a +1 natural armor bonus.
Huge undead: If the form you take is that of a Huge undead, you gain a +6 size bonus to your Strength, a -4 penalty to your Dexterity, and a +6 natural armor bonus.}
        
\DeclareSpell{Undead Anatomy IV}{transmutation (polymorph) []|V,  S,  M (a piece of the creature whose form you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D) (see text)||}[As undead anatomy III, but with more abilities.]
    \DeclareSpellDescription{Undead Anatomy IV}{This spell functions as undead anatomy III, except it allows you to use more abilities. If the form you assume has any of the following abilities, you gain the listed ability: burrow 60 feet, climb 90 feet, fly 120 feet (good maneuverability), swim 120 feet, blindsense 60 feet, darkvision 90 feet, lifesense 60 feet, low-light vision, scent, tremorsense 60 feet, breath weapon, constrict, DR 10/magic and silver, DR 15/bludgeoning and magic, fast healing 5, fiery death, fire aura, grab, incorporeal, jet, poison, pounce, rake, rend, roar, spikes, trample, trip, and web.
If the creature's form is incorporeal, the spell's duration is in rounds per level instead of minutes per level, and your bite and claw (or slam) attacks are incorporeal touch attacks. If the creature has immunity or resistance to any energy types, you gain resistance 30 to those energy types. If the creature has vulnerability to an energy type, you gain that vulnerability.
In this form, you gain a +8 bonus on saves against mindaffecting effects, disease, poison, sleep, and stunning. If the form has a vulnerability to an attack (such as sunlight), you gain that vulnerability.
Tiny undead: If the form you take is that of a Tiny undead, you gain a -2 penalty to your Strength, a +8 size bonus to your Dexterity, and a +3 natural armor bonus.
Large undead: If the form you take is that of a Large undead, you gain a +6 size bonus to your Strength, a -2 penalty on your Dexterity, a +2 size bonus to your Constitution, and a +6 natural armor bonus.}
        
\DeclareSpell{Unholy Ice}{transmutation () [cold,  evil,  water]|V,  S,  M (a flask of unholy water or 5 pounds of powdered silver worth 25 gp)|1 standard action|medium (100 ft. + 10 ft./level)|Effectwall of ice or flying ice javelins (see text)|1 minute/level, instantaneous, or until expended (see text)|Reflex negates or none (see text)|yes}[Create wall or javelins of frozen unholy water.]
    \DeclareSpellDescription{Unholy Ice}{This spell functions as holy ice, except it is made of frozen unholy water rather than holy water.}
        
\DeclareSpell{Unholy Sword}{evocation () [evil]|V,  S|1 standard action|touch|Targetsmelee weapon touched|1 round/level|none|no}[Weapon becomes +5, deals +2d6 damage vs. good.]
    \DeclareSpellDescription{Unholy Sword}{This spell allows you to channel the powers of evil into your sword, or any other melee weapon you choose. The weapon acts as a +5 unholy weapon (+5 enhancement bonus on attack and damage rolls, extra 2d6 damage against good opponents).
It also emits a magic circle against good effect (as the spell). If the magic circle ends, the sword creates a new one on your turn as a free action. The spell is automatically canceled 1 round after the weapon leaves your hand. You cannot have more than one unholy sword at a time.
If this spell is cast on a magic weapon, the powers of the spell supersede any that the weapon normally has, rendering the normal enhancement bonus and powers of the weapon inoperative for the duration of the spell. This spell is not cumulative with any spells that modify the weapon in any way.
This spell does not work on artifacts. A masterwork weapon's bonus to attack does not stack with this spell's enhancement bonus to attack.}
        
\DeclareSpell{Unnatural Lust}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 round|Will negates|yes}[Target is compelled to kiss or caress another.]
    \DeclareSpellDescription{Unnatural Lust}{Your target is filled with lust and desire for a single creature or object as designated by you at the time of casting. That creature or object must be within the spell's range and perceivable by the target of the spell. The target is filled with the compulsion to rush to the subject of its lust and passionately kiss or caress that subject on its next turn, taking no other actions. If the target would not normally have lustful feelings toward the designated creature or object, it receives a +4 bonus on its saving throw.}
        
\DeclareSpell{Unprepared Combatant}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 minute/level|Will negates|yes}[Target takes –4 on initiative and Reflex saves.]
    \DeclareSpellDescription{Unprepared Combatant}{The target takes a -4 penalty on initiative checks and Reflex saves.}
        
\DeclareSpell{Unshakable Chill}{necromancy () [cold]|V,  S,  M|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|10 minutes/level; see text|Fortitude negates (see text)|yes}[Target is afflicted with severe cold.]
    \DeclareSpellDescription{Unshakable Chill}{The target is filled with an unshakable chill for the duration of the spell, and suffers from the effects of severe cold (Core Rulebook 442). Severe cold means if the initial saving throw fails, the target takes 1d6 points of nonlethal cold damage and must save every 10 minutes (using the DC of severe cold instead of this spell's DC) or take additional damage.}
        
\DeclareSpell{Utter Contempt}{enchantment () [emotion]|V,  S,  M (spittle)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 minute/level|Will negates|yes}[Target's attitude worsens by two categories.]
    \DeclareSpellDescription{Utter Contempt}{You fill the target's heart with malice for all other creatures.
The target's attitude toward all creatures other than itself worsens by two steps.}
        
\DeclareSpell{Vengeful Outrage}{enchantment (compulsion) [emotion,  language-dependent,  mind-affecting]|V,  S|1 round|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 minute/level|Will negates|yes}[Target is compelled to destroy one enemy.]
    \DeclareSpellDescription{Vengeful Outrage}{You place a magical command upon a creature to seek out and destroy a single enemy that has inflicted some perceived or actual harm to the target. You designate the enemy at the time of casting, which must be known by the target (such as "your brother's murderer") or can easily identify by sight (such as "the hill giant king"). The target is under the of a geas to find and capture or kill this enemy, and the target takes the penalties of that spell as long as it is not actively trying to reach the enemy. When the target enters combat with the enemy, it gains a +6 morale bonus to Strength and Constitution, a +3 morale bonus on Will saves, and is immune to the shaken and frightened conditions.
If you designate one of the target's friends or loved ones as the enemy, the target gains another saving throw to overcome the spell as soon as it enters combat with the enemy.}
        
\DeclareSpell{Vermin Shape I}{transmutation (polymorph) []|V,  S,  M (a piece of the creature whose form you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level||}[Take the form and some of the powers of a Small or Medium vermin.]
    \DeclareSpellDescription{Vermin Shape I}{When you cast this spell, you assume the form of any Small or Medium creature of the vermin type. If the form you assume has any of the following abilities, you gain the listed ability: climb 30 feet, fly 30 feet (average maneuverability), swim 30 feet, darkvision 60 feet, low-light vision, scent, and lunge. You don't gain full immunity to mind-affecting effects, but you do gain a +2 resistance bonus on all saving throws against such effects.
Small vermin: If you take the form of a Small vermin, you gain a +2 size bonus to your Dexterity and a +2 natural armor bonus.
Medium vermin: If you take the form of a Medium vermin, you gain a +2 size bonus to your Strength and a +3 natural armor bonus.}
        
\DeclareSpell{Vermin Shape II}{transmutation (polymorph) []|V,  S,  M (a piece of the creature whose form you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level||}[As vermin shape, but Tiny or Large.]
    \DeclareSpellDescription{Vermin Shape II}{This spell functions as vermin shape I, except it also allows you to assume the form of a Tiny or Large creature of the vermintype. If the form you assume has any of the following abilities, you gain the listed ability: burrow 30 feet, climb 60 feet, fly 60 feet (good maneuverability), swim 60 feet, darkvision 60 feet, low-light vision, tremorsense 30 feet, scent, blood drain, constrict, grab, lunge, poison, pull, trample, and web. You don't gain full immunity to mind-affecting effects, but you do gain a +4 bonus on all saving throws against such effects.
Tiny vermin: If you take the form of a Tiny vermin, you gain a +4 size bonus to your Dexterity, a -2 penalty to your Strength, and a +1 natural armor bonus.
Large vermin: If you take the form of a Large vermin, you gain a +4 size bonus to your Strength, a -2 penalty to your Dexterity, and a +5 natural armor bonus.}
        
\DeclareSpell{Vestment of the Champion}{abjuration () []|V,  S|1 standard action|touch|Targetsarmor or shield touched|1 minute/level|none|no}[Armor or shield gains a]
    \DeclareSpellDescription{Vestment of the Champion}{This functions as magic vestment, except it only affects armor or a shield you are wearing or carrying. If the armor or shield is worn or carried by anyone other than you, the spell has no effect, but resumes its effect when you are wearing or carrying it again.}
        
\DeclareSpell{Virtuoso Performance}{transmutation () []|V|1 standard action|personal|Targetsyou|1 round/level||}[Start a second bardic performance while maintaining the first.]
    \DeclareSpellDescription{Virtuoso Performance}{While this spell is active, you may start a second bardic performance while maintaining another. Starting the second performance costs 2 rounds of bardic performance instead of 1. Maintaining both performances costs a total of 3 rounds of bardic performance for each round they are maintained.
When this spell ends, one of the performances ends immediately (your choice).
Virtuoso performance does not stack with any other method of maintaining simultaneous bardic performances.}
        
\DeclareSpell{Vision of Hell}{illusion (glamer) [evil,  fear]|V,  M (a pinch of brimstone)|1 standard action|medium (100 ft. + 10 ft./level)|Effect50-ft.-radius emanation|1 minute/level (D)|Will negates|no}[Illusory hellscape makes creatures shaken.]
    \DeclareSpellDescription{Vision of Hell}{You overlay a realistic illusion of a terrifying hellscape upon an area. Structures, equipment, and creatures within the area are not hidden, though environmental features take on an infernal appearance. While you are prepared for these images and are not affected by them, any other creature within the area must make a Will save or become shaken and also take a -2 penalty on saves versus fear effects; the fear and penalty persists as long as the creature remains in the area. Devils and any lawful evil creatures suffer no negative effects from this spell.}
        
\DeclareSpell{Vitriolic Mist}{evocation () [acid]|V,  S,  M (a piece of lemon rind)|1 standard action|personal|Targetsyou|1 round/level (D)||}[As fire shield, except acid damage.]
    \DeclareSpellDescription{Vitriolic Mist}{This functions as fire shield, except it wreathes you in yellow or green acidic mist instead of hot or cold flames. The spell deals acid damage to attackers and protects you against acid damage. This spell does not shed light.}
        
\DeclareSpell{Vocal Alteration}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone humanoid creature|1 minute/level|Fortitude negates|yes}[Disguise target's voice.]
    \DeclareSpellDescription{Vocal Alteration}{You alter the target's voice to something else. For example, you could make the target's voice high-pitched, husky, or nasal, or change its accent to an accent you are familiar with.
If this spell is used as part of a disguise, the target gets a +10 bonus on the Disguise check when trying to fool a listener.
The target can vary the disguised voice just as it could its normal voice. For example, a halfling female given a male dwarf noble's voice and accent could speak in falsetto, with a rural halfling accent, and so on.}
        
\DeclareSpell{Volcanic Storm}{evocation () [fire]|V,  S,  M/DF (obsidian and ash)|1 standard action|long (400 ft. + 40 ft./level)|Areacylinder (20-ft. radius, 40 ft. high)|1 round/level (D)|none|yes}[Hot rocks deal 5d6 damage.]
    \DeclareSpellDescription{Volcanic Storm}{Chunks of hot volcanic rock and clumps of ash pound down when this spell is cast, dealing 3d6 points of bludgeoning damage and 2d6 points of fire damage to every creature in the area. This damage only occurs once, when the spell is cast.
For the remaining duration of the spell, heavy ash rains down in the area. Creatures inside this area take a -4 penalty on Perception skill checks and the entire area is treated as difficult terrain. At the end of the duration, the rock and ash disappear, leaving no aftereffects (other than the damage dealt).}
        
\DeclareSpell{Wall of Sound}{evocation () [sonic]|V,  S,  M (a tuning fork and a quartz crystal)|1 standard action|medium (100 ft. + 10 ft./level)|Effecttranslucent wall of sound up to 20 ft. long/level or a ring of sound with a radius of up to 5 ft./two levels; either form 20 ft. high|concentration + 1 round/level|none|yes}[Sonic wall deflects and damages creatures.]
    \DeclareSpellDescription{Wall of Sound}{A translucent barrier of pure sound springs into existence. This wall is silent except for a faint hum, but bursts with discordant noise when touched by an object or creature. The wall deflects arrows, bolts, loose debris, and Small or smaller flying creatures like a wind wall spell, except these things rebound harmlessly rather than being directed upward. The burst of discordant noise deals 2d4 points of sonic damage to creatures within 10 feet of the triggering object or creature; touching or passing through the wall deals 2d6 points of sonic damage + 1 point of sonic damage per caster level (maximum +20). If you evoke the wall so that it appears where creatures are, each creature takes damage as if passing through the wall. A silence spell suppresses the wall within its area, but the wall reappears when the silence ends.}
        
\DeclareSpell{Wartrain Mount}{enchantment (compulsion) [mind-affecting]|V,  S,  M (a swatch of black cloth)|1 minute|close (25 ft. + 5 ft./2 levels)|Targetsone indifferent or friendly animal|1 hour/level|none|yes}[Animal gains the combat training general purpose.]
    \DeclareSpellDescription{Wartrain Mount}{You instill the target animal with the combat training general purpose (see the Handle Animal skill, Core Rulebook 98). This supersedes the animal's previous trained purpose and any tricks it knows. When the spell ends, it reverts to its previous trained purpose and known tricks.}
        
\DeclareSpell{Waves of Ecstasy}{enchantment (compulsion) [emotion,  mind-affecting]|V,  S|1 standard action|30 ft.|Areacone-shaped burst|1 round/level; see text|Will partial (see text)|yes}[Pleasure stuns and staggers creatures.]
    \DeclareSpellDescription{Waves of Ecstasy}{You emanate waves of intense pleasure that cause all targets within range to falter. Affected creatures are stunned for 1 round and are staggered for the remainder of the spell. A creature that makes its save is staggered for the first round and can act normally thereafter.}
        
\DeclareSpell{Web Shelter}{conjuration (creation) []|V,  S,  DF|1 minute|close (25 ft. + 5 ft./two levels)|Effect5 ft.-10 ft. diameter web sphere or 5 ft.-20 ft. hemisphere|1 hour/level (D)|none|no}[Create a comfortable shelter made of webbing.]
    \DeclareSpellDescription{Web Shelter}{You create a shelter of slightly sticky webbing. The shelter has a hinged door large enough to accommodate a Medium creature. The opaque walls of the shelter measure 1 inch thick and provide total cover to anyone within it.
Only Fine creatures with negligible Strength can be caught in the webbing (including swarms); all other creatures can pull themselves free without making a Strength check or taking an action. The webbing is sticky enough to hold twigs, leaves, dirt, and other light items, allowing you to conceal the shelter. The shelter is watertight and insulated when the door is closed. Its surface has a hardness of 0 and 2 hit points for every 5-foot square of web surface area. It takes normal damage from fire and burns as easily as wood. When the spell ends, the webbing decays rapidly and disappears.}
        
\DeclareSpell{Witness}{divination (scrying) []|V,  S|1 standard action|long (400 ft. + 40 ft./level)|Targetsone living creature|1 minute/level (D)|Will negates (harmless)|yes (harmless)}[See through the target's eyes and ears.]
    \DeclareSpellDescription{Witness}{You link your senses to the target, allowing you to see and hear through its eyes and ears. As a move action you can shift your senses from yourself to the target or back again. When using the target's senses, you are blind and deaf. When perceiving through the target, you use its normal and special senses (such as darkvision), not your own.}
        
\DeclareSpell{Wooden Phalanx}{conjuration (creation) []|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Effectthree or more wood golems, no two of which can be more than 30 ft. apart (see text)|1 hour/level (D)|none|no}[Creates 1d4+2 temporary wood golems to fight for you.]
    \DeclareSpellDescription{Wooden Phalanx}{You create 1d4+2 wood golems with the advanced template (Bestiary 164, 294). The golems willingly aid you in combat or battle, perform a specific mission, or serve as bodyguards. You can only have one wooden phalanx spell in effect at one time.
If you cast this spell while another casting is still in effect, the previous casting is dispelled.}
        
\DeclareSpell{Word of Resolve}{abjuration () []|V,  DF|1 immediate action|close (25 ft. + 5 ft./2 levels)|Targetsone ally|instantaneous|Will negate (harmless)|yes (harmless)}[Ally rerolls a save against charm or fear.]
    \DeclareSpellDescription{Word of Resolve}{You focus your aura on one ally, allowing it to reroll a failed saving throw against a charm or fear effect with a +4 sacred bonus. If you do not have the aura of courage class ability, this spell has no effect on the target's fear. If you do not have the aura of resolve class ability, this spell has no effect on any charm effects on the target.}
        
\DeclareSpell{Youthful Appearance}{transmutation (polymorph) []|V,  S|1 standard action|touch|Targetscreature touched|1 hour/level||}[Target appears younger.]
    \DeclareSpellDescription{Youthful Appearance}{You make your target look like a younger version of itself. You select how much younger it looks (for example, "10 years" or "as a young adult"). You cannot otherwise change details of the target's appearance other than those directly associated with aging (for example, gray hair returns to its original color). The target cannot appear so much younger that it changes size.
This spell does not affect any age-based modifications to ability scores or other age-related effects.}
        
\DeclareSpell{Silk To Steel}{transmutation () []|V,  S|1 standard action|touch|Targetsone scarf|1 round/level|none|no}[Use a scarf as a shield or whip.]
    \DeclareSpellDescription{Silk To Steel}{You imbue an ordinary scarf (or similar piece of clothing) with the strength of steel without altering its weight or flexibility.
Each round on your turn, you can decide to use the scarf to defend yourself (gaining a +2 shield bonus to your Armor Class) or to attack as if the scarf were a whip.}
    