    
\DeclareSpell{Aroden's Magic Army}{transmutation () []|V,  S,  DF|1 standard action|long (400 ft. + 40 ft./level)|Targetsweapons carried by allies|1 hour/level|Will negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Aroden's Magic Army}{You imbue all manufactured weapons carried by allies within range with magic, granting each weapon a +1 enhancement bonus on attack rolls and damage rolls per 5 caster levels (maximum +4).}
        
\DeclareSpell{Aroden's Spellsword}{transmutation () []|V,  S,  F (a magic rod or staff)|1 round|touch|Effectone melee weapon sized appropriately for you|10 minutes/level|Will negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Aroden's Spellsword}{When you cast this spell on a weapon, you cause an extradimensional space to open within the weapon. As part of the casting, you can insert a single magic rod or magic staff into the weapon's extradimensional space, after which the space closes. For the spell's duration, a character wielding the transmuted weapon is also considered to be wielding the rod or staff as well. If the rod or staff can be used to make attacks, you can attack normally with the weapon or use the weapon as if it were the merged rod or staff. If the effect created by the rod or staff requires an attack roll to successfully strike a foe, you can make the attack roll as if you were making an attack with the weapon at its highest bonus (including any bonuses the weapon would normally receive) rather than just a normal attack with the rod or staff-doing so does not allow you to add the weapon's damage to the attack, but instead allows you to use your skill with the weapon to boost your chance of hitting with the rod or staff's attack, spell, or effect.  At the end of the spell's duration, the merged rod or staff is ejected from the weapon. If you have a free hand, you can catch the rod or staff as a free action; otherwise, it drops to the ground.  If the merged weapon is broken or destroyed during the duration of Aroden's spellsword, the merged rod or staff is similarly broken or destroyed.}
        
\DeclareSpell{Banishing Blade}{abjuration () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectone melee weapon|1 round/level or until discharged|none and Will partial (see text)|yes (see text)}[]
    \DeclareSpellDescription{Banishing Blade}{You imbue a weapon with the power to drive foes back. The first time each round the weapon strikes a creature, the weapon attempts a free bull rush combat maneuver check against that creature. This does not provoke attacks of opportunity. The combat maneuver for the bull rush is equal to 1d20 + your caster level. You do not have to move to push creatures more than 5 feet with this bull rush. If a creature you strike has spell resistance, you must attempt a caster level check to overcome its spell resistance the first time you strike it. If you fail, that creature is immune to the effects of this casting of banishing blade.  The first time each extraplanar creature whose Hit Dice don't exceed your caster level is driven back at least 10 feet by this spell, it must attempt a Will save. If it fails, it is sent back to its home plane. Whether it succeeds or fails, that creature is staggered for 1 round and banishing blade's duration ends.}
        
\DeclareSpell{Create Armaments}{conjuration (creation) []|V,  S,  M (diamonds worth price of arms to be created)|1 minute|0 ft.|Effectone nonmagical weapon, shield, or set of armor|instantaneous|none|no}[]
    \DeclareSpellDescription{Create Armaments}{You create one nonmagical weapon, shield, or set of armor. To determine whether the item functions as intended, you must attempt an appropriate Craft check with the DC required to create the item normally. If you fail, the item is created with the broken condition. You can create items made of rare or unusual materials if you include a bit of that material as an additional material component when you cast the spell, but cannot create cold iron items with this spell.}
        
\DeclareSpell{Expeditious Construction}{conjuration (creation) [earth]|V,  S,  M (a handful of earth or stone)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effecta low wall 10 feet long per 3 levels (minimum 10 feet) (S)|instantaneous|none|no}[]
    \DeclareSpellDescription{Expeditious Construction}{You create a low wall or other simple structure of packed earth or loose stone measuring 3 feet thick, 3 feet tall, and 10 feet long per 3 caster levels you possess (minimum 10 feet). Each square of the structure can appear only in unoccupied spaces atop earthen or stone surfaces able to support it. The wall grants cover as per a low wall and can be climbed with a successful DC 5 Climb check. Large and larger creatures don't need to attempt a Climb check to climb over it.  At your discretion, you can make the structure half as long but thicker by forming it into a berm consisting of a steep slope on each side. Characters moving uphill (to an adjacent square of higher elevation) must spend 2 squares of movement to enter a square of steep slope. Characters running or charging downhill (moving to an adjacent square  of lower elevation) must attempt a DC 10 Acrobatics check upon entering the first steep slope square. Mounted characters attempt a DC 10 Ride check instead. Characters who fail this check stumble and must end their movement 1d2 x 5 feet later. Characters who fail by 5 or more fall prone in the square where they end their movement. A steep slope increases the DC of Acrobatics checks by 2.}
        
\DeclareSpell{Force Sword}{evocation () [force]|V,  S|1 standard action|0 ft.|Effectone sword-shaped weapon of force|1 minute/level|none|yes}[]
    \DeclareSpellDescription{Force Sword}{You create a +1 longsword of pure force sized appropriately for you that you can wield or give to another creature like any other longsword. At 8th level, the sword functions as a +2 longsword. At 13th level, it functions as a +3 longsword. A force sword cannot be attacked or harmed by physical attacks, but dispel magic, disintegrate, a sphere of annihilation, or a rod of cancellation affects it.  If a creature you attack with the sword has spell resistance, you must attempt a caster level check (1d20 + your caster level) against that spell resistance the first time the force sword strikes it. If you fail the check, the spell is dispelled. If you succeed, the weapon has its normal full effect on that creature for the duration of the spell.}
        
\DeclareSpell{Grand Destiny}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Effectone willing creature|10 minutes/level or until discharged|none (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Grand Destiny}{You inspire the target with the power to seize a grand destiny. The target gains a +4 competence bonus that it can choose to apply before rolling any attack roll, caster level check, saving throw, or skill check. The spell ends once the bonus has been applied to two rolls. At 12th level and 15th level, the bonus can be applied an additional time before the spell is discharged. A subject can be under the effect of only one grand destiny spell at a time.}
        
\DeclareSpell{Guardian Monument, Lesser}{abjuration () []|V,  S,  F (an unattended,  nonmagical object)|1 full round|touch|Area40-ft. radius from touched object or 60-ft. radius from touched object; see text|1 hour/level|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Guardian Monument, Lesser}{You touch an unattended, nonmagical object to create a touchstone for humans defending the area. Such human defenders are protected by a shimmering aura as long as they are in the area. The spell grants each subject damage reduction 2/magic. Humans who leave the area and reenter regain the damage reduction. The spell is suppressed if the object is moved from its place, but resumes if the object is put back. Its duration continues to elapse while it is suppressed this way.  Normally, the area of effect is 40 feet from the touched object. If the touched object is a monument to human achievement, the area increases to a 60-foot radius.}
        
\DeclareSpell{Guardian Monument, Greater}{abjuration () []|V,  S,  F (an unattended,  nonmagical object)|1 full round|touch|Area40-ft. radius from touched object or 60-ft. radius from touched object; see text|1 hour/level|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Guardian Monument, Greater}{This spell functions as lesser guardian monument, except it grants DR 4/magic.}
        
\DeclareSpell{Human Potential}{transmutation () []|V,  S,  M (a human hair)|1 standard action|touch|Targetscreature touched|1 minute/level|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Human Potential}{The target shares in humanity's great potential as encouraged by Aroden. The target chooses one ability score and gains a +2 enhancement bonus to that ability score. The bonus confers the usual benefit to skills and abilities based on the ability enhanced, but does not affect bonus spells or skill ranks.}
        
\DeclareSpell{Human Potential, Mass}{transmutation () []|V,  S,  M (a human hair)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature/level, no two of which can be more than 30 ft. apart|1 minute/level|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Human Potential, Mass}{This spell functions like human potential, except it affects multiple creatures. Each target can choose a different ability score to be enhanced by this spell.}
        
\DeclareSpell{Last Azlanti's Defending Sword}{evocation () [force]|V,  S,  F (a miniature platinum sword worth 250 gp)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectone sword|1 round/level (D)|none|yes}[]
    \DeclareSpellDescription{Last Azlanti's Defending Sword}{You create a sword of force that functions as mage's sword except as described here. The sword does not receive the additional +3 enhancement bonus a mage's sword receives, and deals 3d6 points of force damage. You cannot command the sword. Until the sword is triggered, it hovers in your space without interfering with  your actions. While hovering in this way, the sword attempts to defend you from incoming attacks, granting you a +4 shield bonus to your AC. The first time a foe within close range damages you or forces you to attempt a saving throw that you fail, the sword is triggered and begins attacking that target as described in mage's sword for the duration of the spell. This ends the shield bonus. You cannot direct the sword to defend against a new target once it has begun to attack. If its target moves beyond the sword's range, the sword returns to you and hovers until the target is again within range. The sword's return does not restore the spell's shield bonus to AC.}
        
\DeclareSpell{Last Azlanti's Defending Sword, Mass}{evocation () [force]|V,  S,  F (a miniature platinum sword worth 250 gp)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effectup to one sword per 3 levels|1 round/level (D)|none|yes}[]
    \DeclareSpellDescription{Last Azlanti's Defending Sword, Mass}{This spell functions as Aroden's defending sword, except you can create one sword per 5 caster levels, each of which must defend a different creature within range.}
        
\DeclareSpell{Linked Legacy}{divination () []|V,  S|1 round|close (25 ft. + 5 ft./2 levels)|Targetstwo willing creatures plus another creature per 6 levels, no two of which can be more than 30 feet apart|10 minutes/level|none|yes}[]
    \DeclareSpellDescription{Linked Legacy}{This spell helps build community and ensure a shared vision for the future. When any of the affected creatures succeeds at a Knowledge check to answer a question within its field of study or identify a monster and its special powers or vulnerabilities, as a free action the affected creature can share any information gained automatically with all targets of the spell. If any of the targets move out of the spell's range, the spell ceases to function for all of them until they are all within close range of you again.}
        
\DeclareSpell{Splinter Spell Resistance}{transmutation () []|V,  S|1 standard action|touch|Targetsmelee or thrown weapon or up to 50 pieces of ammunition touched|1 minute/level|Fortitude negates|no}[]
    \DeclareSpellDescription{Splinter Spell Resistance}{You create an aura around the target weapon that weakens a foe's magical defenses. The first time each round the weapon damages a creature with spell resistance, that creature's spell resistance is reduced by 5 for 1 round. This reduction is not cumulative for multiple attacks within the same round, even if the target is struck by different weapons, each affected by a different casting of splinter spell resistance. However, the same creature's spell resistance can be reduced on multiple rounds by subsequent hits.}
        
\DeclareSpell{Winged Sword}{transmutation () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone melee weapon|10 minutes/level|Will negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Winged Sword}{The weapon targeted by this spell grows small feathered wings. For the duration of the spell, the weapon acts as if it had the throwing weapon special ability. This spell can be used in place of magic stone as a prerequisite for the throwing weapon special ability.}
        
\DeclareSpell{Celestial Healing}{conjuration (healing) [good]|V,  S,  M (1 drop of blood from a good outsider or 1 dose of holy water)|1 round|touch|Targetscreature touched|1 round/2 levels|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Celestial Healing}{You anoint a wounded creature with the blood of an outsider with the good subtype (such as an angel) or holy water, giving it fast healing 1. The target radiates the aura of a good creature for the duration of the spell and can sense the righteousness of the magic, though this has no long-term effect on the target's alignment. If the target has its own evil aura, this is not suppressed by celestial healing, and can also be detected normally.}
        
\DeclareSpell{Celestial Healing, Greater}{conjuration (healing) [good]|V,  S,  M (1 drop of blood from a good outsider or 1 dose of holy water)|1 round|touch|Targetscreature touched|1 round/2 levels|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Celestial Healing, Greater}{As per celestial healing, except the target gains fast healing 4 and the target radiates the aura of a good cleric.}
        
\DeclareSpell{Cyclic Reincarnation}{transmutation () []|V,  S,  M,  DF (oils worth 5, 000 gp)|10 minutes|touch|Targetsdead creature touched|instantaneous|none, see text|yes (harmless)}[]
    \DeclareSpellDescription{Cyclic Reincarnation}{This spell allows a dead creature that died no more than 1 year before the casting of the spell to return to life in a body that closely resembles its original body; it functions as reincarnate except as noted. Cyclic reincarnation returns the dead creature to life in a new body of the same race that the target belonged to in life, and the new body appears physically similar to the creature's previous one, to the extent that the creature could be easily mistaken for its own offspring or kin. If the affected creature isn't a humanoid, there is a 75\% chance that the creature returns to life as a youth of its race, gaining the young creature simple template instead (or becomes a juvenile, in the case of dragons and other creatures whose power is determined by their age category).  You can use cyclic reincarnation on someone who was killed by a death effect or turned into an undead creature and then destroyed, but nonhumanoids so restored always return to life with the young creature simple template (or as a juvenile, in the case of creatures whose power is determined by their age category).}
        
\DeclareSpell{Jatembe's Ire}{transmutation () [good]|V,  S,  M (octopus or squid tentacle)|1 standard action|medium (100 ft. + 10 ft./level)|Area120-ft.-radius spread|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Jatembe's Ire}{The scholars of the Magaambya claim that Old-Mage Jatembe developed this spell to help eradicate the lost city of Ird, although such claims have never been confirmed. This spell causes tall grass, weeds, and other plants to swell into Gargantuan vines  and tendrils that erupt from the ground, reaching for any structure or any creature of evil alignment, functioning like black tentacles except as noted. When you are determining the tendrils' CMB, the tendrils use your caster level as their base attack bonus and have a +13 bonus due to their Strength. Any tendril that succeeds in grappling a foe deals 4d6+13 points of damage to the grappled creature. Additionally, the tendrils created by this spell can detect evil auras, as if they had spent 3 rounds observing all creatures and objects within the spell's area using detect evil, and attack and impede the movement of only evil creatures, though they also attack any structures in their area. Each structure suffers a single attack each round; your caster level acts as the base attack bonus for these attacks, and the tendrils deal 4d6+13 points of damage on each successful attack. Creatures that lack evil auras are not attacked or impeded by this spell.}
        
\DeclareSpell{Artificer's Curse}{transmutation () []|V,  S,  M (a blank scroll or page from a spellbook)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets1 magical item|1 minute/level (D)|Will negates (object)|yes}[]
    \DeclareSpellDescription{Artificer's Curse}{You temporarily suppress the most powerful qualities of a magical item. This item can be any object you suspect bears a magical enchantment, but if the targeted item is not magical, your spell has no effect. The spell reduces the object's caster level by an amount equal to your caster level, to a minimum of 0. If the item grants a competence, deflection, enhancement, insight, luck, morale, natural armor, profane, resistance, or sacred bonus, the bonus is reduced by 1 for every 4 caster levels the item loses. If the item's caster level is reduced to 0, all its magic qualities are suppressed (as if dispelled) for the duration of the spell. This spell has no effect on artifacts.}
        
\DeclareSpell{Deft Digits}{transmutation () []|V,  S|1 standard action|Medium (100 ft. + 10 ft./level)|Targets1 unattended gauntlet or glove|10 minutes/level|None (harmless, object)|no}[]
    \DeclareSpellDescription{Deft Digits}{You animate the target of the spell, manipulating the glove with your own hand from a distance. The glove moves as you direct it with a fly speed of 30 feet and average maneuverability. Directing the glove is a standard action, though the glove can move up to its speed and perform a task in the same action. You can attempt Disable Device and Sleight of Hand checks using the glove, though attempting these checks at a distance increases the normal skill check DCs by 5, or by 20 if you do not have line of sight to the object you are manipulating. The glove can also lift or drag objects using your caster level as your Strength score. The glove cannot wield weapons or make attacks effectively while this spell is in effect. If you cast this spell on a magical glove, its innate magic is suppressed for the duration of the spell.}
        
\DeclareSpell{Dissolution}{transmutation () []|V,  S,  M (vial of alchemical reagents worth 50 gp)|1 standard action|touch|TargetsTiny or smaller object touched|10 minutes/level (D)|Fortitude negates (object)|no}[]
    \DeclareSpellDescription{Dissolution}{You touch a Tiny or smaller item, causing the item to vanish as if it did not exist at all. The item doesn't take damage or otherwise gain any condition; it simply ceases to be visible to or interact with the world in any way, as if it no longer existed. The oil vanishes with the item and leaves no residue, nor does it affect surfaces that handle or hold the item during its application. No spell or ability short of miracle or wish can locate or affect the item  while it is under the effect of this spell. Though the item seems to not exist while under the effects of this spell, its own reality is consistent (it ages normally, and any ongoing effects upon it continue normally). The target object can be one size larger than Tiny for every 5 caster levels above 5th you possess.  The target item returns to existence when the spell's duration expires. An item returns to existence in exactly the same location and condition it left. If the location no longer has room for the item, the item takes 1d0 points of damage (bypassing hardness) and is teleported to the nearest location that has room for it. If that location is more than 5 feet from the original location, there is a 25\% chance the item is instead shifted to a randomly determined alternate plane.}
        
\DeclareSpell{Emblem Of Greed}{transmutation (polymorph) []|V,  S,  M (a masterwork or magical melee weapon)|1 standard action|touch|Targets1 masterwork melee weapon touched|1 minute/level|none (object)|no}[]
    \DeclareSpellDescription{Emblem Of Greed}{You transform one melee weapon into a burning glaive similar to the ones wielded by the runelords of old. The target of your spell must be a masterwork or magical melee weapon appropriate to your size. The weapon becomes a glaive appropriate to your size and has a +1 enhancement bonus and the flaming weapon special ability. When wielding the glaive, you are considered proficient with it and use your caster level as your base attack bonus (which may give you multiple attacks). When you reach caster level 14th, the glaive gains the spell-storing weapon special ability. When you reach caster level 17th, it loses the flaming weapon special ability, and gains the flaming burst weapon special ability. The glaive's enhancement bonus increases to +2 at caster level 15th, and +3 at caster level 19th.  If this spell is cast on a magic weapon, the powers of the spell supersede any that the weapon normally has, rendering the normal enhancement bonus and powers of the weapon inoperative for the duration of the spell. This spell is not cumulative with greater magic weapon or any other spell that might modify the weapon in any way. This spell does not work on artifacts. A masterwork weapon's bonus on attack rolls does not stack with an enhancement bonus to attack.}
        
\DeclareSpell{Full Pouch}{transmutation () []|V,  S,  M (alchemical reagents or herbs worth 1 gp)|1 swift action|touch|Targets1 object touched|instantaneous|Fortitude negates (object)|no}[]
    \DeclareSpellDescription{Full Pouch}{You cast this spell as you draw out a consumable alchemical item to use. The object must be an alchemical item, but not a dose of disease, a poison, a magic potion, or another type of consumable item. The item divides itself into two nearly identical copies and the newly separated one is delivered into your hand. The new item functions as the original in all ways except the copied item suffers a slight reduction in quality. Saves against the new alchemical item's affects use the original item's save DC or the save DC of this spell, whichever is higher.}
        
\DeclareSpell{Legendary Proportions}{transmutation () []|V,  S,  M (a dinosaur bone and powdered amber worth at least 200 gp)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets1 creature (see text)|1 minute/level|Fortitude negates (harmless)|no}[]
    \DeclareSpellDescription{Legendary Proportions}{You call upon the primordial power of ancient megafauna to boost the size of your target. Because of its connection to living creatures of the distant past, the spell does not function on outsiders, undead, and summoned creatures. Your target grows to legendary proportions, increasing in size by one category. The creature's height doubles and its weight increases by a factor of 8. The target gains a +6 size bonus to its Strength score and a +4 size bonus to its Constitution score. It gains a +6 size bonus to its natural armor, and DR 10/adamantine. Its carrying capacity changes to reflect its new size. The creature's equipment and weapons, if any, also increase in size. Any enlarged item that leaves the creature's possession returns to its original size (though thrown weapons and ammunition deal damage at their enlarged size before returning to their true proportions).  If insufficient room is available to accommodate the creature's growth, it attains the maximum possible size and can attempt a Strength check (using its increased Strength score) to burst any  enclosures in the process. If it fails, it is constrained without harm by the materials enclosing it. The spell cannot crush a creature by enclosing it.}
        
\DeclareSpell{Liquefy}{transmutation () []|V,  S,  M (a specially prepared glass bottle)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets1 object weighing up to 1 pound/level|1 round/level (D)|Fortitude negates (object)|no}[]
    \DeclareSpellDescription{Liquefy}{The object you target becomes a liquid version of itself and drips or runs like a thin oil until it pools on any flat surface. If the item has magical or alchemical properties, they become inert for the duration of the spell. If you are holding the item when you cast this spell, you can drain it into the bottle used as focus for the spell. Items with hit point damage or the broken condition regain 5 hit points/caster level if drained into a bottle in this way. The duration of temporary effects (such as applied poison or greater magic weapon) passes normally and may expire while the object is in liquid form. The liquid is clearly unsafe to drink, but if, for some reason, a creature does drink the liquid and the spell ends, the creature takes 3d6 points of damage, and brings up the solid version of the item as a standard action in a coughing fit.  Any spell or effect that would disperse or dilute an object affected by liquefy forces the object to attempt a Fortitude save (using the effect's DC, or DC 15 for effects with no saving throws of their own, such as pouring a liquefied object into a stream). A failed save causes the object to gain the broken condition. If the item is already broken, it is instead destroyed on a failed save. Liquefy has no effect on artifacts, constructs, or intelligent magic items.}
        
\DeclareSpell{Open Arms}{transmutation () []|V,  S,  F (a magical or masterwork melee weapon)|1 immediate action|touch|Targetsmelee weapon touched|1 minute/level|none|no}[]
    \DeclareSpellDescription{Open Arms}{You cast this spell in response to a specific cavalier's challenge (Pathfinder Roleplaying Game: Advanced Player's Guide 32), inquisitor's judgment (Advanced Player's Guide 38), or smite (such as a paladin's smite evil) declared against you by an enemy creature. It can also be cast if a creature uses a spell that causes you to qualify as the creature's favored enemy when you normally wouldn't, such as instant enemy (Advanced Player's Guide 229).  You imbue your weapon with a powerful ability to ward off attacks made against you by the creature that challenged you. You gain a +5 insight bonus to your AC and CMD against the attacks of the initiating creature as long as you hold the weapon. If you release the weapon for any reason, the spell ends. You can cast this spell only in response to one of the conditions listed  above. The spell fails if you attempt to cast it when you were not subject to a challenge or similar effect since your last turn.}
        
\DeclareSpell{Rags To Riches}{transmutation () []|V,  S,  M (a bit of burlap wrapped over a copper coin)|1 standard action|touch|Targets1 weapon, suit or armor, shield, tool, or skill kit touched/5 levels|10 minutes/level|Fortitude negates (object)|no}[]
    \DeclareSpellDescription{Rags To Riches}{The target object is enhanced to function as a masterwork item. In addition to any bonuses for the masterwork quality, the object gains other bonuses. Skill kits and other equipment add an additional +1 insight bonus for every 4 caster levels you possess to skill checks made with them that already receive a bonus from the skill kit. Armor and weapons gain temporary hit points equal to your caster level. If the object already has an enhancement bonus, this bonus increases by 1. If the object of the spell has hardness, that hardness increases by 5.}
        
\DeclareSpell{Rune Of Ruin}{transmutation () [curseUM]|V,  S,  M (a self-portrait on a thin sheet of paper)|1 standard action|Medium (100 ft. plus 10 ft./level)|Targets1 object|instantaneous|Fortitude negates (object)|no}[]
    \DeclareSpellDescription{Rune Of Ruin}{You curse a magic item, such as magical clothing, a suit of armor, or a weapon. The object is reduced to 1/4 its normal hit point total, gains the broken condition, and appears damaged and worn. If it grants a numeric bonus, such as a +2 deflection bonus to AC, that bonus is reduced by 1 for every 3 caster levels you possess, to a minimum of +0. Other magical qualities fail to work 50\% of the time when called upon, so a resistance bonus on saves or a weapon's flaming special ability could fail each time the item is used.  If the object is an intelligent magical item, its Ego score remains unchanged despite its reduced quality. The weapon has only a 50\% chance to successfully use any spells or spell-like abilities it has, and has a 25\% chance of forgetting its special purpose (if any). If an intelligent weapon is actively dominating its wielder when it fails its save against rune of ruin, the wielder gains an immediate saving throw with a +4 bonus to regain control. Rune of ruin has no affect on magical artifacts.}
        
\DeclareSpell{Tears To Wine}{transmutation () []|V,  S,  M (a single grape)|1 standard action|10 ft.|Targets1 cu. ft./2 levels of liquid (see text)|10 minutes/level|Will negates (object)|yes (object)}[]
    \DeclareSpellDescription{Tears To Wine}{Legend claims runelords used this spell to literally benefit from drinking the tears of their captured foes. This spell turns nonmagic liquids-including spoiled, rotten, diseased, poisonous, or otherwise contaminated drinks, tears, seawater, and similar fluids-into mead or wine of average quality. This spell does not prevent subsequent natural decay or spoilage. Unholy water and similar liquids of significance are spoiled by tears to wine, but the spell has no effect on creatures of any type or on magic potions.  Creatures that drink the mead or wine created by this spell become sharp-witted and clear-minded, gaining a +2 enhancement bonus on all Intelligence- and Wisdom-based skill checks. This increases to a +5 bonus at caster level 9th, and to +10 (the maximum) at caster level 15th.}
        
\DeclareSpell{Transmute Golem}{transmutation (polymorph) []|V,  S,  M (powdered metals with a variable cost,  see text)|8 hours|touch|Targetsgolem touched|instantaneous|none|no}[]
    \DeclareSpellDescription{Transmute Golem}{You turn one type of golem into another. The golem must be willing-it must be commanded to transform by its master or must be a creature able to make informed decisions that opts to submit to the spell. You must provide various powdered metals with a value equal to 150\% of the difference in creation costs between the old and new type of golem, even if the new golem type is cheaper to create. Both types of golems must share the same subtypes, if any. You cannot transmute a golem into a new type of golem with a CR higher than your caster level.  If all of these conditions are satisfied, the old golem completely changes to the new golem type. Its abilities and statistics are identical to one of the new golem type, including its magic immunities and special attacks. The new golem is still affected by any damage or conditions it suffered before the spell was cast.}
        
\DeclareSpell{Find Fault}{divination () []|V,  S|1 standard action|medium (100 ft. plus 10 ft./level)|Targets1 creature|instantaneous|none|yes}[]
    \DeclareSpellDescription{Find Fault}{You instantly learn many of the target's weaknesses, as if you had made an appropriate Knowledge skill check with a result equal to 20 + your caster level. Additionally, your first melee or ranged attack roll against the creature before the end of your next turn gains a +5 insight bonus. If the creature is polymorphed, disguised, or hidden by an illusion and you are not aware of it's true form, this spell fails as if the target has spell resistance you failed to penetrate (the GM may have you attempt a caster level check to conceal the true reason for the spell's failure).}
        
\DeclareSpell{Foretell Failure}{divination () []|V,  S|1 swift action|personal|Targetsyou|instantaneous||}[]
    \DeclareSpellDescription{Foretell Failure}{You cast this spell immediately before you would take an action that requires a d20 roll, such as a skill check, attack roll, or ability check. The action must be something you can complete in a single round. The spell magically informs you whether the action will succeed if you roll a 10 or better on the d20 roll involved. If the action would be successful under those circumstances, you must take the action. If the action would not be successful, you can take a different action.}
        
\DeclareSpell{Perfect Placement}{divination () []|V,  S,  M (a chess piece)|1 standard action|close (25 ft. plus 5 ft./2 levels)|Targetsone creature/level, no two of which can be more than 30 ft. apart|1 round/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Perfect Placement}{Affected creatures gain tactical knowledge and maximize their efficiency on the field of battle. Each gains a +1 insight bonus to AC and Reflex saves. Against attacks of opportunity, the insight bonus to AC increases to +3.}
        
\DeclareSpell{Heckle}{enchantment (compulsion) [emotionUM,  mind-affecting]|V,  S,  M (a tomato)|1 standard action|medium (100 ft. + 10 ft./level)|Targets1 creature|1 minute/level|Will negates|yes}[]
    \DeclareSpellDescription{Heckle}{You badger and nitpick the subject of your spell until its mood sours. The target's attitude shifts one category toward hostile regarding you and everyone within 30 feet of the target at the time the spell is cast. The target also takes a -2 penalty on attack rolls, on saving throws, and on ability and skill checks that rely on Intelligence, Wisdom, or Charisma.}
        
\DeclareSpell{Stage Fright}{enchantment (compulsion) [emotionUM,  fear,  mind-affecting]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targets1 creature/level, no two of which may be more than 30 ft. apart|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Stage Fright}{You fill your targets with the sudden fear of failure. A creature that fails its saving throw takes a -4 penalty on ability checks, skill checks, and any checks that require concentration (such as casting a spell in difficult circumstances or operating a complex device).}
        
\DeclareSpell{Tough Crowd}{abjuration () []|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targets1 creature/level|10 minutes/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Tough Crowd}{You fortify your allies against attempts to control or mislead them. Each ally in the spell's range gains a +4 insight bonus on the saving throw to resist the next enchantment or illusion spell cast on it. In addition, the DC of any Bluff, Diplomacy, Disguise, or Intimidate check to influence an affected character increases by 4 for the duration of the spell.}
    