    
\DeclareSpell{Breeze}{evocation [air]|V,  S,  M (a miniature fan)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature or object|1 hour (D)|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Breeze}{You create a light wind that blows against the target, from a direction of your choice. The breeze grants the subject a +2 bonus on saves against very hot conditions, severe heat, breath weapons, and saves against cloud vapors and gases (such as cloudkill, stinking cloud, and inhaled poisons). This spell does not function without air or underwater.

You can only have one breeze active at any one time. If you cast this spell while another casting is still in effect, the previous casting is dispelled.}
        
\DeclareSpell{Drench}{conjuration (creation) [water]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature or object of size Large or smaller|1 round|Reflex negates (object)|yes (object)}[]
    \DeclareSpellDescription{Drench}{A sudden downpour soaks the target creature or object. The rain follows the subject up to the range of the spell, soaking the target with water. If the target is on fire, the flames are automatically extinguished. Fires smaller than campfires (such as lanterns and torches) are automatically extinguished by this spell.}
        
\DeclareSpell{Jolt}{transmutation [electricity]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Effect: spark of electricity|instantaneous|none|Yes}[]
    \DeclareSpellDescription{Jolt}{You cause a spark of electricity to strike the target with a successful ranged touch attack. The spell deals 1d3 points of electricity damage.}
        
\DeclareSpell{Penumbra}{evocation [darkness]|V,  S,  M (a bit of soot)|1 standard action|touch|Targets: creature or object touched|10 minutes/level (D)|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Penumbra}{This spell keeps the creature or object touched slightly in shadow. The target of this spell does not suffer any penalties or blindness caused by bright light, such as those from light sensitivity or light blindness.

You can have only one penumbra spell active at any one time. If you cast this spell while another casting is still in effect, the previous casting is dispelled.}
        
\DeclareSpell{Root}{transmutation [earth]|V,  S,  M (a pinch of dirt)|1 standard action|touch|Targets: creature touched|1 minute (D)|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Root}{This spell strengthens the subject's connection to the ground below, bolstering its defense against combat maneuvers. It gains a +2 insight bonus to its CMD to resist being moved or tripped and a +2 competence bonus on all Acrobatics checks made to balance or remain standing on earth, sand, stone, or a similar rocky substance.}
        
\DeclareSpell{Scoop}{evocation [force]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Effect: 6 inch diameter container of force Duration concentration||none|yes}[]
    \DeclareSpellDescription{Scoop}{You will a small vessel of force into existence. As a move action, you can direct the container up to 15 feet per round in any direction, though the spell ends if the distance between you and the container ever exceeds the spell's range. You can dip the container to pick up or drop a liquid as a move action. The vessel holds up to 1 pint of liquid or small objects, weighing up to 5 pounds. You can also gather up a pint of liquid or small objects spread cross a surface with 1 minute of careful concentration.}
    