    
\DeclareSpell{Sadomasochism}{necromancy () [pain]|V,  S|1 standard action|personal|Targetsyou|1 minute/level (D)|Will negates, see text|yes}[]
    \DeclareSpellDescription{Sadomasochism}{While subject to this spell, anytime you are dealt damage, your attacker must roll damage for the attack twice and take the higher result, but the attacker must also succeed at a Will saving throw or be demoralized (Pathfinder RPG Core Rulebook 99) for 1 round. Each time you deal damage to a creature demoralized by this spell, you roll damage twice and take the higher result. This spell originally appeared in Pathfinder Campaign Setting: Inner Sea Gods.}
        
\DeclareSpell{Infuse Decay}{necromancy () [evil]|V,  S,  F (a set of fine mortician's tools worth 100 gp)|10 minutes|touch|Areacorporeal undead touched; see text|permanent until discharged (D)|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Infuse Decay}{This spell functions as per imbue with spell ability, except it can only target corporeal undead creatures, and can only transfer touch spells. The number and level of spells the subject can be granted depends on the undead creature's Hit Dice; even multiple castings of infuse decay can't exceed this limit.   HD of UndeadTouch Spells Infused5 or lowerOne 1st-level spell6-10One or two 1st-level spells11 or higherOne or two 1st-level spells and one 2nd-level spell   Once you cast infuse decay, you can't prepare a new 4th-level spell to replace it (see imbue with spell ability on page 299 of the Pathfinder RPG Core Rulebook for further details). The infused spell is automatically triggered the next time the undead creature makes a successful touch attack or attack with a natural weapon. An intelligent undead can choose not to trigger the spell on a hit. Only one infused spell can be triggered per attack. An intelligent undead can choose which spell to trigger if it has more than one infused spell. A nonintelligent undead triggers a random spell when it hits with a natural weapon. Only one spell can be triggered per round, regardless of the number of attacks the undead makes.}
        
\DeclareSpell{Unlock Flesh}{necromancy () []|V,  S, F (any slashing weapon or cutting tool)|1 standard action|touch|Areacreature touched|1 round/level (living target) or instantaneous (undead target); see below|Fort negates|yes}[]
    \DeclareSpellDescription{Unlock Flesh}{By touching a creature with a bladed instrument, you cause the creature's flesh to loosen and slide against its skeletal moorings. A living creature touched becomes staggered by the disturbing and uncomfortable sensation for 1 round per level. Each round on its turn, the subject can attempt a new saving throw to end the effect. This is a standard action that does not provoke attacks of opportunity. A corporeal undead creature targeted by this spell instead takes 1d6 points of damage per caster level (maximum 5d6 at 5th level) as wet, oozing chunks of flesh slough off its desiccated bones (a successful Fortitude save halves this damage). Incorporeal creatures, or creatures that do not have flesh, are immune to this spell's effects.}
    