    
\DeclareSpell{Augmenting Wall}{evocation () [see text]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Effect20-ft.-high wall of energy whose area is up to one 10-ft. square/level|1 round/2 levels (see text)|none (object)|no (object)}[]
    \DeclareSpellDescription{Augmenting Wall}{You create a wall of faintly shimmering elemental energy. Upon casting the spell, choose either acid, cold, electricity, or fire. The spell gains the chosen descriptor, and any thrown weapons or ammunition that pass through the augmenting wall as part of a ranged attack deal 1d6 points of energy damage of the specified type in addition to their normal damage. The wall has no effect on melee weapons or items not thrown as part of an attack.  As you cast the spell, you can limit the wall so that it only affects ranged weapons passing through it in the direction of your choice. Doing so halves the spell's duration.}
        
\DeclareSpell{Bloody Arrows}{necromancy () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone willing creature|1 round/level|none (harmless)|no (harmless)}[]
    \DeclareSpellDescription{Bloody Arrows}{Whenever this spell's target hits a creature with a ranged weapon that successfully deals piercing or slashing damage, the struck creature takes 1 point of bleed damage. Unlike most bleed damage, the bleed damage dealt by the subject of this spell is cumulative up to an amount equal to 1/2 your caster level (to a maximum of 5 points of bleed damage at 10th level).}
        
\DeclareSpell{Calm Air}{abjuration () [air]|V,  S|1 standard action|long (400 ft. + 40 ft./level)|Areacylinder (5-ft./level radius, 40 ft. high)|10 minute/level (D)|none (object)|no (object)}[]
    \DeclareSpellDescription{Calm Air}{This spell calms the air and disperses fog, dust, and other particles. The wind force in the area is reduced in strength by one step per 4 caster levels (to a minimum wind force of light) and clouds are dispersed, although parts of nonmagical clouds that extend beyond the area are not affected. If a magical cloud or wind's point of origin is inside the area of a calm air spell, the whole effect is suppressed; otherwise, only the part inside the area is suppressed. Suppression still counts against the duration of a wind or cloud effect. Magical wind and cloud effects are suppressed only if you succeed at a caster level check (DC 11 + effect's caster level). You can move the calm air effect by concentrating as a standard action.}
        
\DeclareSpell{Conversing Wind}{transmutation () [air]|V,  S|1 standard action|1 mile/level|Area10-ft.-radius spread|1 hour/level (D)|none|no}[]
    \DeclareSpellDescription{Conversing Wind}{This spell functions as whispering wind, except it can carry responses and doesn't end after delivering its first message. After the wind completes its initial message, it waits for 1 round, then copies what it hear, and returns at the same speed and by the same route. It delivers what it heard to the location where the spell was originally cast. The wind continues back and forth in this way until the duration ends or the spell is dismissed.}
        
\DeclareSpell{Rain Of Arrows}{conjuration (creation) []|V,  S,  M (a quiver full of 20 arrows worth 1 gp)|1 standard action|long (400 ft. + 40 ft./level)|Effect15-ft.-radius cloud of arrows|instantaneous|Reflex halves|no}[]
    \DeclareSpellDescription{Rain Of Arrows}{You point your finger and conjure a cloud of magical arrows that rain down on any creatures and objects in the indicated area. You must have line of sight to the intended area. The arrows deal 1d6 points of piercing damage per caster level (maximum 20d6) to each creature and object in a 15-foot radius centered on the targeted square or intersection.  If the arrows used as a material component are all made of the same material (such as cold iron), the arrows created by the spell are also made of that material.}
        
\DeclareSpell{Telekinetic Volley}{transmutation () []|V,  S|1 standard action|touch|Targetsup to one touched object per level weighing up to 5 lbs. each|1 round/level or until discharged (D)|none (object)|no (object)}[]
    \DeclareSpellDescription{Telekinetic Volley}{The touched items levitate in your space. When you cast the spell and once per round thereafter, you can launch one item at a target of your choice as a standard action. The ranged attack is made as if you had thrown the item unless it's ammunition for a weapon, in which case the attack is made as if fired from a heavy crossbow (if a bolt), a halfling sling staff (if a sling bullet), a blowgun (if a blowgun dart), a composite longbow with a +2 Strength rating (if an arrow), an atlatlUE (if an atlatl dart), or a pistolUE (if a firearm bulletUE). A firearm pelletUE launched by the spell functions as a shuriken.  When you launch ammunition with this spell, you don't take a penalty on your attack rolls for lacking proficiency with the ammunition's weapon; you do, however, take the usual -4 penalty for throwing an improvised weapon if you launch an item not intended to be used as a weapon. The attack roll uses your caster level in place of your base attack bonus and your Intelligence or Charisma modifier (whichever is higher) in place of your Dexterity modifier. Range increment and proficiency penalties apply as normal. The attack has an effective Strength bonus, if applicable, equal to the higher of your Intelligence and Charisma modifiers. The spell is discharged when all touched items have been launched.}
    