    
\DeclareSpell{Detect Fiendish Presence}{divination () []|V,  S|1 standard action|60 ft.|Areacone-shaped emanation|concentration, up to 10 minutes/level (D)|none|no}[]
    \DeclareSpellDescription{Detect Fiendish Presence}{This spell functions like detect evil, except that it detects only outsiders with the evil subtype, as well as the lingering effects caused by their gifts, presence, and spells. It can also detect clerics and paladins of fiendish deities, including Asmodeus, archdevils, daemonic harbingers, and demon lords.}
        
\DeclareSpell{Devil Snare}{abjuration () [good]|V,  S,  M (a pouch of silvered powder worth 25 gp)|1 full-round action|touch|Effect10-ft.-radius circle|1 round/level|Will negates; see text|yes; see text}[]
    \DeclareSpellDescription{Devil Snare}{Your touch creates an invisible circle on a flat surface. Any outsider passing through this circle must succeed at a Will save or be caught within. Once trapped, a creature must succeed at a Will save as a standard action to physically exit the confines of the circle, teleport, or use any form of extradimensional travel (as per dimensional anchor). Contained outsiders can still attack adjacent creatures outside of the circle, or target others with ranged attacks, spells, and spell-like abilities. Despite the spell's name, devil snare captures outsiders of any type, not only devils.  As a standard action, you can dismiss the circle, expelling any outsiders still trapped within to their planes of origin (as per dismissal). An outsider can resist this effect with a successful Will save, enabling it to remain after the spell is dismissed.}
        
\DeclareSpell{Punishing Armor}{abjuration () []|V,  S|1 standard action|personal|Targetsyou|10 minutes/level (D)|Fortitude negates; see below|no}[]
    \DeclareSpellDescription{Punishing Armor}{You coat yourself with a thin layer of shimmering energy. Any creature dealing nonlethal damage to you immediately takes half the amount of nonlethal damage dealt. A successful Fortitude save made by the attacking creature negates this damage.}
        
\DeclareSpell{Unholy Ward}{abjuration () [evil]|V,  S,  DF|1 standard action|personal|Targetsyou|10 minutes/level (D)|Fort negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Unholy Ward}{This spell grants you resistance to the holy powers of good-aligned deities and their servants. You resist 10 points of damage from holy sources (divine power damage from flame strike, additional damage from smite evil, channeled positive energy, etc.), provided they originate from a good-aligned source or a servant of a good-aligned god. You ignore a maximum of 10 points of damage per caster level, at which point the spell ends.}
        
\DeclareSpell{Blood Tentacles}{necromancy () []|V,  S,  M (a fresh handful of the caster's blood)|1 standard action|personal|Targetsyou|1 round/level|Will negates (harmless)|no}[]
    \DeclareSpellDescription{Blood Tentacles}{You smear a handful of your own blood across your chest, causing one writhing tentacle per caster level to burst forth. You can direct these tentacles to attack a single creature within 15 feet as a standard action, or one creature per 5 caster levels as a full-round action. Each tentacle has an attack bonus equal to your base attack bonus plus either your Constitution or Charisma bonus (whichever is higher). Each tentacle deals 2d6 points of damage, and a tentacle collapses into dried blood on a successful hit, granting you a number of temporary hit points equal to the damage dealt. You can't gain more temporary hit points than your maximum number of hit points. These temporary hit points disappear after 1 hour.}
        
\DeclareSpell{Caustic Safeguard}{abjuration () [acid]|V,  S,  M (a thin metal wire and a vial of acid)|1 round|touch|Targetsobject touched|1 hour/level (D)|Reflex half (see text)|no}[]
    \DeclareSpellDescription{Caustic Safeguard}{You imbue a single object with an acidic protective ward. Any creature other than you that touches the object takes 1d6 points of acid damage per 2 caster levels (maximum 10d6; Reflex half). Each time the spell discharges, the number of damage dice it deals is halved (rounded down); when the spell's damage dice reach 0, the spell ends. While casting this spell, you can touch up to one creature per 4 caster levels, which allows them to handle the warded object without triggering this spell.}
        
\DeclareSpell{Coward's Cowl}{enchantment () [mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 minute/level|Will negates (harmless)|no}[]
    \DeclareSpellDescription{Coward's Cowl}{You imbue the target with a compulsion to avoid threats, enhancing its defensive instincts. So long as the affected creature  does not move closer to enemies during its turn, or moves at least 5 feet away from adjacent enemies, it gains a +1 morale bonus to its AC, and a +1 morale bonus on saves and on attack rolls made as readied actions and attacks of opportunity. Alternatively, if the affected creature does not close with its enemies, it can increase the DC of all spells it casts as part of a readied action by 1. If the subject of the spell willingly moves toward a threatening creature, the spell immediately ends.  While affected by coward's cowl, a creature takes a -2 penalty on all saving throws against fear effects.}
        
\DeclareSpell{Dream Dalliance}{illusion (phantasm) [mind-affecting]|V,  S|1 round|medium (100 ft. + 10 ft./level)|Targetsone creature|instantaneous|Will disbelief, then Will partial (see text)|yes}[]
    \DeclareSpellDescription{Dream Dalliance}{You create a comforting phantasm, which leeches onto the psyche of a nearby target. The creature can attempt a Will saving throw to prevent the phantasm from entering its psyche, but otherwise it takes up permanent residence in the creature's mind. The phantasm fills its target's dreams with happy visions, comforting manifestations of loved ones, and incredible vistas, feeding the target a perfect fantasy life it never wishes to leave. After the target's next night's sleep, the target must succeed at a Will saving throw to wake up; otherwise, it remains asleep for the rest of the day and following night. Each night it must succeed at a new saving throw or remain asleep for days or weeks on end as it slowly starves to death (presuming it normally needs to eat to survive). Loud noises, jostling, and even pain won't rouse the slumbering target. Dealing 1 point of damage per the target's Hit Die awakens the target, but it awakens fatigued and takes a -2 penalty on all saving throws against spells and effects that may put it back to sleep until the phantasm has been banished.  The phantasm remains in its host's mind indefinitely, requiring a new Will saving throw to wake up every time the target rests, until it is removed via break enchantment, greater restoration, or miracle. Alternatively, the phantasm can be confronted in its host's mindscape (Pathfinder RPG Occult Adventures 202), where it manifests as a slothful duplicate of its host with identical abilities, skills, and attributes.}
        
\DeclareSpell{Enticing Adulation}{enchantment () [mind-affecting]|V,  S,  M (a lock of your hair)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|10 minutes/level|Will negates|yes}[]
    \DeclareSpellDescription{Enticing Adulation}{A targeted creature that fails its saving throw is filled with a deep desire to protect and care for you, fawning over your needs and ensuring your comfort. If another creature harms you, the target is immediately overcome with rage and is compelled to attack the aggressor, gaining a +2 morale bonus to Strength and Constitution, a +1 morale bonus on Will saves, and a -2 penalty to its Armor Class. These bonuses last until the instigating creature is defeated or retreats, or the target of the spell is killed or rendered unconscious. If other creatures have harmed you while the target is under this effect, the target continues to rage until all threats against you are defeated or driven off, after which the target creature is fatigued for as many rounds as it raged. Your target continues to fly into defensive rages each time a creature harms you so long as the spell's duration lasts, but cannot rage while fatigued.  If you are reduced below 0 hit points by an attack, the target creature must succeed at a second Will save or be compelled to defend your body, attacking anyone who comes near, for the remainder of the spell's duration. If the creature succeeds at this second save, the spell immediately ends.}
        
\DeclareSpell{Golden Guise}{transmutation () []|V,  S,  M (10 gold pieces)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone object weighing no more than 5 lbs./level|1 minute/level|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Golden Guise}{You cause an object to briefly transform into gold. Affected items gain the properties of gold (Pathfinder RPG Ultimate Equipment 53) until the spell expires. Weapons reduce their hardness by half and gain the fragile quality, while piercing and slashing weapons take a -2 penalty on damage rolls (minimum 1 damage). This spell increases the affected item's armor check penalty by 2 and decreases its armor or shield bonus by 2. Gold armor has hardness 5.}
    