    
\DeclareSpell{Apathy}{enchantment (compulsion) [emotionUM,  mind-affecting]|S,  V,  M (a shiny bead)|1 standard action|long (400 ft. + 40 ft./level)|Targetsone creature|1 hour/level|Will negates|yes}[]
    \DeclareSpellDescription{Apathy}{You cause a creature to temporarily lose interest in a passion or pursuit, taking the heat off your trail to facilitate a getaway, the finalization of a scheme, or the elimination of incriminating evidence. When casting the spell, you designate a subject or activity about which the target becomes indifferent. While under the effects of apathy, the target takes a -5 penalty on all skill checks and ability checks to investigate, pursue, or otherwise advance its goals in relation to the designated subject. In most cases, however, the target does not attempt such checks if they can be avoided, as it simply has no interest in putting effort into the endeavor.  If the chosen activity is something that would be harmful for the target to refrain from doing (such as eating, sleeping, or holding its breath underwater), the target receives a +5 bonus on the saving throw or other check required by its inaction, and receives a new saving throw to negate the effects of this spell with the same +5 bonus immediately after. The bonus on these saving throws and checks increases by 1 for each subsequent check required by the same condition. If you directly interact with the target of this spell (such as engaging it in combat or targeting it with another spell or effect), the spell immediately ends.}
        
\DeclareSpell{Assumed Likeness}{illusion (phantasm) [emotionUM,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature/level, no two of which can be more than 30 ft. apart|10 minutes/level (D)|Will disbelief|yes}[]
    \DeclareSpellDescription{Assumed Likeness}{You draw upon the memories of the targets to create a visual disguise for yourself that only they can see. When you cast the spell, you choose an emotion from the table below. Each target perceives you as a creature it feels that way toward. If it doesn't feel that way toward anyone, it instead perceives you as a stranger with features likely to  evoke that emotion (e.g., if you choose respect, a guard who was taught to respect her elders but who currently knows no elders might see you as an elderly version of yourself). Since you don't know how you will appear to each target, you must match your actions and statements to fit with the illusion as best you can. While the spell grants a +10 bonus on Disguise checks like disguise self does, you also take a -5 penalty on Disguise checks until you can get a sense of who the target thinks you are. Each target who fails to disbelieve the phantasm and is fooled by your Disguise check takes a -2 penalty on Sense Motive checks to notice your lies, and each emotion choice grants you an additional benefit against such targets, as listed in the table below.     EmotionEffectFear+4 bonus on Intimidate checksHate+2 bonus on attack rolls, -2 penalty to ACLust+4 bonus on Sleight of Hand checksRespect+4 bonus on Diplomacy checksTrust+4 bonus on Bluff checks }
        
\DeclareSpell{Calistria's Guardian Wasps}{conjuration (summoning) []|V,  S,  M (a glob of spiced honey)|10 minutes; see text|close (25 ft. + 5 ft./2 levels)|Effectswarm of wasps that builds a nest; see text|1 day/level|none|no}[]
    \DeclareSpellDescription{Calistria's Guardian Wasps}{You summon a wasp swarm (Pathfinder RPG Bestiary 275) that builds a 10-foot-by-10-foot nest in the place you designate-typically under the eaves of a house, amid the rafters of a tavern, or in another obscured place. The wasp swarm takes the spell's casting time to build its nest; if the  swarm is disrupted in any way (such as by being attacked) before you finish casting this spell, the wasps disappear and the spell fizzles.  Once the wasp swarm has built its nest, this spell also wards the area. As per alarm, when intruders that do not speak the password pass within 20 feet, the swarm is alerted and immediately leaves its nest and attacks the nearest intruder. The swarm pursues that intruder as best it can. Once the swarm attacks an intruder, you have no control over its target or direction of travel. When the spell ends, if the wasps have not left their nest, they and their nest disappear.}
        
\DeclareSpell{Commune With Texts}{divination () []|V,  S,  M (incense worth 250 gp)|1 minute|close (25 ft. + 5 ft./2 levels)|Targetsa collection of texts|1 hour/level||}[]
    \DeclareSpellDescription{Commune With Texts}{You quickly absorb the knowledge in the target, which can be any assortment of books, scrolls, or other texts. During the spell's duration, you can search the texts and immediately find the most relevant information regarding any topic the collection holds, potentially including singling out spellbooks or scrolls containing individual or particular types of spells. You can attempt Knowledge checks related to the collection's topics as if you were trained in those skills, and you know whether the collection contains any information about which you failed a Knowledge check in the past 24 hours. The bonus on Knowledge checks granted by the collection of texts (if any) increases by 2.  Additionally, you always deplete the maximum number of knowledge points from a library whenever you succeed at a Research check (Pathfinder RPG Ultimate Intrigue 148) using the target texts while this spell is in effect, even if completing the Research check takes longer than this spell lasts. Once during the duration of this spell, for a number of minutes equal to your caster level, you can also speak with the texts about anyone who has read or handled them previously, as per stone tell.}
        
\DeclareSpell{Daggermark's Exchange}{transmutation () [poisonUM]|V,  S,  M (a dose of poison)|1 standard action|personal|Targetsyou|instantaneous||}[]
    \DeclareSpellDescription{Daggermark's Exchange}{You swallow a dose of poison with no effect and regurgitate a dose of a different poison (your choice) into the old container (or another you have on hand). Attempt a Craft (alchemy) check against the new poison's DC. If you succeed, you create a dose of your chosen poison. If you fail, the poison you regurgitate is inert. If you roll a natural 1, you expose yourself to the original poison (although you remain immune to that poison if you have venom immunity or a similar class feature or ability). The new poison's price must be the same as or less than the original poison's price.}
        
\DeclareSpell{Diminished Detection}{abjuration () []|S,  V,  M (a piece of wool)|1 standard action|personal|Targetsyou|1 hour/level||}[]
    \DeclareSpellDescription{Diminished Detection}{You can avoid being detected when you are on the edges of some divination spells' ranges. Whenever you would normally be within the area of effect of a detection spell (such as detect magic, detect evil, or detect undead), the area of effect is reduced by half for the purposes of the spell's caster detecting you or your possessions. The caster of the detect spell is unaware of this reduction in her spell's range; she simply does not detect you.}
        
\DeclareSpell{Dongun Shaper's Touch}{transmutation () []|V,  S|1 standard action|touch|Targetsobject touched|concentration, up to 1 round/level|none|no}[]
    \DeclareSpellDescription{Dongun Shaper's Touch}{You create an alchemical residue on your hands that allows you to reshape any nonmagical, unattended object with  hardness 19 or less as though it were clay. Objects with hardness 9 or less are like soft clay, allowing you to reshape up to 1 cubic foot per round of effort. Objects with hardness 10 or higher are harder to mold, allowing you to reshape up to 1/4 cubic foot per round. The object retains its new shape for 24 hours before returning to its original shape. This spell does not allow you to reshape a portion of a large object, such as a wall; you must be able to reshape the entire target within the spell's duration or the spell fizzles and has no effect.}
        
\DeclareSpell{Dream Reality}{illusion (compulsion) [mind-affecting]|V|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 minute/level (D)|Will disbelief|yes}[]
    \DeclareSpellDescription{Dream Reality}{You cause the target to perceive the world as if in a dream. When the spell ends, the target forgets all identifying details of events that transpired while the spell lasted. The memories were not taken from it; rather, its mind never recorded the memories as real in the first place. If modify memory is cast upon it before the spell ends, the target remembers these events. A target under the effect of lullaby before this spell is cast applies its penalty to the saving throw against this spell.}
        
\DeclareSpell{Implant Urge}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 hour/level|Will partial|yes}[]
    \DeclareSpellDescription{Implant Urge}{You make the target unconsciously desire a goal you define when you cast this spell. The DC of any Diplomacy check to ask the target to act in a way that it believes will lead it toward that goal decreases by 5. The target takes a -2 penalty on saving throws against mind-affecting effects that compel it to act in a way that it believes will lead it toward that goal. Spells that reveal the target's goals or thoughts reveal the implanted urge as the target's most important goal and the target does not register as thinking of anything else as long as it is presented with the focus of its urge or a way to move toward its goal. Anyone studying the target's thoughts can notice the implanted nature of this urge with a successful caster level check.}
        
\DeclareSpell{Inveigle Monster}{enchantment (charm) [mind-affecting]|V,  M (a drop of alcohol)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone living creature|1 day/level|Will negates|yes}[]
    \DeclareSpellDescription{Inveigle Monster}{This spell functions as inveigle person except as noted above.}
        
\DeclareSpell{Inveigle Person}{enchantment (charm) [mind-affecting]|V,  M (a drop of alcohol)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone humanoid creature|1 hour/level|Will negates|yes}[]
    \DeclareSpellDescription{Inveigle Person}{You cause the target to become extremely amiable. The target treats all other living creatures as if it were friendly toward them. Any overtly hostile or harmful act toward the target by any living creature ends the spell.  An inveigled creature attempts to fulfill multiple requests in the same manner as it would favors for its true friends. If such requests conflict, it usually chooses the more reasonable option-overriding this preference requires succeeding at an opposed Charisma check, as if under multiple forms of mental control (Pathfinder RPG Core Rulebook 209).}
        
\DeclareSpell{Nex's Secret Workshop}{abjuration () []|V,  S,  M (diamond dust worth 150 gp)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsany number of creatures or objects in range|1 hour/level|Will negates (harmless, object)|yes (harmless, object)}[]
    \DeclareSpellDescription{Nex's Secret Workshop}{Designed to protect a large number of items from rivals of the Arclords of Nex, this spell functions as nondetection except as noted above. You can exclude any creatures or objects in the spell's range when casting this spell, if you wish.}
        
\DeclareSpell{Oath Of Anonymity}{illusion (glamer) []|V|1 standard action|personal|Targetsyou|10 minutes/level||}[]
    \DeclareSpellDescription{Oath Of Anonymity}{You swear an oath not to reveal your identity, magically preventing anyone from discovering it so long as you avoid revealing your face or other easily identifiable features. The spell distorts your voice and subtly alters your body language and the appearance of your gear and any animals you use, whether as companions, mounts, or otherwise. This spell does not make you appear to be a different creature type, nor does it change your apparent height or body type.  This spell provides you with a +10 bonus on Disguise checks to conceal your identity, but not on checks to impersonate anyone in particular. This spell distorts the appearance of your voice, gear, and animals in the same way each time, essentially creating an alternate persona that can be recognized by those who have observed it before.}
        
\DeclareSpell{Recorporeal Incarnation}{necromancy () []|V,  S,  F (a gem worth at least 250 gp)|10 minutes|touch|Targetsone willing living creature and one humanoid corpse|1 week/level|none|no}[]
    \DeclareSpellDescription{Recorporeal Incarnation}{Recorporeal incarnation effectively replaces the target living creature's body with that of the target corpse. The target corpse must be fresh-either dead for no more than 24 hours or appropriately preserved by an effect such as gentle repose. While casting the spell, you must remain in contact with the corpse while touching the living target with the focus item. As the spell is cast, the dead body's flesh unravels like ribbons to sheathe the living target, who must be within one size category of the corpse. While the spell is in effect, the focus item must remain within 30 feet of the target living creature.  The living target gains the physical appearance and size of the corpse, and gains its abilities as defined in alter self as well as any immunities, weapon proficiencies, weaknesses, and spell resistance the dead target had while living. The living target gains a +20 circumstance bonus on Disguise checks to impersonate the individual whose corpse is targeted by this spell. The disguise created by recorporeal incarnation lasts for a number of weeks equal to your caster level, or until the focus item is moved more than 30 feet away from the living target. When the effect ends, the living target returns to its normal form, sloughing off the corpse's flesh.  The greatest strength of recorporeal incarnation is the difficulty of detecting it as a disguise. If subjected to detect magic, the living target sheds no magical aura, though the focus item gives off an aura of strong necromantic magic. True seeing does not reveal the living target's true form, since the corpse's flesh magically obscures it. The spell detect undead and similar effects indicate the living target is an undead creature, but the target is not truly undead, and is not affected by any other effects that target undead creatures. Recorporeal incarnation does not disguise the target's alignment.  If the living target of recorporeal incarnation dies while the spell is in effect, the spell continues. Any raise dead or similar spell cast upon that target resurrects that target, not the corpse flesh. Since recorporeal incarnation destroys the majority of the target corpse's physical remains, the target corpse cannot be restored to life except by miracle, resurrection, true resurrection, or wish.  Recorporeal incarnation can be made permanent by a 15th-level caster using permanency with a material component worth 17,500 gp.}
        
\DeclareSpell{Rotting Alliance}{necromancy () [curseUM,  diseaseUM]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone living creature/level, no two of which can be more than 60 feet apart|permanent|Fortitude negates|yes}[]
    \DeclareSpellDescription{Rotting Alliance}{You curse two or more creatures to sicken and waste away while in each others' company. Each target that fails a Fortitude save becomes cursed with a wasting sickness. The disease has no onset period, and those who contracted it must attempt a second Fortitude save immediately. A target that fails this second saving throw takes 1d6 points of Constitution damage and 1d6 points of Charisma damage. Every day thereafter, each target that was within 100 feet of another target during the previous 24 hours takes 1d6 points of Constitution damage and 1d6 points of Charisma damage (reroll to determine the specific amount of damage each day). A successful Fortitude save negates the damage for that day only.  A target cannot be healed of damage from this disease (naturally or by magic) while the target is within 100 feet of another target. If healed of such damage while away from other targets, a target might take damage again the day they reconvene. This disease is a curse, and can never be cured by successful saving throws. The spell can be ended on a single target only with a successful casting of remove curse followed by a successful casting of remove disease while the target is within 100 feet of at least one other target. When the curse remains on only one target, it ends automatically.}
        
\DeclareSpell{Sealed Sending}{conjuration (creation) [language-dependent]|V,  S|1 standard action|unlimited|Effectone nonmagical parchment with a written message|1 hour/level or until discharged|none (harmless)|no (harmless)}[]
    \DeclareSpellDescription{Sealed Sending}{You create a scroll bearing a message in any language you can speak, with a maximum length of 50 words. The scroll magically appears anywhere you have viewed at least once on the same plane of existence you are on now. When the spell ends or when the message has been read completely, the scroll disintegrates, leaving no trace. This spell cannot be detected, traced, or blocked by any spell of a lower level.}
        
\DeclareSpell{Searching Shadows}{illusion (shadow) [shadowUM]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Effectshadows in a 10-foot-radius spread|concentration|Reflex partial|yes}[]
    \DeclareSpellDescription{Searching Shadows}{Strands of shadow probe an area, searching for a creature or object you specify by shape, size, or texture. Each round, the shadows attempt a Perception check on the squares they touch with a total bonus equal to your caster level + your Charisma or Intelligence modifier, whichever is higher. You can move the shadows up to 30 feet or change the search criteria as part of concentrating on the spell. Whenever the shadows come into contact with a creature with spell resistance, you must attempt a caster level check to overcome its spell resistance. If you fail, the spell ends.  When the shadows locate a desired item or creature, you are aware of its shape and size and can order the shadows to try to seize it. If the shadows are seeking a creature, the area they cover becomes difficult terrain for that creature, and the creature must succeed at a Reflex saving throw or become entangled and unable to move. Changing the criteria of the creature or object sought or moving the shadows away from an entangled target frees it. If the target is an object carried by a creature, the shadows attempt a disarm or stealAPG combat maneuver check as appropriate, using the same modifier as for their Perception check. The shadows can pick up and move unattended, nonmagical objects that weigh up to 5 pounds.}
        
\DeclareSpell{Seeds Of Influence}{enchantment (compulsion) [emotionUM,  mind-affecting]|S,  M (a rose)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 hour/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Seeds Of Influence}{You leave a magical trace in the mind of a creature with an attitude of at least indifferent toward you. The target takes a cumulative -2 penalty on its Will save to negate the spell for each step by which its attitude is better than indifferent.  The target takes a -2 penalty on saving throws against divination spells you cast. You can target that creature with mind-affecting spells of a spell level lower than seeds of influence as if those spells were modified by Enlarge Spell (the modified spell doesn't take longer to cast and doesn't use a higher-level spell slot). Whenever the target succeeds at a saving throw against a divination or mind-affecting spell you cast, seeds of influence ends for that target. A creature can  be subject to only one seeds of influence spell at a time; later castings of seeds of influence remove any previous casting.}
        
\DeclareSpell{Seeds Of Influence, Greater}{enchantment (compulsion) [emotionUM,  mind-affecting]|S,  M (a rose)|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsone creature|1 day/level (D)|Will negates|yes}[]
    \DeclareSpellDescription{Seeds Of Influence, Greater}{This spell functions as seeds of influence, except that if the target is protected by a spell that grants immunity, spell resistance, or a saving throw bonus against a divination or mind-affecting spell you cast on the target, you can attempt caster level checks to dispel each such effect before applying the effects of those protections against the spell. The DC of the caster level check to dispel each effect is equal to 11 + the effect's caster level. Such spells cast on the target while greater seeds of influence is active grant no protection against greater seeds of influence.}
        
\DeclareSpell{Seek Shelter}{enchantment (compulsion) [fear,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targetsall non-hostile creatures with 4 or fewer HD in a 30-ft. spread|1 hour/level (D)|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Seek Shelter}{You send an empathic urge to seek safety both as fast as possible and in an orderly fashion, and to remain in such secure locations for the duration of the spell. Targets with 5 or more Hit Dice are unaffected. When you cast the spell, you can designate a fortified location-either general (such as "indoors") or specific (such as "the local garrison")-for the targets to attempt to reach. If you do not specify a location for the targets to retreat to, they attempt to find safety to the best of their ability. Affected creatures defend themselves normally but attack only if provoked.}
        
\DeclareSpell{Substitute Trail}{transmutation () []|V,  S|1 standard action||Targets1 creature/level; see text|1 day/level (D)|none|no}[]
    \DeclareSpellDescription{Substitute Trail}{This spell can affect any creatures with which you interacted in the last 24 hours. You alter the trails left by the chosen creatures, making it appear that another creature with which you are familiar left the trail instead (you must have met the creature with which you are familiar). If a tracker exceeds the DC of the skill check to follow the trail by an amount equal to  your caster level, the tracker recognizes that the trail has been manipulated by this spell, although it cannot see the trail's true nature unless it uses magical means, such as true seeing.}
        
\DeclareSpell{Transfiguring Touch}{transmutation () []|V,  S, M,  whichever is more)|1 standard action|touch|Targetsobject touched, up to 1 cubic foot per level|instantaneous|none|no}[]
    \DeclareSpellDescription{Transfiguring Touch}{You create an alchemical residue on your hands that gradually converts a touched, unattended, nonmagical object into iron, paper, or wood (your choice). The spell converts at most 1 cubic foot of material per caster level you have; if the object is larger than the maximum volume, the transfiguration stops once that amount of matter has been converted. If your caster level is at least 14th, you can opt to create lead. If your caster level is at least 19th, you can opt to create precious metals. If you create a precious metal, you must use an equivalent value of alchemical reagents as a material component (5 sp per pound of copper, 5 gp per pound of silver, 50 gp per pound of gold, 500 gp per pound of platinum).}
        
\DeclareSpell{True Skill}{divination () []|S,  V|1 standard action|personal|Targetsyou|1 minute/level||}[]
    \DeclareSpellDescription{True Skill}{When faced with an important situation, you grant yourself a magical edge to ensure your success. When casting this spell, select one skill for which you can attempt a skill check. The next time you attempt a skill check using the selected skill (before the spell's duration ends), you gain an insight bonus on the check equal to 1/2 your caster level (minimum 1).}
        
\DeclareSpell{Violent Accident}{transmutation () [curseUM]|V,  S|1 standard action|long (400 ft. + 40 ft./level)|Targetsone creature|1 day or until discharged|Reflex half; see text|yes}[]
    \DeclareSpellDescription{Violent Accident}{You curse the target to suffer a violent accident  within the next 24 hours. You have no control over the form the accident takes or when it strikes. The target can avoid being cursed with spell resistance when you cast the spell, but otherwise receives no saving throw. Regardless of the accident's nature, it is magically empowered to deal an amount of damage equal to 1d8 x your caster level (maximum 5d8 points of damage), and the damage is of a type appropriate to the source of damage (such as fire for an explosion or bludgeoning for a falling object). When the accident occurs, the target can attempt a Reflex saving throw to reduce the damage by half. Although others might be surprised or inconvenienced by the accident, it damages only the target.}
        
\DeclareSpell{Wandering Trail}{transmutation () []|V,  S|1 standard action|1 mile/level|Targetsup to one creature/level within 180 feet|1 day/level (D)|none|no}[]
    \DeclareSpellDescription{Wandering Trail}{You cause the trail left by the targets within range to automatically reroute, potentially taking any course within the area. Your modification of the trail within the spell's area can result in a trail at least half the original length or up to twice the original length. If the trail continues beyond the spell's range, you must leave it connecting at that point on the edge of the spell's range. If a tracking creature exceeds the DC of the skill check to follow the trail by an amount equal to your caster level, the tracker recognizes that the trail has been manipulated by this spell, although it cannot see the trail's true nature unless it uses magical means, such as true seeing.}
    