    
\DeclareSpell{Disrupt Link}{abjuration () []|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone creature and her animal companion, familiar, or other bonded creature (which may be no more than 30 ft. apart)|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Disrupt Link}{The target has her link with her bonded creature temporarily severed. If the subject has a familiar, she loses the benefits of the alertness, deliver touch spells, empathic link, scry on familiar, share spells, and speak with master abilities. If the target has an animal companion, she loses the benefits of the link, share spells, and devotion abilities. The target and her familiar or animal companion also lose any other abilities (such as those from archetypes or feats) that rely on the two having a connection.}
        
\DeclareSpell{Duplicate Familiar}{conjuration (creation) []|V,  S,  M (alchemically preserved mockingfey feathers),  F (familiar)|1 standard action|touch|Effecttemporary duplicate of familiar touched|10 minutes/level|Fortitude negates|no}[]
    \DeclareSpellDescription{Duplicate Familiar}{You create a duplicate of a familiar. The familiar's master can use the duplicate as if it were his familiar in all respects, though he doesn't gain the bonus special ability from more  than one familiar at a time. When the spell's duration expires, the familiar duplicate shrivels into nothing, even if petrified or otherwise transformed.}
        
\DeclareSpell{Empathy Conduit}{necromancy () []|V,  S,  F (a glass rod)|1 standard action|medium (100 ft. + 10 ft./level)|Targetsan animal companion, familiar, or other bonded creature and its master (which may be no more than 30 ft. apart)|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Empathy Conduit}{You make a conduit between the targeted master and her familiar, allowing you to target the master or the familiar with your spells in order to affect the other. If the master succeeds at its save to resist this spell but the familiar fails, you can choose to have your spells that target the master affect the familiar instead. If the familiar resists but the master doesn't, your spells that target the familiar can affect the master instead. If both the familiar and the master fail to resist this spell, you can affect either the familiar or the master when you target either with a spell. When you target the master to affect her familiar or vice versa, the target attempts a save (if one is allowed) with its own saving throw bonus, but the other creature is affected by the spell.  Only spells that target one or more creatures can be cast through empathy conduit. The creature to be affected must still be a valid target of the spell being cast; for example, you can't affect a familiar with charm person through an empathy conduit. Spells with a duration other than instantaneous that are cast through an empathy conduit last either their normal duration or until the empathy conduit expires, whichever comes first. Whenever the master or its familiar is targeted with a spell intended to affect the other creature, the targeted creature can attempt an additional save against the empathy conduit.}
        
\DeclareSpell{Soulswitch}{necromancy () []|V,  S,  F (two brass collars worth 50 gp each)|1 standard action|touch|Targetsyou and your familiar|10 minutes/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Soulswitch}{You may only cast this spell if you currently have a familiar. You place your soul into the body of your familiar, and your familiar's soul is placed in your body. This functions as if you possessed your familiar using magic jar; your familiar simultaneously possesses your body in the same manner. You can't freely transfer your soul between your body and your familiar's-if you choose to return to your body as a standard action, the spell ends. If either body is killed, both spirits return to their original bodies, the spell ends, and the original owner of the slain body dies.}
        
\DeclareSpell{Transfer Familiar}{evocation () []|V,  S|1 standard action|touch|Targetsyour familiar and one willing creature|1 day/level (D)|none|no}[]
    \DeclareSpellDescription{Transfer Familiar}{You temporarily grant control of your familiar to another willing creature. You, your familiar, and the target creature must all be touching each other when you cast this spell. The target gains all the benefits and abilities normally associated with having a familiar, including the ability to share spells, speak with the familiar, and so on. You lose all of these benefits for the duration of the spell. If the target already has a familiar, the spell fails.}
    