    
\DeclareSpell{Ape Walk}{transmutation|V,  S,  M (an ape or monkey paw)|1 standard action|touch|Targets: creature touched|10 minutes/level|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Ape Walk}{(harmless) The subject can climb as well as an ape or monkey, gaining a climb speed of 30 feet and a +8 racial bonus on Climb skill checks. The affected creature must have her hands free to climb in this manner. In addition, as long as she has 10 feet of space in which to make a running start, the subject can make a long jump of up to 10 feet without making an Acrobatics check (an Acrobatics check is still required to jump longer distances).}
        
\DeclareSpell{Defoliate}{necromancy|V,  S,  M (a locust)|1 standard action|close (25 ft. + 5 ft./2 levels)|Area: see text|instantaneous|none|yes}[]
    \DeclareSpellDescription{Defoliate}{You hurl a tiny ball of negative energy, destroying plant life either in a line 60 feet long or a 10-foot-radius spread. This effect removes the cover and concealment provided by trees and undergrowth, eliminates the movement penalties associated with undergrowth, and so forth.

You may also target a single plant creature with this spell.

You must succeed on a ranged touch attack to hit your target.

An affected plant creature takes 2d8 points of damage.}
        
\DeclareSpell{Heatstroke}{evocation [fire]|V,  S,  M (a drop of sweat)|1 standard action|close (25 ft. + 5 ft./2 levels)|Effect: ray|1 minute/level|Fortitude partial, see text|yes}[]
    \DeclareSpellDescription{Heatstroke}{A wavering red ray projects from your finger. You must succeed on a ranged touch attack with the ray to hit your target.

The ray inflicts 1d4 points of nonlethal damage, causing the target to suffer from heatstroke as its body temperature dramatically increases. Except as noted above, this spell otherwise functions as ray of exhaustion.

Characters wearing heavy clothing or armor of any sort take a -4 penalty on their saves.}
    