    
\DeclareSpell{Anywhere But Here}{conjuration (teleportation) []|V|1 standard action|touch|Targetsyou and up to four willing creatures, none of whom can be on their home plane|instantaneous|Will negates (harmless)|no}[Transport yourself and willing creatures to a random planar destination.]
    \DeclareSpellDescription{Anywhere But Here}{This spell functions similarly to plane shift, but instead of transporting the targets to a destination near an intended location on a specific plane, anywhere but here transports affected creatures to a random plane. A creature can be affected by anywhere but here only if it is currently not on its home plane (although targets can, by chance, end up traveling to their home plane as a result of this spell). Subjects always appear in a location that is not inherently harmful, but the exact destination is otherwise random. The specific plane is determined by the table below; the location on the destination plane where the transported creatures arrive is completely subject to the GM's whim.     d\%Planar Destination1-7Abyss8-14Abaddon15-20Hell21-24Shadow Plane25-28First World29-35Maelstrom36-42Boneyard43-49Axis50-56Ethereal Plane57-63Elysium64-70Nirvana71-77Heaven78-84Astral Plane85-90Random demiplane91-95Material Plane (random world)96-100GM's choice   A creature that is transported by anywhere but here cannot be affected by a subsequent casting of anywhere but here for 24 hours afterward (but can be affected normally by other forms of planar travel).}
        
\DeclareSpell{Arbitrament}{evocation () [sonic]|V|1 standard action|40 ft.|Targetsnon-neutral creatures in a 40-ft.-radius spread centered on you|instantaneous|Will partial, see text|yes}[Harms creatures of extreme alignments.]
    \DeclareSpellDescription{Arbitrament}{All chaotic evil, chaotic good, lawful evil, and lawful good creatures within the area of this spell suffer the following conditions, based on their Hit Dice.   Hit DiceEffectEqual to caster levelSickenedUp to caster level - 1Sickened, staggeredUp to caster level - 5Nauseated, sickened, staggeredUp to caster level - 10Killed, nauseated, sickened, staggered   The effects are concurrent. A creature can attempt a Will save to reduce or negate the effects. If subject to multiple effects, the creature rolls once and applies the result to each effect.  Sickened: The creature is sickened for 1d4 rounds (Will negates).  Staggered: The creature is staggered for 2d4 rounds, or for 1d4 rounds on a successful Will save.  Nauseated: The creature is nauseated for 1d10 minutes, or for 1d4 rounds on a successful Will save.  Killed: Living creatures die, and undead creatures are destroyed. On a successful Will save, the creature instead takes 3d6 points of damage + 1 point per caster level (maximum +25).  Furthermore, if you are on your home plane when you cast this spell, all chaotic evil, chaotic good, lawful evil, and lawful good extraplanar creatures within the area are banished to their home planes (Will negates, at a -4 penalty). Creatures so banished cannot return for at least 24 hours. This effect takes place regardless of whether the creatures hear the arbitrament.  Creatures whose Hit Dice exceed your caster level are unaffected by arbitrament.}
        
\DeclareSpell{Ardor's Onslaught}{evocation () []|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Area20-ft.-radius burst|instantaneous or 1d6 rounds; see text|Will partial, see text|yes}[Power of conviction harms neutral foes.]
    \DeclareSpellDescription{Ardor's Onslaught}{You unleash the power of zealous conviction to smite your enemies with a burst of pulsing metallic energy. Only creatures with a neutral alignment component are harmed by the spell.  The spell deals 1d8 points of damage per 2 caster levels (maximum 5d8) to creatures whose alignment is neutral with no other alignment components (with the exception of neutral outsiders, who take 1d6 points of damage per caster level,  maximum 10d6). Neutral outsiders are also nauseated for 1d6 rounds. A creature can attempt a Will save to halve the damage and negate the nauseated effect.  The spell deals half damage against creatures that are chaotic neutral, lawful neutral, neutral evil, or neutral good, and such targets are not nauseated. On a successful Will save, such a creature reduces the damage to one-quarter the damage rolled.}
        
\DeclareSpell{Bestow Planar Infusion I}{evocation () []|V,  S|1 standard action|touch|Targetscreature touched|1 hour/level|Fortitude negates (harmless)|yes}[Grant a target the effects of a planar infusion.]
    \DeclareSpellDescription{Bestow Planar Infusion I}{This spell draws upon the latent planar energy of the caster's surroundings, allowing her to temporarily infuse a creature with the plane's power. The touched creature gains that plane's basic infusion for the spell's duration. This spell has no effect if cast on the Material Plane, and it ends as soon as the spell's target leaves the plane with which it has been infused. Details on planar infusions can be found in each plane's Infusion section, as presented in Chapter 3 of this book.  Once a creature gains the benefits of bestow planar infusion I, it remains attuned to that plane for 24 hours. Additional castings of bestow planar infusion I during this time bestow the same infusion that was granted by the initial casting that day. Planar infusions that can be used a limited number of times per day are not refreshed by multiple castings of bestow planar infusion I.}
        
\DeclareSpell{Bestow Planar Infusion II}{evocation () []|V,  S|1 standard action|touch|Targetscreature touched|1 hour/level|Fortitude negates (harmless)|yes}[Grant a target the effects of an improved planar infusion.]
    \DeclareSpellDescription{Bestow Planar Infusion II}{This functions as bestow planar infusion I, except that the touched creature gains the improved infusion of the current plane.}
        
\DeclareSpell{Bestow Planar Infusion III}{evocation () []|V,  S|1 standard action|touch|Targetscreature touched|1 hour/level|Fortitude negates (harmless)|yes}[Grant a target the effects of a greater planar infusion.]
    \DeclareSpellDescription{Bestow Planar Infusion III}{This functions as bestow planar infusion I, except that the touched creature gains the greater infusion of the current plane.}
        
\DeclareSpell{Counterbalancing Aura}{abjuration () []|V,  S,  F (a set of scales worth 500 gp)|1 standard action|20 ft.|Targetsone creature/level in a 20-ft.-radius burst centered on you|1 round/level|see text|yes}[Targets gain +4 to AC and saves; resist attacks and spells from neutral creatures.]
    \DeclareSpellDescription{Counterbalancing Aura}{An oscillating bronze glow surrounds the targets, protecting them from attacks, granting them resistance to spells cast by neutral creatures, and sickening or nauseating neutral creatures that strike the targets. This abjuration has four effects.  First, each warded creature gains a +4 deflection bonus to AC and a +4 resistance bonus on saving throws. This benefit applies against all attacks and effects, not just attacks by neutral creatures.  Second, a warded creature gains spell resistance 23 against spells cast by chaotic neutral, lawful neutral, neutral evil, and neutral good creatures, and spell resistance 27 against spells cast by neutral creatures with no other alignment components.  Third, the spell protects warded creatures from possession and influence by such creatures (otherwise as protection from evil).  Finally, if a chaotic neutral, lawful neutral, neutral evil, or neutral good creature successfully hits a warded creature with a melee attack, the attacker is sickened for 1d6 rounds (Fortitude negates). If a neutral creature successfully hits a warded creature with a melee attack, the attacker is instead nauseated for 1d6 rounds (Fortitude negates).}
        
\DeclareSpell{Diminish Resistance}{transmutation () []|V,  S,  M/DF (a pinch of coarse sand)|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone creature|1 round/level (D)|Fortitude negates|yes}[Weaken a creature’s energy resistance.]
    \DeclareSpellDescription{Diminish Resistance}{You weaken a creature's resistance against one energy type you select: acid, cold, electricity, fire, or sonic. The creature's resistance to that energy type decreases by 5 (minimum 0), plus an additional 5 for every 5 caster levels beyond 3rd (to a maximum of 20 at 18th level).}
        
\DeclareSpell{Dispel Balance}{abjuration () []|V,  S,  DF|1 standard action|touch|Targetsyou and a touched, neutral creature from another plane, or you and an enchantment on a touched creature or object|1 round/level or until discharged, whichever comes first|see text|see text}[You are protected from neutral creatures.]
    \DeclareSpellDescription{Dispel Balance}{Pulsing bronze energy surrounds you, bestowing three effects.  First, you gain a +3 deflection bonus to AC against attacks by chaotic neutral, lawful neutral, neutral evil, and neutral good creatures. Against attacks by creatures whose alignment is neutral with no other alignment components, this deflection bonus is instead +5.  Second, upon making a successful melee touch attack against a creature from another plane with a neutral component to its alignment, you can banish that creature back to its home plane. The creature's spell resistance applies to this attempt, and the creature can negate this effect with a successful Will save. If the creature's alignment is neutral with no other alignment components, the creature takes a -2 penalty on this saving throw. This use discharges and ends the spell.  Third, with a touch, you can automatically dispel any one enchantment spell cast by a creature with a neutral component to its alignment. Spells that can't be dispelled by dispel magic also can't be dispelled by dispel balance. Saving Throws and spell resistance do not apply to this effect. This use discharges and ends the spell.}
        
\DeclareSpell{Ether Step}{transmutation () []|S|1 immediate action|personal|Targetsyou|see text||}[Step briefly into the Ethereal Plane to avoid attacks and dangers that would otherwise harm you.]
    \DeclareSpellDescription{Ether Step}{You step into the Ethereal Plane long enough to dodge a blow or confound a spell; you must cast ether step after you are targeted by an attack or effect but before you learn the results of the attack or effect. This spell functions as ethereal jaunt, except that you become ethereal until the beginning of your next turn. On the turn after you cast this spell and return to your starting point, you can take only move actions or free actions.}
        
\DeclareSpell{Hasten Judgment}{necromancy () [curseUM]|V,  S,  M (2 silver pieces)|1 standard action|touch|Targetsone living or corporeal undead creature|1 day/level|Will negates|yes}[Quicken a soul’s journey to judgment—hampering resurrection or weakening undead foes.]
    \DeclareSpellDescription{Hasten Judgment}{This potent curse weighs upon the target's soul, hastening a living creature's journey to the Boneyard upon death or weakening an undead creature's animating force. A living creature that dies during the spell's duration cannot be affected by breath of life or similar effects, and the period during which attempts to restore the target to life can succeed is reduced to 1 hour/level (for raise dead), 1 day/level (for resurrection), or 10 days/level (for true resurrection). Reincarnate and similar effects work normally on a creature killed under this spell's effects.  An undead creature affected by this spell cannot gain temporary hit points, and any existing channel resistance the undead may have is reduced by half as long as the curse persists.  Creatures whose souls are separate from their bodies (such as liches) or are merged with their bodies (such as non-native outsiders) are unaffected by hasten judgment.}
        
\DeclareSpell{Homeward Bound}{abjuration () []|V,  S|1 minute|touch|Targetsone willing extraplanar creature|instantaneous|Will negates (harmless)|yes}[Return a creature to its home plane.]
    \DeclareSpellDescription{Homeward Bound}{This spell functions as dismissal, except as noted above.}
        
\DeclareSpell{Infuse Self}{transmutation (polymorph) []|V,  S,  M (a piece of the creature whose form you plan to assume)|1 standard action|personal|Targetsyou|10 minutes/level (D)||}[Assume the form of a native outsider.]
    \DeclareSpellDescription{Infuse Self}{When you cast this spell, you assume the form of a native outsider from the following list: aasimar, aphorite (see page 224), duskwalker (see page 230), fetchlingB2, ganzi (see page 234), ifritB2, oreadB2, shabtiB5, suliB3, sylphB2, tiefling, or undineB2. You gain a +2 size bonus to one physical ability score of your choice. If the race has resistance to one or more energy types, you gain energy resistance 5 to your choice of one of those types. If the race gains a racial bonus on saving throws or skills, you gain those bonuses. If the race has darkvision or low-light vision, you gain those qualities.}
        
\DeclareSpell{Invoke Deity}{transmutation () [see text]|V,  S,  M (incense worth 1, 000 gp),  F (a bejeweled holy symbol of your patron deity worth 2, 500 gp)|1 round|personal|Targetsyou|10 minutes/level||}[Infuse yourself with the powers of your deity’s planar realm.]
    \DeclareSpellDescription{Invoke Deity}{By holding aloft a holy symbol and calling your deity's name, you take on an aspect of that divinity. When you cast this spell, choose a domain offered by your deity. You gain that domain's benefits from the list below, along with the listed physical changes; abilities that allow a saving throw use this spell's DC. At any point during the duration of this spell, you can change which domain benefit you gain by concentrating for 1 round-this provokes attacks of opportunity and reduces the remaining duration of the spell by 10 minutes. If you have less than 10 minutes of the spell's duration remaining, you cannot change the selected domain in this way. If you change your domain, all ongoing effects from your previously chosen domain end.  You must worship a single divinity in order to cast this spell, even if you do not normally cast divine spells. If you perform an action that blatantly violates your deity's precepts while under this spell's effects, invoke deity immediately ends and you are stunned for a number of rounds equal to your Hit Dice. Invoke deity has the same alignment descriptors ([chaotic], [evil], [good], or [lawful]) as your deity's alignment. If an ability duplicates a spell, it functions as that spell heightened to a level equal to your invoke deity spell.  Air: You become wispy and translucent. You gain a fly speed of 60 feet with perfect maneuverability, or you increase your current fly speed by 30 feet-whichever results in a faster speed. While flying, you gain a +1 dodge bonus to your AC.  Animal: Your form becomes bestial with animalistic features. You gain low-light vision, scent, a +6 natural armor bonus, and a bite attack that deals damage as normal for a creature of your size. If you already have a bite attack, the damage increases as if you increased one size category. You can use speak with animals at will.  Artifice: Parts of your body are replaced by pistons and gears. You can be affected by spells that specifically affect constructs (such as make whole). You are immune to bleed, disease, and poison effects, and you gain a +4 bonus on saving throws against death effects, mind-affecting effects, and necromancy effects.  Chaos: Your flesh churns and swirls chaotically. You are immune to additional damage from critical hits and precision damage (such as sneak attack damage), and weapons you wield count as chaotic for the purpose of overcoming damage reduction.  Charm: You become overwhelmingly attractive and persuasive. You gain a +6 enhancement bonus to Charisma.  Community: Your voice echoes with the sound of multitudes. Select a number of creatures within 30 feet equal to your level divided by three-you gain the effects of status and telepathic bond with those creatures.  Darkness: Your eyes become solid black orbs. You become immune to blindness and can see perfectly in darkness of any kind, even that created by a deeper darkness spell.  Death: Your flesh becomes pallid. You are healed by both positive and negative energy, are immune to energy drain and death effects, and automatically stabilize when reduced below 0 hit points.  Destruction: The air around you crackles. You gain a +2 bonus on damage rolls with two-handed melee weapons. Spells you cast that cause hit point damage have their save DCs (if any) increased by 1. You gain a +4 bonus on Strength checks to break objects, and you ignore the first 5 points of hardness any object has when you attack it with a melee weapon.  Earth: Your flesh becomes stony. You gain DR 10/bludgeoning and are immune to petrification effects.  Evil: Your appearance becomes corrupted and fiendish. You automatically confirm critical hits, and weapons you wield count as evil for the purpose of overcoming damage reduction.  Fire: Your hair ignites into flames. You are immune to fire. As a standard action once per minute, you can fire a ray of flame, as per scorching ray (limit one ray).  Glory: Your countenance becomes stern and implacable, and your wrath devastates the undead. You gain the benefits of heroism and protection from evil, and your first successful attack each round against an undead target deals an additional 1d6 points of positive energy damage.  Good: Your appearance becomes pristine and angelic. You are immune to fear and compulsion effects, and weapons you wield count as good for the purpose of overcoming damage reduction.  Healing: Your appearance becomes hale and hearty. You gain fast healing 3, and your spells and class features that restore hit points each restore an additional 1d8 hit points.  Knowledge: You are surrounded by the sound of numerous turning pages. You gain a +6 enhancement bonus to Intelligence.  Law: A haze of mathematical symbols hovers around you. You are immune to hostile transmutation effects and all confusion effects, and weapons you wield count as lawful for the purpose of overcoming damage reduction.  Liberation: Your form becomes lithe and flexible. You gain a +6 enhancement bonus to Dexterity.  Luck: The faint sound of tinkling bells plays around you. You gain a +1 luck bonus to your Armor Class and on attack rolls, ability checks, saving throws, and skill checks. As an immediate action, you can force a single creature within 10 feet to reroll a single d20 it just rolled-you must use this ability before the results of the d20 roll are known. Each time you use this ability, the remaining duration of invoke deity decreases by 10 minutes, and you can't use this ability if you have less than 10 minutes remaining of the spell's duration.  Madness: Your voice takes on an eerie, grating quality. As a standard action, you can inflict madness on a creature within 30 feet; that creature must succeed at a Will save or become confused for 1d4 rounds. You cannot target a creature more than once a minute with this effect.  Magic: You shimmer with magical power. You gain spell resistance equal to 11 + your caster level against hostile spells.  Nobility: Your voice becomes resonant and imperious. As a move action, you can issue one order to a single creature within 30 feet. This effect functions as if you had cast the spell command.  Plant: Your appearance becomes plantlike, with leafy hair and green skin. You become immune to paralysis, poison, polymorph effects, sleep effects, and stunning.  Protection: An aura of protective energy surrounds you. Select three of the following spells: delay poison, false life, mage armor, protection from chaos, protection from evil, protection from good, protection from law, resist energy, shield, or shield of faith; you gain the protective benefits of those spells.  Repose: Your eyes become pure, bleak white. You gain a +6 enhancement bonus to Wisdom.  Rune: Your skin is marked with runic tattoos. Your presence does not trigger the effects of glyphs of warding, symbol spells, and similar effects unless you choose to, and you are immune to their harmful effects. You can use read magic at will and can resolve the effects of scrolls using your own caster level rather than the scroll's caster level.  ScalykindB6: Your flesh becomes squamous, and your mouth grows venomous fangs. You gain a bite attack that deals damage as normal for a creature of your size; if you already have a bite attack, the damage increases as if you had increased one size category. Each creature you bite must succeed at a Fortitude save or become sickened for 1d4 rounds (or if already sickened, staggered for 1 round); this is a poison effect.  Strength: Your body visibly ripples with muscle. You gain a +6 enhancement bonus to Strength.  Sun: Your form blazes with solar light. You are immune to blindness, the dazzled condition, and all effects generated by powerful light (such as searing light, sunray, or the blinding light of a shining childB2), and you radiate light as the daylight spell. Creatures that are harmed or hindered by sunlight take a -2 penalty on attack rolls against you, and you gain a +2 bonus on saving throws against effects originating from such creatures.  Travel: Faint afterimages trail behind you when you move. You gain a +6 enhancement bonus to Constitution.  Trickery: Your appearance changes as you desire (as veil, except affecting only yourself). Changing your appearance is a swift action. You gain a +4 bonus on Bluff, Disguise, Sleight of Hand, and Stealth checks.  VoidB6: Your clothes and hair seem to float about you, as if you were adrift in a weightless environment. You are immune to cold damage and no longer need to breathe. You can exist comfortably in the depths of outer space.  War: You are surrounded by the sounds of battle. You gain a +2 insight bonus on attack rolls with your deity's favored weapon and deal an additional 1d6 points of damage with your deity's favored weapon each time you hit a foe. You can use your deity's favored weapon as a divine focus or holy symbol.  Water: You gain gills, webbed fingers, and other ichthyic features. You gain a swim speed of 40 feet, can breathe water, and ignore the usual penalties on weapon attack and damage rolls from fighting underwater.  Weather: Your hair and clothing are constantly wind-tossed, and you crackle with electricity. You do not take penalties or damage or suffer from reduced visibility or other effects due to natural weather. You are immune to electricity damage, and your call lightning and call lightning storm spells and effects always function as though called outdoors in stormy weather.}
        
\DeclareSpell{Judgment Undone}{necromancy () []|V,  S,  M (diamonds worth 50, 000 gp),  F (see text)|10 minutes|touch|Targetsone willing petitioner|instantaneous|none|no}[Restores a petitioner to its mortal life.]
    \DeclareSpellDescription{Judgment Undone}{This powerful, elaborate, and risky spell undoes Pharasma's judgment, returning a willing petitioner to its mortal life. This spell must be cast on the plane to which the petitioner was sent, and the petitioner must be present for the entire casting. In addition, the caster must provide a specific object that the petitioner valued deeply in its mortal life as a focus for the spell. This is different for every petitioner and usually requires research to discover, although those who knew the petitioner well in life can often identify the item easily. At the completion of the spell's casting, the petitioner returns to the mortal form it had as a young adult, with all of its memories and class levels (or equivalent statistics) intact.  The casting of judgment undone is not without risk. The servants of Pharasma vigilantly watch for perversions of the order of fate and death, though it can take time for them to pinpoint disruptions when they occur. After 1d6+5 minutes from the beginning of this spell's 10-minute casting time, an olethrosB6 appears within 50 feet of the caster; this psychopomp demands the caster cease casting the spell immediately and attacks if its request is ignored. The psychopomp never attempts to harm the petitioner unless judgment undone has already been successfully cast by the time the psychopomp arrives, in which case it attempts to eliminate the returned mortal as well. If the caster and returned mortal are no longer present, the olethros does what she can to track both down and exact judgment-how successful she may be depends on the GM's discretion.  The caster of judgment undone can pause the spell's casting for up to 1 minute without causing the spell to fail. During this time, the caster does not need to concentrate on judgment undone and can act normally and cast other spells without disrupting the spell, but if she does not begin casting again before this 1-minute window elapses, the spell fails.  It is possible to cast judgment undone without incurring the wrath of a psychopomp, but doing so requires the caster to first visit the Boneyard and seek out a powerful agent of Pharasma to gain permission to restore the petitioner to its mortal life. The details and difficulty of this task are subject to the GM's discretion, but at the very least should involve a significant expenditure of time and resources. The granting of permission to cast judgment undone is an excellent reward for a quest given to a party of adventurers from a powerful psychopomp. If the PCs exceed expectations in fulfilling this quest, it's not unheard of for the psychopomp to not only grant permission for the spell's casting, but to also provide the diamonds needed for the spell's material component, information about the required focus, or even both. Worshipers of Pharasma who cast this spell without securing permission in this manner are considered to have grossly violated Pharasma's code of conduct.}
        
\DeclareSpell{Positive Pulse}{necromancy () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Area5-ft.-radius burst|instantaneous plus 1 round (see text)|Will negates or Will negates (harmless); see text|yes}[Energy harms undead or bolsters the living.]
    \DeclareSpellDescription{Positive Pulse}{This spell causes a wave of positive energy to spread from a point you designate, damaging foes vulnerable to positive energy and bolstering living creatures. Each creature damaged by positive energy in the area (such as undead) must succeed at a Will save or take 1d6 points of damage, plus 1 point for every 2 caster levels (maximum +5). Haunts manifesting in the spell's area also take this damage.  This spell does not heal creatures healed by positive energy; such creatures instead gain a +2 bonus on saving throws against death effects, energy drain, negative energy, and effects directly caused by haunts. This bonus lasts for 1 round.}
        
\DeclareSpell{Positive Pulse, Greater}{necromancy () []|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Area15-ft.-radius burst|instantaneous plus 1 round (see text)|Will negates or Will negates (harmless); see text|yes}[A large pulse of positive energy damages undead and bolsters living creatures.]
    \DeclareSpellDescription{Positive Pulse, Greater}{This spell functions like positive pulse, except that the damage dealt increases to 3d6 plus your caster level, and the bonus on saving throws increases to +8.}
        
\DeclareSpell{Quintessence Mastery}{transmutation () []|V,  S, M, 500 gp)|1 round or 4 hours; see text|personal or up to 10 10-ft. cubes/level (S)|Effectcontrol over a plane's terrain and traits|1 hour/level or 1 day/level; see text||}[Exercise limited control over the quintessence of an Outer Plane, creating or shaping terrain.]
    \DeclareSpellDescription{Quintessence Mastery}{This spell grants the caster limited control over the quintessence of an Outer Plane. The control granted by quintessence mastery can take one of two forms, depending on the version of the spell cast. Both versions can be cast only on one of the nine Outer Planes, for it is these planes, not the Transitive or Inner Planes, that are comprised of quintessence.  Planewarp: This allows the caster to create various objects or effects. When this spell is cast, you can replicate a number of effects from one or more of the following spells: control water, diminish plants, fog cloud, major creation, move earth, plant growth, secure shelter, soften earth and stone, spike growth, spike stones, stone shape, transmute mud to rock, transmute rock to mud, wall of stone, or wall of thorns. The total spell levels of effects to be created must not exceed 8. For example, you could use this spell to replicate the effects of fog cloud, secure shelter, and soften earth and stone (since these three spells have levels that add up to 8) or diminish plants and spike stones (since these two spells have levels that add up to 7), but not move earth and plant growth (since these two spells have levels that add up to 9). If a spell appears on different spell lists at different levels, use the lowest level-control water, for example, counts as a 4th-level spell even though it's a 6th-level spell for sorcerers and wizards. This list need not be exhaustive; at the GM's discretion, this list may be expanded to include similar spells from other sources or similarly themed effects that do not mimic specific spells. This version of the spell has a casting time of 1 round and lasts for 1 hour per caster level or until its effects are expended.  Shape Realm: This functions similarly to create demiplaneUM, except that it alters an equivalent area of the plane the caster is on rather than creating a self-contained realm on the Astral or Ethereal Plane. You cannot grant the affected area an alignment or essence trait opposed by the plane's traits (such as granting the lawful-aligned trait to a portion of Elysium), and the area is not self-contained. At the GM's discretion, additional restrictions beyond those listed in the create demiplane spell may limit this spell's effects, and additional options for customizing the affected area may be available. This version of the spell has a casting time of 4 hours and lasts for 1 day per caster level. This version of quintessence mastery can be made permanent in the same way and for the same cost as create demiplane. This version of quintessence mastery does not function within the boundaries of a divine realm.}
        
\DeclareSpell{Shadow Invasion}{conjuration (summoning) []|V,  S,  F (a masterwork piercing or slashing weapon)|1 standard action|30 ft.|Area30-ft. radius emanation centered on you|1 round/level (D); see text|none|no}[Create an area of darkness that strengthens shadow spells and attracts kytons.]
    \DeclareSpellDescription{Shadow Invasion}{Using a slashing motion with the spell's focus as part of the casting of shadow invasion, you cut open a rift to the Plane of Shadow that fills a 30-foot area with shadowy energies. This area is stationary and becomes dark and gloomy, reducing the light level by one step (as darkness). Certain spells are enhanced within the area; spells of the shadow subschool that have reduced effects when disbelieved (such as shadow evocation) have their reduced effects increased by 20\% (to a maximum of 90\%) when determining their effects on targets within the area of shadow invasion.  In addition, the rift created by shadow invasion has a chance of attracting attention from the other side, and the spell can be inverted to bring these watchers through. When shadow invasion is dismissed as a standard action, there is a chance that a single evangelist kyton (Pathfinder RPG Bestiary 185) will be summoned under the caster's command (as per summon monster V). This chance is 5\% for every full round that shadow invasion was active. If the caster level of shadow invasion is 16th or greater, this effect summons an interlocutorB3 kyton instead. A kyton summoned this way remains for a number of rounds equal to what the remaining duration of shadow invasion would have been had it not been dismissed. Successfully summoning a kyton this way is a lawful and evil act, as though casting a spell with the lawful and evil descriptors.}
        
\DeclareSpell{Songbird}{conjuration () [good]|S|1 swift action|personal|Targetsyou|1 round||}[Conjure music from a good-aligned plane.]
    \DeclareSpellDescription{Songbird}{You conjure uplifting music from the wilds of Elysium, Heaven, or Nirvana to bolster other musical activities.  If you cast songbird during the same round in which you attempt a Perform check, songbird acts as accompaniment and grants a +3 bonus on that Perform check.  If you cast songbird in the same round in which you activate a bardic performance, that round of bardic performance does not count against your total rounds of bardic performance available for the day.  If you cast songbird in the same round in which you cast a spell with the sonic descriptor, that spell's save DC increases by 1.}
        
\DeclareSpell{Soulseeker}{divination () []|V,  S,  M (incense worth 250 gp),  F (see text)|1 hour|unlimited|Targetsone soul|instantaneous or 1 hour/level|Will negates (see text)|no}[Determine a soul’s location.]
    \DeclareSpellDescription{Soulseeker}{You identify the stage of a given soul's judgment, or determine its fate post-judgment. You must either unambiguously identify  the soul you seek or use the skull of the body the soul vacated as a focus. If the subject does not share your alignment, the soul can attempt a Will save to resist this spell's effects as if it were still alive. If the subject is still alive or its soul has been destroyed, this spell fails without providing any information.  If the soul has not yet been judged and moved on to its final reward or punishment, soulseeker provides an estimate of its location; in most cases, this is somewhere in the River of Souls or the Boneyard. While this may assist in physically traveling to the soul's location, especially in cases involving effects such as soul bind or a devourer's devour soul ability, the spell's primary purpose is to identify how long the subject has been dead (and what form of life-restoring magic is necessary). If the soul has already been judged, soulseeker instead identifies the plane to which the soul has been sent as a petitioner and the petitioner's general location on that plane (such as "Elysium, beneath the boughs of the Witchwood").  If soulseeker is cast on the same plane on which the soul's new petitioner form currently exists, it guides you along the shortest, most direct physical route to the petitioner, as described in find the path. In this case, the spell's duration is 1 hour per level.}
        
\DeclareSpell{Speak With Soul}{necromancy () []|V,  S,  M (a drop of candle wax)|1 minute|10 ft.|Targetssee text|1 minute/level (D)|Will negates; see text|no}[Hold an extended conversation with a soul.]
    \DeclareSpellDescription{Speak With Soul}{You commune with the soul of a dead creature. To cast this spell, you must be at the soul's place of death or be in the soul's presence, whether it is contained in a receptacle, powers an intelligent magic item, or other possibilities. The soul can attempt a Will save to resist the spell as if it were alive.  A soul contacted this way can speak normally in any language it knows. Unlike speak with dead and similar spells, you are not limited to asking questions and can engage in normal conversation with the soul (and vice versa). The soul isn't an undead creature and isn't compelled to speak or be truthful. Generally, the soul only knows what it knew in life, although souls that persisted with awareness of their surroundings after death may have more to offer.}
    