    
\DeclareSpell{Staggering Fall}{transmutation|V,  S|1 immediate action|medium (100 ft. + 10 ft./level)|Targets: one falling creature|1 round/level (see below)|Fort. partial (see below)|yes}[]
    \DeclareSpellDescription{Staggering Fall}{This spell must be cast on a creature as it falls, either from a height or after being knocked prone or tripped. The magic of this spell causes the creature to hit the ground particularly hard, knocking the wind from it. The creature takes an additional 1d6 points of damage from the fall. In addition, the creature becomes staggered for the duration of the spell unless it makes a Will save. Each round the spell's effects persist, the creature may attempt a new Will save as a free action to end the staggered effect early. A creature under the effects of this spell must take a standard action to stand up.}
        
\DeclareSpell{Sheet Lightning}{evocation [electricity]|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Targets: 20-ft.-radius spread|instantaneous|Fortitude partial|yes}[]
    \DeclareSpellDescription{Sheet Lightning}{You create a dazzling flash of electricity that fills the target area. Sheet lightning inflicts 1 point of electricity damage to all creatures within the area of effect (no save). The true power of the spell, though, lies not in the damage it inflicts but in the overwhelming pain the lightning creates. The sudden flash and jolt dazes living creatures for 1 round if they fail a saving throw. Creatures that save are instead dazzled for 1 round. Any creature wearing metal armor takes a -2 penalty to its saving throw against this spell.}
        
\DeclareSpell{Dazzling Blade}{illusion (pattern)|V,  S|1 swift action|touch|Targets: one metal weapon|1 minute/level|Will negates (see text)|yes (harmless, object)}[]
    \DeclareSpellDescription{Dazzling Blade}{Dazzling blade makes a weapon appear dazzlingly shiny, as if crafted from pure silver and heavily polished. In combat, the flashing movements of a dazzling blade become almost hypnotic. The wielder of a weapon under the effects of dazzling blade gains a +1 competence bonus on all Bluff checks made to feint in combat. The wielder also gains a +1 competence bonus on all CMB checks made to disarm a foe, and a +1 competence bonus to his CMD against disarm attempts made against the weapon bearing the dazzling blade effect. This bonus increases by +1 for every 3 caster levels, to a maximum bonus of +5 at 12th level.

The wielder of a dazzling blade can discharge the spell into a blinding burst of silvery light as a free action. The wielder selects an adjacent opponent as the focal point of this burst of light-that creature must make a Will save to avoid being blinded for 1 round (with a successful save, the creature is instead dazzled for 1 round).

Despite its shiny appearance, a dazzling blade grants no extra benefit against creatures that are vulnerable to silver.}
        
\DeclareSpell{Mass Dazzling Blade}{illusion (pattern)|V,  S|1 swift action|close (25 ft. + 5 ft./2 levels)|Targets: One metal weapon/level, no two of which can be more than 30 ft. apart|1 minute/level|Will negates (see text)|yes (harmless, object)}[]
    \DeclareSpellDescription{Mass Dazzling Blade}{This spell functions like dazzling blade, except that it affects multiple weapons. Each wielder of a dazzling blade can discharge the weapon's effect to attempt to blind a foe independently of the others.\\\\

{\centering\bf Dazzling Blade\hrule}

Dazzling blade makes a weapon appear dazzlingly shiny, as if crafted from pure silver and heavily polished. In combat, the flashing movements of a dazzling blade become almost hypnotic. The wielder of a weapon under the effects of dazzling blade gains a +1 competence bonus on all Bluff checks made to feint in combat. The wielder also gains a +1 competence bonus on all CMB checks made to disarm a foe, and a +1 competence bonus to his CMD against disarm attempts made against the weapon bearing the dazzling blade effect. This bonus increases by +1 for every 3 caster levels, to a maximum bonus of +5 at 12th level.

The wielder of a dazzling blade can discharge the spell into a blinding burst of silvery light as a free action. The wielder selects an adjacent opponent as the focal point of this burst of light-that creature must make a Will save to avoid being blinded for 1 round (with a successful save, the creature is instead dazzled for 1 round).

Despite its shiny appearance, a dazzling blade grants no extra benefit against creatures that are vulnerable to silver.}
        
\DeclareSpell{Summon Accuser}{conjuration (summoning) [evil,  lawful]|V,  S,  F/DF (chunk of rotten meat)|1 round|close (25 ft. + 5 ft./2 levels)|Effect: 1 accuser devil|10 minutes/level|none|no}[]
    \DeclareSpellDescription{Summon Accuser}{This spell summons a single accuser devil from Hell to do the spellcaster's bidding, similar to how summon monster spells function. Accuser devils, known to diabolists as zebubs, are hideous flying creatures with the torso of a plump human infant and the body and wings of an enormous fly. They make excellent spies, for they have the ability to grant visions of what they have witnessed to others-the Queen's Hands sometimes use summoned zebubs to observe suspects from afar. Accuser devils are detailed on page 84 of the Pathfinder RPG Bestiary 2.}
        
\DeclareSpell{Summon Infernal Host}{conjuration (summoning) [evil,  lawful]|V,  S,  F/DF (strip of rune-inscribed parchment)|1 round|close (25 ft. + 5 ft./2 levels)|Effect: 1d4+1 lesser host devils or 1 greater host devil|1 round/level|none|no}[]
    \DeclareSpellDescription{Summon Infernal Host}{This spell functions as summon monster V, save that it can only be used to summon host devils. These noxious flying devils, known also as gaavs and magaavs, are detailed on page 58 of Pathfinder Campaign Setting: Princes of Darkness, Book of the Damned, Vol. 1.}
        
\DeclareSpell{Echean's Excellent Enclosure}{abjuration [force]|V,  S,  M (a sphere of glass worth 100 gp and an iron nail,  with which you pierce the glass on casting)|1 standard action|touch|Area: immobile 10-ft.-radius emanation|1 round/level (D)|none|see text}[]
    \DeclareSpellDescription{Echean's Excellent Enclosure}{You call into being around you an invisible barrier of force within which magic cannot persist. Within the area of the spell, effects are suppressed and creatures are affected as by antimagic field. An immobile sphere of impenetrable force surrounds the field, equivalent in all ways to a spherical wall of force, including its immunity to dispel magic and vulnerability to a sphere of annihilation or rod of cancellation. The barrier has hardness 40 and 20 hit points per caster level, and can be damaged by both mundane attacks and spells cast from outside the field. If the bubble of force is destroyed, the spell's duration ends.

Spells cannot be cast within, into, or out of the enclosure, and teleportation effects that ignore a wall of force (such as dimension door or teleport) are thwarted by the enclosure's field of antimagic.

Echean's excellent enclosure has the same effect on summoned creatures of any type and incorporeal undead that an antimagic field does, causing them to wink out of existence for the duration of Echean's excellent enclosure unless their spell resistance, if any, allows them to remain where they are within the field.}
    