    
\DeclareSpell{Antithetical Constraint}{enchantment (compulsion) [mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one living creature|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Antithetical Constraint}{You constrain the target such that the target automatically misses with all attacks made against creatures that are not of the opposite alignment of it. For example, a lawful evil target would automatically fail at all attacks except those made against chaotic good creatures, and a neutral good target would automatically fail at all attacks except those made against neutral evil creatures. For the purposes of antithetical constraint, creatures that are chaotic evil, chaotic good, lawful evil, or lawful good are all considered to have the opposite alignment of a target whose alignment is neutral with no other alignment components. This restriction doesn't apply to effects that do not require attack rolls, such as magic missile.}
        
\DeclareSpell{Recentering Drone}{abjuration|V,  S,  DF|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one creature/2 levels (no two of which may be more than 30 ft. apart)|concentration|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Recentering Drone}{You emit a calming subsonic drone that allows the targets to temporarily refocus and restore their balance when they're suffering from debilitating conditions. A target with the dazzled, fatigued, shaken, or sickened condition ignores the penalties of those conditions for the duration of this spell. A target with one of the following conditions is treated as having the associated lesser condition for the duration of the spell, as shown by the following table.

 ConditionLesser ConditionBlindedDazzledExhaustedFatiguedFrightenedShakenNauseatedSickened    At the end of the spell's duration, the targets are again subject to the appropriate penalties if the original conditions affecting the target are still in effect.}
    