    
\DeclareSpell{Dragon Turtle Shell}{abjuration|V,  S,  M (a piece of turtle shell)|1 standard action|personal|Targets: you|1 round/level||}[]
    \DeclareSpellDescription{Dragon Turtle Shell}{When you are struck by an opponent's natural attacks, the damage is resolved as if the attack came from a creature one size smaller per 5 caster levels (maximum of four size categories smaller at CL 20th). Refer to Table 3-1 in the Pathfinder RPG Bestiary to determine an attack's altered base damage. If the creature's natural attack deals nonstandard damage, refer instead to the Improved Natural Attack feat on page 315 of the Bestiary. It is not possible to reduce the base damage of a creature's natural attack below 1d2 with this spell.}
        
\DeclareSpell{Draconic Suppression}{abjuration|V,  S|1 standard action|close (25 ft. + 5 ft./level)|Targets: one dragon|1 round/level (D)|Fortitude negates|yes}[]
    \DeclareSpellDescription{Draconic Suppression}{A dragon that fails its saving throw cannot use its breath weapon for the duration of the spell and is treated as one age category younger for determining which special abilities it can use. For example, an ancient green dragon would revert to the special abilities of a very old dragon and lose access to its miasma ability and its dominate person spell-like ability. This spell has no effect on a dragon's armor class, feats, frightful presence, hit points, physical attacks, saving throws, senses, size, skills, spellcasting, or statistics.}
        
\DeclareSpell{Dragonvoice}{transmutation|V,  S|1 standard action|personal|Targets: you|1 minute/level||}[]
    \DeclareSpellDescription{Dragonvoice}{By magically altering the way your vocal cords create sounds, you can emulate the vocal inflections of dragons. This grants a +6 circumstance bonus on Charisma checks and Charisma-related skill checks when dealing with dragons.  In addition, your voice is much louder than normal, halving the penalties to others' Perception checks to hear you due to distance, intervening doors, and so on.}
        
\DeclareSpell{Dungeonsight}{divination|V,  S,  F (a small glass orb worth 150 gp)|1 standard action|personal|Area: 60-ft.-radius emanation|instantaneous||}[]
    \DeclareSpellDescription{Dungeonsight}{You receive a clear and memorable view of the layout of chambers, barriers, and connecting passages within the area of effect. This spell does not reveal the contents or inhabitants of any of these locations, only the basic architecture of the space. For example, a staircase leading up to a pair of doors would be apparent, but the iron golems guarding the doors would not. This spell does identify the locations of secret doors and hidden passages but gives no clue as to the means of opening or accessing them.}
        
\DeclareSpell{Erode Defenses}{transmutation|V,  S|1 standard action|close (25 ft. + 5 ft./level)|Targets: one creature|1 round/level|Fortitude negates (see below)|yes}[]
    \DeclareSpellDescription{Erode Defenses}{Your spell slowly begins to eat away at the defenses of your target. If the target fails its saving throw, it loses 1 point from any damage reduction and natural armor bonus it may have. If the initial save was not successful, the target may attempt a new saving throw each round for the duration of the spell or continue to suffer cumulative losses. If the first save fails but a subsequent save succeeds, the eroding effects stop at that point, though any of the penalties already accrued remain until the spell expires. At the end of the spell's duration, the target's damage reduction and natural armor bonus immediately return to normal.  Only one erode defenses spell can affect a particular target at any one time.}
        
\DeclareSpell{Gravity Well}{transmutation|V,  S,  M (a small lead weight)|1 standard action|medium (100 ft. + 10 ft./level)|Targets: one creature|1 round/level (D)|Fortitude negates|no}[]
    \DeclareSpellDescription{Gravity Well}{You bring into being a localized region of increased gravity that crushes a creature to the ground. Affected targets weigh twice as much as normal, can move only at half speed, jump only half as far as normal, and can lift and carry only half as much as normal. Any flying target has its maneuverability worsened by two steps (from good to poor, for example; minimum clumsy) and plummets to the ground unless it succeeds at a DC 25 Fly check to remain in the air.  Freedom of movement negates the effects of this spell. A creature targeted by gravity well behaves normally in the area of a reverse gravity spell.}
        
\DeclareSpell{Heart Of The Mammoth}{transmutation|V,  S,  F (a fetish of mammoth hair soaked in dragon's blood)|1 standard action|touch|Targets: creature touched|1 round/level|Will (harmless)|no}[]
    \DeclareSpellDescription{Heart Of The Mammoth}{The target creature becomes stronger, hardier, and imbued with the courage of the greatest megafauna of the tundra. The spell grants a +8 enhancement bonus to Strength and Constitution, immunity to fear, a +4 morale bonus to Will saves, and doubles the critical threat range of all its attacks against creatures of the dragon type (this does not stack with Improved Critical, keen edge, or similar effects).}
        
\DeclareSpell{Illusory Hoard}{illusion (phantasm) [mind-affecting]|S,  M (an item from the hoard,  see below)|1 standard action|medium (100 ft. + 10 ft./level)|Targets: one creature|1 hour/level (D)|Will negates (and see below)|yes}[]
    \DeclareSpellDescription{Illusory Hoard}{The spell forces the target to believe that nothing in its hoard is missing or has been disturbed. This spell fools all the senses, convincing the target that its hoard feels and behaves as it should. Only if the target tries to use an item from this illusory hoard for some other purpose does it receive another saving throw to disbelieve the effects of the spell (a wizard trying to use an illusory wand or a dragon trying to unlock a door with an illusory key). For the purposes of this spell, a hoard is any amount of treasure that is too big to be carried by the treasure's owner without magical tools such as bags of holding or portable holes, such as a dragon's hoard, a king's treasury, a merchant's strongbox, or a thief's hidden cache.  The material component is any item worth 10 gp or more taken from the original hoard. This item is consumed by the spell.}
    