    
\DeclareSpell{Halfling Vengeance}{divination|V,  S|1 standard action|touch|Targets: one Small or smaller creature touched|1 round/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Halfling Vengeance}{You grant the touched target the ability to ascertain the weaknesses of foes. The target deals an additional 1d6 points of precision damage on successful attacks with daggers or slings against foes within 30 feet, as long as the attacked foe is denied its Dexterity bonus to Armor Class or is flanked by the target. This additional damage increases by 1d6 for every 4 caster levels you have beyond 3rd, to a maximum of 5d6 at 19th level. This bonus damage is precision damage and stacks with other sources of precision damage, such as sneak attack. This bonus damage is not multiplied on a critical hit.  Once per round on a successful attack that deals this precision damage, the target can choose to forgo 2d6 points of precision damage (either granted by this spell or from other sources of precision damage, such as sneak attack) to inflict one of the following conditions on the attacked foe for 1 round:   The attacked foe can't make attacks of opportunity against creatures smaller than it.   The attacked foe is denied its Dexterity bonus to Armor Class against attacks made with daggers or slings.   The attacked foe takes a -2 penalty on attacks against creatures smaller than it.   The attacked foe can't take 5-foot steps.  A creature can benefit from only one halfling vengeance spell at a time.}
        
\DeclareSpell{Mass Halfling Vengeance}{divination|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one Small or smaller creature/level, no two of which can be more than 30 ft. apart|1 round/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Mass Halfling Vengeance}{This spell functions like halfling vengeance, except that it affects multiple creatures.\\\\

{\centering\bf Halfling Vengeance\hrule}

You grant the touched target the ability to ascertain the weaknesses of foes. The target deals an additional 1d6 points of precision damage on successful attacks with daggers or slings against foes within 30 feet, as long as the attacked foe is denied its Dexterity bonus to Armor Class or is flanked by the target. This additional damage increases by 1d6 for every 4 caster levels you have beyond 3rd, to a maximum of 5d6 at 19th level. This bonus damage is precision damage and stacks with other sources of precision damage, such as sneak attack. This bonus damage is not multiplied on a critical hit.  Once per round on a successful attack that deals this precision damage, the target can choose to forgo 2d6 points of precision damage (either granted by this spell or from other sources of precision damage, such as sneak attack) to inflict one of the following conditions on the attacked foe for 1 round:   The attacked foe can't make attacks of opportunity against creatures smaller than it.   The attacked foe is denied its Dexterity bonus to Armor Class against attacks made with daggers or slings.   The attacked foe takes a -2 penalty on attacks against creatures smaller than it.   The attacked foe can't take 5-foot steps.  A creature can benefit from only one halfling vengeance spell at a time.}
        
\DeclareSpell{Word Of Beckoning}{conjuration (teleportation)|V,  S,  M/DF (fine copper wire)|10 minutes|see text|Targets: one creature|1 round; see text|none|no}[]
    \DeclareSpellDescription{Word Of Beckoning}{This spell functions like sending, except the subject also receives knowledge of a command word that, when spoken, summons you to the open space nearest to the subject.  The subject must speak the command word within 1 round of knowing it to summon you, although the subject isn't obligated to speak it. You can be transported any distance within a plane but cannot travel between planes. You can bring along objects as long as their weight doesn't exceed your maximum load. You may also bring one additional willing Medium or smaller creature (carrying gear or objects up to its maximum load) or its equivalent per three caster levels. A Large creature counts as two Medium creatures, a Huge creature counts as four Medium creatures, and so forth. All creatures to be transported must be in contact with one another, and at least one of those creatures must be in contact with you.\\\\

{\centering\bf Sending\hrule}

You contact a particular creature with which you are familiar and send a short message of 25 words or less to the subject. The subject recognizes you if it knows you. It can answer in like manner immediately. A creature with an Intelligence score as low as 1 can understand the sending, though the subject's ability to react is limited as normal by its Intelligence. Even if the sending is received, the subject is not obligated to act upon it in any manner.

If the creature in question is not on the same plane of existence as you are, there is a 5\% chance that the sending does not arrive. (Local conditions on other planes may worsen this chance considerably.)}
    