    
\DeclareSpell{Apsu's Shining Scales}{evocation () [draconic,  good]|V,  S,  M (a drop of mercury)|1 standard action|personal|Targetsyou|1 minute/level|Will negates (harmless)|no}[]
    \DeclareSpellDescription{Apsu's Shining Scales}{You envelop your body with silver radiance that manifests as scales surrounding your body, granting you a +5 armor bonus to your AC and causing your natural attacks and unarmed strikes to bypass damage reduction as if they were good and silver weapons.  Whenever you attack with a breath weapon (including effects that are similar to a dragon's breath weapon, such as an elixir of dragon breath or the dragon's breathAPG spell), you can discharge the Apsu's shining scales spell as a swift action in order to infuse your breath with silver light, causing any evil creature caught within the area of the breath to take a -4 penalty on its Reflex save and to lose the benefits of the evasion ability against that breath weapon attack. Evil creatures with improved evasion are instead treated as if they had only evasion when attempting to save against this breath weapon attack.  Clerics, inquisitors, oracles, paladins, and warpriests who worship Apsu add Apsu's shining scales to their class spell lists as a 3rd-level spell.}
        
\DeclareSpell{Dahak's Release}{enchantment (compulsion) [draconic,  evil,  mind-affecting]|V,  S,  M (a dried drop of blood)|1 standard action|touch|Targetscreature touched|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Dahak's Release}{You unleash all the target's anger and destructive urges, causing it to fly into a violent bloodlust. The target attacks creatures as determined by the following table. If a creature is killed or the target is for some reason unable to effectively attack it, roll on the table again to select a new action for the target.     d\%Behavior1-25Target attacks the creature nearest to it.26-75Target attacks its nearest ally.76-100Target always attacks the last creature to attack it.     Beginning on its next turn, the target attacks the subject determined by the chart with a melee weapon, natural weapon, or supernatural ability that deals damage. If necessary, it moves to or charges to the subject in order to make this attack. If it is unable to reach its subject on its next turn, the target uses its turn to get as close as possible to the subject of its bloodlust. The target gains a +2 morale bonus on attack and damage rolls, and cannot use any Charisma-, Dexterity-, or Intelligence-based skills (except Acrobatics, Fly, Intimidate, and Ride) or any abilities that require patience or concentration. This spell is otherwise treated as confusion and rage-any creature immune to confusion or rage is immune to this spell, and any ability or effect that ends confusion or rage (such as calm emotions) can end this spell.  Antipaladins, bloodragers, clerics, and inquisitors who worship Dahak add Dahak's release to their spell lists as a 4th-level spell.}
        
\DeclareSpell{Draconic Ally}{conjuration (creation) [draconic]|V,  S,  M (a scale from a dragon and 250 gp)|10 minutes|close (25 ft. + 5 ft./2 levels)|Effectone intelligent draconic servant|1 day/level (D)|none|no}[]
    \DeclareSpellDescription{Draconic Ally}{You create a semi-living intelligent draconic servant that loyally obeys and serves you. Treat this servant as a pseudodragon with all of the abilities granted by one of the following spells: form of the alien dragon I, form of the dragon I, or form of the exotic dragon I. Your draconic ally can use its breath weapon once per day. Once conjured, the creature is not limited to the spell's range, and can go a considerable distance to carry out missions at your command. The draconic ally speaks one language of your choice that you know. You cannot have more than one draconic ally at a time. As long as a previous ally exists, you cannot successfully cast  this spell again. If you have a breath weapon, you can cast this spell as a standard action by expending one use of your breath weapon as a free action when you cast the spell.  Clerics, inquisitors, oracles, and warpriests who worship Apsu or Dahak add draconic ally to their spell lists as a 3rd-level spell.}
        
\DeclareSpell{Draconic Malice}{enchantment () [draconic]|V,  S|1 standard action|personal|Effect10-foot aura centered on you|1 minute/level|Will negates (harmless)|no}[]
    \DeclareSpellDescription{Draconic Malice}{You surround yourself with a palpable aura of draconic fear and dread. Living creatures within this aura that are normally immune to fear or mind-affecting abilities lose those immunities against your spells, spell-like abilities, and supernatural abilities that create fear effects, as well as any Intimidate checks you attempt to demoralize foes.  If you have the antipaladin aura of cowardice class feature, this spell instead changes the penalty imposed by aura of cowardice to -6 for its duration.}
        
\DeclareSpell{Form Of The Alien Dragon I}{transmutation (polymorph) []|V,  S,  M (a scale of the dragon type you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)|see text|no}[]
    \DeclareSpellDescription{Form Of The Alien Dragon I}{You become a Medium esoteric or outer dragon. Psychics can choose from the esoteric dragon (astral, dream, etheric, nightmare, or occult) forms only. You gain a +4 size bonus to your Strength, a +2 size bonus to your Constitution, a +4 natural armor bonus, a fly speed of 60 feet (poor), darkvision with a range of 60 feet, a breath weapon, and resistance to one form of energy or effect. You also gain one bite attack (1d8), two claw attacks (1d6), and two wing attacks (1d4). Your breath weapon and resistance depend on the type of dragon. You can use the breath weapon only once per casting of this spell. All breath weapons deal 6d8 points of damage unless noted otherwise and allow a Reflex save to halve the normal damage. In addition, some of the dragon types grant additional abilities, as noted below.  Astral Dragon: 30-foot cone of force (damage dice are d4s instead of d8s), psychic resilience (Pathfinder RPG Bestiary 5 297).  Dream Dragon: 30-foot cone of electricity, dream fortress, dreamsight (Bestiary 5 90).  Etheric Dragon: 30-foot line of force (damage dice are d4s instead of d8s), gaseous form (only when taking no actions other than move actions for a round, and only for a maximum of 1 round/caster level for each casting of form of the alien dragon).  Lunar Dragon: 60-foot line of cold, cold resistance 20, burrow 20 feet.  Nightmare Dragon: 30-foot cone of acid, see in darkness, +4 on saves vs. mind-affecting effects.  Occult Dragon: 30-foot cone of cold or fire, +4 resistance bonus on saving throws against evil spells and effects, natural armor bonus to AC increases to +6.  Solar Dragon: 60-foot line of fire, fire resistance 30, vulnerability to cold.  Time Dragon: 30-foot cone of electricity, cold resistance 20, +4 bonus on initiative checks.  Void Dragon: 30-foot cone of cold, cold resistance 20, +4 bonus on saves vs. emotion spells and effects.  Vortex Dragon: 30-foot cone of fire, fire resistance 30, vulnerability to cold.}
        
\DeclareSpell{Form Of The Alien Dragon II}{transmutation (polymorph) []|V,  S,  M (a scale of the dragon type you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)|see text|no}[]
    \DeclareSpellDescription{Form Of The Alien Dragon II}{This spell functions as per form of the alien dragon I, except it also allows you to assume the form of a Large esoteric or outer dragon. Psychics can choose from the esoteric dragon (astral, dream, etheric, nightmare, or occult) forms only. You gain the following abilities: a +6 size bonus to your Strength, a +4 size bonus to your Constitution, a +6 natural armor bonus, a fly speed of 90 feet (poor), darkvision with a range of 60 feet, a breath weapon, damage reduction 5/magic, and resistance to one form of energy or effect. You also gain one bite attack (2d6), two claw attacks (1d8), a tail slap attack (1d8), and two wing attacks (1d6). All breath weapons deal 6d8 points of damage unless noted otherwise and allow a Reflex save to halve the normal damage. Line breath weapons increase to 80-foot lines and cones increase to 40-foot cones.}
        
\DeclareSpell{Form Of The Alien Dragon III}{transmutation (polymorph) []|V,  S,  M (a scale of the dragon type you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)|see text|no}[]
    \DeclareSpellDescription{Form Of The Alien Dragon III}{This spell functions as per form of the alien dragon II, except it also allows you to take the form of a Huge esoteric or outer dragon. Psychics can choose from the esoteric dragon (astral, dream, etheric, nightmare, or occult) forms only. You gain the following: a +10 size bonus to your Strength, a +8 size bonus to your Constitution, a +8 natural armor bonus, a fly speed of 120 feet (poor), blindsense with a range of 60 feet, darkvision with a range of 120 feet, a breath weapon, damage reduction 10/magic, frightful presence (DC = DC for this spell), and immunity to one form of energy or effect (of the same type form of the alien dragon I grants either a bonus against or resistance to, if any). You also gain one bite attack (2d8), two claw attacks (2d6), two wing attacks (1d8), and one tail slap attack (2d6). You can use the breath weapon as often as you like, but must wait 1d4 rounds between uses. All breath weapons deal 12d8 points of damage unless noted otherwise and allow a Reflex save to halve the normal damage. Line breath weapons increase to 100-foot lines and cones increase to 50-foot cones.}
        
\DeclareSpell{Form Of The Exotic Dragon I}{transmutation (polymorph) []|V,  S,  M (a scale of the dragon type you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)|see below|no}[]
    \DeclareSpellDescription{Form Of The Exotic Dragon I}{You become a Medium imperial or primal dragon. Druids can choose from the primal dragon (brine, cloud, crystal, magma, or umbral) forms only. You gain a +4 size bonus to your Strength, a +2 size bonus to your Constitution, a +4 natural armor bonus, a fly speed of 60 feet (poor), darkvision with a range of 60 feet, a breath weapon, and either resistance to one form of energy or some other bonus. You also gain one bite attack (1d8), two claw attacks (1d6), and either a gore attack (1d8) if you assume the form of an imperial dragon or two wing attacks (1d4) if you assume the form of a primal dragon. Your breath weapon, resistance, and any other benefits you gain depend on the type of dragon. You can use the breath weapon only once per casting of this spell. All breath weapons deal 6d8 points of damage unless noted otherwise and allow a Reflex save to halve the normal damage. In addition, some of the dragon types grant additional abilities, as noted below.  Brine Dragon: 60-foot line of acid, acid resistance 20, swim 60 feet.  Cloud Dragon: 30-foot cone of electricity, electricity resistance 20, swim 40 feet.  Crystal Dragon: 30-foot cone of sonic (damage dice are d6s instead of d8s), sonic resistance 20, climb 20 feet, burrow 20 feet.  Forest Dragon: 30-foot cone of piercing, burrow 20 feet, climb 30 feet.  Magma Dragon: 30-foot cone of fire, fire resistance 30, vulnerability to cold.  Sea Dragon: 30-foot cone of fire, electricity resistance 20, swim 40 feet.  Sky Dragon: 30-foot cone of electricity, electricity resistance 20, improve fly speed maneuverability to average.  Sovereign Dragon: 30-foot cone of sonic (damage dice are d6s instead of d8s), spell resistance equal to 13 + the spell's level.  Umbral Dragon: 30-foot cone of negative energy (damage dice are d6s instead of d8s; doesn't heal undead creatures), cold resistance 20, +4 on saves vs. death effects.  Underworld Dragon: 30-foot cone of fire, fire resistance 20, vulnerability to cold, burrow 20 feet.}
        
\DeclareSpell{Form Of The Exotic Dragon II}{transmutation (polymorph) []|V,  S,  M (a scale of the dragon type you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)|see below|no}[]
    \DeclareSpellDescription{Form Of The Exotic Dragon II}{This spell functions as per form of the exotic dragon I, except it also allows you to assume the form of a Large imperial or primal dragon. Druids can choose from the primal dragon (brine, cloud, crystal, magma, or umbral) forms only. You gain the following abilities: a +6 size bonus to your Strength, a +4 size bonus to your Constitution, a +6 natural armor bonus, a fly speed of 90 feet (poor), darkvision with a range of 60 feet, a breath weapon, damage reduction 5/magic, and resistance to one form of energy or some other bonus. You gain one bite attack (2d6), two claw attacks (1d8), a tail slap attack (1d8), and either a gore attack (2d6) if you assume the form of an imperial dragon or two wing attacks (1d6) if you assume the form of a primal dragon. All breath weapons deal 8d8 points of damage unless noted and allow a Reflex save to halve the normal damage. Line breath weapons increase to 80-foot lines and cones increase to 40-foot cones.}
        
\DeclareSpell{Form Of The Exotic Dragon III}{transmutation (polymorph) []|V,  S,  M (a scale of the dragon type you plan to assume)|1 standard action|personal|Targetsyou|1 minute/level (D)|see below|no}[]
    \DeclareSpellDescription{Form Of The Exotic Dragon III}{This spell functions as per form of the exotic dragon II except that it also allows you to take the form of a Huge imperial or primal dragon. Druids can choose from the primal dragon (brine, cloud, crystal, magma, or umbral) forms only. You gain the following abilities: a +10 size bonus to your Strength, a +8 size bonus to your Constitution, a +8 natural armor bonus, a fly speed of 120 feet (poor), blindsense with a range of 60 feet, darkvision with a range of 120 feet, a breath weapon, damage reduction 10/ magic, frightful presence (DC = DC for this spell), and immunity to one form of energy (of the same type form of the exotic dragon I grants a resistance to, if any). You gain one bite attack (2d8), two claw attacks (2d6), a one tail slap attack (2d6), and either a gore attack (2d8) if you assume the form of an imperial dragon or two wing attacks (1d8) if you assume the form of a primal dragon. You can use the breath weapon as often as you like, but must wait 1d4 rounds between uses. All breath weapons deal 12d8 points of damage unless noted otherwise and allow a Reflex save to halve the normal damage. Line breath weapons increase to 100-foot lines and cones increase to 50-foot cones.}
        
\DeclareSpell{Hermean Potential}{enchantment (compulsion) [mind-affecting]|V,  S,  F (a gold dragon scale)|1 standard action|touch|Targetscreature touched|1 minute/level|Will negates (harmless)|no}[]
    \DeclareSpellDescription{Hermean Potential}{You gift the target with the ability to perfect its actions via mental clarity. On the next attack roll, saving throw, ability check, or skill check the target attempts, it rolls twice and takes the more favorable result. For every 5 caster levels you have, the target can roll twice on an additional attack roll, saving throw, ability check, or skill check (to a maximum of 5 rolls at 20th level).  Hermean potential is countered and dispelled by ill omenAPG, but does not itself counter or dispel ill omen.}
        
\DeclareSpell{Scales Of Deflection}{abjuration () [draconic]|V,  M (a dragon scale)|1 standard action|personal|Targetsyou|1 minute/level (see text)||}[]
    \DeclareSpellDescription{Scales Of Deflection}{Brilliant draconic iconography matching your draconic heritage (or a kind of dragon whose alignment matches your own) surrounds you. Any touch attack attempted against you resolves against your normal AC. Once such an attack has been resolved, this spell is dismissed at the end of your next turn.}
        
\DeclareSpell{Tail Strike}{transmutation () [draconic]|V,  M (a dragon scale)|1 standard action|personal|Targetsyou|1 minute/level (see text)||}[]
    \DeclareSpellDescription{Tail Strike}{You grow a draconic tail (clothing and armor adjust as necessary), or if you already have a tail, it takes on a draconic appearance. If you have a draconic bloodline, the tail matches the appearance of that dragon type; otherwise, it matches the appearance of a dragon type whose alignment matches your own. You gain a tail slam attack that deals 1d6 points of damage (1d4 if Small, 1d8 if Large) + your Strength modifier. If you already have a tail attack, you instead extend the reach of your tail attack by 5 feet. If you have a tail sweep attack, this spell increases its radius by 10 feet.  If used as part of a full-attack action, the tail slam is considered a secondary attack, is made at your full base attack bonus - 5, and adds half your Strength modifier to its damage. You can end this spell before its normal duration by uttering a bestial roar as a swift action. When you do, you can attempt an Intimidate check to demoralize all foes within a 30-foot radius that can hear the roar.  Clerics, inquisitors, oracles, and warpriests who worship dragon deities add tail strike to their class spell lists as a 4th-level spell.}
    