\DeclareSpell{Amanuensis}{Transmutation|V, S|1 standard action|Close|Target: Object or objects with writing|10 minutes/level|Will Negates (Object)|Yes (Object)}[Copies nonmagical text.]
\DeclareSpellDescription{Amanuensis}{
	You point at the writing and then move your hand as though holding a stylus or quill. As you intone the spell, the script appears on a sheet of paper close at hand.
	
	You cause writing from one source (such as a book) to be copied into a book, paper, or parchment. This spell copies 250 words per minute and creates a perfect duplicate of the original. The spell copies only nonmagical text, not illustrations or magical writings (such as the text of a spellbook, a spell scroll, or a sepia snake sigil). If the target contains normal and magical writing (such as a letter with explosive runes), only the normal text is copied, leaving blank space in the copied text where the magical writing would be expected. Likewise, if the target contains text and illustration, only the text is copied.
	
	The spell triggers (but does not copy) writing-based magic traps in the material being copied.
	
	Blank paper, parchment, or a book must be provided for the spell to write upon. If the target has multiple pages, the spell automatically turns to the next blank page whenever necessary. If more pages in the target exist than blank pages are available, the spell copies the original until it runs out of
	blank pages. At any time during the spell's duration you can redirect the magic to copy from another target, copy onto a different blank source, or resume a duplication that was interrupted by a shortfall of blank pages.
	
	The spell does not translate the copied writing. If you do not understand the original, you have no additional ability to understand the copy.
}

\DeclareSpell{Detect Faerie}{Divination|V, S, DF|1 standard action|60 ft.|Area:Cone-shaped emanation|Concentration, up to 10 min./ level (D)|None|No}[Detects the presence of fey creatures]
\DeclareSpellDescription{Detect Faerie}{
	You can sense the influences of Faerie. The amount of information revealed depends on how long you study a particular area or subject.
	
	1st Round
	
	Presence or absence of Faerie influences.
	
	2nd Round
	
	Number of Faerie auras (creatures, objects, or spells) in the area and the power of the most potent Faerie aura present.
	
	
	If the strongest Faerie aura's power is overwhelming (see below), and the HD or level of the aura's source is at least twice your character level, you are stunned for 1 round and the spell ends.
	
	3rd Round
	
	The power and location of each aura. If an aura is outside your line of sight, then you discern its direction but not its exact location.
	
	Aura Power
	
	A Faerie aura's power depends on the type of fey creature or object that you're detecting and its HD, caster level, or (in the case of a druid) class level; see the accompanying table. If an aura falls into more than one strength category, the spell indicates the stronger of the two.
	
	Lingering Aura
	
	An evil aura lingers after its original source dissipates (in the case of a spell) or is destroyed (in the case of a creature or magic item). If detect evil is cast and directed at such a location, the spell indicates an aura strength of dim (even weaker than a faint aura). How long the aura lingers at this dim level depends on its original power:
	
	
	Animals, traps, poisons, and other potential perils are not evil, and as such this spell does not detect them.
	
	
	Each round, you can turn to detect evil in a new area. The spell can penetrate barriers, but 1 foot of stone, 1 inch of common metal, a thin sheet of lead, or 3 feet of wood or dirt blocks it.
}