    
\DeclareSpell{Alter Summoned Monster}{conjuration (summoning)|V,  S|1 standard action|close (25 ft. + 5 ft./ 2 levels)|Targets: one summoned creature|instantaneous|Will negates|yes}[]
    \DeclareSpellDescription{Alter Summoned Monster}{You swap a creature summoned by a conjuration (summoning) spell for a creature you could summon with a summon monster or summon nature's ally spell. The new creature must be an option from a spell of the same level or lower as the spell that summoned the target. The new creature cannot be summoned into an environment that cannot support it. The target can attempt a Will saving throw to negate this effect, but if the target is under your control, it receives no saving throw. Alter summoned monster does not alter the duration of the spell that summoned the target, nor does it affect any additional creatures summoned by the same spell as the target. The new creature has the same conditions and amount of damage as the target creature, and remains affected by all curses, diseases, poisons, and penalties that affected the target, but no other spells or effects carry over. Alter summoned monster is a spell of the same alignment type or types as the creature for which you exchange the target. An eidolon can't be targeted by this spell.}
        
\DeclareSpell{Final Sacrifice}{evocation|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one summoned creature|instantaneous|Fortitude negates, then Reflex half (see text)|yes}[]
    \DeclareSpellDescription{Final Sacrifice}{You disrupt the conjuring energies within a summoned creature, causing it to violently explode. If the target fails its Fortitude save, it is immediately slain and all creatures within 20 feet of the target take 1d4 points of damage per spell level of the  summoning spell that conjured the target. This damage is fire damage unless the target creature has the cold or water subtype, in which case it's cold damage. Creatures caught in this explosion take half damage if they succeed at their Reflex saves against this spell's DC. Final sacrifice can detonate a summoner's eidolon, though an eidolon receives a +4 bonus on its Fortitude save unless the spell is cast by the eidolon's own summoner. If this spell targets an eidolon, creatures within 20 feet of the eidolon take an amount of damage equal to 1d4 + 1/2 the caster level of the summoner who controlled the eidolon.}
        
\DeclareSpell{Gird Ally}{abjuration|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: one summoned creature you control/level, no two of which can be more than 30 ft. apart|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Gird Ally}{You create a magical field around summoned creatures you control that deflects attacks made against them. The targets gain a deflection bonus to their AC equal to 1 + 1 for every 6 caster levels you possess (maximum +4 deflection bonus at 18th level). A summoner can target his eidolon with this spell.}
        
\DeclareSpell{Instant Restoration}{conjuration (healing)|V,  S,  F/DF (a thimble of water and a seed)|1 immediate action|close (25 ft. + 5 ft./2 levels)|Targets: one summoned creature you control|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Instant Restoration}{Instant restoration channels planar energy into a summoned creature. This spell can be cast as an immediate action when a summoned creature you control drops to 0 or fewer hit points. Rather than immediately disappear, the creature is healed for 4d8 hp + 1 hit point per caster level (maximum 4d8+10 hit points). If this healing brings your summoned creature's hit point total to 1 or more hit points, it remains as if its hit points had never dropped to 0 or fewer. Creatures slain by death effects cannot be saved by instant restoration. A summoner can target his eidolon with this spell.}
        
\DeclareSpell{Master's Escape}{conjuration (teleportation)|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels)|Targets: you and one summoned creature you control|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Master's Escape}{You create an extradimensional link between yourself and one summoned creature you control that allows you to switch places. After casting master's escape, you can teleport to your summoned creature's space as a swift action, causing your summoned creature to teleport to your former space. If your summoned creature is reduced to 0 or fewer hit points before you can use this spell's effect, you can teleport to a space that you can see within 30 feet as an immediate action. After using either of these effects, the spell ends. A summoner can target his eidolon with this spell.}
        
\DeclareSpell{Master's Mutation}{transmutation (polymorph)|V,  S|1 standard action|close (25 ft. + 5 ft./level)|Targets: you and one summoned creature you control|1 round/level (D)|none|no}[]
    \DeclareSpellDescription{Master's Mutation}{You can mold the ephemeral substance of the Outer Planes, mutating one summoned creature that you control to better suit your needs. Select up to two of the following abilities and grant them to the target for the spell's duration: burrow 30 feet, climb 40 feet, constrict, darkvision 90 feet, ferocity, fly 60 feet (average maneuverability), grab, jet, low-light vision, poison, rake, scent, swim 60 feet, trample, trip, or water breathing. Additionally, instead of selecting an ability, you can replace one of the target's primary natural attacks with another natural attack that deals the same amount of damage, such as replacing a Medium target's bite attack (1d6) with a gore attack (1d6). If you choose to alter a creature's natural attacks, all attacks of the chosen type are altered. A summoner can target his eidolon with this spell.}
        
\DeclareSpell{Summon Laborers}{conjuration (summoning)|V,  S,  F/DF (a strip of rune-inscribed parchment)|10 minutes|close (25 ft. + 5 ft./2 levels)|Effect: one summoned petitioner/caster level|8 hours (D)|none|no}[]
    \DeclareSpellDescription{Summon Laborers}{Summon laborers summons one humanoid petitioner per caster level. These petitioners hail from one plane of your choice and perform tasks at your direction. The petitioners cannot fight or travel to dangerous lands, but do assist your downtime activities (Pathfinder RPG Ultimate Campaign 8 4) w ithin a s ettlement, increasing the effect of Influence or Labor you spend by 50\%, to  a maximum of 1 additional point of Influence or Labor for every 2 caster levels you possess. This stacks with any increase to the effect of Influence or Labor that you receive from your followers within the settlement where the downtime activity takes place (if any). Summon laborers is a spell of the same alignment type as the plane from which the summoned petitioners hail (chaotic and evil for the Abyss, lawful and good for Heaven, and so on). Effects that increase the number of creatures summoned by a spell (such as Superior SummoningUM) do not affect summon laborers.}
    