    
\DeclareSpell{Grand Curse}{necromancy () [curse]|V,  S,  DF|1 standard action or see below|close (25 ft. +5 ft./2 levels)|Areasee below|permanent|Will negates|yes}[]
    \DeclareSpellDescription{Grand Curse}{You can use the grand curse to duplicate the effects of major curse, except the DC to remove the curse is equal to the save DC +10, or the grand curse can be used to place a permanent curse on an area.
If used to place a curse on an area, the caster may affect one 10 ft. by 10 ft. square per caster level.
The nature of the grand curse is decided by the spellcaster upon conclusion of the ritual, which takes 1 hour to complete; any of the effects of bestow curse may be placed upon the area, and any time a target comes into contact with the area they are subject to the curse. If another spell effect is desired, the grand curse may duplicate any compulsion spell of 4th level or less. The player should be creative with the types of curses available, but should be in line with the above restrictions.}
        
\DeclareSpell{Mage's Evasion}{evocation () []|V,  S,  M,  (quicksilver,  and an eyelash from the caster),  F (silver statuette of the caster worth 5, 000 gp)|at least 10 minutes; see text|personal|Targetsyou|1day/level or until discharged||}[]
    \DeclareSpellDescription{Mage's Evasion}{This powerful variant of the contingency spell transfers you and everything you carry (except for other creatures or objects that weigh more than 50 pounds) to a destination you designate at the time of casting. When casting mage's evasion, you must specify the locale and detail up to six specific conditions that trigger this spell. When any of these conditions occurs, your body, mind, and soul are transported to the target destination. The location can be any place you have familiarity (studied carefully, as defined by the teleport spell), even another plane.
When casting the spell, you cast greater teleport and possibly other spells that take effect when you arrive at your destination point. The 10 minute casting time is the minimum total for all spells cast (if the companion spells have combined times longer than 10 minutes, use the combined casting times instead). In addition to any material components required by the companion spells, the initial casting of mage's evasion drains 1d6 hp from the spellcaster. These hit points are "stored" in the spell, and may be regained by the caster normally.
The stored hit points are immediately recovered by the caster upon the triggering of the evasion.
The greater teleport aspect of this spell takes you to your destination, so any condition that prevents teleporting also prevents mage's evasion. Once reaching the destination point, the companion spells included in the evasion instantly and simultaneously take effect. The companion spells must be ones that have a range of personal and be of a spell level no higher than one-third of your caster level. The total combined level of companion spells may not exceed your caster level. The conditions you specify to bring the spell into effect must be clear, although they can be general in nature (see the contingency spell, in the Pathfinder Roleplaying Game Core Rulebook for guidelines).
The spell pulls together your mind, body, and soul if they have been separated. For example, if your soul is trapped in a magic jar when the evasion is triggered, your soul returns to your body (breaking the magic jar spell).If your body or soul has been bound (for example, with a binding, imprisonment, or trap the soul spell), you must succeed at a opposed caster level check (DC 11 + the caster level of the person who cast the trapping spell) to break free.
You may only use one mage's evasion spell at a time; if a second is cast, or if a contingency spell is cast, the first spell (if still active) is dispelled.}
        
\DeclareSpell{Chant}{conjuration (creation) []|V,  S,  DF|1 standard action|40 ft.|Areaall allies and foes within a 40-ft. burst centered on you|concentration; maximum 5 min./level (see below)|none|no}[]
    \DeclareSpellDescription{Chant}{As long as you chant, you bring special favor upon your allies and bring disfavor to your enemies. You and your allies gain a +1 luck bonus on attack rolls, weapon damage rolls, saves, and skill checks while your foes take a -1 penalty on such rolls.  You must chant in a clear voice. Any interruption in your chanting, such as a failed concentration check, a silence spell or speaking or casting another spell, ends this spell. As an exception to the general rule, the effects of this spell stack with those of a prayer spell if cast by a cleric of your alignment and who worships the same deity as you.}
    