    
\DeclareSpell{Blood Rage}{enchantment (compulsion) [mind-affecting]|V,  S,  M (a drop of blood from each creature to be affected)|1 standard action|close (25 ft. + 5 ft./level)|Targets: one willing living creature per 2 levels, no two of which may be more than 30 ft. apart|1 round/level|Will negates (harmless)|yes (harmless)}[]
    \DeclareSpellDescription{Blood Rage}{The targets of this spell become angrier as they fight, the pain of their wounds fueling their strength. An affected creature gains a cumulative +2 morale bonus to Strength and a cumulative -1 penalty to AC for every 5 points of damage it takes (maximum +10 Strength, -5 AC) for the duration of the spell. These bonuses last until the spell expires or the target falls unconscious.}
        
\DeclareSpell{Shield The Banner}{abjuration|V,  S,  DF|1 standard action|touch|Targets: standard touched|1 minute/level|Will negates|no}[]
    \DeclareSpellDescription{Shield The Banner}{This spell is used to protect one of a tribe's most valuable possessions: its tribal banner. Any creature (other than a member of the tribe which the standard represents) attempting to directly attack or touch the standard must make a Will save. This spell functions as sanctuary, but only protects a standard or banner. In addition, the spell grants a +2 bonus to the standard's hardness, and +10 to the standard's hit points for the duration of the spell.}
        
\DeclareSpell{Vigor}{transmutation|V,  S|1 standard action|touch|Targets: creature touched|1 minute or until discharged|Will negates (harmless)|yes}[]
    \DeclareSpellDescription{Vigor}{This spell infuses the subject with a small surge of strength.

The creature gets a +1 competence bonus on a single melee damage roll. It must choose to use the bonus before making the roll to which it applies. Ranged or spell attacks are unaffected by this spell.}
    