    
\DeclareSpell{Protection From Spores}{abjuration () []|V,  S|1 standard action|touch|Targetscreature touched|1 minute/level|Fortitude negates (harmless)|no}[]
    \DeclareSpellDescription{Protection From Spores}{With a touch, you bolster a creature's body to protect it from the harmful effects of spores and similar afflictions. While under the effect of this spell, a creature is immune to the effects of brown mold, green slime, russet mold, yellow mold, and any similar hazard, provided the hazard is CR 6 or lower. Similarly, the creature is immune to poison, disease, and infestation attacks from all fungal creatures of CR 6 or lower, including  effects such as basidirond spores, violet fungus rot, and the like. The target is immune to fungus-based toxins, such as striped toadstool. Against similar hazards or monsters of CR 7 or higher, the target gains a bonus on all saving throws against the effect equal to half your caster level. Protection from spores offers no protection against fungal infestations created by the seeded, by the spell what grows within, or by Xhamen-Dor.}
        
\DeclareSpell{What Grows Within}{necromancy () [evil]|V|1 swift action|personal|Effectyou|1 round/level|see text|no}[]
    \DeclareSpellDescription{What Grows Within}{By speaking the name "Xhamen-Dor," you infuse yourself with the essence of the Inmost Blot and gain a +3 profane bonus on Will saving throws for the spell's duration. When you prepare what grows within for the first time, or the first time you use it via a spell-completion or spell-trigger item, you can thereafter be targeted by Xhamen-Dor's infected dreams ability (see page 86). As long as you are under the effects of what grows within, your mind-affecting spells carry this supernatural taint within them and can infect those who succumb to those effects. Whenever you successfully affect a creature with one of your mind-affecting spells (this requires the target to fail its saving throw against the spell if the spell allows a save, but automatically affects a target if the spell does not allow a saving throw), that target must also succeed at a Fortitude saving throw against what grows within or it immediately becomes afflicted by a lesser version of Xhamen-Dor's seeded infestation. This infestation does not expose the victim to Xhamen-Dor's infectious dreams, but it can ultimately  result in that creature's transformation into one of the seeded. Each time you affect a creature with what grows within in this manner, the remaining duration of what grows within is reduced by 1 round. If you affect multiple creatures in a round, you choose the order in which they must save against the effects of what grows within, and reduce the spell's remaining duration by 1 round each time one of them is affected by the infestation.  Lesser Seeded Infestation-save Fortitude DC = spell's save DC; onset immediate; frequency 1/day; effect 1d4 Constitution drain; cure none. This infestation can be cured by magic alone. A creature whose Constitution is reduced to 0 by this infestation dies and rises from death in 1d4 rounds as a seeded creature (see page 90). This is an infestation effect.}
    