    
\DeclareSpell{Blot}{transmutation () []|V,  S,  M (a bit of cloth made wet with saliva)|1 standard action|close (25 ft. + 5 ft/2 levels)|Area10 ft.-radius burst|24 hours|Will negates (object)|yes (object)}[]
    \DeclareSpellDescription{Blot}{This spell reduces all types of writing and other recognizable symbols found on any sort of surface within range into illegible smears. It affects books, carvings on stone, or even tattoos with equal ease. It does not affect writing that is not actually on a surface, such as an illusion, projection, reflection, or anything similar. Spellbooks and magical items that contain writing (such as scrolls) gain a saving throw to resist the effects of this spell. Against magical writing created by spell effects (such as glyphs of warding or symbols), blot instead functions as a dispel magic spell capable of targeting all such spell effects in the area. This spell has no on writing found on artifacts or similarly unique surfaces.}
        
\DeclareSpell{Fire Sneeze}{evocation () [air,  fire]|V,  S,  M (hot pepper soaked in oil)|1 standard action|personal|Targetsyou|1 round + 1 round/2 levels|Reflex half|yes}[]
    \DeclareSpellDescription{Fire Sneeze}{This spell causes you to begin sneezing gouts of fire that can not only set creatures ablaze but also drop them flat on their backs.
Once you cast this spell, you must sneeze each round as a standard action-you can take no other standard action as long as this spell is in effect, nor can you take full-round actions. Each time you sneeze, you produce a 10-foot-long cone of fire and wind. All creatures caught in this cone take 2d6 points of fire damage-a successful Reflex save halves this damage. Any creature that fails to resist this spell with a Reflex save must immediately make a DC 12 Fortitude save or be knocked prone by the blast of wind associated with the sneeze.}
        
\DeclareSpell{Limp Lash}{necromancy () []|V,  S,  M (a dead wasp)|1 standard action|20 ft.|Targets1 creature|special (see below)|none|yes}[]
    \DeclareSpellDescription{Limp Lash}{You create a dark whip-shaped field of energy that wraps around an enemy's neck, leaving everything except his head paralyzed until you let go of the whip or it is destroyed. You must make a ranged touch attack with this spell. If you strike your target, he takes a 1d6 penalty to his Strength, Dexterity, and Constitution each round.
This penalty cannot reduce any attribute to less than 1, and once any of these attributes reaches 1 the target collapses and his body, except his head, becomes paralyzed. While paralyzed in this way, the target retains full use of his senses, including the ability to feel pain, and can speak (including casting spells with only verbal components). The whip has a maximum length of 20 feet, 15 hit points, and a hardness of 5. The spell ends immediately if you let go of the whip or it is destroyed. When the spell ends, all penalties the target took from this spell also end.}
    