    
\DeclareSpell{Illusory Maze}{illusion (figment) []|V,  S|1 standard action|medium (100 ft. + 10 ft./level)|Area20-ft.-radius spread|1 round/level|Will disbelief (if interacted with)|yes}[]
    \DeclareSpellDescription{Illusory Maze}{This spell creates the illusion of a translucent, ever-changing maze of glass in the target area. Creatures in the area who believe the maze to be real cannot move more than 5 feet continuously in any one direction and can't move diagonally, forcing them to take a circuitous route to their destination.}
        
\DeclareSpell{Make Lost}{enchantment (compulsion) [mind-affecting]|V,  S|1 round|close (25 ft. + 5 ft./2 levels)|Targetsone creature/level, no two of which can be more than 30 ft. apart|instantaneous|Will negates|yes}[]
    \DeclareSpellDescription{Make Lost}{You strip the targets of their senses of direction and recent memories of travel. They immediately forget the route they  took in the last hour (but not details of encounters along the way) and become lost (Pathfinder RPG Core Rulebook 424).}
        
\DeclareSpell{Mind Maze}{enchantment (compulsion) [mind-affecting]|V,  S,  M/DF (a chicken skull)|1 standard action|medium (100 ft. + 10 ft./level)|Targetsone living creature|1 round/level|Will negates|yes}[]
    \DeclareSpellDescription{Mind Maze}{This spell causes the target to act as though it's wandering through a maze. While under the effects of the spell, the target can't make attacks or cast spells and must take at least one move action each round to walk in a random direction determined using the guidelines for missed splash weapons (Core Rulebook 202). The target must move at its maximum speed during this required movement, though additional move actions after the first can cover shorter distances. If this movement takes the target into a dangerous area, such as through a threatened square or off a ledge, the target receives a second saving throw to end the effect before moving into peril. Walking into a harmless obstacle, such as a wall, ends the target's movement.}
        
\DeclareSpell{Puzzle Box}{enchantment (compulsion) [curseUM,  mind-affecting]|V,  S|1 standard action|close (25 ft. + 5 ft./2 levels) or touch; see text|Targetsone creature or one object up to 5 lbs./level|1 round/level or permanent; see text|Will negates or none|yes}[]
    \DeclareSpellDescription{Puzzle Box}{This spell causes even commonly used objects to become conundrums. When cast on a creature, the target loses all weapon and shield proficiencies. The target also forgets how to use all spell-completion, spell-trigger, and use-activated magic items, as well as any mundane items used as part of a skill check, imposing a -5 penalty on all ability and skill checks attempted with such items. These effects last for 1 round per level. As a move action, the target can attempt a skill check to negate the effects of this spell for one object. Weapons, shields, and mundane objects require a successful Craft skill check of the type required to craft the item in question, with a DC equal to the spell's save DC. Magic items require a successful Spellcraft or Use Magic Device skill check against the spell's save DC.  Alternatively, this spell can be cast on a single touched object that weighs up to 5 pounds per the caster's level. Use of this object becomes a puzzle even to those previously familiar with it. Any creature attempting to use an item affected in this way is treated as though the creature was the target of puzzle box for that item only. When cast on an object, the duration of this spell is permanent.}
    